### 2015-12-09 paperReviews.tex
getting a start

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Paper summaries of related work}
\author{}
\date{December 2015}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Introduction}
Give a short description of papers that are useful.

\section{\cite{yin2011}}
Surveys a data set of approximately 500 (mis)configuration file and classifies the types of errors. 
Gives a frequency for each classification.
The frequency for the errors we are interested in are as follows: (a) = 15\%,...

\includegraphics[width=\textwidth]{configErrors.png}

\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2015-12-10 proposedSolution.tex
outline of algo

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Proposed Solution}
\author{}
\date{December 2015}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{color}

\definecolor{identifierColor}{rgb}{0.65,0.16,0.16}
\definecolor{comment_color}{rgb}{0.40,0.46,0.3}
\definecolor{num_color}{gray}{0.55}
\lstset{
  basicstyle=\footnotesize,
  breaklines=true,
  frame=bottomline,
  language=haskell,
  %identifierstyle=\color{identifierColor},
  morecomment=[l][\color{comment_color}\ttfamily]{--},
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  %captionpos=b,                    % sets the caption-position to bottom
  %commentstyle=\color{mygreen},    % comment style
  %frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  otherkeywords={*,let, Server, Replication, FaultGraph, rankRCG, print, fialProb, goal, ...},           % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{num_color}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  %title=\lstname                  % show the filename of files included with \lstinputlisting; also try caption instead of title
  mathescape=true,
  tabsize=3,
  literate=*{->}{{\textcolor{blue}{$\to$}}}{1}
           {<-}{{\textcolor{blue}{$\leftarrow$}}}{1}
}

\begin{document}

\maketitle

\section{Introduction}
In order to solve the misconfiguration problems outlined in \cite{yin2011}, we take a two stage process.

\begin{enumerate}
  \item Preprocessor
  \begin{enumerate}
    \item Given a set of config files in a language $[C_{httpd}]$, convert them to a set $[D]$ in our language.
    \item Learn constraints on syntax based on $[D]$ to generate the rule set $R_{httpd}$
  \end{enumerate}
  \item Usertime checking
  \begin{enumerate}
    \item convert a given configuration file $c_{httpd}$, into a file $d$, in our own language.
    \item check $d$ against $R_{httpd}$ and report errors to user.
  \end{enumerate}
\end{enumerate}

Expressed in pseduocode:

\begin{lstlisting}
main = 
  r = preproc learningSet
  e = usertime r userFile

preproc :: [ConfigFile a] -> (RuleSet,a)
preproc cs =
  ds = map convert cs 
  rules = learnOn ds
  fileType = getType cs
  return (rules,fileType)

convert :: ConfigFile a -> ConfigFile Common
getType :: [ConfigFile a] -> a
learnOn :: [ConfigFile Common] -> RuleSet

usertime :: (RuleSet,a) -> ConfigFile a -> Maybe Error
usertime r c =
  d = convert c
  e = verifyOn r d
  return e
\end{lstlisting}

\section{Preprocessor}
The first step is to use a \texttt{CONVERTER} to translate any config file type (httpd,MySQL,etc.) to a common format. 
Our \texttt{LEARNER} for learning constaints will depend on all files having a common format. 
The types of constraints, and the proposed solution to learn such constraints are outlined here.

\subsection{Format - Lexical}
This problem is exemplified in box (a) of the image.

\subsection{Format - Syntax}
This problem is exemplified in box (b) and (c) of the image.

\subsection{Value - Value Inconsistency}
This problem is exemplified in box (f) (g) and (h) of the image.

\section{Usertime Checking}

\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2015-12-10 proposedSolution.tex
rough approach to types of errors

@@
 \subsection{Format - Lexical}
-This problem is exemplified in box (a) of the image.
+This problem is exemplified in box (a) of the image - a certain parameter cannot contain lowercase values.
+To build these rules, we collect every instance of setting that parameter over $[D]$, then infer a partition (like strisynth) on those examples.
 
@@
 This problem is exemplified in box (b) and (c) of the image.
+These are ordering/dependency errors and require analysis over multiple lines.
+Looking for substrings over lines can solve (b).
+Not sure about (c)
 
@@
 This problem is exemplified in box (f) (g) and (h) of the image.
+I don't understand (f), how can we know if query.log is a file or a table.
+
+Interger constraints are hard to find since we dont know which ones are supposed to be coorelated.
+Maybe we can build constraints between all integers in a file, then remove constraints as we see counter examples.
+Is this counter-example guided synthesis?
 

### 2015-12-12 proposedSolution.tex
starting some examples
writing pseduocode

@@
   return e
+
+data RuleSet = {Lexical = [Clause], Syntax = [Clause], Value = [Clause]}
 \end{lstlisting}
@@
 
+\begin{lstlisting}
+learnOn :: [ConfigFile Common] -> RuleSet
+learnOn cs = 
+  rs = map genConstraints cs
+  foldl1 mergeRules rs
+
+genConstraints :: ConfigFile Common -> RuleSet
+genConstraints c =
+  r1 = learnLexicalConstraints c
+  r2 = learnSyntaxConstraints c
+  r3 = learnValueConstraints c
+  return RuleSet {r1, r2, r3}
+
+mergeRules :: RuleSet -> RuleSet -> RuleSet
+mergeRules rs rs' =
+  return RuleSet
+    { mergeLex (Lexical rs) (Lexical rs')
+    , mergeSyn (Syntax rs)  (Syntax rs')
+    , mergeVal (Value rs)   (Value rs')}
+\end{lstlisting}
+
 \subsection{Format - Lexical}
@@
 
+\begin{lstlisting}
+learnLexicalConstraints :: ConfigFile Common -> [Clause]
+learnLexicalConstraints =
+
+mergeLex =
+  strisynth?
+\end{lstlisting}
+
 \subsection{Format - Syntax}
@@
 These are ordering/dependency errors and require analysis over multiple lines.
-Looking for substrings over lines can solve (b).
-Not sure about (c)
+
+\begin{lstlisting}
+learnSyntaxConstraints :: ConfigFile Common -> [Clause]
+learnSyntaxConstraints c =
+  ls = lines c
+  concatMap (makeOrderPairs ls) ls
+
+makeOrderPairs :: [Text] -> Text -> [(Text,Text)]
+makeOrderPairs ls l = 
+  map (,l) ls
+
+mergeSyn :: [Clause] -> [Clause] -> [Clause]
+mergeSyn curr new =
+  combined = intersect curr new
+  return combined
+\end{lstlisting}
 
@@
 
+\begin{lstlisting}
+learnValueConstraints :: Config Common -> RuleSet
+learnValueConstraints c =
+  ls = lines cs
+  tys = seperateValsOnType ls :: [(Type,Text)]
+  concatMap (makeRelations tys) tys
+
+makeRelations :: [(Type,Text)] -> (Type,Text)
+makeRelations ts (ty,tx) =
+  map (f (ty,tx)) ts
+  f (ty,tx) (ty',tx') = if ty==ty' then synthesizeComparison ty tx tx' else []
+
+synthesizeComparison :: Type -> Text -> Text -> Clause
+synthesizeComparison Int t t' =
+  if t<t' then "t<t'"
+  if t==t' then "t==t'"
+  ...
+synthesizeComparison String t t' =
+synthesizeComparison IP t t' =
+...
+
+mergeVal rs rs' = 
+\end{lstlisting}
+
 \section{Usertime Checking}

### 2015-12-21 paper/proposedSolution.tex
reorganize

--- 2015-12-10 proposedSolution.tex
@@
 
-\begin{lstlisting}
-main = 
-  r = preproc learningSet
-  e = usertime r userFile
-
-preproc :: [ConfigFile a] -> (RuleSet,a)
-preproc cs =
-  ds = map convert cs 
-  rules = learnOn ds
-  fileType = getType cs
-  return (rules,fileType)
-
-convert :: ConfigFile a -> ConfigFile Common
-getType :: [ConfigFile a] -> a
-learnOn :: [ConfigFile Common] -> RuleSet
-
-usertime :: (RuleSet,a) -> ConfigFile a -> Maybe Error
-usertime r c =
-  d = convert c
-  e = verifyOn r d
-  return e
-\end{lstlisting}
-
 \section{Preprocessor}
@@
 
+\begin{lstlisting}
+\end{lstlisting}
+
 \subsection{Format - Lexical}
@@
 
+\begin{lstlisting}
+\end{lstlisting}
+
 \subsection{Format - Syntax}
@@
 These are ordering/dependency errors and require analysis over multiple lines.
-Looking for substrings over lines can solve (b).
-Not sure about (c)
+
+\begin{lstlisting}
+\end{lstlisting}
 
@@
 
+\begin{lstlisting}
+\end{lstlisting}
+
 \section{Usertime Checking}

### 2015-12-21 code/Main.hs

@@ -1,0 +1,9 @@
+module Main where
+
+import Preproc
+import Usertime
+
+main = 
+  r = preproc learningSet
+  e = usertime r userFile
+

### 2015-12-21 code/Preproc.hs

@@ -1,0 +1,51 @@
+module Preproc where
+
+preproc :: [ConfigFile a] -> (RuleSet,a)
+preproc cs =
+  ds = map convert cs 
+  rules = learnOn ds
+  fileType = getType cs
+  return (rules,fileType)
+
+learnOn :: [ConfigFile Common] -> RuleSet
+learnOn cs = 
+  rs = map genConstraints cs
+  foldl1 mergeRules rs
+
+genConstraints :: ConfigFile Common -> RuleSet
+genConstraints c =
+  r1 = learnLexicalConstraints c
+  r2 = learnSyntaxConstraints c
+  r3 = learnValueConstraints c
+  return RuleSet {r1, r2, r3}
+
+mergeRules :: RuleSet -> RuleSet -> RuleSet
+mergeRules rs rs' =
+  return RuleSet
+    { mergeLex (Lexical rs) (Lexical rs')
+    , mergeSyn (Syntax rs)  (Syntax rs')
+    , mergeVal (Value rs)   (Value rs')}
+
+learnLexicalConstraints :: ConfigFile Common -> [Clause]
+learnLexicalConstraints =
+  
+
+mergeLex =
+  strisynth?
+
+learnSyntaxConstraints :: ConfigFile Common -> [Clause]
+learnSyntaxConstraints c =
+  ls = lines c
+  concatMap (makeOrderPairs ls) ls
+  
+makeOrderPairs :: [Text] -> Text -> [(Text,Text)]
+makeOrderPairs ls l = 
+  map (,l) ls
+
+mergeSyn :: [Clause] -> [Clause] -> [Clause]
+mergeSyn curr new =
+  combined = intersect curr new
+  return combined
+
+learnValueConstraints :: Config Common -> RuleSet
+learnValueConstraints c =

### 2015-12-21 code/Types.hs

@@ -1,0 +1,7 @@
+module Types where
+
+convert :: ConfigFile a -> ConfigFile Common
+getType :: [ConfigFile a] -> a
+
+data RuleSet = {Lexical = [Clause], Syntax = [Clause], Value = [Clause]}
+data ConfigFile a = (Filepath, a)

### 2015-12-21 code/Usertime.hs

@@ -1,0 +1,10 @@
+module Usertime where
+
+import Types
+
+usertime :: (RuleSet,a) -> ConfigFile a -> Maybe Error
+usertime r c =
+  d = convert c
+  e = verifyOn r d
+  return e
+

### 2016-01-25 abs.tex
porting from yale repo

\begin{abstract}

Software failures resulting from configuration errors 
have been commonplaces as modern software systems 
become increasingly larger and more complex.
The lack of language constructs in configuration files, 
such as types and grammars, 
directed the focus of a configuration file verification 
towards building post-failure error diagnosis tools. 
In addition, the existing tools are generally language
specific, requiring the user to define at least a grammar for the language
models and explicit rules to check. 
In this paper, we propose a framework which analyzes
datasets of correct configuration files and derives rules for building a
language model for the given dataset. 
The resulting language model can be used
to verify new configuration files and detect errors in them. 
Our proposed framework is highly modular, 
does not rely on the system source code, and
can be applied to any new configuration file type with minimal user input.  
Our tool, named \app, relies on an abstract representation of language 
rules to allow for this modularity. 
\app supports learning of various rules, such as orderings,
value relations, and type errors, 
by defining a minimal interface for a rule, and by using a probabilistic types inference stategy.

\end{abstract}

### 2016-01-25 abs_systems.tex
porting from yale repo

\begin{abstract}

Software failures resulting from configuration errors have been
commonplaces as modern software systems become increasingly larger
and more complex. Although existing efforts aim to overcome
misconfiguration problems by either building post-failure error diagnosis 
tools or hardening systems based on misconfiguration reports, these
retroactive solutions, nevertheless, require human (\eg, user) 
intervention, thus leading to impractical administration cost. 
%especially in large-scale software systems. 
Complementing existing post-failure forensics, 
this paper proposes, \app, a {\em proactive} misconfiguration checker.
With \app in hand, the users of software systems can submit their
configuration files to \app for misconfiguration detection
{\em before} deploying them in the real software settings.
At the heart of \app lies a machine learning mechanism, 
which learns rules and constraints from pluggable 
correct sampling configuration files, 
and then detects errors violating the learned constraints.
\app mainly offers three significant benefits.
First, there is no any extra burden added to users who only need to 
simply use \app as a ``seamless'' pre-checker for their configurations.
Second, because many misconfiguration errors have been eliminated 
by \app, the workloads of post-failure forensics in runtime
are significantly reduced, thus making these tools truly practical.
Finally, since there have been many correct but not specific 
example configuration files in practice, 
increasingly more samples can be freely added to \app,
thus giving \app evolutionary capability.

\end{abstract}

### 2016-01-25 design.tex
porting from yale repo

\section{\app Design}

\xxx{
\app Design: 
  \begin{itemize}
  \item Present an architecture of \app with a fig. Briefly describe 
    how it works (step by step).
  \item Detail learner part
  \item Merge
  \item Check 
  \item Limitations
  \end{itemize}
}

A rule R is added to the set of all rules,
  if $\exists$ learning file f s.t. R(f) is non vacuously true
That rule R is then removed from the set of all rules,
  if $\exists$ learning file f st R(f) is false.

This is accomplished in two passes.
First we collect all possible rules for every file.
Then we merge the all the rules to create our final set.
This conviently gives rise to an embarresingly parallel situation, which Haskell allows us to easily take advantage of by
  using the parallel mapping library parmap.

\begin{lstlisting}
  potentialRules = parmap findAllRules learningSet.
  finalRules = foldl1 mergeRules potenialRules
\end{lstlisting}

Each rule is of the Attribute typeclass, which means a rule must support the following operations:
\begin{lstlisting}
class Attribute r where
  learn :: ConfigFile Common -> [r]
  merge :: [r] -> [r] -> [r] 
  check :: [r] -> ConfigFile Common -> Error
\end{lstlisting}

\subsection{learn}
  For a single given file, we take very line ordering to be a rule.
\subsection{merge}
  Then when merging these sets of rules, we take the intersection of the rules infered on the individual files.
  Maybe we could also do something like only taking rules that show up multiple times.
\subsection{check}
  To check a file by using a rule set, we simply take all the rules that are releveant to the user's file.
  Rules that are relavent are the ones where both parts of the ordering are present.
  We learn the rule set for the user file, and every rule in the learned set must be present in the user file.

### 2016-01-25 intro.tex
porting from yale repo

\section{Introduction}

Configuration errors are one of the most important root-causes of 
modern software system failures~\cite{xu15systems,yin11anempirical}. 
In practice, misconfiguration problems may result in 
security vulnerabilities,
application crashes, severe disruptions in software functionality,
and incorrect program executions%
~\cite{xu15systems,zhang14encore,yuan11context}.
Although several efforts have been proposed to automate configuration
error diagnosis after failures occur%
~\cite{wang04automatic,attariyan10automating,%
su07autobash,whitaker04configuration}, 
they rely on manual ways to understand and detect the failure symptoms.
Such solutions typically incur high administration cost (\eg, 
requiring users to write pattern-matching scripts) 
and are unreliable (\eg, some errors may show no user-visible symptoms).
These shortcomings often lead to prolonged delays between
the occurrence and the detection of errors, thus causing unrecoverable
damage to system states.

We expect to explore a fundamentally different means to tackle 
the misconfiguration problem. Rather than using retroactive approaches
to deal with configuration errors after the software failures occur, 
we would like to {\em proactively} prevent misconfiguration problems 
{\em before} users first deploy the configuration files to 
their system settings. In other words, we aim to offer users 
a configuration error filter in order to significantly minimize 
the probability of misconfigurations in the system runtime.

Based on the above intuition, this paper presents \app, 
a proactive misconfiguration checker which takes users' 
configuration files as input and then reports potential configuration 
errors to the users before they deploy their systems 
according to these configurations.
At the heart of \app lies a machine learning mechanism, 
which learns rules and constraints from pluggable 
correct sampling configuration files (\ie, for the training purposes), 
and then detects errors violating the learned constraints.

\app mainly offers users three significant benefits.
First, there is no any extra burden added to users who only need to 
simply use \app as a ``seamless'' pre-checker for their configurations.
Second, because many misconfiguration errors have been eliminated 
by \app, the workloads of post-failure forensics in runtime
are significantly reduced, thus making these tools truly practical.
Finally, since there have been many correct but not specific 
example configuration files in practice, 
increasingly more samples can be freely added to \app,
thus giving \app evolutionary capability.

Using these ideas, we make the following contriubtions:

\begin{enumerate}

  \item Our tool, \app can learn a language model from a set of examples of correct configuration files, and use the model to verify new files.
  \item We present a probabalistic type that can be used to assign a confidence distribution over a set of types to a valule.
  \item In \app, we define a minimal interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.

\end{enumerate}

### 2016-01-25 related.tex
porting from yale repo

\section{Related Work and Conclusions}

\xxx{conclude here ...}

### 2016-01-25 code/Convert.hs

@@ -1,0 +1,60 @@
+{-# LANGUAGE OverloadedStrings #-}
+{-# LANGUAGE RecordWildCards#-}
+
+module Convert where
+
+import Types
+
+import qualified Data.Text as T
+import qualified Data.Map as M
+import Control.Monad 
+
+import Data.List.Unique as L
+
+import Debug.Trace
+
+convert ::  TypeMap -> ConfigFile Language -> IRConfigFile
+convert tyMap f =
+  map (addConfigType tyMap) (parse f)
+
+addConfigType :: TypeMap -> (Keyword,Value) -> IRLine
+addConfigType tyMap (keyword,value) = 
+  case M.lookup keyword tyMap of
+    Just configType -> IRLine{..}
+    Nothing -> IRLine{configType = emptyConfigQType,..}
+
+-- | If the user wants to give hints to how to parse a config file based on filetype they go here
+parse :: ConfigFile Language -> [(Keyword,Value)]
+parse (t, l) = 
+  let
+    noComments = (map (stripComment l) $ T.lines t)
+    noEmpty = filter (not. T.null) noComments
+    noEmptyAsKV = map seperateVals noEmpty
+    noDups = foldl (\rs r -> makeUniq rs r) [] noEmptyAsKV
+  in
+    noEmptyAsKV
+    --noDups
+
+makeUniq :: [(Keyword,Value)] -> (Keyword,Value) -> [(Keyword,Value)]
+makeUniq rs (k,v) = 
+  let
+   c = L.countElem k (map fst rs)
+   k' = if c >= 2 then T.append k (T.pack $show c) else k
+  in
+   rs ++ [(k',v)]
+ 
+stripComment :: Language -> T.Text -> T.Text
+stripComment l t = case l of
+  MySQL -> T.takeWhile (/='#') t
+  HTTPD -> T.takeWhile  (/=';') t
+
+-- | for now we are just using spaces and = to seperate keywords and values
+seperateVals :: T.Text -> (Keyword,Value)
+seperateVals t = 
+  let
+    ts = T.split isDelimeter (T.strip t)
+    isDelimeter c = (c=='=') || (c==' ')
+  in
+    (head ts, last ts)
+
+

### 2016-01-25 code/Learners.hs

@@ -1,0 +1,5 @@
+module Learners where
+
+import Order
+import IntRel
+import Missing

### 2016-01-25 code/Learners/IntRel.hs

@@ -1,0 +1,71 @@
+{-# LANGUAGE TupleSections #-}
+{-# LANGUAGE FlexibleInstances #-}
+{-# LANGUAGE RecordWildCards #-}
+
+module IntRel where
+
+import Types
+import qualified Data.Text as T
+import qualified Data.Text.IO as T
+import qualified Data.List as L
+import qualified Data.Map as M
+
+import Debug.Trace
+
+-- I haven't found a nice package for SMTLIB format in haskell yet, its out there tho, im sure
+
+instance Attribute IntRelRule where
+  learn ts =
+    let
+      ts' = pairs $ filter couldBeInt ts
+      rules = foldl (\rs p -> rs ++ findeqRules p) [] ts'
+    in
+      rules
+
+  check rs f = 
+    let
+     fRules = learn f 
+     diff = trace ("RS"++(show rs)) rs L.\\ traceShow fRules fRules
+    in
+     if null diff then Nothing else Just ("ERROR on Int relations"++ (show diff))
+  
+  merge curr new = L.unionBy (sameKeyRel) curr new
+
+-- | remove rules with mathcing keys, but diff formulas
+sameKeyRel :: IntRelRule -> IntRelRule -> Bool
+sameKeyRel r1 r2 = 
+   not $
+    (l1 r1) == (l1 r2) && (l2 r2) == (l2 r2) && (formula r1) /= (formula r2) 
+
+findeqRules :: (IRLine,IRLine) -> [IntRelRule]
+findeqRules (l1,l2) = 
+  let
+    getI = read . T.unpack . value 
+    i1 = getI l1 :: Int  
+    i2 = getI l2 :: Int  
+    makeR f = if f i1 i2 then [IntRelRule {formula = (f),l1=keyword l1, l2=keyword l2}] else []
+  in
+    makeR (==) ++ makeR (<=) ++ makeR (>=)
+
+-- only for comparators! careful!
+instance Eq (Int -> Int -> Bool) where
+  (==) f1 f2 = 
+    (f1 1 1) == (f2 1 1) &&
+    (f1 0 1) == (f2 0 1) &&
+    (f1 1 0) == (f2 1 0)
+
+instance Eq IntRelRule where
+  (==) r1 r2 = 
+    (formula r1) == (formula r2) && 
+    (l1 r1) == (l1 r2) &&
+    (l2 r1) == (l2 r2)
+ 
[…]

### 2016-01-25 code/Learners/Missing.hs

@@ -1,0 +1,43 @@
+{-# LANGUAGE TupleSections #-}
+
+module Missing where
+
+import Types
+import qualified Data.Text as T
+import qualified Data.Text.IO as T
+import qualified Data.List as L
+import qualified Data.Map as M
+
+import Debug.Trace
+
+
+instance Attribute MissingKVRule where
+  learn [] = []
+  learn (l:ls) = concatMap (\l' -> if (keyword l == keyword l') then [] else [MissingKVRule l l']) ls ++ learn ls
+
+  check rs f = 
+   let
+     fRules = learn f
+     diff = rs L.\\ fRules --the difference between the two rule sets
+     x = if null diff then Nothing else Just $ "Error in Missing Keyword-value Entry on "++(show diff)
+   in 
+    x
+  
+  merge curr new = L.intersect curr new
+
+  
+instance Attribute MissingKRule where
+  learn [] = []
+  learn (l:ls) = concatMap (\l' -> if (keyword l == keyword l') then [] else [MissingKRule (keyword l) (keyword l')]) ls ++ learn ls
+
+  check rs f = 
+   let
+     fRules = learn f
+     rs' = L.nub rs
+     diff = rs' L.\\ fRules --the difference between the two rule sets
+     x = if null diff then Nothing else Just $ "Error in Missing Keyword Entry on "++(show diff)
+   in 
+     x
+  
+  merge curr new = L.intersect curr new
+

### 2016-01-25 code/Learners/Order.hs

@@ -1,56 +1,45 @@
 {-# LANGUAGE TupleSections #-}
 {-# LANGUAGE FlexibleInstances #-}
 
--- {-# LANGUAGE LambdaCase #-}
--- {-# LANGUAGE TypeSynonymInstances #-}
-
 module Order where
 
 import Types
 import qualified Data.Text as T
 import qualified Data.Text.IO as T
 import qualified Data.List as L
+import qualified Data.Map as M
 
 import Debug.Trace
 
--- essential we reduce the problem to finding ordering pairs that are always true
--- pairs that hold over the whole learning set become rules at usertime
--- [[A,B,C],[A,C,B]] -> [(A,B),(A,C)]
 
-instance Attribute SynRule where
-  learn = learnOrderConstraints
-  check = checkSyn
-  merge = mergeSyn
+instance Attribute OrdRule where
+  learn f = pairs f
 
-learnOrderConstraints :: ConfigFile Common -> [SynRule]
-learnOrderConstraints (t,c) = 
-  makeOrderPairs $ T.lines t
-
-
--- | honestly, i thought this would be approximately correct
--- but by pure luck seems to be exactly correct
-checkSyn :: [SynRule] -> ConfigFile Common -> Bool
-checkSyn rs f = let
-  fileAsLines = T.lines (fst f)
-  f' = makeOrderPairs fileAsLines
-  diff = (filter (hasRuleFor fileAsLines) rs)  L.\\ f' --the difference between the two rule sets
-  x = if diff == f' then True else trace (show diff) False
-  in x
+  check rs f = 
+   let
+     relevantRules = filter (hasRuleFor f) (rs)
+     fRules = learn f
+     diff = traceMe relevantRules L.\\ fRules --the difference between the two rule sets
+     x = if null diff then Nothing else Just $ "Error in ordering on "++(show diff)
+   in 
+    x
   
-hasRuleFor :: [T.Text] -> SynRule -> Bool
+  merge curr new = L.intersect curr new
+
+-- | is the rule relevant to the file
+--   ie have we seen the (keyword, value) pairing before
+hasRuleFor :: [IRLine] -> OrdRule -> Bool
 hasRuleFor ts r = 
-  elem (snd r) ts && elem (fst r) ts
[…]

### 2016-01-25 code/Learners/Values.hs

@@ -1,16 +1,0 @@
-{-# LANGUAGE FlexibleInstances #-}
-
-module Values where
-
-import Types
--- similar to Order.hs, we reduce the problem to 
--- finding relations that always hold 
-
--- [[(A,1),(B,2)],[(A,1),(B,3)] -> [(A==1),(2<b<3)]
-
-
-
-instance Attribute Clause where
-  learn f = []
-  check cs f = True
-  merge c1 c2 = c1

### 2016-01-25 code/Main.hs

@@ -4,22 +4,51 @@ module Main where
 
 import Preproc
 import Usertime
+import TypeMapper
+import Convert
+ 
 import Types
-import qualified Data.Text as T
 
+import qualified Data.Text as T
+import qualified Data.Text.IO as T
 import System.IO.Unsafe
+import System.Directory
+
+import Control.Applicative
+
+import Debug.Trace
 
 main = 
  let
-  r = preproc learningSet
-  e = usertime r userFile
- in return e
+  tyMap = learnTypes learningSet
+  rules = learnRules tyMap learningSet
 
+  errors = verifyOn rules tyMap userFile
+ in do
+   mapM  putStrLn errors
 
-learningSet = map (\x -> (T.pack . unsafePerformIO $ readFile x, MySQL))
-  [ ("learn/file1.txt")
+lsDir = "dataset/correctMySQL/"
+--lsDir = "dataset/group2-entry-missing/correct/"
+--lsDir = "dataset/group5-value-correlation/correct/"
+--lsDir = "dataset/group4-ordering/correct/"
+learningSet = map (\x -> (u $ T.readFile (lsDir++x), MySQL))
+  (u $ listDirectory lsDir)
+
+{-  [ ("learn/file1.txt")
   , ("learn/file2.txt")
-  ]
+  ]-}
 
 userFile =
-  (T.pack $ unsafePerformIO $ readFile "user/order1.txt",MySQL)
+  (unsafePerformIO $ T.readFile "dataset/group5-value-correlation/error",MySQL)
+--  (unsafePerformIO $ T.readFile "dataset/group2-entry-missing/error",MySQL)
+--  (unsafePerformIO $ T.readFile "dataset/group4-ordering/error",HTTPD)
+
+u = unsafePerformIO
+
+-- | from the newest version of the package, which i cant get for some reason
+listDirectory :: FilePath -> IO [FilePath]
+listDirectory path =
+  (filter f) <$> (getDirectoryContents path)
+  where
+    isDir = not . u . doesDirectoryExist
+    f filename = filename /= "." && filename /= ".." && isDir (path++filename)

### 2016-01-25 code/Preproc.hs

@@ -1,42 +1,36 @@
+
 module Preproc where
 
-import Lexical
-import Values
-import Order
 import Types
+
+import Learners
+import Convert
 
 import qualified Data.Text.IO as T
 
--- | learn rules based on a set of files
-preproc :: [ConfigFile Language] -> RuleSet
-preproc cs = let
-  ds = map convert cs 
-  rules = learnOn ds
- in
-  rules
-
-
--- | call each of the learning modules
-genConstraints :: ConfigFile Common -> RuleSet
-genConstraints f = RuleSet
-  { lexical = learn f
-  , order   = learn f
-  , value   = learn f}
-
 -- | collect contraints from each file indepentantly
 -- this should be parmap
-learnOn :: [ConfigFile Common] -> RuleSet
-learnOn cs = let
-  rs = map genConstraints cs 
+learnRules :: TypeMap -> [ConfigFile Language] -> RuleSet
+learnRules tyMap fs = let
+  fs' = map (convert tyMap) fs
+  rs = map findAllRules fs'
  in
   foldl1 mergeRules rs
 
+-- | call each of the learning modules
+findAllRules :: IRConfigFile -> RuleSet
+findAllRules f = RuleSet
+  { order   = learn f
+  , intRel = learn f
+  , missing = learn f}
+
 -- | reconcile all the information we have learned
--- later, think about merging this step with genConstraints
+-- later, think about merging this step with findAllRules
 -- no more parallel, but might be faster
 mergeRules :: RuleSet -> RuleSet -> RuleSet
 mergeRules rs rs' = RuleSet
-  { lexical = merge (lexical rs) (lexical rs')
-  , order  = merge (order rs) (order rs')
-  , value   = merge (value rs)  (value rs')}
+  { order  = merge (order rs) (order rs')
+  , intRel = merge (intRel rs) (intRel rs')
+  , missing = merge (missing rs) (missing rs')
+  }
 

### 2016-01-25 code/TypeMapper.hs

@@ -1,0 +1,65 @@
+{-# LANGUAGE MultiWayIf #-}
+{-# LANGUAGE OverloadedStrings #-}
+{-# LANGUAGE RecordWildCards#-}
+
+module TypeMapper where
+
+import Types
+import Convert
+
+import Data.Char
+import qualified Data.Text as T
+import qualified Data.Map as M
+
+
+-- | in this pass we build a mapping from keywords to types
+-- to be reused when checking a userfile
+-- with a large learning set, concatMap might run out of memory
+learnTypes :: [ConfigFile Language] -> TypeMap
+learnTypes fs =
+ let
+    fs' = concatMap parse fs
+  in
+    foldl addTypeToMap M.empty fs' 
+
+-- | can use all sorts of nice Data.map fxns (see docs)
+addTypeToMap :: TypeMap -> (Keyword, Value) -> TypeMap
+addTypeToMap m (k,v) =
+  let
+    newCType = assignProbs v
+  in
+    snd $ M.insertLookupWithKey updateProbs k newCType m
+
+updateProbs :: Keyword -> ConfigQType -> ConfigQType -> ConfigQType
+updateProbs k old new =
+  new
+
+assignProbs :: Value -> ConfigQType
+assignProbs t = 
+  let 
+   cint =
+     buildConf (T.all isDigit t) (read $ T.unpack t :: Int)
+   cstring = 
+     buildConf (T.all isAlpha t) (T.unpack t :: String)
+   cfilepath =
+     buildConf 
+       ((T.length $ last $ T.splitOn "." t) <= 4 && 
+        (length $ T.splitOn "." t) == 2)
+       (T.unpack t :: FilePath)
+   cdirpath = 
+     buildConf 
+       ((T.isInfixOf "/" t) && 
+        (not $ T.isInfixOf "." t))
+       (T.unpack t :: DirPath)
+  in 
+   ConfigQType{..}
+
+buildConf :: Bool -> a -> Config a
+buildConf b v = 
+  if b then (Config 1.0::Config a) else zeroProb
+
+-- | should be dual of attemptCoerce, but not sure how to write that cleanly
+--   maybe also want subtyping?
+{-checkType :: Value -> ConfigType -> Bool
+checkType v t =
+  attemptCoerce v == t-}

### 2016-01-25 code/Types.hs

@@ -1,38 +1,84 @@
+{-# LANGUAGE RecordWildCards#-}
+{-# LANGUAGE MultiWayIf#-}
+{-# LANGUAGE FlexibleInstances #-}
+
 module Types where
 
+import qualified Data.Text as T
+import qualified Data.Map as M
 
-import Data.Text as T
-
-
-
-
-data RuleSet = RuleSet {
-  lexical :: [LexRule], 
-  order :: [SynRule], 
-  value :: [Clause],
-  intRels :: [IntRelRule]}
+-- | can i replace this with an exstientially quantified type?
+-- oh that would be beautiful
+-- forall a . Attribute a => [a]
+data RuleSet = RuleSet 
+  { order :: [OrdRule]
+  , intRel :: [IntRelRule]
+  , missing :: [MissingKRule]
+  }
 
 class Attribute a where
-  learn :: ConfigFile Common -> [a]
+  learn :: IRConfigFile -> [a]
   merge :: [a] -> [a] -> [a]
-  check :: [a] -> ConfigFile Common -> Bool
+  check :: [a] -> IRConfigFile -> Error
 
-type SynRule = (T.Text,T.Text)
-type LexRule = (T.Text,T.Text,Int)
-type IntRelRule = Int -> Int -> Int
-type Clause = T.Text
--- the types of these rules restricts the search space for learning modules
-
-
-
+type Error = Maybe String
 
 type ConfigFile a = (T.Text, a)
 data Language = MySQL | HTTPD
-data Common = Common
 
-type Error = String
+-- the types of these rules restricts the search space for learning modules
+type OrdRule = (IRLine,IRLine)
+--you are missing a key-value pair correlation
+data MissingKVRule = MissingKVRule {
+  l11 ::IRLine,
+  l22 :: IRLine} deriving (Show,Eq)
+--you are missing a key correlation
+data MissingKRule = MissingKRule {
+  k1 :: Keyword,
+  k2 :: Keyword} deriving (Show,Eq)
+data IntRelRule = IntRelRule {
+  l1 :: Keyword,
+  l2 :: Keyword,
+  formula :: (Int -> Int -> Bool)} deriving (Show)
 
--- | for now just id
-convert :: ConfigFile Language -> ConfigFile Common
-convert (t, MySQL) = (t,Common)
-convert (t, HTTPD) = (t,Common)
+instance Show (Int-> Int -> Bool) where
+  show f1 = 
[…]

### 2016-01-25 code/Usertime.hs

@@ -1,24 +1,21 @@
 module Usertime where
 
-import Lexical
-import Values
-import Order
 import Types
 
-usertime :: RuleSet -> ConfigFile Language -> Bool --Maybe Error
-usertime r c = 
- let
-  d = convert c
-  e = verifyOn r d
- in
-  e
+import Learners
+import Convert
 
-verifyOn :: RuleSet -> ConfigFile Common -> Bool -- -> Maybe Error
-verifyOn r f = 
+import Control.Monad
+import Data.Maybe
+
+verifyOn :: RuleSet -> TypeMap -> ConfigFile Language -> [String]
+verifyOn r tyMap f = 
   let
-    l = check (lexical r) f
-    s = check (order r ) f
-    v = check (value r) f
-    all = l && s && v
+    f' = convert tyMap f 
+    s = fromMaybe ""
+    orderingError = s$ check (order r) f'
+    intRelError   = s$ check (intRel r) f'
+    missingError   = s$ check (missing r) f'
+    all = [missingError,  orderingError, intRelError]
   in
     all 

### 2016-01-25 code/sketch.hs

@@ -5,7 +5,7 @@
       then [(Variable,Value)]
       else [Text]
   
-  translate :: ConfigFile a -> ConfigFile Common
+  translate :: ConfigFile a -> IRConfigFile
   translate ls = 
     map seperateVal ls
 

### 2016-01-25 codeNew/Convert.hs

@@ -1,35 +1,0 @@
-{-# LANGUAGE OverloadedStrings #-}
-{-# LANGUAGE RecordWildCards#-}
-
-module Convert where
-
-import Types
-
-import qualified Data.Text as T
-import qualified Data.Map as M
-
-
-convert ::  TypeMap -> ConfigFile Language -> IRConfigFile
-convert tyMap f =
-  map (addConfigType tyMap) (parse f)
-
-addConfigType :: TypeMap -> (Keyword,Value) -> IRLine
-addConfigType tyMap (keyword,value) = 
-  case M.lookup keyword tyMap of
-    Just configType -> IRLine{..}
-    Nothing -> IRLine{configType = ConfigUnknown,..}
-
--- | If the user wants to give hints to how to parse a config file based on filetype they go here
-parse :: ConfigFile Language -> [(Keyword,Value)]
-parse (t, MySQL) = map seperateVals (T.lines t)
-parse (t, HTTPD) =  map seperateVals (T.lines t)
-
-
--- | for now we are just using spaces and = to seperate keywords and values
-seperateVals :: T.Text -> (Keyword,Value)
-seperateVals t = 
-  let
-    ts = T.split isDelimeter (T.strip t)
-    isDelimeter c = (c=='=') || (c==' ')
-  in
-    (head ts, last ts)

### 2016-01-25 codeNew/Learners.hs

@@ -1,4 +1,0 @@
-module Learners where
-
-import Order
-import IntRel

### 2016-01-25 codeNew/Learners/IntRel.hs

@@ -1,23 +1,0 @@
-{-# LANGUAGE TupleSections #-}
-{-# LANGUAGE FlexibleInstances #-}
-
-module IntRel where
-
-import Types
-import qualified Data.Text as T
-import qualified Data.Text.IO as T
-import qualified Data.List as L
-import qualified Data.Map as M
-
-import Debug.Trace
-
--- I haven't found a nice package for SMTLIB format in haskell yet, its out there tho, im sure
-
-instance Attribute IntRelRule where
-  learn ts = [(+)]
-
-  check rs f = Nothing
-  
-  merge curr new = [(+)]
-
-

### 2016-01-25 codeNew/Learners/Order.hs

@@ -1,39 +1,0 @@
-{-# LANGUAGE TupleSections #-}
-{-# LANGUAGE FlexibleInstances #-}
-
-module Order where
-
-import Types
-import qualified Data.Text as T
-import qualified Data.Text.IO as T
-import qualified Data.List as L
-import qualified Data.Map as M
-
-import Debug.Trace
-
-
-instance Attribute OrdRule where
-  learn f = allLinePairs f
-
-  check rs f = 
-   let
-     relevantRules = filter (hasRuleFor f) rs
-     fRules = learn f
-     diff = relevantRules L.\\ fRules --the difference between the two rule sets
-     x = if null diff then Nothing else Just $ "Error in ordering on "++(show diff)
-   in 
-    x
-  
-  merge curr new = L.intersect curr new
-
--- | is the rule relevant to the file
---   ie have we seen the (keyword, value) pairing before
-hasRuleFor :: [IRLine] -> OrdRule -> Bool
-hasRuleFor ts r = 
-  elem (fst r) ts && elem (snd r) ts
-
-allLinePairs :: [IRLine]  -> [OrdRule]
-allLinePairs [] = []
-allLinePairs (l:ls) = map (l,) ls ++ allLinePairs ls
-
-traceMe x = traceShow x x

### 2016-01-25 codeNew/Main.hs

@@ -1,30 +1,0 @@
-{-# LANGUAGE OverloadedStrings #-}
-
-module Main where
-
-import Preproc
-import Usertime
-import TypeMapper
-import Convert
- 
-import Types
-
-import qualified Data.Text as T
-import System.IO.Unsafe
-
-main = 
- let
-  tyMap = learnTypes learningSet
-  rules = learnRules tyMap learningSet
-
-  errors = verifyOn rules tyMap userFile
- in return errors
-
-
-learningSet = map (\x -> (T.pack . unsafePerformIO $ readFile x, MySQL))
-  [ ("learn/file1.txt")
-  , ("learn/file2.txt")
-  ]
-
-userFile =
-  (T.pack $ unsafePerformIO $ readFile "user/order1.txt",MySQL)

### 2016-01-25 codeNew/Preproc.hs

@@ -1,32 +1,0 @@
-module Preproc where
-
-import Types
-
-import Learners
-import Convert
-
-import qualified Data.Text.IO as T
-
--- | collect contraints from each file indepentantly
--- this should be parmap
-learnRules :: TypeMap -> [ConfigFile Language] -> RuleSet
-learnRules tyMap fs = let
-  fs' = map (convert tyMap) fs
-  rs = map findAllRules fs'
- in
-  foldl1 mergeRules rs
-
--- | call each of the learning modules
-findAllRules :: IRConfigFile -> RuleSet
-findAllRules f = RuleSet
-  { order   = learn f
-  , intRel = learn f}
-
--- | reconcile all the information we have learned
--- later, think about merging this step with findAllRules
--- no more parallel, but might be faster
-mergeRules :: RuleSet -> RuleSet -> RuleSet
-mergeRules rs rs' = RuleSet
-  { order  = merge (order rs) (order rs')
-  , intRel = merge (intRel rs) (intRel rs')}
-

### 2016-01-25 codeNew/TypeMapper.hs

@@ -1,36 +1,0 @@
-{-# LANGUAGE MultiWayIf #-}
-
-module TypeMapper where
-
-import Types
-import Convert
-
-import Data.Char
-import qualified Data.Text as T
-import qualified Data.Map as M
-
-
--- | in this pass we build a mapping from keywords to types
--- to be reused when checking a userfile
--- with a large learning set, concatMap might run out of memory
-learnTypes :: [ConfigFile Language] -> TypeMap
-learnTypes fs =
- let
-    fs' = concatMap parse fs
-  in
-    foldl addTypeToMap M.empty fs' 
-
--- | can use all sorts of nice Data.map fxns (see docs)
-addTypeToMap :: TypeMap -> (Keyword, Value) -> TypeMap
-addTypeToMap m (k,v) =
-  let
-    ty = attemptCoerce v
-  in
-    M.insert k ty m  
-
--- | can use all sorts of nice Data.map fxns (see docs)
-attemptCoerce :: Value -> ConfigType
-attemptCoerce t = if
-   | T.all isDigit t -> ConfigInt
-   | T.all isAlpha t -> ConfigString
-   | otherwise -> ConfigUnknown

### 2016-01-25 codeNew/Types.hs

@@ -1,41 +1,0 @@
-module Types where
-
-
-import qualified Data.Text as T
-import qualified Data.Map as M
-
-
-data RuleSet = RuleSet 
-  { order :: [OrdRule]
-  , intRel :: [IntRelRule]
-  }
-
-class Attribute a where
-  learn :: IRConfigFile -> [a]
-  merge :: [a] -> [a] -> [a]
-  check :: [a] -> IRConfigFile -> Error
-
--- the types of these rules restricts the search space for learning modules
-type OrdRule = (IRLine,IRLine)
-type IntRelRule = Int -> Int -> Int
-
-type ConfigFile a = (T.Text, a)
-data Language = MySQL | HTTPD
-
-type IRConfigFile = [IRLine]
-data IRLine = IRLine {
-  keyword :: Keyword,
-  configType :: ConfigType,
-  value :: Value } deriving (Show, Eq)
-type Keyword = T.Text
-type Value = T.Text
-data ConfigType = 
-  ConfigInt | 
-  ConfigString | 
-  ConfigUnknown deriving (Show, Eq)
-
-type Error = Maybe String
-
-
-type TypeMap = M.Map Keyword ConfigType
-

### 2016-01-25 codeNew/Usertime.hs

@@ -1,19 +1,0 @@
-module Usertime where
-
-import Types
-
-import Learners
-import Convert
-
-import Control.Monad
-
-
-verifyOn :: RuleSet -> TypeMap -> ConfigFile Language -> Error
-verifyOn r tyMap f = 
-  let
-    f' = convert tyMap f 
-    orderingError = check (order r) f'
-    intRelError   = check (intRel r) f'
-    all = mplus orderingError intRelError
-  in
-    all 

### 2016-01-27 design.tex
whcih errors

@@
 }
+
+We are not quite machine learning because we use more formal reasoning.
+This let's us have a nice garuntee that while we have false positives, but not false negatives.
+
+\forall errors, error \in report
+not \forall report r \in error
+
+Another benefit is that, unlike machine learning algorithms, such as nueral nets, we can actually see the source of errors and the systems reasoning about why a line should be considered an error.
+In nueral nets, we just get a boolean value, and the mechanics of the system are entirly lost. 
+The language model is then recoverable and editable.
+
+The system is also flexible so that changes to the algorithm can be made at a high level.
 

### 2016-01-28 design.tex
a pretty good outline for the meat of the paper

--- 2016-01-25 design.tex
@@
 
-A rule R is added to the set of all rules,
-  if $\exists$ learning file f s.t. R(f) is non vacuously true
-That rule R is then removed from the set of all rules,
-  if $\exists$ learning file f st R(f) is false.
+\section{Learning strategy}
 
-This is accomplished in two passes.
-First we collect all possible rules for every file.
+A primary concern in any machine learning type task is to minimize false negatives and false positives.
+In the context of configuration file verification,
+  a false positive is when \app reports an error on a valid confiuration file and
+  a false negative is when \app fails to reports an error on an invalid confiuration file.
+Too many false positives will cause users to ignore the reported error\cite{}.
+However, since the cost of system failure is so high from a misconfiguration, \app propritzes the minimization of false negatives.
+
+While a traditional classififcation learning machine learning approach can reduce both of these situations, there is can generally be no garuntee that all false negatives will be eliminated.
+Instead of building classification models over the learning set (such as an SVM), we learn the largest set of rules that all correct configuration files satisfy.
+In this way, \app can garuntee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set.
+The only case of a false negative can be when there was no evidece of such a rule in the learning set - we cannot generate rules from nothing.
+Framed as the question "Is this file valid", \app is complete but not sound \xxx{maybe? Im not sure}
+
+That is, taking the following definitions:
+\begin{multline*}\\
+\text{\{Considered Rules\}} = \forall files \in \text{\{Learning Set\}}, \{ r | r(files) = True \land r \text{ is non-trivial}\}\\
+\text{\{Reported Rules\}} = {r | r(userfile)=False } \\
+\text{\{True Rules\}} = \{r | \text{ if } r(userfile)=False \text{ then system crash } \land \\
+   \exists file \in \text{\{Learning Set\}}, r(file) \text{ is non-trivial}\}
+\end{multline*}
+
+We have the following specification of \app.
+\begin{multline*}\\
+\text{\{True Rules\}} \subseteq \text{\{Considered Rules\}} \\
+\forall r \in \text{\{True Rules\}}, if r(userfile)=False then \exists r \in \text{\{Reported Rules\}} \\
+\neg \forall r \in \text{\{Reported Rules\}}, r \in \text{\{True Rules\}} \\
+\end{multline*}
+
+Another benefit to a rule based approach is that, unlike many classificaton models, \app can actually report the reason for failure, similar to a comiler for a programming language.
+This is in contrast to neural nets for example, where we would just get a boolean value, and the mechanics of the system are entirly lost.
+Reporting useful errors that specify a point of failure is important to help users fix their misconfigurations.
+
+\section{Intermediate Representation}
+
+Since we don't want to rewrite checkers for every config file type, we made an intermediate representation.
+The intermediate reprentation is simply a list of keyword value pairs.
+A keyword is the setting being adjust in the configuration file, and the value is the new value for that setting.
+The user only needs to specify the delimiters of the file (characters for assignment and comments usually).
+
+\section{Rules}
+
+In order to flexibly consider many different types of rules, we introduce a inferface (or typeclass in Haskell) that each rule type must support.
+The typeclass is presented here with simplified type signatures for those unfamiliar with Haskell.
+
+\begin{lstlisting}
+class Attribute r where
+  learn :: IRConfigFile -> Set r
+  merge :: Set r -> Set r -> Set r
+  check :: Set r -> IRConfigFile -> Error
+\end{lstlisting}
+
+To build the set Considered Rules, we first collect all possible rules for every file.
 Then we merge the all the rules to create our final set.
-This conviently gives rise to an embarresingly parallel situation, which Haskell allows us to easily take advantage of by
-  using the parallel mapping library parmap.
+
+\subsection{learn}
+  For a single given file in the intermediate representation format, learn a set of rules.
+  In fact, we need to learn every possible rule that this file can satisfy.
+  By overfitting to each file, we can eventually garuntee the completness of \app
+
+\subsection{merge}
+  Merging the sets of rules from two files to build a new set that is true over both files
+  This is generally an intersection like operation, but depending on the particular rule, there may be different stratgeies for merging.
+  The formal specification of this method is that:
+  \begin{multline*}
+  \text{Output Set} = \{r \mid \\
+    r \in \text{\{Input Set1\}} \cup \text{\{Input Set2\}} \land \\
+    \exists file \forall r' \in \text{\{Input Set1\}} \cup \text{\{Input Set2\}}, r(file) = True \land r'(file) = True \} \\
+  \end{multline*}
+
+\subsection{check}
+  To check a file by using a rule set, we simply take all the rules that are releveant to the user's file.
+  Rules that are relavent are the ones where both parts of the ordering are present.
+  We learn the rule set for the user file, and every rule in the learned set must be present in the user file.
+
+\section{Implementation}
+
+\subsection{System}
+Since we learn a set of rules on each file in isolation from the other, we have an embarresingly parallel situation.
+Haskell allows us to easily take advantage of by using the parallel mapping library, parmap.
 
@@
 
-Each rule is of the Attribute typeclass, which means a rule must support the following operations:
-\begin{lstlisting}
-class Attribute r where
-  learn :: ConfigFile Common -> [r]
-  merge :: [r] -> [r] -> [r] 
-  check :: [r] -> ConfigFile Common -> Error
-\end{lstlisting}
+\subsection{Type Error Rules}
+This builds a map between keywords and types, using the values as evidence.
+see quantum.tex for more
+i will write more on this tomorrow.
 
-\subsection{learn}
-  For a single given file, we take very line ordering to be a rule.
-\subsection{merge}
-  Then when merging these sets of rules, we take the intersection of the rules infered on the individual files.
-  Maybe we could also do something like only taking rules that show up multiple times.
-\subsection{check}
-  To check a file by using a rule set, we simply take all the rules that are releveant to the user's file.
-  Rules that are relavent are the ones where both parts of the ordering are present.
-  We learn the rule set for the user file, and every rule in the learned set must be present in the user file.
+\subsection{Integer Relation Rules}
+we only consider the relations , (==), (<=), (>=) because they are easy to pass aroud (as actual functions) in haskell.
+We also committed cardinal since and create an instance for equality over these functions.
+instance Eq (Int->Int->Bool) where
+
+With more engineering effort, this could be extened with the use of a SMT solver to create more fine grained relational rules.
+From our experience, more specific rule are not really needed for integer relations in configuration files.
+However an SMT solver approach would be particularly useful for relations on strings, especially when considering substring relations between filepaths.
+
+\subsection{Ordering and Missing Entry Rules}
+These are the simpiliest of all rules, just making a lot of pairs and seeing which pairs continue to appear over the learning set.

### 2016-01-28 design.tex
we are not complete over ordering!

@@
 These are the simpiliest of all rules, just making a lot of pairs and seeing which pairs continue to appear over the learning set.
+
+There is actually a bit of a catch in ordering though - we are not complete over ordering rules.
+This is because only our implementation does not satisfy the specification for the merge function listed above.
+The problem arises from the fact the configuration files may have non-unique keywords.
+Therefor, in the follwoing file we will derive the valid, but conflicting rules ([client],port) and (port,[client]).
+\begin{verbatim}
+[client]
+port = 3306
+[mysqld]
+port = 3306
+\end{verbatim}
+Our implementation of merge removes and conflicting rules for the running set.
+By introducing a renaming pass in the initial parsing we may be able to solve this, but have not found a satisfactory solution yet.

### 2016-01-28 code/Learners/IntRel.hs
make Attributes Foldable

@@ -2,6 +2,7 @@
 {-# LANGUAGE FlexibleInstances #-}
 {-# LANGUAGE RecordWildCards #-}
 {-# LANGUAGE OverloadedStrings#-}
+{-# LANGUAGE MultiParamTypeClasses#-}
 
 module IntRel where
 
@@ -17,7 +18,7 @@ import Debug.Trace
 
 -- I haven't found a nice package for SMTLIB format in haskell yet, its out there tho, im sure
 
-instance Attribute [IntRelRule] where
+instance Attribute [] IntRelRule where
   -- | this has the problem that order is important
   --   (foo,bar,==) is different than (bar,foo,==)
   learn ts =
@@ -37,7 +38,6 @@ instance Attribute [IntRelRule] where
   
   merge curr new = L.nub $ foldl removeConflicts [] $ L.union curr new
 
-  empty = []
 
 traceMe x = let
   ls = (filter (\r -> "innodb_flush_log_at_trx_commit" == (l1 r)) x)

### 2016-01-28 code/Learners/Missing.hs

@@ -1,5 +1,6 @@
 {-# LANGUAGE TupleSections #-}
 {-# LANGUAGE FlexibleInstances #-}
+{-# LANGUAGE MultiParamTypeClasses#-}
 
 module Missing where
 
@@ -12,7 +13,7 @@ import qualified Data.Map as M
 import Debug.Trace
 
 
-instance Attribute [MissingKVRule] where
+instance Attribute [] MissingKVRule where
   learn [] = []
   learn (l:ls) = concatMap (\l' -> if (keyword l == keyword l') then [] else [MissingKVRule l l']) ls ++ learn ls
 
@@ -26,9 +27,8 @@ instance Attribute [MissingKVRule] where
   
   merge curr new = L.intersect curr new
 
-  empty = []
  
-instance Attribute [MissingKRule] where
+instance Attribute [] MissingKRule where
   learn [] = []
   learn (l:ls) = concatMap (\l' -> if (keyword l == keyword l') then [] else [MissingKRule (keyword l) (keyword l')]) ls ++ learn ls
 
@@ -42,5 +42,4 @@ instance Attribute [MissingKRule] where
      x
   
   merge curr new = L.intersect curr new
-  empty = []
 

### 2016-01-28 code/Learners/Order.hs

@@ -1,5 +1,6 @@
 {-# LANGUAGE TupleSections #-}
 {-# LANGUAGE FlexibleInstances #-}
+{-# LANGUAGE MultiParamTypeClasses#-}
 
 module Order where
 
@@ -12,7 +13,7 @@ import qualified Data.Map as M
 import Debug.Trace
 
 
-instance Attribute [OrdRule] where
+instance Attribute [] OrdRule where
   learn f = pairs f
 
   check rs f = 
@@ -20,12 +21,14 @@ instance Attribute [OrdRule] where
      relevantRules = filter (hasRuleFor f) (rs)
      fRules = learn f
      diff = traceMe relevantRules L.\\ fRules --the difference between the two rule sets
-     x = if null diff then Nothing else Just (L.nub diff)
+     x = if null diff then Nothing else Just diff
    in 
     x
-  
-  merge curr new = L.intersect curr new
-  empty = []
+ 
+  -- | delete rules when (foo,bar) && (bar,foo)
+  -- NB : wihtout unique names, this is actualyl wrong and makes our tool incomplete over ordering
+  -- this is "ok" becuase odering merge does not satisfy the algorithm spec (see paper)
+  merge curr new = L.nub $ L.intersect curr new
 
 -- | is the rule relevant to the file
 --   ie have we seen the (keyword, value) pairing before

### 2016-01-28 code/Learners/TypeMapper.hs

@@ -3,6 +3,7 @@
 {-# LANGUAGE RecordWildCards#-}
 {-# LANGUAGE TypeSynonymInstances#-}
 {-# LANGUAGE FlexibleInstances#-}
+{-# LANGUAGE MultiParamTypeClasses#-}
 
 module TypeMapper where
 
@@ -15,7 +16,7 @@ import qualified Data.Map as M
 
 import Debug.Trace
 
-instance Attribute TypeMap where
+instance Attribute (M.Map Keyword) ConfigQType where 
   learn f = 
     foldl addTypeToMap M.empty f
       
@@ -27,7 +28,6 @@ instance Attribute TypeMap where
       if M.null mismatches then Nothing else Just mismatches
 
   merge oldMap newMap = M.unionWithKey (updateProbs) oldMap newMap
-  empty = M.empty
 
 traceMe x = trace (concatMap (\x-> show x++"\n")(M.toList x)) x
 
@@ -38,7 +38,7 @@ typeConflict t1 t2 =
   
 
 -- | can use all sorts of nice Data.map fxns (see docs)
-addTypeToMap :: TypeMap -> IRLine -> TypeMap
+addTypeToMap :: TypeMap ConfigQType -> IRLine -> TypeMap ConfigQType 
 addTypeToMap m IRLine{..} =
   let
     newCType = assignProbs value
@@ -59,13 +59,12 @@ assignProbs t =
      buildConfTy (T.all isAlpha t) (T.unpack t :: String)
    cfilepath =
      buildConfTy 
-       ((T.length $ last $ T.splitOn "." t) <= 4 && 
-        (length $ T.splitOn "." t) == 2) --this might not be true
+       ((T.isInfixOf "/" t) || (T.isInfixOf "." t) || (T.isInfixOf "\\" t))
        (T.unpack t :: FilePath)
-   cdirpath = 
+   {-cdirpath = 
      buildConfTy 
        ((T.isInfixOf "/" t))
-       (T.unpack t :: DirPath)
+       (T.unpack t :: DirPath)-}
   in 
    ConfigQType{..}
 

### 2016-01-28 code/Main.hs

@@ -31,9 +31,23 @@ learningSet = map (\x -> (u $ T.readFile (lsDir++x), MySQL))
 
 benchmarks = [
     "dataset/group2-entry-missing/error"
+  , "dataset/group2-entry-missing/error2"
+  , "dataset/group2-entry-missing/error3"
+  , "dataset/group2-entry-missing/error4"
+  , "dataset/group2-entry-missing/error5"
   , "dataset/group3-path-type/error"
+  , "dataset/group3-path-type/error2"
+  , "dataset/group3-path-type/error3"
+  , "dataset/group3-path-type/error4"
   , "dataset/group4-ordering/error_mysql"
+  , "dataset/group4-ordering/error2"
+  , "dataset/group4-ordering/error3"
+  , "dataset/group4-ordering/error4"
   , "dataset/group5-value-correlation/error"
+  , "dataset/group5-value-correlation/error2"
+  , "dataset/group5-value-correlation/error3"
+  , "dataset/group5-value-correlation/error4"
+  , "dataset/group5-value-correlation/error5"
   ]
 
 u = unsafePerformIO

### 2016-01-28 code/Types.hs

@@ -1,11 +1,13 @@
 {-# LANGUAGE RecordWildCards#-}
 {-# LANGUAGE MultiWayIf#-}
 {-# LANGUAGE FlexibleInstances #-}
+{-# LANGUAGE MultiParamTypeClasses#-}
 
 module Types where
 
 import qualified Data.Text as T
 import qualified Data.Map as M
+import Data.Foldable
 
 -- | can i replace this with an exstientially quantified type?
 -- oh that would be beautiful
@@ -14,18 +16,21 @@ data RuleSet = RuleSet
   { order :: [OrdRule]
   , intRel :: [IntRelRule]
   , missing :: [MissingKRule]
-  , typeErr :: TypeMap
+  , typeErr :: TypeMap ConfigQType
   }
 
-class Attribute a where
-  learn :: IRConfigFile -> a
-  merge :: a -> a -> a
-  check :: a -> IRConfigFile -> Maybe a
-  empty :: a
+class Foldable t => Attribute t a where
+  learn :: IRConfigFile -> t a
+  merge :: t a -> t a -> t a
+  check :: t a -> IRConfigFile -> Maybe (t a)
+    
 
 type ConfigFile a = (T.Text, a)
 data Language = MySQL | HTTPD
 
+--(rule broken, expected value, actual value)
+--data Error a = (Maybe a, 
+--
 -- the types of these rules restricts the search space for learning modules
 type OrdRule = (IRLine,IRLine)
 --you are missing a key-value pair correlation
@@ -40,7 +45,7 @@ data IntRelRule = IntRelRule {
   l1 :: Keyword,
   l2 :: Keyword,
   formula :: Maybe (Int -> Int -> Bool)} deriving (Show)
-type TypeMap = M.Map Keyword ConfigQType
+type TypeMap a = M.Map Keyword a
 
 instance Show (Int-> Int -> Bool) where
   show f1 = 
@@ -65,10 +70,11 @@ type Probability = Double --st 0<=x<=1
 data Config a = Config {p :: Probability} deriving (Show,Eq)
 
 data ConfigQType = ConfigQType {
-  cint :: Config Int ,
-  cstring :: Config String ,
-  cfilepath :: Config FilePath , 
-  cdirpath :: Config DirPath }
+    cint :: Config Int 
+  , cstring :: Config String 
+  , cfilepath :: Config FilePath 
[…]

### 2016-01-28 code/Usertime.hs

@@ -9,6 +9,8 @@ import Control.Monad
 import Data.Maybe
 import qualified Data.Map as M
 
+import Data.Foldable
+
 verifyOn :: RuleSet -> ConfigFile Language -> [String]
 verifyOn r f = 
   let
@@ -23,11 +25,12 @@ verifyOn r f =
       , show intRelError
       , show missingError
       ]
+    sizeErr = maybe 0 length
     count = 
       (maybe 0 M.size typeError) +
-      (length $ fromMaybe [] orderingError) +
-      (length $ fromMaybe [] missingError) +
-      (length $ fromMaybe [] intRelError) 
+      (sizeErr orderingError) +
+      (sizeErr missingError) +
+      (sizeErr intRelError) 
   in
-    all ++ [show count]
+    ["\n"]++all ++ [show count]
     

### 2016-01-28 design.tex
need empty relations!

@@
 \section{Rules}
+
+Different classes of rules that we consider are represented as types.
+These types tend to be pairs of values with a relation.
+For instance, an integer relation rule is a pair of keywords with a formula that the pairs must satisfy.
+It is important that the relation has some empty value, to state that there is no relation between the values.
+This will prevent \app from trying to relearn rules when they have been eliminated from the set.
 

### 2016-01-28 design.tex
more on modulatiry

--- 2016-01-28 design.tex
@@
 The only case of a false negative can be when there was no evidece of such a rule in the learning set - we cannot generate rules from nothing.
-Framed as the question "Is this file valid", \app is complete but not sound \xxx{maybe? Im not sure}
+Framed as the question "Is this file valid", \app is complete but not sound.
 
@@
 
-Since we don't want to rewrite checkers for every config file type, we made an intermediate representation.
-The intermediate reprentation is simply a list of keyword value pairs.
-A keyword is the setting being adjust in the configuration file, and the value is the new value for that setting.
-The user only needs to specify the delimiters of the file (characters for assignment and comments usually).
+Part of the reason configuration file errors are so common is because of the large number of different systems being used on the market.
+Rather than proposing a new, unifying, configuration language (so that there would then be n+1 configuration languages), we use in intermediate representation language.
+This allows us to reuse all our algorithms over any configuration file that can be convereted to the intermediate representation.
+The portability of \app means that with very little intervtion, it can be widely used and adopted.
+
+More grammatically complex languages tend to be harder to translation to an intermediate representation.
+While there can be some context senestive structures in configuration files, we found it is easier to design the rule modules (Section \ref{}) to handle learning such structure, rather than encoding it in the intermediate representation.
+Additionally, configuration files are generally grammatically simple, consisting mostly of a list of keyword-value pairs.
+The keyword is the variable to be used in the system, and the value is the new value for that variable.
+
+To specialize the converter for a particular language, a user must define a new language type, which simply acts as a flag for translation.
+If a langauge requires specialized parsing, the user can write such code in the convert function based on pattern matching over the language type.
+For example, the user must specify the delimiters of the language (characters for assignment and comments) for their new language.
 
@@
 
-In order to flexibly consider many different types of rules, we introduce a inferface (or typeclass in Haskell) that each rule type must support.
-The typeclass is presented here with simplified type signatures for those unfamiliar with Haskell.
+A core design principle in \app is modularity, so that a user can easily exentend it to their verification needs.
+Rather than try to support every type of verification over configuration files, we provide a framework for defining new verfication properties.
+We call each verification property a rule, for example the correct ordering of keywords or integer relationships between values.
+These rules tend to be pairs of values with a relation.
+For instance, an integer relation rule might be that the value of "foo" must be greater than the value of "bar".
+It is also important that the rule has some empty value, to state that it is known there is no relation between the values.
+This will prevent \app from trying to relearn rules when they have already been refuted.
+
+These rules are represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
+The typeclass can support anything that is Foldable, which roughly the user can use any datastructure.
+In fact, in our implementation, two rules are implemented with lists, and two others use hashmaps.
 
 \begin{lstlisting}
-class Attribute r where
-  learn :: IRConfigFile -> Set r
-  merge :: Set r -> Set r -> Set r
-  check :: Set r -> IRConfigFile -> Error
+class Foldable t => Attribute t a where
+  learn :: IRConfigFile -> t a
+  merge :: t a -> t a -> t a
+  check :: t a -> IRConfigFile -> Error
 \end{lstlisting}
 
-To build the set Considered Rules, we first collect all possible rules for every file.
-Then we merge the all the rules to create our final set.
+The functions of this typeclass will be used, invisibly to the user, to make the overall system run.
+As long as the specifications for each function are met, \app can garuntee completness.
 
 \subsection{learn}
-  For a single given file in the intermediate representation format, learn a set of rules.
-  In fact, we need to learn every possible rule that this file can satisfy.
-  By overfitting to each file, we can eventually garuntee the completness of \app
+  For a single given file in the intermediate representation format, learn the full set of rules on that file.
+  By overfitting to each file, we can eventually garuntee the completness of \app.
+  The specification of this function is the obvious reduction of the Considered Set definition.
+
+  $\text{learn } file =  \{ r | r(file) = True \land r \text{ is non-trivial}\}$
 
 \subsection{merge}
-  Merging the sets of rules from two files to build a new set that is true over both files
-  This is generally an intersection like operation, but depending on the particular rule, there may be different stratgeies for merging.
+  Merging the sets of rules from two files to build a new set that is true over both files is the most difficult and important function a rule must implement.
+  This is generally implemented as a filter over the union of the two set, but may vary slightly.
   The formal specification of this method is that:
   \begin{multline*}
-  \text{Output Set} = \{r \mid \\
-    r \in \text{\{Input Set1\}} \cup \text{\{Input Set2\}} \land \\
-    \exists file \forall r' \in \text{\{Input Set1\}} \cup \text{\{Input Set2\}}, r(file) = True \land r'(file) = True \} \\
+  \text{merge } Set1 \: Set2= \{r \mid \\
+    r \in \text{Set1} \cup \text{Set2} \land \\
+    \exists file \forall r' \in \text{Set1} \cup \text{Set2}, r(file) = True \land r'(file) = True \} \\
   \end{multline*}
@@
 \subsection{System}
-Since we learn a set of rules on each file in isolation from the other, we have an embarresingly parallel situation.
-Haskell allows us to easily take advantage of by using the parallel mapping library, parmap.
+Since we learn a set of rules on each file in isolation from the other, we have an embarrassing parallel situation.
+Haskell allows us to easily take advantage of by using the parallel mapping library, parmap, both for translation to the intermediate representation, and for learning the rules on each file.
+\xxx{merge can also be parallelized, but i haven't done it yet and might not get a chance}
 
 \begin{lstlisting}
-  potentialRules = parmap findAllRules learningSet.
-  finalRules = foldl1 mergeRules potenialRules
+learnRules :: [ConfigFile Language] -> RuleSet
+learnRules fs = let
+  fs' = parMap rseq convert fs
+  rs = parMap rdeepseq findAllRules fs'
+ in
+  foldl1 mergeRules rs
 \end{lstlisting}

### 2016-01-29 intro1.tex
starting

--- 2016-01-25 intro.tex
@@
 ~\cite{xu15systems,zhang14encore,yuan11context}.
-Although several efforts have been proposed to automate configuration
+Although several tools have been proposed to automate configuration
 error diagnosis after failures occur%
@@
 su07autobash,whitaker04configuration}, 
-they rely on manual ways to understand and detect the failure symptoms.
+these tools rely on manual ways to understand and detect the failure symptoms.
+The main reason for this approach ...
+\ruzica{Ennan, can you talk here how usually config files look, only untyped assigments}
+
 Such solutions typically incur high administration cost (\eg, 

### 2016-01-29 motiv1.tex
starting

\section{Motivating Examples}
\label{sec:motiv}

We begin our motivation for a tool such as \app by providing several misconfiguration examples, and showing how do we address them. All these examples are extracted from real-world reports%
~\cite{yin11anempirical, configdataset}. When writing configuration files, the user usually takes already existing files and modifies them. If the original file is already corrupted, the errors are propagated further. However, even if the original file is correct, changing the file by a non-expert user can easily result in errors.

\subsection{Ordering Errors}

When configuring PHP to run with the Apache HTTP Server the user writes, among others, the following lines:\\
 \texttt{
 \hspace*{3em}extension = mysql.so\\
 \hspace*{3em}...\\
 \hspace*{3em}extension = recode.so}\\
This file caused that the Apache server could not start due to 
the segmentation fault error. Running \app on this file returns\\
 \texttt{
  one line output from our tool that indicates that things should be reordered}\\
Indeed, this was the source of the error. When using PHP in Apache, the
extension ``mysql.so'' depends on ``recode.so'' and the relative ordering 
of two of them is crucial. The user is informed that ``recode.so'' should appear before ``mysql.so''.

\begin{figure}[t] \centering
\includegraphics[width=0.98\textwidth]{figs/example}
\caption{Motivating examples. Our target configuration errors are
  classified into five groups. The five examples here correspond to
  these groups, respectively.}
\label{fig-example}
\end{figure}

Fig.~\ref{fig-example} presents misconfiguration examples in real-world
that we aim to address. All the examples are extracted from
misconfiguration issues reported in real-world efforts%
~\cite{yin11anempirical, configdataset}.
We classify our target configuration errors
into five groups: 1) format error; 2) entry missing error; 3) value type
error; 4) ordering error; and 5) value correlation error.
The five examples in Fig.~\ref{fig-example} correspond to the above five
groups, respectively.

### 2016-01-29 intro1.tex

@@
 su07autobash,whitaker04configuration}, 
-these tools rely on manual ways to understand and detect the failure symptoms.
-The main reason for this approach ...
-\ruzica{Ennan, can you talk here how usually config files look, only untyped assigments}
+these tools rely on manual ways to understand and detect the failure 
+symptoms. The main reasons are:
+1) entries in configuration files are untyped assignments, 
+2) there is no explicit structure policy for the entries in 
+configuration files, and 3) there is surprisingly little rules 
+specifying the entries' constraints.
 

### 2016-01-29 motiv1.tex

@@
 
+\subsection{Entry Missing Errors}
+
+When the user wants to use OpenLDAP to enable her directory access
+protocol, she need to use the password policy overlay, so she may need
+to write the following entries in her OpenLDAP configuration file:\\
+\texttt{
+ \hspace*{3em}overlay ppolicy\\}
+However, this configuration makes LDAP server fail to work.
+Running \app on this configuration file returns:
+\xxx{Mark, put results here}\\
+This was the source of the error. When using the password policy overlay
+in OpenLDAP, we have to first include the related schema before the
+{\tt overlay ppolicy}. Namely, the correct configuration should be:\\
+\texttt{
+ \hspace*{3em}include schema/ppolicy.schema\\
+ \hspace*{3em}overlay ppolicy\\
+}
+
+\subsection{Value Type Errors}
+
+When the user tries to install MySQL, she needs to initiate the path for
+log information generated by MySQL. A user put the following code in 
+her MySQL configuration file:\\
+\texttt{
+ \hspace*{3em}general\_log = /var/log/mysql/mysql.log\\}
+Unfortunately, the log information cannot be correctly written.
+Running \app on this configuration file returns:
+\xxx{Mark, put results here}\\
+This is the root-cause of this misconfiguration problem. 
+The entry ``general\_log'' should be an integer, 
+rather than string. In MySQL, there is another entry named
+``general\_log\_file'' used to specify the log path.
+
+\subsection{Value Correlation Errors}
+
+When configuring PHP on MySQL, the user writes the following lines 
+of entries in her both PHP and MySQL configuration files:\\
+\texttt{
+ \hspace*{3em}mysql's config\\
+ \hspace*{3em}max\_connections = 300\\
+ \hspace*{3em}...\\
+ \hspace*{3em}php's config\\
+ \hspace*{3em}mysql.max\_persistent = 400\\}
+Unfortunately, the MySQL outputs the error information:
+``too many connections''.
+Running \app on this combined configuration file returns:
+\xxx{Mark, put results here}\\
+This is the root-cause of the problem.
+In particular, the ``mysql.max\_persistent'' in PHP should be no
+larger than the ``max\_connections'' in MySQL configuration file.
+
+\subsection{Format Errors}
+\xxx{I am not sure if we still need the format error, so I 
+put it the last one.}
+
+When configuring NetApp commercial storage system, 
+the user writes the following entry:\\
+\texttt{
+ \hspace*{3em}InitiatorName: iqn:DEV\_DOMAIN\\
+} 
+The NetApp storage share cannot be recognized. 
+Thus, we run \app on this configuration file and get the results:
+\xxx{Mark, put results here}\\
+This is the root-cause of the problem,
+since the iscsi device's initiator name, \ie, InitiatorName,
+only allows lowercase letters. However, the user sets the name with
+capital letters ``DEV\_DOMAIN''.
+
+\com{
 \begin{figure}[t] \centering
@@
 groups, respectively.
+
+}

### 2016-01-29 motiv1.tex
one result

@@
 Running \app on this configuration file returns:
-\xxx{Mark, put results here}\\
+\begin{verbatim}
+TYPE ERR ("general_log[mysqld]",ConfigQType {cint = Config {p = 1.0}, cstring = Config {p = 0.0}, cfilepath = Config {p = 0.0}})
+\end{verbatim}
 This is the root-cause of this misconfiguration problem. 

### 2016-01-29 motiv1.tex
lala

--- 2016-01-29 motiv1.tex
@@
 
-When the user wants to use OpenLDAP to enable her directory access
-protocol, she need to use the password policy overlay, so she may need
-to write the following entries in her OpenLDAP configuration file:\\
+If the user wants to use OpenLDAP to enable her directory access
+protocol, she needs to use the password policy overlay. This is usually
+done through the following entries in the OpenLDAP configuration file:\\
 \texttt{
  \hspace*{3em}overlay ppolicy\\}
-However, this configuration makes LDAP server fail to work.
+However, this configuration file will make LDAP server fail to work.
 Running \app on this configuration file returns:
@@
 This was the source of the error. When using the password policy overlay
-in OpenLDAP, we have to first include the related schema before the
-{\tt overlay ppolicy}. Namely, the correct configuration should be:\\
+in OpenLDAP, we have to first include the related schema. The correct configuration should be:\\
 \texttt{
@@
 
-When the user tries to install MySQL, she needs to initiate the path for
-log information generated by MySQL. A user put the following code in 
+If the user tries to install MySQL, she first needs to 
+initiate the path for the
+log information generated by MySQL. A user puts the following code in 
 her MySQL configuration file:\\
@@
 Unfortunately, the log information cannot be correctly written.
-Running \app on this configuration file returns:
+After \app analyzed this configuration file, it correctly identifies the error:
 \xxx{Mark, put results here}\\
-This is the root-cause of this misconfiguration problem. 
 The entry ``general\_log'' should be an integer, 
-rather than string. In MySQL, there is another entry named
-``general\_log\_file'' used to specify the log path.
+and not a string. In MySQL, there is another entry named
+``general\_log\_file'' which is used to specify the log path.
 
@@
  \hspace*{3em}mysql.max\_persistent = 400\\}
-Unfortunately, the MySQL outputs the error information:
+This will cause MySQL to abort with the error information:
 ``too many connections''.
@@
 \xxx{Mark, put results here}\\
-This is the root-cause of the problem.
+We are successfully able to derive arithmetic relations between integer values.
 In particular, the ``mysql.max\_persistent'' in PHP should be no

### 2016-01-29 system.tex
lala

--- 2016-01-28 design.tex
@@
-\section{\app Design}
+\section{System Overview}
+\label{sec:system}
 
-\xxx{
-\app Design: 
-  \begin{itemize}
-  \item Present an architecture of \app with a fig. Briefly describe 
-    how it works (step by step).
-  \item Detail learner part
-  \item Merge
-  \item Check 
-  \item Limitations
-  \end{itemize}
-}
+\begin{figure}[t] \centering
+\includegraphics[width=0.8\textwidth]{figs/overview}
+\caption{\app's workflow overview.}
+\label{fig-overview}
+\end{figure}
 
-\section{Learning strategy}
+Fig.~\ref{fig-overview} describes an overview of our system. Our goal is first to learn
 
-A primary concern in any machine learning type task is to minimize false negatives and false positives.
-In the context of configuration file verification,
-  a false positive is when \app reports an error on a valid confiuration file and
-  a false negative is when \app fails to reports an error on an invalid confiuration file.
-Too many false positives will cause users to ignore the reported error\cite{}.
-However, since the cost of system failure is so high from a misconfiguration, \app propritzes the minimization of false negatives.
-
-While a traditional classififcation learning machine learning approach can reduce both of these situations, there is can generally be no garuntee that all false negatives will be eliminated.
-Instead of building classification models over the learning set (such as an SVM), we learn the largest set of rules that all correct configuration files satisfy.
-In this way, \app can garuntee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set.
-The only case of a false negative can be when there was no evidece of such a rule in the learning set - we cannot generate rules from nothing.
-Framed as the question "Is this file valid", \app is complete but not sound \xxx{maybe? Im not sure}
-
-That is, taking the following definitions:
-\begin{multline*}\\
-\text{\{Considered Rules\}} = \forall files \in \text{\{Learning Set\}}, \{ r | r(files) = True \land r \text{ is non-trivial}\}\\
-\text{\{Reported Rules\}} = {r | r(userfile)=False } \\
-\text{\{True Rules\}} = \{r | \text{ if } r(userfile)=False \text{ then system crash } \land \\
-   \exists file \in \text{\{Learning Set\}}, r(file) \text{ is non-trivial}\}
-\end{multline*}
-
-We have the following specification of \app.
-\begin{multline*}\\
-\text{\{True Rules\}} \subseteq \text{\{Considered Rules\}} \\
-\forall r \in \text{\{True Rules\}}, if r(userfile)=False then \exists r \in \text{\{Reported Rules\}} \\
-\neg \forall r \in \text{\{Reported Rules\}}, r \in \text{\{True Rules\}} \\
-\end{multline*}
-
-Another benefit to a rule based approach is that, unlike many classificaton models, \app can actually report the reason for failure, similar to a comiler for a programming language.
-This is in contrast to neural nets for example, where we would just get a boolean value, and the mechanics of the system are entirly lost.
-Reporting useful errors that specify a point of failure is important to help users fix their misconfigurations.
-
-\section{Intermediate Representation}
-
-Since we don't want to rewrite checkers for every config file type, we made an intermediate representation.
-The intermediate reprentation is simply a list of keyword value pairs.
-A keyword is the setting being adjust in the configuration file, and the value is the new value for that setting.
-The user only needs to specify the delimiters of the file (characters for assignment and comments usually).
-
-\section{Rules}
-
-In order to flexibly consider many different types of rules, we introduce a inferface (or typeclass in Haskell) that each rule type must support.
-The typeclass is presented here with simplified type signatures for those unfamiliar with Haskell.
-
-\begin{lstlisting}
-class Attribute r where
-  learn :: IRConfigFile -> Set r
-  merge :: Set r -> Set r -> Set r
-  check :: Set r -> IRConfigFile -> Error
-\end{lstlisting}
-
-To build the set Considered Rules, we first collect all possible rules for every file.
-Then we merge the all the rules to create our final set.
-
-\subsection{learn}
-  For a single given file in the intermediate representation format, learn a set of rules.
-  In fact, we need to learn every possible rule that this file can satisfy.
-  By overfitting to each file, we can eventually garuntee the completness of \app
-
-\subsection{merge}
-  Merging the sets of rules from two files to build a new set that is true over both files
-  This is generally an intersection like operation, but depending on the particular rule, there may be different stratgeies for merging.
-  The formal specification of this method is that:
-  \begin{multline*}
-  \text{Output Set} = \{r \mid \\
-    r \in \text{\{Input Set1\}} \cup \text{\{Input Set2\}} \land \\
-    \exists file \forall r' \in \text{\{Input Set1\}} \cup \text{\{Input Set2\}}, r(file) = True \land r'(file) = True \} \\
-  \end{multline*}
-
-\subsection{check}
-  To check a file by using a rule set, we simply take all the rules that are releveant to the user's file.
-  Rules that are relavent are the ones where both parts of the ordering are present.
-  We learn the rule set for the user file, and every rule in the learned set must be present in the user file.
-
-\section{Implementation}
-
-\subsection{System}
-Since we learn a set of rules on each file in isolation from the other, we have an embarresingly parallel situation.
-Haskell allows us to easily take advantage of by using the parallel mapping library, parmap.
-
-\begin{lstlisting}
-  potentialRules = parmap findAllRules learningSet.
-  finalRules = foldl1 mergeRules potenialRules
-\end{lstlisting}
-
-\subsection{Type Error Rules}
-This builds a map between keywords and types, using the values as evidence.
-see quantum.tex for more
-i will write more on this tomorrow.
-
-\subsection{Integer Relation Rules}
-we only consider the relations , (==), (<=), (>=) because they are easy to pass aroud (as actual functions) in haskell.
-We also committed cardinal since and create an instance for equality over these functions.
-instance Eq (Int->Int->Bool) where
-
-With more engineering effort, this could be extened with the use of a SMT solver to create more fine grained relational rules.
-From our experience, more specific rule are not really needed for integer relations in configuration files.
-However an SMT solver approach would be particularly useful for relations on strings, especially when considering substring relations between filepaths.
-
-\subsection{Ordering and Missing Entry Rules}
-These are the simpiliest of all rules, just making a lot of pairs and seeing which pairs continue to appear over the learning set.
-
-There is actually a bit of a catch in ordering though - we are not complete over ordering rules.
-This is because only our implementation does not satisfy the specification for the merge function listed above.
-The problem arises from the fact the configuration files may have non-unique keywords.
-Therefor, in the follwoing file we will derive the valid, but conflicting rules ([client],port) and (port,[client]).
-\begin{verbatim}
-[client]
-port = 3306
-[mysqld]
-port = 3306
-\end{verbatim}
-Our implementation of merge removes and conflicting rules for the running set.
-By introducing a renaming pass in the initial parsing we may be able to solve this, but have not found a satisfactory solution yet.
+Initially
+we use a large number of correct configuration files as training data

### 2016-01-29 motiv1.tex
random

@@
  \hspace*{3em}general\_log = /var/log/mysql/mysql.log\\}
-Unfortunately, the log information cannot be correctly written.
 After \app analyzed this configuration file, it correctly identifies the error:
-\xxx{Mark, put results here}\\
+\begin{verbatim}
+TYPE ERR ("general_log[mysqld]",ConfigQType {cint = Config {p = 1.0}, cstring = Config {p = 0.0}, cfilepath = Config {p = 0.0}})
+\end{verbatim}
 The entry ``general\_log'' should be an integer, 

### 2016-01-29 code/Convert.hs
passing all benchmarks - im the best

@@ -31,19 +31,21 @@ parse (t, l) =
     noComments = (map (stripComment l) $ T.lines t)
     noEmpty = filter (not. T.null) noComments
     noEmptyAsKV = map seperateVals noEmpty
-    noDups = foldl (\rs r -> makeUniq rs r) [] noEmptyAsKV
+    noDups = makeUniq l noEmptyAsKV
   in
-    map (\(k,v)-> IRLine{keyword=k,value=v}) noEmptyAsKV
+    map (\(k,v)-> IRLine{keyword=k,value=v}) noDups -- noEmptyAsKV
     --noDups
 
-makeUniq :: [(Keyword,Value)] -> (Keyword,Value) -> [(Keyword,Value)]
-makeUniq rs (k,v) = 
-  let
-   c = L.countElem k (map fst rs)
-   k' = if c >= 2 then T.append k (T.pack $show c) else k
-  in
-   rs ++ [(k',v)]
- 
+makeUniq :: Language -> [(Keyword,Value)] -> [(Keyword,Value)]
+makeUniq lang ls = case lang of
+  MySQL ->
+    let
+      f _ [] = []
+      f header (x:xs) =
+        if (fst x==snd x) && T.isInfixOf "[" (fst x) then f x xs else (T.append (fst x) (fst header),snd x) : f header xs
+    in
+      f (head ls) ls
+     
 stripComment :: Language -> T.Text -> T.Text
 stripComment l t = case l of
   MySQL -> T.takeWhile (/='#') t

### 2016-01-29 code/Types.hs

@@ -15,7 +15,7 @@ import Control.DeepSeq
 -- forall a . Attribute a => [a]
 data RuleSet = RuleSet 
   { order :: OrdMap Bool
-  , intRel :: [IntRelRule]
+  , intRel :: IntRelMap 
   , missing :: [MissingKRule]
   , typeErr :: TypeMap ConfigQType
   }
@@ -50,9 +50,11 @@ data IntRelRule = IntRelRule {
   l1 :: Keyword,
   l2 :: Keyword,
   formula :: Maybe (Int -> Int -> Bool)} deriving (Show)
+
 type TypeMap a = M.Map Keyword a
 type OrdMap a = M.Map (IRLine,IRLine) a
-
+type IntRelMap = M.Map (Keyword,Keyword) (Maybe (Int->Int->Bool))
+type Formula = Maybe (Int->Int->Bool)
 instance Show (Int-> Int -> Bool) where
   show f1 = 
     if | (f1 0 1)  -> "<="

### 2016-01-29 code/Usertime.hs

@@ -19,18 +19,19 @@ verifyOn r f =
     intRelError   =  check (intRel r) f'
     missingError  =  check (missing r) f'
     typeError     =  check (typeErr r) f'
+    typeShow = maybe "" (\x->"TYPE ERR "++(unlines.(map show).M.toList) x) typeError
     all = [
-        show typeError
-      , show orderingError
-      , show intRelError
-      , show missingError
+        typeShow
+      , maybe "" (\x->"ORDER ERR "++(unlines.(map show).M.toList) x) orderingError
+      , maybe "" (\x->"INT REL ERR "++(unlines.(map show).M.toList) x) intRelError
+      , maybe "" (\x-> "MISSING ERR "++(unlines.(map show)) x) missingError
       ]
     sizeErr = maybe 0 length
-    count = 
-      (maybe 0 M.size typeError) +
+    typeSize = (maybe 0 M.size typeError) 
+    count = typeSize +
       (maybe 0 M.size orderingError) +
       (sizeErr missingError) +
-      (sizeErr intRelError) 
+      (maybe 0 M.size intRelError) 
   in
-    ["\n"]++all ++ [show count]
+    if typeSize >0 then ["\n"] ++ [typeShow]++ [show typeSize] else ["\n"]++all ++ [show count]
     

### 2016-01-29 code/Types.hs
fixing benchmarks and collecting data and a short write up

@@ -83,7 +83,17 @@ data ConfigQType = ConfigQType {
   , cfilepath :: Config FilePath 
   --, cdirpath :: Config DirPath 
   }
-  deriving (Show, Eq)
+  deriving (Eq)
+
+instance Show ConfigQType where
+ show ConfigQType{..} = 
+  let
+    i = if p cint >0 then "Int with P="++(show (p cint))++" " else ""
+    s = if p cstring >0 then "String with P="++(show (p cstring))++" " else ""
+    f = if p cfilepath >0 then "Filepath with P="++(show (p cfilepath))++" " else ""
+    u = if (i++s++f)=="" then "Unknown Type" else ""
+  in
+    i++s++f++u
 
 zeroProb:: Config a
 zeroProb= Config 0  

### 2016-01-29 code/Usertime.hs

@@ -9,7 +9,7 @@ import Control.Monad
 import Data.Maybe
 import qualified Data.Map as M
 
-import Data.Foldable
+--import Data.Foldable
 
 verifyOn :: RuleSet -> ConfigFile Language -> [String]
 verifyOn r f = 
@@ -19,12 +19,39 @@ verifyOn r f =
     intRelError   =  check (intRel r) f'
     missingError  =  check (missing r) f'
     typeError     =  check (typeErr r) f'
-    typeShow = maybe "" (\x->"TYPE ERR "++(unlines.(map show).M.toList) x) typeError
+   
+    --the dreaded monomorphism restriction. i tihnk there is way to turn it off tho
+    typeShow = 
+      let 
+        es = maybe [] M.toList typeError
+        f = (\x->"TYPE ERROR: Expected a "++(show$snd x)++" for "++(show$fst x)++"\n")
+      in
+        concatMap f es
+
+    orderingShow =
+      let 
+        es = maybe [] M.toList orderingError
+        f = (\x->"ORDERING ERROR: Expected "++(show$fst $fst x)++" BEFORE "++(show$snd$fst  x)++"\n")
+      in
+        concatMap f es
+   
+    intRelShow = 
+      let  
+        es = maybe [] M.toList intRelError
+        f = (\x->"INTEGER RELATION ERROR: Expected "++(show$fst $fst x)++(show$fromJust$snd x)++(show$snd$fst x)++"\n")
+      in
+        concatMap f es
+    missingShow = 
+      let  
+        es = fromMaybe [] missingError
+        f = (\x->"MISSING KEYWORD ERROR: Expected "++(show$k1 x)++" in the same file as: "++(show$k2 x)++"\n")
+      in
+        concatMap f es
     all = [
         typeShow
-      , maybe "" (\x->"ORDER ERR "++(unlines.(map show).M.toList) x) orderingError
-      , maybe "" (\x->"INT REL ERR "++(unlines.(map show).M.toList) x) intRelError
-      , maybe "" (\x-> "MISSING ERR "++(unlines.(map show)) x) missingError
+      , orderingShow
+      , intRelShow
+      , missingShow
       ]
     sizeErr = maybe 0 length
     typeSize = (maybe 0 M.size typeError) 

### 2016-01-29 intro1.tex
lala
random

@@
-\section{Introduction}
+\section{Introduction and System Overview}
+\label{sec:Intro}
 
@@
 
-Such solutions typically incur high administration cost (\eg, 
-requiring users to write pattern-matching scripts) 
-and are unreliable (\eg, some errors may show no user-visible symptoms).
-These shortcomings often lead to prolonged delays between
-the occurrence and the detection of errors, thus causing unrecoverable
-damage to system states.
+We propose an approach to the verification of  
+configuration files which is based on learning rules about the language 
+model for configuration files.
 
-We expect to explore a fundamentally different means to tackle 
-the misconfiguration problem. Rather than using retroactive approaches
-to deal with configuration errors after the software failures occur, 
-we would like to {\em proactively} prevent misconfiguration problems 
-{\em before} users first deploy the configuration files to 
-their system settings. In other words, we aim to offer users 
-a configuration error filter in order to significantly minimize 
-the probability of misconfigurations in the system runtime.
+\begin{figure}[t] \centering
+\includegraphics[width=0.8\textwidth]{figs/overview}
+\caption{An overview of the \app's workflow.}
+\label{fig-overview}
+\end{figure}
 
-Based on the above intuition, this paper presents \app, 
-a proactive misconfiguration checker which takes users' 
-configuration files as input and then reports potential configuration 
-errors to the users before they deploy their systems 
-according to these configurations.
-At the heart of \app lies a machine learning mechanism, 
-which learns rules and constraints from pluggable 
-correct sampling configuration files (\ie, for the training purposes), 
-and then detects errors violating the learned constraints.
+Fig.~\ref{fig-overview} describes an overview of our system. We start with
+an assumption that we are given a number of correct configuration files belonging to the same category (for instance, MySQL or Apache). Such files
+follow the same naming conventions and we use that fact in a learning 
+algorithm which will result with the rules describing the language model used in the files.
+Since the ``language'' of configuration types is untyped and unstructured, we first parse the files and translate them
+into a more structured, typed, intermediary representation. Having more structured files, we use them as a training set to learn the rules about the 
+language model. These rules are used for detecting errors violating the learned constraints in the files given by the user.
 
-\app mainly offers users three significant benefits.
-First, there is no any extra burden added to users who only need to 
-simply use \app as a ``seamless'' pre-checker for their configurations.
+From a  practical perspective there is no additional burden 
+to the users: they can use \app to verify their configuration files.
+
 Second, because many misconfiguration errors have been eliminated 
@@
 
-Using these ideas, we make the following contriubtions:
+Using these ideas, we make the following contributions:
 
@@
   \item Our tool, \app can learn a language model from a set of examples of correct configuration files, and use the model to verify new files.
-  \item We present a probabalistic type that can be used to assign a confidence distribution over a set of types to a valule.
+  \item We present a probabilistic type that can be used to assign a confidence distribution over a set of types to a value.
   \item In \app, we define a minimal interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.

### 2016-01-29 system.tex
random

--- 2016-01-28 design.tex
@@
-\section{\app Design}
+\section{Quantum Types}
 
-\xxx{
-\app Design: 
-  \begin{itemize}
-  \item Present an architecture of \app with a fig. Briefly describe 
-    how it works (step by step).
-  \item Detail learner part
-  \item Merge
-  \item Check 
-  \item Limitations
-  \end{itemize}
-}
+Because our type inference is based on machine learning, we cannot be sure that a keyword unambigously has a single type.
+This is an issue when we try to learn relational rules between keywords. 
+Take the following file in the learning
+
+foo = 300
+bar = 300.txt
+
+We want to learn the rule that $foo \in {substring(bar)}$, however using unambigous type inference, we would assign foo type int, and never try to generate a string relation rule for these two keywords.
+By assigning foo a quantum type (e.g. ${Int <90\%>, String <10\%>}$), we can now generate rules for both types.
+
+At runtime, when the user wants to check a file we update the probabilities one last time then 'collapse' the quantum type to a concrete type.
+If the concrete type collapses to a Int, we consider the rules for ints, and vice versa.
+
+This idea is closely related to exstentially quantified types.
 

### 2016-01-29 intro1.tex
random

@@
 into a more structured, typed, intermediary representation. Having more structured files, we use them as a training set to learn the rules about the 
-language model. These rules are used for detecting errors violating the learned constraints in the files given by the user.
+language model. The learning algorithm is template-based. We provide an initial set of
+templates and the learner learns some concrete instances from 
+the training set. For example, a template is $X_1 \le X_2$, where $X_1$ and $X_2$ are integer variables. A rule that we might learn is that
+$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$.
+These rules are used for detecting errors violating the learned constraints in the files given by the user.
 
@@
 to the users: they can use \app to verify their configuration files.
+We support learning rules
+
+present in the literature
+
+modularity
 

### 2016-01-29 intro1.tex
config: comments

@@
 configuration files which is based on learning rules about the language 
-model for configuration files.
+model for configuration files. \xxx{I think we should explicitly 
+mention our approach aims to solve 
+misconfiguration from different way with the
+previous work. Previous work tries to find out the problem after the
+failures occur, but our approach is a proactive method, which can
+find out error before the system failure occurs. Such an effort (i.e., 
+preventing misconfiguration before installation) is
+important, because the majority of errors can be 
+detected before running your system. 
+Thus, 1) users will not complain too much because they are using
+``very healthy'' configuration files, 
+and 2) this is a great complementary to existing reactive misconfiguration 
+detectors. -- Ennan}
 

### 2016-01-29 intro1.tex
random

--- 2016-01-29 intro1.tex
@@
 modern software system failures~\cite{xu15systems,yin11anempirical}.
-In practice, misconfiguration problems may result in 
-security vulnerabilities,
-application crashes, severe disruptions in software functionality,
-and incorrect program executions%
-~\cite{xu15systems,zhang14encore,yuan11context}.
-Although several tools have been proposed to automate configuration
-error diagnosis after failures occur%
-~\cite{wang04automatic,attariyan10automating,%
-su07autobash,whitaker04configuration}, 
-these tools rely on manual ways to understand and detect the failure 
-symptoms. The main reasons are:
-1) entries in configuration files are untyped assignments, 
-2) there is no explicit structure policy for the entries in 
-configuration files, and 3) there is surprisingly little rules 
-specifying the entries' constraints.
+In practice, misconfiguration problems may result in security
+vulnerabilities, application crashes, severe disruptions in software
+functionality, and incorrect program executions%
+~\cite{xu15systems,zhang14encore,yuan11context}.  Although several
+tools have been proposed to automate configuration error diagnosis
+after failures occur~\cite{wang04automatic,attariyan10automating,
+su07autobash,whitaker04configuration}, these tools rely on manual ways
+  to understand and detect the failure symptoms. The main reasons are:
+  1) entries in configuration files are untyped assignments, 2) there
+  is no explicit structure policy for the entries in configuration
+  files, and 3) there is surprisingly little rules specifying the
+  entries' constraints.
 
-We propose an approach to the verification of  
-configuration files which is based on learning rules about the language 
-model for configuration files.
+We propose an approach to the verification of configuration files
+which is based on learning rules about the language model for
+configuration files.
 
@@
 
-Fig.~\ref{fig-overview} describes an overview of our system. We start with
-an assumption that we are given a number of correct configuration files belonging to the same category (for instance, MySQL or Apache). Such files
-follow the same naming conventions and we use that fact in a learning 
-algorithm which will result with the rules describing the language model used in the files.
-Since the ``language'' of configuration types is untyped and unstructured, we first parse the files and translate them
-into a more structured, typed, intermediary representation. Having more structured files, we use them as a training set to learn the rules about the 
-language model. These rules are used for detecting errors violating the learned constraints in the files given by the user.
+Fig.~\ref{fig-overview} describes an overview of our system. We start
+with an assumption that we are given a number of correct configuration
+files belonging to the same category (for instance, MySQL or
+Apache). Such files follow the same naming conventions and we use that
+fact in a learning algorithm which will result with the rules
+describing the language model used in the files. Since the
+``language'' of configuration types is untyped and unstructured, we
+first parse the files and translate them into a more structured,
+typed, intermediary representation. Having more structured files, we
+use them as a training set to learn the rules. The learning algorithm
+is template-based. We provide an initial set of templates and the
+learner learns some concrete instances from the training set. These
+rules are used for detecting errors violating the learned constraints
+in the files given by the user.
+
+As an 
+illustration for a simple rule that we can learn, consider a template is $X_1 \le X_2$, where $X_1$ and $X_2$ are
+integer variables. The learned might derive the rule stating that
+$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. There is a classification and taxonomy of configuration errors in the 
+existing work on automated configuration troubleshooting~\cite{yin11anempirical, configdataset}. We provide templates for every class that \app can handle: we consider integer constraints, ordering
+constraints, typing constraints, constraints about correlated entries (such as ``if $X$ is present, $Y$ has to appear as well'').
+Unfortunately, there are a few classes of errors that we cannot handle.
+They
+ rely on the analysis of the whole operating system and our language-based
+approach is not expressive enough for them.
 
 From a  practical perspective there is no additional burden 
-to the users: they can use \app to verify their configuration files.
+to the users: they can simply use \app to check for errors in their configuration files.
+However, they can also easily extend the framework themselves.
+The system is designed to be highly modular.
+If there is a class of rules that \app is not currently learning, the user can develop their own templates and learners for that class.
+The new learner can be added to \app and this way it can check additionally a new set
+for even more errors.
 

### 2016-01-29 intro1.tex
random

@@
 
-We propose an approach to the verification of configuration files
-which is based on learning rules about the language model for
-configuration files.
+We propose an approach to the verification of  
+configuration files which is based on learning rules about the language 
+model for configuration files.
 
@@
 If there is a class of rules that \app is not currently learning, the user can develop their own templates and learners for that class.
-The new learner can be added to \app and this way it can check additionally a new set
-for even more errors.
+The new learner can be added to \app and this way it can check additionally a new set of errors.
+
+Finally, from a system perspective this is the first approach that checks
+
+\xxx{I think we should explicitly 
+mention our approach aims to solve 
+misconfiguration from different way with the
+previous work. Previous work tries to find out the problem after the
+failures occur, but our approach is a proactive method, which can
+find out error before the system failure occurs. Such an effort (i.e., 
+preventing misconfiguration before installation) is
+important, because the majority of errors can be 
+detected before running your system. 
+Thus, 1) users will not complain too much because they are using
+``very healthy'' configuration files, 
+and 2) this is a great complementary to existing reactive misconfiguration 
+detectors. -- Ennan}
 

### 2016-01-29 intro1.tex
random

--- 2016-01-29 intro1.tex
@@
 If there is a class of rules that \app is not currently learning, the user can develop their own templates and learners for that class.
-The new learner can be added to \app and this way it can check additionally a new set
-for even more errors.
+The new learner can be added to \app and this way it can check additionally a new set of errors.
 
-Second, because many misconfiguration errors have been eliminated 
-by \app, the workloads of post-failure forensics in runtime
-are significantly reduced, thus making these tools truly practical.
-Finally, since there have been many correct but not specific 
-example configuration files in practice, 
-increasingly more samples can be freely added to \app,
-thus giving \app evolutionary capability.
+Finally, from a system perspective this is the first approach that checks 
+proactively the correctness of configuration files. All previous work
+~\cite{xu15systems,zhang14encore,yuan11context, wang04automatic,attariyan10automating,
+su07autobash,whitaker04configuration} tries to identify the problem after the
+failure occurs.
+Our approach isolates potential errors before the system failure occurs, e.g.
+before the installation.
+We can also see \app as a tool that can run in conjunction with existing tool.
+Pre-analyzed configuration files are already free from language-based errors, and this way the workloads of post-failure forensics at the runtime
+is significantly reduced, thus making these tools truly practical.
 
@@
 
-  \item Our tool, \app can learn a language model from a set of examples of correct configuration files, and use the model to verify new files.
-  \item We present a probabilistic type that can be used to assign a confidence distribution over a set of types to a value.
+  \item We designed and implemented a tool, \app, that can learn a language model from a set of examples of correct configuration files, and use the model to verify new files.
+  \item We use a probabilistic type that can be used to assign a confidence distribution over a set of types to a value.
   \item In \app, we define a minimal interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.

### 2016-01-29 intro1.tex
config: fig 1

--- 2016-01-29 intro1.tex
@@
 modern software system failures~\cite{xu15systems,yin11anempirical}. 
-In practice, misconfiguration problems may result in security
-vulnerabilities, application crashes, severe disruptions in software
-functionality, and incorrect program executions%
-~\cite{xu15systems,zhang14encore,yuan11context}.  Although several
-tools have been proposed to automate configuration error diagnosis
-after failures occur~\cite{wang04automatic,attariyan10automating,
-su07autobash,whitaker04configuration}, these tools rely on manual ways
-  to understand and detect the failure symptoms. The main reasons are:
-  1) entries in configuration files are untyped assignments, 2) there
-  is no explicit structure policy for the entries in configuration
-  files, and 3) there is surprisingly little rules specifying the
-  entries' constraints.
+In practice, misconfiguration problems may result in 
+security vulnerabilities,
+application crashes, severe disruptions in software functionality,
+and incorrect program executions%
+~\cite{xu15systems,zhang14encore,yuan11context}.
+Although several tools have been proposed to automate configuration
+error diagnosis after failures occur%
+~\cite{wang04automatic,attariyan10automating,%
+su07autobash,whitaker04configuration}, 
+these tools rely on manual ways to understand and detect the failure 
+symptoms. The main reasons are:
+1) entries in configuration files are untyped assignments, 
+2) there is no explicit structure policy for the entries in 
+configuration files, and 3) there is surprisingly little rules 
+specifying the entries' constraints.
 
@@
 configuration files which is based on learning rules about the language 
-model for configuration files.
-
-\begin{figure}[t] \centering
-\includegraphics[width=0.8\textwidth]{figs/overview}
-\caption{An overview of the \app's workflow.}
-\label{fig-overview}
-\end{figure}
-
-Fig.~\ref{fig-overview} describes an overview of our system. We start
-with an assumption that we are given a number of correct configuration
-files belonging to the same category (for instance, MySQL or
-Apache). Such files follow the same naming conventions and we use that
-fact in a learning algorithm which will result with the rules
-describing the language model used in the files. Since the
-``language'' of configuration types is untyped and unstructured, we
-first parse the files and translate them into a more structured,
-typed, intermediary representation. Having more structured files, we
-use them as a training set to learn the rules. The learning algorithm
-is template-based. We provide an initial set of templates and the
-learner learns some concrete instances from the training set. These
-rules are used for detecting errors violating the learned constraints
-in the files given by the user.
-
-As an 
-illustration for a simple rule that we can learn, consider a template is $X_1 \le X_2$, where $X_1$ and $X_2$ are
-integer variables. The learned might derive the rule stating that
-$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. There is a classification and taxonomy of configuration errors in the 
-existing work on automated configuration troubleshooting~\cite{yin11anempirical, configdataset}. We provide templates for every class that \app can handle: we consider integer constraints, ordering
-constraints, typing constraints, constraints about correlated entries (such as ``if $X$ is present, $Y$ has to appear as well'').
-Unfortunately, there are a few classes of errors that we cannot handle.
-They
- rely on the analysis of the whole operating system and our language-based
-approach is not expressive enough for them.
-
-From a  practical perspective there is no additional burden 
-to the users: they can simply use \app to check for errors in their configuration files.
-However, they can also easily extend the framework themselves.
-The system is designed to be highly modular.
-If there is a class of rules that \app is not currently learning, the user can develop their own templates and learners for that class.
-The new learner can be added to \app and this way it can check additionally a new set of errors.
-
-Finally, from a system perspective this is the first approach that checks
-
-\xxx{I think we should explicitly 
+model for configuration files. \xxx{I think we should explicitly 
 mention our approach aims to solve 
@@
 detectors. -- Ennan}
+
+\begin{figure}[t] \centering
+\includegraphics[width=0.8\textwidth]{figs/overview}
+\caption{\app's workflow overview. Green boxes are configuration files,
+  including correct general configuration files and users' input
+  configuration files. Purple boxes are the components within \app.
+  Yellow boxes are results generated by \app's components.}
+\label{fig-overview}
+\end{figure}
+
+Fig.~\ref{fig-overview} describes an overview of our system. We start with
+an assumption that we are given a number of correct configuration files belonging to the same category (for instance, MySQL or Apache). Such files
+follow the same naming conventions and we use that fact in a learning 
+algorithm which will result with the rules describing the language model used in the files.
+Since the ``language'' of configuration types is untyped and unstructured, we first parse the files and translate them
+into a more structured, typed, intermediary representation. Having more structured files, we use them as a training set to learn the rules about the 
+language model. The learning algorithm is template-based. We provide an initial set of
+templates and the learner learns some concrete instances from 
+the training set. For example, a template is $X_1 \le X_2$, where $X_1$ and $X_2$ are integer variables. A rule that we might learn is that
+$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$.
+These rules are used for detecting errors violating the learned constraints in the files given by the user.
+
+From a  practical perspective there is no additional burden 
+to the users: they can use \app to verify their configuration files.
+We support learning rules
+
+present in the literature
+
+modularity
 

### 2016-01-29 intro1.tex
random

--- 2016-01-29 intro1.tex
@@
 \includegraphics[width=0.8\textwidth]{figs/overview}
-\caption{An overview of the \app's workflow.}
+\caption{\app's workflow overview. The green boxes represent configuration files,
+  including both correct general configuration files and users' input
+  configuration files. The purple boxes are the components within \app.
+  The yellow boxes are results generated by \app's components.}
 \label{fig-overview}
@@
 first parse the files and translate them into a more structured,
-typed, intermediary representation. Having more structured files, we
+typed, intermediary representation.
+When parsing the untyped files, sometimes the correct file cannot be determined from a variable declaration.
+We address this problem by introducing so called {\emph{quantum types}}.
+To a variable we do not associate a type, but several types with their probability distributions.
+Having more structured files, we
 use them as a training set to learn the rules. The learning algorithm
@@
 As an 
-illustration for a simple rule that we can learn, consider a template is $X_1 \le X_2$, where $X_1$ and $X_2$ are
+illustration for a simple rule that we can learn, consider a template
+ $X_1 \le X_2$, where $X_1$ and $X_2$ are
 integer variables. The learned might derive the rule stating that
@@
 Finally, from a system perspective this is the first approach that checks 
-proactively the correctness of configuration files. All previous work
+{\emph{proactively}} the correctness of configuration files. All previous work
 ~\cite{xu15systems,zhang14encore,yuan11context, wang04automatic,attariyan10automating,
 su07autobash,whitaker04configuration} tries to identify the problem after the
-failure occurs.
+failure occured.
 Our approach isolates potential errors before the system failure occurs, e.g.
 before the installation.
-We can also see \app as a tool that can run in conjunction with existing tool.
+We can also see \app as a tool that can run in conjunction with existing tools.
 Pre-analyzed configuration files are already free from language-based errors, and this way the workloads of post-failure forensics at the runtime
@@
 
-Using these ideas, we make the following contributions:
+To summarize, this tool papers makes the following contributions:
 
@@
 
-  \item We designed and implemented a tool, \app, that can learn a language model from a set of examples of correct configuration files, and use the model to verify new files.
-  \item We use a probabilistic type that can be used to assign a confidence distribution over a set of types to a value.
-  \item In \app, we define a minimal interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.
+  \item We designed and implemented a tool, \app, that can learn a language model from a set of examples of correct configuration files, and we use the model to verify new files.
+  \item We use probabilistic types to assign to a value a confidence distribution over a set of types.
+  \item In \app we define a minimal interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.
 

### 2016-01-29 evaluation.tex
added eval

\section{evaluation}

We report error that was unrelated to the value of interest as a false positive.
It is worth noting that this is in fact a conservative estimate.
Since these benchmarks are taken from online forums, there is no garuntee the files contain only a single error.
Indeed, while running these benchmarks, \app found errors in the file that were similar to other benchmarks.

We fail one benchmark in Value Relations because we do not yet support relations between file sizes of different units (Mb to Kb)

\begin{table}[]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{lll}
Error Type       & Passing Tests & False Positives  \\
Missing Entry    & 5/5           & 1,0,0,0,1        \\
Type Error       & 4/4           & 0,0,0,0          \\
Keyword Ordering & 4/4*          & 0,10,1,0         \\
Value Relations  & 4/5           & 0,0,0,0,0        \\
*One passing test gives a type error on the misconfigured value rather than an ordering error, as it should.
\end{tabular}
\end{table}

### 2016-01-29 evaluation.tex
more

@@
-\section{evaluation}
+\section{Evaluation}
+
+To evaluate our tool, take a subset of the canonical benchmarks for configuration errors\cite{dataset}.
+We take the subset of benchmarks for which our tool has implemented modules.
+Although our tool is general and extensible, we have only implemented four types of rules over the MySQL configuration language.
 
@@
 \end{table}
+
+All false positives were integer relations.
+Recall from Section \sec{} that false positives are the result of overfitting on rules.
+\app can learn overfit rules when the learning set does not show the full spectrum of possible values.
+Since integer relations have a larger space of relation than say, ordering relations, \app needs a larger learning set in order to eliminate false positives.

### 2016-01-29 evaluation.tex
autocommit

@@
+\section{Implementation}
+
 \section{Evaluation}
@@
 
-We report error that was unrelated to the value of interest as a false positive.
+We call false positives any error that was unrelated to the value of interest.
 It is worth noting that this is in fact a conservative estimate.
@@
 We fail one benchmark in Value Relations because we do not yet support relations between file sizes of different units (Mb to Kb)
+In one Keyword Ordering benchmark, \app reports a type error on the value of interest instead of a ordering error.
+This is a result of our context embedding in the translation to the intermediate represetnation - reordering the value puts it in a new context where the type is now also incorrect.
 
@@
 \centering
-\caption{My caption}
+\caption{}
 \label{my-label}
-\begin{tabular}{lll}
-Error Type       & Passing Tests & False Positives  \\
-Missing Entry    & 5/5           & 1,0,0,0,1        \\
-Type Error       & 4/4           & 0,0,0,0          \\
-Keyword Ordering & 4/4*          & 0,10,1,0         \\
-Value Relations  & 4/5           & 0,0,0,0,0        \\
-*One passing test gives a type error on the misconfigured value rather than an ordering error, as it should.
+\begin{tabular}{l|l|l}
+Error Type       & Passing Tests & False Positives  \\ \hhline{|=|=|=|}
+Missing Entry    & 5/5           & 1, 0, 0, 0, 1        \\ \hline
+Type Error       & 4/4           & 0, 0, 0, 0          \\ \hline
+Keyword Ordering & 4/4          & 0, 10, 1, 0         \\ \hline
+Value Relations  & 4/5           & 0, 1, 0, 0, 0        \\ 
 \end{tabular}
@@
 All false positives were integer relations.
-Recall from Section \sec{} that false positives are the result of overfitting on rules.
+Recall from Section \ref{} that false positives are the result of overfitting on rules.
 \app can learn overfit rules when the learning set does not show the full spectrum of possible values.
 Since integer relations have a larger space of relation than say, ordering relations, \app needs a larger learning set in order to eliminate false positives.
+
+The false positive for value relation is a result of the fact that we cannot learn rules that are disjunctions.

### 2016-01-29 evaluation.tex
new benchmarks!

@@
 \section{Implementation}
+
+\app is implemented in Haskell and takes full advantage of its polymorphism to make the system more modular.
+In particular, rules are represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
+By using various language extensions, this typeclass can be made polymorphic over the data structure (Foldable t =>).
+The user can then choose data structure that is most natural to the rule they are implementing.
+For example, in our implementation, missing keywords were easier to manipulate in lists, while types fit more naturally into a hashmap.
+
+\begin{lstlisting}
+class Foldable t => Attribute t a where
+  learn :: IRConfigFile -> t a
+  merge :: t a -> t a -> t a
+  check :: t a -> IRConfigFile -> Error
+\end{lstlisting}
+
+Since we learn a set of rules on each file in isolation from the other, we have an embarrassing parallel situation.
+Haskell allows us to easily take advantage of by using the parallel mapping library, parmap, both for translation to the intermediate representation, and for learning the rules on each file.
+The merge stage could also be parallelized, using a divide and conquer approach, but \app runs fast enough over our learning set (28 files) and resultsing rules (~4500 for integer relations) that this as not necessary.
+
+The integer relation rule has an unusual implementation that makes use of function as first-class objects in haskell.
+Rather than associated keywords with SMT formula, we directly associate them with a function of type (Int->Int->Bool).
+Since we need to compare rules over equality, we must then have a way to compare functions.
+This limits the types of functions we use to (==), (>=), and (<=).
+Although this is sufficent for most use cases, more fine-grained relations could be encoded with SMT formulas then passed to a solver.
 
@@
 
-We call false positives any error that was unrelated to the value of interest.
+A benchmark passes a test if it reports an error on the source of the misconfiguration.
+We call false positives any reported error that was unrelated to the value of interest.
 It is worth noting that this is in fact a conservative estimate.
@@
 Missing Entry    & 5/5           & 1, 0, 0, 0, 1        \\ \hline
-Type Error       & 4/4           & 0, 0, 0, 0          \\ \hline
-Keyword Ordering & 4/4          & 0, 10, 1, 0         \\ \hline
+Type Error       & 5/5           & 0, 0, 0, 0, 0          \\ \hline
+Keyword Ordering & 5/5           & 0, 1, 1, 0, 10       \\ \hline
 Value Relations  & 4/5           & 0, 1, 0, 0, 0        \\ 
@@
 
-All false positives were integer relations.
+All but one false positives were integer relations.
 Recall from Section \ref{} that false positives are the result of overfitting on rules.
@@
 
-The false positive for value relation is a result of the fact that we cannot learn rules that are disjunctions.
+The false positive for value relation (missing entry) is a result of the fact that we cannot learn rules that are disjunctions.
+In this case, no socket is provided to [mysqld], failing a rule we had learned over the dataset.
+In fact, this is not a misconfiguration because a socket only needs to be provided to one (or both) [mysqld] or [wampsqld].
+We reported an error since none of the files in the learning set had no socket associated with [mysqld].
+In fact, since we do not support disjunctive rules, we could not have even learned such a rule - though in practice these seem to be uncommon.

### 2016-01-29 code/Main.hs

@@ -41,10 +41,12 @@ benchmarks = [
   , "dataset/group3-path-type/error2"
   , "dataset/group3-path-type/error3"
   , "dataset/group3-path-type/error4"
+  , "dataset/group3-path-type/error5"
   , "dataset/group4-ordering/error_mysql"
   , "dataset/group4-ordering/error2"
   , "dataset/group4-ordering/error3"
   , "dataset/group4-ordering/error4"
+  , "dataset/group4-ordering/error5"
   , "dataset/group5-value-correlation/error"
   , "dataset/group5-value-correlation/error2"
   , "dataset/group5-value-correlation/error3"

### 2016-01-29 system.tex
random

@@
-\section{Quantum Types}
+\section{Learning the Rules}
+\label{sec:system}
+
+Before describe how our system for learning rules is working, we first outline a translator which converts configuration files into an intermediary representation.
+Typing is based on already given set of basic types.
+However, typing is also a system module than can be easily extended to support
+more types. In that case the user will need to provide rules for type inference and probability
+
+\subsection{From Untyped Expressions to Quantum Types}
+
+Typing the untyped expressions appearing in configuration files 
+is the first step in parsing and translating the data. 
+Configuration files usually consist of variable assignments, or some simple instructions about including files or libraries. We initially
+collect all assignments into a set of pairs $(n, v)$, where $n$ denotes 
+variable name and $v$ denotes variable value. However, based only on the 
+value $v$ we cannot determine the type of $n$.
+
+Consider for instance the following example:\\
+\texttt{\hspace*{2em}foo = 300\\
+\hspace*{2em}bar = 300.txt}\\
+Most likely \texttt{foo} is an integer, but it could also be a string.
+In the latter case we want to learn the rule $ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. We introduce {\emph{quantum types}} to 
+address this issue.
+
+Let $\mathcal{T}$ be a set of basic types. In \app set $\mathcal{T}$ contains strings, integers, file paths, sizes and IP addresses. 
+A quantum type built from $\mathcal{T}$ is a list of pairs $[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$ such that $\tau_i \in \mathcal{T}$ 
+and $\Sigma p_i = 1$.
 
@@
 Take the following file in the learning
-
-foo = 300
-bar = 300.txt
 
@@
 
-This idea is closely related to exstentially quantified types.
+This idea is closely related to existentially quantified types.
 

### 2016-01-29 system.tex
random

@@
 
-Before describe how our system for learning rules is working, we first outline a translator which converts configuration files into an intermediary representation.
-Typing is based on already given set of basic types.
-However, typing is also a system module than can be easily extended to support
-more types. In that case the user will need to provide rules for type inference and probability
+Before describing how our system for learning rules works, we first outline a translator which converts configuration files into an intermediary representation. Typing is based on an
+already given set of basic types. However, typing is also a system module than can be easily extended to support
+more types. In that case the user will need to provide rules for type inference and probability distributions for values where type inference is ambiguous.
 
@@
 
-Typing the untyped expressions appearing in configuration files 
-is the first step in parsing and translating the data. 
 Configuration files usually consist of variable assignments, or some simple instructions about including files or libraries. We initially
@@
 Let $\mathcal{T}$ be a set of basic types. In \app set $\mathcal{T}$ contains strings, integers, file paths, sizes and IP addresses. 
-A quantum type built from $\mathcal{T}$ is a list of pairs $[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$ such that $\tau_i \in \mathcal{T}$ 
-and $\Sigma p_i = 1$.
+A quantum type built from $\mathcal{T}$ is a list of pairs $[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$ such that $\tau_i \in \mathcal{T}$, 
+$0 \le p_i \le 1$ 
+and $\Sigma p_i = 1$. These probabilities are learned from the training 
+corpus.
 
-Because our type inference is based on machine learning, we cannot be sure that a keyword unambigously has a single type.
-This is an issue when we try to learn relational rules between keywords. 
-Take the following file in the learning
+When a value has a quantum type, we generate rules for all its types. This means that by assigning {\texttt{foo}} a quantum type 
+(e.g. $(\texttt{foo}, 300, [(\textsl{Int},90\%),(\textsl{String},10\%)])$
+we now generate rules for strings and integers.
 
-We want to learn the rule that $foo \in {substring(bar)}$, however using unambigous type inference, we would assign foo type int, and never try to generate a string relation rule for these two keywords.
-By assigning foo a quantum type (e.g. ${Int <90\%>, String <10\%>}$), we can now generate rules for both types.
+For a given value, its quantum type is updated over time. When the
 

### 2016-01-29 system.tex
random

@@
 
-For a given value, its quantum type is updated over time. When the
+For a given value, its quantum type is updated over time.
+When the type inference uniquely determines the type, the probability of all other types is set to zero, and  the associated rules are withdrawn.
 
-At runtime, when the user wants to check a file we update the probabilities one last time then 'collapse' the quantum type to a concrete type.
-If the concrete type collapses to a Int, we consider the rules for ints, and vice versa.
-
-This idea is closely related to existentially quantified types.
+This idea is closely related to existentially quantified types \cite{Launchbury93lazyfunctional}.
 

### 2016-01-29 evaluation.tex
good draft of eval and impl

@@
 
-\app is implemented in Haskell and takes full advantage of its polymorphism to make the system more modular.
+\app is implemented in Haskell takes full advantage of its polymorphism to make the system more modular.
 In particular, rules are represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
-By using various language extensions, this typeclass can be made polymorphic over the data structure (Foldable t =>).
-The user can then choose data structure that is most natural to the rule they are implementing.
-For example, in our implementation, missing keywords were easier to manipulate in lists, while types fit more naturally into a hashmap.
+By using language extensions (FlexibleInstances and MultiParamTypeClasses), this typeclass can be made polymorphic over the data structure as denoted by \lstinline{Foldable t =>}.
+The user can then choose a data structure that is most natural to the rule they are implementing.
+For example, in our implementation, Missing Entries were easier to manipulate in lists, while Type Errors fit more naturally into a hashmap.
+This typeclass defines the three functions that each set of rules must implement to work with our system.
+Typeclasses and other features of Haskell means that our system is only 267 lines of code, with anoth 233 for the rule modules.
+With an average size of 58 lines of code for each rule module, this is evidence of how simple it is to extend \app with new rules.
 
 \begin{lstlisting}
-class Foldable t => Attribute t a where
+class Foldable t => RuleSet t a where
   learn :: IRConfigFile -> t a
@@
 Since we learn a set of rules on each file in isolation from the other, we have an embarrassing parallel situation.
-Haskell allows us to easily take advantage of by using the parallel mapping library, parmap, both for translation to the intermediate representation, and for learning the rules on each file.
-The merge stage could also be parallelized, using a divide and conquer approach, but \app runs fast enough over our learning set (28 files) and resultsing rules (~4500 for integer relations) that this as not necessary.
+Haskell allows us to easily take advantage of this by using the parallel mapping library\cite{}, both for translation to the intermediate representation, and for learning the rules on each file.
+The merge stage could also easily be parallelized, using a divide and conquer approach, but \app runs fast enough over our learning set (28 files, 961 lines of code) that this has not been necessary.
 
-The integer relation rule has an unusual implementation that makes use of function as first-class objects in haskell.
-Rather than associated keywords with SMT formula, we directly associate them with a function of type (Int->Int->Bool).
+The integer relation rule has an unusual implementation that makes use of function as first-class objects in Haskell.
+Rather than associated keywords with SMT formula, we directly associate them with a function of type (\lstinline{Int->Int->Bool}).
 Since we need to compare rules over equality, we must then have a way to compare functions.
-This limits the types of functions we use to (==), (>=), and (<=).
+This limits the types of functions we use to \lstinline{(==),(>=),(<=)}.
 Although this is sufficent for most use cases, more fine-grained relations could be encoded with SMT formulas then passed to a solver.
@@
 To evaluate our tool, take a subset of the canonical benchmarks for configuration errors\cite{dataset}.
-We take the subset of benchmarks for which our tool has implemented modules.
+We take the subset of benchmarks for which our tool has implemented rule modules.
 Although our tool is general and extensible, we have only implemented four types of rules over the MySQL configuration language.
+It would not make sense to run \app on misconfigurations for which there are no rule modules.
 
-A benchmark passes a test if it reports an error on the source of the misconfiguration.
+A benchmark passes a test if it reports an error on the source of the misconfiguration (it is not a false negative).
 We call false positives any reported error that was unrelated to the value of interest.
@@
 Since these benchmarks are taken from online forums, there is no garuntee the files contain only a single error.
-Indeed, while running these benchmarks, \app found errors in the file that were similar to other benchmarks.
+Indeed, on some benchmarks, \app found errors in the file that were similar to rules broken by other benchmarks.
 
-We fail one benchmark in Value Relations because we do not yet support relations between file sizes of different units (Mb to Kb)
+We fail one benchmark in Value Relations because we do not yet support relations between file sizes of different units (Mb to Kb).
 In one Keyword Ordering benchmark, \app reports a type error on the value of interest instead of a ordering error.
@@
 \centering
-\caption{}
+\caption{Benchmarks for misconfiguration detection}
 \label{my-label}
@@
 
-All but one false positives were integer relations.
+All but one false positive reports were integer relations.
 Recall from Section \ref{} that false positives are the result of overfitting on rules.
@@
 
-The false positive for value relation (missing entry) is a result of the fact that we cannot learn rules that are disjunctions.
+The false positive for the Value Relation was a Missing Entry error.
+This is a result of the fact that we cannot learn rules that are disjunctions.
 In this case, no socket is provided to [mysqld], failing a rule we had learned over the dataset.

### 2016-01-29 evaluation.tex
random

@@
 
-\app is implemented in Haskell takes full advantage of its polymorphism to make the system more modular.
+\app is implemented in Haskell and takes full advantage of its polymorphism to make the system more modular.
 In particular, rules are represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
@@
 This typeclass defines the three functions that each set of rules must implement to work with our system.
-Typeclasses and other features of Haskell means that our system is only 267 lines of code, with anoth 233 for the rule modules.
+Typeclasses and other features of Haskell means that our system consists of only 267 lines of code, with another 233 for the rule modules.
 With an average size of 58 lines of code for each rule module, this is evidence of how simple it is to extend \app with new rules.

### 2016-01-29 motiv1.tex
added output for examples

@@
 This file caused that the Apache server could not start due to 
-the segmentation fault error. Running \app on this file returns\\
+the segmentation fault error. Running \app on this file would return\\
  \texttt{
-  one line output from our tool that indicates that things should be reordered}\\
+ORDERING ERROR: Expected "extension"recode.so" BEFORE "extension""mysql.so"
+  }\\
 Indeed, this was the source of the error. When using PHP in Apache, the
@@
 However, this configuration file will make LDAP server fail to work.
-Running \app on this configuration file returns:
-\xxx{Mark, put results here}\\
+Running \app on this configuration file would return:
+MISSING KEYWORD ERROR: Expected "overlay""ppolicy" in the same file as: "include""schema/ppolicy.schema"\\
 This was the source of the error. When using the password policy overlay
@@
 
-\subsection{Value Type Errors}
+\subsection{Type Errors}
 
@@
 \begin{verbatim}
-TYPE ERR ("general_log[mysqld]",ConfigQType {cint = Config {p = 1.0}, cstring = Config {p = 0.0}, cfilepath = Config {p = 0.0}})
+TYPE ERROR: Expected a Int with P=1.0  for "general_log[mysqld]"
 \end{verbatim}
@@
 Running \app on this combined configuration file returns:
-\xxx{Mark, put results here}\\
+INTEGER RELATION ERROR: Expected "max\_connections">="mysql.max\_persistent"
+\\
 We are successfully able to derive arithmetic relations between integer values.
@@
 larger than the ``max\_connections'' in MySQL configuration file.
-
-\subsection{Format Errors}
-\xxx{I am not sure if we still need the format error, so I 
-put it the last one.}
-
-When configuring NetApp commercial storage system, 
-the user writes the following entry:\\
-\texttt{
- \hspace*{3em}InitiatorName: iqn:DEV\_DOMAIN\\
-} 
-The NetApp storage share cannot be recognized. 
-Thus, we run \app on this configuration file and get the results:
-\xxx{Mark, put results here}\\
-This is the root-cause of the problem,
-since the iscsi device's initiator name, \ie, InitiatorName,
-only allows lowercase letters. However, the user sets the name with
-capital letters ``DEV\_DOMAIN''.
 
@@
 into five groups: 1) format error; 2) entry missing error; 3) value type
-error; 4) ordering error; and 5) value correlation error.
-The five examples in Fig.~\ref{fig-example} correspond to the above five
+error; and 4) ordering error
+The examples in Fig.~\ref{fig-example} correspond to the above four
 groups, respectively.

### 2016-01-29 motiv1.tex
fixing up motiv examples

@@
  \hspace*{3em}extension = recode.so}\\
-This file caused that the Apache server could not start due to 
-the segmentation fault error. Running \app on this file would return\\
+This file caused the Apache server to fail to start due to a segmentation fault error.
+When using PHP in Apache, the extension ``mysql.so'' depends on ``recode.so'' and the relative ordering of two of them is crucial. 
+The user is informed that ``recode.so'' should appear before ``mysql.so''.
+ Running \app on this file would return\\
  \texttt{
@@
   }\\
-Indeed, this was the source of the error. When using PHP in Apache, the
-extension ``mysql.so'' depends on ``recode.so'' and the relative ordering 
-of two of them is crucial. The user is informed that ``recode.so'' should appear before ``mysql.so''.
 
@@
 MISSING KEYWORD ERROR: Expected "overlay""ppolicy" in the same file as: "include""schema/ppolicy.schema"\\
-This was the source of the error. When using the password policy overlay
-in OpenLDAP, we have to first include the related schema. The correct configuration should be:\\
+When using the password policy overlay in OpenLDAP, we have to first include the related schema. The correct configuration should be:\\
 \texttt{
@@
  \hspace*{3em}general\_log = /var/log/mysql/mysql.log\\}
+The entry ``general\_log'' should be an integer, 
+and not a string. In MySQL, there is another entry named
+``general\_log\_file'' which is used to specify the log path.  
 After \app analyzed this configuration file, it correctly identifies the error:
@@
 \end{verbatim}
-The entry ``general\_log'' should be an integer, 
-and not a string. In MySQL, there is another entry named
-``general\_log\_file'' which is used to specify the log path.
 
@@
 ``too many connections''.
+We are successfully able to derive arithmetic relations between integer values.
+In particular, the ``mysql.max\_persistent'' in PHP should be no
+larger than the ``max\_connections'' in MySQL configuration file.
 Running \app on this combined configuration file returns:
@@
 \\
-We are successfully able to derive arithmetic relations between integer values.
-In particular, the ``mysql.max\_persistent'' in PHP should be no
-larger than the ``max\_connections'' in MySQL configuration file.
 

### 2016-01-29 system.tex

@@
 This idea is closely related to existentially quantified types \cite{Launchbury93lazyfunctional}.
-
-\section{Learning strategy}
-
-A primary concern in any machine learning type task is to minimize false negatives and false positives.
-In the context of configuration file verification,
-  a false positive is when \app reports an error on a valid confiuration file and
-  a false negative is when \app fails to reports an error on an invalid confiuration file.
-Too many false positives will cause users to ignore the reported error\cite{}.
-However, since the cost of system failure is so high from a misconfiguration, \app propritzes the minimization of false negatives.
-
-While a traditional classififcation learning machine learning approach can reduce both of these situations, there is can generally be no garuntee that all false negatives will be eliminated.
-Instead of building classification models over the learning set (such as an SVM), we learn the largest set of rules that all correct configuration files satisfy.
-In this way, \app can garuntee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set.
-The only case of a false negative can be when there was no evidece of such a rule in the learning set - we cannot generate rules from nothing.
-Framed as the question "Is this file valid", \app is complete but not sound.
-
-That is, taking the following definitions:
-\begin{multline*}\\
-\text{\{Considered Rules\}} = \forall files \in \text{\{Learning Set\}}, \{ r | r(files) = True \land r \text{ is non-trivial}\}\\
-\text{\{Reported Rules\}} = {r | r(userfile)=False } \\
-\text{\{True Rules\}} = \{r | \text{ if } r(userfile)=False \text{ then system crash } \land \\
-   \exists file \in \text{\{Learning Set\}}, r(file) \text{ is non-trivial}\}
-\end{multline*}
-
-We have the following specification of \app.
-\begin{multline*}\\
-\text{\{True Rules\}} \subseteq \text{\{Considered Rules\}} \\
-\forall r \in \text{\{True Rules\}}, if r(userfile)=False then \exists r \in \text{\{Reported Rules\}} \\
-\neg \forall r \in \text{\{Reported Rules\}}, r \in \text{\{True Rules\}} \\
-\end{multline*}
-
-Another benefit to a rule based approach is that, unlike many classificaton models, \app can actually report the reason for failure, similar to a comiler for a programming language.
-This is in contrast to neural nets for example, where we would just get a boolean value, and the mechanics of the system are entirly lost.
-Reporting useful errors that specify a point of failure is important to help users fix their misconfigurations.
-
-\section{Intermediate Representation}
-
-Part of the reason configuration file errors are so common is because of the large number of different systems being used on the market.
-Rather than proposing a new, unifying, configuration language (so that there would then be n+1 configuration languages), we use in intermediate representation language.
-This allows us to reuse all our algorithms over any configuration file that can be convereted to the intermediate representation.
-The portability of \app means that with very little intervtion, it can be widely used and adopted.
-
-More grammatically complex languages tend to be harder to translation to an intermediate representation.
-While there can be some context senestive structures in configuration files, we found it is easier to design the rule modules (Section \ref{}) to handle learning such structure, rather than encoding it in the intermediate representation.
-Additionally, configuration files are generally grammatically simple, consisting mostly of a list of keyword-value pairs.
-The keyword is the variable to be used in the system, and the value is the new value for that variable.
-
-To specialize the converter for a particular language, a user must define a new language type, which simply acts as a flag for translation.
-If a langauge requires specialized parsing, the user can write such code in the convert function based on pattern matching over the language type.
-For example, the user must specify the delimiters of the language (characters for assignment and comments) for their new language.
-
-\section{Rules}
-
-A core design principle in \app is modularity, so that a user can easily exentend it to their verification needs.
-Rather than try to support every type of verification over configuration files, we provide a framework for defining new verfication properties.
-We call each verification property a rule, for example the correct ordering of keywords or integer relationships between values.
-These rules tend to be pairs of values with a relation.
-For instance, an integer relation rule might be that the value of "foo" must be greater than the value of "bar".
-It is also important that the rule has some empty value, to state that it is known there is no relation between the values.
-This will prevent \app from trying to relearn rules when they have already been refuted.
-
-These rules are represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
-The typeclass can support anything that is Foldable, which roughly the user can use any datastructure.
-In fact, in our implementation, two rules are implemented with lists, and two others use hashmaps.
-
-\begin{lstlisting}
-class Foldable t => Attribute t a where
-  learn :: IRConfigFile -> t a
-  merge :: t a -> t a -> t a
-  check :: t a -> IRConfigFile -> Error
-\end{lstlisting}
-
-The functions of this typeclass will be used, invisibly to the user, to make the overall system run.
-As long as the specifications for each function are met, \app can garuntee completness.
-
-\subsection{learn}
-  For a single given file in the intermediate representation format, learn the full set of rules on that file.
-  By overfitting to each file, we can eventually garuntee the completness of \app.
-  The specification of this function is the obvious reduction of the Considered Set definition.
-
-  $\text{learn } file =  \{ r | r(file) = True \land r \text{ is non-trivial}\}$
-
-\subsection{merge}
-  Merging the sets of rules from two files to build a new set that is true over both files is the most difficult and important function a rule must implement.
-  This is generally implemented as a filter over the union of the two set, but may vary slightly.
-  The formal specification of this method is that:
-  \begin{multline*}
-  \text{merge } Set1 \: Set2= \{r \mid \\
-    r \in \text{Set1} \cup \text{Set2} \land \\
-    \exists file \forall r' \in \text{Set1} \cup \text{Set2}, r(file) = True \land r'(file) = True \} \\
-  \end{multline*}
-
-\subsection{check}
-  To check a file by using a rule set, we simply take all the rules that are releveant to the user's file.
-  Rules that are relavent are the ones where both parts of the ordering are present.
-  We learn the rule set for the user file, and every rule in the learned set must be present in the user file.
-
-\section{Implementation}
-
-\subsection{System}
-Since we learn a set of rules on each file in isolation from the other, we have an embarrassing parallel situation.
-Haskell allows us to easily take advantage of by using the parallel mapping library, parmap, both for translation to the intermediate representation, and for learning the rules on each file.
-\xxx{merge can also be parallelized, but i haven't done it yet and might not get a chance}
-
-\begin{lstlisting}
-learnRules :: [ConfigFile Language] -> RuleSet
-learnRules fs = let
-  fs' = parMap rseq convert fs
-  rs = parMap rdeepseq findAllRules fs'
- in
-  foldl1 mergeRules rs
-\end{lstlisting}
-
-\subsection{Type Error Rules}
-This builds a map between keywords and types, using the values as evidence.
-see quantum.tex for more
-i will write more on this tomorrow.
-
-\subsection{Integer Relation Rules}
-we only consider the relations , (==), (<=), (>=) because they are easy to pass aroud (as actual functions) in haskell.
-We also committed cardinal since and create an instance for equality over these functions.
-instance Eq (Int->Int->Bool) where
-
-With more engineering effort, this could be extened with the use of a SMT solver to create more fine grained relational rules.
-From our experience, more specific rule are not really needed for integer relations in configuration files.
-However an SMT solver approach would be particularly useful for relations on strings, especially when considering substring relations between filepaths.
-
-\subsection{Ordering and Missing Entry Rules}
-These are the simpiliest of all rules, just making a lot of pairs and seeing which pairs continue to appear over the learning set.
-
-There is actually a bit of a catch in ordering though - we are not complete over ordering rules.
-This is because only our implementation does not satisfy the specification for the merge function listed above.
-The problem arises from the fact the configuration files may have non-unique keywords.
-Therefor, in the follwoing file we will derive the valid, but conflicting rules ([client],port) and (port,[client]).
-\begin{verbatim}
-[client]
-port = 3306
-[mysqld]
-port = 3306
-\end{verbatim}
-Our implementation of merge removes and conflicting rules for the running set.
-By introducing a renaming pass in the initial parsing we may be able to solve this, but have not found a satisfactory solution yet.

### 2016-01-29 evaluation.tex
random

@@
-\section{Implementation}
+\section{Implementation and Evaluation}
 
@@
 
-Since we learn a set of rules on each file in isolation from the other, we have an embarrassing parallel situation.
-Haskell allows us to easily take advantage of this by using the parallel mapping library\cite{}, both for translation to the intermediate representation, and for learning the rules on each file.
+Since we learn a set of rules on each file in isolation from the other, we have a pleasingly parallel situation.
+Haskell allows us to easily take advantage of this by using the parallel mapping library \cite{}, both for translation to the intermediate representation, and for learning the rules on each file.
 The merge stage could also easily be parallelized, using a divide and conquer approach, but \app runs fast enough over our learning set (28 files, 961 lines of code) that this has not been necessary.
@@
 This limits the types of functions we use to \lstinline{(==),(>=),(<=)}.
-Although this is sufficent for most use cases, more fine-grained relations could be encoded with SMT formulas then passed to a solver.
+Although this is sufficient for most use cases, more fine-grained relations could be encoded with SMT formulas then passed to a solver.
 
-\section{Evaluation}
+\subsection{Evaluation}
 
-To evaluate our tool, take a subset of the canonical benchmarks for configuration errors\cite{dataset}.
+To evaluate our tool, we take a subset of 20 canonical benchmarks for configuration errors~\cite{yin11anempirical, configdataset} which are supported by our tool.
+Table~\ref{table:res} contains an evaluation summary.
+We do not report the running times, since they are negligible: even when
+ running in the interpreter mode, files are analyzed instantaneously. We spent approximately 30 second on learning the rules. When we run the compiled version, we need for lerning and verification 
+combined less than 5 seconds. Our focus is usefulness of the tool: its 
+ ability to detect configuration errors and the number of false positives.
+ For every benchmark class we took five examples.
+The middle column represents the number of detected errors, while the right column represents the number of returned false positives per each benchmark.
+
+\iffalse{
 We take the subset of benchmarks for which our tool has implemented rule modules.
 Although our tool is general and extensible, we have only implemented four types of rules over the MySQL configuration language.
-It would not make sense to run \app on misconfigurations for which there are no rule modules.
+It would not make sense to run \app on misconfigurations for which there are no rule modules.}
+\fi
 
@@
 It is worth noting that this is in fact a conservative estimate.
-Since these benchmarks are taken from online forums, there is no garuntee the files contain only a single error.
+Since these benchmarks are taken from online forums, there is no guarantee the files contain only a single error.
 Indeed, on some benchmarks, \app found errors in the file that were similar to rules broken by other benchmarks.
@@
 In one Keyword Ordering benchmark, \app reports a type error on the value of interest instead of a ordering error.
-This is a result of our context embedding in the translation to the intermediate represetnation - reordering the value puts it in a new context where the type is now also incorrect.
+This is a result of our context embedding in the translation to the intermediate representation - reordering the value puts it in a new context where the type is now also incorrect.
 
@@
 \caption{Benchmarks for misconfiguration detection}
-\label{my-label}
+\label{table:res}
 \begin{tabular}{l|l|l}
@@
 
-All but one false positive reports were integer relations.
-Recall from Section \ref{} that false positives are the result of overfitting on rules.
-\app can learn overfit rules when the learning set does not show the full spectrum of possible values.
-Since integer relations have a larger space of relation than say, ordering relations, \app needs a larger learning set in order to eliminate false positives.
+All but one false positive reports were integer relations. They are the result of overfitting on rules.
+\app can learn overapproximating rules when the learning set does not show the full spectrum of possible values.
+Since integer relations have a larger space of relation than ordering relations for instance, \app needs a larger learning set in order to eliminate false positives.
 

### 2016-01-29 motiv1.tex
motiv are good

@@
 
-We begin our motivation for a tool such as \app by providing several misconfiguration examples, and showing how do we address them. All these examples are extracted from real-world reports%
-~\cite{yin11anempirical, configdataset}.
-When writing configuration files, the user usually takes already existing files and modifies them.
-If the original file is already corrupted, the errors are propagated further.
-However, even if the original file is correct, changing the file by a non-expert user can easily result in errors.
+When writing configuration files, the user usually takes already existing files and modifies the, with little knowledge of the system. 
+The non-expert user can then easily introduce in errors.
+Even worse, the original file may already corrupted and the errors are propagated further. 
+Below we show some examples of the errors commonly found in configuration files.
+All these examples are extracted from real-world reports % ~\cite{yin11anempirical, configdataset}.
+The deep, domain specifc knowledge needed to indentify these error manually is strong motivation for a tool such as \app.
 
@@
 When using PHP in Apache, the extension ``mysql.so'' depends on ``recode.so'' and the relative ordering of two of them is crucial. 
-The user is informed that ``recode.so'' should appear before ``mysql.so''.
- Running \app on this file would return\\
+\app would inform the user that ``recode.so'' should appear before ``mysql.so'', and return the error:\\
  \texttt{
-ORDERING ERROR: Expected "extension"recode.so" BEFORE "extension""mysql.so"
-  }\\
+ORDERING ERROR: Expected "extension"recode.so"\\
+   BEFORE "extension""mysql.so"
+  }
 
@@
 \texttt{
+ \hspace*{3em}include schema/ppolicy.schema\\
  \hspace*{3em}overlay ppolicy\\}
-However, this configuration file will make LDAP server fail to work.
-Running \app on this configuration file would return:
-MISSING KEYWORD ERROR: Expected "overlay""ppolicy" in the same file as: "include""schema/ppolicy.schema"\\
-When using the password policy overlay in OpenLDAP, we have to first include the related schema. The correct configuration should be:\\
+When using the password policy overlay in OpenLDAP, we have to first include the related schema.
+Leaving out the ``include'' statement will cause this LDAP server fail to work:\\
+Running \app on such a misconfiguration file would return:\\
 \texttt{
- \hspace*{3em}include schema/ppolicy.schema\\
- \hspace*{3em}overlay ppolicy\\
-}
+MISSING KEYWORD ERROR: Expected "overlay""ppolicy"\\ 
+in the same file as: "include""schema/ppolicy.schema"}
 
@@
 
-If the user tries to install MySQL, she first needs to 
-initiate the path for the
-log information generated by MySQL. A user puts the following code in 
-her MySQL configuration file:\\
+If the user tries to install MySQL, she first needs to initiate the path for the log information generated by MySQL. 
+A user may put the following code in the MySQL configuration file:\\
 \texttt{
  \hspace*{3em}general\_log = /var/log/mysql/mysql.log\\}
-The entry ``general\_log'' should be an integer, 
-and not a string. In MySQL, there is another entry named
-``general\_log\_file'' which is used to specify the log path.  
-After \app analyzed this configuration file, it correctly identifies the error:
-\begin{verbatim}
-TYPE ERROR: Expected a Int with P=1.0  for "general_log[mysqld]"
-\end{verbatim}
+However, the entry ``general\_log'' should be an integer, not a string.
+ In MySQL, there is another entry named ``general\_log\_file'' which is used to specify the log path.  
+After \app analyzes this configuration file, it correctly identifies the error:\\
+\texttt{
+TYPE ERROR: Expected a Int with P=1.0 for "general\_log[mysqld]"
+}
 
@@
 
-When configuring PHP on MySQL, the user writes the following lines 
-of entries in her both PHP and MySQL configuration files:\\
+When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\
 \texttt{
@@
  \hspace*{3em}mysql.max\_persistent = 400\\}
-This will cause MySQL to abort with the error information:
-``too many connections''.
-We are successfully able to derive arithmetic relations between integer values.
-In particular, the ``mysql.max\_persistent'' in PHP should be no
-larger than the ``max\_connections'' in MySQL configuration file.
-Running \app on this combined configuration file returns:
-INTEGER RELATION ERROR: Expected "max\_connections">="mysql.max\_persistent"
-\\
+This could cause MySQL to abort with the error information: ``too many connections''.
+In this case, the ``mysql.max\_persistent'' in PHP should be no larger than the ``max\_connections'' in MySQL configuration file.
+Another rule we have implemented is learning inequality relations between integers.
+Running \app on this combined configuration file would return:
+\texttt{
+INTEGER RELATION ERROR: Expected "max\_connections">="mysql.max\_persistent"}
 

### 2016-01-29 system.tex
random

@@
 
-\subsection{From Untyped Expressions to Quantum Types}
+\subsection{From Untyped Expressions to Probabilistic Types}
 
@@
 Most likely \texttt{foo} is an integer, but it could also be a string.
-In the latter case we want to learn the rule $ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. We introduce {\emph{quantum types}} to 
+In the latter case we want to learn the rule $ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. We introduce {\emph{probabilistic types}} to 
 address this issue.
@@
 Let $\mathcal{T}$ be a set of basic types. In \app set $\mathcal{T}$ contains strings, integers, file paths, sizes and IP addresses. 
-A quantum type built from $\mathcal{T}$ is a list of pairs $[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$ such that $\tau_i \in \mathcal{T}$, 
+A probabilistic type built from $\mathcal{T}$ is a list of pairs $[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$ such that $\tau_i \in \mathcal{T}$, 
 $0 \le p_i \le 1$ 
@@
 
-When a value has a quantum type, we generate rules for all its types. This means that by assigning {\texttt{foo}} a quantum type 
+When a value has a probabilistic type, we generate rules for all its types. This means that by assigning {\texttt{foo}} a probabilistic type 
 (e.g. $(\texttt{foo}, 300, [(\textsl{Int},90\%),(\textsl{String},10\%)])$
@@
 
-For a given value, its quantum type is updated over time.
+For a given value, its probabilistic type is updated over time.
 When the type inference uniquely determines the type, the probability of all other types is set to zero, and  the associated rules are withdrawn.

### 2016-01-29 abs.tex
rewording to be in english

@@
 Software failures resulting from configuration errors 
-have been commonplaces as modern software systems 
-become increasingly larger and more complex.
+have become commonplace as modern software systems 
+grow increasingly large and more complex.
 The lack of language constructs in configuration files, 
 such as types and grammars, 
-directed the focus of a configuration file verification 
+has directed the focus of a configuration file verification 
 towards building post-failure error diagnosis tools. 
@@
 datasets of correct configuration files and derives rules for building a
-language model for the given dataset. 
+language model from the given dataset. 
 The resulting language model can be used
@@
 \app supports learning of various rules, such as orderings,
-value relations, and type errors, 
-by defining a minimal interface for a rule, and by using a probabilistic types inference stategy.
+value relations, type errors, or user definied rules
+by using a probabilistic type inference stategy and
+defining a small interface for the rule type.
 

### 2016-01-29 motiv1.tex

@@
 Even worse, the original file may already corrupted and the errors are propagated further. 
-Below we show some examples of the errors commonly found in configuration files.
+Below we show some real worlds examples of the errors commonly found in configuration files.
 All these examples are extracted from real-world reports % ~\cite{yin11anempirical, configdataset}.
-The deep, domain specifc knowledge needed to indentify these error manually is strong motivation for a tool such as \app.
+The deep, domain specific knowledge needed to identify these error manually is strong motivation for a tool such as \app.
 

### 2016-01-29 intro1.tex

@@
 after failures occur~\cite{wang04automatic,attariyan10automating,
-su07autobash,whitaker04configuration}, these tools rely on manual ways
-  to understand and detect the failure symptoms. The main reasons are:
+su07autobash,whitaker04configuration}, these tools rely on a manual approach
+  to understand and detect the failure symptoms. The main reasons for this are:
   1) entries in configuration files are untyped assignments, 2) there
   is no explicit structure policy for the entries in configuration
-  files, and 3) there is surprisingly little rules specifying the
+  files, and 3) there are surprisingly few rules specifying the
   entries' constraints.
@@
 Fig.~\ref{fig-overview} describes an overview of our system. We start
-with an assumption that we are given a number of correct configuration
+with the assumption that we are given a number of correct configuration
 files belonging to the same category (for instance, MySQL or
-Apache). Such files follow the same naming conventions and we use that
-fact in a learning algorithm which will result with the rules
-describing the language model used in the files. Since the
+Apache). Such files follow similar patterns, which we exploit
+in a learning algorithm to build rules that
+describe a language model for the files. Since the
 ``language'' of configuration types is untyped and unstructured, we
 first parse the files and translate them into a more structured,
-typed, intermediary representation.
-When parsing the untyped files, sometimes the correct file cannot be determined from a variable declaration.
-We address this problem by introducing so called {\emph{quantum types}}.
-To a variable we do not associate a type, but several types with their probability distributions.
-Having more structured files, we
-use them as a training set to learn the rules. The learning algorithm
-is template-based. We provide an initial set of templates and the
+intermediary representation.
+When running type inference on a configuration file, the type of a variable cannot always be fully determined from a single value.
+We address this problem by introducing so called {\emph{probabalistic types}}.
+Rather than givng a variable a single type, we assign several types with their probability distributions. 
+We can then use these more structured files
+as a training set to learn the rules. The learning algorithm
+is template-based to be easily extensible. We provide an initial set of templates and the
 learner learns some concrete instances from the training set. These
@@
 As an 
-illustration for a simple rule that we can learn, consider a template
+illustration of a simple rule that we can learn, consider a template
  $X_1 \le X_2$, where $X_1$ and $X_2$ are
@@
 existing work on automated configuration troubleshooting~\cite{yin11anempirical, configdataset}. We provide templates for every class that \app can handle: we consider integer constraints, ordering
-constraints, typing constraints, constraints about correlated entries (such as ``if $X$ is present, $Y$ has to appear as well'').
-Unfortunately, there are a few classes of errors that we cannot handle.
-They
- rely on the analysis of the whole operating system and our language-based
-approach is not expressive enough for them.
+constraints, typing constraints, and constraints about correlated entries (such as ``if $X$ is present, $Y$ has to appear as well''). 
+Unfortunately, we cannot handle the class of errors that rely on the analysis of the whole operating system.
+Our language-based approach can only learn on sets of text files, not the system environment.
 
@@
 
-Finally, from a system perspective this is the first approach that checks 
-{\emph{proactively}} the correctness of configuration files. All previous work
+Finally, from a systems perspective this is the first approach that {\emph{proactively}} checks 
+ the correctness of configuration files. All previous work
 ~\cite{xu15systems,zhang14encore,yuan11context, wang04automatic,attariyan10automating,
@@
 
-  \item We designed and implemented a tool, \app, that can learn a language model from a set of examples of correct configuration files, and we use the model to verify new files.
-  \item We use probabilistic types to assign to a value a confidence distribution over a set of types.
-  \item In \app we define a minimal interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.
+  \item We designed and implemented a tool, \app, that can learn a language model from an example set of correct configuration files, and we use the model to verify new files.
+  \item We use probabilistic types to assign a confidence distribution over a set of types to a value.
+  \item In \app we define a interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.
 

### 2016-01-29 intro1.tex
autocommit

@@
 
-From a  practical perspective there is no additional burden 
+From a practical perspective \app introduces no additional burden 
 to the users: they can simply use \app to check for errors in their configuration files.

### 2016-01-29 related.tex

@@
-\section{Related Work and Conclusions}
+\section{Conclusions}
 
-\xxx{conclude here ...}
+In this paper, we propose a highly-modular framework that helps 
+users to verify their configuration files through learning
+rules from datasets of correct configuration files.
+We have implemented design as a tool, named \app, in Haskell 
+and evaluated \app by checking real incorrect configuration file datasets.

### 2016-01-29 motiv1.tex

@@
 
-\subsection{Ordering Errors}
-
-When configuring PHP to run with the Apache HTTP Server the user writes, among others, the following lines:\\
+\vspace{1em}{\bf{Ordering Errors.}} When configuring PHP to run with the Apache HTTP Server the user writes, among others, the following lines:\\
  \texttt{
@@
 
-\subsection{Entry Missing Errors}
-
-If the user wants to use OpenLDAP to enable her directory access
+\vspace{1em}{\bf{Entry Missing Errors.}} If the user wants to use OpenLDAP to enable her directory access
 protocol, she needs to use the password policy overlay. This is usually
@@
 
-\subsection{Type Errors}
-
-If the user tries to install MySQL, she first needs to initiate the path for the log information generated by MySQL. 
+\vspace{1em}{\bf{Type Errors.}} If the user tries to install MySQL, she first needs to initiate the path for the log information generated by MySQL. 
 A user may put the following code in the MySQL configuration file:\\
@@
 
-\subsection{Value Correlation Errors}
-
-When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\
+\vspace{1em}{\bf{Value Correlation Errors.}} When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\
 \texttt{
@@
 \texttt{
-INTEGER RELATION ERROR: Expected "max\_connections">="mysql.max\_persistent"}
+INTEGER RELATION ERROR: \\
+Expected "max\_connections">="mysql.max\_persistent"}
 

### 2016-01-29 system.tex
reduce type section

@@
 
-Configuration files usually consist of variable assignments, or some simple instructions about including files or libraries. We initially
-collect all assignments into a set of pairs $(n, v)$, where $n$ denotes 
-variable name and $v$ denotes variable value. However, based only on the 
-value $v$ we cannot determine the type of $n$.
+Each line of a configuration files can be reduced to a keyword value pair
+In the parsing step we collect all lines in the file into a set of such pairs $(k, v)$, where $k$ denotes 
+variable name and $v$ denotes variable value. 
+However, based only on a single example value of $v$ we cannot fully determine the type of $k$.
+We instead assign a distribution of type to a value, an idea is closely related to existentially quantified types \cite{Launchbury93lazyfunctional}.
 
@@
 \hspace*{2em}bar = 300.txt}\\
-Most likely \texttt{foo} is an integer, but it could also be a string.
-In the latter case we want to learn the rule $ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. We introduce {\emph{probabilistic types}} to 
-address this issue.
+Most likely \texttt{foo} is an integer and we learn an equality rule, but it could also be a string.
+In this case we want to learn the rule $ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. 
+For more advanced rules, we may need to even compose these types to learn complex rules.
+We introduce {\emph{probabilistic types}} to address this issue.
 
@@
 $0 \le p_i \le 1$ 
-and $\Sigma p_i = 1$. These probabilities are learned from the training 
-corpus.
-
+and $\Sigma p_i = 1$. These probabilities are updated each time a new example value for a keyword is encountered.
 When a value has a probabilistic type, we generate rules for all its types. This means that by assigning {\texttt{foo}} a probabilistic type 
 (e.g. $(\texttt{foo}, 300, [(\textsl{Int},90\%),(\textsl{String},10\%)])$
-we now generate rules for strings and integers.
-
-For a given value, its probabilistic type is updated over time.
-When the type inference uniquely determines the type, the probability of all other types is set to zero, and  the associated rules are withdrawn.
-
-This idea is closely related to existentially quantified types \cite{Launchbury93lazyfunctional}.
+we now generate rules for both strings and integers.
+Once the type inference can uniquely determine the type, the probability of all other types is set to zero, and the associated rules are withdrawn.

### 2016-01-29 motiv1.tex

@@
 
-\vspace{1em}{\bf{Ordering Errors.}} When configuring PHP to run with the Apache HTTP Server the user writes, among others, the following lines:\\
+\para{Ordering Errors.} When configuring PHP to run with the Apache HTTP Server the user writes, among others, the following lines:\\
  \texttt{
@@
 
-\vspace{1em}{\bf{Entry Missing Errors.}} If the user wants to use OpenLDAP to enable her directory access
+\para{Entry Missing Errors.} If the user wants to use OpenLDAP to enable her directory access
 protocol, she needs to use the password policy overlay. This is usually
@@
 
-\vspace{1em}{\bf{Type Errors.}} If the user tries to install MySQL, she first needs to initiate the path for the log information generated by MySQL. 
+\para{Type Errors.} If the user tries to install MySQL, she first needs to initiate the path for the log information generated by MySQL. 
 A user may put the following code in the MySQL configuration file:\\
@@
 
-\vspace{1em}{\bf{Value Correlation Errors.}} When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\
+\para{Value Correlation Errors.} When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\
 \texttt{

### 2016-01-29 system.tex
autocommit

@@
 
-Before describing how our system for learning rules works, we first outline a translator which converts configuration files into an intermediary representation. Typing is based on an
-already given set of basic types. However, typing is also a system module than can be easily extended to support
-more types. In that case the user will need to provide rules for type inference and probability distributions for values where type inference is ambiguous.
+To learn rules, we first translate to the intermediate representation where each line of a configuration file is reduced to a keyword-value pair $(k,v)$.
+Of course, parsing is language dependant and users may provide extra help to the translator for their specific language, such as specifying a comment character.
+We must assign types to the keywords to guide the learning modules.
+With typed keyword-value pairs, we can run each learning module independent of each other.
+We learn a set of rules over a every file, then merge the rules of all files based on some user definied measure of consistency.
+The final rule set is all the rules that are true on the learning set
 
@@
 
-Each line of a configuration files can be reduced to a keyword value pair
-In the parsing step we collect all lines in the file into a set of such pairs $(k, v)$, where $k$ denotes 
-variable name and $v$ denotes variable value. 
 However, based only on a single example value of $v$ we cannot fully determine the type of $k$.
 We instead assign a distribution of type to a value, an idea is closely related to existentially quantified types \cite{Launchbury93lazyfunctional}.
+However, typing is also a system module than can be easily extended to support more types. 
+In that case the user will need to provide rules for type inference and probability distributions for values where type inference is ambiguous.
 

### 2016-01-29 evaluation.tex
config: updated

@@
 
-\begin{table}[]
+\begin{table}[t]
 \centering
@@
 \begin{tabular}{l|l|l}
-Error Type       & Passing Tests & False Positives  \\ \hhline{|=|=|=|}
+Error Type       & Passing Tests & False Positives  \\ \hhline{=|=|=}
 Missing Entry    & 5/5           & 1, 0, 0, 0, 1        \\ \hline
@@
 \end{table}
+%\vspace{-5em}
 

### 2016-01-29 motiv1.tex

@@
 
-\para{Ordering Errors.} When configuring PHP to run with the Apache HTTP Server the user writes, among others, the following lines:\\
+\para{Example~1: Ordering Errors.} When configuring PHP to run with the Apache HTTP Server the user writes, among others, the following lines:\\
  \texttt{
@@
 
-\para{Entry Missing Errors.} If the user wants to use OpenLDAP to enable her directory access
+\para{Example~2: Entry Missing Errors.} If the user wants to use OpenLDAP to enable her directory access
 protocol, she needs to use the password policy overlay. This is usually
@@
 
-\para{Type Errors.} If the user tries to install MySQL, she first needs to initiate the path for the log information generated by MySQL. 
+\para{Example~3: Type Errors.} If the user tries to install MySQL, she first needs to initiate the path for the log information generated by MySQL. 
 A user may put the following code in the MySQL configuration file:\\
@@
 
-\para{Value Correlation Errors.} When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\
+\para{Example~4: Value Correlation Errors.} When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\
 \texttt{

### 2016-01-29 intro1.tex
config: fig
random

@@
 \begin{figure}[t] \centering
-\includegraphics[width=0.8\textwidth]{figs/overview}
-\caption{\app's workflow overview. The green boxes represent configuration files,
+\includegraphics[width=0.65\textwidth]{figs/overview}
+\caption{{\footnotesize \app's workflow. The green boxes represent configuration files,
   including both correct general configuration files and users' input
   configuration files. The purple boxes are the components within \app.
-  The yellow boxes are results generated by \app's components.}
+  The yellow boxes are results generated by \app's components.}}
 \label{fig-overview}
@@
 
-Fig.~\ref{fig-overview} describes an overview of our system. We start
+Figure~\ref{fig-overview} describes an overview of our system. We start
 with the assumption that we are given a number of correct configuration
@@
 We address this problem by introducing so called {\emph{probabalistic types}}.
-Rather than givng a variable a single type, we assign several types with their probability distributions. 
+Rather than giving a variable a single type, we assign several types with their probability distributions. 
 We can then use these more structured files
@@
  $X_1 \le X_2$, where $X_1$ and $X_2$ are
-integer variables. The learned might derive the rule stating that
+integer variables. The learner might derive the rule stating that
 $\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. There is a classification and taxonomy of configuration errors in the 

### 2016-01-29 motiv1.tex
config: motiv

@@
 
-\para{Example~1: Ordering Errors.} When configuring PHP to run with the Apache HTTP Server the user writes, among others, the following lines:\\
+\para{Example~1: Ordering Errors.} When configuring PHP to run with the
+Apache HTTP Server, the user writes, among others, the following lines:\\
  \texttt{
@@
 When using the password policy overlay in OpenLDAP, we have to first include the related schema.
-Leaving out the ``include'' statement will cause this LDAP server fail to work:\\
+Leaving out the ``include'' statement will cause the failure of 
+this LDAP:\\
 Running \app on such a misconfiguration file would return:\\
@@
 
+\vspace{-0.15cm}
 \para{Example~4: Value Correlation Errors.} When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\

### 2016-01-29 evaluation.tex

@@
 
-To evaluate our tool, we take a subset of 20 canonical benchmarks for configuration errors~\cite{yin11anempirical, configdataset} which are supported by our tool.
+To evaluate our tool, we take a subset of 20 benchmarks from an existsing dataset of configuration errors~\cite{yin11anempirical, configdataset} which are supported by our tool.
 Table~\ref{table:res} contains an evaluation summary.

### 2016-01-29 intro1.tex
config: intro

@@
 \begin{figure}[t] \centering
-\includegraphics[width=0.65\textwidth]{figs/overview}
+\includegraphics[width=0.63\textwidth]{figs/overview}
 \caption{{\footnotesize \app's workflow. The green boxes represent configuration files,
@@
 
-  \item We designed and implemented a tool, \app, that can learn a language model from an example set of correct configuration files, and we use the model to verify new files.
+  \item We designed and implemented a tool, \app, that can learn a
+language model from an example set of correct configuration files, and
+we use the model to verify new configuration files.
   \item We use probabilistic types to assign a confidence distribution over a set of types to a value.

### 2016-01-29 related.tex
autocommit

--- 2016-01-25 related.tex
@@
-\section{Related Work and Conclusions}
+\section{Conclusions}
 
-\xxx{conclude here ...}
+In this paper, we propose a highly-modular framework that allows verification of configuration files, even without language model of the file.
+\app can easily be extended to support new verification properties and new configuration langauages.
+New verification properties require only a small amount of code and are not language specific, all indicating that \app could be widely adopted by system administrators.
+Having such verification tool that scales in both performance and expressivity can revolutionize configuration file checking, reducing the cost of system maintaince and failure dramatically.

### 2016-01-29 motiv1.tex
config: error

@@
 
-When writing configuration files, the user usually takes already existing files and modifies the, with little knowledge of the system. 
+When writing configuration files, users usually take already existing
+files and modifies the files, with little knowledge of the system. 
 The non-expert user can then easily introduce in errors.
@@
 Leaving out the ``include'' statement will cause the failure of 
-this LDAP:\\
-Running \app on such a misconfiguration file would return:\\
+this LDAP. Running \app on such a misconfiguration file would return:\\
 \texttt{
@@
 
-\vspace{-0.15cm}
+\vspace{-0.25cm}
 \para{Example~4: Value Correlation Errors.} When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\

### 2016-01-29 related.tex
autocommit

--- 2016-01-25 related.tex
@@
-\section{Related Work and Conclusions}
+\section{Conclusions}
 
-\xxx{conclude here ...}
+In this paper, we introduce \app, a highly-modular framework that allows verification of configuration files, even without a language model of the file.
+New verification properties require only a small amount of code and are not language specific, all indicating that \app could be widely adopted by system administrators.
+Such a verification tool that scales in both performance and expressivity can revolutionize configuration file checking, reducing the cost of system maintaince and failure dramatically.

### 2016-01-29 system.tex
random

@@
 To learn rules, we first translate to the intermediate representation where each line of a configuration file is reduced to a keyword-value pair $(k,v)$.
-Of course, parsing is language dependant and users may provide extra help to the translator for their specific language, such as specifying a comment character.
+Parsing is language dependent and users may provide extra help to the translator for their specific language, such as specifying a comment character.
 We must assign types to the keywords to guide the learning modules. 
 With typed keyword-value pairs, we can run each learning module independent of each other.
-We learn a set of rules over a every file, then merge the rules of all files based on some user definied measure of consistency.
-The final rule set is all the rules that are true on the learning set
+We learn a set of rules over a every file, then merge the rules of all files.
 
-\subsection{From Untyped Expressions to Probabilistic Types}
-
-However, based only on a single example value of $v$ we cannot fully determine the type of $k$.
-We instead assign a distribution of type to a value, an idea is closely related to existentially quantified types \cite{Launchbury93lazyfunctional}.
-However, typing is also a system module than can be easily extended to support more types. 
-In that case the user will need to provide rules for type inference and probability distributions for values where type inference is ambiguous.
-
+{\bf {Introducing the types.}} Based only on a single example value of $v$ we cannot fully determine the type of $k$.
 Consider for instance the following example:\\
@@
 In this case we want to learn the rule $ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. 
-For more advanced rules, we may need to even compose these types to learn complex rules.
+We therefore assign a distribution of types to a value, an idea closely related to existentially quantified types \cite{Launchbury93lazyfunctional}.
 We introduce {\emph{probabilistic types}} to address this issue.
@@
 and $\Sigma p_i = 1$. These probabilities are updated each time a new example value for a keyword is encountered.
+
 When a value has a probabilistic type, we generate rules for all its types. This means that by assigning {\texttt{foo}} a probabilistic type 
@@
 Once the type inference can uniquely determine the type, the probability of all other types is set to zero, and the associated rules are withdrawn.
+
+Note that typing is also a system module than can be easily extended to support more types. 
+In that case the user will need to provide rules for type inference and probability distributions for values where type inference is ambiguous.
+
+{\bf {Rules Learning.}}
+
+While a traditional classification learning machine learning approach can reduce both of these situations, there is can generally be no guarantee that all false negatives will be eliminated.
+Instead of building classification models over the learning set (such as an SVM), we learn the largest set of rules that all correct configuration files satisfy.
+In this way, \app can guarantee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set.
+The only case of a false negative can be when there was no evidence of such a rule in the learning set - we cannot generate rules from nothing.
+Framed as the question "Is this file valid", \app is complete but not sound

### 2016-02-09 CAV/abs.tex
make a new dir for icfp

--- 2016-01-29 abs.tex
@@
 \app supports learning of various rules, such as orderings,
-value relations, type errors, or user definied rules
-by using a probabilistic type inference stategy and
+value relations, type errors, or user defined rules
+by using a probabilistic type inference strategy and
 defining a small interface for the rule type.

### 2016-02-09 CAV/arch.tex
make a new dir for icfp

\section{Architecture Overview}

A rule R is added to the set of all rules,
  if $\exists$ learning file f s.t. R(f) is non vacuously true
That rule R is then removed from the set of all rules,
  if $\exists$ learning file f st R(f) is false.

This is accomplished in two passes.
First we collect all possible rules for every file.
Then we merge the all the rules to create our final set.
This conviently gives rise to an embarresingly parallel situation, which Haskell allows us to easily take advantage of by
  using the parallel mapping library parmap.

\begin{lstlisting}
  potentialRules = parmap findAllRules learningSet.
  finalRules = foldl1 mergeRules potenialRules
\begin{lstlisting}

Each rule is of the Attribute typeclass, which means a rule must support the following operations:
\begin{lstlisting}
class Attribute r where
  learn :: ConfigFile Common -> [r]
  merge :: [r] -> [r] -> [r] 
  check :: [r] -> ConfigFile Common -> Error
\end{lstlisting}

\section{Ordering}
\subsection{learn}
  For a single given file, we take very line ordering to be a rule.
\subsection{merge}
  Then when merging these sets of rules, we take the intersection of the rules infered on the individual files.
  Maybe we could also do something like only taking rules that show up multiple times.
\subsection{check}
  To check a file by using a rule set, we simply take all the rules that are releveant to the user's file.
  Rules that are relavent are the ones where both parts of the ordering are present.
  We learn the rule set for the user file, and every rule in the learned set must be present in the user file.

### 2016-02-09 CAV/design.tex
make a new dir for icfp

--- 2016-01-28 design.tex
@@
 
-There is actually a bit of a catch in ordering though - we are not complete over ordering rules.
+There is actually a bit of a catch in ordering though - we are not complete over ordering rules.\xxx{since last code update to add context we complete again}
 This is because only our implementation does not satisfy the specification for the merge function listed above.

### 2016-02-09 CAV/quantum.tex
make a new dir for icfp

\section{Quantum Types}

Because our type inference is based on machine learning, we cannot be sure that a keyword unambigously has a single type.
This is an issue when we try to learn relational rules between keywords. 
Take the following file in the learning

foo = 300
bar = 300.txt

We want to learn the rule that $foo \in {substring(bar)}$, however using unambigous type inference, we would assign foo type int, and never try to generate a string relation rule for these two keywords.
By assigning foo a quantum type (e.g. ${Int <90\%>, String <10\%>}$), we can now generate rules for both types.

At runtime, when the user wants to check a file we update the probabilities one last time then 'collapse' the quantum type to a concrete type.
If the concrete type collapses to a Int, we consider the rules for ints, and vice versa.

This idea is closely related to exstentially quantified types.

### 2016-02-09 CAV/system.tex
make a new dir for icfp

--- 2016-01-29 system.tex
@@
 
-{\bf {Rules Learning.}}
-
-While a traditional classification learning machine learning approach can reduce both of these situations, there is can generally be no guarantee that all false negatives will be eliminated.
-Instead of building classification models over the learning set (such as an SVM), we learn the largest set of rules that all correct configuration files satisfy.
-In this way, \app can guarantee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set.
+{\bf {Rule Learning.}} With every type we associate a set of templates, specific to this type.
+Once the input files are fully type-annotated, we generate rules that are instances of these templates.
+We always learn the largest set of rules that all correct configuration files satisfy.
+This way \app can guarantee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set.
 The only case of a false negative can be when there was no evidence of such a rule in the learning set - we cannot generate rules from nothing.
-Framed as the question "Is this file valid", \app is complete but not sound
+%Framed as the question "Is this file valid", \app is complete but not sound

### 2016-02-09 ICFP/formalism.tex
make a new dir for icfp

--- 2016-01-28 design.tex
@@
-\section{\app Design}
-
-\xxx{
-\app Design: 
-  \begin{itemize}
-  \item Present an architecture of \app with a fig. Briefly describe 
-    how it works (step by step).
-  \item Detail learner part
-  \item Merge
-  \item Check 
-  \item Limitations
-  \end{itemize}
-}
-
 \section{Learning strategy}
@@
 \end{multline*}
-
-Another benefit to a rule based approach is that, unlike many classificaton models, \app can actually report the reason for failure, similar to a comiler for a programming language.
-This is in contrast to neural nets for example, where we would just get a boolean value, and the mechanics of the system are entirly lost.
-Reporting useful errors that specify a point of failure is important to help users fix their misconfigurations.
-
-\section{Intermediate Representation}
-
-Part of the reason configuration file errors are so common is because of the large number of different systems being used on the market.
-Rather than proposing a new, unifying, configuration language (so that there would then be n+1 configuration languages), we use in intermediate representation language.
-This allows us to reuse all our algorithms over any configuration file that can be convereted to the intermediate representation.
-The portability of \app means that with very little intervtion, it can be widely used and adopted.
-
-More grammatically complex languages tend to be harder to translation to an intermediate representation.
-While there can be some context senestive structures in configuration files, we found it is easier to design the rule modules (Section \ref{}) to handle learning such structure, rather than encoding it in the intermediate representation.
-Additionally, configuration files are generally grammatically simple, consisting mostly of a list of keyword-value pairs.
-The keyword is the variable to be used in the system, and the value is the new value for that variable.
-
-To specialize the converter for a particular language, a user must define a new language type, which simply acts as a flag for translation.
-If a langauge requires specialized parsing, the user can write such code in the convert function based on pattern matching over the language type.
-For example, the user must specify the delimiters of the language (characters for assignment and comments) for their new language.
 

### 2016-02-11 ICFP/formalism.tex
polishing formulas

@@
 
-A primary concern in any machine learning type task is to minimize false negatives and false positives.
+A primary concern in any machine learning type task is to minimize both false negatives and false positives.
 In the context of configuration file verification,
@@
 
-While a traditional classififcation learning machine learning approach can reduce both of these situations, there is can generally be no garuntee that all false negatives will be eliminated.
+While a traditional classififcation learning machine learning approach can reduce both of these situations, generally, there is can be no garuntee that all false negatives will be eliminated.
 Instead of building classification models over the learning set (such as an SVM), we learn the largest set of rules that all correct configuration files satisfy.
@@
 The only case of a false negative can be when there was no evidece of such a rule in the learning set - we cannot generate rules from nothing.
-Framed as the question "Is this file valid", \app is complete but not sound.
+
+$\mathcal{L}$ = Learned Rules\\
+$\mathcal{C}$ = Correct Configuration File Learning Set\\
+$\mathcal{R}$ = Reported Rules\\
+$\mathcal{T}$ = True Rules\\
 
 That is, taking the following definitions:
-\begin{multline*}\\
-\text{\{Considered Rules\}} = \forall files \in \text{\{Learning Set\}}, \{ r | r(files) = True \land r \text{ is non-trivial}\}\\
-\text{\{Reported Rules\}} = {r | r(userfile)=False } \\
-\text{\{True Rules\}} = \{r | \text{ if } r(userfile)=False \text{ then system crash } \land \\
-   \exists file \in \text{\{Learning Set\}}, r(file) \text{ is non-trivial}\}
-\end{multline*}
+\begin{flalign*}
+\mathcal{T}& =\ \{ r\ \mid \\
+  & \forall file \in \mathcal{C},\ r(file)\  \land\\
+  & \exists file \in \mathcal{C},\ r(file) \text{ is non-trivial}\ \land \\
+  & \text{ if } \neg r(userfile) \text{ then system crash} \} \\
+\mathcal{L}& =\ \{ r\ \mid \\
+  & \forall file \in \mathcal{C},\ r(file)\  \land\\
+  & \exists file \in \mathcal{C},\ r(file) \text{ is non-trivial} \} \\
+\mathcal{R}& =\ \{ r\ \mid \\
+  & r \in \mathcal{L}\ \land\\
+  & \neg r(userfile) \}&\\
+\end{flalign*}
 
-We have the following specification of \app.
-\begin{multline*}\\
-\text{\{True Rules\}} \subseteq \text{\{Considered Rules\}} \\
-\forall r \in \text{\{True Rules\}}, if r(userfile)=False then \exists r \in \text{\{Reported Rules\}} \\
-\neg \forall r \in \text{\{Reported Rules\}}, r \in \text{\{True Rules\}} \\
-\end{multline*}
+We can then conclude that \app is complete but unsound.
+The key to showing that \app can be complete lies in proving $\mathcal{R}$ is indeed the set it claims to be.
+In order to do this, we must closely examine our implementation.
+\begin{flalign}
+& \forall r \in \mathcal{T}, r \in \mathcal{R} \qquad \text{[Complete]} \\
+& \exists r \in \mathcal{R}, r \notin \mathcal{T} \qquad \text{[Unsound]}
+\end{flalign}
 
-\section{Rules}
+The learned rule set, $\mathcal{L}$, is represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
+The three methods of this typeclass and the associated specification will help to show completeness of our system.
+The functions of this typeclass will be used, invisibly to the user, to make the overall system run.
+As long as the specifications for each function are met, \app can garuntee completness.
 
-A core design principle in \app is modularity, so that a user can easily exentend it to their verification needs.
-Rather than try to support every type of verification over configuration files, we provide a framework for defining new verfication properties.
-We call each verification property a rule, for example the correct ordering of keywords or integer relationships between values.
-These rules tend to be pairs of values with a relation.
-For instance, an integer relation rule might be that the value of "foo" must be greater than the value of "bar".
-It is also important that the rule has some empty value, to state that it is known there is no relation between the values.
-This will prevent \app from trying to relearn rules when they have already been refuted.
-
-These rules are represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
-The typeclass can support anything that is Foldable, which roughly the user can use any datastructure.
+The typeclass can support anything that is Foldable, which roughly means the user can use any datastructure they prefer.
 In fact, in our implementation, two rules are implemented with lists, and two others use hashmaps.
@@
 
-The functions of this typeclass will be used, invisibly to the user, to make the overall system run.
-As long as the specifications for each function are met, \app can garuntee completness.
+\section{Rules}
 
@@
 
-  $\text{learn } file =  \{ r | r(file) = True \land r \text{ is non-trivial}\}$
+  $\text{learn } file =  \{ r | r(file) \land r \text{ is non-trivial}\}$
 
@@
   This is generally implemented as a filter over the union of the two set, but may vary slightly.
-  The formal specification of this method is that:
-  \begin{multline*}
-  \text{merge } Set1 \: Set2= \{r \mid \\
-    r \in \text{Set1} \cup \text{Set2} \land \\
-    \exists file \forall r' \in \text{Set1} \cup \text{Set2}, r(file) = True \land r'(file) = True \} \\
-  \end{multline*}
+  The second predicate of formal specification states that the rule cannot conflict with other existing rules.
+  \begin{align*}
+  \text{merge }& Set1 \: Set2= \{r \mid \\
+    & r \in \text{Set1} \cup \text{Set2}\ \land \\
+    & \exists file\ \forall r' \in \text{Set1} \cup \text{Set2}, r(file) \land r'(file) \} \\
+  \end{align*}
 
@@
 
-\section{Implementation}
+% \section{Implementation}
+%
+% \subsection{System}
+% Since we learn a set of rules on each file in isolation from the other, we have an embarrassing parallel situation.
+% Haskell allows us to easily take advantage of by using the parallel mapping library, parmap, both for translation to the intermediate representation, and for learning the rules on each file.
+%
+% \begin{lstlisting}
+% learnRules :: [ConfigFile Language] -> RuleSet
+% learnRules fs = let
+%   fs' = parMap rseq convert fs
+%   rs = parMap rdeepseq findAllRules fs'
+%  in
+%   foldl1 mergeRules rs
+% \end{lstlisting}
+%
+% \subsection{Type Error Rules}
+% This builds a map between keywords and types, using the values as evidence.
+% see quantum.tex for more
+% i will write more on this tomorrow.
+%
+% \subsection{Integer Relation Rules}
+% we only consider the relations , (==), (<=), (>=) because they are easy to pass aroud (as actual functions) in haskell.
+% We also committed cardinal since and create an instance for equality over these functions.
+% instance Eq (Int->Int->Bool) where
+%
+% With more engineering effort, this could be extened with the use of a SMT solver to create more fine grained relational rules.
+% From our experience, more specific rule are not really needed for integer relations in configuration files.
+% However an SMT solver approach would be particularly useful for relations on strings, especially when considering substring relations between filepaths.
+%
+% \subsection{Ordering and Missing Entry Rules}
+% These are the simpiliest of all rules, just making a lot of pairs and seeing which pairs continue to appear over the learning set.
+% There is actually a bit of a catch in ordering though - we are not complete over ordering rules.
+% This is because only our implementation does not satisfy the specification for the merge function listed above.
+% The problem arises from the fact the configuration files may have non-unique keywords.
+% Therefor, in the follwoing file we will derive the valid, but conflicting rules ([client],port) and (port,[client]).
+% \begin{verbatim}
+% [client]
+% port = 3306
+% [mysqld]
+% port = 3306
+% \end{verbatim}
+% Our implementation of merge removes and conflicting rules for the running set.
+% By introducing a renaming pass in the initial parsing we may be able to solve this, but have not found a satisfactory solution yet.
 
-\subsection{System}
-Since we learn a set of rules on each file in isolation from the other, we have an embarrassing parallel situation.
-Haskell allows us to easily take advantage of by using the parallel mapping library, parmap, both for translation to the intermediate representation, and for learning the rules on each file.
-\xxx{merge can also be parallelized, but i haven't done it yet and might not get a chance}
-
-\begin{lstlisting}
-learnRules :: [ConfigFile Language] -> RuleSet
-learnRules fs = let
-  fs' = parMap rseq convert fs
-  rs = parMap rdeepseq findAllRules fs'
- in
-  foldl1 mergeRules rs
-\end{lstlisting}
-
-\subsection{Type Error Rules}
-This builds a map between keywords and types, using the values as evidence.
-see quantum.tex for more
-i will write more on this tomorrow.
-
-\subsection{Integer Relation Rules}
-we only consider the relations , (==), (<=), (>=) because they are easy to pass aroud (as actual functions) in haskell.
-We also committed cardinal since and create an instance for equality over these functions.
-instance Eq (Int->Int->Bool) where
-
-With more engineering effort, this could be extened with the use of a SMT solver to create more fine grained relational rules.
-From our experience, more specific rule are not really needed for integer relations in configuration files.
-However an SMT solver approach would be particularly useful for relations on strings, especially when considering substring relations between filepaths.
-
-\subsection{Ordering and Missing Entry Rules}
-These are the simpiliest of all rules, just making a lot of pairs and seeing which pairs continue to appear over the learning set.
-
-There is actually a bit of a catch in ordering though - we are not complete over ordering rules.
-This is because only our implementation does not satisfy the specification for the merge function listed above.
-The problem arises from the fact the configuration files may have non-unique keywords.
-Therefor, in the follwoing file we will derive the valid, but conflicting rules ([client],port) and (port,[client]).
-\begin{verbatim}
-[client]
-port = 3306
-[mysqld]
-port = 3306
-\end{verbatim}
-Our implementation of merge removes and conflicting rules for the running set.
-By introducing a renaming pass in the initial parsing we may be able to solve this, but have not found a satisfactory solution yet.
+% A core design principle in \app is modularity, so that a user can easily exentend it to their verification needs.
+% Rather than try to support every type of verification over configuration files, we provide a framework for defining new verfication properties.
+% We call each verification property a rule, for example the correct ordering of keywords or integer relationships between values.
+% These rules tend to be pairs of values with a relation.
+% For instance, an integer relation rule might be that the value of "foo" must be greater than the value of "bar".
+% It is also important that the rule has some empty value, to state that it is known there is no relation between the values.
+% This will prevent \app from trying to relearn rules when they have already been refuted.

### 2016-02-11 ProbabalisticTypes/quantum.tex
started a space for quantum types

\section{Quantum Types}

Because our type inference is based on machine learning, we cannot be sure that a keyword unambigously has a single type.
This is an issue when we try to learn relational rules between keywords.
Take the following file in the learning

foo = 300
bar = 300.txt

We want to learn the rule that $foo \in {substring(bar)}$, however using unambigous type inference, we would assign foo type int, and never try to generate a string relation rule for these two keywords.
By assigning foo a quantum type (e.g. ${Int <90\%>, String <10\%>}$), we can now generate rules for both types.

At runtime, when the user wants to check a file we update the probabilities one last time then 'collapse' the quantum type to a concrete type.
If the concrete type collapses to a Int, we consider the rules for ints, and vice versa.

This idea is closely related to exstentially quantified types.

Here is what we know:
- When parsing unstructured (plaintext) data, we may not be given, or able to fully determine, the type of a value.
- We can guess types based on regular expressions over a value.*
- Guessing a concrete type can be overly restrictive. In ConfigC is prematurely pruning the rule search.
- By guessing a set of types with probabilities, we can continously update the distribution, and decide on a concrete type later when we have more information.

Here are things we need to know:
- In ConfigC, we are building probabilistic types, but only operate (i.e. build rules) over the component, concrete types. Can we also operate over probabilistic types and maintain type safety? Fundamentally, we ask "What do we need to add to the simply typed lambda calculus to express probabilistic types?"
- How is this related to existentially quantified types (another "heterogeneous collection" type). Can/should we use this for an implementation?
- How is this related to a value-level probabilistic lambda calculus (where probabilities are on value).
- Does this type system need to be tied to the specific machine learning techniques used in infering types?
- Can we do inference based on more interesting things than just regular expression (something a bit like **, maybe which types generate better rules)
- We might also ask, is there any good reason to operate over probabilistic types? What are other situations when we might need/encounter probabilistic types?

*This focuses mostly on using regular expression to infer concrete types. http://people.csail.mit.edu/rishabh/papers/popl16-semantic.pdf
** http://conf.researchr.org/event/POPL-2016/popl-2016-papers-estimating-types-in-binaries-using-predictive-modeling

### 2016-02-11 ICFP/formalism.tex
make which will change

@@
 
+For probablistic learing
+$\mathcal{C'}$ = Incorrect Configuration File Learning Set\\
+
 That is, taking the following definitions:
@@
 \mathcal{T}& =\ \{ r\ \mid \\
-  & \forall file \in \mathcal{C},\ r(file)\  \land\\
+  & \forall file \in \mathcal{C},\ r(file)\ *  \land\\
   & \exists file \in \mathcal{C},\ r(file) \text{ is non-trivial}\ \land \\
@@
   \begin{align*}
-  \text{merge }& Set1 \: Set2= \{r \mid \\
+  \text{merge* }& Set1 \: Set2= \{r \mid \\
     & r \in \text{Set1} \cup \text{Set2}\ \land \\

### 2016-02-27 ICFP/formalism.tex
start formlism of probablistic

--- 2016-02-11 ICFP/formalism.tex
@@
 In the context of configuration file verification,
-  a false positive is when \app reports an error on a valid confiuration file and
-  a false negative is when \app fails to reports an error on an invalid confiuration file.
+  a false positive is when \app reports an error on a valid configuration file and
+  a false negative is when \app fails to reports an error on an invalid configuration file.
 Too many false positives will cause users to ignore the reported error\cite{}.
-However, since the cost of system failure is so high from a misconfiguration, \app propritzes the minimization of false negatives.
+However, since the cost of system failure is so high from a misconfiguration, \app prioritizes the minimization of false negatives.
 
-While a traditional classififcation learning machine learning approach can reduce both of these situations, generally, there is can be no garuntee that all false negatives will be eliminated.
+While a traditional classification learning machine learning approach can reduce both of these situations, generally, there is can be no guarantee that all false negatives will be eliminated.
 Instead of building classification models over the learning set (such as an SVM), we learn the largest set of rules that all correct configuration files satisfy.
-In this way, \app can garuntee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set.
-The only case of a false negative can be when there was no evidece of such a rule in the learning set - we cannot generate rules from nothing.
+In this way, \app can guarantee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set.
+The only case of a false negative can be when there was no evidence of such a rule in the learning set - we cannot generate rules from nothing.
 
+$\mathcal{C}$ = Correct Configuration File Learning Set\\
 $\mathcal{L}$ = Learned Rules\\
-$\mathcal{C}$ = Correct Configuration File Learning Set\\
 $\mathcal{R}$ = Reported Rules\\
@@
 
+\section{Incorrect Learning Set}
+We have a database of incorrect configuration files.
+Rather than manually correct each file, we observe that the files are usually incorrect in only one or two lines.
+We then extend the previous formalism to handle probabilistic learning, when we have a collection of such files.
+
+$\mathcal{CP}$ = Incorrect Configuration File Learning Set\\
+$\mathcal{LP}$ = Probabilistically Learned Rules\\
+$\mathcal{RP}$ = Probabilistically Reported Rules\\
+
+\begin{flalign*}
+\mathcal{LP}& =\ \{ r\ \mid \\
+  & \Pi file \in \mathcal{CP},\ r(file)\  \land\\
+  & \exists file \in \mathcal{CP},\ r(file) \text{ is non-trivial} \} \\
+\mathcal{RP}& =\ \{ r\ \mid \\
+  & r \in \mathcal{LP}\ \land\\
+  & \neg r(userfile) \}&\\
+\end{flalign*}
+
+Where $\Pi$ indicates some percentage of the files in CP.
+In this case, we can no longer conclude that \app is complete.
+
+\begin{flalign}
+& \forall r \in \mathcal{T}, r \in \mathcal{RP} \qquad \text{[Incomplete]} \\
+& \exists r \in \mathcal{RP}, r \notin \mathcal{T} \qquad \text{[Unsound]}
+\end{flalign}
+
+\section{Implementation}
+
 The learned rule set, $\mathcal{L}$, is represented as a type, where the type must support a particular interface (called a typeclass in Haskell) to be compatible with our system.
@@
 The functions of this typeclass will be used, invisibly to the user, to make the overall system run.
-As long as the specifications for each function are met, \app can garuntee completness.
+As long as the specifications for each function are met, \app can guarantee completeness.
 
@@
   For a single given file in the intermediate representation format, learn the full set of rules on that file.
-  By overfitting to each file, we can eventually garuntee the completness of \app.
+  By overfitting to each file, we can eventually guarantee the completeness of \app.
   The specification of this function is the obvious reduction of the Considered Set definition.
@@
 \subsection{check}
-  To check a file by using a rule set, we simply take all the rules that are releveant to the user's file.
-  Rules that are relavent are the ones where both parts of the ordering are present.
+  To check a file by using a rule set, we simply take all the rules that are relevant to the user's file.
+  Rules that are relevant are the ones where both parts of the ordering are present.
   We learn the rule set for the user file, and every rule in the learned set must be present in the user file.

### 2016-05-01 OSDI/arch.tex
config: for osdi16

--- 2016-01-29 intro1.tex
@@
-\section{Introduction and System Overview}
-\label{sec:Intro}
+\section{\app Overview}
 
-Configuration errors are one of the most important root-causes of
-modern software system failures~\cite{xu15systems,yin11anempirical}.
-In practice, misconfiguration problems may result in security
-vulnerabilities, application crashes, severe disruptions in software
-functionality, and incorrect program executions%
-~\cite{xu15systems,zhang14encore,yuan11context}.  Although several
-tools have been proposed to automate configuration error diagnosis
-after failures occur~\cite{wang04automatic,attariyan10automating,
-su07autobash,whitaker04configuration}, these tools rely on a manual approach
-  to understand and detect the failure symptoms. The main reasons for this are:
-  1) entries in configuration files are untyped assignments, 2) there
-  is no explicit structure policy for the entries in configuration
-  files, and 3) there are surprisingly few rules specifying the
-  entries' constraints.
-
-We propose an approach to the verification of  
-configuration files which is based on learning rules about the language 
-model for configuration files.
-
-\begin{figure}[t] \centering
-\includegraphics[width=0.65\textwidth]{figs/overview}
+\begin{figure*}[tbp] \centering
+\includegraphics[width=0.68\textwidth]{figs/overview}
 \caption{{\footnotesize \app's workflow. The green boxes represent configuration files,
@@
 \label{fig-overview}
-\end{figure}
+\end{figure*}
 
@@
 with the assumption that we are given a number of correct configuration
-files belonging to the same category (for instance, MySQL or
-Apache). Such files follow similar patterns, which we exploit
+files belonging to the same category, such as MySQL or Apache. 
+Such files follow similar patterns, which we exploit
 in a learning algorithm to build rules that
@@
 intermediary representation.
-When running type inference on a configuration file, the type of a variable cannot always be fully determined from a single value.
-We address this problem by introducing so called {\emph{probabalistic types}}.
+When running type inference on a configuration file, 
+the type of a variable cannot always be fully determined from 
+a single value.
+We address this problem 
+by introducing so called {\emph{probabilistic types}}.
 Rather than giving a variable a single type, we assign several types with their probability distributions. 
@@
 
-From a practical perspective \app introduces no additional burden 
-to the users: they can simply use \app to check for errors in their configuration files.
-However, they can also easily extend the framework themselves.
-The system is designed to be highly modular.
-If there is a class of rules that \app is not currently learning, the user can develop their own templates and learners for that class.
-The new learner can be added to \app and this way it can check additionally a new set of errors.
+\com{
+A rule R is added to the set of all rules,
+  if $\exists$ learning file f s.t. R(f) is non vacuously true
+That rule R is then removed from the set of all rules,
+  if $\exists$ learning file f st R(f) is false.
 
-Finally, from a systems perspective this is the first approach that {\emph{proactively}} checks 
- the correctness of configuration files. All previous work
-~\cite{xu15systems,zhang14encore,yuan11context, wang04automatic,attariyan10automating,
-su07autobash,whitaker04configuration} tries to identify the problem after the
-failure occured.
-Our approach isolates potential errors before the system failure occurs, e.g.
-before the installation.
-We can also see \app as a tool that can run in conjunction with existing tools.
-Pre-analyzed configuration files are already free from language-based errors, and this way the workloads of post-failure forensics at the runtime
-is significantly reduced, thus making these tools truly practical.
+This is accomplished in two passes.
+First we collect all possible rules for every file.
+Then we merge the all the rules to create our final set.
+This conviently gives rise to an embarresingly parallel situation, which Haskell allows us to easily take advantage of by
+  using the parallel mapping library parmap.
 
-To summarize, this tool papers makes the following contributions:
+\begin{lstlisting}
+  potentialRules = parmap findAllRules learningSet.
+  finalRules = foldl1 mergeRules potenialRules
+\begin{lstlisting}
 
-\begin{enumerate}
+Each rule is of the Attribute typeclass, which means a rule must support the following operations:
+\begin{lstlisting}
+class Attribute r where
+  learn :: ConfigFile Common -> [r]
+  merge :: [r] -> [r] -> [r] 
+  check :: [r] -> ConfigFile Common -> Error
+\end{lstlisting}
 
-  \item We designed and implemented a tool, \app, that can learn a language model from an example set of correct configuration files, and we use the model to verify new files.
-  \item We use probabilistic types to assign a confidence distribution over a set of types to a value.
-  \item In \app we define a interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.
-
-\end{enumerate}
+}

### 2016-05-01 OSDI/check.tex
config: for osdi16

\section{Checker}

\ennan{Here, we need to describe how we check whether 
the target configuration file meets learned rules using SMT solver.}

### 2016-05-01 OSDI/concl.tex
config: for osdi16

--- 2016-01-29 related.tex
@@
-\section{Conclusions}
+\section{Conclusion}
 
-In this paper, we introduce \app, a highly-modular framework that allows verification of configuration files, even without a language model of the file.
-New verification properties require only a small amount of code and are not language specific, all indicating that \app could be widely adopted by system administrators.
-Such a verification tool that scales in both performance and expressivity can revolutionize configuration file checking, reducing the cost of system maintaince and failure dramatically.
+In this paper, we introduce \app, a highly-modular framework 
+that allows verification of configuration files, 
+even without a language model of the file.
+New verification properties require only a small amount of code 
+and are not language specific, 
+all indicating that \app could be widely adopted by system administrators.
+Such a verification tool that scales in both performance and expressivity 
+can revolutionize configuration file checking, 
+reducing the cost of system maintenance and failure dramatically.

### 2016-05-01 OSDI/eval.tex
config: for osdi16

\section{Implementation and Evaluations}

\ennan{Here, we describe the implementation and evaluations}

### 2016-05-01 OSDI/evaluation.tex
config: for osdi16

--- 2016-01-29 evaluation.tex
@@
 Since we learn a set of rules on each file in isolation from the other, we have a pleasingly parallel situation.
-Haskell allows us to easily take advantage of this by using the parallel mapping library \cite{}, both for translation to the intermediate representation, and for learning the rules on each file.
+Haskell allows us to easily take advantage of this by using the parallel
+mapping library \cite{parallel}, both for translation to the intermediate representation, and for learning the rules on each file.
 The merge stage could also easily be parallelized, using a divide and conquer approach, but \app runs fast enough over our learning set (28 files, 961 lines of code) that this has not been necessary.

### 2016-05-01 OSDI/intro.tex
config: for osdi16

--- 2016-01-29 intro1.tex
@@
-\section{Introduction and System Overview}
-\label{sec:Intro}
+\section{Introduction}
+\label{sec-intro}
 
@@
 model for configuration files.
-
-\begin{figure}[t] \centering
-\includegraphics[width=0.63\textwidth]{figs/overview}
-\caption{{\footnotesize \app's workflow. The green boxes represent configuration files,
-  including both correct general configuration files and users' input
-  configuration files. The purple boxes are the components within \app.
-  The yellow boxes are results generated by \app's components.}}
-\label{fig-overview}
-\end{figure}
 
@@
 
-To summarize, this tool papers makes the following contributions:
+To summarize, this tool paper makes the following contributions:
 

### 2016-05-01 OSDI/learner.tex
config: for osdi16

\section{Learner}

\ennan{This section details how we extract rules from the
intermediate representations. This section should include: 
1) our learning algorithm, 2) how to customize templates,
3) how to input environmental templates, and 4) other methods
for learning rules.}

### 2016-05-01 OSDI/limit.tex
config: for osdi16

\section{Discussion and Limitations}

\ennan{Of course, our tool has many limitations. For example, we cannot
detect the misconfiguration correlation across multiple individual
systems unwilling to share configuration information with each other.}

### 2016-05-01 OSDI/main.tex
config: for osdi16

\documentclass[letterpaper,twocolumn,10pt]{article}

\usepackage{times}            % standard fixed width font
\usepackage{usenix}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{footnote}
\usepackage{cite}
\usepackage{amsfonts}
\usepackage{subfig}
%\usepackage{natbib}
\usepackage{balance}
\usepackage{hhline}
%\usepackage{multirow}
\usepackage{setspace} 
\usepackage{epsfig}
\usepackage[hyphens]{url}
\usepackage[colorlinks,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage[hyphenbreaks]{breakurl}
\usepackage{booktabs}
%\usepackage[compact]{titlesec}
\usepackage{xcolor}
%\usepackage[algoruled,vlined,ruled,linesnumbered]{algorithm2e}
\usepackage{lipsum}
%\usepackage{courier}
\usepackage{listings}
\lstset{
  language=C,
	basicstyle=\footnotesize\ttfamily,breaklines=true
}

%\usepackage[T1]{fontenc}
%\usepackage[scaled=0.78]{DejaVuSansMono}

\clubpenalty=10000      % penalty for creating a club line at end of line.
\widowpenalty=10000     % penalty for creating a widow line at top of page.

% Select one or other if want to see comments.
% \com is sometimes displayed during draft.
\long\def\com#1{}
%\long\def\com#1{{\bf \sc comment: }{\small [#1]}{\bf \sc\ endcomment}\newline}

\long\def\ennan#1{{\color{blue}{\bf Ennan: }{\small [#1]}}}
\long\def\ruzica#1{{\color{red}{\bf Ruzica: }{\small [#1]}}}
%\long\def\xxx#1{}

% Use this macro to force page breaks where ugly widows/orphans occur;
% be sure to recheck all uses after any significant change to the text!
\def\widowpage{\pagebreak}

% Choose abbreviated or long-version alternatives in paper
%\long\def\abbr#1#2{#1}			% abbreviated version
\long\def\abbr#1#2{#2}			% long version

% Choose abbreviations or long names/titles in bibliography
%\def\bibbrev#1#2{#1}			% short version
%\def\bibbrev#1#2{#2}			% long version
\def\bibbrev#1#2{\abbr{#1}{#2}}		% follow abbr macro

% Abbreviated or full citation lists: \abcite{basic}{others}
\newcommand{\abcite}[2]{\abbr{\cite{#1}}{\cite{#1,#2}}}

% Conference abbreviations: \bibconf[Nth]{SOSP}{Symposium on ...}
\newcommand{\bibconf}[3][]{#1 \bibbrev{#2}{#3 (#2)}}

\newcommand{\ie}{{\em i.e.\xspace}}
\newcommand{\eg}{{\em e.g.\xspace}}

% system related terms
\newcommand{\app}{ConfigC\xspace}

% Fault graph terms

\newcommand{\para}[1]{\smallskip\noindent {\bf #1}}

\begin{document}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

% Uncomment one of the following two, if you are not going for the 
% traditional copyright transfer agreement.

%\exclusivelicense                % ACM gets exclusive license to publish, 
                                  % you retain copyright

%\permissiontopublish             % ACM gets nonexclusive license to publish
                                  % (paid open-access papers, 
                                  % short abstracts)

%\titlebanner{banner above paper title}        % These are ignored unless
%\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Probabilistic Automated Language Learning for Configuration Files}

\author{~}

\maketitle
%\vspace{-50pt}

\input{abs}

\input{intro}
\input{motiv}
%\input{system}
\input{arch}
\input{trans}
\input{learner}
\input{check}
\input{limit}
\input{eval}
\input{rel}
\input{concl}

%\newpage

\bibliographystyle{plain}
\bibliography{os}

\end{document}

### 2016-05-01 OSDI/motiv.tex
config: for osdi16

--- 2016-01-29 motiv1.tex
@@
 When writing configuration files, users usually take already existing
-files and modifies the files, with little knowledge of the system. 
+files and modify the files, with little knowledge of the system. 
 The non-expert user can then easily introduce in errors.
@@
 
-\para{Example~1: Ordering Errors.} When configuring PHP to run with the
+\para{Example~1: Ordering errors.} 
+When configuring PHP to run with the
 Apache HTTP Server, the user writes, among others, the following lines:\\
@@
 
-\para{Example~2: Entry Missing Errors.} If the user wants to use OpenLDAP to enable her directory access
+\para{Example~2: Entry missing errors.} 
+If the user wants to use OpenLDAP to enable her directory access
 protocol, she needs to use the password policy overlay. This is usually
@@
 
-\para{Example~3: Type Errors.} If the user tries to install MySQL, she first needs to initiate the path for the log information generated by MySQL. 
+\para{Example~3: Type errors.} 
+If the user tries to install MySQL, she first needs to initiate the path for the log information generated by MySQL. 
 A user may put the following code in the MySQL configuration file:\\
@@
 
-\vspace{-0.25cm}
-\para{Example~4: Value Correlation Errors.} When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\
+\para{Example~4: Value correlation errors.} 
+When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\
 \texttt{

### 2016-05-01 OSDI/rel.tex
config: for osdi16

\section{Related Work}

Providing language support has been considered as a promising means
of tackling configuration problems~\cite{xu15systems}.
Nevertheless, practical language-based misconfiguration
detection approach still remains an open problem.

\para{Configuration languages.}
There have been several language-support efforts proposed to prevent
configuration errors introduced by fundamental deficiencies in
either untyped or low-level languages. For example, in network
configuration management area, it is easy for administrators to
produce configuration errors in their routing configuration files.
PRESTO~\cite{} automates the generation of device-native configurations
with configlets in a template language. 
Loo {\em et al.}~\cite{} adopt Datalog to reason about 
routing protocols in a declarative fashion. COOLAID~\cite{} constructs
a language to describe domain knowledge about network devices and
services to convenient network reasoning and management.

Compared with these existing efforts, 
our work mainly focused on software systems, \eg, MySQL and Apache,
rather than network configurations. In addition, we do not need 
the user of \app to manually write a configuration file with the proposed
language, since \app can automatically parse a target configuration
file into our proposed representation.

\para{Misconfiguration detection.}
Misconfiguration detection techniques aim at checking the configuration
efforts before the system outages occur.
Most of existing detection approaches check 
the configuration files against a set of predefined correctness 
rules, named constraints, and then report the errors if 
the checked configuration files do not satisfy these rules.

Huang {\em et al.}~\cite{huang15confvalley} proposed a specification 
language, ConfValley, to validate 
whether given configuration files meet administrators' 
``belief'' in mind. Different from \app, ConfValley itself does not
have inherent misconfiguration checking capability, since it only offers
a language representation. In addition, administrators have to
manually write specifications with ConfValley, which is an error-prone
process; on the contrary, \app does not need users to manually
write anything.

Several machine learning-based misconfiguration detection efforts 
also have been proposed~\cite{yuan11context, zhang14encore}.
Specifically, EnCore~\cite{zhang14encore} introduces a template-based
learning approach to improve the accuracy of their learning results.
The learning process is guided by a set of predefined rule templates
that enforce learning to focus on patterns of interests.
By this way, EnCore filters out irrelevant information and reduces
the false positives; moreover, the templates are able to express
system environment information that state-of-the-art machine learning
techniques cannot handle.
Compared with EnCore, which focuses on a specific type of
misconfiguration, \app is capable of tackling more general configuration
errors.

\para{Misconfiguration diagnosis.}
Many misconfiguration diagnosis approaches have been proposed~\cite{}.
For example, ConfAid~\cite{} and X-ray~\cite{} use dynamic information
flow tracking to find possible configuration errors that may result in
failures or performance problems. AutoBash~\cite{} speculatively
executes processes and tracks causality to automatically fix 
misconfigurations. Different from \app, most of misconfiguration
diagnosis efforts aim at finding out errors after the system
failures occur, which typically lead to prolonged recover time.

\para{Misconfiguration tolerance.}
There have been several efforts proposed to test whether systems are 
tolerant to misconfigurations~\cite{xu13do}. 
ConfErr~\cite{} uses a human error hodel from psychology and
linguistics to inject misconfigurations into systems.
SPEX~\cite{xu13do} takes a white-box testing approach to automatically
extract configuration parameter constraints from source code and generates 
misconfigurations to test whether systems can tolerate the potential
configuration errors.

Making systems gracefully handle misconfigurations and eliminating
configuration errors are two orthogonal directions.
The former helps improve the robustness of systems and make 
diagnosis easier. This is especially important for 
software that will be widely distributed to end users.
Our work belongs to the latter case, which is used to 
prevent configuration errors before the system failures occur.

### 2016-05-01 OSDI/trans.tex
config: for osdi16

\section{Translator}

\ennan{Translator is, in some sense, like a parser. 
This section is used to detail how we design the parser.
We need to include: 1) probabilistic type, 2) language model
and 3) parser design.}

### 2016-05-01 OSDI/limit.tex
config: related work and limitation sec

@@
 systems unwilling to share configuration information with each other.}
+
+This section discusses a few \app's limitations
+and possible solutions.
+
+\para{Legal misconfigurations.}
+While \app can check diverse configuration errors without
+human participations, all the misconfiguration detection techniques,
+including \app, cannot handle some types of configuration errors
+resulting from events occurred during system runtime.
+Such configuration errors are referred to as {\em legal misconfigurations}%
+~\cite{yin11anempirical}. As shown in Yin {\em et al.}%
+~\cite{yin11anempirical}, many parameter misconfigurations have 
+perfectly legal parameters but do not deliver the functionality intended
+by users. These cases are more difficult to detect by
+automatic checkers and may require more user training or
+better configuration design.
+A potential solution is to combine existing misconfiguration diagnosis
+tools, \eg, X-ray~\cite{}, with \app in order to enhance the 
+misconfiguration checking capability.
+
+\para{}

### 2016-05-01 OSDI/rel.tex
config: related work and limitation sec

@@
 techniques cannot handle.
-Compared with EnCore, which focuses on a specific type of
-misconfiguration, \app is capable of tackling more general configuration
-errors.
+Compared with EnCore, \app has the following advantages.
+First, \app does not rely on whether the files in given configuration set 
+are 100\% correct. Second, \app can cover much more types of 
+misconfigurations, since \app introduces probabilistic type checking
+mechanism. Finally, \app is a language framework, which could 
+even be used to write configuration files, but EnCore is only a 
+misconfiguration detection tool.
 

### 2016-05-01 CAV/evaluation.tex
config: cav paper fixed some typo

--- 2016-05-01 OSDI/evaluation.tex
@@
 
-To evaluate our tool, we take a subset of 20 benchmarks from an existsing dataset of configuration errors~\cite{yin11anempirical, configdataset} which are supported by our tool.
-Table~\ref{table:res} contains an evaluation summary.
+To evaluate our tool, we take a subset of 20 benchmarks from an
+existing dataset of configuration errors~\cite{yin11anempirical,xu15hey,configdataset} which are supported by our tool. Table~\ref{table:res} contains an evaluation summary.
 We do not report the running times, since they are negligible: even when
- running in the interpreter mode, files are analyzed instantaneously. We spent approximately 30 second on learning the rules. When we run the compiled version, we need for lerning and verification 
+ running in the interpreter mode, files are analyzed instantaneously. We
+spent approximately 30 second on learning the rules. When we run the
+compiled version, we need for learning and verification 
 combined less than 5 seconds. Our focus is usefulness of the tool: its 
@@
 
-All but one false positive reports were integer relations. They are the result of overfitting on rules.
+All but one false positive reports were integer relations. They are the
+result of overfitting on rules.
 \app can learn overapproximating rules when the learning set does not show the full spectrum of possible values.

### 2016-05-01 CAV/intro1.tex
config: cav paper fixed some typo

--- 2016-01-29 intro1.tex
@@
 functionality, and incorrect program executions%
-~\cite{xu15systems,zhang14encore,yuan11context}.  Although several
+~\cite{xu15systems,xu13do,zhang14encore,yuan11context}.  Although several
 tools have been proposed to automate configuration error diagnosis
@@
 
-Finally, from a systems perspective this is the first approach that {\emph{proactively}} checks 
+Finally, from a systems perspective this is the first approach 
+that {\emph{proactively}} checks 
  the correctness of configuration files. All previous work
@@
 su07autobash,whitaker04configuration} tries to identify the problem after the
-failure occured.
+failure occurred.
 Our approach isolates potential errors before the system failure occurs, e.g.

### 2016-05-01 CAV/motiv1.tex
make a new dir for icfp
config: cav paper fixed some typo

--- 2016-01-29 motiv1.tex
@@
 Below we show some real worlds examples of the errors commonly found in configuration files.
-All these examples are extracted from real-world reports % ~\cite{yin11anempirical, configdataset}.
+All these examples are extracted from real-world reports%
+~\cite{yin11anempirical,xu15hey}.
 The deep, domain specific knowledge needed to identify these error manually is strong motivation for a tool such as \app.
@@
 
-\vspace{-0.25cm}
+\vspace{-10pt}
 \para{Example~4: Value Correlation Errors.} When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\

### 2016-05-02 OSDI/abs.tex
config: for osdi16
config: abs

--- 2016-01-25 abs.tex
@@
-\begin{abstract}
+\section*{Abstract}
 
-Software failures resulting from configuration errors 
-have been commonplaces as modern software systems 
-become increasingly larger and more complex.
-The lack of language constructs in configuration files, 
-such as types and grammars, 
-directed the focus of a configuration file verification 
-towards building post-failure error diagnosis tools. 
-In addition, the existing tools are generally language
-specific, requiring the user to define at least a grammar for the language
-models and explicit rules to check. 
-In this paper, we propose a framework which analyzes
-datasets of correct configuration files and derives rules for building a
-language model for the given dataset. 
-The resulting language model can be used
+System failures resulting from configuration errors 
+have become the major factors affecting the availability and
+reliability of today's software systems.
+While many misconfiguration handling techniques,
+\eg, misconfiguration checking and troubleshooting, have been proposed, 
+offering automatic verification to configuration files -- like
+what we did to regular programs -- is still an open problem.
+The main reason is software configuration files are poorly structured 
+and typed, thus obstructing any possible language-based verification. 
+This paper presents, \app, the first automatic verification framework for
+software configurations.
+In order to verify a configuration file,
+\app first analyzes a given dataset sample of configuration files, 
+and then derives rules for building a language model from 
+the given configuration dataset. 
+Finally, the resulting language model can be used
 to verify new configuration files and detect errors in them.
-Our proposed framework is highly modular, 
+At the heart of \app lies a novel learning engine, 
+which employs a probabilistic type inference strategy and
+defines an intermediate representation for the rule type.
+Using this engine, \app learns various type rules (\eg, orderings,
+value relations, type errors, and user defined rules)
+to verify configuration files of interest.
+\app framework is highly modular, 
 does not rely on the system source code, and
 can be applied to any new configuration file type with minimal user input.  
-Our tool, named \app, relies on an abstract representation of language 
-rules to allow for this modularity. 
-\app supports learning of various rules, such as orderings,
-value relations, and type errors, 
-by defining a minimal interface for a rule, and by using a probabilistic types inference stategy.
-
-\end{abstract}
+%Our tool, named \app, relies on an abstract representation of language 
+%rules to allow for this modularity. 
+\ennan{One or two sentences here describe the most important
+experimental results.}

### 2016-05-02 OSDI/intro.tex
config: abs

@@
 
-Figure~\ref{fig-overview} describes an overview of our system. We start
-with the assumption that we are given a number of correct configuration
-files belonging to the same category (for instance, MySQL or
-Apache). Such files follow similar patterns, which we exploit
-in a learning algorithm to build rules that
-describe a language model for the files. Since the
-``language'' of configuration types is untyped and unstructured, we
-first parse the files and translate them into a more structured,
-intermediary representation.
-When running type inference on a configuration file, the type of a variable cannot always be fully determined from a single value.
-We address this problem by introducing so called {\emph{probabalistic types}}.
-Rather than giving a variable a single type, we assign several types with their probability distributions. 
+Building a practical framework for checking the type-safety of
+configuration files, nevertheless, requires addressing several
+challenges. First, given the fact that 
+different systems' configuration files use various representations, 
+the cost of introducing a completely new configuration
+language (or representation) to instead of all these existing format looks 
+like an impractical goal. This is not only because administrators need 
+to learn this new language, but also changes existing system
+infrastructure to support such a new language. 
+In order to avoid the above issues, we propose a representation,
+which is a type-based representation and 
+much more structured than existing configuration format, 
+but use it as an intermediate layer. We, at the same time,
+develop many pluggable parsers
+that can transform different systems' configuration representations
+into our proposed intermediate representation for the post process.
+
+Second, when running type inference on any given configuration file, 
+the type of a variable cannot always be fully determined from a single 
+value. For example, an entry {\tt foo = MAX\_SIZE} is most likely
+an integer rather than string. We address this problem by introducing 
+so called {\emph{probabilistic types}}.
+Rather than assigning only one variable to a single type, 
+we assign several types with their probability distributions. 
+The entry in the above example should be assigned 
+a probabilistic type like 
+{\tt \{foo, MAX\_SIZE, [(Int, 90\%), (String, 10\%)]\}}.
+\ennan{I am not quite sure probabilistic types are obviously
+better than deterministic types.}
+
 We can then use these more structured files

### 2016-05-02 OSDI/rel.tex
config: abs

@@
 also have been proposed~\cite{yuan11context, zhang14encore}.
-Specifically, EnCore~\cite{zhang14encore} introduces a template-based
+EnCore~\cite{zhang14encore} is the most close work to \app.
+It introduces a template-based
 learning approach to improve the accuracy of their learning results.
@@
 the false positives; moreover, the templates are able to express
-system environment information that state-of-the-art machine learning
+system environment information that other machine learning
 techniques cannot handle.
@@
 First, \app does not rely on whether the files in given configuration set 
-are 100\% correct. Second, \app can cover much more types of 
-misconfigurations, since \app introduces probabilistic type checking
-mechanism. Finally, \app is a language framework, which could 
+are 100\% correct. Second, \app not only can cover much more types of 
+misconfigurations, but also introduces probabilistic type.
+Finally, \app is a language framework, which could 
 even be used to write configuration files, but EnCore is only a 

### 2016-05-02 OSDI/abs.tex
config: new abs

@@
 System failures resulting from configuration errors 
-have become the major factors affecting the availability and
+have become the major causes affecting the availability and
 reliability of today's software systems.
 While many misconfiguration handling techniques,
-\eg, misconfiguration checking and troubleshooting, have been proposed, 
-offering automatic verification to configuration files -- like
+\eg, misconfiguration checking, troubleshooting and repair, 
+have been proposed, 
+offering automatic verification for configuration files -- like
 what we did to regular programs -- is still an open problem.
-The main reason is software configuration files are poorly structured 
-and typed, thus obstructing any possible language-based verification. 
+This is because 1) software configurations are typically written in
+poorly structured and untyped representations, and 2) 
+writing specifications or constraints for configuration 
+verification is non-trivial.
 This paper presents, \app, the first automatic verification framework for
 software configurations.
-In order to verify a configuration file,
-\app first analyzes a given dataset sample of configuration files, 
-and then derives rules for building a language model from 
-the given configuration dataset. 
+For a given configuration file,
+\app first analyzes a dataset sample of configuration files,
+thus generating a well-structured and probabilistically-typed 
+intermediate representations.
+Then, \app derives rules and constraints by analyzing
+the intermediate representations.
+The above two steps have formulated a language model.
 Finally, the resulting language model can be used
-to verify new configuration files and detect errors in them.
-At the heart of \app lies a novel learning engine, 
-which employs a probabilistic type inference strategy and
-defines an intermediate representation for the rule type.
-Using this engine, \app learns various type rules (\eg, orderings,
-value relations, type errors, and user defined rules)
-to verify configuration files of interest.
-\app framework is highly modular, 
+to verify the given configuration file and capable of 
+detecting various tricky errors,
+including orderings, value correlation, type errors, and entry missing.
+%At the heart of \app lies a novel learning engine, 
+%which employs a probabilistic type inference strategy and
+%defines an intermediate representation for the rule type.
+%With this engine, \app learns various type rules (\eg, orderings,
+%value relations, type errors, and user defined rules)
+%to verify configuration files of interest.
+Our \app framework is highly modular, 
 does not rely on the system source code, and
@@
 \ennan{One or two sentences here describe the most important
-experimental results.}
+experimental results. For example, we verify real-world misconfiguration 
+files and find 95\% errors are detected.}

### 2016-05-02 OSDI/intro.tex
config: new abs

@@
 
-Configuration errors are one of the most important root-causes of
-modern software system failures~\cite{xu15systems,yin11anempirical}.
-In practice, misconfiguration problems may result in security
+Configuration errors are one of the most important root causes of
+today's software system failures~\cite{xu15systems, yin11anempirical}.
+In practice, misconfiguration problems may lead to security
 vulnerabilities, application crashes, severe disruptions in software
 functionality, and incorrect program executions%
-~\cite{xu15systems,zhang14encore,yuan11context}.  Although several
-tools have been proposed to automate configuration error diagnosis
-after failures occur~\cite{wang04automatic,attariyan10automating,
-su07autobash,whitaker04configuration}, these tools rely on a manual approach
-  to understand and detect the failure symptoms. The main reasons for this are:
+~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.  
+Although many efforts tackling misconfigurations have been proposed 
+to check, troubleshoot, diagnose and repair configuration errors%
+~\cite{wang04automatic, attariyan10automating,
+su07autobash, whitaker04configuration}, these efforts rely on a manual 
+approach to understand and detect the failure symptoms. 
+The main reasons for this are:
 1) entries in configuration files are untyped assignments, 2) there
@@
 entries' constraints.
+
+Verifying configuration files have been advocated as a reasonable means
+to check the correctness of configuration files of interest.
 

### 2016-05-02 OSDI/abs.tex
config: new abs

@@
 reliability of today's software systems.
-While many misconfiguration handling techniques,
+Although many misconfiguration handling techniques,
 \eg, misconfiguration checking, troubleshooting and repair, 
@@
 what we did to regular programs -- is still an open problem.
-This is because 1) software configurations are typically written in
-poorly structured and untyped representations, and 2) 
-writing specifications or constraints for configuration 
-verification is non-trivial.
+This is because software configurations are typically written in
+poorly structured and untyped ``languages'', and 
+specifying constraints and rules for configuration 
+verification is non-trivial in practice.
+
 This paper presents, \app, the first automatic verification framework for
-software configurations.
-For a given configuration file,
-\app first analyzes a dataset sample of configuration files,
-thus generating a well-structured and probabilistically-typed 
+general software configurations.
+Given a target configuration file,
+\app first analyzes a dataset containing sample configuration files,
+thus generating well-structured and probabilistically-typed 
 intermediate representations.
 Then, \app derives rules and constraints by analyzing
-the intermediate representations.
-The above two steps have formulated a language model.
-Finally, the resulting language model can be used
-to verify the given configuration file and capable of 
-detecting various tricky errors,
-including orderings, value correlation, type errors, and entry missing.
-%At the heart of \app lies a novel learning engine, 
-%which employs a probabilistic type inference strategy and
-%defines an intermediate representation for the rule type.
-%With this engine, \app learns various type rules (\eg, orderings,
-%value relations, type errors, and user defined rules)
-%to verify configuration files of interest.
-Our \app framework is highly modular, 
-does not rely on the system source code, and
+the intermediate representations, thus building a language model.
+Finally, \app uses the resulting language model
+to verify the given configuration file.
+\app framework is highly modular, 
+does not rely on the system source code or templates and
 can be applied to any new configuration file type with minimal user input.
+
+\app is capable of detecting various tricky errors,
+previous methods cannot detect,
+including ordering errors, fine-grained value correlation errors, 
+entry missing errors, and environment related errors. 
 %Our tool, named \app, relies on an abstract representation of language 

### 2016-05-02 OSDI/intro.tex
config: new abs

@@
 ~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.  
-Although many efforts tackling misconfigurations have been proposed 
+For example, Yin {\em et al.}~\cite{yin11anempirical} reveal
+that about 31\% system failures are caused by misconfiguration problem.
+
+Although many efforts have been proposed 
 to check, troubleshoot, diagnose and repair configuration errors%
 ~\cite{wang04automatic, attariyan10automating,
-su07autobash, whitaker04configuration}, these efforts rely on a manual 
-approach to understand and detect the failure symptoms. 
+su07autobash, whitaker04configuration}, 
+offering automatic verification to configuration files -- like what we
+did for verifying regular programs -- is still an open problem.
 The main reasons for this are:
@@
 
-Verifying configuration files have been advocated as a reasonable means
-to check the correctness of configuration files of interest.
+%Offering automatic verification to configuration files -- like
+%what we did to programs -- has been advocated as a reasonable means
+%to check the correctness of configuration files of interest.
+%Nevertheless, it is still an open problem, because 
+%1) software configurations are typically written in poorly structured 
+%and untyped languages, and 2) writing specifications or constraints
+%for configuration verification is non-trivial in practice.
 
-We propose an approach to the verification of  
-configuration files which is based on learning rules about the language 
-model for configuration files.
+This paper presents \app, the first automatic verification framework
+for general software configurations.
+The insight of \app design is that we first analyze and learn 
+a dataset sample of configuration files, thus building 
+a structured and typed language model. Using this ``learned'' language
+model, we can verify the target configuration files.
+Such a design insight overcomes the above obstacles:
+1) learned language model itself is well-structured and typed, so
+that we can parse target configuration files to it and verify these
+files; 2) because we learn and derive rules and constraints 
+from an existing sample dataset, 
+we do not need users to write explicit constraints or specifications.
 
-Building a practical framework for checking the type-safety of
-configuration files, nevertheless, requires addressing several
-challenges. First, given the fact that 
+In general, \app's workflow to verifying a given configuration file
+could be looked as a three-step methodology.
+First, \app analyzes a dataset containing sample configuration files,
+thus generating a well-structured and probabilistically-typed 
+intermediate representation.
+Second, \app derives rules and constraints by analyzing
+the intermediate representations, thus building a language model.
+Finally, \app uses the resulting language model
+to verify the given configuration file and detect potential errors.
+
+Building such an automatic verification framework for
+configuration files, nevertheless, still requires addressing several
+challenges. 
+First, when inferencing each entry's type in a given configuration file, 
+the type of a variable cannot always be fully determined from a single 
+value. For example, an entry {\tt foo = MAX\_SIZE} is most likely
+an integer rather than string. We address this problem by introducing 
+so called {\emph{probabilistic types}}.
+Rather than assigning only one variable to a single type,
+like previous work did~\cite{zhang14encore}, 
+we assign several types with their probability distributions. 
+The entry in the above example should be assigned 
+a probabilistic type like 
+{\tt \{foo, MAX\_SIZE, [(Int, 90\%), (String, 10\%)]\}}.
+\ennan{I am not quite sure probabilistic types are obviously
+better than deterministic types.}
+
+Second, \ennan{Here, we need to add a challenge description about
+why using learning algorithm is interesting.}
+
+\com{First, given the fact that 
 different systems' configuration files use various representations, 
@@
 that can transform different systems' configuration representations
-into our proposed intermediate representation for the post process.
-
-Second, when running type inference on any given configuration file, 
-the type of a variable cannot always be fully determined from a single 
-value. For example, an entry {\tt foo = MAX\_SIZE} is most likely
-an integer rather than string. We address this problem by introducing 
-so called {\emph{probabilistic types}}.
-Rather than assigning only one variable to a single type, 
-we assign several types with their probability distributions. 
-The entry in the above example should be assigned 
-a probabilistic type like 
-{\tt \{foo, MAX\_SIZE, [(Int, 90\%), (String, 10\%)]\}}.
-\ennan{I am not quite sure probabilistic types are obviously
-better than deterministic types.}
+into our proposed intermediate representation for the post process.}
 
@@
 
+\com{
 Finally, from a systems perspective this is the first approach that {\emph{proactively}} checks 
@@
 is significantly reduced, thus making these tools truly practical.
+}
 

### 2016-05-03 OSDI/abs.tex
config: abs and intro

@@
 general software configurations.
-Given a target configuration file,
-\app first analyzes a dataset containing sample configuration files,
-thus generating well-structured and probabilistically-typed 
-intermediate representations.
-Then, \app derives rules and constraints by analyzing
-the intermediate representations, thus building a language model.
-Finally, \app uses the resulting language model
-to verify the given configuration file.
+\app verifies a target configuration file $F$ through three steps.
+First, \app analyzes a dataset containing many sample configuration 
+files belonging to the same system as $F$,
+and translates these sample files to a
+well-structured and probabilistically-typed 
+intermediate representation.
+Second, \app derives rules and constraints by analyzing
+this intermediate representation, thus building a
+language model.
+Finally, \app uses the resulting language model to verify $F$.
 \app framework is highly modular, 
@@
 
-\app is capable of detecting various tricky errors,
-previous methods cannot detect,
+\app is capable of detecting various tricky errors that cannot
+be detected by previous efforts,
 including ordering errors, fine-grained value correlation errors, 

### 2016-05-03 OSDI/intro.tex
config: abs and intro

@@
 today's software system failures~\cite{xu15systems, yin11anempirical}.
-In practice, misconfiguration problems may lead to security
-vulnerabilities, application crashes, severe disruptions in software
+For example, Yin {\em et al.}~\cite{yin11anempirical} reveal
+that about 31\% system failures were caused by misconfiguration problems. 
+Misconfigurations, in practice, may result in various
+system-wide problems, such as security vulnerabilities, 
+application crashes, severe disruptions in software
 functionality, and incorrect program executions%
 ~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.
-For example, Yin {\em et al.}~\cite{yin11anempirical} reveal
-that about 31\% system failures are caused by misconfiguration problem.
 
-Although many efforts have been proposed 
+While many efforts have been proposed 
 to check, troubleshoot, diagnose and repair configuration errors%
-~\cite{wang04automatic, attariyan10automating,
+~\cite{attariyan10automating,
 su07autobash, whitaker04configuration}, 
 offering automatic verification to configuration files -- like what we
-did for verifying regular programs -- is still an open problem.
-The main reasons for this are:
-1) entries in configuration files are untyped assignments, 2) there
+did for verifying regular programs -- is still highly
+desirable~\cite{wang04automatic, zhang14encore}.
+Nevertheless, the main obstacles are:
+1) entries in configuration files are untyped entries, 2) there
 is no explicit structure policy for the entries in configuration
@@
 entries' constraints.
+
+In order to avoid these obstacles,
+researchers propose statistical analysis and learning based approaches%
+~\cite{wang04automatic, zhang14encore, yuan11context}. 
+These efforts build checking policies by learning a sample 
+data set, rather than explicitly specifying entries' types or rules.
+In particular, for each entry in a certain configuration file, 
+if it deviates from the common values used in a large collection
+of configurations (\ie, the training set), it is typically
+suspected as a potential configuration error.
+However, because these learning 
+efforts {\em either} are limited to simplistic 
+configuration errors (\eg, type errors and syntax errors), 
+{\em or} heavily rely on template-based inference~\cite{zhang14encore}, 
+many sophisticated configuration errors, 
+\eg, hard to be templated in practice, cannot be detected.
+For example, if {\tt extension = mysql.so} appears 
+before {\tt extension = recode.so} in PHP configuration file,  
+it would lead to a crash error, since the correct ordering 
+should be {\tt extension = recode.so} before 
+{\tt extension = mysql.so}~\cite{yin11anempirical};
+however, such an error cannot be detected by existing
+learning efforts, since it is hard to build a template for this
+error~\cite{xu15systems}.
 
@@
 
-This paper presents \app, the first automatic verification framework
+In order to truly achieve automatic configuration verification,
+we argue that we need to leverage a collection of more powerful learning 
+algorithms (not necessarily depending on templates) to derive 
+a more sophisticated language model (with abundant rules covering
+tricky configuration errors), and then check the configuration files
+of interest through the learned language model.
+
+Based on the above insight, 
+this paper presents \app, the first automatic verification framework
 for general software configurations.
-The insight of \app design is that we first analyze and learn 
-a dataset sample of configuration files, thus building 
-a structured and typed language model. Using this ``learned'' language
-model, we can verify the target configuration files.
-Such a design insight overcomes the above obstacles:
-1) learned language model itself is well-structured and typed, so
-that we can parse target configuration files to it and verify these
-files; 2) because we learn and derive rules and constraints 
-from an existing sample dataset, 
-we do not need users to write explicit constraints or specifications.
-
-In general, \app's workflow to verifying a given configuration file
+In particular, \app's workflow to verifying a given configuration file
 could be looked as a three-step methodology.
@@
 to verify the given configuration file and detect potential errors.
+Compared with previous efforts,
+\app does not necessarily rely on users' templates, 
+and is capable of detecting more tricky configuration errors that
+cannot be identified by existing work (details in $\S$\ref{sec-motiv}).
 
 Building such an automatic verification framework for
-configuration files, nevertheless, still requires addressing several
-challenges. 
-First, when inferencing each entry's type in a given configuration file, 
-the type of a variable cannot always be fully determined from a single 
-value. For example, an entry {\tt foo = MAX\_SIZE} is most likely
+configuration files, nevertheless, requires addressing several challenges. 
+First, before formulating the language model, 
+we need to infer each entry's type in a given configuration file;
+however, the type of a variable cannot always be fully determined 
+from a single value. 
+For example, an entry {\tt foo = MAX\_SIZE} is most likely
 an integer rather than string. We address this problem by introducing 
@@
 
-Second, \ennan{Here, we need to add a challenge description about
-why using learning algorithm is interesting.}
+Second, without template, how to learn rules and constraints present
+a difficult. \ennan{Here, we need to add a describe to illustrate
+how we learn rules without templates.}
 
@@
 
-We can then use these more structured files
-as a training set to learn the rules. The learning algorithm
-is template-based to be easily extensible. We provide an initial set of templates and the
-learner learns some concrete instances from the training set. These
-rules are used for detecting errors violating the learned constraints
-in the files given by the user.
+From a practical perspective, 
+\app introduces no additional burden 
+to the users: they can simply use \app to check for errors in their
+configuration files. However, they can also easily extend the framework
+themselves. The system is designed to be highly modular. If there is a
+class of rules that \app is not currently learning, the user can develop
+their own templates and learners for that class. The new learner can be
+added to \app and this way it can check additionally a new set of
+errors.
 
-As an 
-illustration of a simple rule that we can learn, consider a template
- $X_1 \le X_2$, where $X_1$ and $X_2$ are
-integer variables. The learner might derive the rule stating that
-$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. There is a classification and taxonomy of configuration errors in the 
-existing work on automated configuration troubleshooting~\cite{yin11anempirical, configdataset}. We provide templates for every class that \app can handle: we consider integer constraints, ordering
-constraints, typing constraints, and constraints about correlated entries (such as ``if $X$ is present, $Y$ has to appear as well''). 
-Unfortunately, we cannot handle the class of errors that rely on the analysis of the whole operating system.
-Our language-based approach can only learn on sets of text files, not the system environment.
-
-From a practical perspective \app introduces no additional burden 
-to the users: they can simply use \app to check for errors in their configuration files.
-However, they can also easily extend the framework themselves.
-The system is designed to be highly modular.
-If there is a class of rules that \app is not currently learning, the user can develop their own templates and learners for that class.
-The new learner can be added to \app and this way it can check additionally a new set of errors.
+Our \app prototype still has a few limitations,
+\eg, cannot handle errors occurred in execution time.
+Nevertheless, we believe \app may suggest a practical path
+toward automatic and language-based configuration verification.
 
@@
 
-  \item We designed and implemented a tool, \app, that can learn a
-language model from an example set of correct configuration files, and
-we use the model to verify new configuration files.
-  \item We use probabilistic types to assign a confidence distribution over a set of types to a value.
-  \item In \app we define a interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.
+\item We propose the first automatic configuration verification
+framework, \app, that can learn a language model from an example set of 
+correct configuration files, and we use the model to verify 
+new configuration files.
+
+\item \app uses probabilistic types to assign a confidence 
+distribution over a set of types to each entry, 
+while generating the intermediate representation.
+
+\item \app applies existing machine learning algorithms to 
+enable powerful rule and constraint inference without the assistance 
+from any pre-defined templates.
+
+\item \app is capable of detecting various tricky errors that cannot
+be detected by previous efforts,
+including ordering errors, fine-grained value correlation errors, 
+entry missing errors, and environment related errors.
+
+\item We implement a \app prototype and evaluate it by
+conducting comprehensive experiments.
 

### 2016-05-03 OSDI/motiv.tex
config: abs and intro
config: abs, intro and motiv

@@
 \section{Motivating Examples}
-\label{sec:motiv}
+\label{sec-motiv}
 
-When writing configuration files, users usually take already existing
-files and modify the files, with little knowledge of the system. 
-The non-expert user can then easily introduce in errors.
-Even worse, the original file may already corrupted and the errors are propagated further. 
-Below we show some real worlds examples of the errors commonly found in configuration files.
-All these examples are extracted from real-world reports % ~\cite{yin11anempirical, configdataset}.
-The deep, domain specific knowledge needed to identify these error manually is strong motivation for a tool such as \app.
+In this section, we present several tricky configuration errors
+extracted from real-world examples. 
+Existing efforts, \eg, learning-based checking
+efforts~\cite{zhang14encore, wang04automatic}, cannot detect
+these sophisticated misconfiguration problems.
 
 \para{Example~1: Ordering errors.} 
-When configuring PHP to run with the
-Apache HTTP Server, the user writes, among others, the following lines:\\
- \texttt{
- \hspace*{3em}extension = mysql.so\\
- \hspace*{3em}...\\
- \hspace*{3em}extension = recode.so}\\
-This file caused the Apache server to fail to start due to a segmentation fault error.
-When using PHP in Apache, the extension ``mysql.so'' depends on ``recode.so'' and the relative ordering of two of them is crucial. 
-\app would inform the user that ``recode.so'' should appear before ``mysql.so'', and return the error:\\
- \texttt{
-ORDERING ERROR: Expected "extension"recode.so"\\
-   BEFORE "extension""mysql.so"
-  }
+The first example configuration error is extracted from 
+Yin {\em et al.}~\cite{yin11anempirical}.
+When a user configure PHP to run with the
+Apache HTTP Server, this user writes, among others, the following lines
+in the configuration file.
 
-\para{Example~2: Entry missing errors.} 
-If the user wants to use OpenLDAP to enable her directory access
+\begin{lstlisting}[language=C]
+extension = mysql.so
+...
+extension = recode.so
+\end{lstlisting}
+
+Such a configuration file will cause the Apache server to 
+fail to start due to a segmentation fault error~\cite{yin11anempirical}. 
+This is because when using PHP in Apache, the extension {\tt mysql.so} 
+depends on {\tt recode.so}, and the relative ordering of two of them 
+is crucial. \app is able to inform the user that {\tt recode.so} 
+should appear before {\tt mysql.so}, and reports the error.
+
+\begin{lstlisting}[language=C]
+ORDERING ERROR: Expected "extension" "recode.so"
+BEFORE "extension" "mysql.so"
+\end{lstlisting}
+
+\para{Example~2: Fine-grained value correlation errors.} 
+In a real-world misconfiguration example~\cite{correlation}, 
+a user configures his MySQL as the following:
+
+\begin{lstlisting}[language=C]
+key_buffer_size = 384M
+max_heap_table_size = 128M
+max_connections = 64
+thread_cache_size = 8
+...
+sort_buffer_size = 32M
+join_buffer_size = 32M
+read_buffer_size = 32M
+read_rnd_buffer_size = 8M
+...
+\end{lstlisting}
+
+This user complained his MySQL's load is very high and the website's
+respond speed is very slow.
+In this case, {\tt key\_buffer\_size} is used by all the threads
+cooperatively while {\tt join\_buffer} and {\tt sort\_buffer} are 
+created by each thread for private use; thus, the maximum amount
+of used key buffer, \ie, {\tt key\_buffer\_size} should be larger than 
+{\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
+Clearly, in the above example, it is not, so that this misconfiguration
+causes MySQL loads very slow.
+
+\app is able to check such fine-grained value correlation problem.
+If we run \app on this configuration file, \app  would return:
+
+\begin{lstlisting}[language=C]
+INTEGER RELATION ERROR:
+Expected "key_buffer_size">="max_connections"*"sort_buffer_size"
+\end{lstlisting}
+
+Note that existing effort, EnCore, aims to detect value correlation 
+errors. However, different from \app, EnCore can only detect simple
+correlation, \eg, {\tt mysql.max\_persistent} < {\tt max\_connections},
+rather than the fine-grained computation-based value correlation
+done by \app.
+
+\para{Example~3: Entry missing errors.} 
+If a user wants to use OpenLDAP to enable her directory access
 protocol, she needs to use the password policy overlay. This is usually
-done through the following entries in the OpenLDAP configuration file:\\
-\texttt{
- \hspace*{3em}include schema/ppolicy.schema\\
- \hspace*{3em}overlay ppolicy\\}
-When using the password policy overlay in OpenLDAP, we have to first include the related schema.
+done through the following entries in the OpenLDAP configuration file:
+
+\begin{lstlisting}[language=C]
+include schema/ppolicy.schema
+overlay ppolicy
+\end{lstlisting}
+
+When using the password policy overlay in OpenLDAP, 
+we have to first include the related schema.
 Leaving out the ``include'' statement will cause the failure of 
-this LDAP. Running \app on such a misconfiguration file would return:\\
-\texttt{
-MISSING KEYWORD ERROR: Expected "overlay""ppolicy"\\ 
-in the same file as: "include""schema/ppolicy.schema"}
+this LDAP. Running \app on such a misconfiguration file would return:
 
-\para{Example~3: Type errors.} 
-If the user tries to install MySQL, she first needs to initiate the path for the log information generated by MySQL. 
-A user may put the following code in the MySQL configuration file:\\
-\texttt{
- \hspace*{3em}general\_log = /var/log/mysql/mysql.log\\}
-However, the entry ``general\_log'' should be an integer, not a string.
- In MySQL, there is another entry named ``general\_log\_file'' which is used to specify the log path.  
-After \app analyzes this configuration file, it correctly identifies the error:\\
-\texttt{
-TYPE ERROR: Expected a Int with P=1.0 for "general\_log[mysqld]"
-}
+\begin{lstlisting}[language=C]
+MISSING KEYWORD ERROR: Expected "overlay" "ppolicy"
+in the same file: "include" "schema/ppolicy.schema"
+\end{lstlisting}
 
-\para{Example~4: Value correlation errors.} 
-When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\
-\texttt{
- \hspace*{3em}mysql's config\\
- \hspace*{3em}max\_connections = 300\\
- \hspace*{3em}...\\
- \hspace*{3em}php's config\\
- \hspace*{3em}mysql.max\_persistent = 400\\}
-This could cause MySQL to abort with the error information: ``too many connections''.
-In this case, the ``mysql.max\_persistent'' in PHP should be no larger than the ``max\_connections'' in MySQL configuration file.
-Another rule we have implemented is learning inequality relations between integers.
-Running \app on this combined configuration file would return:
-\texttt{
-INTEGER RELATION ERROR: \\
-Expected "max\_connections">="mysql.max\_persistent"}
+\ennan{Example~4: This should be the singular value error.}
 
-\com{
-\begin{figure}[t] \centering
-\includegraphics[width=0.98\textwidth]{figs/example}
-\caption{Motivating examples. Our target configuration errors are
-  classified into five groups. The five examples here correspond to
-  these groups, respectively.}
-\label{fig-example}
-\end{figure}
-
-Fig.~\ref{fig-example} presents misconfiguration examples in real-world
-that we aim to address. All the examples are extracted from
-misconfiguration issues reported in real-world efforts%
-~\cite{yin11anempirical, configdataset}.
-We classify our target configuration errors
-into five groups: 1) format error; 2) entry missing error; 3) value type
-error; and 4) ordering error
-The examples in Fig.~\ref{fig-example} correspond to the above four
-groups, respectively.
-
-}
+\para{Other errors.}
+\app can also deal with the configuration errors that can be detected by
+existing work, such as EnCore~\cite{zhang14encore}.
+For example, both \app and EnCore can handle system execution related
+misconfiguration problems.
+Furthermore, \app is also able to detect type errors and syntax errors
+in configuration files.

### 2016-05-04 OSDI/arch.tex
config: new abs
config: updated

@@
-\section{\app Overview}
+\section{The \app Framework Overview}
 
 \begin{figure*}[tbp] \centering
-\includegraphics[width=0.68\textwidth]{figs/overview}
-\caption{{\footnotesize \app's workflow. The green boxes represent configuration files,
+\includegraphics[width=0.78\textwidth]{figs/overview}
+\caption{\app's workflow. The green boxes represent configuration files,
   including both correct general configuration files and users' input
   configuration files. The purple boxes are the components within \app.
-  The yellow boxes are results generated by \app's components.}}
+  The yellow boxes are results generated by \app's components.}
 \label{fig-overview}
@@
 
-Figure~\ref{fig-overview} describes an overview of our system. We start
-with the assumption that we are given a number of correct configuration
-files belonging to the same category, such as MySQL or Apache. 
+We propose \app, an automatic verification framework,
+which can solve configuration errors, \eg, ordering errors
+and fine-grained value correlation, that previous work cannot tackle.
+As depicted in Figure~\ref{fig-overview}, \app has three main steps:
+translation, learning and checking. In this section, we briefly
+describe how does each step work.
+
+\para{Initial state.}
+We start
+with the assumption that we are given a number of (not necessarily) 
+correct configuration files belonging to the same system, 
+such as MySQL or Apache. 
 Such files follow similar patterns, which we exploit
 in a learning algorithm to build rules that
-describe a language model for the files. Since the
-``language'' of configuration types is untyped and unstructured, we
-first parse the files and translate them into a more structured,
-intermediary representation.
-When running type inference on a configuration file, 
+describe a language model for the files.
+
+\para{Translator.}
+The translator component first parses the input sample 
+dataset (containing both configuration files and system environment
+information), and then transforms them to a more structured
+and typed intermediate representation.
+When we run type inference on a configuration file, 
 the type of a variable cannot always be fully determined from 
@@
 We address this problem 
-by introducing so called {\emph{probabilistic types}}.
-Rather than giving a variable a single type, we assign several types with their probability distributions. 
-We can then use these more structured files
-as a training set to learn the rules. The learning algorithm
-is template-based to be easily extensible. We provide an initial set of templates and the
+by introducing so called {\em probabilistic types}.
+Rather than giving a variable a single type, 
+we assign several types with their probability distributions. 
+We can later use these more structured files
+as a training set to learn the rules.
+
+\para{Learning.}
+The learning algorithm is template-based to be easily extensible. 
+We provide an initial set of templates and the
 learner learns some concrete instances from the training set. These
@@
 
-As an 
-illustration of a simple rule that we can learn, consider a template
+As an illustration of a simple rule that we can learn, consider a template
  $X_1 \le X_2$, where $X_1$ and $X_2$ are
@@
 constraints, typing constraints, and constraints about correlated entries (such as ``if $X$ is present, $Y$ has to appear as well'').
-Unfortunately, we cannot handle the class of errors that rely on the analysis of the whole operating system.
-Our language-based approach can only learn on sets of text files, not the system environment.
-
-\com{
-A rule R is added to the set of all rules,
-  if $\exists$ learning file f s.t. R(f) is non vacuously true
-That rule R is then removed from the set of all rules,
-  if $\exists$ learning file f st R(f) is false.
-
-This is accomplished in two passes.
-First we collect all possible rules for every file.
-Then we merge the all the rules to create our final set.
-This conviently gives rise to an embarresingly parallel situation, which Haskell allows us to easily take advantage of by
-  using the parallel mapping library parmap.
-
-\begin{lstlisting}
-  potentialRules = parmap findAllRules learningSet.
-  finalRules = foldl1 mergeRules potenialRules
-\begin{lstlisting}
-
-Each rule is of the Attribute typeclass, which means a rule must support the following operations:
-\begin{lstlisting}
-class Attribute r where
-  learn :: ConfigFile Common -> [r]
-  merge :: [r] -> [r] -> [r] 
-  check :: [r] -> ConfigFile Common -> Error
-\end{lstlisting}
-
-}

### 2016-05-04 OSDI/intro.tex
config: updated

@@
 did for verifying regular programs -- is still highly
-desirable~\cite{wang04automatic, zhang14encore}.
-Nevertheless, the main obstacles are:
+desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
+Nevertheless, the main obstacles to the configuration verification are:
 1) entries in configuration files are untyped entries, 2) there
@@
 
-In order to avoid these obstacles,
+In order to overcome these obstacles,
 researchers propose statistical analysis and learning based approaches%
@@
 if it deviates from the common values used in a large collection
-of configurations (\ie, the training set), it is typically
+of configurations (\ie, the training data set), it is typically
 suspected as a potential configuration error.
@@
 
-Based on the above insight, 
+Based on the above argument, 
 this paper presents \app, the first automatic verification framework
@@
 configuration files, nevertheless, requires addressing several challenges. 
-First, before formulating the language model, 
+First, in order to formulate a correct language model, 
 we need to infer each entry's type in a given configuration file;
@@
 For example, an entry {\tt foo = MAX\_SIZE} is most likely
-an integer rather than string. We address this problem by introducing 
+an integer rather than string; however, existing type inference 
+work would report this is an error, because foo should be assigned
+an integer~\cite{zhang14encore}. We address this problem by introducing 
 so called {\emph{probabilistic types}}.
 Rather than assigning only one variable to a single type, 
-like previous work did~\cite{zhang14encore}, 
 we assign several types with their probability distributions. 
-The entry in the above example should be assigned 
+The entry in the above example might be assigned 
 a probabilistic type like 
-{\tt \{foo, MAX\_SIZE, [(Int, 90\%), (String, 10\%)]\}}.
-\ennan{I am not quite sure probabilistic types are obviously
-better than deterministic types.}
+{\tt \{foo, MAX\_SIZE, [(Int, 60\%), (String, 40\%)]\}}.
+With such probabilistic types in hand,
+we can generate a more accurate language model,
+thus significantly improving our checking capability.
 
 Second, without template, how to learn rules and constraints present
-a difficult. \ennan{Here, we need to add a describe to illustrate
-how we learn rules without templates.}
+a difficult. \ennan{Here, we need to add one-paragraph description 
+to illustrate how we learn rules without templates.}
 
@@
 toward automatic and language-based configuration verification.
+To summarize, this tool paper makes the following contributions:
 
@@
 
-To summarize, this tool paper makes the following contributions:
-
 \begin{enumerate}
@@
 framework, \app, that can learn a language model from an example set of 
-correct configuration files, and we use the model to verify 
-new configuration files.
+correct configuration files, and then uses this language model to verify 
+interested configuration files.
 
-\item \app uses probabilistic types to assign a confidence 
+\item \app proposes probabilistic types to assign a confidence 
 distribution over a set of types to each entry, 
@@
 
-\item \app applies existing machine learning algorithms to 
+\item \app employs a collection of machine learning algorithms to 
 enable powerful rule and constraint inference without the assistance 

### 2016-05-04 OSDI/limit.tex
config: updated

@@
 \section{Discussion and Limitations}
-
-\ennan{Of course, our tool has many limitations. For example, we cannot
-detect the misconfiguration correlation across multiple individual
-systems unwilling to share configuration information with each other.}
 
@@
 A potential solution is to combine existing misconfiguration diagnosis
-tools, \eg, X-ray~\cite{}, with \app in order to enhance the 
+tools, \eg, X-ray~\cite{attariyan12x-ray}, 
+with \app in order to enhance the 
 misconfiguration checking capability.
 
-\para{}
+\para{Misconfiguration across software components.}
+As exposed by Yin {\em et al.}~\cite{yin11anempirical},
+cross-software configuration correlation problems also account
+for a considerable number of misconfiguration cases.
+For example, in a LAMP-based Web server, one entry in 
+PHP configuration file, {\tt mysql.max\_persistent = 400}
+may make users encounter a ``too many connections'' error,
+because a correlated entry in the underlying MySQL's configuration
+file assigns {\tt max\_connection} to 300, which is less
+than the MySQL connection numbers in PHP's configuration file (\ie, 400).
+It is quite difficult to detect such a type of tricky error
+through leaning approaches, because not only users or engineers 
+are not aware of the hidden interactions~\cite{xu15systems},
+but also it is hard to obtain a global knowledge to the entire
+configurations.
+One possible solution to this problem might be to introduce
+some cryptographic protocol, \eg, private set
+intersection~\cite{kissner05privacy}, to privately extract the
+overlapping entries, \eg, {\tt mysql.max\_connection} in the 
+above MySQL and PHP case, for double-checking.
+
+\para{Network configuration verification.}
+\app mainly focuses on software configurations, \eg, MySQL and Apache,
+so that our approach is limited to support network configuration
+verification. This is because network configurations have quite
+different representations, format and rules from software configurations,
+since network configurations are typically written in 
+more domain-specific policy languages.
+In fact, many network verification tools, 
+\eg, NoD~\cite{lopes15checking} and 
+Dobrescu {\em et al.}~\cite{dobrescu14software},
+have been proposed to check whether network configurations
+meet their specifications.

### 2016-05-04 OSDI/motiv.tex
config: updated

@@
 
-In this section, we present several tricky configuration errors
+In this section, we present several {\em tricky} configuration errors
 extracted from real-world examples. 
-Existing efforts, \eg, learning-based checking
+The reason we call them tricky is
+most of existing efforts, \eg, learning-based checking
 efforts~\cite{zhang14encore, wang04automatic}, cannot detect
-these sophisticated misconfiguration problems.
+these configuration errors.
+On the other hand, we also investigated 
+many misconfiguration problems in practice were caused by 
+these tricky configuration errors, \eg, reported by Stack Overflow.
 
 \para{Example~1: Ordering errors.} 
-The first example configuration error is extracted from 
+The first example configuration error is first reported by 
 Yin {\em et al.}~\cite{yin11anempirical}.
-When a user configure PHP to run with the
-Apache HTTP Server, this user writes, among others, the following lines
-in the configuration file.
+For instance, when a user configures PHP to run with the
+Apache HTTP Server, this user may write, among others, 
+the following lines in the configuration file.
 
@@
 depends on {\tt recode.so}, and the relative ordering of two of them 
-is crucial. \app is able to inform the user that {\tt recode.so} 
-should appear before {\tt mysql.so}, and reports the error.
+is crucial. 
+We call the above example misconfiguration situation 
+as {\em ordering errors}.
+Yin {\em et al.} find that ordering errors widely exist in
+many system configurations, \eg, PHP and MySQL,
+and typically lead to multiple system crash events;
+however, there is no existing effort that can effectively solve 
+or detect this problem~\cite{zhang14encore, xu15systems, xu13do}.
+
+If this user is using \app, she can avoid such a configuration error.
+In particular, \app is able to inform the user that {\tt recode.so} 
+should appear before {\tt mysql.so}, and reports the error (as shown
+below).
 
@@
 
-\ennan{Example~4: This should be the singular value error.}
+\ennan{Example~4: This should be the singular value error.
+We need an example from Stack Overflow to illustrate the 
+real-world problem. I guess the buffer size example is fine.}
 
@@
 in configuration files.
+\ennan{We may need one example here.}

### 2016-05-05 OSDI/osdi_algorithm.tex
my writeup of my probabilistic learners

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb,amsfonts,listings}

\begin{document}
\section{The Probabilistic Learning Algorithm}

\subsection{Intuition and Formalism}
Our probabilistic approaches for learning the Missing Values, Keyword Ordering, and Integer Relations rules stem from our previous work with building the non-probabilistic versions of these rule-learning algorithms. We start with the idea that for each of these rules, we are going to consider all possible pairs of keywords that appear in every file, and for our learning process, calculate the likelihood that each of these pairs constitute a rule. In essence, this is a mechanism that will consider many different possible pairs of lines in the file, and attempt to compile a set of these pairs that are expressed more often than others as a basis for finding patterns within the example set that can be used to evaluate new files.

More formally, this approach can be defined as follows. The output of our learning algorithm, for any of these three rules, can be though of as a mapping
\[
\{ (a_j, a_k) | j \neq k \} \rightarrow \{ (N_1, N_2, ... , N_n) \}
\]
where $a_j$ and $a_k$ are either two different keywords or two different lines from our intermediate representation, or more formally, $a_j \neq a_k \wedge (a_j, a_k \in \{ K \} \vee a_j, a_k \in \{ L \})$ where $\{ K \}$ is the set of keywords found in the intermediate representation of the learning set, and $\{ L \}$ is the set of lines (keyword and value pairs) found in the intermediate representation of our learning set. We can think of each of these $(a_j, a_k)$ possibly having a different relationship, defined by the set of probability events/outcomes $\{ A_i \}$, where the set of these possible outcomes cover the entire outcome space of possible relationships between the two values $(a_j, a_k)$, or more formally $\cup_{i = 1}^n A_i = \Omega$. (For example, in the missing keywords rules case, we can define $A_1$ the event that $a_j$ and $a_k$ always appear together, and $A_2$ to be the event that $a_j$ appears without $a_k$ or $a_k$ appears without $a_j$. In the keyword ordering, we have $A_1$ be the event that $a_j$ appears before $a_k$ and $A_2$ be the event that $a_k$ appears before $a_j$. In the integer relations case, we have that $A_1$ is the case that $a_j \leq a_k$, $A_2$ the case that $a_j = a_k$, and $A_3$ the case that $a_j \geq a_k$. Notice that the $A_i$ do not have to be disjoint, but only have to union to the entire probability space.)

The way we derive the tuple of integers $(N_1, N_2, ..., N_n)$ from the set of possible outcomes is that $N_i$ must keep track of how may times we have seen the outcome $A_i$ in the example set. Ideally, in order to pass the results of the learner into the checker, we have to have the mapping
\[
\{ (a_j, a_k) | j \neq k \} \rightarrow \{ A_i \}
\]
so that for each pair of keywords or lines will correspond to a single outcome that can be evaluted to either being upheld or refuted. Hence, since the algorithm works in two parts: the first to generate $\{ (N_1, ..., N_n) \}$ from the intermediate representation, and then to interpret these observed counts of each of the events to pick the most likely event from the $A_i$ to use for the checker evaluation. The rest of this section will talk in more detail about these two pieces of the algorithm for each of the three probabilistic rules.

\subsection{Missing Values (MisingP.hs)}
As with the non-probabilistic approaches, the accumulation of the counts in the tuples happens in the $learn$ and $merge$ functions. Given each file, this algorithm starts out by assembling all the possible (unordered, so $(a_j,a_k)$ is equal to $(a_k,a_j)$) pairs of keywords (where the two keywords in the pair are not equal) found in the intermediate representation, with the default tuple value of $(1,0)$, since we saw one case of each $(a_j, a_k)$ appearing together. During the merge step, where we merge the set of rules $A$ and $B$, we must consider three different sets of $(a_j, a_k)$. The first set is the set of pairs that appear in both $A$ (with the mapped value $(N_1^A, N_2^A$) and $B$ (with the mapped value $(N_1^B, N_2^B)$, which can be merged with the value in the merged mapping equaling $(N_1^A + N_1^B, N_2^A + N_2^B)$. Now, for the second (appears in $A$ but not $B$) and third (appears in $B$ but not $A$) sets, without the loss of generality, we consider a pair $(a_j, a_k)$ that appears in $A$ but does not appear in $B$, which means that on all of the example files that were considered to learn $B$, no example of $a_j$ and $a_k$ appearing together was found. We must count this phenomena as there being multiple observations in $B$ where either $a_j$ was seen without $a_k$ and vice versa. Here, to count how many of these observations we have seen, we must find a pair in $B$ that has the maximum number of total observations and at least one of either $a_k$ or $a_j$ in the pair. Using this maximum observation value $M$ for the pair $(a_j, a_k)$ not found in $B$, the mapped value of $(a_j, a_k)$ will be $(N_1^A, N_2^A + M)$. With these two functions defined, we construct the set of learned rules over the example set by learning the rules for each file in the set and then merging them all together.

\subsubsection{Example}
Let us consider three configuration files
\begin{lstlisting}
file1
a = 1
b = 1
c = 1

file2
a = 1
c = 1
d = 1

file3
b = 1
a = 1
d = 1
\end{lstlisting}
After the $learn$ function is called on each of these files, we will have the following learned rule sets for each of the files
\begin{lstlisting}
file1
(a,b) -> (1, 0)
(a,c) -> (1, 0)
(b,c) -> (1, 0)

file2
(a,c) -> (1, 0)
(a,d) -> (1, 0)
(c,d) -> (1, 0)

file3
(b,a) -> (1, 0)
(b,d) -> (1, 0)
(a,d) -> (1, 0)
\end{lstlisting}
Let us merge the rules from file1 and file2 first. Since $(a,c)$ is in both of these files, we can combine their counts to get $(2, 0)$. For each of $(a,b)$, $(b,c)$, $(a,d)$, and $(c,d)$ we must now find a pair in the other set that 1) has at least one of the keywords in common with the pair in question and 2) has the maximum number of observations amongst such a set of pairs. (If no pairs in the other set share even one of the keywords with the pair in question, we default to a value of $0$, since we haven't seen any examples of one of the keywords appearing without the other.) Since all the counts are $(1,0)$, the maximum number of observations are each $1$ for each of these four pairs, and we have the merged count $(1,1)$ for each of them. Hence, the rule sets now are
\begin{lstlisting}
file1 + file2
(a,b) -> (1, 1)
(a,c) -> (2, 0)
(b,c) -> (1, 1)
(a,d) -> (1, 1)
(c,d) -> (1, 1)

file3
(b,a) -> (1, 0)
(b,d) -> (1, 0)
(a,d) -> (1, 0)
\end{lstlisting}
And when we merge in file3, the important notes are to remember that $(a_j, a_k)$ and $(a_k, a_j)$ are equivalent in the mapping. (If we think of the mapping as a function $f$, then $f(a_j, a_k) = f(a_k, a_j)$, and hence, there is a symmetry akin to that of even functions in the missing values rule.) We can combine $(b,a)$ and $(a,d)$ since they appear in both sets, and for $(b,d)$, the pair that has either one of those symbols and the largest number of observations is still $(a,b)$ at $2$ observations, so we get
\begin{lstlisting}
file1 + file2 + file3
(a,b) -> (2, 1)
(a,c) -> (2, 0)
(b,c) -> (1, 1)
(a,d) -> (2, 1)
(c,d) -> (1, 1)
(b,d) -> (1, 2)
\end{lstlisting}
which is very much in line with what we wanted to measure. For example, $(b,d)$ has a count of $(1,2)$ because it has one file where it is satisfied (file3) but two files (file1 and file2) where either b or d appear without the other. $(a,b)$ has a count of $(2,1)$ because they appear together in files file1 and file3 but not file2, and so on. Form these counts, after learning from a sufficiently large set, we should be able to say that pairs that have a high number of positive observations, along with a high proportion of positive to negative observations, are likely to be rules because they were seen together in most of the learning set.

\subsection{Keyword Ordering (OrderPK.hs)}
Very much like the Missing Values algorithm, our approach will be to generate all pairs where one keyword appears before another, with a base observation of $(1, 0)$, and then merge the counts across each of the files in the learning set. One important distinction here is that although the mapping for Missing Values resembled an even function, the symmetry for keyword ordering resembles an odd function, since $f(a_j, a_k) = inv(f(a_k, a_j))$ because if $(a_j, a_k) -> (N_1, N_2)$ has $N_1$ instances of $a_j$ before $a_k$ and $N_2$ instances of $a_k$ before $a_j$, then $(a_k, a_j) -> (N_2, N_1)$ by the definition of $N_i$ as the result of $(a_j, a_k)$. Hence, the difference here is that during the merge, we only have to make sure we add up the corresponding counts for $(a_j, a_k)$ and $(a_k, a_j)$ cases properly. Here, if a certain pair does not appear in one of the learned rule sets to be merged, then it takes on a default value of $(0, 0)$ because if we do not see either $a_j$ come before $a_k$ or vice versa, we should not be commenting on whether that particular file is an instance of support for $a_j$ before $a_k$ or vice versa.

\subsubsection{Example}
Let our three files be

\begin{lstlisting}
file1
a = 1
b = 1
c = 1

file2
a = 1
c = 1
d = 1

file3
b = 1
a = 1
d = 1
\end{lstlisting}
which leads to the exact same initial learned tuples
\begin{lstlisting}
file1
(a,b) -> (1, 0)
(a,c) -> (1, 0)
(b,c) -> (1, 0)

file2
(a,c) -> (1, 0)
(a,d) -> (1, 0)
(c,d) -> (1, 0)

file3
(b,a) -> (1, 0)
(b,d) -> (1, 0)
(a,d) -> (1, 0)
\end{lstlisting}
Here, when we merge the contents of file1 and file2, since $(a,c)$ appears in both, we will simply add their mapped values together. For $(a,b)$, $(b,c)$, $(a,d)$, and $(c,d)$, we should set their values to be $(0,0)$ in the learned rule set for the files in which they don't appear because we should not be making a call for either ordering. We merge these with addition to get
\begin{lstlisting}
file1 + file2
(a,b) -> (1, 0)
(a,c) -> (2, 0)
(b,c) -> (1, 0)
(a,d) -> (1, 0)
(c,d) -> (1, 0)

file3
(b,a) -> (1, 0)
(b,d) -> (1, 0)
(a,d) -> (1, 0)
\end{lstlisting}
Now, we see that the keyword pair $(b,a)$ is the inverse of $(a,b)$ so $(b,a) -> (1, 0)$ is equivalent to $(a,b) -> (0, 1)$. Since $(a,d)$ is present in both sets, and $(b,d)$ is only present in the second set, we do not have to worry about inverting their values. Adding these through, we get the final merged learned rule set
\begin{lstlisting}
file1 + file2 + file3
(a,b) -> (1, 1)
(a,c) -> (2, 0)
(b,c) -> (1, 0)
(a,d) -> (2, 0)
(c,d) -> (1, 0)
(b,d) -> (1, 0)
\end{lstlisting}
and we see that $(a,c)$ and $(a,d)$ are most likely to be rules, and $(a,b)$ is probably not a rule.

\subsection{Integer Relations (IntRelP.hs)}
The algorithm for this rule is quite similar to the Keyword Ordering rule, since there is also a symmetry that resembles odd functions in integer relations, because, without loss of generality, $a_j \leq a_k \Leftrightarrow a_k \geq a_j$, so the mapping of (less than, equals, greater than) becomes (greater than, equals, less than). Like the Keyword Ordering, a pair that does not appear in one of the learned rule sets to be merged gets a default value of $(0, 0, 0)$, since the fact that the pair doesn't appear in the learned rule set means that $a_j$ and $a_k$ in the pair never appeared together in the same file, and hence, if we did not make an observation with both keywords in the same file, then we should not add any observations one way or the other. One observation, however is that the probabilithy of a certain $A_i$ is not simply $\frac{A_i}{A_1 + A_2}$ as in the other two rules, but actually
\[
\frac{A_i}{A_{1} + A_{3} - A_{2}} =
\frac{A_i}{A_{\leq} + A_{\geq} - A_{=}}
\]
since the cases of equality are already counted in the less-than-and-equals-to as well as the greater-than-or-equals-to, so in order to compute the total number of observations, we should use the Inclusion-Exclusion principle and not double count the equality cases.

\subsubsection{Example}
Let us start with the files
\begin{lstlisting}
file1
a = 1
b = 2
c = 2

file2
b = 1
a = 2
c = 3
d = 0
\end{lstlisting}
which translates to the following learned tuples
\begin{lstlisting}
file1
(a,b) -> (1, 0, 0)
(a,c) -> (1, 0, 0)
(b,c) -> (1, 1, 1)

file2
(b,a) -> (1, 0, 0)
(b,c) -> (1, 0, 0)
(b,d) -> (0, 0, 1)
(a,c) -> (1, 0, 0)
(a,d) -> (0, 0, 1)
(c,d) -> (0, 0, 1)
\end{lstlisting}
because the tuple counts the cases of $(a_j \leq a_k, a_j = a_k, a_j \geq a_k)$, since although it would be easier to make the three cases mutually exclusive, many of the rules we want to find are in the format $\leq$ or $\geq$, and thus, we have corresponding templates as such. Hence, we end up with the tuple $(1, 1, 1)$ for $(b,c)$, since $b = c$ satisfies all three cases. Let us merge these next:
\begin{lstlisting}
file1 + file2
(a,b) -> (1, 0, 1)
(a,c) -> (2, 0, 0)
(b,c) -> (2, 1, 1)
(b,d) -> (0, 0, 1)
(a,d) -> (0, 0, 1)
(c,d) -> (0, 0, 1)
\end{lstlisting}
Since $(b,a)$ is the inverse of $(a,b)$, we also had to invert the tuple from $(1, 0, 0)$ to $(0, 0, 1)$ in order to merge it with the value for $(a,b)$ in the learned rule set from file1. For the pairs containing $d$, since they do not appear in file1, we merge them with the default value $(0, 0, 0)$. The rest of the pairs are in both of the learned rule sets, so we merge them through addition.

\subsection{Going from $(N_1, ... , N_n)$ to $A_i$}
The reason why we did not cover this section during the computation of the rules for each of the previous three probabilistic templates is because there should not be a conversion from the tuple of observed integers to a specific rule until we have gained the most accurate count possible by merging through all of the files in the example set. Since some heuristics of converting these integer tuples to a single rule also take into account the counts in each of the integers in respect to the rest of the tuples observed, we should endeavor to keep the learned rules in their integer tuple format for as long as possible and not do the conversion until we are absolutely sure that we have a learned rule set as complete as it can get. Furthermore, we should store the learned rule set in its integer tuple form because it makes learning new rules from additional examples easier. If we convert them, then there is too much loss of information to extract the counts in the tuples we need in order to adjust the converted rules in the context of the newly seen example files.

A good heuristic is that the $A_i$ we pick will correspond to the $N_i$ that is the maximum of the $N_1$ through the $N_n$. The challenge, however, is providing a certainty value along with this conversion, which corresponds to how certain we are that this is a rule. Many of our techniques deal with separating out the rules that are more certainly rules from ones that are less certain, and the heuristics that solve that problem use a cutoff for a certain proportion of observations yes versus no, along with a cutoff for the minimum number of total observations needed for certainty.

There are some fancier heuristics that we employ, such as the one-tailed null-hypothesis testing on proportions. For this heuristic, we count each integer tuple as an experiment. Our null hypothesis is that the true probabilty (the proportion) of cases of a certain rule held versus not is less than or equal to some user-specified value, for example, 70\% of files out there support this rule. Hence, our alternate hypothesis (the one we want to show true) will be that the true probability (proportion) will be higher than the user-specified value. Then, based on the tuple we observed, we can say with what probability we would see results like this if the null-hypothesis held true, and if this calculated probability (called the p-score) is less than some significance level, say 5\%, we can say with 95\% certaintiy that the rule is held in more than 70\% of the files.

Although this approach is mathematically more sound, often in practice, this is produces a very similar final set of converted rules as a user-set probability and number of observations cutoff. Hence,. we can conclude that the cutoff heuristics are a very good approximator of the hypothesis test, at least in our use case.

\subsubsection{Example}
Suppose we had the user-specified bounds of $65\%$ in proportions/probability and a mininum number of observations at $120$, as defined in the Settings.hs file. If we have the following pairs with the following tuples, for the Keyword Ordering rule
\begin{lstlisting}
(a,b) -> (77,43)
(c,d) -> (5,0)
(e,f) -> (20,180)
\end{lstlisting}
We say that $f$ comes before $e$ is the only valid rule we have learned from this set, as $(a,b)$ does not meet the probability bounds (although it meets the number of observation bounds) and $(c,d)$ does not meet the number of observation bounds, although it meets probability bounds. Although $(e,f)$ has a low probability in itself, its inverse $(f,e)$ has a fairly high probability, and is the rule to be extracted from the following counts. Hence, our checker will only check for the $(f,e)$ rule, as it is the only one that meets the user-specified certainty bounds.
\end{document}

### 2016-05-05 OSDI/intro.tex
config: new fig and motivation

@@
 desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
-Nevertheless, the main obstacles to the configuration verification are:
+Nevertheless, the main obstacles to the automatic 
+configuration verification are:
 1) entries in configuration files are untyped entries, 2) there
@@
 In order to overcome these obstacles,
-researchers propose statistical analysis and learning based approaches%
+researchers have proposed 
+statistical analysis and learning based approaches%
 ~\cite{wang04automatic, zhang14encore, yuan11context}. 
@@
 if it deviates from the common values used in a large collection
-of configurations (\ie, the training data set), it is typically
+of configurations (\ie, the data set for training), it is typically
 suspected as a potential configuration error.
@@
 
-Our \app prototype still has a few limitations,
-\eg, cannot handle errors occurred in execution time.
+Our \app prototype still has a few limitations:
+for example, we cannot handle configuration errors that can be only
+triggered in system execution time.
 Nevertheless, we believe \app may suggest a practical path
-toward automatic and language-based configuration verification.
+toward automatic and modular language-based configuration verification.
 To summarize, this tool paper makes the following contributions:

### 2016-05-05 OSDI/motiv.tex
config: new fig and motivation

@@
 
-\begin{lstlisting}[language=C]
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
 extension = mysql.so
@@
 
-\begin{lstlisting}[language=C]
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
 ORDERING ERROR: Expected "extension" "recode.so"
@@
 
-\begin{lstlisting}[language=C]
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
 key_buffer_size = 384M
@@
 {\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
-Clearly, in the above example, it is not, so that this misconfiguration
-causes MySQL loads very slow.
+Clearly, in the above example, it does not hold, 
+so that this misconfiguration causes MySQL loads very slow.
 
-\app is able to check such fine-grained value correlation problem.
+We call the above situation as a {\em fine-grained value correlation
+error}, which is a more challenging case than 
+{\em value correlation error} reported
+by some existing investigations~\cite{yin11anempirical, zhang14encore}.
+A typical value correlation error
+means one entry's value should have a certain correlation with
+another entry's value. For example, in MySQL,
+the value of {\tt max\_connections} should be higher than
+{\tt mysql.max\_persistent}. Although some work, \eg,
+EnCore~\cite{zhang14encore}, can detect the normal value
+correlation case, 
+none of existing efforts can detect the fine-grained value correlation
+errors, which ``hides'' an equation-aware correlation, as shown in
+the above example.
+As mentioned by Xu {\em et al.}~\cite{xu15hey},
+detecting the fine-grained value correlation errors 
+present a much more challenging
+task than normal value correlation problems.
+
+To the best of our knowledge, \app is the first effort that
+is able to check such fine-grained value correlation problem.
 If we run \app on this configuration file, \app  would return:
 
-\begin{lstlisting}[language=C]
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
 INTEGER RELATION ERROR:
-Expected "key_buffer_size">="max_connections"*"sort_buffer_size"
+Expected "key_buffer_size" >= "max_connections" * "sort_buffer_size"
 \end{lstlisting}
@@
 correlation, \eg, {\tt mysql.max\_persistent} < {\tt max\_connections},
-rather than the fine-grained computation-based value correlation
-done by \app.
+rather than the fine-grained computation-based value correlation,
+like {\tt key\_buffer\_size >= max\_connections * sort\_buffer\_size}
+identified by \app.
 
 \para{Example~3: Entry missing errors.} 
-If a user wants to use OpenLDAP to enable her directory access
+Many critical system outages result from the fact that important
+entry was missing in the configuration file. 
+We call such a problem as {\em entry missing error}.
+Below is a real-world entry missing error example,
+when a user wants to use OpenLDAP to enable her directory access
 protocol, she needs to use the password policy overlay. This is usually
@@
 
-\begin{lstlisting}[language=C]
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
 include schema/ppolicy.schema
@@
 When using the password policy overlay in OpenLDAP, 
-we have to first include the related schema.
-Leaving out the ``include'' statement will cause the failure of 
-this LDAP. Running \app on such a misconfiguration file would return:
+users have to first include the related schema.
+Leaving out the ``include'' entry, 
+which have been left by many users~\cite{yin11anempirical}, 
+will cause the failure of this LDAP. 
+If this user has \app, she can run \app on such a misconfiguration file,
+and \app would return:
 
-\begin{lstlisting}[language=C]
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
 MISSING KEYWORD ERROR: Expected "overlay" "ppolicy"

### 2016-05-05 OSDI/arch.tex
config: sec 3, 4 and fig

@@
 \begin{figure*}[tbp] \centering
-\includegraphics[width=0.78\textwidth]{figs/overview}
-\caption{\app's workflow. The green boxes represent configuration files,
-  including both correct general configuration files and users' input
-  configuration files. The purple boxes are the components within \app.
-  The yellow boxes are results generated by \app's components.}
+\includegraphics[width=0.88\textwidth]{figs/overview}
+\caption{\app's workflow. The green components represent configuration 
+  files, including both sample configuration datasets and users' input
+  configuration files to verify. 
+  The purple components are the modules of \app.
+  Because template DB is not necessarily used, we use dashed
+  arrow between it and the learner.
+  Red boxes are sub-modules within the checker.
+  The yellow components are results generated by \app's modules.}
 \label{fig-overview}

### 2016-05-05 OSDI/trans.tex
config: sec 3, 4 and fig

@@
 \ennan{Translator is, in some sense, like a parser. 
-This section is used to detail how we design the parser.
-We need to include: 1) probabilistic type, 2) language model
-and 3) parser design.}
+This section is used to detail how we design the parser.}
+
+The responsibility of the translator is to transform a given set of
+configuration files into another set of files written in
+typed and well-structured representations.
+In some sense, the translator looks like a parser, and it is only
+used to generate an intermediate representation for the post
+process, such as learning rules (see $\S$\ref{sec-learn}).
+Coupled with rules generated by learner module,
+we will have a complete language model to verify configuration files
+of our interest.
+
+Translating or parsing is system dependent. In other words, for MySQL
+and HDFS, we need to develop different parsers to handle each of them,
+respectively. \app allows users to provide extra help to the translator
+for their specific system configuration, such as specifying a comment 
+character. Each of the entries in the intermediate representations
+must be assigned types, and these types would guide the learning
+modules later.
+
+\ennan{We need a kind of formal definition (using a figure) to
+define the grammar of our intermediate representation. The basic
+view of this definition should be similar to define a type language
+grammar.}
+
+\para{Introducing probabilistic types.}
+Based on a single example value of $v$,
+the translator cannot fully determine the type of $k$.
+Consider for instance the following example:
+
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
+foo = 300
+bar = 300.txt
+\end{lstlisting}
+
+Most likely {\tt foo} should be an integer, but it could also be a string.
+In this case, we want to learn the rule like 
+$ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. 
+The translator, therefore, assigns a distribution of types 
+to a value, an idea closely related to existentially quantified 
+types~\cite{Launchbury93lazyfunctional}. 
+We introduce {\em probabilistic types} to address this issue.
+
+Let $\mathcal{T}$ be a set of basic types. 
+In \app set $\mathcal{T}$ contains strings, integers, file paths, 
+sizes and IP addresses. 
+A probabilistic type built from $\mathcal{T}$ is a list of pairs 
+$[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$,
+such that $\tau_i \in \mathcal{T}$, $0 \le p_i \le 1$ 
+and $\Sigma p_i = 1$. 
+These probabilities are updated each time a new example value 
+for a key is encountered.
+
+When a value has a probabilistic type, we generate rules for all its types.
+This means that by assigning {\texttt{foo}} a probabilistic type 
+(\eg, {\tt (\texttt{foo}, 300, [(\textsl{Int},90\%), 
+(\textsl{String},10\%)])},
+we would generate rules for both strings and integers.
+Once the type inference can uniquely determine the type, 
+the probability of all other types is set to zero, 
+and the associated rules are withdrawn.
+
+Note that typing is also a system module than 
+can be easily extended to support more types. 
+In that case the user will need to provide rules for type inference 
+and probability distributions for values where type inference is ambiguous.

### 2016-05-06 OSDI/arch.tex
config: checker part

@@
 constraints, typing constraints, and constraints about correlated entries (such as ``if $X$ is present, $Y$ has to appear as well'').
+
+\para{Checking.}
+The checker is used to detect the rule violations in the configuration
+files of interest. The inputs of checker are the learned rules 
+and the target configuration file to verify.
+Its outputs a report (as shown in $\S$\ref{sec-motiv}) about 
+whether it finds any error, \eg, rule violations, or a suspicious value.
+As shown in Figure~\ref{fig-overview},
+there are two sub-modules in the checker. They are responsible for
+checking rule violations and suspicious values, respectively.
+\ennan{I really wanted to say we are using MaxSMT to check and rank
+these errors ...}
+In our experience, we find learned rules can be significantly reused
+to check different configuration files, thus improving our usability.

### 2016-05-06 OSDI/arch.tex
config: updated arch

@@
 \para{Learning.}
-The learning algorithm is template-based to be easily extensible. 
-We provide an initial set of templates and the
-learner learns some concrete instances from the training set. These
-rules are used for detecting errors violating the learned constraints
-in the files given by the user.
+The input of learner is a set of files that have been translated
+into well-structured and typed representations.
+The learner module employs a collection of learning algorithms
+to generate various rule and constraints,
+potentially used to handle different types of configuration errors.
+These rules are the output of the learner, and will be 
+used by the checker to detect errors.
+By combining the translated representations and the learned
+rules together, we already build a language model for
+configuration verifications.
+Because the translator outputs probabilistic typed entries,
+the learner is responsible for determining a type for each entry.
 
-As an illustration of a simple rule that we can learn, consider a template
- $X_1 \le X_2$, where $X_1$ and $X_2$ are
-integer variables. The learner might derive the rule stating that
-$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. There is a classification and taxonomy of configuration errors in the 
-existing work on automated configuration troubleshooting~\cite{yin11anempirical, configdataset}. We provide templates for every class that \app can handle: we consider integer constraints, ordering
-constraints, typing constraints, and constraints about correlated entries (such as ``if $X$ is present, $Y$ has to appear as well'').
+Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
+which needs users or developers to provide explicit templates,
+\app's learner encodes some predefined error-patterns 
+to generate rules. 
+As an illustration of a simple rule that we can learn,
+consider an encoded pattern $X_1 \le X_2$, where $X_1$ and $X_2$ are
+integer variables. The learner may derive the rule stating that
+$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. 
+There is a classification and taxonomy of configuration errors in the 
+existing work on automated configuration troubleshooting%
+~\cite{yin11anempirical, configdataset}. 
+Each class is looked as an error-pattern 
+that \app should handle: we consider integer constraints, 
+ordering errors, typing errors, correlation errors, etc.
+
+Although the learner does necessarily rely on templates,
+\app still offers a template DB, which will be used to offer
+execution environment related information.
+It is widely known that any existing learning algorithm cannot
+derive rules checking environment violation, \eg,
+whether current account is the owner of a certain path.
+In order to deal with comprehensive misconfiguration problems,
+the learner needs a template DB to provide environment information,
+thus detecting system environment related configuration errors.
 

### 2016-05-06 OSDI/intro.tex
config: updated arch

@@
 a difficult. \ennan{Here, we need to add one-paragraph description 
-to illustrate how we learn rules without templates.}
+to illustrate how we learn rules without templates, 
+or why we say our learning results are better than existing
+learning approach, \eg, EnCore.}
 

### 2016-05-06 OSDI/check.tex
config: checker, eval

@@
 \section{Checker}
+\label{sec-checker}
 
-\ennan{Here, we need to describe how we check whether 
-the target configuration file meets learned rules using SMT solver.}
+With the learned rules and constraints in hand,
+\app checks whether any entry in a target configuration file
+violates the learned rules.
+For a given configuration file, \app parses it using the same
+way employed in the translator, thus obtaining a structured
+and typed representation for the target configuration file.
+Then, the checker uses two sub-modules to check the
+following aspects of the target configuration file.
+
+\para{Ordering violation.}
+\app can check whether two or more entries have the ordering 
+problem, which means whether the order of some entries in the 
+target configuration follows the rules output by the learner.
+
+\para{Correlation violation.}
+\app checks if the target configuration file follows the 
+correlation rules (including fine-grained value correlation rules)
+learned from the training set. The rule would be ignored 
+if the involved entries are absent in the target configuration file.
+
+\para{Data type violation.}
+For each entry to be checked in the target configuration file,
+the checker reads its type information inferred from the training set,
+and uses the generated language model to verify whether the types
+are matched. A type violation is reported if the verification
+fails.
+
+\para{Suspicious warning.}
+This checking occurs in the second sub-module of the checker.
+Different from the previous checking tasks,
+suspicious warning is just to detect whether some value
+is too different (or distinguished) from the same entries in the
+training dataset. Even if some values are statistically different
+from the ones in the training dataset, 
+it does not mean such a value is incorrect;
+thus \app, in this case, throw out a warning to the user who
+enters the target configuration file, and a report containing 
+normal values in the training dataset.
+\app allows users to choose whether they want to change 
+the values according to the ones in the training configuration
+files or not.

### 2016-05-06 OSDI/eval.tex
config: checker, eval

@@
-\section{Implementation and Evaluations}
+\section{Implementation}
 
-\ennan{Here, we describe the implementation and evaluations}
+\ennan{We need to describe how do we implement each module. We may need to
+have three paragraphs: one is for translator, one is for learner 
+and one is for checker.}
+
+\section{Evaluations}
+
+We mainly conduct three parts of experiments to evaluate our \app
+prototype.
+
+We want to answer several questions:
+
+\begin{itemize}
+
+\item Whether \app can detect real-world configuration errors?
+
+\item How does the size of training dataset impact on the correctness
+  of \app?
+
+\item What is the rule inference accuracy?
+
+\item How long can we run the verification?
+
+\end{itemize}
+
+\subsection{\app's effectiveness}
+
+In order to evaluate the effectiveness of \app, we extract
+20 misconfiguration files from a MySQL dataset~\cite{xu15hey},
+and perform \app on them. \ennan{Here, we first need a table to 
+list each configuration error with error type, description,
+and whether \app correctly reports the issues.}
+
+Next, we inject some errors to correct configuration files,
+and run \app to check whether our framework can correctly detect
+these injected errors. \ennan{We also need a table here, 
+and list each injected problem.}
+
+\subsection{Training Set Impact}
+
+In this experiment, we vary the number of training configuration files,
+and observe whether the correctness of \app would increase 
+accordingly. \ennan{We may need a table whose x-axis is the number
+of entries in the training configuration files, and y-axis is the 
+accuracy or something close.}
+
+\subsection{The accuracy of Rule Inference}
+
+\ennan{I am still trying to think about this part ...}
+
+\subsection{The Run-Time of Verification}
+
+\ennan{Here, we need three pictures. In the first figure, x-axis should
+be the number (or the size) of entries in the training dataset, and 
+y-axis should be the run-time of parsing. In the second figure,
+we need to measure the time of generating rules. }

### 2016-05-06 code/Benchmarks.hs
fix quote error

@@ -4,9 +4,32 @@
 module Benchmarks where
 
 import Types
-
 import Settings
 
+import qualified Data.Text as T
+import qualified Data.Text.IO as T
+import System.Directory
+import System.IO.Unsafe
+
+import Debug.Trace
+
+testLearnSet = genSet "testLearn/"
+learningSet = genSet "dataset/correctMySQL/"
+bigLearningSet = genSet  "dump/MySQL/"
+
+genSet s =
+  map (\x -> (u $ T.readFile (s++x), MySQL))
+    (u (listDirectory s))
+
+u = unsafePerformIO
+
+-- | from the newest version of the package, which i cant get for some reason
+listDirectory :: FilePath -> IO [FilePath]
+listDirectory path =
+  filter f <$> getDirectoryContents path
+  where
+    isDir = not . u . doesDirectoryExist
+    f filename = filename /= "." && filename /= ".." && isDir (path++filename)
 
 makeError (errLoc1,errLoc2,errIdent) =
   Error {errMsg="Spec",..}
@@ -15,10 +38,10 @@ getFileName = fst . errLoc1
 benchmarkFiles :: [FilePath]
 benchmarkFiles = map getFileName $ concat benchmarks
 benchmarks :: [ErrorReport]
-benchmarks =
-  if Settings.pROBRULES
-    then group2 ++ group4 ++ group5 ++ group6
-    else group2 ++ group3 ++ group4 ++ group5
+benchmarks = case Settings.pROBRULES of
+  Test -> testBenchSet
+  NonProb -> group2 ++ group3 ++ group4 ++ group5
+  Prob -> group2 ++ group4 ++ group5 -- ++ group6
 
 group2 :: [ErrorReport]
 group2 = map (map makeError) [
@@ -49,7 +72,7 @@ group4 = map (map makeError) [
 
 group5 :: [ErrorReport]
 group5 = map (map makeError) [
-    [(("dataset/group5-value-correlation/error","max_allowed_packet[wampmysqld]"),("dataset/group5-value-correlation/error","key_buffer[wampmysqld]"),"INTREL")]
+    [(("dataset/group5-value-correlation/error","max_allowed_packet[wampmysqld"),("dataset/group5-value-correlation/error","key_buffer[wampmysqld]"),"INTREL")]
[…]

### 2016-05-06 code/Learners/IntRelP.hs

@@ -21,8 +21,9 @@ import Debug.Trace
 -- I haven't found a nice package for SMTLIB format in haskell yet, its out there tho, im sure
 
 -- for tuning which probabilistic rules to throw out
-cutoffProb = 0.7
-cutoffPerc = 0.2
+-- between 0-1?
+cutoffProb = 1
+cutoffPerc = 0.9
 
 instance Attribute (M.Map (Keyword,Keyword)) FormulaC where
   -- | this has the problem that order is important
@@ -40,13 +41,13 @@ instance Attribute (M.Map (Keyword,Keyword)) FormulaC where
   check rs f =
     let
       emptyFC (FormulaC l g e) = g == 0 && l == 0 && e == 0
-      relevantRules' = M.filterWithKey (\k v-> (not $ emptyFC v) && hasRuleFor f k) (rs)
+      relevantRules' = M.filterWithKey (\k v-> not (emptyFC v) && hasRuleFor f k) rs
       fRules' = learn f :: IntRelMapC
-      relevantRules = (filterRuleSet cutoffProb cutoffPerc) relevantRules'
+      relevantRules = filterRuleSet cutoffProb cutoffPerc relevantRules'
       fRules = forcePairOrientation relevantRules fRules'
       diff = M.differenceWith compRules relevantRules fRules --diff is the rules we should have met, but didnt
     in
-      if M.null diff then Nothing else Just diff
+      if M.null diff then Nothing else ((trace (show $ diff) Just diff))
 
   -- merge curr new = foldl combineCounts [] $ L.union curr (traceShow (length curr) new)
   merge curr new =
@@ -184,6 +185,7 @@ findeqRules (l1,l2) =
        | not bothSame -> []
        | length all /= 1 && bothSame -> makeR "=="
 
+traceMe x = trace (show x) x
 -- only for comparators! careful!
 --instance Eq (Int -> Int -> Bool) where
 --  (==) f1 f2 =

### 2016-05-06 code/Main.hs

@@ -16,9 +16,6 @@ import qualified Data.Text.IO as T
 import qualified Data.List as L
 import Control.Monad
 
-import System.IO.Unsafe
-
-import System.Directory
 import Data.Aeson
 import qualified Data.ByteString.Lazy as B
 import Data.Maybe
@@ -32,27 +29,39 @@ import qualified Settings
 main = do
  bs <- mapM T.readFile benchmarkFiles :: IO [T.Text]
  let bs' = zip bs (replicate (length bs) MySQL)
- -- bigLearningSet ++
- let rules = learnRules (if Settings.pROBRULES then ( learningSet) else learningSet)
- B.writeFile "cachedRules.json" $ encode $ (toLists rules:: RuleSetLists)
+ unless Settings.uSE_CACHE $ B.writeFile "cachedRules.json" $ encode (toLists rules:: RuleSetLists)
  cached <- B.readFile "cachedRules.json"
- either (putStrLn) (runVerify bs' . fromLists)(eitherDecode cached  :: Either String RuleSetLists)
+ fitness <- runVerify bs' (if Settings.uSE_CACHE then (fromLists. fromJust $ decode cached) else rules)
+ putStrLn ("FITNESS : "++show fitness)
+ return ()
 
-runVerify :: [ConfigFile Language] -> RuleSet -> IO()
+rules =
+  learnRules $ case Settings.pROBRULES of
+  Settings.Test -> testLearnSet
+  Settings.NonProb -> learningSet
+  Settings.Prob -> bigLearningSet ++ learningSet
+
+verifyCache c = when (rules /= (fromLists. fromJust $ decode c)) (fail  "error in json cache")
+
+runVerify :: [ConfigFile Language] -> RuleSet -> IO Int
 runVerify bs' rules = do
- let errors =  zipWith (verifyOn $ rules) bs' benchmarkFiles
+ let errors =  zipWith (verifyOn rules) bs' benchmarkFiles
  when Settings.vERBOSE $ mapM_ putStrLn $ showProbRules rules
 
  --mapM putStrLn (zipWith (++) benchmarks (map unlines errors))
- zipWithM_ reportBenchmarkPerformance benchmarks errors
- return ()
+ fitnesses <- zipWithM reportBenchmarkPerformance benchmarks errors
+ return $ sum fitnesses
 
  -- | compare the original benchark spec to the generated one
-reportBenchmarkPerformance :: ErrorReport -> ErrorReport -> IO()
[…]

### 2016-05-06 code/Settings.hs

@@ -1,4 +1,7 @@
 module Settings where
 
   vERBOSE = False
-  pROBRULES = True
+  uSE_CACHE = True
+  pROBRULES = Prob
+
+  data ModeSetting = NonProb | Prob | Test

### 2016-05-06 code/Types.hs

@@ -36,7 +36,7 @@ data RuleSet = RuleSet
   , missingP :: [(MissingKRule, Int, Int)]
   , orderP :: OrdMap (Integer, Integer)
   , intRelP :: IntRelMapC
-  } deriving (Show, Generic, Data,Typeable)
+  } deriving (Eq, Show, Generic, Data,Typeable)
 
 data RuleSetLists = RuleSetLists
   { orderl :: [((IRLine,IRLine),Bool)]
@@ -182,6 +182,10 @@ data Error = Error{
   , errIdent :: ErrorType
   , errMsg :: String
 }
+
+instance Show Error where
+    show e = "Error between "++(show$ errLoc1 e)++" and "++(show$ errLoc2 e)++" of type: "++(show $errIdent e)++"\n   -->"
+    -- ++(show $errMsg e)++"\n"
 
 -- | as long as we have the correct type of error
 --   and have identified one similar fail point the errors are similar enough

### 2016-05-06 code/Usertime.hs

@@ -23,9 +23,7 @@ import Debug.Trace
 
 import qualified Settings
 
-instance Show Error where
-    --show e = "Error between "++(show$ errLoc1 e)++" and "++(show$ errLoc2 e)++" of type: "++(show $errIdent e)++"\n"
-    show e = errMsg e
+
 
 showProbRules :: RuleSet -> [String]
 showProbRules r =
@@ -62,12 +60,12 @@ showProbRules r =
         findOrFindInverse (x,y) =
           M.findWithDefault Nothing (x,y) i <|> inverseIntRel (M.findWithDefault Nothing (y,x) i)-}
   in
-    if Settings.pROBRULES
-      then
+    case Settings.pROBRULES of
+      Settings.Prob ->
         (["rule" ++ delimiter ++ "yes" ++ delimiter ++ "no" ++ delimiter ++ "valid"] ++ (map showMissingP m)) ++
         (["rule|yes|no|valid"] ++ (map showOrderP $ M.toList o)) ++
         (["ordering|less_than|equals|greater_than|answer"] ++ (map showIntRelP $ M.toList i))
-      else
+      _ ->
         (map (\x -> "Expected " ++ (show $ k1 x) ++ " with " ++ (show $ k2 x)) m') ++
         (map (\(x,y) -> "Expected " ++ (show $ fst x) ++ " before " ++ (show $ snd x)) $ filter snd $ M.toList o')
 
@@ -114,17 +112,16 @@ verifyOn r f fname =
     orderingShowP =
       showErr orderingErrorP orderingPErrMsg
 
+    intRelPErrMsg :: ((Keyword,Keyword),FormulaC) -> Error
     intRelPErrMsg x =
       let
         es = maybe [] M.toList intRelErrorP
-        k1 x = show $ fst $ fst x
         fc x = show $ snd x
-        k2 x = show $ snd $ fst x
       in
-        Error {errLoc1 = (fname,T.pack$k1 x)
-              ,errLoc2 = (fname,T.pack$k2 x)
+        Error {errLoc1 = (fname,fst$fst x)
+              ,errLoc2 = (fname,snd$fst x)
               ,errIdent = "INTREL(PROB)"
-              ,errMsg = "INTEGER RELATION ERROR (PROB): Expected "++(k1 x)++(fc x)++(k2 x)}
[…]

### 2016-05-06 CAV/evaluation.tex
Updates from ShareLaTeX

--- 2016-05-01 OSDI/evaluation.tex
@@
 Error Type       & Passing Tests & False Positives  \\ \hhline{=|=|=}
-Missing Entry    & 5/5           & 1, 0, 0, 0, 1        \\ \hline
+Missing Entry    & 5/5           & 1, 0, 0, 0, 4        \\ \hline
 Type Error       & 5/5           & 0, 0, 0, 0, 0          \\ \hline
-Keyword Ordering & 5/5           & 0, 1, 1, 0, 10       \\ \hline
-Value Relations  & 4/5           & 0, 1, 0, 0, 0        \\ 
+Keyword Ordering & 5/5           & 0, 2, 1, 0, 6       \\ \hline
+Value Relations  & 4/5           & 0, 0, 0, 1, 0        \\ 
 \end{tabular}

### 2016-05-06 OSDI/learner.tex
config: sec 3, 4 and fig

@@
 \section{Learner}
+\label{sec-learn}
 
-\ennan{This section details how we extract rules from the
-intermediate representations. This section should include: 
-1) our learning algorithm, 2) how to customize templates,
-3) how to input environmental templates, and 4) other methods
-for learning rules.}
+\ennan{This section details how do we extract rules from the
+intermediate representations. This section may should have the following
+two subsections: Aaron's part (including Xinyu's fine-grained
+value correlation rule learning) and Jonathon's part.
+In addition, we may need to add one more subsection about
+learning system environment information related rules,
+\eg, for paths and users.}

### 2016-05-06 OSDI/limit.tex
config: checker part

@@
 While \app can check diverse configuration errors without
-human participations, all the misconfiguration detection techniques,
-including \app, cannot handle some types of configuration errors
-resulting from events occurred during system runtime.
+human participations, most of the existing proactive 
+misconfiguration detection techniques,
+including \app, cannot handle configuration errors
+resulting from events occurred during the system runtime.
 Such configuration errors are referred to as {\em legal misconfigurations}%
-~\cite{yin11anempirical}. As shown in Yin {\em et al.}%
-~\cite{yin11anempirical}, many parameter misconfigurations have 
-perfectly legal parameters but do not deliver the functionality intended
-by users. These cases are more difficult to detect by
+~\cite{yin11anempirical}. In particular, 
+many parameter misconfigurations have 
+perfectly legal types and values, 
+but do not deliver the functionality intended by users. 
+For example, after a website's traffic significantly increases,
+the parameter {\tt Max\_key\_buffer} in MySQL may not 
+be able to handle increasingly more data traffic,
+thus leading to the outage of the whole system.
+These cases are more difficult to detect by
 automatic checkers and may require more user training or
@@
 A potential solution is to combine existing misconfiguration diagnosis
-tools, \eg, X-ray~\cite{attariyan12x-ray}, 
+tools, \eg, X-ray~\cite{attariyan12x-ray} 
+and ConfAid~\cite{attariyan10automating},
 with \app in order to enhance the 
@@
 meet their specifications.
+
+\ennan{One more limitation description here.}

### 2016-05-06 OSDI/motiv.tex

@@
 \app can also deal with the configuration errors that can be detected by
-existing work, such as EnCore~\cite{zhang14encore}.
+existing work, such as EnCore~\cite{zhang14encore} and
+CODE~\cite{yuan11context}.
 For example, both \app and EnCore can handle system execution related
@@
 in configuration files.
-\ennan{We may need one example here.}

### 2016-05-06 OSDI/rel.tex

@@
 produce configuration errors in their routing configuration files.
-PRESTO~\cite{} automates the generation of device-native configurations
+PRESTO~\cite{enck07configuration} 
+automates the generation of device-native configurations
 with configlets in a template language. 
-Loo {\em et al.}~\cite{} adopt Datalog to reason about 
-routing protocols in a declarative fashion. COOLAID~\cite{} constructs
+Loo {\em et al.}~\cite{loo05declarative} adopt Datalog to reason about 
+routing protocols in a declarative fashion. 
+COOLAID~\cite{chen10declarative} constructs
 a language to describe domain knowledge about network devices and
@@
 \para{Misconfiguration diagnosis.}
-Many misconfiguration diagnosis approaches have been proposed~\cite{}.
-For example, ConfAid~\cite{} and X-ray~\cite{} use dynamic information
+Many misconfiguration diagnosis approaches have been proposed%
+~\cite{attariyan10automating, attariyan12x-ray}.
+For example, ConfAid~\cite{attariyan10automating} 
+and X-ray~\cite{attariyan12x-ray} use dynamic information
 flow tracking to find possible configuration errors that may result in
-failures or performance problems. AutoBash~\cite{} speculatively
+failures or performance problems. AutoBash~\cite{su07autobash} 
+speculatively
 executes processes and tracks causality to automatically fix 
@@
 tolerant to misconfigurations~\cite{xu13do}. 
-ConfErr~\cite{} uses a human error hodel from psychology and
-linguistics to inject misconfigurations into systems.
+%ConfErr~\cite{} uses a human error hodel from psychology and
+%linguistics to inject misconfigurations into systems.
 SPEX~\cite{xu13do} takes a white-box testing approach to automatically

### 2016-05-06 OSDI/limit.tex
config: more discussions and bib

@@
 but also it is hard to obtain a global knowledge to the entire
-configurations.
+configurations due to the business privacy concerns of
+each software provider.
 One possible solution to this problem might be to introduce
@@
 
-\ennan{One more limitation description here.}
+\para{More complex configuration structure.}
+The current \app mainly targets key-value configuration files,
+but in practice many systems, \eg, OpenStack~\cite{OpenStack},
+employ very complex configuration format and structure,
+which \app cannot handle.
+Verifying such structurally complex configurations typically needs
+\app to learn a much more sophisticated language model,
+which is challenging in practice.
+Recent efforts~\cite{raychev15predicting, raychev16learning} 
+may present a possible solution on this limitation.
+These techniques can learn a call-graph from a training program set,
+and check a new program based on properties extracted from this
+generated call-graph. If we look a structurally complex configuration 
+file as a program in these tools, we may be able to use a similar way
+to verify whether the configuration file violates any 
+property of our interest.

### 2016-05-07 OSDI/arch.tex
config: more update

@@
 
-We propose \app, an automatic verification framework,
-which can solve configuration errors, \eg, ordering errors
-and fine-grained value correlation, that previous work cannot tackle.
-As depicted in Figure~\ref{fig-overview}, \app has three main steps:
+We propose \app, an automatic verification framework for 
+software configuration files.
+In particular, \app can solve many sophisticated 
+configuration errors (\eg, ordering errors, missing entry errors 
+and fine-grained value correlation) that previous efforts cannot 
+detect. As depicted in Figure~\ref{fig-overview}, 
+a typical \app verification workflow has three steps:
 translation, learning and checking. In this section, we briefly
@@
 
-\para{Initial state.}
-We start
-with the assumption that we are given a number of (not necessarily) 
-correct configuration files belonging to the same system, 
+\para{Initial phase.}
+We start with the assumption 
+that we are given a number of (not necessarily correct) 
+configuration files belonging to the same system, 
 such as MySQL or Apache. 
-Such files follow similar patterns, which we exploit
+These given files follow similar patterns, which we exploit
 in a learning algorithm to build rules that
@@
 \para{Translator.}
-The translator component first parses the input sample 
+The translator module first parses the input sample 
 dataset (containing both configuration files and system environment
@@
 ordering errors, typing errors, correlation errors, etc.
+\ennan{I do know we are using in some sense templates, but
+we should use pattern or some words to persuade we are 
+using an implicit ``templates''; otherwise, too similar 
+to what EnCore did.}
 
 Although the learner does necessarily rely on templates,
-\app still offers a template DB, which will be used to offer
-execution environment related information.
+\app still offers a database to contain many templates,
+as shown in Figure~\ref{fig-overview}.
+Some of these templates are responsible for offering
+specific system executional environment information.
 It is widely known that any existing learning algorithm cannot

### 2016-05-07 OSDI/motiv.tex
config: more update

@@
 We call such a problem as {\em entry missing error}.
-Below is a real-world entry missing error example,
+In a public misconfiguration dataset~\cite{configdataset},
+the major problems of MySQL failure reports were caused by
+entry missing errors.
+Below is a real-world entry missing error example~\cite{yin11anempirical},
 when a user wants to use OpenLDAP to enable her directory access
@@
 CODE~\cite{yuan11context}.
-For example, both \app and EnCore can handle system execution related
+For a configuration error reported recently made MySQL
+daemon failed to start~\cite{syserror}.
+One entry in a MySQL configuration file is written as 
+{\tt datadir=/root/appfinder/mysql}, and the type as well as 
+format seem to be correct.
+However, the problem is this directory should not be
+initiated as a root directory, and the correct entry
+should be {\tt datadir=/appfinder/mysql}.
+Such an error is called system environment related configuration error.
+Both \app and EnCore can handle system execution related
 misconfiguration problems.

### 2016-05-07 code/Learners/IntRelP.hs
print best rules

@@ -22,7 +22,7 @@ import Debug.Trace
 
 -- for tuning which probabilistic rules to throw out
 -- between 0-1?
-cutoffProb = 0 -- probability this rule is correct (# positive evidence / # total evidence)
+cutoffProb = 1 -- probability this rule is correct (# positive evidence / # total evidence)
 cutoffPerc = 1 -- take the top x percent of observation counts. this removes low count rules, like (1+,0-)
 
 instance Attribute (M.Map (Keyword,Keyword)) FormulaC where
@@ -58,23 +58,30 @@ instance Attribute (M.Map (Keyword,Keyword)) FormulaC where
     in
       cu
 
+prob (FormulaC l g e) =
+  let
+    total = fromIntegral $ l + g - e
+    l' = fromIntegral l
+    g' = fromIntegral g
+    e' = fromIntegral e
+  in
+    maximum [l' / total, g' / total, e' / total]
+
 -- as in the other rules, institute a filter over a top percentile of observations and probability cutoff
 filterRuleSet :: Double -> Double -> IntRelMapC -> IntRelMapC
-filterRuleSet probCutoff percObsCutoff m =
+filterRuleSet probCutoff percObsCutoff rs =
   let
+    keep = M.filter
+    highestProbRs = keep (\r -> prob r >= probCutoff) rs
+    compareTotalObs (_,f1) (_,f2) =
+      if totalObs f1 > totalObs f2 then LT else GT
+    sortedByObs = L.sortBy compareTotalObs $ M.toList highestProbRs
+    rs' = take (round $ percObsCutoff * fromIntegral (length highestProbRs - 1)) sortedByObs
+
     totalObs (FormulaC l g e) = l + g - e -- remember that <= and >= intersect on the event ==
-    obs = reverse $ L.sort $ map totalObs $ M.elems m
-    obsCutoff = obs !! min (round $ percObsCutoff * (fromIntegral.length) obs) (length obs -1)
-    prob (FormulaC l g e) =
-      let
-        total = fromIntegral $ totalObs (FormulaC l g e)
-        l' = fromIntegral l
-        g' = fromIntegral g
-        e' = fromIntegral e
-      in
-        maximum [l' / total, g' / total, e' / total]
   in
-    M.filter (\x -> totalObs x >= obsCutoff) $ M.filter (\x -> prob x >= probCutoff) m
+    --trace (unlines $ map show  rs' ) M.fromList rs'
[…]

### 2016-05-07 code/Learners/MissingP.hs

@@ -11,15 +11,17 @@ import qualified Data.List as L
 import qualified Data.Map as M
 import qualified Data.Ord as O
 
+import Data.Maybe
+
 import Debug.Trace
 
 -- programmed in cutoff for testing?
-cutoffProb :: Double
-cutoffProb = 0.5
-cutoffObsPercentile :: Double
-cutoffObsPercentile = 0.1
+probCutoff :: Double
+probCutoff = 1
+percObsCutoff :: Double
+percObsCutoff = 1
 -- and to make dealing with probs easier
-prob :: Eq a => Show a => (a, Int, Int) -> Double
+prob :: (a, Int, Int) -> Double
 prob (_, y, n) =
   let
     y' = fromIntegral y
@@ -27,15 +29,19 @@ prob (_, y, n) =
   in y' / (y' + n')
 -- and to actually filter the rules
 -- have settings in the settings file to set cutoff percentage/percentile/hard number of observations
-filterRuleSet :: Eq a => Show a => Double -> Double -> [(a, Int, Int)] -> [(a, Int, Int)]
+filterRuleSet ::  Double -> Double -> [(a, Int, Int)] -> [(a, Int, Int)]
 filterRuleSet probCutoff percObsCutoff rs =
   let
-    rs' = filter (\x -> prob x > probCutoff) rs
-    obs = reverse $ L.sort $ map (\(_, y, n) -> y + n) rs'
-    topObsCutoff = obs !! min (round $ percObsCutoff * (fromIntegral.length) obs) (length obs -1)
-    rs'' = filter (\(_, y, n) -> y + n >= topObsCutoff) rs'
+    keep = filter
+    highestProbRs = keep (\r -> prob r >= probCutoff) rs
+    compareTotalObs (_, y, n) (_, y', n') =
+      if y + n > y' + n' then LT else GT
+    sortedByObs = L.sortBy compareTotalObs highestProbRs
+    rs' = take (round $ percObsCutoff * fromIntegral (length highestProbRs - 1)) sortedByObs
   in
-    rs''
+    --trace (unlines $ map (\x -> show x++" "++(show $ prob x)) highestProbRs ) rs''
+    rs'
+
 
 -- when we need to go from MissingKRule to [(MissingKRule, Int, Int)]
 --  (hack type matching)
@@ -81,8 +87,8 @@ instance Attribute [] (MissingKRule, Int, Int) where
   check rs f =
    let
      fRules = learn f
[…]

### 2016-05-07 code/Learners/TypeMapper.hs

@@ -59,7 +59,7 @@ addTypeToMap m IRLine{..} =
     -- will only lookup if a file has duplicate keywords
     snd $ M.insertLookupWithKey updateProbs keyword newCType m
 
--- TODO avg?
+-- TODO merge two QTypes intelligently
 updateProbs :: Keyword -> ConfigQType -> ConfigQType -> ConfigQType
 updateProbs k old new =
   new
@@ -70,6 +70,7 @@ assignProbs t =
   let
    cint =
      buildConfTy (T.all isDigit t) (read $ T.unpack t :: Int)
+   --TODO strings should be able to have numbers?
    cstring =
      buildConfTy (T.all isAlpha t) (T.unpack t :: String)
    cfilepath =

### 2016-05-07 code/Main.hs

@@ -29,8 +29,9 @@ import qualified Settings
 main = do
  bs <- mapM T.readFile benchmarkFiles :: IO [T.Text]
  let bs' = zip bs (replicate (length bs) MySQL)
- unless Settings.uSE_CACHE $ B.writeFile "cachedRules.json" $ encode (toLists rules:: RuleSetLists)
+ --unless Settings.uSE_CACHE $ B.writeFile "cachedRules.json" $ encode (toLists rules:: RuleSetLists)
  cached <- B.readFile "cachedRules.json"
+ --(putStrLn . show) ((fromJust $ decode cached) :: RuleSetLists)
  fitness <- runVerify bs' (if Settings.uSE_CACHE then (fromLists. fromJust $ decode cached) else rules)
  putStrLn ("FITNESS : "++show fitness)
  return ()
@@ -39,15 +40,15 @@ rules =
   learnRules $ case Settings.pROBRULES of
   Settings.Test -> testLearnSet
   Settings.NonProb -> learningSet
-  Settings.Prob -> bigLearningSet ++ learningSet
+  Settings.Prob -> probLearnSet
 
 verifyCache c = when (rules /= (fromLists. fromJust $ decode c)) (fail  "error in json cache")
 
 runVerify :: [ConfigFile Language] -> RuleSet -> IO Int
 runVerify bs' rules = do
  let errors =  zipWith (verifyOn rules) bs' benchmarkFiles
- when Settings.vERBOSE $ mapM_ putStrLn $ showProbRules rules
-
+ --when Settings.vERBOSE $ mapM_ putStrLn $ showProbRules rules
+ when True $ mapM_ putStrLn $ showProbRules rules
  --mapM putStrLn (zipWith (++) benchmarks (map unlines errors))
  fitnesses <- zipWithM reportBenchmarkPerformance benchmarks errors
  return $ sum fitnesses

### 2016-05-07 code/Types.hs

@@ -190,6 +190,7 @@ instance Show Error where
 -- | as long as we have the correct type of error
 --   and have identified one similar fail point the errors are similar enough
 --   both will point the user to the item that needs to be fixed
+--   NB DEF OF FALSE POSITIVE - THIS IS REALLY IMPORTANT!!!
 
 instance Eq Error where
   (==) x y =
@@ -203,6 +204,6 @@ instance Eq Error where
         MISSING -> (exactLocMatch || transitiveLocMatch) && identMatch
         ORDERING -> exactLocMatch && identMatch
         INTREL -> anyMatch && identMatch
-        TYPE -> anyMatch
+        TYPE -> (exactLocMatch || transitiveLocMatch) && identMatch
 
 type ErrorReport = [Error]

### 2016-05-07 code/Usertime.hs

@@ -29,7 +29,7 @@ showProbRules :: RuleSet -> [String]
 showProbRules r =
   let
     delimiter = "|"
-    m = missingP r
+    m = filter (\(_,y,n) -> y+n>20 && n==0) $ missingP r
     o = orderP r
     i = intRelP r
     m' = missing r
@@ -40,10 +40,10 @@ showProbRules r =
         ++ delimiter ++ (show n)
         ++ delimiter ++ (show $ elem r m')
     showOrderP (r, (y, n)) =
-      "Expected " ++ (show $ fst r) ++ " before " ++ (show $ snd r)
-        ++ delimiter ++ (show y)
-        ++ delimiter ++ (show n)
-        ++ delimiter ++ (show $ M.findWithDefault False r o')
+          "Expected " ++ (show $ fst r) ++ " before " ++ (show $ snd r)
+          ++ delimiter ++ (show y)
+          ++ delimiter ++ (show n)
+          ++ delimiter ++ (show $ M.findWithDefault False r o')
     showIntRelP (r, f) =
       (show $ fst r) ++ " <=> " ++ (show $ snd r)
         ++ delimiter ++ (show $ lt f)
@@ -62,9 +62,9 @@ showProbRules r =
   in
     case Settings.pROBRULES of
       Settings.Prob ->
-        (["rule" ++ delimiter ++ "yes" ++ delimiter ++ "no" ++ delimiter ++ "valid"] ++ (map showMissingP m)) ++
-        (["rule|yes|no|valid"] ++ (map showOrderP $ M.toList o)) ++
-        (["ordering|less_than|equals|greater_than|answer"] ++ (map showIntRelP $ M.toList i))
+        (["\n\nrule" ++ delimiter ++ "yes" ++ delimiter ++ "no" ++ delimiter ++ "valid"] ++ (map showMissingP m)) ++
+        (["\n\nrule|yes|no|valid"] ++ (map showOrderP $ filter (\(r, (y, n)) -> y+n>50 && n==0) $ M.toList o)) ++
+        (["\n\nordering|less_than|equals|greater_than|answer"] ++ (map showIntRelP $ filter (\(r, f) ->lt f==0 && eq f==0 && gt f > 35) $ M.toList i))
       _ ->
         (map (\x -> "Expected " ++ (show $ k1 x) ++ " with " ++ (show $ k2 x)) m') ++
         (map (\(x,y) -> "Expected " ++ (show $ fst x) ++ " before " ++ (show $ snd x)) $ filter snd $ M.toList o')

### 2016-05-07 OSDI/learner-ranges.tex

\section{Ranges}
\label{sec-learn-ranges}

We discuss the technique we use to detect anomalous values for numerical attributes. For a given test file, let $A$ be the set of attributes contained in the file. Let $A_n$ be the subset of attributes of $A$ which are numerical types. Then, for each attribute $a \in A_n$, we construct a vector $v_a$ of the values corresponding to attribute $a$ seen over the entire data-set. For each $v_a$, we compute an interval  $$[\hat{v_a} - 3*MAD(v_a), \hat{v_a} + 3*MAD(v_a)],$$ 
where $\hat{v_a}$ represents the median over the values in $v_a$ and $MAD(v_a$) refers to the median absolute deviation. This is a standard outlier detection test, namely the Hampel identifier. \footnote{Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation for a normal distribution.} If the value for a numerical attribute in a test file falls outside of this interval, a warning is printed to the user indicating the violating value, the attribute, and the upper or lower Hampel threshold.

### 2016-05-07 OSDI/learner-ranges.tex
add intuition for ranges

@@
 
-We discuss the technique we use to detect anomalous values for numerical attributes.
-For a given test file, let $A$ be the set of attributes contained in the file.
-Let $A_n$ be the subset of attributes of $A$ which are numerical types.
-Then, for each attribute $a \in A_n$, we construct a vector $v_a$ of the values corresponding to attribute $a$ seen over the entire data-set.
-For each $v_a$, we compute an interval  $$[\hat{v_a} - 3*MAD(v_a), \hat{v_a} + 3*MAD(v_a)],$$
-where $\hat{v_a}$ represents the median over the values in $v_a$ and $MAD(v_a$) refers to the median absolute deviation.
-This is a standard outlier detection test, namely the Hampel identifier.
-\footnote{Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation for a normal distribution.} If the value for a numerical attribute in a test file falls outside of this interval, a warning is printed to the user indicating the violating value, the attribute, and the upper or lower Hampel threshold.
+We discuss the technique we use to detect anomalous values for numerical attributes. For a given 
+test file, let $A$ be the set of attributes contained in the file. Let $A_n$ be the subset of attributes 
+of $A$ which are numerical types. Then, for each attribute $a \in A_n$, we construct a vector $v_a$ of the 
+values corresponding to attribute $a$ seen over the entire data-set. For each $v_a$, we compute 
+an interval  $$[\hat{v_a} - 3*MAD(v_a), \hat{v_a} + 3*MAD(v_a)],$$ 
+where $\hat{v_a}$ represents the median over the values in $v_a$ and $MAD(v_a$) refers to the 
+median absolute deviation. This is a standard outlier detection test, namely the Hampel identifier. 
+\footnote{Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation 
+for a normal distribution.} If the value for a numerical attribute in a test file 
+falls outside of this interval, a warning is printed to the user indicating the violating value, 
+the attribute, and the upper or lower Hampel threshold.
+
+The intuition for this test is that if the user has input a value that falls outside of an 
+interval containing values that are considered "normal" over the entire data set, 
+that value will probably cause an error, in particular for performance. We cannot know for sure
+if this value will cause an issue. For instance, a user might have a machine with 
+particularly high-end hardware, in which case a value beyond the upper Hampel threshold may be appropriate.

### 2016-05-08 OSDI/intro.tex

@@
 today's software system failures~\cite{xu15systems, yin11anempirical}.
-For example, Yin {\em et al.}~\cite{yin11anempirical} reveal
-that about 31\% system failures were caused by misconfiguration problems. 
+For example, Yin {\em et al.}~\cite{yin11anempirical} report
+that about 31\% system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code. 
 Misconfigurations, in practice, may result in various
@@
 su07autobash, whitaker04configuration},
-offering automatic verification to configuration files -- like what we
+
+Ruzica!!!!
+
+they are still not on the level of
+automatic verification o
+
+to configuration files -- like what we
 did for verifying regular programs -- is still highly

### 2016-05-08 OSDI/intro.tex
start

@@
 su07autobash, whitaker04configuration},
+those tools mainly try to understand {\emph{what}} caused the error ---
+they are still not on a level of
+automatic verification tools used for regular program 
+verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15}.
+Nevertheless, automated verification of configuration 
+files would be highly
+desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
+Two main obstacles why we cannot simply apply the existing automatic 
+tools and techniques to verification of configuration files are: 1) a lack
+of a specification which would describe properties of configuration files, and 2) a program structure of configuration files -- they
+are mainly a sequence of entries assigning some value to system variables. The language in which configuration files are written does 
+not adhere to a specific grammar or syntax. In particular,  the
+entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries and there
+is no explicit structure policy for the entries.
 
-Ruzica!!!!
-
-they are still not on the level of
-automatic verification o
-
-to configuration files -- like what we
-did for verifying regular programs -- is still highly
-desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
-Nevertheless, the main obstacles to the automatic 
-configuration verification are:
-1) entries in configuration files are untyped entries, 2) there
-is no explicit structure policy for the entries in configuration
-files, and 3) there are surprisingly few rules specifying the
-entries' constraints.
-
-In order to overcome these obstacles,
+In order to overcome all these obstacles,
 researchers have proposed 

### 2016-05-08 OSDI/rel.tex
improve some grammar

@@
 
-Providing language support has been considered as a promising means
-of tackling configuration problems~\cite{xu15systems}.
-Nevertheless, practical language-based misconfiguration
+Providing language support has been considered a promising way  
+to tackle configuration problems~\cite{xu15systems}.
+Nevertheless, a practical language-based misconfiguration
 detection approach still remains an open problem.
@@
 \para{Configuration languages.}
-There have been several language-support efforts proposed to prevent
+There have been several language-support efforts proposed for preventing
 configuration errors introduced by fundamental deficiencies in
-either untyped or low-level languages. For example, in network
+either untyped or low-level languages. For example, in the network
 configuration management area, it is easy for administrators to

### 2016-05-08 OSDI/rel.tex
more corrections

@@
 
-Providing language support has been considered a promising way  
+Language support has been considered a promising way  
 to tackle configuration problems~\cite{xu15systems}.
@@
 COOLAID~\cite{chen10declarative} constructs
-a language to describe domain knowledge about network devices and
-services to convenient network reasoning and management.
+a language to describe domain knowledge about devices and
+services for convenient network reasoning and management.
 
@@
 \para{Misconfiguration detection.}
-Misconfiguration detection techniques aim at checking the configuration
-efforts before the system outages occur.
-Most of existing detection approaches check 
+Misconfiguration detection techniques aim at checking configuration
+efforts before system outages occur.
+Most existing detection approaches check 
 the configuration files against a set of predefined correctness 
-rules, named constraints, and then report the errors if 
+rules, named constraints, and then report errors if 
 the checked configuration files do not satisfy these rules.
@@
 also have been proposed~\cite{yuan11context, zhang14encore}.
-EnCore~\cite{zhang14encore} is the most close work to \app.
+EnCore~\cite{zhang14encore} is the work closest to \app.
 It introduces a template-based
@@
 The learning process is guided by a set of predefined rule templates
-that enforce learning to focus on patterns of interests.
-By this way, EnCore filters out irrelevant information and reduces
-the false positives; moreover, the templates are able to express
+that enforce learning to focus on patterns of interest.
+In this way, EnCore filters out irrelevant information and reduces
+false positives; moreover, the templates are able to express
 system environment information that other machine learning
 techniques cannot handle.
-Compared with EnCore, \app has the following advantages.
-First, \app does not rely on whether the files in given configuration set 
-are 100\% correct. Second, \app not only can cover much more types of 
+Compared to EnCore, \app has the following advantages.
+Firstly, \app does not rely on 100\% correctness in the files of the given configuration set. 
+Secondly, \app not only can cover much more types of 
 misconfigurations, but also introduces probabilistic type.
@@
 executes processes and tracks causality to automatically fix 
-misconfigurations. Different from \app, most of misconfiguration
+eisconfigurations. Different from \app, most of misconfiguration
 diagnosis efforts aim at finding out errors after the system

### 2016-05-08 OSDI/concl.tex
some more grammar

@@
 
-In this paper, we introduce \app, a highly-modular framework 
+In this paper, we introduce \app, a highly modular framework 
 that allows verification of configuration files, 

### 2016-05-08 OSDI/rel.tex
some more grammar

@@
 language, ConfValley, to validate 
-whether given configuration files meet administrators' 
-``belief'' in mind. Different from \app, ConfValley itself does not
+whether given configuration files meet administrators' specifications. 
+Different from \app, ConfValley does not
 have inherent misconfiguration checking capability, since it only offers
-a language representation. In addition, administrators have to
-manually write specifications with ConfValley, which is an error-prone
-process; on the contrary, \app does not need users to manually
+a language representation and requires administrators to
+manually write specifications, which is an error-prone
+process. On the contrary, \app does not need users to manually
 write anything.
@@
 Firstly, \app does not rely on 100\% correctness in the files of the given configuration set. 
-Secondly, \app not only can cover much more types of 
-misconfigurations, but also introduces probabilistic type.
-Finally, \app is a language framework, which could 
+Secondly, \app not only covers many more types of 
+misconfigurations, but also introduces probabilistic types.
+Finally, \app is a language framework, which can 
 even be used to write configuration files, but EnCore is only a 
@@
 executes processes and tracks causality to automatically fix 
-eisconfigurations. Different from \app, most of misconfiguration
-diagnosis efforts aim at finding out errors after the system
-failures occur, which typically lead to prolonged recover time.
+misconfigurations. Different from \app, most misconfiguration
+diagnosis efforts aim at finding errors after system
+failures occur, which typically leads to prolonged recovery time.
 
@@
 Our work belongs to the latter case, which is used to 
-prevent configuration errors before the system failures occur.
+prevent configuration errors before system failures occur.

### 2016-05-08 OSDI/rel.tex
slight changes

@@
 \para{Configuration languages.}
-There have been several language-support efforts proposed for preventing
+There have been several language support efforts proposed for preventing
 configuration errors introduced by fundamental deficiencies in
@@
 
-Huang {\em et al.}~\cite{huang15confvalley} proposed a specification 
+Huang {\em et al.}~\cite{huang15confvalley} proposed a 
 language, ConfValley, to validate 
@@
 executes processes and tracks causality to automatically fix 
-misconfigurations. Different from \app, most misconfiguration
+misconfigurations. Unlike \app, most misconfiguration
 diagnosis efforts aim at finding errors after system
@@
 extract configuration parameter constraints from source code and generates 
-misconfigurations to test whether systems can tolerate the potential
+misconfigurations to test whether systems can tolerate potential
 configuration errors.

### 2016-05-08 OSDI/abs.tex
better abstract

@@
 System failures resulting from configuration errors 
-have become the major causes affecting the availability and
+are major reasons for compromised availability and
 reliability of today's software systems.
-Although many misconfiguration handling techniques,
-\eg, misconfiguration checking, troubleshooting and repair, 
+Although many misconfiguration handling techniques
+such as checking, troubleshooting, and repair, 
 have been proposed, 
-offering automatic verification for configuration files -- like
-what we did to regular programs -- is still an open problem.
+offering automatic verification for configuration files -- as often  
+done for regular programs -- is still an open problem.
 This is because software configurations are typically written in
@@
 
-This paper presents, \app, the first automatic verification framework for
+This paper presents \app, the first automatic verification framework for
 general software configurations.
 \app verifies a target configuration file $F$ through three steps.
-First, \app analyzes a dataset containing many sample configuration 
+Firstly, \app analyzes a dataset containing many sample configuration 
 files belonging to the same system as $F$,
-and translates these sample files to a
+translating these sample files to a
 well-structured and probabilistically-typed 
 intermediate representation.
-Second, \app derives rules and constraints by analyzing
+Secondly, \app derives rules and constraints by analyzing
 this intermediate representation, thus building a
-language model.
+sophisticated language model.
 Finally, \app uses the resulting language model to verify $F$.

### 2016-05-08 OSDI/abs.tex
some commas

@@
 Although many misconfiguration handling techniques
-such as checking, troubleshooting, and repair, 
+such as checking, troubleshooting, and repair
 have been proposed, 
@@
 \app framework is highly modular, 
-does not rely on the system source code or templates and
+does not rely on the system source code or templates, and
 can be applied to any new configuration file type with minimal user input.

### 2016-05-08 OSDI/intro.tex
improve intro tiny bit

@@
 While many efforts have been proposed 
-to check, troubleshoot, diagnose and repair configuration errors%
+to check, troubleshoot, diagnose, and repair configuration errors%
 ~\cite{attariyan10automating,
@@
 those tools mainly try to understand {\emph{what}} caused the error ---
-they are still not on a level of
+they are still not on the level of
 automatic verification tools used for regular program 

### 2016-05-08 OSDI/intro.tex
little correction

@@
 
-In order to overcome all these obstacles,
+In order to overcome these obstacles,
 researchers have proposed 
-statistical analysis and learning based approaches%
+statistical analysis and learning-based approaches%
 ~\cite{wang04automatic, zhang14encore, yuan11context}. 
@@
 framework, \app, that can learn a language model from an example set of 
-correct configuration files, and then uses this language model to verify 
-interested configuration files.
+correct configuration files, and then use this language model to verify 
+configuration files of interest.
 

### 2016-05-08 OSDI/intro.tex
better wording

@@
 desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
-Two main obstacles why we cannot simply apply the existing automatic 
-tools and techniques to verification of configuration files are: 1) a lack
-of a specification which would describe properties of configuration files, and 2) a program structure of configuration files -- they
-are mainly a sequence of entries assigning some value to system variables. The language in which configuration files are written does 
+We cannot simply apply existing automatic 
+tools and techniques to verification of configuration files for two main reasons: 1) a lack
+of a specification for describing properties of configuration files and 2) a lack of a program structure for configuration files -- they
+are mainly sequences of entries assigning some values to system variables. The language in which configuration files are written does 
 not adhere to a specific grammar or syntax. In particular,  the

### 2016-05-08 OSDI/intro.tex
better wording

@@
 ~\cite{wang04automatic, zhang14encore, yuan11context}. 
-These efforts build checking policies by learning a sample 
+These efforts build checking policies by learning from a sample 
 data set, rather than explicitly specifying entries' types or rules.
 In particular, for each entry in a certain configuration file, 
-if it deviates from the common values used in a large collection
-of configurations (\ie, the data set for training), it is typically
-suspected as a potential configuration error.
+if it deviates from common values used in a large collection
+of configuration files (\ie, the data set for training), it is typically
+suspected to contain a potential configuration error.
 However, because these learning 
 efforts {\em either} are limited to simplistic 
-configuration errors (\eg, type errors and syntax errors), 
+configuration errors (\eg, type errors and syntax errors)
 {\em or} heavily rely on template-based inference~\cite{zhang14encore}, 
 many sophisticated configuration errors, 
-\eg, hard to be templated in practice, cannot be detected.
+which are difficult to template in practice, cannot be detected.
 For example, if {\tt extension = mysql.so} appears 
-before {\tt extension = recode.so} in PHP configuration file,  
+before {\tt extension = recode.so} in a PHP configuration file,  
 it would lead to a crash error, since the correct ordering 
@@
 however, such an error cannot be detected by existing
-learning efforts, since it is hard to build a template for this
-error~\cite{xu15systems}.
+learning efforts, since it is hard to build a corresponding template ~\cite{xu15systems}.
 

### 2016-05-08 OSDI/intro.tex
more comments

@@
 tricky configuration errors), and then check the configuration files
-of interest through the learned language model.
+of interest through the learned language model. \jon{Too many parentheses in setence. Cut down}
 
@@
 for general software configurations.
-In particular, \app's workflow to verifying a given configuration file
-could be looked as a three-step methodology.
-First, \app analyzes a dataset containing sample configuration files,
+In particular, \app's workflow for verifying a given configuration file
+can be viewed as a three-step methodology.
+Firstly, \app analyzes a dataset containing sample configuration files,
 thus generating a well-structured and probabilistically-typed 
 intermediate representation.
-Second, \app derives rules and constraints by analyzing
+Secondly, \app derives rules and constraints by analyzing
 the intermediate representations, thus building a language model.
@@
 Compared with previous efforts,
-\app does not necessarily rely on users' templates, 
-and is capable of detecting more tricky configuration errors that
+\app does not necessarily rely on users' templates 
+and is capable of detecting tricky configuration errors that
 cannot be identified by existing work (details in $\S$\ref{sec-motiv}).
@@
 configuration files, nevertheless, requires addressing several challenges. 
-First, in order to formulate a correct language model, 
-we need to infer each entry's type in a given configuration file;
-however, the type of a variable cannot always be fully determined 
+Firstly, in order to formulate a correct language model, 
+we need to infer each entry's type in a given configuration file, but 
+the type of a variable cannot always be fully determined 
 from a single value. 
@@
 an integer rather than string; however, existing type inference 
-work would report this is an error, because foo should be assigned
-an integer~\cite{zhang14encore}. We address this problem by introducing 
+work would report this is an error, because {\tt foo} should be assigned
+an integer~\cite{zhang14encore}. \jon{Unclear what the error is. Be more precise} We address this problem by introducing 
 so called {\emph{probabilistic types}}.

### 2016-05-08 OSDI/abs.tex
better

@@
 including ordering errors, fine-grained value correlation errors, 
-entry missing errors, and environment related errors. 
+entry missing errors, and environment-related errors. 
 %Our tool, named \app, relies on an abstract representation of language 

### 2016-05-08 OSDI/intro.tex
some comments
better

@@
 tricky configuration errors), and then check the configuration files
-of interest through the learned language model. \jon{Too many parentheses in setence. Cut down}
+of interest through the learned language model. \jon{Too many parentheses in sentence. Cut down}
 
@@
 an integer~\cite{zhang14encore}. \jon{Unclear what the error is. Be more precise} We address this problem by introducing 
-so called {\emph{probabilistic types}}.
+{\emph{probabilistic types}}.
 Rather than assigning only one variable to a single type, 
@@
 
-Second, without template, how to learn rules and constraints present
-a difficult. \ennan{Here, we need to add one-paragraph description 
+Secondly, without templates, learning rules and constraints is a challenge. 
+\ennan{Here, we need to add one-paragraph description 
 to illustrate how we learn rules without templates, 
@@
 class of rules that \app is not currently learning, the user can develop
-their own templates and learners for that class. The new learner can be
-added to \app and this way it can check additionally a new set of
+her own templates and learners for that class. The new learner can be
+added to \app and this way it can check an additional new set of
 errors.
@@
 Our \app prototype still has a few limitations:
-for example, we cannot handle configuration errors that can be only
-triggered in system execution time.
+for example, we cannot handle configuration errors that can be 
+triggered during system execution time.
 Nevertheless, we believe \app may suggest a practical path
@@
 \item \app employs a collection of machine learning algorithms to 
-enable powerful rule and constraint inference without the assistance 
+enable powerful rule and constraint inference without assistance 
 from any pre-defined templates.
@@
 including ordering errors, fine-grained value correlation errors, 
-entry missing errors, and environment related errors.
+entry missing errors, and environment-related errors.
 

### 2016-05-08 OSDI/arch.tex
hyphens

@@
 the learner needs a template DB to provide environment information,
-thus detecting system environment related configuration errors.
+thus detecting system environment-related configuration errors.
 

### 2016-05-08 OSDI/motiv.tex
hyphens
better motiv

@@
 extracted from real-world examples. 
-The reason we call them tricky is
+The reason we call them tricky is that
 most of existing efforts, \eg, learning-based checking
@@
 On the other hand, we also investigated 
-many misconfiguration problems in practice were caused by 
+many misconfiguration problems in practice which were caused by 
 these tricky configuration errors, \eg, reported by Stack Overflow.
@@
 
-This user complained his MySQL's load is very high and the website's
-respond speed is very slow.
+This user complained that his MySQL's load was very high and the website's
+respond speed was very slow.
 In this case, {\tt key\_buffer\_size} is used by all the threads
@@
 should be {\tt datadir=/appfinder/mysql}.
-Such an error is called system environment related configuration error.
+Such an error is called system environment-related configuration error.
 Both \app and EnCore can handle system execution related

### 2016-05-08 OSDI/motiv.tex
better motiv

@@
 is crucial. 
-We call the above example misconfiguration situation 
-as {\em ordering errors}.
+We call the above example misconfiguration 
+an {\em ordering error}.
 Yin {\em et al.} find that ordering errors widely exist in
@@
 In particular, \app is able to inform the user that {\tt recode.so} 
-should appear before {\tt mysql.so}, and reports the error (as shown
+should appear before {\tt mysql.so} and reports the error (as shown
 below).
@@
 In this case, {\tt key\_buffer\_size} is used by all the threads
-cooperatively while {\tt join\_buffer} and {\tt sort\_buffer} are 
+cooperatively, while {\tt join\_buffer} and {\tt sort\_buffer} are 
 created by each thread for private use; thus, the maximum amount
@@
 
-We call the above situation as a {\em fine-grained value correlation
+We call the above situation a {\em fine-grained value correlation
 error}, which is a more challenging case than 
@@
 correlation case, 
-none of existing efforts can detect the fine-grained value correlation
+no existing effort can detect fine-grained value correlation
 errors, which ``hides'' an equation-aware correlation, as shown in
@@
 As mentioned by Xu {\em et al.}~\cite{xu15hey},
-detecting the fine-grained value correlation errors 
-present a much more challenging
-task than normal value correlation problems.
+detecting fine-grained value correlation errors 
+is a much more challenging
+task than the normal value correlation problems.
 

### 2016-05-08 OSDI/motiv.tex
better motiv

@@
 The reason we call them tricky is that
-most of existing efforts, \eg, learning-based checking
+most existing efforts, \eg, learning-based checking
 efforts~\cite{zhang14encore, wang04automatic}, cannot detect
@@
 Clearly, in the above example, it does not hold, 
-so that this misconfiguration causes MySQL loads very slow.
+so this misconfiguration causes MySQL to load very slowly.
 

### 2016-05-08 OSDI/motiv.tex
better motiv

@@
 no existing effort can detect fine-grained value correlation
-errors, which ``hides'' an equation-aware correlation, as shown in
+errors, which ``hide'' equation-aware correlations, as shown in
 the above example.
@@
 is a much more challenging
-task than the normal value correlation problems.
+task than the normal value correlation problem.
 
 To the best of our knowledge, \app is the first effort that
-is able to check such fine-grained value correlation problem.
+is able to check such fine-grained value correlation problems.
 If we run \app on this configuration file, \app  would return:
@@
 
-Note that existing effort, EnCore, aims to detect value correlation 
+\jon{The following paragraph is repetitive, same as the one two above -- just remove it?}
+Note that an existing effort, EnCore, aims to detect value correlation 
 errors. However, different from \app, EnCore can only detect simple
-correlation, \eg, {\tt mysql.max\_persistent} < {\tt max\_connections},
+correlations, \eg, {\tt mysql.max\_persistent} < {\tt max\_connections},
 rather than the fine-grained computation-based value correlation,
@@
 \para{Example~3: Entry missing errors.} 
-Many critical system outages result from the fact that important
+Many critical system outages result from the fact that an important
 entry was missing in the configuration file. 
@@
 In a public misconfiguration dataset~\cite{configdataset},
-the major problems of MySQL failure reports were caused by
+many MySQL failure reports were caused by
 entry missing errors.

### 2016-05-08 CAV/evaluation.tex

@@
 This typeclass defines the three functions that each set of rules must implement to work with our system.
+The core learning algorithm is simply a fold using \lstinline{merge} over the derived rules from running \lstinline{learn} on each file in the learning set.
+
 Typeclasses and other features of Haskell means that our system consists of only 267 lines of code, with another 233 for the rule modules.
@@
 Although this is sufficient for most use cases, more fine-grained relations could be encoded with SMT formulas then passed to a solver.
+
+The tool is available for download at \url{marksantolucito.com/cavae.html}.
 
@@
 We fail one benchmark in Value Relations because we do not yet support relations between file sizes of different units (Mb to Kb).
-In one Keyword Ordering benchmark, \app reports a type error on the value of interest instead of a ordering error.
+In one Keyword Ordering benchmark, \app reports a type error on the value of interest instead of an ordering error.
 This is a result of our context embedding in the translation to the intermediate representation - reordering the value puts it in a new context where the type is now also incorrect.

### 2016-05-08 CAV/related.tex

--- 2016-05-01 OSDI/concl.tex
@@
-\section{Conclusion}
+\section{Conclusions}
 
-In this paper, we introduce \app, a highly-modular framework 
-that allows verification of configuration files, 
-even without a language model of the file.
-New verification properties require only a small amount of code 
-and are not language specific, 
-all indicating that \app could be widely adopted by system administrators.
-Such a verification tool that scales in both performance and expressivity 
-can revolutionize configuration file checking, 
-reducing the cost of system maintenance and failure dramatically.
+In this paper, we introduce \app, a highly-modular framework that allows verification of configuration files, even without a language model of the file.
+New verification properties require only a small amount of code and are not language specific, all indicating that \app could be widely adopted by system administrators.
+Such a verification tool that scales in both performance and expressivity can revolutionize configuration file checking, reducing the cost of system maintenance and failure dramatically.
+
+The field of verification must guarantee the reliability entire systems, and 31\% of all system failures are caused by misconfiguration, while only 20\% are caused by program bugs ~\cite{xu13do}.
+We hope \app can be  a catalyst to spark interest in the potential impact of verification for configuration files.

### 2016-05-08 OSDI/motiv.tex
grammar for entry missing

@@
 entry was missing in the configuration file. 
-We call such a problem as {\em entry missing error}.
+We call such a problem an {\em entry missing error}.
 In a public misconfiguration dataset~\cite{configdataset},
 many MySQL failure reports were caused by
-entry missing errors.
+missing entry error.
 Below is a real-world entry missing error example~\cite{yin11anempirical},

### 2016-05-08 OSDI/motiv.tex
better wording

@@
 many MySQL failure reports were caused by
-missing entry error.
-Below is a real-world entry missing error example~\cite{yin11anempirical},
+missing entry errors.
+Below is a real-world entry missing error example~\cite{yin11anempirical}:
 when a user wants to use OpenLDAP to enable her directory access
@@
 users have to first include the related schema.
-Leaving out the ``include'' entry, 
-which have been left by many users~\cite{yin11anempirical}, 
-will cause the failure of this LDAP. 
+Leaving out the {\tt include} entry, 
+which has been left out by many users~\cite{yin11anempirical}, 
+will cause failure of this LDAP. 
 If this user has \app, she can run \app on such a misconfiguration file,

### 2016-05-08 OSDI/motiv.tex
better motiv

@@
 will cause failure of this LDAP. 
-If this user has \app, she can run \app on such a misconfiguration file,
+The user can run \app on such a misconfiguration file,
 and \app would return:
@@
 CODE~\cite{yuan11context}.
-For a configuration error reported recently made MySQL
-daemon failed to start~\cite{syserror}.
+A configuration error reported recently made MySQL
+daemon fail to start~\cite{syserror}.
 One entry in a MySQL configuration file is written as 

### 2016-05-08 OSDI/motiv.tex
better motiv

@@
 CODE~\cite{yuan11context}.
-A configuration error reported recently made MySQL
+A configuration error reported recently made the MySQL
 daemon fail to start~\cite{syserror}.
-One entry in a MySQL configuration file is written as 
-{\tt datadir=/root/appfinder/mysql}, and the type as well as 
-format seem to be correct.
-However, the problem is this directory should not be
-initiated as a root directory, and the correct entry
+One entry was written as 
+{\tt datadir=/root/appfinder/mysql}, and the type, as well as 
+format, seemed correct.
+However, the problem is that this directory should not 
+contain the root directory; the correct entry
 should be {\tt datadir=/appfinder/mysql}.
-Such an error is called system environment-related configuration error.
-Both \app and EnCore can handle system execution related
-misconfiguration problems.
+Such an error is called a system environment-related configuration error.
+Both \app and EnCore can handle misconfigurations concerning system execution.
 Furthermore, \app is also able to detect type errors and syntax errors

### 2016-05-08 OSDI/arch.tex
better arch

@@
 In particular, \app can solve many sophisticated 
-configuration errors (\eg, ordering errors, missing entry errors 
+configuration errors (\eg, ordering errors, missing entry errors,
 and fine-grained value correlation) that previous efforts cannot 
@@
 a typical \app verification workflow has three steps:
-translation, learning and checking. In this section, we briefly
+translation, learning, and checking. In this section, we briefly
 describe how does each step work.
@@
 We address this problem 
-by introducing so called {\em probabilistic types}.
+by introducing {\em probabilistic types}.
 Rather than giving a variable a single type, 
-we assign several types with their probability distributions. 
+we assign several types over a probability distribution. 
 We can later use these more structured files

### 2016-05-08 OSDI/arch.tex
better arch

@@
 \para{Learning.}
-The input of learner is a set of files that have been translated
+The input of the learner is a set of files that have been translated
 into well-structured and typed representations.
@@
 By combining the translated representations and the learned
-rules together, we already build a language model for
+rules together, we build a language model for
 configuration verifications.
@@
 ~\cite{yin11anempirical, configdataset}. 
-Each class is looked as an error-pattern 
+Each class can be viewed as an error-pattern 
 that \app should handle: we consider integer constraints, 
@@
 Although the learner does necessarily rely on templates,
-\app still offers a database to contain many templates,
+\app still offers a database containing many templates,
 as shown in Figure~\ref{fig-overview}.
@@
 specific system executional environment information.
-It is widely known that any existing learning algorithm cannot
-derive rules checking environment violation, \eg,
-whether current account is the owner of a certain path.
-In order to deal with comprehensive misconfiguration problems,
+A learning algorithm cannot derive rules related to environment violations, \eg,
+whether the current account is the owner of a certain path, without information 
+about the environment. In order to deal with comprehensive misconfiguration problems,
 the learner needs a template DB to provide environment information,
@@
 \para{Checking.}
-The checker is used to detect the rule violations in the configuration
-files of interest. The inputs of checker are the learned rules 
+The checker is used to detect rule violations in the configuration
+files of interest. The inputs of the checker are the learned rules 
 and the target configuration file to verify.
-Its outputs a report (as shown in $\S$\ref{sec-motiv}) about 
+It outputs a report (as shown in $\S$\ref{sec-motiv}) about 
 whether it finds any error, \eg, rule violations, or a suspicious value.

### 2016-05-08 CAV/evaluation.tex
config: cav paper

@@
 
+\para{Implementation.}
 \app is implemented in Haskell and takes full advantage of its polymorphism to make the system more modular.
@@
 
-The integer relation rule has an unusual implementation that makes use of function as first-class objects in Haskell.
+The integer relation rule has an unusual implementation that uses function as first-class objects in Haskell.
 Rather than associated keywords with SMT formula, we directly associate them with a function of type (\lstinline{Int->Int->Bool}).
-Since we need to compare rules over equality, we must then have a way to compare functions.
+Since we need to compare rules over equality, we must have a way to compare functions.
 This limits the types of functions we use to \lstinline{(==),(>=),(<=)}.
-Although this is sufficient for most use cases, more fine-grained relations could be encoded with SMT formulas then passed to a solver.
+Although this is sufficient for most cases, more fine-grained relations could be encoded with SMT formulas then passed to a solver.
 
@@
 
-\subsection{Evaluation}
-
+\para{Evaluation.}
 To evaluate our tool, we take a subset of 20 benchmarks from an
@@
 \label{table:res}
-\begin{tabular}{l|l|l}
-Error Type       & Passing Tests & False Positives  \\ \hhline{=|=|=}
+\begin{tabular}{|l|l|l|}
+\hline
+Error Type       & Passing Tests & False Positives  \\ 
+\hline
+\hline
 Missing Entry    & 5/5           & 1, 0, 0, 0, 4        \\ \hline
@@
 Value Relations  & 4/5           & 0, 0, 0, 1, 0        \\ 
+\hline
 \end{tabular}
 \end{table}
-%\vspace{-5em}
 

### 2016-05-08 CAV/intro1.tex
?
config: cav paper

@@
 model for configuration files. 
+There is no universal definition of a "configuration file".
+In general, most configuration files tend to be a series of assignment to system variables.
+Configuration files generally do not have more complicated language constructs, lest they become a setup script.
 
+{
+\setlength{\floatsep}{-10pt}
+\setlength{\abovecaptionskip}{-.5pt}
+\setlength{\belowcaptionskip}{-14pt}
 \begin{figure}[t] \centering
-\includegraphics[width=0.63\textwidth]{figs/overview}
+\includegraphics[width=0.6\textwidth]{figs/overview}
 \caption{{\footnotesize \app's workflow. The green boxes represent configuration files,
@@
 \end{figure}
+}
 
@@
 When running type inference on a configuration file, the type of a variable cannot always be fully determined from a single value.
-We address this problem by introducing so called {\emph{probabalistic types}}.
+We address this problem by introducing so called {\emph{probabilistic types}}.
 Rather than giving a variable a single type, we assign several types with their probability distributions. 
@@
 
-To summarize, this tool paper makes the following contributions:
-
-\begin{enumerate}
-
-  \item We designed and implemented a tool, \app, that can learn a
+To summarize, this tool paper makes the following contributions.
+First, we designed and implemented a tool, \app, that can learn a
 language model from an example set of correct configuration files, and
 we use the model to verify new configuration files.
-  \item We use probabilistic types to assign a confidence distribution over a set of types to a value.
-  \item In \app we define a interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.
-
-\end{enumerate}
+Second, we use probabilistic types to assign a confidence distribution over a set of types to a value.
+Finally, in \app we define a interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.

### 2016-05-08 CAV/system.tex
config: cav paper

@@
 With typed keyword-value pairs, we can run each learning module independent of each other.
-We learn a set of rules over a every file, then merge the rules of all files.
+We learn a set of rules over every file, then merge them.
 
-{\bf {Introducing the types.}} Based only on a single example value of $v$ we cannot fully determine the type of $k$.
+\para{Introducing the types.} 
+Based only on a single example value of $v$ we cannot fully determine the type of $k$.
 Consider for instance the following example:\\
@@
 
-{\bf {Rule Learning.}} With every type we associate a set of templates, specific to this type.
+\para{Rule Learning.} 
+With every type we associate a set of templates, specific to this type.
 Once the input files are fully type-annotated, we generate rules that are instances of these templates.

### 2016-05-08 OSDI/intro.tex
start

@@
 today's software system failures~\cite{xu15systems, yin11anempirical}.
-For example, Yin {\em et al.}~\cite{yin11anempirical} report
+In their empirical study Yin {\em et al.}~\cite{yin11anempirical} report
 that about 31\% system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code. 
@@
 While many efforts have been proposed 
-to check, troubleshoot, diagnose, and repair configuration errors%
+to check, troubleshoot, diagnose and repair configuration errors%
 ~\cite{attariyan10automating,
@@
 those tools mainly try to understand {\emph{what}} caused the error ---
-they are still not on the level of
+they are still not on a level of
 automatic verification tools used for regular program 
-verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15}.
-Nevertheless, automated verification of configuration 
-files would be highly
-desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
-We cannot simply apply existing automatic 
-tools and techniques to verification of configuration files for two main reasons: 1) a lack
-of a specification for describing properties of configuration files and 2) a lack of a program structure for configuration files -- they
-are mainly sequences of entries assigning some values to system variables. The language in which configuration files are written does 
+verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
+detect errors without executing the code.
+Two main obstacles why we cannot simply apply the existing automatic 
+tools and techniques to verification of configuration files are: 1) a lack
+of a specification which would describe properties of configuration files, and 2) a program structure of configuration files -- they
+are mainly a sequence of entries assigning some value to system variables. The language in which configuration files are written does 
 not adhere to a specific grammar or syntax. In particular, the
@@
 is no explicit structure policy for the entries.
+Nevertheless, automated verification of configuration 
+files, that could detect would be highly
+desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
 

### 2016-05-08 OSDI/eval.tex
config: eval

@@
 We mainly conduct three parts of experiments to evaluate our \app
-prototype.
-
-We want to answer several questions:
+prototype. We want to answer several questions:
 
@@
 and whether \app correctly reports the issues.}
+
+\begin{table*}[t]
+\centering
+\caption{Sampled benchmarks for misconfiguration detection}
+\label{table-casestudy}
+\begin{tabular}{|l|l|l|l|}
+\hline
+{\bf ID} & {\bf Problem Description} & {\bf Error Type} & 
+{\bf \app Report}  \\ 
+\hline
+\hline
+1 & How to configure MySql master slave to  
+& Type Error 
+& Expected a Filepath with P=1.0 \\ & backup master to slave & 
+& for log-bin[mysqld] \\ \hline
+
+2 & data import from MySql dies when MySQL  
+& Correlation 
+& Expected thread\_cache\_size[mysqld] > \\ & query limit is removed 
+& & innodb\_buffer\_pool\_size \\ \hline
+
+\end{tabular}
+\end{table*}
 

### 2016-05-09 OSDI/motiv.tex
more concise
better wording for first part

@@
 efforts~\cite{zhang14encore, wang04automatic}, cannot detect
-these configuration errors.
-On the other hand, we also investigated 
+these configuration errors. We investigated 
 many misconfiguration problems in practice which were caused by 
-these tricky configuration errors, \eg, reported by Stack Overflow.
+these tricky configuration errors, such as those reported on StackOverflow.
 
@@
 
-\ennan{Example~4: This should be the singular value error.
+\para{Example~4: Singular Value Errors} 
+This should be the singular value error.
 We need an example from Stack Overflow to illustrate the 
@@
 Both \app and EnCore can handle misconfigurations concerning system execution.
-Furthermore, \app is also able to detect type errors and syntax errors
+Furthermore, \app is also able to detect type and syntax errors
 in configuration files.

### 2016-05-09 OSDI/motiv.tex
better wording for last part
better wording for Example 1

@@
 \para{Example~1: Ordering errors.} 
-The first example configuration error is first reported by 
+The first class of configuration errors we handle was first reported by 
 Yin {\em et al.}~\cite{yin11anempirical}.
 For instance, when a user configures PHP to run with the
-Apache HTTP Server, this user may write, among others, 
+Apache HTTP Server, this user might write, amongst others, 
 the following lines in the configuration file.
@@
 
-If this user is using \app, she can avoid such a configuration error.
+By using \app, the user can avoid such a configuration error.
 In particular, \app is able to inform the user that {\tt recode.so} 
-should appear before {\tt mysql.so} and reports the error (as shown
-below).
+should appear before {\tt mysql.so}, as shown
+below.
 
@@
 CODE~\cite{yuan11context}.
-A configuration error reported recently made the MySQL
+A recently reported configuration error made the MySQL
 daemon fail to start~\cite{syserror}.

### 2016-05-09 OSDI/motiv.tex
better wording

@@
 In a real-world misconfiguration example~\cite{correlation}, 
-a user configures his MySQL as the following:
+a user configures his MySQL as the following.
 
@@
 
-This user complained that his MySQL's load was very high and the website's
-respond speed was very slow.
+This user complained that her MySQL load was very high, causing the website's
+respond speed to be very slow.
 In this case, {\tt key\_buffer\_size} is used by all the threads
@@
 
-\jon{The following paragraph is repetitive, same as the one two above -- just remove it?}
+\jon{The following paragraph is repetitive, same as the above -- already mentioned
+this exact error for EnCore -- just remove it?}
 Note that an existing effort, EnCore, aims to detect value correlation 
@@
 protocol, she needs to use the password policy overlay. This is usually
-done through the following entries in the OpenLDAP configuration file:
+achieved via the following entries in the OpenLDAP configuration file:
 
@@
 Leaving out the {\tt include} entry, 
-which has been left out by many users~\cite{yin11anempirical}, 
+as done by many users~\cite{yin11anempirical}, 
 will cause failure of this LDAP. 

### 2016-05-09 OSDI/arch.tex
a comma
a little progress

@@
 configuration errors (\eg, ordering errors, missing entry errors,
-and fine-grained value correlation) that previous efforts cannot 
+and fine-grained value correlation errors) that previous efforts cannot 
 detect. As depicted in Figure~\ref{fig-overview}, 
@@
 translation, learning, and checking. In this section, we briefly
-describe how does each step work.
+describe how each step works.
 
@@
 It outputs a report (as shown in $\S$\ref{sec-motiv}) about 
-whether it finds any error, \eg, rule violations, or a suspicious value.
+whether it finds any error, \eg, rule violations or a suspicious value.
 As shown in Figure~\ref{fig-overview},

### 2016-05-09 OSDI/intro.tex
intro

@@
 
-In order to overcome these obstacles,
-researchers have proposed 
-statistical analysis and learning-based approaches%
-~\cite{wang04automatic, zhang14encore, yuan11context}. 
-These efforts build checking policies by learning from a sample 
-data set, rather than explicitly specifying entries' types or rules.
-In particular, for each entry in a certain configuration file, 
-if it deviates from common values used in a large collection
-of configuration files (\ie, the data set for training), it is typically
-suspected to contain a potential configuration error.
-However, because these learning 
-efforts {\em either} are limited to simplistic 
-configuration errors (\eg, type errors and syntax errors)
-{\em or} heavily rely on template-based inference~\cite{zhang14encore}, 
-many sophisticated configuration errors, 
-which are difficult to template in practice, cannot be detected.
-For example, if {\tt extension = mysql.so} appears 
-before {\tt extension = recode.so} in a PHP configuration file,  
-it would lead to a crash error, since the correct ordering 
+To overcome these obstacles, researchers have proposed approaches based on
+a statistical analysis and learning~\cite{wang04automatic, zhang14encore, yuan11context}
+that try to infer the rules and policies how configuration files are constructed.
+Rather than explicitly specifying entries' types or rules, these research directions are focused
+on learning policies from a sample data set.
+The learned rules are usually constructed along the following pattern: for every entry in a configuration file, 
+we check if it deviates from a ``typical'' value, \ie a value computed from a large training set consisting of configuration files.
+If the entry is significantly different that the typical value, we suspect that it could be a potential configuration error.
+The downside of this approach is that these learning efforts are limited to simplistic 
+configuration errors, such as type errors and syntax errors, or they 
+heavily rely on template-based inference~\cite{zhang14encore}. As we pointed out earlier, since configuration files are not written in a typed language with a fixed syntax,
+type errors and syntax errors are relatively rare and easy to detect. However, many sophisticated configuration errors, 
+which are difficult to template in practice, cannot be detected this way. As an illustration of such an error consider the ordering errors, which
+happen when some entries are inserted in a wrong order. 
+For example, if in a PHP configuration file an entry {\tt extension = mysql.so} appears 
+before {\tt extension = recode.so},  
+it would lead to a crash error, where the Apache server cannot start due to the segmentation fault error. The correct ordering 
 should be {\tt extension = recode.so} before 
-{\tt extension = mysql.so}~\cite{yin11anempirical};
-however, such an error cannot be detected by existing
-learning efforts, since it is hard to build a corresponding template ~\cite{xu15systems}.
+{\tt extension = mysql.so}~\cite{yin11anempirical}.
+These types of errors cannot be detected by existing
+learning efforts, since it is hard to build a corresponding template ~\cite{xu15systems}: we would need to capture ordering relations of all the entries. Some of 
+them can appear in an arbitrary ordering and the resulting templates would be too large and not efficient for a practical use.
 
@@
 
-In order to truly achieve automatic configuration verification,
-we argue that we need to leverage a collection of more powerful learning 
-algorithms (not necessarily depending on templates) to derive 
-a more sophisticated language model (with abundant rules covering
-tricky configuration errors), and then check the configuration files
-of interest through the learned language model. \jon{Too many parentheses in sentence. Cut down}
+In this paper we present \app, the first automatic verification framework
+for general software configurations. \app is based a collection of more powerful learning 
+algorithms, that do not necessarily depend on templates. The learning process can be seen as a process of deriving  
+a specification of configuration files, from a dataset containing a large sample of configuration files. In order to do that
+we utilize a more sophisticated language model. Thus, in the first step \app analyzes the given dataset and generates a 
+well-structured and probabilisticly-typed 
+intermediate representation.
+
+which aims to truly  achieve automatic configuration verification. we need to leverage a collection of more powerful learning 
+algorithms, that do not necessarily depend on templates. In order to do that
+there should be a more sophisticated language model, to which we would translate configuration files' entries.
+Based on  the learned language model we would develop an abundant set of rules covering 
+complex configuration errors. The set of learned rules should be accurate and we should be able to efficiently check 
+the configuration files
+of interest.
 

### 2016-05-09 OSDI/motiv.tex
a little progress
config: fix

@@
 \para{Example~4: Singular Value Errors} 
+A common error is that a value is set too high or too low.
+For example, consider the following:
 This should be the singular value error.
 We need an example from Stack Overflow to illustrate the 
-real-world problem. I guess the buffer size example is fine.}
+real-world problem. I guess the buffer size example is fine.
 

### 2016-05-09 OSDI/motiv.tex
add Example 4

@@
 A common error is that a value is set too high or too low.
-For example, consider the following:
-This should be the singular value error.
-We need an example from Stack Overflow to illustrate the 
-real-world problem. I guess the buffer size example is fine.
+For example, a parameter relating to memory might be too large,
+exhausting the RAM and causing extreme slowness. 
+Consider the following real-world misconfiguration file \cite{singleValue}: the
+user was experiencing the ``My SQL Server has gone away" error.  
+She had the following line in her configuration file.
+
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
+max_allowed_packet = 100M
+\end{lstlisting}
+
+The user resolved the issue by replacing the above line with {\tt max\_allowed\_packet=20M}. 
+It turns out that the original value, 100 MB, is extremely large, a  
+statistically anomalous value for the {\tt max\_allowed\_packet} attribute. ConfigV can detect these
+outliers. Run on the user's original configuration file, ConfigV would output:
+
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
+WARNING: Violated Upper Hampel Rule for max_allowed_packet with value 104857600 
+\end{lstlisting}
+
+In the above, 104857600 represents the integer value of 100 megabytes.
 

### 2016-05-09 OSDI/arch.tex

@@
 that we are given a number of (not necessarily correct) 
-configuration files belonging to the same system, 
-such as MySQL or Apache. 
-These given files follow similar patterns, which we exploit
-in a learning algorithm to build rules that
-describe a language model for the files.
+configuration files, called {\em sample dataset}, 
+belonging to the same system, such as MySQL or Apache. 
+These files, therefore, follow similar patterns.
+%In the following steps,
+%we will exploit in a collection of learning algorithms 
+%to build rules that describe a language model for the files.
 
@@
 dataset (containing both configuration files and system environment
-information), and then transforms them to a more structured
+information), and then transforms them into a more structured
 and typed intermediate representation.
-When we run type inference on a configuration file, 
-the type of a variable cannot always be fully determined from 
-a single value.
+When we infer the types of entries in a configuration file, 
+the type of an entry cannot always be fully determined from 
+a single value, since it is very hard to understand
+the purposes of key-value entries in modern
+software configuration files~\cite{xu15hey}.
 We address this problem 
 by introducing {\em probabilistic types}.
-Rather than giving a variable a single type, 
+In particular, rather than giving a variable a single type, 
 we assign several types over a probability distribution. 
@@
 The input of the learner is a set of files that have been translated
-into well-structured and typed representations.
-The learner module employs a collection of learning algorithms
-to generate various rule and constraints,
+into well-structured and typed representations (\ie, the translator's
+outputs). The learner module employs a collection of learning algorithms
+to generate various rules and constraints,
 potentially used to handle different types of configuration errors.
-These rules are the output of the learner, and will be 
-used by the checker to detect errors.
+These rules and constraints are the outputs of the learner, 
+and will be used by the checker to detect errors later.
 By combining the translated representations and the learned
@@
 ordering errors, typing errors, correlation errors, etc.
-\ennan{I do know we are using in some sense templates, but
-we should use pattern or some words to persuade we are 
-using an implicit ``templates''; otherwise, too similar 
-to what EnCore did.}
 
@@
 specific system executional environment information.
-A learning algorithm cannot derive rules related to environment violations, \eg,
-whether the current account is the owner of a certain path, without information 
-about the environment. In order to deal with comprehensive misconfiguration problems,
+A learning algorithm cannot derive rules 
+related to environment violations, \eg,
+whether the current account is 
+the owner of a certain path, without information 
+about the environment. 
+In order to deal with comprehensive misconfiguration problems,
 the learner needs a template DB to provide environment information,
@@
 and the target configuration file to verify.
-It outputs a report (as shown in $\S$\ref{sec-motiv}) about 
-whether it finds any error, \eg, rule violations or a suspicious value.
+It generates a report (as shown in $\S$\ref{sec-motiv}) about 
+whether it finds any error, \eg, rule violations 
+or some suspicious values.
 As shown in Figure~\ref{fig-overview},
@@
 checking rule violations and suspicious values, respectively.
-\ennan{I really wanted to say we are using MaxSMT to check and rank
-these errors ...}
-In our experience, we find learned rules can be significantly reused
+In our experience, we find learned rules could be significantly reused
 to check different configuration files, thus improving our usability.

### 2016-05-09 OSDI/motiv.tex
make correction

@@
 For example, a parameter relating to memory might be too large,
-exhausting the RAM and causing extreme slowness. 
+exhausting the RAM and causing extreme slowness or even a crash. 
 Consider the following real-world misconfiguration file \cite{singleValue}: the
@@
 
-The user resolved the issue by replacing the above line with {\tt max\_allowed\_packet=20M}. 
+The user resolved the issue by replacing the above line with {\tt max\_allowed\_packet=2M}. 
 It turns out that the original value, 100 MB, is extremely large, a  
@@
 
-In the above, 104857600 represents the integer value of 100 megabytes.
+In the above, 104857600 represents the integer value of 100 megabytes. The idea is to give the user
+a warning that their value falls outside of a range considered normal and to prompt the  
+appropriate adjustments.
 

### 2016-05-09 OSDI/motiv.tex
better wording

@@
 
-In the above, 104857600 represents the integer value of 100 megabytes. The idea is to give the user
-a warning that their value falls outside of a range considered normal and to prompt the  
-appropriate adjustments.
+In the above, 104857600 represents the integer value of 100 megabytes. The idea is to output
+a warning to the user that her value falls outside of a range considered normal, so that she
+can make the appropriate adjustment to the value herself.
 

### 2016-05-09 OSDI/motiv.tex
bit more systems-y

@@
 Consider the following real-world misconfiguration file \cite{singleValue}: the
-user was experiencing the ``My SQL Server has gone away" error.  
-She had the following line in her configuration file.
+user was experiencing the opaque ``My SQL Server has gone away" error.  
+This is difficult to debug, since the error message is not specific.
+It turns out the following line in her configuration file was problematic:
 

### 2016-05-09 OSDI/motiv.tex
config: small updates on motiv

--- 2016-05-09 OSDI/motiv.tex
@@
 \para{Example~4: Singular Value Errors} 
-A common error is that a value is set too high or too low.
+Many system performance problems are caused by 
+error that a value is set too high or too low.
 For example, a parameter relating to memory might be too large,
 exhausting the RAM and causing extreme slowness or even a crash. 
-Consider the following real-world misconfiguration file \cite{singleValue}: the
-user was experiencing the ``My SQL Server has gone away" error.  
+Consider the following real-world misconfiguration file%
+~\cite{singleValue}: a user was experiencing the ``My SQL Server 
+has gone away" error.  
 She had the following line in her configuration file.

### 2016-05-09 OSDI/motiv.tex
make better

@@
 has gone away" error.  
-She had the following line in her configuration file.
+This is difficult to debug, since the error message is not specific.
+It turns out the following line in her configuration file was problematic:
 
@@
 
-The user resolved the issue by replacing the above line with {\tt max\_allowed\_packet=2M}. 
-It turns out that the original value, 100 MB, is extremely large, a  
-statistically anomalous value for the {\tt max\_allowed\_packet} attribute. ConfigV can detect these
+The user eventually resolved the issue by replacing the above line with {\tt max\_allowed\_packet=2M}.
+One possible way to reach this conclusion more quickly is to determine that the original value for 
+{\tt max\_allowed\_packet}, 100 MB, was statistically deviant and extremely large. 
+ConfigV can detect these
 outliers. Run on the user's original configuration file, ConfigV would output:
@@
 a warning to the user that her value falls outside of a range considered normal, so that she
-can make the appropriate adjustment to the value herself.
+can make the appropriate adjustment to the value herself. In the above situation, it is 
+prudent to set the value lower.
 

### 2016-05-09 OSDI/motiv.tex
better motiv

@@
 Many system performance problems are caused by 
-error that a value is set too high or too low.
+issue that a value is set either too high or too low.
 For example, a parameter relating to memory might be too large,
@@
 The user eventually resolved the issue by replacing the above line with {\tt max\_allowed\_packet=2M}.
-One possible way to reach this conclusion more quickly is to determine that the original value for 
-{\tt max\_allowed\_packet}, 100 MB, was statistically deviant and extremely large. 
+One possible way to reach this conclusion more quickly is to determine that the original value, 100 MB, 
+was statistically deviant and extremely large for the {\tt max\_allowed\_packet} attribute. 
 ConfigV can detect these
@@
 can make the appropriate adjustment to the value herself. In the above situation, it is 
-prudent to set the value lower.
+prudent to set the value of {\tt max\_allowed\_packet} lower.
 

### 2016-05-09 OSDI/motiv.tex
minor motiv

@@
 \para{Example~4: Singular Value Errors} 
-Many system performance problems are caused by 
+Many system performance problems are caused by the
 issue that a value is set either too high or too low.
@@
 One possible way to reach this conclusion more quickly is to determine that the original value, 100 MB, 
-was statistically deviant and extremely large for the {\tt max\_allowed\_packet} attribute. 
+is statistically deviant and extremely large for the {\tt max\_allowed\_packet} attribute. 
 ConfigV can detect these

### 2016-05-09 OSDI/motiv.tex
change to error
make consistent

@@
 Many system performance problems are caused by the
-issue that a value is set either too high or too low.
+error that a value is set either too high or too low.
 For example, a parameter relating to memory might be too large,
@@
 Both \app and EnCore can handle misconfigurations concerning system execution.
-Furthermore, \app is also able to detect type and syntax errors
+Furthermore, \app is also able to detect type errors and syntax errors
 in configuration files.

### 2016-05-09 OSDI/learner.tex
config: learner

@@
 \eg, for paths and users.}
+
+In general, the learner module has two parts of learning tasks.
+One is to learn rules in order to check configuration errors like
+entry missing, ordering errors, and correlation errors.
+Another one is to learn constraints to check suspicious (or called
+anomalous) singular values that may violate standard values.
+
+\subsection{Learning Rules}
+\label{subsec-rules}
+
+\subsection{Learning Suspicious Constraints}
+\label{subsec-constraints}
+
+We now describe the technique we use to detect anomalous values for 
+numerical attributes. Let $A$ be the set of attributes contained in the 
+configuration files in the sample dataset. 
+Let $A_n$ be the subset of attributes of $A$ which are numerical types. 
+Then, for each attribute $a \in A_n$, we construct a vector $v_a$ of the 
+values corresponding to attribute $a$, seen over the entire sample dataset.
+For each $v_a$, we compute 
+an interval  $$[\hat{v_a} - 3*MAD(v_a), \hat{v_a} + 3*MAD(v_a)],$$ 
+where $\hat{v_a}$ represents the median over the values 
+in $v_a$ and $MAD(v_a$) refers to the 
+median absolute deviation. 
+This is a standard outlier detection test, namely the Hampel identifier. 
+\footnote{Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation 
+for a normal distribution.} 
+In the checking phase, as long as the checker finds a value for a numerical 
+attribute in the checked file outside of this interval, 
+a warning would be printed to the user indicating the violating value, 
+the attribute, and the upper or lower Hampel threshold.
+
+The intuition behind this is that if the user has input a value 
+that falls outside of an interval containing values that are considered 
+``normal'' over the entire sample dataset, 
+that value will probably cause an error, in particular for performance. 
+We cannot know for sure if this value will cause an issue. 
+For instance, a user might have a machine with 
+particularly high-end hardware, 
+in which case a value beyond the upper Hampel threshold may be appropriate.

### 2016-05-09 OSDI/intro.tex
intro

@@
 In this paper we present \app, the first automatic verification framework
-for general software configurations. \app is based a collection of more powerful learning 
-algorithms, that do not necessarily depend on templates. The learning process can be seen as a process of deriving  
-a specification of configuration files, from a dataset containing a large sample of configuration files. In order to do that
-we utilize a more sophisticated language model. Thus, in the first step \app analyzes the given dataset and generates a 
+for general software configurations. \app is based on a collection of powerful learning 
+algorithms, that do not necessarily depend on templates. The learning process takes as input a
+ large sample of configuration files. The process is language-agnostic and it works for any type of configuration files, 
+but all of the files in the sample need to be of the same type (such as  MySQL or httpd configuration files). From that sample
+\app learns an abundant set of rules specifying various properties that hold on the given sample. The files in the sample might contain
+errors -- we are, therefore, using probabilistic learning to derive a set of accurate rules. One can see this learning process as a
+way of deriving  
+a specification for configuration files. The learning process works in two phases. In the first phase \app analyzes the given dataset and generates a 
 well-structured and probabilisticly-typed 
-intermediate representation.
-
-which aims to truly  achieve automatic configuration verification. we need to leverage a collection of more powerful learning 
-algorithms, that do not necessarily depend on templates. In order to do that
-there should be a more sophisticated language model, to which we would translate configuration files' entries.
-Based on  the learned language model we would develop an abundant set of rules covering 
-complex configuration errors. The set of learned rules should be accurate and we should be able to efficiently check 
-the configuration files
-of interest.
-
-Based on the above argument, 
-this paper presents \app, the first automatic verification framework
-for general software configurations.
-In particular, \app's workflow for verifying a given configuration file
-can be viewed as a three-step methodology.
-Firstly, \app analyzes a dataset containing sample configuration files,
-thus generating a well-structured and probabilistically-typed 
-intermediate representation.
-Secondly, \app derives rules and constraints by analyzing
-the intermediate representations, thus building a language model.
-Finally, \app uses the resulting language model
-to verify the given configuration file and detect potential errors.
+intermediate representation. In the second phase \app derives rules and constraints by analyzing
+the intermediate representations.  The set of learned rules is accurate and we are able to efficiently check 
+the correctness of the configuration files
+of interest and detect potential errors.
 Compared with previous efforts,
 \app does not necessarily rely on users' templates 
-and is capable of detecting tricky configuration errors that
+and is capable of detecting intricate configuration errors that
 cannot be identified by existing work (details in $\S$\ref{sec-motiv}).
@@
 configuration files, nevertheless, requires addressing several challenges. 
-Firstly, in order to formulate a correct language model, 
-we need to infer each entry's type in a given configuration file, but 
+First, for variables of one types we learn different rules than for variables of different type. For example for integer variables $x$ and $Y$ we can learn that $X \leq Y$, while 
+for strings we might want to learn a substring relation. We, therefore, first need to assign a type to every variable in a configuration file during the transformation phase.
+However,
 the type of a variable cannot always be fully determined 
 from a single value. 
-For example, an entry {\tt foo = MAX\_SIZE} is most likely
-an integer rather than string; however, existing type inference 
-work would report this is an error, because {\tt foo} should be assigned
-an integer~\cite{zhang14encore}. \jon{Unclear what the error is. Be more precise} We address this problem by introducing 
+For example, an entry {\tt temp\_dir = 300} assigns to variable {\tt temp\_dir} either a directory named ``300'' or sets the size of that directory to 300 (an integer).
+Some of existing type inference 
+work would report this is an error, because {\tt temp\_dir} should be assigned
+an integer~\cite{zhang14encore}. We address this problem by introducing the concept of
 {\emph{probabilistic types}}.
@@
 The entry in the above example might be assigned 
-a probabilistic type like 
-{\tt \{foo, MAX\_SIZE, [(Int, 60\%), (String, 40\%)]\}}.
-With such probabilistic types in hand,
+the following probabilistic type
+{\tt \{temp\_dir, 300, [(File, 60\%), (Int, 40\%)]\}}.
+Using the probabilistic types model,
 we can generate a more accurate language model,
-thus significantly improving our checking capability.
+thus significantly improving our verification capabilities.
 

### 2016-05-09 OSDI/intro.tex
config: fixed typo in intro

@@
 su07autobash, whitaker04configuration},
-those tools mainly try to understand {\emph{what}} caused the error ---
-they are still not on a level of
+those tools mainly try to understand {\emph{what}} caused the 
+error -- they are still not on a level of
 automatic verification tools used for regular program 
@@
 is no explicit structure policy for the entries.
-Nevertheless, automated verification of configuration 
-files, that could detect would be highly
+Thus, automated verification of configuration 
+files would be highly
 desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
@@
 To overcome these obstacles, researchers have proposed approaches based on
-a statistical analysis and learning~\cite{wang04automatic, zhang14encore, yuan11context}
-that try to infer the rules and policies how configuration files are constructed.
-Rather than explicitly specifying entries' types or rules, these research directions are focused
-on learning policies from a sample data set.
-The learned rules are usually constructed along the following pattern: for every entry in a configuration file, 
-we check if it deviates from a ``typical'' value, \ie a value computed from a large training set consisting of configuration files.
-If the entry is significantly different that the typical value, we suspect that it could be a potential configuration error.
-The downside of this approach is that these learning efforts are limited to simplistic 
-configuration errors, such as type errors and syntax errors, or they 
-heavily rely on template-based inference~\cite{zhang14encore}. As we pointed out earlier, since configuration files are not written in a typed language with a fixed syntax,
-type errors and syntax errors are relatively rare and easy to detect. However, many sophisticated configuration errors, 
-which are difficult to template in practice, cannot be detected this way. As an illustration of such an error consider the ordering errors, which
-happen when some entries are inserted in a wrong order. 
-For example, if in a PHP configuration file an entry {\tt extension = mysql.so} appears 
+a statistical analysis and learning%
+~\cite{wang04automatic, zhang14encore, yuan11context}
+that try to infer the rules and policies 
+how configuration files are constructed.
+Rather than explicitly specifying entries' types or rules, 
+these efforts are focused on learning policies from a sample dataset.
+The learned rules are usually constructed along the following way: 
+for every entry in a configuration file, 
+they check if it deviates from a ``typical'' value, \ie, 
+a value computed from a large training set 
+consisting of configuration files.
+If the entry is significantly different that the typical value, 
+they suspect that it could be a potential configuration error.
+The downside of these approaches is that these learning approaches 
+are limited to simplistic configuration errors, 
+such as type errors and syntax errors, or they 
+heavily rely on template-based inference~\cite{zhang14encore}. 
+As we pointed out earlier, 
+since configuration files are not written in a typed language 
+with a fixed syntax,
+type errors and syntax errors are relatively rare and easy to detect. 
+However, many sophisticated configuration errors, 
+which are difficult to template in practice, 
+cannot be detected by this way. 
+As an illustration of such an error consider the ordering errors, 
+which happens when some entries are inserted in a wrong order. 
+For example, if in a PHP configuration file 
+an entry {\tt extension = mysql.so} appears 
 before {\tt extension = recode.so},  
-it would lead to a crash error, where the Apache server cannot start due to the segmentation fault error. The correct ordering 
+it would lead to a crash error, where the Apache server cannot start 
+due to the segmentation fault error. The correct ordering 
 should be {\tt extension = recode.so} before 
@@
 These types of errors cannot be detected by existing
-learning efforts, since it is hard to build a corresponding template ~\cite{xu15systems}: we would need to capture ordering relations of all the entries. Some of 
-them can appear in an arbitrary ordering and the resulting templates would be too large and not efficient for a practical use.
+learning efforts, 
+since it is hard to build a corresponding template~\cite{xu15systems}: 
+we would need to capture ordering relations of all the entries. 
+Some of them can appear in an arbitrary ordering, 
+and the resulting templates would be too large 
+and not efficient for a practical use.
 
@@
 
-In this paper we present \app, the first automatic verification framework
+In this paper, we present \app, the first automatic verification framework
 for general software configurations. \app is based on a collection of powerful learning 
@@
  large sample of configuration files. The process is language-agnostic and it works for any type of configuration files, 
-but all of the files in the sample need to be of the same type (such as  MySQL or httpd configuration files). From that sample
+but all of the files in the sample need to be of the same type (such as
+MySQL or httpd configuration files). From that sample,
 \app learns an abundant set of rules specifying various properties that hold on the given sample. The files in the sample might contain
@@
 way of deriving  
-a specification for configuration files. The learning process works in two phases. In the first phase \app analyzes the given dataset and generates a 
-well-structured and probabilisticly-typed 
-intermediate representation. In the second phase \app derives rules and constraints by analyzing
+a specification for configuration files. 
+The learning process works in two phases. In the first phase, 
+\app analyzes the sample dataset and generates a 
+well-structured and probabilistically-typed 
+intermediate representation. 
+In the second phase, \app derives rules and constraints by analyzing
 the intermediate representations.  The set of learned rules is accurate and we are able to efficiently check 
@@
 configuration files, nevertheless, requires addressing several challenges. 
-First, for variables of one types we learn different rules than for variables of different type. For example for integer variables $x$ and $Y$ we can learn that $X \leq Y$, while 
+First, for variables of one type 
+we learn different rules than for variables of different types. 
+For example, for integer variables $X$ and $Y$, 
+we can learn that $X \leq Y$, while 
 for strings we might want to learn a substring relation. We, therefore, first need to assign a type to every variable in a configuration file during the transformation phase.

### 2016-05-09 OSDI/learner.tex

@@
 \label{subsec-constraints}
+Anomalous values can cause tricky performance and memory issues that are hard to debug,
+as discussed in Example 4 of Section \ref{sec-motiv}. Consequently, suspicious values 
+should be flagged and a warning returned to the user indicating the violation.
 
@@
 configuration files in the sample dataset. 
-Let $A_n$ be the subset of attributes of $A$ which are numerical types. 
+Let $A_n$ be the subset of attributes of $A$ which are numerically typed. 
 Then, for each attribute $a \in A_n$, we construct a vector $v_a$ of the 

### 2016-05-09 OSDI/intro.tex
config: intro

@@
 they suspect that it could be a potential configuration error.
-The downside of these approaches is that these learning approaches 
+
+The downside of these approaches is that their learning approaches 
 are limited to simplistic configuration errors, 
@@
 heavily rely on template-based inference~\cite{zhang14encore}. 
-As we pointed out earlier, 
-since configuration files are not written in a typed language 
+As we mentioned earlier, 
+because configuration files are not written in a typed language 
 with a fixed syntax,

### 2016-05-09 OSDI/intro.tex
config: intro

@@
 heavily rely on template-based inference~\cite{zhang14encore}. 
-As we mentioned earlier, 
-because configuration files are not written in a typed language 
-with a fixed syntax,
-type errors and syntax errors are relatively rare and easy to detect. 
-However, many sophisticated configuration errors, 
+%As we mentioned earlier, 
+%because configuration files are not written in a typed language 
+%with a fixed syntax,
+%type errors and syntax errors are relatively rare and easy to detect. 
+Many sophisticated configuration errors, 
 which are difficult to template in practice, 
 cannot be detected by this way. 
-As an illustration of such an error consider the ordering errors, 
+As an illustration of such an error, consider the ordering errors, 
 which happens when some entries are inserted in a wrong order. 
@@
 learning efforts, 
-since it is hard to build a corresponding template~\cite{xu15systems}: 
-we would need to capture ordering relations of all the entries. 
-Some of them can appear in an arbitrary ordering, 
-and the resulting templates would be too large 
-and not efficient for a practical use.
+since it is hard to build a corresponding template~\cite{xu15systems}. 
+%we would need to capture ordering relations of all the entries. 
+%Some of them can appear in an arbitrary ordering, 
+%and the resulting templates would be too large 
+%and not efficient for a practical use.
 
@@
 configuration files, nevertheless, requires addressing several challenges. 
-First, for variables of one type 
-we learn different rules than for variables of different types. 
-For example, for integer variables $X$ and $Y$, 
-we can learn that $X \leq Y$, while 
-for strings we might want to learn a substring relation. We, therefore, first need to assign a type to every variable in a configuration file during the transformation phase.
+%First, for variables of one type 
+%we learn different rules than for variables of different types. 
+%For example, for integer variables $X$ and $Y$, 
+%we can learn that $X \leq Y$, while 
+%for strings we might want to learn a substring relation. 
+First, we need to assign a type to every variable in a configuration file during the transformation phase.
 However,

### 2016-05-09 OSDI/arch.tex
overview of probabilistic​ learning

@@
 The input of the learner is a set of files that have been translated
-into well-structured and typed representations (\ie, the translator's
+into a well-structured representations of a list of keyword-value pairs (\ie, the translator's
 outputs). The learner module employs a collection of learning algorithms

### 2016-05-09 OSDI/learner.tex
overview of probabilistic​ learning

@@
 \eg, for paths and users.}
+\markk{I am not sure how much space we have to discuss the details of each learning module, or how important that is here.
+I have only discussed the overall architecture of probabilistic learning, and it already takes quite a bit of space.
+maybe module specific stuff should go into sec 8 (implementation)?
+please advise.}
 
 In general, the learner module has two parts of learning tasks.
-One is to learn rules in order to check configuration errors like
-entry missing, ordering errors, and correlation errors.
-Another one is to learn constraints to check suspicious (or called
-anomalous) singular values that may violate standard values.
+The first is to learn rules in order to check configuration errors like
+missing entry, ordering errors, and correlation errors. These are the types of errors that tend to cause total system failures.
+Once the configuration file as been validated against such rules, the user may choose to invoke a more sensitive constraint checker.
+This second step learns constraints on singular entries to check for suspicious (i.e.
+anomalous) values that may violate standard practice.
 
-\subsection{Learning Rules}
+\subsection{Derivation of probabilistic rules}
 \label{subsec-rules}
+
+\para{Learning from an incorrect set.}
+The first step of \app is to learn relations that must hold over multiple parts of a configuration file.
+Previous work used a set of correct configuration files as a learning set, from which it was possible to derive rules that must hold with absolute certainty\cite{santolucitoCAV}. 
+However, this is approach is severely limiting. 
+It is difficult to obtain a set of files that is both guaranteed to be without misconfiguration and large enough to learn the many rules of configuration files.
+This usual requires manual verification of the learning set, which is prone to error.
+
+As a result of this restriction, the tool introduced in \cite{santolucitoCAV} will only consider a rule if it holds over exactly every file in the learning set.
+This behavior can be formally described as follows:
+
+\begin{flalign*}
+C =&\ \text{Correct Learning Set}\\
+\text{::}\ & \text{\{Configuration Files in Intermediate Representation\}}\\
+LR =&\ \text{Learned Rules :: \{Rule\}}\\
+RR =&\ \text{Reported Rules :: \{Rule\}}\\
+&\\
+LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file)\} \\
+RR =&\ \{ r\ \mid r \in L\ \land \neg\ holds(r,userfile) \}&\\
+\end{flalign*}
+
+Each rule can be thought of as a mapping from lines j and k in a configuration file to a relation, $R$.
+
+\[
+\{ Rule = (a_j, a_k) | j \neq k \} \rightarrow \{ R \}
+\]
+
+Specifically, $a_j$ and $a_k$ are two different lines from our intermediate representation, or more formally, $j \neq k \land \vee a_j, a_k \in \{ L \})$ where  is the set of lines (keyword-value pairs) found in the intermediate representation of our learning set.
+The relation $R$ is a Boolean function specific to the error we wish to detect.
+As an example, to detect the error that keyword k1 must always have a value greater than keyword k2, the relation $R$ is $>$.
+
+In \app, the rule learning mechanism is tolerant enough to accept a database of incorrect configuration files.
+Rather than manually correcting each file, we observe that the files are usually incorrect in only one or two lines.
+We then extend the previous formalism to handle probabilistic learning, when we have a collection of such files.
+
+Our probabilistic approaches for learning the Missing Values, Keyword Ordering, and Integer Relations rules stem from our previous work with building the non-probabilistic versions of these rule-learning algorithms.
+We start with the idea that for each of these rules, we are going to consider all possible pairs of keywords that appear in every file, and for our learning process, calculate the likelihood that each of these pairs constitute a rule.
+In essence, this is a mechanism that will consider many different possible pairs of lines in the file, and attempt to compile a set of these pairs that are expressed more often than others as a basis for finding patterns within the example set that can be used to evaluate new files.
+
+More formally, this approach can be defined as follows.
+The output of our learning algorithm is augmented to a map from keyword-value pairs to a probability distribution over number of possible relations.
+
+\[
+\{ P\_Rule = (a_j, a_k) | j \neq k \} \rightarrow \{ (R_1, R_2, ... , R_n) \}
+\]
+
+We can think of each of these $(a_j, a_k)$ as possibly having a different relationship, defined by the set $\{ R_i \}$, which cover the entire outcome space of possible relationships between the two values $(a_j, a_k)$.
+
+For the missing keywords rules, we define $R_1$ as the event that $a_j$ and $a_k$ appear together, and $R_2$ to be the event that $a_j$ appears without $a_k$, or by the transitive equivalent, $a_k$ appears without $a_j$.
+For the keyword ordering rules, we define $R_1$ as the event that $a_j$ appears before $a_k$ and $R_2$ be the event that $a_k$ appears before $a_j$.
+For the integer relations rule, we define $R_1$ as the event that $a_j \leq a_k$, $R_2$ the event that $a_j = a_k$, and $R_3$ the case that $a_j \geq a_k$.
+Notice that the $R_i$ do not have to be disjoint, but only have to union to the entire probability space.
+
+By examining the learning set, we will derive a distribution of the set $\{R_i\}$ based on how many times we observe an occurrence of each relation.
+This distribution will then be used at checking time to determine if a user's configuration has broken a likely rule.
+
+\begin{flalign*}
+I\ \ =&\ \text{Incorrect Learning Set}\\
+\text{::}\ & \text{\{Configuration Files in Intermediate Representation\}}\\
+LP =&\ \text{Learned Probabilistic Rules :: \{(P\_Rule)\}}\\
+RP =&\ \text{Reported Probabilistic Rules :: \{(P\_Rule)\}}\\
+&\\
+LP =&\ \text{count\_relation\_occurrences}(I)\\
+RP =&\ \{ r\ \mid r \in LP\ \land \Pi(r)>p \land \neg r(userfile) \}&\\
+\end{flalign*}
+
+A rule will be reported as broken if the probability the rule is correct, $\Pi$, is greater than some user defined constant, $p$.
+This constant can be adjust to the user's preference.
+A small $p$ will increase the likelihood of finding an error, but also increase the number of false positives that are reported.
 
@@
 \label{subsec-constraints}
-Anomalous values can cause tricky performance and memory issues that are hard to debug,
-as discussed in Example 4 of Section \ref{sec-motiv}. Consequently, suspicious values 
-should be flagged and a warning returned to the user indicating the violation.
+With a configuration file that has been verified against catastrophic failures, the user may also use \app to find more subtle issues.
+Anomalous values can cause tricky, but impactful, performance and memory issues that are hard to debug, as discussed in Example 4 of Section \ref{sec-motiv}.
+Consequently, suspicious values should be flagged and a warning returned to the user indicating the violation.
 

### 2016-05-09 OSDI/eval.tex
config: eval
add table for anomalies

@@
 
+Finally, we check suspicious values.
+
+\begin{table*}[t]
+\centering
+\caption{Sampled benchmarks for anomaly detection}
+\label{table-casestudy}
+\begin{tabular}{|l|l|l|l|}
+\hline
+{\bf ID} & {\bf Problem Description} & {\bf URL} & 
+{\bf \app Report}  \\ 
+\hline
+\hline
+1 & MySQL Server has gone away error in Wamp 
+& goo.gl/axnezi  
+& WARNING: Violated Upper Hampel Rule for
+
+%this way of doing is awful
+\\ &  & 
+& {\tt max\_allowed\_packet} with value 104857600 
+ \\ \hline
+
+2 &  MySQL has abnormally high load for CPU 
+& goo.gl/JrRLrR
+& WARNING: Violated Upper Hampel Rule for % 
+& &  & 
+& {\tt sort\_buffer\_size} with value 1048576000 
+& & &  & WARNING: Violated Upper Hampel Rule for  
+& & &  & {\tt read\_rnd\_buffer\_size} with value 283115520 \\ \hline
+
+\end{tabular}
+\end{table*}
+
 \subsection{Training Set Impact}
@@
 
-\subsection{The accuracy of Rule Inference}
-
-\ennan{I am still trying to think about this part ...}
-
 \subsection{The Run-Time of Verification}

### 2016-05-09 OSDI/learner.tex
add table for anomalies
more accurate Hampel

@@
 It is difficult to obtain a set of files that is both guaranteed to be without misconfiguration and large enough to learn the many rules of configuration files.
-This usual requires manual verification of the learning set, which is prone to error.
+This usually requires manual verification of the learning set, which is prone to error.
 
@@
 For each $v_a$, we compute 
-an interval  $$[\hat{v_a} - 3*MAD(v_a), \hat{v_a} + 3*MAD(v_a)],$$ 
+an interval  $$[\hat{v_a} - 50*MAD(v_a), \hat{v_a} + 50*MAD(v_a)],$$ 
 where $\hat{v_a}$ represents the median over the values 
@@
 median absolute deviation. 
-This is a standard outlier detection test, namely the Hampel identifier. 
-\footnote{Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation 
+This is a variant of a standard outlier detection test, namely the Hampel identifier.\footnote{Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation 
 for a normal distribution.} 

### 2016-05-09 OSDI/eval.tex
add another element to anomaly table
fix compilation for eval

@@
 & WARNING: Violated Upper Hampel Rule for 
-
-%this way of doing is awful
 \\ &  & 
@@
 & goo.gl/JrRLrR
-& WARNING: Violated Upper Hampel Rule for % 
-& &  & 
-& {\tt sort\_buffer\_size} with value 1048576000 
-& & &  & WARNING: Violated Upper Hampel Rule for  
-& & &  & {\tt read\_rnd\_buffer\_size} with value 283115520 \\ \hline
+& WARNING: Violated Upper Hampel Rule for  
+\\ & & 
+& {\tt sort\_buffer\_size} with value 1048576000 \\
+& & & WARNING: Violated Upper Hampel Rule for  
+\\ & & 
+& {\tt read\_rnd\_buffer\_size} with value 283115520 \\ \hline
+
+3 & User is having performance issues with MySQL 
+& goo.gl/34jTB5
+& WARNING: Violated Upper Hampel Rule for  
+\\ & & 
+& {\tt query\_cache\_limit} with value 134217728 \\ \hline
 

### 2016-05-09 OSDI/motiv.tex
change name to anomaly
make stuff more systems-y
config: eval and motiv

@@
 
-\jon{The following paragraph is repetitive, same as the above -- already mentioned
-this exact error for EnCore -- just remove it?}
-Note that an existing effort, EnCore, aims to detect value correlation 
-errors. However, different from \app, EnCore can only detect simple
-correlations, \eg, {\tt mysql.max\_persistent} < {\tt max\_connections},
-rather than the fine-grained computation-based value correlation,
-like {\tt key\_buffer\_size >= max\_connections * sort\_buffer\_size}
-identified by \app.
+Compared with \app, existing efforts, \eg, EnCore, cannot 
+detect fine-grained value correlation errors.
 
@@
 
-\para{Example~4: Singular Value Errors} 
+\para{Example~4: Singular value anomalies.} 
 Many system performance problems are caused by the
-error that a value is set either too high or too low.
+anomaly that a value is set either too high or too low.
 For example, a parameter relating to memory might be too large,
@@
 can make the appropriate adjustment to the value herself. In the above situation, it is 
-prudent to set the value of {\tt max\_allowed\_packet} lower.
+prudent to set the value of {\tt max\_allowed\_packet} lower. We call such a value a 
+\emph{singular value anomaly}.
 

### 2016-05-09 OSDI/arch.tex
config: updated

@@
 whether it finds any error, \eg, rule violations 
-or some suspicious values.
+or some suspicious values (\eg, singular value anomaly).
 As shown in Figure~\ref{fig-overview},

### 2016-05-09 OSDI/learner.tex
config: updated

--- 2016-05-09 OSDI/learner.tex
@@
 
-\ennan{This section details how do we extract rules from the
-intermediate representations. This section may should have the following
-two subsections: Aaron's part (including Xinyu's fine-grained
-value correlation rule learning) and Jonathon's part.
-In addition, we may need to add one more subsection about
-learning system environment information related rules,
-\eg, for paths and users.}
+The goal of learner module is to derive rules and constraints from
+the intermediate representation generated by the translator.
+In general, the learner module has two parts.
+The first part is to learn rules to check configuration errors like
+missing entry, ordering errors, and fine-grained value correlation errors. 
+These errors tend to cause total system failures.
+%Once the configuration file has been validated against such rules, 
+%the user may choose to invoke a more sensitive constraint checker. 
+The second part of the learner aims to derive 
+constraints on entries to check for suspicious (\ie, anomalous) values 
+that may violate standard practice (like the example~4 in
+$\S$\ref{sec-motiv}).
 
-In general, the learner module has two parts of learning tasks.
-One is to learn rules in order to check configuration errors like
-entry missing, ordering errors, and correlation errors.
-Another one is to learn constraints to check suspicious (or called
-anomalous) singular values that may violate standard values.
+\subsection{Derivation of Probabilistic Rules}
+\label{subsec-rules}
 
-\subsection{Learning Rules}
-\label{subsec-rules}
+\para{A strawman solution.}
+The first step of \app is to learn relations 
+that must hold over multiple parts of a configuration file.
+We now first present a strawman solution (employed by
+previous work~\cite{santolucitoCAV, zhang14encore}) that uses 
+a set of correct configuration files as a learning set, 
+from which it was possible to derive rules 
+that must hold with absolute certainty. 
+However, this is approach is severely limiting. 
+It is difficult to obtain a set of files 
+that is both guaranteed to be without misconfiguration 
+and large enough to learn the many rules of configuration files.
+This usually requires manual verification of the learning set, 
+which is prone to error.
+
+As a result of this restriction, 
+these efforts only consider a rule if it holds over exactly every file in 
+the learning set. This behavior can be formally described as follows:
+
+\begin{small}
+\begin{flalign*}
+C =&\ \text{Correct Learning Set}\\
+\text{::}\ & \text{\{Configuration Files in Intermediate Representation\}}\\
+LR =&\ \text{Learned Rules :: \{Rule\}}\\
+RR =&\ \text{Reported Rules :: \{Rule\}}\\ 
+LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file)\} \\
+RR =&\ \{ r\ \mid r \in L\ \land \neg\ holds(r,userfile) \}
+\end{flalign*}
+\end{small}
+
+Each rule can be thought of as a mapping from 
+lines $j$ and $k$ in a configuration file to a relation, $R$.
+
+\[
+\{ Rule = (a_j, a_k) | j \neq k \} \rightarrow \{ R \}
+\]
+
+Specifically, $a_j$ and $a_k$ are two different lines from our
+intermediate representation, or more formally, $j \neq k \land
+a_j, a_k \in \{ L \}$ where is the set of lines (key-value pairs) found
+in the learning set. The relation $R$
+is a Boolean function specific to the error to detect. 
+As an example, to detect the error that key $k_1$ must always 
+have a value greater than key $k_2$, the relation $R$ is $>$.
+
+\para{Our approach.}
+In \app, the rule learning mechanism is tolerant 
+enough to accept a dataset {\em full of} incorrect configuration files.
+Rather than manually correcting each file, 
+%we observe that the files are usually incorrect in several lines.
+We extend the previous formalism to run probabilistic learning
+on our intermediate representations (generated by the translator).
+
+Our probabilistic approaches for learning the missing values, 
+ordering, and fine-grained value correlation rules stem 
+from our previous work with building 
+the non-probabilistic versions of these rule-learning algorithms. 
+We start with the idea that for each of these rules, 
+we are going to consider all possible pairs of keys that appear in every 
+file, and for our learning process, calculate the likelihood that each of 
+these pairs constitute a rule. 
+In essence, this is a mechanism that will consider many different possible 
+pairs of lines in the file, 
+and attempt to compile a set of these pairs 
+that are expressed more often than others as a basis for finding patterns 
+within the example set that can be used to evaluate new files.
+
+More formally, this approach can be defined as follows. 
+The output of our learning algorithm is augmented to a map from 
+key-value pairs to a probability distribution over number of possible 
+relations.
+
+\[
+\{ P\_Rule = (a_j, a_k) | j \neq k \} \rightarrow \{ (R_1, R_2, ... , R_n) \}
+\]
+
+We can think of each of these $(a_j, a_k)$ as possibly having a different relationship, defined by the set $\{ R_i \}$, which cover the entire outcome space of possible relationships between the two values $(a_j, a_k)$.
+
+For the entry missing rules, we define $R_1$ as the event that $a_j$ and
+$a_k$ appear together, and $R_2$ to be the event that $a_j$ appears
+without $a_k$, or by the transitive equivalent, $a_k$ appears without
+$a_j$. For the ordering rules, we define $R_1$ as the event that
+$a_j$ appears before $a_k$ and $R_2$ be the event that $a_k$ appears
+before $a_j$. For the value correlation rules, we define $R_1$ as the
+event that $a_j \leq a_k$, $R_2$ the event that $a_j = a_k$, and $R_3$
+the case that $a_j \geq a_k$. Notice that the $R_i$ do not have to be
+disjoint, but only have to union to the entire probability space.
+
+By examining the learning set, we will derive a distribution of the set $\{R_i\}$ based on how many times we observe an occurrence of each relation.
+This distribution will then be used at checking time to determine if a user's configuration has broken a likely rule.
+
+\begin{small}
+\begin{flalign*}
+I\ \ =&\ \text{Incorrect Learning Set}\\
+\text{::}\ & \text{\{Configuration Files in Intermediate Representation\}}\\
+LP =&\ \text{Learned Probabilistic Rules :: \{(P\_Rule)\}}\\
+RP =&\ \text{Reported Probabilistic Rules :: \{(P\_Rule)\}}\\
+LP =&\ \text{count\_relation\_occurrences}(I)\\
+RP =&\ \{ r\ \mid r \in LP\ \land \Pi(r)>p \land \neg r(userfile) \}
+\end{flalign*}
+\end{small}
+
+A rule will be reported as broken if the probability the rule is correct, $\Pi$, is greater than some user defined constant, $p$.
+This constant can be adjust to the user's preference.
+A small $p$ will increase the likelihood of finding an error, but also increase the number of false positives that are reported.
 
@@
 \label{subsec-constraints}
-Anomalous values can cause tricky performance and memory issues that are hard to debug,
-as discussed in Example 4 of Section \ref{sec-motiv}. Consequently, suspicious values 
-should be flagged and a warning returned to the user indicating the violation.
+
+With a configuration file that has been verified against catastrophic
+failures, the user may also use \app to find more subtle issues.
+Anomalous values can cause tricky, but impactful, performance and memory
+issues that are hard to debug, as discussed in Example 4 of 
+$\S$\ref{sec-motiv}. 
+Consequently, suspicious values should be flagged and a warning returned
+to the user indicating the violation.
 

### 2016-05-09 OSDI/trans.tex
config: checker part
config: updated

@@
 \section{Translator}
+\label{sec-trans}
 
-\ennan{Translator is, in some sense, like a parser. 
-This section is used to detail how we design the parser.}
-
-The responsibility of the translator is to transform a given set of
-configuration files into another set of files written in
+The responsibility of the translator is to transform a given sample
+dataset of configuration files into another set of files written in
 typed and well-structured representations.
@@
 and HDFS, we need to develop different parsers to handle each of them,
-respectively. \app allows users to provide extra help to the translator
-for their specific system configuration, such as specifying a comment 
-character. Each of the entries in the intermediate representations
-must be assigned types, and these types would guide the learning
+respectively. \app also allows users to 
+provide extra help to the translator
+for their specific system configurations,
+but not necessarily. 
+Each of the entries in the intermediate representations
+have been assigned types, and these types would guide the learning
 modules later.
@@
 \para{Introducing probabilistic types.}
-Based on a single example value of $v$,
-the translator cannot fully determine the type of $k$.
-Consider for instance the following example:
+For any key-value entry in the sample configuration files,
+the translator cannot fully determine the type of key 
+based on a single example value.
+Consider the following example.
 
@@
 
-Note that typing is also a system module than 
+\com{Note that typing is also a system module than 
 can be easily extended to support more types. 
@@
 and probability distributions for values where type inference is ambiguous.
+}

### 2016-05-09 OSDI/learner.tex
config: learner

@@
 In general, the learner module has two parts.
-The first part is to learn rules to check configuration errors like
+The first part ($\S$\ref{subsec-rules}) 
+is to learn rules to check configuration errors like
 missing entry, ordering errors, and fine-grained value correlation errors. 
@@
 %the user may choose to invoke a more sensitive constraint checker. 
-The second part of the learner aims to derive 
+The second part of the learner ($\S$\ref{subsec-constraints}) 
+aims to derive 
 constraints on entries to check for suspicious (\ie, anomalous) values 
@@
 \para{A strawman solution.}
-The first step of \app is to learn relations 
+The first part of the learner is to learn relations 
 that must hold over multiple parts of a configuration file.
@@
 that must hold with absolute certainty. 
-However, this is approach is severely limiting. 
-It is difficult to obtain a set of files 
+However, in practice, it is difficult to obtain a set of files 
 that is both guaranteed to be without misconfiguration 
-and large enough to learn the many rules of configuration files.
+and large enough to learn many rules of configuration files.
 This usually requires manual verification of the learning set, 
@@
 \para{Our approach.}
-In \app, the rule learning mechanism is tolerant 
+In \app's leaner module, the rule learning mechanism is tolerant 
 enough to accept a dataset {\em full of} incorrect configuration files.

### 2016-05-09 OSDI/eval.tex
config: eval and motiv
config: eval and learner

@@
 and one is for checker.}
+
+\begin{table*}[t]
+\centering
+\caption{Sampled benchmarks for misconfiguration detection}
+\label{table-casestudy}
+\begin{small}
+\begin{tabular}{|l|l|l|l|}
+\hline
+{\bf ID} & {\bf Problem Description} & {\bf Error Type} & 
+{\bf \app Report}  \\ 
+\hline
+\hline
+1 & MySQL cannot create test file  
+& Entry Missing 
+& Expected innodb\_force\_recovery=1 in the \\ & & 
+&  same file as: innodb\_strict\_mode=1\\ \hline
+
+2 & How can my wait\_timeout/interactive\_timeout  
+& Entry Missing
+& Expected set\_time=1 in the same\\ & be ignored 
+& & file as wait\_timeout \\ \hline
+
+3 & MySQL on EC2 instance becomes very slow
+& Correlation
+& Expected key\_buffer\_size $>=$ \\ & after the first query
+&& thread\_size * sort\_buffer\_size \\ \hline
+
+4 & MySQL cannot successfully make  
+& Type Error
+& Expected master-host[mysqld] should 
+ \\ & replication &&  be a valid IP address\\ \hline
+
+5 & MySQL running on production servers has
+& Type Error
+& Expected set-variable[myisamchk] \\ &  gone away error in memory
+&&  should be a memory size like 20M \\ \hline
+
+6 & Cannot start MySQL 5.5 as normal 
+& Ordering
+& Expected socket[mysqld]=/var/lib/ \\ & user Fedora 15 
+&&  mysql/mysql.sock BEFORE  \\ & && user[mysqld]=mysql
+
+\\ \hline
+
+7 & Fail to login MySQL
+& Type Error
+& Expected old\_passwords[mysqld] 
+ \\ &&&  should be a valid value \\ \hline
+
+8 & MySQL running at CentOS cannot know 
+& Ordering
+& Expected localhost before bind-
+ \\ & enable named pipe
+&&  address[mysqld] \\ \hline
+
+9 & Troubles installing MySQL5 via  Darwin 
+& Ordering
+& Expected port[mysqld]=3306 BEFORE \\ & Ports
+&&  socket[mysqld]=/tmp/mysql.sock \\ \hline
+
+10 & Fail to install Percona xtraDB 
+& Entry Missing
+& Expected wsrep\_node\_address[mysqld] \\ & cluster on ubuntu 13.04
+&&  in the same file as: wsrep\_sst\_method \\ &&& [mysqld] \\ \hline
+
+11 & MySQL access denied for user rootlocalhost 
+& Ordering
+& Expected port[mysqld]=3306  \\ & &&   BEFORE socket[mysqld]= \\ &&& /tmp/mysql.sock
+\\ \hline
+
+12 & MySQL Partition Problem
+& Correlation
+& Expected innodb\_flush\_max  \\ & &&  \_commit[mysqld] $>=$ innodb \\ &&&  \_support[mysqld] \\ \hline
+
+13 & mysql\_upgrade script problems on 
+& Type Error
+& Expected log-slow-queries[mysqld]  \\ & MySQL 5.0.24 
+&&  should be a path type\\ \hline
+
+14 & MySQL: bug report!!
+& Ordering
+& Expected innodb\_file\_io\_threads[mysqld]  \\ & 
+&& BEFORE innodb\_log\_files\_in\_group[mysqld]\\ \hline
+
+15 & MySQL max connections changed 
+& Correlation
+& Expected innodb\_file\_per\_table \\ & without notice
+&&  [mysqld] $<=$ max\_connections[mysqld]  \\ \hline
+
+16 & Enabling log in MySQL 5 6 
+& Type Error
+& Expected sql\_mode[mysqld] should  \\ & prevents server from starting
+&&  be a string \\ \hline
+
+17 & MySQL needs help for rapidly growing 
+& Correlation
+& Expected innodb\_buffer\_pool\_size \\ & table and decreasing speed
+&&  [mysqld] $>$ sort\_buffer\_size[mysqld] \\ \hline
+
+18 & MySQL filled all RAM on the system
+& Correlation
+& Expected join\_buffer\_szie * \\ & && max\_connections $<=$ key\_buffer\_size \\ \hline
+
+19 & MySQL hit a max limit
+& Correlation
+& Expected join\_buffer\_size * \\ &&& max\_connections $<=$ key\_buffer\_size \\ \hline
+
+20 & Cannot create a new thread
+& Correlation
+& Expected join\_buffer\_size * \\ &&& max\_connections $<=$ key\_buffer\_size \\ \hline
+
+\end{tabular}
+\end{small}
+\end{table*}
 
@@
 
-\begin{table*}[t]
-\centering
-\caption{Sampled benchmarks for misconfiguration detection}
-\label{table-casestudy}
-\begin{tabular}{|l|l|l|l|}
-\hline
-{\bf ID} & {\bf Problem Description} & {\bf Error Type} & 
-{\bf \app Report}  \\ 
-\hline
-\hline
-1 & How to configure MySql master slave to  
-& Type Error 
-& Expected a Filepath with P=1.0 \\ & backup master to slave & 
-& for log-bin[mysqld] \\ \hline
-
-2 & data import from MySql dies when MySQL  
-& Correlation 
-& Expected thread\_cache\_size[mysqld] > \\ & query limit is removed 
-& & innodb\_buffer\_pool\_size \\ \hline
-
-\end{tabular}
-\end{table*}
-
 Next, we inject some errors to correct configuration files,
@@
 \caption{Sampled benchmarks for anomaly detection}
-\label{table-casestudy}
+\label{table-anomaly}
+\begin{small}
 \begin{tabular}{|l|l|l|l|}
@@
 \end{tabular}
+\end{small}
 \end{table*}

### 2016-05-09 OSDI/learner.tex
config: eval and learner

@@
 aims to derive 
-constraints on entries to check for suspicious (\ie, anomalous) values 
+constraints on entries to check for suspicious (or anomalous) values 
 that may violate standard practice (like the example~4 in
@@
 
+The first part of the learner is to learn rules 
+that must hold over multiple parts of a configuration file.
+
 \para{A strawman solution.}
-The first part of the learner is to learn relations 
-that must hold over multiple parts of a configuration file.
 We now first present a strawman solution (employed by
@@
 Rather than manually correcting each file, 
-%we observe that the files are usually incorrect in several lines.
-We extend the previous formalism to run probabilistic learning
+we extend the previous formalism to run probabilistic learning
 on our intermediate representations (generated by the translator).
 
-Our probabilistic approaches for learning the missing values, 
+Our probabilistic approaches for learning the entry missing, 
 ordering, and fine-grained value correlation rules stem 
-from our previous work with building 
+from existing work with building 
 the non-probabilistic versions of these rule-learning algorithms. 
@@
 In essence, this is a mechanism that will consider many different possible 
-pairs of lines in the file, 
+pairs of lines of entries in the file, 
 and attempt to compile a set of these pairs 
@@
 With a configuration file that has been verified against catastrophic
-failures, the user may also use \app to find more subtle issues.
+failures (\eg, entry missing, type and ordering errors), 
+the user may also want to find out more subtle issues.
 Anomalous values can cause tricky, but impactful, performance and memory
@@
 $\S$\ref{sec-motiv}. 
-Consequently, suspicious values should be flagged and a warning returned
+Consequently, anomalous values should be flagged and a warning returned
 to the user indicating the violation.

### 2016-05-09 OSDI/check.tex
config: updated

@@
 
-With the learned rules and constraints in hand,
+With the learned rules and constraints in hand (generated
+by the learner module),
 \app checks whether any entry in a target configuration file
-violates the learned rules.
+violates the learned rules and constraints.
 For a given configuration file, \app parses it using the same
@@
 following aspects of the target configuration file.
+
+\para{Entry missing violation.}
+\app 's checker can detect whether two or more entries should
+appear together in the same configuration file based upon
+entry missing rules generated by the learner.
 

### 2016-05-09 OSDI/eval.tex
config: updated

--- 2016-05-09 OSDI/eval.tex
@@
 
+\input{table}
+
 \subsection{\app's effectiveness}
@@
 and whether \app correctly reports the issues.}
-
-\begin{table*}[t]
-\centering
-\caption{Sampled benchmarks for misconfiguration detection}
-\label{table-casestudy}
-\begin{tabular}{|l|l|l|l|}
-\hline
-{\bf ID} & {\bf Problem Description} & {\bf Error Type} & 
-{\bf \app Report}  \\ 
-\hline
-\hline
-1 & How to configure MySql master slave to  
-& Type Error 
-& Expected a Filepath with P=1.0 \\ & backup master to slave & 
-& for log-bin[mysqld] \\ \hline
-
-2 & data import from MySql dies when MySQL  
-& Correlation 
-& Expected thread\_cache\_size[mysqld] > \\ & query limit is removed 
-& & innodb\_buffer\_pool\_size \\ \hline
-
-\end{tabular}
-\end{table*}
 

### 2016-05-09 OSDI/motiv.tex
config: updated

@@
 
-\para{Example~1: Ordering errors.} 
+\para{Example~1: Ordering error.} 
 The first class of configuration errors we handle was first reported by 
@@
 
-\para{Example~2: Fine-grained value correlation errors.} 
+\para{Example~2: Fine-grained value correlation error.} 
 In a real-world misconfiguration example~\cite{correlation}, 
@@
 
-\para{Example~3: Entry missing errors.} 
+\para{Example~3: Entry missing error.} 
 Many critical system outages result from the fact that an important

### 2016-05-09 OSDI/table.tex
config: updated

\begin{table*}[tbp]
\centering
\caption{Sampled benchmarks for misconfiguration detection}
\label{table-casestudy}
\begin{small}
\begin{tabular}{|l|l|l|l|}
\hline
{\bf ID} & {\bf Problem Description} & {\bf Error Type} & 
{\bf \app Report}  \\ 
\hline
\hline
1 & MySQL cannot create test file  
& Entry Missing 
& Expected innodb\_force\_recovery=1 in the \\ & & 
&  same file as: innodb\_strict\_mode=1\\ \hline

2 & How can my wait\_timeout/interactive\_timeout  
& Entry Missing
& Expected set\_time=1 in the same\\ & be ignored 
& & file as wait\_timeout \\ \hline

3 & MySQL on EC2 instance becomes very slow
& Correlation
& Expected key\_buffer\_size $>=$ \\ & after the first query
&& thread\_size * sort\_buffer\_size \\ \hline

4 & MySQL cannot successfully make  
& Type Error
& Expected master-host[mysqld] should 
 \\ & replication &&  be a valid IP address\\ \hline

5 & MySQL running on production servers has
& Type Error
& Expected set-variable[myisamchk] \\ &  gone away error in memory
&&  should be a memory size like 20M \\ \hline

6 & Cannot start MySQL 5.5 as normal 
& Ordering
& Expected socket[mysqld]=/var/lib/ \\ & user Fedora 15 
&&  mysql/mysql.sock BEFORE  \\ & && user[mysqld]=mysql

\\ \hline

7 & Fail to login MySQL
& Type Error
& Expected old\_passwords[mysqld] 
 \\ &&&  should be a valid value \\ \hline

8 & MySQL running at CentOS cannot know 
& Ordering
& Expected localhost before bind-
 \\ & enable named pipe
&&  address[mysqld] \\ \hline

9 & Troubles installing MySQL5 via  Darwin 
& Ordering
& Expected port[mysqld]=3306 BEFORE \\ & Ports
&&  socket[mysqld]=/tmp/mysql.sock \\ \hline

10 & Fail to install Percona xtraDB 
& Entry Missing
& Expected wsrep\_node\_address[mysqld] \\ & cluster on ubuntu 13.04
&&  in the same file as: wsrep\_sst\_method \\ &&& [mysqld] \\ \hline

11 & MySQL access denied for user rootlocalhost 
& Ordering
& Expected port[mysqld]=3306  \\ & &&   BEFORE socket[mysqld]= \\ &&& /tmp/mysql.sock
\\ \hline

12 & MySQL Partition Problem
& Correlation
& Expected innodb\_flush\_max  \\ & &&  \_commit[mysqld] $>=$ innodb \\ &&&  \_support[mysqld] \\ \hline

13 & mysql\_upgrade script problems on 
& Type Error
& Expected log-slow-queries[mysqld]  \\ & MySQL 5.0.24 
&&  should be a path type\\ \hline

14 & MySQL: bug report!!
& Ordering
& Expected innodb\_file\_io\_threads[mysqld]  \\ & 
&& BEFORE innodb\_log\_files\_in\_group[mysqld]\\ \hline

15 & MySQL max connections changed 
& Correlation
& Expected innodb\_file\_per\_table \\ & without notice
&&  [mysqld] $<=$ max\_connections[mysqld]  \\ \hline

16 & Enabling log in MySQL 5 6 
& Type Error
& Expected sql\_mode[mysqld] should  \\ & prevents server from starting
&&  be a string \\ \hline

17 & MySQL needs help for rapidly growing 
& Correlation
& Expected innodb\_buffer\_pool\_size \\ & table and decreasing speed
&&  [mysqld] $>$ sort\_buffer\_size[mysqld] \\ \hline

18 & MySQL filled all RAM on the system
& Correlation
& Expected join\_buffer\_szie * \\ & && max\_connections $<=$ key\_buffer\_size \\ \hline

19 & MySQL hit a max limit
& Correlation
& Expected join\_buffer\_size * \\ &&& max\_connections $<=$ key\_buffer\_size \\ \hline

20 & Cannot create a new thread
& Correlation
& Expected join\_buffer\_size * \\ &&& max\_connections $<=$ key\_buffer\_size \\ \hline

\end{tabular}
\end{small}
\end{table*}

### 2016-05-09 OSDI/motiv.tex
stuff

@@
 
-In this section, we present several {\em tricky} configuration errors
-extracted from real-world examples. 
-The reason we call them tricky is that
-most existing efforts, \eg, learning-based checking
-efforts~\cite{zhang14encore, wang04automatic}, cannot detect
+In this section we illustrate functionality of \app on several non-trivial configuration errors
+extracted from real-world examples. Although the errors are relatively simple, we call them 
+non-trivial, because the majority of existing tools, \eg, learning-based checking
+tools~\cite{zhang14encore, wang04automatic}, cannot detect
 these configuration errors. We investigated 

### 2016-05-09 OSDI/abs.tex
config: abs

@@
 entry missing errors, and environment-related errors. 
-%Our tool, named \app, relies on an abstract representation of language 
-%rules to allow for this modularity. 
-\ennan{One or two sentences here describe the most important
-experimental results. For example, we verify real-world misconfiguration 
-files and find 95\% errors are detected.}
+Our experiment shows \app is able to detect 83\% errors from
+a real-world dataset with 261 incorrect MySQL configuration files.

### 2016-05-09 OSDI/learner.tex

@@
 
-The goal of learner module is to derive rules and constraints from
+The goal of the learner module is to derive rules and constraints from
 the intermediate representation generated by the translator.
-In general, the learner module has two parts.
-The first part ($\S$\ref{subsec-rules}) 
-is to learn rules to check configuration errors like
-missing entry, ordering errors, and fine-grained value correlation errors. 
+It has two components.
+The first component ($\S$\ref{subsec-rules}) 
+learns rules for checking misconfiguration errors like
+missing entry, ordering, and fine-grained value correlation errors. 
 These errors tend to cause total system failures.
@@
 %the user may choose to invoke a more sensitive constraint checker. 
-The second part of the learner ($\S$\ref{subsec-constraints}) 
+The second component ($\S$\ref{subsec-constraints}) 
 aims to derive 
 constraints on entries to check for suspicious (or anomalous) values 
-that may violate standard practice (like the example~4 in
-$\S$\ref{sec-motiv}).
+that may violate standard practice. These anomalies can cause partial 
+degradation of the system, such as significant reduction in performance, or even 
+total failure as in Example~4 of $\S$\ref{sec-motiv}.
 
@@
 
-The first part of the learner is to learn rules 
-that must hold over multiple parts of a configuration file.
+The first component learns rules that must hold over 
+multiple parts of a configuration file.
 
@@
 a set of correct configuration files as a learning set, 
-from which it was possible to derive rules 
+from which it is possible to derive rules 
 that must hold with absolute certainty. 
-However, in practice, it is difficult to obtain a set of files 
+In practice, however, it is difficult to obtain a set of files 
 that is both guaranteed to be without misconfiguration 

### 2016-05-09 OSDI/learner.tex
config: learner

@@
 the intermediate representation generated by the translator.
-It has two components.
+In general, the learner module has two components.
 The first component ($\S$\ref{subsec-rules}) 
-learns rules for checking misconfiguration errors like
-missing entry, ordering, and fine-grained value correlation errors. 
+learns rules for checking configuration errors like
+entry missing, ordering errors, and fine-grained value correlation errors. 
 These errors tend to cause total system failures.
@@
 that may violate standard practice. These anomalies can cause partial 
-degradation of the system, such as significant reduction in performance, or even 
+degradation of the system, 
+such as significant reduction in performance, or even 
 total failure as in Example~4 of $\S$\ref{sec-motiv}.
@@
 
-The first component learns rules that must hold over 
-multiple parts of a configuration file.
+The first component learns rules 
+that must hold over multiple parts of a configuration file.
 
@@
 
-A rule will be reported as broken if the probability the rule is correct, $\Pi$, is greater than some user defined constant, $p$.
-This constant can be adjust to the user's preference.
-A small $p$ will increase the likelihood of finding an error, but also increase the number of false positives that are reported.
+A rule will be reported as broken if the probability the rule is
+correct, $\Pi$, is greater than some user defined constant, $p$. This
+constant can be adjust to the user's preference. A small $p$ will
+increase the likelihood of finding an error, but also increase the
+number of false positives that are reported.
+
+\ennan{So far, it is still not clear what does 
+our claimed language model look like?}
 

### 2016-05-09 OSDI/learner.tex
progress to strawman

@@
 \para{A strawman solution.}
-We now first present a strawman solution (employed by
+We first present a strawman solution (employed by
 previous work~\cite{santolucitoCAV, zhang14encore}) that uses 
@@
 the learning set. This behavior can be formally described as follows:
+\begin{small}
+\begin{align*}
+C :=&\ \text{Correct Learning Set}\\
+LR :=&\ \text{Learned Rules} :: \{\textrm{Rule}\}\\
+RR :=&\ \text{Reported Rules} :: \{\textrm{Rule}\}\\ 
+C =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
+LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file)\} \\
+RR =&\ \{ r\ \mid r \in LR \ \land \neg\ holds(r,\textrm{user file}) \}\\
+\end{align*}
+\end{small}
+In the above, the ":: \{Rule\}" notation indicates that the $LR$ learned rules 
+and $RR$ reported rules are sets of rules.
+A rule is only committed to the $LR$ learned rule set if 
+the rule holds on all files in the training set $C$, as denoted by the $\forall$ quantifier. 
+A broken rule is reported to the user in the $RR$ rule set if the rule is in $LR$, 
+but does not hold on the input user file.
 
-\begin{small}
-\begin{flalign*}
-C =&\ \text{Correct Learning Set}\\
-\text{::}\ & \text{\{Configuration Files in Intermediate Representation\}}\\
-LR =&\ \text{Learned Rules :: \{Rule\}}\\
-RR =&\ \text{Reported Rules :: \{Rule\}}\\ 
-LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file)\} \\
-RR =&\ \{ r\ \mid r \in L\ \land \neg\ holds(r,userfile) \}
-\end{flalign*}
-\end{small}
-
-Each rule can be thought of as a mapping from 
+Each rule can be viewed as a mapping from 
 lines $j$ and $k$ in a configuration file to a relation, $R$.

### 2016-05-10 OSDI/motiv.tex
ruzica

@@
 tools~\cite{zhang14encore, wang04automatic}, cannot detect
-these configuration errors. We investigated 
-many misconfiguration problems in practice which were caused by 
-these tricky configuration errors, such as those reported on StackOverflow.
+these configuration errors. Most of the presented examples were found on StackOverflow,
+a popular question and answer website for programmers. To better understand problems that users have with 
+configuration files, we explored and analyzed a large number of user forums and on-line discussion sites, focused on misconfigurations.
 
 \para{Example~1: Ordering error.} 
-The first class of configuration errors we handle was first reported by 
-Yin {\em et al.}~\cite{yin11anempirical}.
-For instance, when a user configures PHP to run with the
-Apache HTTP Server, this user might write, amongst others, 
-the following lines in the configuration file.
-
+Ordering errors were reported by Yin {\em et al.}~\cite{yin11anempirical} and our first
+example illustrates how ordering errors can cause a system to crash. When a user configures PHP 
+to run with the
+Apache HTTP Server, most likely the user will take some already existing configuration files and adapt them
+to suite her needs. The configuration file might contain, among others, 
+the following lines:
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
@@
 
-Such a configuration file will cause the Apache server to 
-fail to start due to a segmentation fault error~\cite{yin11anempirical}. 
-This is because when using PHP in Apache, the extension {\tt mysql.so} 
-depends on {\tt recode.so}, and the relative ordering of two of them 
+This configuration file will cause that the Apache server will
+fail to start due to a segmentation fault error. 
+This is because, when using PHP in Apache, the extension {\tt mysql.so} 
+depends on {\tt recode.so}, and their relative ordering
 is crucial. 
-We call the above example misconfiguration 
+We call the above example of a misconfiguration file
 an {\em ordering error}.
-Yin {\em et al.} find that ordering errors widely exist in
+Yin {\em et al.} report that ordering errors widely exist in
 many system configurations, \eg, PHP and MySQL,
-and typically lead to multiple system crash events;
-however, there is no existing effort that can effectively solve 
+and typically lead to multiple system crash events.
+However, none of existing tools can effectively solve 
 or detect this problem~\cite{zhang14encore, xu15systems, xu13do}.
 
-By using \app, the user can avoid such a configuration error.
-In particular, \app is able to inform the user that {\tt recode.so} 
+By invoking \app, the user can detect such a configuration error.
+In particular, \app reports that {\tt recode.so} 
 should appear before {\tt mysql.so}, as shown
-below.
+below:
 
@@
 \para{Example~2: Fine-grained value correlation error.} 
-In a real-world misconfiguration example~\cite{correlation}, 
-a user configures his MySQL as the following.
+Our next real-world misconfiguration example~\cite{correlation} comes from a discussion on StackOverflow.
+The user has configured his MySQL as the following:
 
@@
 
-This user complained that her MySQL load was very high, causing the website's
+The user the complains that her MySQL load was very high, causing the website's
 respond speed to be very slow.
@@
 
-We call the above situation a {\em fine-grained value correlation
-error}, which is a more challenging case than 
-{\em value correlation error} reported
-by some existing investigations~\cite{yin11anempirical, zhang14encore}.
-A typical value correlation error
-means one entry's value should have a certain correlation with
-another entry's value. For example, in MySQL,
-the value of {\tt max\_connections} should be higher than
-{\tt mysql.max\_persistent}. Although some work, \eg,
-EnCore~\cite{zhang14encore}, can detect the normal value
-correlation case, 
-no existing effort can detect fine-grained value correlation
-errors, which ``hide'' equation-aware correlations, as shown in
-the above example.
-As mentioned by Xu {\em et al.}~\cite{xu15hey},
-detecting fine-grained value correlation errors 
-is a much more challenging
-task than the normal value correlation problem.
-
-To the best of our knowledge, \app is the first effort that
-is able to check such fine-grained value correlation problems.
 If we run \app on this configuration file, \app  would return:
@@
 
-Compared with \app, existing efforts, \eg, EnCore, cannot 
-detect fine-grained value correlation errors.
+We can see that during the learning process we do not learn only simple statements, that compare two values, 
+but we also learn more complex correlations. We call them {\em fine-grained value correlations}, and the error
+a fine-grained value correlation
+error. This types of errors are more sophisticated than simple value correlations that some tools can detect~\cite{yin11anempirical, zhang14encore}.
+A typical value correlation error
+states that one entry's value should have a certain correlation with
+another entry's value. For example, in MySQL,
+the value of {\tt max\_connections} should be higher than
+{\tt mysql.max\_persistent}.
 
-\para{Example~3: Entry missing error.} 
+Our tool can learn this simple correlations as well, but learning more complex properties requires a different 
+approach to the learning 
+process. We need to track several variables. It is not enough just to compare them, but we need to learn, as in this particular case, which
+invariant do they have to preserve. It was pointed out by Xu {\em et al.}~\cite{xu15hey} that
+detecting fine-grained value correlation errors 
+is a much more challenging
+task than the normal value correlation problem.
+
+To the best of our knowledge, \app is the first tool that
+is able to check such fine-grained value correlation problems.
+
+\para{Example~3: Missing entry error.} 
 Many critical system outages result from the fact that an important
 entry was missing in the configuration file. 
-We call such a problem an {\em entry missing error}.
+We call such a problem an {\em missing entry error}.
 In a public misconfiguration dataset~\cite{configdataset},
@@
 When using the password policy overlay in OpenLDAP, 
-users have to first include the related schema.
-Leaving out the {\tt include} entry, 
+users must first include the related schema.
+Leaving out the {\tt include schema/ppolicy.schema} entry, 
 as done by many users~\cite{yin11anempirical}, 
-will cause failure of this LDAP. 
-The user can run \app on such a misconfiguration file,
-and \app would return:
+causes the failure of LDAP. 
+If the user runs \app on such a misconfiguration file,
+\app would return:
 

### 2016-05-10 OSDI/impl.tex
config: impl

\section{Implementation}

\ennan{We need to describe how do we implement each module. We may need to
have three paragraphs: one is for translator, one is for learner 
and one is for checker.}

### 2016-05-10 OSDI/intro.tex
config: impl

@@
 
-Secondly, without templates, learning rules and constraints is a challenge. 
-\ennan{Here, we need to add one-paragraph description 
-to illustrate how we learn rules without templates, 
-or why we say our learning results are better than existing
-learning approach, \eg, EnCore.}
+Second, without templates, learning rules and constraints is 
+another challenge.
+Rather than relying on pre-defined templates or 
+manually correcting training set,
+we introduce and perform probabilistic learning approaches 
+on probabilistically typed representations
+generated in the transformation phase.
+The learning process first analyzes the occurrences of each pair
+of entries in the training set, 
+then computes the likelihood that each pair can constitute a rule, 
+and finally derive many rules.
 

### 2016-05-10 OSDI/intro.tex
ruzica

@@
 but all of the files in the sample need to be of the same type (such as
-MySQL or httpd configuration files). From that sample,
+MySQL or httpd configuration files).
+From that sample,
 \app learns an abundant set of rules specifying various properties that hold on the given sample. The files in the sample might contain
-errors -- we are, therefore, using probabilistic learning to derive a set of accurate rules. One can see this learning process as a
+errors -- we are, therefore, using probabilistic learning to derive a set of accurate rules.
+
+For practical purposes we use the dataset given at~\cite{configdataset}. Every file in our dataset contains an error, but it is 
+always a different error and it only appears in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
+accurate set of rules. The rules in general specify what properties do variables need to satisfy. One can see this learning process as a
 way of deriving  
-a specification for configuration files. 
+a specification for configuration files.  Once there is a specification, we can start with formal verification. With these rules we can efficiently check the correctness of the configuration files
+of interest and detect potential errors.
+
 The learning process works in two phases. In the first phase, 
@@
 In the second phase, \app derives rules and constraints by analyzing
-the intermediate representations.  The set of learned rules is accurate and we are able to efficiently check 
-the correctness of the configuration files
-of interest and detect potential errors.
-Compared with previous efforts,
-\app does not necessarily rely on users' templates 
-and is capable of detecting intricate configuration errors that
-cannot be identified by existing work (details in $\S$\ref{sec-motiv}).
+the intermediate representations.  Every learned rule is annotated with a probability depicting in
+which percentage of the files the rule was seen as correct. As learned rules we only select those rules whose 
+correctness probability is above the set threshold.
 
@@
 and finally derive many rules.
+
+Compared with previous efforts,
+\app does not only rely on users' templates, it learns the rules about  
+and is capable of detecting intricate configuration errors that
+cannot be identified by existing work (details in $\S$\ref{sec-motiv}).
 

### 2016-05-10 OSDI/motiv.tex
ruzica

@@
 \para{Other errors.}
-\app can also deal with the configuration errors that can be detected by
+In addition to the given motivating examples \app can also detect and report configuration errors that can be exposed by
 existing work, such as EnCore~\cite{zhang14encore} and
-CODE~\cite{yuan11context}.
+CODE~\cite{yuan11context} (a full scope of \app's capabilities is given in $\S$\ref{sec-eval}).
 A recently reported configuration error made the MySQL
@@
 Furthermore, \app is also able to detect type errors and syntax errors
-in configuration files.
+in configuration files. An example of a type error is assigning to a variable {\tt {general\_log}} 
+a file path {\tt {/var/log/mysql/mysql.log}}. \app successfully reports this typing error: 
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
+TYPE ERROR: Expected a Int with P=1.0 for "general_log[mysqld]"
+\end{lstlisting}

### 2016-05-10 OSDI/trans.tex
ruzica

@@
 typed and well-structured representations.
-In some sense, the translator looks like a parser, and it is only
+The translator can be seen a parser, and it is only
 used to generate an intermediate representation for the post

### 2016-05-10 OSDI/eval.tex
ruzica
config: impl
config: first part in eval

@@
-\section{Implementation}
+\section{Evaluations}
+\label{sec-eval}
 
-\ennan{We need to describe how do we implement each module. We may need to
-have three paragraphs: one is for translator, one is for learner 
-and one is for checker.}
-
-\section{Evaluations}
-
-We mainly conduct three parts of experiments to evaluate our \app
+We conduct three parts of experiments to evaluate our \app
 prototype. We want to answer several questions:
@@
 
-\subsection{\app's effectiveness}
+\subsection{\app's Effectiveness}
 
-In order to evaluate the effectiveness of \app, we extract
-20 misconfiguration files from a MySQL dataset~\cite{xu15hey},
-and perform \app on them. \ennan{Here, we first need a table to 
-list each configuration error with error type, description,
-and whether \app correctly reports the issues.}
+We now apply \app to check against real-world misconfiguration problems.
+We use a real misconfiguration dataset~\cite{xu15hey}
+that are collected from several online forums, \eg, 
+Stack Overflow and MySQL forum.
+Each configuration file in this dataset was posted by 
+programmers or system administrators, 
+when they confront the misconfiguration issues in practice.
+This dataset contains 261 incorrect MySQL configuration files.
 
-Next, we inject some errors to correct configuration files,
-and run \app to check whether our framework can correctly detect
-these injected errors. \ennan{We also need a table here, 
-and list each injected problem.}
+We apply \app to learn and check the configuration files in this
+dataset. Then, we observe how many errors \app can detect,
+and manually check whether these detected errors are indeed
+configuration errors.
+For all the 261 configuration files, we found \app is
+able to report all the errors correctly.
+For 217 of the 261 configuration files, we found \app's 
+error detection results are correct and accurate,
+\ie, correctly report the real misconfiguration problem.
+However, for 44 of them, \app outputs relatively high false positives,
+\eg, higher than 50 false positives,
+which is not very helpful to users in practice.
+The reason is our training set contains too many incorrect configuration
+files, which produce a lot of noises to our learning process,
+thus resulting in so many false positives.
 
-Finally, we check suspicious values.
+In order to clearly evaluate the effectiveness of \app,
+we extract 20 incorrect configuration files from the dataset.
+As a case study, we present the problem descriptions of these files, 
+the types of their errors, and the outputs produced by \app.
+Table~\ref{table-casestudy} details this information.
+
+As shown in Table~\ref{table-casestudy},
+we found \app is capable of detecting many configuration errors previous
+efforts, \eg, EnCore~\cite{zhang14encore}, cannot deal with.
+To the best of our knowledge, no existing effort
+is able to detect fine-grained value correlation errors in the 
+MySQL configuration files.
+For example, the third case in Table~\ref{table-casestudy}
+presents \app detects the fine-grained correlation,
+{\tt key\_buffer\_size} should be larger than 
+{\tt sort\_buffer\_size} * {\tt max\_connections}.
 

### 2016-05-10 OSDI/eval.tex
config: eval

@@
 
-We conduct three parts of experiments to evaluate our \app
-prototype. We want to answer several questions:
+We conduct three experiments to evaluate our \app
+prototype. Our experiments aim to answer the following
+questions.
 
@@
 
-\item Whether \app can detect real-world configuration errors?
+\item Whether \app can successfully 
+  detect real-world configuration errors?
 
-\item How does the size of training dataset impact on the correctness
-  of \app?
+\item Whether \app can correctly detect anomalous values?
 
-\item What is the rule inference accuracy?
-
-\item How long can we run the verification?
+\item How long do training and verification last?
 
@@
 
-\subsection{Training Set Impact}
+\subsection{Detecting Anomalous Values}
 
-In this experiment, we vary the number of training configuration files,
-and observe whether the correctness of \app would increase 
-accordingly. \ennan{We may need a table whose x-axis is the number
-of entries in the training configuration files, and y-axis is the 
-accuracy or something close.}
+The purpose of checking anomalous values in configuration files 
+is to avoid potential performance or workload problems. 
+Checking anomalous values is mainly the responsibility of
+the second sub-module checker of \app (see $\S$\ref{sec-checker}).
+
+We run \app to check 30 real-world benchmarks from Stack Overflow 
+website, and found \app is able to report anomalous values in
+these configurations. We also manually check whether these
+anomalous values are correct by comparing our results with
+the answers on Stack Overflow.
+
+Table~\ref{table-anomaly} shows three examples.
+We present the problem description, the link and the output results
+of \app. We found these anomalous values are very hard for
+administrators or users to detect, because they look correct.
+However, as shown in the links posted in Table~\ref{table-anomaly},
+such anomalous values typically lead to critical performance
+problems in practice.
 

### 2016-05-10 OSDI/intro.tex
ruzica

@@
 
+Finally, we checks whether a
+given variable
+
 Building such an automatic verification framework for
@@
 
-Second, without templates, learning rules and constraints is 
-another challenge.
-Rather than relying on pre-defined templates or 
-manually correcting training set,
-we introduce and perform probabilistic learning approaches 
-on probabilistically typed representations
-generated in the transformation phase.
-The learning process first analyzes the occurrences of each pair
-of entries in the training set, 
-then computes the likelihood that each pair can constitute a rule, 
-and finally derive many rules.
-
-Compared with previous efforts,
-\app does not only rely on users' templates, it learns the rules about  
-and is capable of detecting intricate configuration errors that
-cannot be identified by existing work (details in $\S$\ref{sec-motiv}).
+Second, when learning rules we use very general templates to 
+infer them. The user does not need to provide any templates -- they are internally associated to the types.
+Nevertheless, in addition to those general templates, we still need specific algorithms to learn
+rules that cannot be easily templated.
 

### 2016-05-10 OSDI/trans.tex
ruzica

@@
 
-The responsibility of the translator is to transform a given sample
+The translator takes as input a sample dataset of configuration files and transforms a given sample
 dataset of configuration files into another set of files written in

### 2016-05-10 OSDI/learner.tex
add an algorithm

@@
 Each rule can be viewed as a mapping from 
-lines $j$ and $k$ in a configuration file to a relation, $R$.
-
-\[
-\{ Rule = (a_j, a_k) | j \neq k \} \rightarrow \{ R \}
-\]
-
-Specifically, $a_j$ and $a_k$ are two different lines from our
-intermediate representation, or more formally, $j \neq k \land
-a_j, a_k \in \{ L \}$ where is the set of lines (key-value pairs) found
-in the learning set. The relation $R$
-is a Boolean function specific to the error to detect. 
-As an example, to detect the error that key $k_1$ must always 
-have a value greater than key $k_2$, the relation $R$ is $>$.
+attributes $a_j$ and $a_k$ in the intermediate representation of a 
+configuration file to a boolean function, $R$: this can be represented by a rule
+$r := (a_j, a_k) \rightarrow B_{rel}$.
+$B_{rel}$ is a Boolean function specific to the relation to assess, meaning that 
+the desired relation can either be satisfied or not satisfied. 
+For instance, for the rule that {\tt max\_connections} must 
+be greater than {\tt mysql.max\_persistent}, the relation of interest is $>$ 
+and $B_{>}$ would be set to true.
 
 \para{Our approach.}
-In \app's leaner module, the rule learning mechanism is tolerant 
+In \app's learner module, the rule learning mechanism is tolerant 
 enough to accept a dataset {\em full of} incorrect configuration files.
@@
 on our intermediate representations (generated by the translator).
+
+\begin{algorithm}
+\STATE Let $\theta$ be the list of possible types for the intermediate representation of interest.
+\caption{Probabilistically Learn Rules}
+  \begin{algorithmic}[1]
+    \STATE learnRules($C$):\\
+    Input: $C$ contains intermediate representations\\ 
+     \qquad \enspace \enspace of configuration files\\
+%    Intermediate Representation of configuration file, $M$, where the $i$-th entry of $M$ is denoted by $M_i$\\
+    \FOR{each file $F$ in $C$}
+        \FOR{each entry $e$ in $F$}
+               \IF{$g(e)$ is false}
+                        \STATE continue to next entry
+               \ENDIF
+                \FOR{$\tau \in typelist(e)$}
+                        \FOR{$t \in templates(\tau)$}
+                        \IF{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
+                                        \STATE update $p_{\tau}$ appropriately
+%                                \ELSIF{anti($t$) is satisfied over rest of entries}
+%                                        \STATE update $p_{\tau}$ appropriately
+                                \ENDIF
+                        %Check if $t$ is satisfied  over rest 
+                        \ENDFOR
+               \ENDFOR
+          \ENDFOR
+      \ENDFOR
+  \end{algorithmic}
+\end{algorithm}
+
+%each entry is listed as (g,k,v,typelist)
 

### 2016-05-10 OSDI/trans.tex
add an algorithm

@@
 Each of the entries in the intermediate representations
-have been assigned types, and these types would guide the learning
+have been assigned types, and these types guide the learning
 modules later.
 
-\ennan{We need a kind of formal definition (using a figure) to
-define the grammar of our intermediate representation. The basic
-view of this definition should be similar to define a type language
-grammar.}
-
-\para{Introducing probabilistic types.}
+\para{Probabilistic types.}
 For any key-value entry in the sample configuration files,
@@
 
+\para{Formal Intermediate Representation.}
+The formal grammar we use for our intermediate representation presented in the following. 
+Firstly, we make a list of the possible types for a configuration file. This is present in 
+Secondly, we
+
+\begin{table}
+  \begin{tabular}{| l | c | r |}
+    \hline
+    Type & Operation & 3 \\ \hline
+    4 & 5 & 6 \\ \hline
+    7 & 8 & 9 \\
+    \hline
+  \end{tabular}
+\caption{Table of Types Along with Operation Pools}
+\label{table:kysymys}
+\end{table}
+
+We come up with the following types:
+
+1. Port 
+The $i$-th entry inside an intermediate representation corresponding to a 
+translated file
+
+We declare a quadruple $(g,k,v,\{\tau_1, \ldots, \tau_n\}_i$
+We need a kind of formal definition (using a figure) to
+define the grammar of our intermediate representation. The basic
+view of this definition should be similar to define a type language
+grammar.
+
 \com{Note that typing is also a system module than 

### 2016-05-10 OSDI/learner.tex
tmp fix

@@
 
-\begin{algorithm}
-\STATE Let $\theta$ be the list of possible types for the intermediate representation of interest.
-\caption{Probabilistically Learn Rules}
-  \begin{algorithmic}[1]
-    \STATE learnRules($C$):\\
-    Input: $C$ contains intermediate representations\\ 
-     \qquad \enspace \enspace of configuration files\\
+%\begin{algorithm}
+%\STATE Let $\theta$ be the list of possible types for the intermediate representation of interest.
+%\caption{Probabilistically Learn Rules}
+%  \begin{algorithmic}[1]
+%    \STATE learnRules($C$):\\
+%    Input: $C$ contains intermediate representations\\ 
+%     \qquad \enspace \enspace of configuration files\\
 %    Intermediate Representation of configuration file, $M$, where the $i$-th entry of $M$ is denoted by $M_i$\\
-    \FOR{each file $F$ in $C$}
-        \FOR{each entry $e$ in $F$}
-               \IF{$g(e)$ is false}
-                        \STATE continue to next entry
-               \ENDIF
-                \FOR{$\tau \in typelist(e)$}
-                        \FOR{$t \in templates(\tau)$}
-                        \IF{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
-                                        \STATE update $p_{\tau}$ appropriately
+%    \FOR{each file $F$ in $C$}
+%        \FOR{each entry $e$ in $F$}
+%               \IF{$g(e)$ is false}
+%                        \STATE continue to next entry
+%               \ENDIF
+%                \FOR{$\tau \in typelist(e)$}
+%                        \FOR{$t \in templates(\tau)$}
+%                        \IF{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
+%                                        \STATE update $p_{\tau}$ appropriately
 %                                \ELSIF{anti($t$) is satisfied over rest of entries}
 %                                        \STATE update $p_{\tau}$ appropriately
-                                \ENDIF
+%                                \ENDIF
                         %Check if $t$ is satisfied  over rest 
-                        \ENDFOR
-               \ENDFOR
-          \ENDFOR
-      \ENDFOR
-  \end{algorithmic}
-\end{algorithm}
+%                        \ENDFOR
+%               \ENDFOR
+%          \ENDFOR
+%      \ENDFOR
+%  \end{algorithmic}
+%\end{algorithm}
 

### 2016-05-10 OSDI/intro.tex
ruzica

@@
 always a different error and it only appears in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
-accurate set of rules. The rules in general specify what properties do variables need to satisfy. One can see this learning process as a
+accurate set of rules. The rules, in general, specify which properties do variables need to satisfy. One can see this learning process as a
 way of deriving  
-a specification for configuration files.  Once there is a specification, we can start with formal verification. With these rules we can efficiently check the correctness of the configuration files
+a specification for configuration files.  Once there is a specification, we can do a formal verification. With these 
+rules we can efficiently check the correctness of the configuration files
 of interest and detect potential errors.
@@
 the intermediate representations.  Every learned rule is annotated with a probability depicting in
-which percentage of the files the rule was seen as correct. As learned rules we only select those rules whose 
-correctness probability is above the set threshold.
+which percentage of the files the rule was seen as correct. We only accept those rules whose 
+correctness probability is above the given threshold.
 
-Finally, we checks whether a
-given variable
+Finally, while the learned rules establish correlations between two or more variables, using \app one can also detect whether a
+single variable has an appropriate value assigned to it. We do that by measuring the values, that are typically assigned to that variable 
+and reporting if the current value deviates too much from the recorded values.
 

### 2016-05-10 OSDI/learner.tex
add algorithm

--- 2016-05-10 OSDI/learner.tex
@@
 \begin{algorithm}
-\STATE Let $\theta$ be the list of possible types for the intermediate representation of interest.
+%\State Let $\theta$ be the list of possible types for the intermediate representation of interest.
 \caption{Probabilistically Learn Rules}
   \begin{algorithmic}[1]
-    \STATE learnRules($C$):\\
+    \State learnRules($C$):\\
     Input: $C$ contains intermediate representations\\ 
      \qquad \enspace \enspace of configuration files\\
-%    Intermediate Representation of configuration file, $M$, where the $i$-th entry of $M$ is denoted by $M_i$\\
-    \FOR{each file $F$ in $C$}
-        \FOR{each entry $e$ in $F$}
-               \IF{$g(e)$ is false}
-                        \STATE continue to next entry
-               \ENDIF
-                \FOR{$\tau \in typelist(e)$}
-                        \FOR{$t \in templates(\tau)$}
-                        \IF{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
-                                        \STATE update $p_{\tau}$ appropriately
-%                                \ELSIF{anti($t$) is satisfied over rest of entries}
-%                                        \STATE update $p_{\tau}$ appropriately
-                                \ENDIF
+    Intermediate Representation of configuration file, $M$, where the $i$-th entry of $M$ is denoted by $M_i$\\
+    \For{each file $F$ in $C$}
+        \For{each entry $e$ in $F$}
+               \If{$g(e)$ is false}
+                        \State continue to next entry
+               \EndIf
+                \For{$\tau \in typelist(e)$}
+                        \For{$t \in templates(\tau)$}
+                        \If{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
+                                        \State update $p_{\tau}$ appropriately
+                                \ElsIf{anti($t$) is satisfied over rest of entries}
+                                        \State update $p_{\tau}$ appropriately
+                                \EndIf
                         %Check if $t$ is satisfied  over rest 
-                        \ENDFOR
-               \ENDFOR
-          \ENDFOR
-      \ENDFOR
+                        \EndFor
+               \EndFor
+          \EndFor
+      \EndFor
   \end{algorithmic}

### 2016-05-10 OSDI/impl.tex
starting on implementation

@@
 and one is for checker.}
+
+\app is primarily implemented in Haskell, but the suspicious values module was written in R.
+The suspicious value module re implements the main functionality of the Haskell system, and is is a testament to the simplicity of the algorithm and the ease of reproduction.
+For clarity, we only present the key components of the Haskell implementation here.
+
+The translator is a simple parser for a small grammar, as described in ($\S$\ref{sec-trans}). The implementation presented no interesting challenges.
+
+The learning and checking steps of the algorithm are designed to allow for extensibility by new users.
+In order to verify a configuration file against a new type of error, the user must provide a new type that is an instance of the \textit{Attribute} typeclass (\ie define some functions over that type).
+In particular, for each type of error the use wishes to detect, they must implement three functions; learn, merge, and check.
+
+\begin{lstlisting}
+class Foldable t => RuleSet t a where
+  learn :: IRConfigFile -> t a
+  merge :: t a -> t a -> t a
+  check :: t a -> IRConfigFile -> [Error]
+\end{lstlisting}
+
+This typeclass is polymorphic over the data structure as denoted by \lstinline{Foldable t =>}, which means user can choose any data structure they prefer.
+In general, the best data structure is a hashmap from key-value pairs to relations, previously defined as a \textit{P\_Rule} in ($\S$\ref{subsec-rules}).
+
+The \lstinline{learn} function will take the intermediate representation of a single configuration file (as generated by the translator), and generate the set of rules that can be derived from that file.
+The \lstinline{merge} function will unify two sets of rules, from two separate configuration files, into a single consistent set of rules.
+For the probabilistic rules, this is simply a union tends to a summation of the  over be a
+The \lstinline{merge} function
+
+The \lstinline{check} function will start will all the rules we have learned, and filter until we only have the rules that have been broken by the file of interest.
+We first eliminate the rules that pass the probability check defined in ($\S$\ref{subsec-rules}).
+Second, we only consider the rules which are relevant to the file - we do not need to check rules about keywords which do not appear in the file.
+Lastly, we take the errors as any rule that does not hold over the given file.
+
+A sketch of a typical implementation of these three functions is shown below. Again, the specifics of this implementation will vary based on the type of error being detected.
+
+\begin{lstlisting}
+learn f = 
+  count_relation_events (all_line_pairs f)
+merge s1 s2 = 
+  unionWith sum s1 s2
+check rs f = 
+  likely_rs  = filter prob_check rs
+  related_rs = filter applies_to_file likely_rs
+  errors_rs  = filter (is_valid f) related_rs
+ in errors
+\end{lstlisting}
+
+The core learning algorithm is simply a fold using \lstinline{merge} over the derived rules from running \lstinline{learn} on each file in the learning set.
+
+Since we learn a set of rules on each file in isolation from the other, we have a pleasingly parallel situation.
+Haskell allows us to easily take advantage of this by using the parallel
+mapping library \cite{parallel}, both for translation to the intermediate representation, and for learning the rules on each file.
+The merge stage could also easily be parallelized, using a divide and conquer approach, but \app runs fast enough over our learning set (28 files, 961 lines of code) that this has not been necessary.
+
+The tool is freely available for download at \url{--redacted--}.

### 2016-05-10 OSDI/learner.tex
starting on implementation

@@
 \text{::}\ & \text{\{Configuration Files in Intermediate Representation\}}\\
-LP =&\ \text{Learned Probabilistic Rules :: \{(P\_Rule)\}}\\
-RP =&\ \text{Reported Probabilistic Rules :: \{(P\_Rule)\}}\\
+LP =&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
+RP =&\ \text{Reported Probabilistic Rules :: \{P\_Rule\}}\\
 LP =&\ \text{count\_relation\_occurrences}(I)\\

### 2016-05-10 OSDI/limit.tex
starting on implementation

@@
 \para{Legal misconfigurations.}
-While \app can check diverse configuration errors without
-human participations, most of the existing proactive 
+While \app can check for diverse configuration errors without
+human intervention, most of the existing proactive 
 misconfiguration detection techniques,

### 2016-05-10 OSDI/main.tex
config: abs
config: abs and intro
config: abs, intro and motiv
jc's file
config: more update
start
config: learner
overview of probabilistic​ learning
config: impl
add an algorithm
add algorithm
starting on implementation

@@
 \usepackage{usenix}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+%\usepackage{algorithmic}
 
@@
 %\usepackage{natbib}
-\usepackage{balance}
 \usepackage{hhline}
@@
 %\usepackage[compact]{titlesec}
-\usepackage{xcolor}
+%\usepackage{xcolor}
 %\usepackage[algoruled,vlined,ruled,linesnumbered]{algorithm2e}
 \usepackage{lipsum}
-%\usepackage{courier}
 \usepackage{listings}
+
 \lstset{
-  language=C,
-	basicstyle=\footnotesize\ttfamily,breaklines=true
+  basicstyle=\footnotesize\ttfamily,
+  breaklines=true,
+  frame=bottomline,
+  language=haskell,
+  %identifierstyle=\color{identifierColor},
+  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
+  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
+  %captionpos=b,                    % sets the caption-position to bottom
+  %commentstyle=\color{mygreen},    % comment style
+  %frame=single,	                   % adds a frame around the code
+  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
+  keywordstyle=\color{blue},       % keyword style
+  otherkeywords={*,let, Server, Replication, FaultGraph, rankRCG, print, fialProb, goal, ...},           % if you want to add more keywords to the set
+  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
+  numbersep=5pt,                   % how far the line-numbers are from the code
+  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
+  showtabs=false,                  % show tabs within strings adding particular underscores
+  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
+  %title=\lstname                  % show the filename of files included with \lstinputlisting; also try caption instead of title
+  mathescape=true,
+  tabsize=3,
+  literate=*{->}{{\textcolor{blue}{$\to$}}}{1}
+           {<-}{{\textcolor{blue}{$\leftarrow$}}}{1}
 }
 
-%\usepackage[T1]{fontenc}
-%\usepackage[scaled=0.78]{DejaVuSansMono}
+\usepackage[T1]{fontenc}
+%Ruzica\usepackage[scaled=0.78]{DejaVuSansMono}
 
@@
 \long\def\ennan#1{{\color{blue}{\bf Ennan: }{\small [#1]}}}
+\long\def\markk#1{{\color{violet}{\bf Mark: }{\small [#1]}}}
 \long\def\ruzica#1{{\color{red}{\bf Ruzica: }{\small [#1]}}}
+\long\def\jon#1{{\color{orange}{\bf Jon: }{\small [#1]}}}
 %\long\def\xxx#1{}
@@
 % system related terms
-\newcommand{\app}{ConfigC\xspace}
+\newcommand{\app}{ConfigV\xspace}
 
@@
 
-\title{Probabilistic Automated Language Learning for Configuration Files}
+\title{An Automatic Verification Framework for Software Configurations}
 
@@
 \input{learner}
+%\input{learner-ranges}
 \input{check}
 \input{limit}
+\input{impl}
 \input{eval}

### 2016-05-10 OSDI/impl.tex
maybe i didnt send everything?

@@
 The \lstinline{check} function will start will all the rules we have learned, and filter until we only have the rules that have been broken by the file of interest.
-We first eliminate the rules that pass the probability check defined in ($\S$\ref{subsec-rules}).
+We first eliminate the rules that do not pass the probability check defined in ($\S$\ref{subsec-rules}).
 Second, we only consider the rules which are relevant to the file - we do not need to check rules about keywords which do not appear in the file.
@@
 Since we learn a set of rules on each file in isolation from the other, we have a pleasingly parallel situation.
-Haskell allows us to easily take advantage of this by using the parallel
-mapping library \cite{parallel}, both for translation to the intermediate representation, and for learning the rules on each file.
-The merge stage could also easily be parallelized, using a divide and conquer approach, but \app runs fast enough over our learning set (28 files, 961 lines of code) that this has not been necessary.
+Haskell allows us to easily take advantage of this by using the parallel mapping library \cite{parallel}, both for translation to the intermediate representation, and for learning the rules on each file.
+The merge stage could also be parallelized, using a divide and conquer approach, but this is not a priority since the learning stage only needs to be run once per learning set, and can then be cached (in our case, as a .json file) for fast reading when doing verification.
 

### 2016-05-10 OSDI/learner.tex
add algorithm

@@
 \begin{algorithm}
-%\State Let $\theta$ be the list of possible types for the intermediate representation of interest.
 \caption{Probabilistically Learn Rules}
+  Let $\theta$ be the list of possible types for the intermediate representation of interest.
   \begin{algorithmic}[1]
-    \State learnRules($C$):\\
+  \State \textbf{learnRules}($C$):\\
+
     Input: $C$ contains intermediate representations\\ 
      \qquad \enspace \enspace of configuration files\\
-    Intermediate Representation of configuration file, $M$, where the $i$-th entry of $M$ is denoted by $M_i$\\
+
     \For{each file $F$ in $C$}
-        \For{each entry $e$ in $F$}
+      \For{each $\tau \in \theta$}
+        \State $R = \{\}$
+        \State $Q = filter(F,\tau)$ 
+        \State // $Q$ contains entries in $F$ with $\tau$ in type list
+        \For{each entry $e$ in $Q$}
                \If{$g(e)$ is false}
                         \State continue to next entry
-               \EndIf
-                \For{$\tau \in typelist(e)$}
-                        \For{$t \in templates(\tau)$}
-                        \If{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
-                                        \State update $p_{\tau}$ appropriately
-                                \ElsIf{anti($t$) is satisfied over rest of entries}
-                                        \State update $p_{\tau}$ appropriately
+                        \Else \enspace $R = R  \cup  \textrm{constructRules}(e, \tau, Q)$
                \EndIf
@@
         \EndFor
+     \State Update $p_{\tau}$ appropriately
      \EndFor
     \EndFor
+  \end{algorithmic}
+\end{algorithm}
+
+%                \For{$\tau \in typelist(e)$}
+%                        \For{$t \in templates(\tau)$}
+%                        \If{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
+%                                        \State update $p_{\tau}$ appropriately
+%                                \ElsIf{anti($t$) is satisfied over rest of entries}
+%                                        \State update $p_{\tau}$ appropriately
+%                                \EndIf
+
+\begin{algorithm}
+\caption{constructRules}
+  \begin{algorithmic}[1]
+  \State \textbf{constructRules}($e, \tau, Q$):\\
+    Input: entry $e$ from intermediate representation\\ 
+     \qquad \enspace \enspace type $\tau$\\
+     \qquad \enspace \enspace set of entries $Q$\\
+     $R = \{\}$
+     \For{each $t \in templates(\tau)$}
+      \State Let $P$ be the set of permutations of distinct entries from $Q$, with arity of $t$, containing $e$
+      \For{each $p \in P$}
+%      \State Let an entry in $D$ be represented by $(e, e_1, e_2, \ldots)$
+      \State Construct the rule $r$ corresponding to $t(v(e_1), v(e_2), \ldots, v(e), \ldots, v(e_{n-1}), v(e_n))$.
+      \If{$r$ is satisfied}
+        $R = R \cup r$
+      \EndIf
      \EndFor
+     \EndFor
+     \State return $R$
   \end{algorithmic}

### 2016-05-10 OSDI/learner.tex
cleaner algorithm

@@
 
-    Input: $C$ contains intermediate representations\\ 
+  Input: set $C$ contains intermediate representations\\ 
      \qquad \enspace \enspace of configuration files\\
 
+    \State $R = \{\}$ // denotes rule set
+    \State $P$ // denotes probabilities associated with rule set
     \For{each file $F$ in $C$}
       \For{each $\tau \in \theta$}
-        \State $R = \{\}$
         \State $Q = filter(F,\tau)$ 
         \State // $Q$ contains entries in $F$ with $\tau$ in type list
+        \State $RM$ contains entries in remove set
         \For{each entry $e$ in $Q$}
@@
                         \State continue to next entry
-                        \Else \enspace $R = R  \cup  \textrm{constructRules}(e, \tau, Q)$
+                        \Else \enspace $CR = \textrm{constructRules}(e, \tau, Q \backslash RM)$
+                        \State $R = R  \cup CR$
+                        \State For each $r \in CR$, update $P$ 
                \EndIf
-                        %Check if $t$ is satisfied  over rest 
-        \EndFor
-     \State Update $p_{\tau}$ appropriately
+               \State $RM = RM \cup e$
         \EndFor
      \EndFor
+    \EndFor
+    \State Based on $P$, accept rules in $R$ according to threshold. 
   \end{algorithmic}
 \end{algorithm}
-
-%                \For{$\tau \in typelist(e)$}
-%                        \For{$t \in templates(\tau)$}
-%                        \If{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
-%                                        \State update $p_{\tau}$ appropriately
-%                                \ElsIf{anti($t$) is satisfied over rest of entries}
-%                                        \State update $p_{\tau}$ appropriately
-%                                \EndIf
 
@@
   \begin{algorithmic}[1]
-  \State \textbf{constructRules}($e, \tau, Q$):\\
+  \State \textbf{constructRules}($e, \tau, S$):\\
     Input: entry $e$ from intermediate representation\\ 
      \qquad \enspace \enspace type $\tau$\\
-     \qquad \enspace \enspace set of entries $Q$\\
+     \qquad \enspace \enspace set of entries $S$\\
      $R = \{\}$
      \For{each $t \in templates(\tau)$}
-      \State Let $P$ be the set of permutations of distinct entries from $Q$, with arity of $t$, containing $e$
+        \State Let $n$ be the arity of $t$
+        \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$. 
         \For{each $p \in P$}
-%      \State Let an entry in $D$ be represented by $(e, e_1, e_2, \ldots)$
-      \State Construct the rule $r$ corresponding to $t(v(e_1), v(e_2), \ldots, v(e), \ldots, v(e_{n-1}), v(e_n))$.
+         \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
+           \For{$i = 1:n$}
+           \State Create a $n$-tuple by placing $e$ at the $i$-th place and filling the remaining entries with $p$, in order. Let this $n$-tuple be $u = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
+           \State $r = \textrm{constructRule}(u)$ 
             \If{$r$ is satisfied}
@@
         \EndFor
+     \EndFor
      \State return $R$
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{constructRule}
+  \begin{algorithmic}[1]
+  \State \textbf{constructRule}($u$):\\
+  Input: a tuple of entries, $u$, denoted by $(e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$ \\
+    \State return $t(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$.
   \end{algorithmic}

### 2016-05-10 OSDI/eval.tex
config: eval done

@@
 \item Whether \app can successfully 
-  detect real-world configuration errors?
+  detect real-world configuration errors ($\S$\ref{subsec-effectiveness})?
 
-\item Whether \app can correctly detect anomalous values?
+\item Whether \app can correctly detect anomalous values
+($\S$\ref{subsec-anomalous})?
 
-\item How long do training and verification last?
+\item How long do training and verification last ($\S$\ref{subsec-time})?
 
@@
 \subsection{\app's Effectiveness}
+\label{subsec-effectiveness}
 
 We now apply \app to check against real-world misconfiguration problems.
-We use a real misconfiguration dataset~\cite{xu15hey}
+We use a real misconfiguration dataset~\cite{configdataset}
 that are collected from several online forums, \eg, 
@@
 \subsection{Detecting Anomalous Values}
+\label{subsec-anomalous}
 
@@
 
-\subsection{The Run-Time of Verification}
+\subsection{Training \& Verification Performance}
+\label{subsec-time}
 
-\ennan{Here, we need three pictures. In the first figure, x-axis should
-be the number (or the size) of entries in the training dataset, and 
-y-axis should be the run-time of parsing. In the second figure,
-we need to measure the time of generating rules. }
+We run our experiments measuring the run-time of training and
+verification of \app.
+Our experiments were run on a machine equipped with
+64-bit Intel Core i7-4790 CPU @ 3.60GHz and 8 GB of RAM.
+
+\para{Training performance.}
+We first evaluate the training time of \app. Namely, how long
+does \app need to use to generate rules.
+We vary the number of configuration files in our training dataset
+between 10 and 200, and record the corresponding time.
+Table~\ref{table-training} presents our evaluational results.
+We found the training time of \app is acceptable in practice,
+because 150 files in the training dataset have been able to make
+us obtain good enough rules.
+For 150 files, \app only needs about 7 minutes.
+Furthermore, even if we train \app with a 200-file dataset,
+we need less than 15 minutes, but such a training dataset
+can generate about 200,000 rules.
+
+\para{Verification performance.}
+We also measure the verification time of \app, and found
+the verification time is very fast. With 232,613 rules,
+\app needs less than one second to verify a MySQL configuration file.
+\app only needs 3 minutes to finish the verifications to
+the real-world dataset~\cite{configdataset}, we used to 
+evaluate the effectiveness of \app,
+which contains 261 misconfiguration files.
+
+\begin{table}[t]
+\centering
+\caption{Training time for different datasets}
+\label{table-training}
+\begin{tabular}{|c|c|}
+\hline
+{\bf The \# of Files for Training}       & {\bf Training Time (sec.)}  \\ 
+\hline
+\hline
+10   & 2.997        \\ \hline
+50   & 46.4208          \\ \hline
+100  & 206.7798       \\ \hline
+150  & 431.7772        \\ \hline
+200  & 856.6383  \\ 
+\hline
+\end{tabular}
+\end{table}

### 2016-05-10 OSDI/learner.tex
get rid of denotes
fix some keys

@@
 learns rules for checking configuration errors like
-entry missing, ordering errors, and fine-grained value correlation errors. 
+missing entry errors, ordering errors, and fine-grained value correlation errors. 
 These errors tend to cause total system failures.
@@
 \end{small}
-In the above, the ":: \{Rule\}" notation indicates that the $LR$ learned rules 
-and $RR$ reported rules are sets of rules.
+In the above, the ":: \{Rule\}" notation indicates that $LR$, the learned rule set, 
+and $RR$, the reported rule set, are sets of rules.
 A rule is only committed to the $LR$ learned rule set if 
 the rule holds on all files in the training set $C$, as denoted by the $\forall$ quantifier. 
-A broken rule is reported to the user in the $RR$ rule set if the rule is in $LR$, 
+A broken rule is reported to the user in $RR$ rule set if the rule is in $LR$, 
 but does not hold on the input user file.
@@
 Each rule can be viewed as a mapping from 
-attributes $a_j$ and $a_k$ in the intermediate representation of a 
-configuration file to a boolean function, $R$: this can be represented by a rule
-$r := (a_j, a_k) \rightarrow B_{rel}$.
+entry keys $(k_1, \ldots, k_n)$ in the intermediate representation of a 
+configuration file to a boolean function, $B_{rel}$. This can be represented by a rule
+$r := (k_1, \ldots, k_n) \rightarrow B_{rel}$.
 $B_{rel}$ is a Boolean function specific to the relation to assess, meaning that 
@@
 For instance, for the rule that {\tt max\_connections} must 
-be greater than {\tt mysql.max\_persistent}, the relation of interest is $>$ 
-and $B_{>}$ would be set to true.
+be greater than {\tt mysql.max\_persistent}, the rule is denoted by
+({\tt max\_connections}, {\tt mysql.max\_persistent}) $\to 1$, where 
+$B_{>}$ is set to 1.
 
@@
 \caption{Probabilistically Learn Rules}
+\label{alg:plearn}
   Let $\theta$ be the list of possible types for the intermediate representation of interest.
@@
 
-    \State $R = \{\}$ // denotes rule set
-    \State $P$ // denotes probabilities associated with rule set
+    \State $R = \{\}$ // rule set
+    \State $P$ // probabilities associated with rule set
     \For{each file $F$ in $C$}
@@
 \begin{algorithm}
-\caption{constructRules}
+\caption{Construct Rules}
+\label{alg:crules}
   \begin{algorithmic}[1]
@@
 
-\begin{algorithm}
-\caption{constructRule}
-  \begin{algorithmic}[1]
-  \State \textbf{constructRule}($u$):\\
-  Input: a tuple of entries, $u$, denoted by $(e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$ \\
-    \State return $t(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$.
-  \end{algorithmic}
-\end{algorithm}
+%\begin{algorithm}
+%\caption{constructRule}
+%  \begin{algorithmic}[1]
+%  \State \textbf{constructRule}($u$):\\
+%  Input: a tuple of entries, $u$, denoted by $(e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$ \\
+%    \State return $t(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$.
+%  \end{algorithmic}
+%\end{algorithm}
 

### 2016-05-10 OSDI/impl.tex
Updates from ShareLaTeX

--- 2016-05-10 OSDI/impl.tex
@@
 
-\ennan{We need to describe how do we implement each module. We may need to
-have three paragraphs: one is for translator, one is for learner 
-and one is for checker.}
-
 \app is primarily implemented in Haskell, but the suspicious values module was written in R.
-The suspicious value module re implements the main functionality of the Haskell system, and is is a testament to the simplicity of the algorithm and the ease of reproduction.
+The suspicious value module reimplements the main functionality of the Haskell system, and is is a testament to the simplicity of the algorithm and the ease of reproduction.
 For clarity, we only present the key components of the Haskell implementation here.
 
-The translator is a simple parser for a small grammar, as described in ($\S$\ref{sec-trans}). The implementation presented no interesting challenges.
+The translator is a simple parser for a small grammar, as described in $\S$\ref{sec-trans}. The implementation presented no interesting challenges.
 
 The learning and checking steps of the algorithm are designed to allow for extensibility by new users.
-In order to verify a configuration file against a new type of error, the user must provide a new type that is an instance of the \textit{Attribute} typeclass (\ie define some functions over that type).
-In particular, for each type of error the use wishes to detect, they must implement three functions; learn, merge, and check.
+In order to verify a configuration file against a new type of error, the user only needs to provide a new type that is an instance of the \textit{Attribute} typeclass (\ie define some functions over that type).
+In particular, for each type of error the use wishes to detect, they must implement three functions; \lstinline{learn}, \lstinline{merge}, and \lstinline{check}.
 
@@
 This typeclass is polymorphic over the data structure as denoted by \lstinline{Foldable t =>}, which means user can choose any data structure they prefer.
-In general, the best data structure is a hashmap from key-value pairs to relations, previously defined as a \textit{P\_Rule} in ($\S$\ref{subsec-rules}).
+In general, the best data structure is a hashmap from key-value pairs to relations, previously defined as a \textit{P\_Rule} in $\S$\ref{subsec-rules}.
 
 The \lstinline{learn} function will take the intermediate representation of a single configuration file (as generated by the translator), and generate the set of rules that can be derived from that file.
+Specifically, these rules take the form of a \textit{P\_Rule} to track the counts of relation events.
 The \lstinline{merge} function will unify two sets of rules, from two separate configuration files, into a single consistent set of rules. 
-For the probabilistic rules, this is simply a union tends to a summation of the  over be a
-The \lstinline{merge} function
+For the probabilistic rules, this tends to be simply a union between the two sets. 
+When two equivalent rules are merged, the relation event counts should be summed to update the probability distributions.
 
 The \lstinline{check} function will start will all the rules we have learned, and filter until we only have the rules that have been broken by the file of interest.
-We first eliminate the rules that pass the probability check defined in ($\S$\ref{subsec-rules}).
+We first eliminate the rules that do not pass the probability check defined in $\S$\ref{subsec-rules}.
 Second, we only consider the rules which are relevant to the file - we do not need to check rules about keywords which do not appear in the file.
@@
 
-The core learning algorithm is simply a fold using \lstinline{merge} over the derived rules from running \lstinline{learn} on each file in the learning set.
+The rest of the system is structural code to handle these modules for the user. The core learning algorithm will learn over each file individually, then merge the results of learning together. 
+Since we learn each set of rules on each file in isolation from the others, we have a pleasingly parallel situation.
+The \lstinline{learn} function can then be called in parallel over the entire learning set.
+As a functional language, there is no programming overhead to implement this in Haskell - we simply import the parallel mapping library \cite{parallel} to replace all uses of  \lstinline{map} with \lstinline{parmap}.
+The merge stage could also be parallelized by using a divide and conquer approach, but this is not a priority since the learning stage only needs to be run once per learning set, and can then be cached (in our case, as a .json file) for fast reading when doing verification.
 
-Since we learn a set of rules on each file in isolation from the other, we have a pleasingly parallel situation.
-Haskell allows us to easily take advantage of this by using the parallel
-mapping library \cite{parallel}, both for translation to the intermediate representation, and for learning the rules on each file.
-The merge stage could also easily be parallelized, using a divide and conquer approach, but \app runs fast enough over our learning set (28 files, 961 lines of code) that this has not been necessary.
-
-The tool is freely available for download at \url{--redacted--}.
+The source code for our implementation is available at {\em (URL omitted for blind review)}.

### 2016-05-10 OSDI/learner.tex
update learner

@@
 the rule holds on all files in the training set $C$, as denoted by the $\forall$ quantifier. 
-A broken rule is reported to the user in $RR$ rule set if the rule is in $LR$, 
+A broken rule is reported to the user in the $RR$ rule set if the rule is in $LR$, 
 but does not hold on the input user file.
 
-Each rule can be viewed as a mapping from 
+In general, each rule can be viewed as a mapping from 
 entry keys $(k_1, \ldots, k_n)$ in the intermediate representation of a 
-configuration file to a boolean function, $B_{rel}$. This can be represented by a rule
-$r := (k_1, \ldots, k_n) \rightarrow B_{rel}$.
-$B_{rel}$ is a Boolean function specific to the relation to assess, meaning that 
-the desired relation can either be satisfied or not satisfied. 
+configuration file to a probability function, $P_{rel}$. This can be represented by a rule
+$r := (k_1, \ldots, k_n) \rightarrow P_{rel}$.
+$P_{rel}$ is a probability function specific to the relation to assess.
+The problem with the strawman solution is that the probability functions are restricted to be 
+boolean, which is to say that the relation can either be unsatisfied or satisfied, either 0 or 1. 
 For instance, for the rule that {\tt max\_connections} must 
@@
 ({\tt max\_connections}, {\tt mysql.max\_persistent}) $\to 1$, where 
-$B_{>}$ is set to 1.
+$B_{>}$ is set to 1. In our approach, we permit the probability functions to take on any value from 0 to 1.
 
@@
     \State $R = \{\}$ // rule set
-    \State $P$ // probabilities associated with rule set
+    \State $\Pi$ // probabilities associated with rule set
     \For{each file $F$ in $C$}
@@
                         \State $R = R  \cup CR$
-                        \State For each $r \in CR$, update $P$ 
+                        \State For each $r \in CR$, update $\Pi$ 
                \EndIf
@@
     \EndFor
-    \State Based on $P$, accept rules in $R$ according to threshold. 
+    \State return $(\Pi,R)$
   \end{algorithmic}
@@
 
-Our probabilistic approaches for learning the entry missing, 
+Our probabilistic approaches for learning missing entry, 
 ordering, and fine-grained value correlation rules stem 
 from existing work with building 
-the non-probabilistic versions of these rule-learning algorithms. 
-We start with the idea that for each of these rules, 
-we are going to consider all possible pairs of keys that appear in every 
-file, and for our learning process, calculate the likelihood that each of 
-these pairs constitute a rule. 
-In essence, this is a mechanism that will consider many different possible 
-pairs of lines of entries in the file, 
-and attempt to compile a set of these pairs 
-that are expressed more often than others as a basis for finding patterns 
-within the example set that can be used to evaluate new files.
+non-probabilistic versions of these rule-learning algorithms. 
+For each of these rules, 
+we consider all possible permutations of keys that appear in every 
+file which are appropriately typed, and for our learning process, calculate the likelihood that each of 
+these permutations constitute a rule. 
+Rule patterns in the example set that appear frequently are accepted,
+so they can be used to evaluate new files.
 
-More formally, this approach can be defined as follows. 
-The output of our learning algorithm is augmented to a map from 
-key-value pairs to a probability distribution over number of possible 
-relations.
-
-\[
-\{ P\_Rule = (a_j, a_k) | j \neq k \} \rightarrow \{ (R_1, R_2, ... , R_n) \}
-\]
-
-We can think of each of these $(a_j, a_k)$ as possibly having a different relationship, defined by the set $\{ R_i \}$, which cover the entire outcome space of possible relationships between the two values $(a_j, a_k)$.
-
-For the entry missing rules, we define $R_1$ as the event that $a_j$ and
-$a_k$ appear together, and $R_2$ to be the event that $a_j$ appears
-without $a_k$, or by the transitive equivalent, $a_k$ appears without
-$a_j$. For the ordering rules, we define $R_1$ as the event that
-$a_j$ appears before $a_k$ and $R_2$ be the event that $a_k$ appears
-before $a_j$. For the value correlation rules, we define $R_1$ as the
-event that $a_j \leq a_k$, $R_2$ the event that $a_j = a_k$, and $R_3$
-the case that $a_j \geq a_k$. Notice that the $R_i$ do not have to be
-disjoint, but only have to union to the entire probability space.
-
-By examining the learning set, we will derive a distribution of the set $\{R_i\}$ based on how many times we observe an occurrence of each relation.
-This distribution will then be used at checking time to determine if a user's configuration has broken a likely rule.
+More formally, this approach can be defined as follows:
 
@@
 \begin{flalign*}
-I\ \ =&\ \text{Incorrect Learning Set}\\
-\text{::}\ & \text{\{Configuration Files in Intermediate Representation\}}\\
-LP =&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
-RP =&\ \text{Reported Probabilistic Rules :: \{P\_Rule\}}\\
-LP =&\ \text{count\_relation\_occurrences}(I)\\
-RP =&\ \{ r\ \mid r \in LP\ \land \Pi(r)>p \land \neg r(userfile) \}
+I\ \ :=&\ \text{Incorrect Learning Set}\\
+LP :=&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
+RP :=&\ \text{Reported Probabilistic Rules :: \{P\_Rule\}}\\
+I =&\  \text{\{Configuration Files in Intermediate Representation\}}\\
+(\Pi, LP) =&\ \text{learnRules}(I)\\
+RP =&\ \{ r\ \mid r \in LP\ \land \Pi(r)>p \land \neg holds(r, userfile) \}
 \end{flalign*}
@@
 
-A rule will be reported as broken if the probability the rule is
-correct, $\Pi$, is greater than some user defined constant, $p$. This
+%this approach can be defined in Algorithm~\ref{alg:crules}.
+
+%More formally, this approach can be defined in Algorithm~\ref{alg:plearn}. 
+Note that the probability set associated with the rules, $\Pi$, contains values
+ranging from 0 to 1, which are then compared against an acceptance threshold for the final output.
+%\[
+%\{ P\_Rule = (a_j, a_k) | j \neq k \} \rightarrow \{ (R_1, R_2, ... , R_n) \}
+%\]
+
+%We can think of each of these $(a_j, a_k)$ as possibly having a different relationship, defined by the set $\{ R_i \}$, which cover the entire outcome space of possible relationships between the two values $(a_j, a_k)$.
+
+%For the entry missing rules, we define $R_1$ as the event that $a_j$ and
+%$a_k$ appear together, and $R_2$ to be the event that $a_j$ appears
+%without $a_k$, or by the transitive equivalent, $a_k$ appears without
+%$a_j$. For the ordering rules, we define $R_1$ as the event that
+%$a_j$ appears before $a_k$ and $R_2$ be the event that $a_k$ appears
+%before $a_j$. For the value correlation rules, we define $R_1$ as the
+%event that $a_j \leq a_k$, $R_2$ the event that $a_j = a_k$, and $R_3$
+%the case that $a_j \geq a_k$. Notice that the $R_i$ do not have to be
+%disjoint, but only have to union to the entire probability space.
+
+%By examining the learning set, we will derive a distribution of the set $\{R_i\}$ based on how many times we observe an occurrence of each relation.
+This distribution will then be used at checking time to determine if a user's configuration has broken a likely rule.
+
+A rule $r$ will be reported as broken if the probability the rule is
+correct, $\Pi(r)$, is greater than some user defined constant, $p$. This
 constant can be adjust to the user's preference. A small $p$ will

### 2016-05-10 OSDI/eval.tex
config: impl, eval and rel

@@
 We conduct three experiments to evaluate our \app
-prototype. Our experiments aim to answer the following
+prototype. We answer the following
 questions.
@@
 We use a real misconfiguration dataset~\cite{configdataset}
-that are collected from several online forums, \eg, 
+that were collected from several online forums, \eg, 
 Stack Overflow and MySQL forum.
@@
 We apply \app to learn and check the configuration files in this
-dataset. Then, we observe how many errors \app can detect,
-and manually check whether these detected errors are indeed
+dataset. Then, we observe how many errors \app can detect.
+We next manually check whether these detected errors are indeed
 configuration errors.
@@
 error detection results are correct and accurate,
-\ie, correctly report the real misconfiguration problem.
-However, for 44 of them, \app outputs relatively high false positives,
+\ie, correctly report the real misconfiguration problems
+and with few false positives.
+For the rest of 44 cases, 
+although \app can detect the errors,
+\app outputs relatively high false positives,
 \eg, higher than 50 false positives,
@@
 we extract 20 incorrect configuration files from the dataset.
-As a case study, we present the problem descriptions of these files, 
-the types of their errors, and the outputs produced by \app.
-Table~\ref{table-casestudy} details this information.
+\app is able to correctly report these configuration errors,
+and these errors cannot be handled by any existing efforts.
+Table~\ref{table-casestudy} details this information,
+including the problem descriptions of these files, 
+error types, and the outputs produced by \app.
 

### 2016-05-10 OSDI/impl.tex
config: impl, eval and rel

@@
 
-\app is primarily implemented in Haskell, but the suspicious values module was written in R.
-The suspicious value module reimplements the main functionality of the Haskell system, and is is a testament to the simplicity of the algorithm and the ease of reproduction.
-For clarity, we only present the key components of the Haskell implementation here.
+\app is primarily implemented in Haskell, and the suspicious values
+detection module was written in R. 
+%The suspicious value module reimplements the
+%main functionality of the Haskell system, and is is a testament to the
+%simplicity of the algorithm and the ease of reproduction. 
+For clarity,
+we only present the key components of the Haskell implementation here.
 
-The translator is a simple parser for a small grammar, as described in $\S$\ref{sec-trans}. The implementation presented no interesting challenges.
+The translator is developed as a parser for the grammar
+described in $\S$\ref{sec-trans}. 
+%The implementation presented no interesting challenges.
 
-The learning and checking steps of the algorithm are designed to allow for extensibility by new users.
-In order to verify a configuration file against a new type of error, the user only needs to provide a new type that is an instance of the \textit{Attribute} typeclass (\ie define some functions over that type).
-In particular, for each type of error the use wishes to detect, they must implement three functions; \lstinline{learn}, \lstinline{merge}, and \lstinline{check}.
+The learning and checking modules are developed to allow
+for customized extensibility. In order to verify a configuration file
+against a new type of error, a user only needs to provide a new type
+that is an instance of the \textit{Attribute} typeclass (\ie, define some
+functions over that type). 
+In particular, for each type of error the users
+wish to detect, they must implement three functions;
+\lstinline{learn}, \lstinline{merge}, and \lstinline{check}.
 
+\com{
 \begin{lstlisting}
@@
 
-This typeclass is polymorphic over the data structure as denoted by \lstinline{Foldable t =>}, which means user can choose any data structure they prefer.
-In general, the best data structure is a hashmap from key-value pairs to relations, previously defined as a \textit{P\_Rule} in $\S$\ref{subsec-rules}.
+This typeclass is polymorphic over the data structure as denoted by 
+\lstinline{Foldable t =>}, 
+which means user can choose any data structure they prefer.
+In general, the best data structure is a hashmap 
+from key-value pairs to relations, 
+previously defined as a \textit{P\_Rule} in $\S$\ref{subsec-rules}.
+}
 
-The \lstinline{learn} function will take the intermediate representation of a single configuration file (as generated by the translator), and generate the set of rules that can be derived from that file.
-Specifically, these rules take the form of a \textit{P\_Rule} to track the counts of relation events.
+The \lstinline{learn} function takes the intermediate representation of 
+a single configuration file (as generated by the translator), 
+and generates the set of rules that can be derived from that file.
+Specifically, these rules take the form of 
+a \textit{P\_Rule} to track the counts of relation events.
 The \lstinline{merge} function will unify two sets of rules, from two separate configuration files, into a single consistent set of rules. 
@@
 
-The \lstinline{check} function will start will all the rules we have learned, and filter until we only have the rules that have been broken by the file of interest.
-We first eliminate the rules that do not pass the probability check defined in $\S$\ref{subsec-rules}.
-Second, we only consider the rules which are relevant to the file - we do not need to check rules about keywords which do not appear in the file.
-Lastly, we take the errors as any rule that does not hold over the given file.
+The \lstinline{check} function will start all the rules we have learned, 
+and filter until we only have the rules that have been broken by the file 
+of interest. We first eliminate the rules 
+that do not pass the probability check defined in $\S$\ref{subsec-rules}.
+Second, we only consider the rules which are relevant to the file -- we 
+do not need to check rules about the entries 
+that do not appear in the file.
+Lastly, we take the errors 
+as any rule that does not hold over the given file.
 
+\com{
 A sketch of a typical implementation of these three functions is shown below. Again, the specifics of this implementation will vary based on the type of error being detected.
@@
 \end{lstlisting}
+}
 
-The rest of the system is structural code to handle these modules for the user. The core learning algorithm will learn over each file individually, then merge the results of learning together. 
+%The rest of the system is structural code to handle these modules for the user. 
+The core learning algorithm will learn over each file individually, 
+then merge the results of learning together. 
 Since we learn each set of rules on each file in isolation from the others, we have a pleasingly parallel situation.
 The \lstinline{learn} function can then be called in parallel over the entire learning set.
-As a functional language, there is no programming overhead to implement this in Haskell - we simply import the parallel mapping library \cite{parallel} to replace all uses of  \lstinline{map} with \lstinline{parmap}.
+As a functional language, there is no programming overhead to implement
+this in Haskell -- we simply import the parallel mapping library \cite{parallel} to replace all uses of  \lstinline{map} with \lstinline{parmap}.
 The merge stage could also be parallelized by using a divide and conquer approach, but this is not a priority since the learning stage only needs to be run once per learning set, and can then be cached (in our case, as a .json file) for fast reading when doing verification.

### 2016-05-10 OSDI/rel.tex
config: impl, eval and rel

@@
 file into our proposed representation.
+
+Huang {\em et al.} proposed a specification for configuration validation%
+~\cite{huang15confvalley}. We will 
+discuss this work in the misconfiguration
+detection part.
 
@@
 failures or performance problems. AutoBash~\cite{su07autobash} 
-speculatively
-executes processes and tracks causality to automatically fix 
+tracks causality and automatically fixes 
 misconfigurations. Unlike \app, most misconfiguration

### 2016-05-10 OSDI/learner.tex
slightly better learner

@@
 %More formally, this approach can be defined in Algorithm~\ref{alg:plearn}. 
-Note that the probability set associated with the rules, $\Pi$, contains values
-ranging from 0 to 1, which are then compared against an acceptance threshold for the final output.
+Note that the formalism relies on Algorithm~\ref{alg:plearn}. For brevity, Algorithm~\ref{alg:plearn} only considers
+templates without mixed types; that is, the arguments of the template are all similarly typed. Adding support for
+mixed types is not much more difficult.
+
+%probability set associated with the rules, $\Pi$, contains values
+%ranging from 0 to 1, which are then compared against an acceptance threshold for the final output.
 %\[

### 2016-05-10 OSDI/concl.tex
config: concl

@@
 In this paper, we introduce \app, a highly modular framework 
-that allows verification of configuration files, 
-even without a language model of the file.
-New verification properties require only a small amount of code 
-and are not language specific, 
-all indicating that \app could be widely adopted by system administrators.
-Such a verification tool that scales in both performance and expressivity 
-can revolutionize configuration file checking, 
-reducing the cost of system maintenance and failure dramatically.
+that allows automatic verification of configuration files.
+\app employs translator to parse a sample configuration dataset
+into well-structured and typed intermediate representation,
+and then uses a learner module to derive rules, 
+thus building a language model.
+For a given configuration file we want to verify,
+\app uses the generated language model to check
+whether any rule is violated.
+We evaluate \app using a real-world dataset~\cite{configdataset}
+which contains 261 incorrect MySQL configuration files.
+Our experimental result shows \app is able to
+correctly detect errors in 217 files (\ie, 83\% accuracy).

### 2016-05-10 OSDI/learner.tex
update learner

@@
      \For{each $t \in templates(\tau)$}
-        \State Let $n$ be the arity of $t$
+        \State Let $n$ be the arity of $t$.
         \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$. 
@@
            \For{$i = 1:n$}
-           \State Create a $n$-tuple by placing $e$ at the $i$-th place and filling the remaining entries with $p$, in order. Let this $n$-tuple be $u = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
+           \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $u = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
            \State $r = \textrm{constructRule}(u)$ 
@@
 
-%this approach can be defined in Algorithm~\ref{alg:crules}.
-
-%More formally, this approach can be defined in Algorithm~\ref{alg:plearn}. 
-Note that the formalism relies on Algorithm~\ref{alg:plearn}. For brevity, Algorithm~\ref{alg:plearn} only considers
-templates without mixed types; that is, the arguments of the template are all similarly typed. Adding support for
-mixed types is not much more difficult.
+Note that the formalism relies on Algorithm~\ref{alg:plearn}. For brevity, Algorithm 1 only considers
+templates without mixed types; that is, the arguments of the template are all of the same type. This is
+demonstrated via the filtration step, which filters rules in a file that are possibly of the same type.  
+Adding support for mixed types would be handled in a branching statement in Algorithm 1.
+Note that in Algorithm~\ref{alg:crules}, constructRule refers to the creation of a rule from a tuple of entries, $u = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
+Then the rule creation is formally represented as $t(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$; in order to 
+determine if the rule satisfied, the relation associated with $t(v(e_1), v(e_2), \ldots, v(e_i), \ldots, v(e_{n-1}))$ is evaluated.
 
@@
 our claimed language model look like?}
+
+\jon{I will include examples for things like mixed type, rule creation, etc after the translation section is finished.}
 

### 2016-05-10 OSDI/learner.tex
update learner slightly

@@
 Then the rule creation is formally represented as $t(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$; in order to 
-determine if the rule satisfied, the relation associated with $t(v(e_1), v(e_2), \ldots, v(e_i), \ldots, v(e_{n-1}))$ is evaluated.
+determine if the rule satisfied, the relation associated with $t(v(e_1), v(e_2), \ldots, v(e_i), \ldots, v(e_{n-1}))$ is evaluated for truth.
 
@@
 With a configuration file that has been verified against catastrophic
-failures (\eg, entry missing, type and ordering errors), 
-the user may also want to find out more subtle issues.
+failures (\eg, entry missing, type, and ordering errors), 
+the user may also want to examine more subtle issues.
 Anomalous values can cause tricky, but impactful, performance and memory

### 2016-05-10 OSDI/trans.tex
starting on implementation
almost done

@@
 
-The translator takes as input a sample dataset of configuration files and transforms a given sample
-dataset of configuration files into another set of files written in
+The translator takes as input a sample dataset of configuration files and transforms it into another set of files written in
 typed and well-structured representations.
@@
 and HDFS, we need to develop different parsers to handle each of them,
-respectively. \app also allows users to 
-provide extra help to the translator
+respectively. \app allows users to 
+provide an extra help to the translator
 for their specific system configurations,
-but not necessarily. 
-Each of the entries in the intermediate representations
-have been assigned types, and these types guide the learning
-modules later.
+but it is not required.
 
-\para{Probabilistic types.}
-For any key-value entry in the sample configuration files,
-the translator cannot fully determine the type of key 
-based on a single example value.
+The majority of entries in a configuration files are assignments.Our first attempt was to simply
+translate every key-value entry {\tt {k = v}} into a triple $(k, v, \tau)$, where $\tau$ is a type of 
+$v$. However, sometimes we could not fully determine the type of key 
+based on a single example value. For this reason, we introduced {\emph {probabilistic types}}.
+
 Consider the following example.
 
-\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-foo = 300
-bar = 300.txt
-\end{lstlisting}
+\noindent{\tt {foo = 300}}\\
+{\tt {bar = 300.txt}}
 
 Most likely {\tt foo} should be an integer, but it could also be a string.
-In this case, we want to learn the rule like 
+In the second case, we can learn the rule stating 
 $ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. 
-The translator, therefore, assigns a distribution of types 
+Instead of assigning one type to a value, the translator assigns a distribution of types 
 to a value, an idea closely related to existentially quantified 
 types~\cite{Launchbury93lazyfunctional}.
-We introduce {\em probabilistic types} to address this issue.
 
-Let $\mathcal{T}$ be a set of basic types. 
-In \app set $\mathcal{T}$ contains strings, integers, file paths, 
-sizes and IP addresses. 
+Formally, we define probabilistic types as follows: let $\mathcal{T}$ be a set of basic types (cf. Table~\ref{table:kysymys}).
 A probabilistic type built from $\mathcal{T}$ is a list of pairs 
@@
 
+In \app set $\mathcal{T}$ contains strings, integers, file paths, 
+sizes and IP addresses. With every type we associate a list of templates 
+that are use to learn the rules about that files. Table~\ref{table:kysymys} contains
+the most important types and templates.
+
+\begin{table}
+  \begin{tabular}{| l |  l |}
+    \hline
+    Type & Operation  \\ \hline
+    Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline
+    String & $U = V, U \neq V, \textsf{prefix}(U,V), \textsf{sufix}(U,V), \ldots$   \\ \hline
+    File & $\textsf{file}(F), \textsf{dir}(D),\ldots$   \\ \hline
+    Size & similar as for integers   \\ \hline
+    Port &    \\ \hline
+    IP Addr.  &   \\
+
+    \hline
+  \end{tabular}
+\caption{Table of types used in \app together with templates associated to every type}
+\label{table:kysymys}
+\end{table}
+
 \para{Formal Intermediate Representation.}
+
+An additional problem is that configuration files sometimes contain a simple version of the {\tt {if-then}} which 
+sets under which conditions some actions should be applied.
+
 The formal grammar we use for our intermediate representation presented in the following. 
@@
 Secondly, we
-
-\begin{table}
-  \begin{tabular}{| l | c | r |}
-    \hline
-    Type & Operation & 3 \\ \hline
-    4 & 5 & 6 \\ \hline
-    7 & 8 & 9 \\
-    \hline
-  \end{tabular}
-\caption{Table of Types Along with Operation Pools}
-\label{table:kysymys}
-\end{table}
 

### 2016-05-10 OSDI/abs.tex
slightly change abstract

@@
 \app framework is highly modular, 
-does not rely on the system source code or templates, and
+does not rely on system source code or templates, and
 can be applied to any new configuration file type with minimal user input.

### 2016-05-10 OSDI/intro.tex
config: small fix in intro
some grammar

@@
 In their empirical study Yin {\em et al.}~\cite{yin11anempirical} report
-that about 31\% system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code. 
+that about 31\% of system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code. 
 Misconfigurations, in practice, may result in various
@@
 these efforts are focused on learning policies from a sample dataset.
-The learned rules are usually constructed along the following way: 
+The learned rules are usually constructed in the following way: 
 for every entry in a configuration file, 
@@
 consisting of configuration files.
-If the entry is significantly different that the typical value, 
+If the entry is significantly different from a typical value, 
 they suspect that it could be a potential configuration error.
@@
 
-For practical purposes we use the dataset given at~\cite{configdataset}. Every file in our dataset contains an error, but it is 
-always a different error and it only appears in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
+For practical purposes we use the dataset given at~\cite{configdataset}. 
+Every file in our dataset contains several errors, 
+but they are typically different errors and only appear 
+in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
 accurate set of rules. The rules, in general, specify which properties do variables need to satisfy. One can see this learning process as a

### 2016-05-10 OSDI/learner.tex
add algorithms

@@
 
-The first component learns rules 
-that must hold over multiple parts of a configuration file.
+The first component learns rules over typed templates and \emph{untyped specifications}, 
+which must hold over multiple parts of a configuration file. An example of an
+untyped specification is the ordering or missing entry constraint.
 
@@
 \label{alg:plearn}
-  Let $\theta$ be the list of possible types for the intermediate representation of interest.
+  Let $\theta$ be the list of possible types. 
+  Let $U$ be the list of possible untyped specifications. 
   \begin{algorithmic}[1]
@@
                         \State continue to next entry
-                        \Else \enspace $CR = \textrm{constructRules}(e, \tau, Q \backslash RM)$
+                        \Else 
+                        \State $CR = \textrm{constructTRules}(e, \tau, Q \backslash RM)$
                         \State $R = R  \cup CR$
@@
                \State $RM = RM \cup e$
+        \EndFor
+     \EndFor
+      \For{each $u \in U$}
+        \State $RM$ contains entries in remove set
+        \For{each entry $e$ in $F$}
+               \If{$g(e)$ is false}
+                        \State continue to next entry
+                        \Else 
+                        \State $CR = \textrm{constructURules}(e, u, F \backslash RM)$
+                        \State $R = R  \cup CR$
+                        \State For each $r \in CR$, update $\Pi$ 
+               \EndIf
+               \State $RM = RM \cup e$
+        \EndFor
      \EndFor
@@
 \begin{algorithm}
-\caption{Construct Rules}
+\caption{Construct Template Rules}
 \label{alg:crules}
   \begin{algorithmic}[1]
-  \State \textbf{constructRules}($e, \tau, S$):\\
+  \State \textbf{constructTRules}($e, \tau, S$):\\
     Input: entry $e$ from intermediate representation\\ 
@@
            \For{$i = 1:n$}
-           \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $u = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
-           \State $r = \textrm{constructRule}(u)$ 
+           \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $v = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
+           \State $r = \textrm{constructTRule}(v)$ 
             \If{$r$ is satisfied}
@@
           \EndFor
+        \EndFor
+     \EndFor
+     \State return $R$
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{Construct Untyped Specification Rules}
+\label{alg:curules}
+  \begin{algorithmic}[1]
+  \State \textbf{constructURules}($e, u, S$):\\
+    Input: entry $e$ from intermediate representation\\ 
+     \qquad \enspace \enspace untyped specification $u$\\
+     \qquad \enspace \enspace set of entries $S$\\
+     $R = \{\}$
+        \State Let $n$ be the arity of $t$.
+        \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$. 
+        \For{each $p \in P$}
+         \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
+           \For{$i = 1:n$}
+           \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $v = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
+           \State $r = \textrm{constructURule}(v)$ 
+            \If{$r$ is satisfied}
+              $R = R \cup r$
+            \EndIf
           \EndFor

### 2016-05-10 OSDI/check.tex
config: checker

--- 2016-05-01 OSDI/check.tex
@@
 \section{Checker}
+\label{sec-checker}
 
-\ennan{Here, we need to describe how we check whether 
-the target configuration file meets learned rules using SMT solver.}
+With the learned rules and constraints in hand (generated
+by the learner module),
+\app checks whether any entry in a target configuration file
+violates the learned rules and constraints.
+For a given configuration file, \app parses it using the same
+way employed in the translator, thus obtaining a structured
+and typed representation for the target configuration file.
+Then, the checker uses the two sub-modules (shown in 
+Figure~\ref{fig-overview}) to check the target
+configuration file based on rules and constraints.
+
+\para{Error detecting.}
+The first sub-module of our checker,
+named error detecting in Figure~\ref{fig-overview}, 
+is able to detect the following errors:
+entry missing errors, ordering errors, 
+correlation errors (including fine-grained value correlation errors),
+type errors and system environment errors (depending on templates).
+In particular, the checker just see whether the representations 
+parsed from the target configuration files violate our
+learned rules.
+
+\para{Anomaly checking.}
+This checking occurs in the second sub-module of the checker.
+Different from the previous checking tasks,
+suspicious warning is just to detect whether some value
+is too different (or distinguished) from the same entries in the
+training dataset. Even if some values are statistically different
+from the ones in the training dataset, 
+it does not mean such a value is incorrect;
+thus \app, in this case, throw out a warning to the user who
+enters the target configuration file, and a report containing 
+normal values in the training dataset.
+\app allows users to choose whether they want to change 
+the values according to the ones in the training configuration
+files or not.

### 2016-05-10 OSDI/trans.tex

@@
 
-\para{Formal Intermediate Representation.}
+In general, the templates work as follows: if there are two entries ${\tt {k1 = v1}}$ and 
+${\tt {k2 = v2}}$, let $t(X, Y)$ be a template that can be applied to those values (wrt. their types).
+If $t(v1, v2)$ holds, \ie the template states is valid for those concrete values, then we will add a rule
+$t(k1, k2)$ to a list of potentially correct specifications. Note that the rule expresses a correlation between variables.
 
-An additional problem is that configuration files sometimes contain a simple version of the {\tt {if-then}} which 
-sets under which conditions some actions should be applied.
+With the help of probabilistic types we addressed ambiguities during the parsing phase. A next problem that we need to solve
+is that configuration files sometimes contain a simple version of the {\tt {if-then}}, that 
+sets under which conditions some actions should be applied. Therefore, we also add this guard during the parsing phase. The meaning 
+of the guard is that, before deriving a rule, we first check if the guard is true.
 
+To summarize, the translator translates every entry ${\tt {k = v}}$ in a configuration file into a quadruple 
+$$(g,k,v,\textsf{List}[p_1:\tau_1, \ldots, p_n:\tau_n])$$
+
+\iffalse
 The formal grammar we use for our intermediate representation presented in the following. 
@@
 }
+\fi

### 2016-05-10 OSDI/impl.tex
config: table 2
config: table
config: imple

@@
 described in $\S$\ref{sec-trans}. 
+The learner and checker module fully implemented 
+the design in $\S$\ref{sec-learn} and $\S$\ref{sec-checker},
+respectively.
+
 %The implementation presented no interesting challenges. 
-
+\com{
 The learning and checking modules are developed to allow
@@
 wish to detect, they must implement three functions;
-\lstinline{learn}, \lstinline{merge}, and \lstinline{check}.
+\lstinline{learn}, \lstinline{merge}, and \lstinline{check}.}
 
@@
 }
+
+To verify errors,
+our prototype follows three functions, 
+\lstinline{learn}, \lstinline{merge}, and \lstinline{check},
+to learn the rules.
 

### 2016-05-10 OSDI/trans.tex
better trans

--- 2016-05-10 OSDI/trans.tex
@@
 The translator can be seen a parser, and it is only
-used to generate an intermediate representation for the post
-process, such as learning rules (see $\S$\ref{sec-learn}).
+used to generate an intermediate representation for post-processing, 
+such as learning rules (see $\S$\ref{sec-learn}).
 Coupled with rules generated by learner module,
@@
 respectively. \app allows users to 
-provide an extra help to the translator
+provide extra help to the translator
 for their specific system configurations,
@@
 
-The majority of entries in a configuration files are assignments.Our first attempt was to simply
+The majority of entries in a configuration files are assignments. Our first attempt was to simply
 translate every key-value entry {\tt {k = v}} into a triple $(k, v, \tau)$, where $\tau$ is a type of 
@@
 
-In \app set $\mathcal{T}$ contains strings, integers, file paths, 
-sizes and IP addresses. With every type we associate a list of templates 
-that are use to learn the rules about that files. Table~\ref{table:kysymys} contains
+In \app, the set $\mathcal{T}$ contains strings, integers, file paths, 
+sizes, and IP addresses. With every type, we associate a list of templates 
+that are used to learn the rules about those files. Table~\ref{table:kysymys} contains
 the most important types and templates.
@@
     Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline
-    String & $U = V, U \neq V, \textsf{prefix}(U,V), \textsf{sufix}(U,V), \ldots$   \\ \hline
-    File & $\textsf{file}(F), \textsf{dir}(D),\ldots$   \\ \hline
-    Size & similar as for integers   \\ \hline
-    Port &    \\ \hline
-    IP Addr.  &   \\
+    String & $\textsf{substr}(U, V), \textsf{prefix}(U,V), \textsf{suffix}(U,V), \ldots$   \\ \hline
+    File Path & $\textsf{isFile}(F), \textsf{isDir}(D),\ldots$   \\ \hline
+    Size & Similar to integers   \\ \hline
+    Port & $P_1 > P_2$ \\ \hline
+    IP Addr.  & $\textsf{sameSubnet}(addr1, addr2)$   \\
 
@@
 
-\para{Formal Intermediate Representation.}
+In general, the templates works as follows: if there are two entries ${\tt {k1 = v1}}$ and 
+${\tt {k2 = v2}}$, let $t(X, Y)$ be a template that can be applied to those values (w.r.t. their types).
+If $t(v1, v2)$ holds, \ie the template condition is valid for those concrete values, then we will add a rule
+$t(k1, k2)$ to a list of potentially correct specifications. Note that the rule expresses a relation between variables.
 
-An additional problem is that configuration files sometimes contain a simple version of the {\tt {if-then}} which 
-sets under which conditions some actions should be applied.
+With the help of probabilistic types, we addressed ambiguities during the parsing phase. Another problem that we need to solve
+is that configuration files sometimes contain a simple version of the {\tt {if-then}}, such as in Apache HTTPD, that 
+sets conditions under which some action should be applied. Therefore, we also add this guard to our entry 
+during the parsing phase. We first check if the guard is true before deriving a rule; otherwise, we skip the entry.
 
-The formal grammar we use for our intermediate representation presented in the following. 
-Firstly, we make a list of the possible types for a configuration file. This is present in 
-Secondly, we
+To summarize, the translator translates every entry ${\tt {k = v}}$ in a configuration file into a quadruple 
+$$(g,k,v,\textsf{List}[p_1:\tau_1, \ldots, p_n:\tau_n])$$
 
-We come up with the following types:
-
-1. Port 
-The $i$-th entry inside an intermediate representation corresponding to a 
-translated file
-
-We declare a quadruple $(g,k,v,\{\tau_1, \ldots, \tau_n\}_i$
-We need a kind of formal definition (using a figure) to
-define the grammar of our intermediate representation. The basic
-view of this definition should be similar to define a type language
-grammar.
+For an entry, we denote the corresponding guard by $g(e)$, the key by $k(e)$, the value by $v(e)$, and the  
+type list by $typelist(e)$.
 

### 2016-05-10 OSDI/intro.tex
config: abs and intro

@@
 
-To overcome these obstacles, researchers have proposed approaches based on
-a statistical analysis and learning%
+To overcome these obstacles, researchers proposed approaches based on
+statistical analysis and learning%
 ~\cite{wang04automatic, zhang14encore, yuan11context}
@@
 Rather than explicitly specifying entries' types or rules, 
-these efforts are focused on learning policies from a sample dataset.
+these efforts focused on learning policies from a sample dataset.
 The learned rules are usually constructed in the following way: 
@@
 
-\com{First, given the fact that 
-different systems' configuration files use various representations, 
-the cost of introducing a completely new configuration
-language (or representation) to instead of all these existing format looks 
-like an impractical goal. This is not only because administrators need 
-to learn this new language, but also changes existing system
-infrastructure to support such a new language. 
-In order to avoid the above issues, we propose a representation,
-which is a type-based representation and 
-much more structured than existing configuration format, 
-but use it as an intermediate layer. We, at the same time,
-develop many pluggable parsers
-that can transform different systems' configuration representations
-into our proposed intermediate representation for the post process.}
-
 From a practical perspective, 

### 2016-05-10 OSDI/trans.tex
update trans

@@
 ${\tt {k2 = v2}}$, let $t(X, Y)$ be a template that can be applied to those values (w.r.t. their types).
-If $t(v1, v2)$ holds, \ie the template condition is valid for those concrete values, then we will add a rule
+If $t(v1, v2)$ holds, \ie, the template condition is valid for those concrete values, then we will add a rule
 $t(k1, k2)$ to a list of potentially correct specifications. Note that the rule expresses a relation between variables.
@@
 is that configuration files sometimes contain a simple version of the {\tt {if-then}}, such as in Apache HTTPD, that 
-sets conditions under which some action should be applied. Therefore, we also add this guard to our entry 
+sets conditions for which an action should be applied. Therefore, we also add this guard to our entry 
 during the parsing phase. We first check if the guard is true before deriving a rule; otherwise, we skip the entry.
 
-To summarize, the translator translates every entry ${\tt {k = v}}$ in a configuration file into a quadruple 
+To summarize, the translator translates every entity ${\tt {k = v}}$ in a configuration file into a quadruple entry
 $$(g,k,v,\textsf{List}[p_1:\tau_1, \ldots, p_n:\tau_n])$$

### 2016-05-10 OSDI/trans.tex
update trans

@@
     \hline
-    Type & Operation  \\ \hline
+    Type &  Template \\ \hline
     Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline
@@
   \end{tabular}
-\caption{Table of types used in \app together with templates associated to every type}
+\caption{Table of types, along with associated templates, used in \app}
 \label{table:kysymys}
@@
 
-For an entry, we denote the corresponding guard by $g(e)$, the key by $k(e)$, the value by $v(e)$, and the  
+For an entry, we denote the corresponding guard by $g(e)$, the key by $k(e)$, the value by $v(e)$, and the probabilistic
 type list by $typelist(e)$.

### 2016-05-10 OSDI/learner.tex
edit algorithm
lalala

@@
 
-The first component learns rules over typed templates and \emph{untyped specifications}, 
-which must hold over multiple parts of a configuration file. An example of an
+The first component learns two types of rules: rules that are inferred  using typed templates and 
+rules which we call \emph{untyped specifications}. Those are rules
+that must hold over multiple parts of a configuration file. An example of an
 untyped specification is the ordering or missing entry constraint.
@@
 We first present a strawman solution (employed by
-previous work~\cite{santolucitoCAV, zhang14encore}) that uses 
+previous work~\cite{santolucitoCAV}) that uses 
 a set of correct configuration files as a learning set, 
@@
     \For{each file $F$ in $C$}
-      \For{each $\tau \in \theta$}
+      \State Initialize $opt$ flag.
+      \For{each $z \in \theta \cup U$}
+        \If{$z$ is a type} $opt = 1$
+        \ElsIf{$z$ is an untyped spec} $opt = 0$
+        \EndIf
+        \State $Q$ contains candidate entries to pass on %
+        \State $RM$ contains entries in remove set
+        \If{opt}
           \State $Q = filter(F,\tau)$ 
-        \State // $Q$ contains entries in $F$ with $\tau$ in type list
-        \State $RM$ contains entries in remove set
+          \State // Q contains $F$ entries with $\tau$ in type list
+          \Else{$\enspace Q = F$}
+        \EndIf
         \For{each entry $e$ in $Q$}
@@
                \Else
-                        \State $CR = \textrm{constructTRules}(e, \tau, Q \backslash RM)$
-                        \State $R = R  \cup CR$
-                        \State For each $r \in CR$, update $\Pi$ 
-               \EndIf
-               \State $RM = RM \cup e$
-        \EndFor
-     \EndFor
-      \For{each $u \in U$}
-        \State $RM$ contains entries in remove set
-        \For{each entry $e$ in $F$}
-               \If{$g(e)$ is false}
-                        \State continue to next entry
-                        \Else 
-                        \State $CR = \textrm{constructURules}(e, u, F \backslash RM)$
-                        \State $R = R  \cup CR$
-                        \State For each $r \in CR$, update $\Pi$ 
+                        \State $Y = \textrm{constructRules}(e, z, opt, Q \backslash RM)$
+                        \State $R = R  \cup Y$
+                        \State For each $r \in Y$, update $\Pi$ 
                \EndIf
@@
     \EndFor
-    \EndFor
+%      \For{each $u \in U$}
+%        \State $RM$ contains entries in remove set
+%        \For{each entry $e$ in $F$}
+%               \If{$g(e)$ is false}
+%                        \State continue to next entry
+%                        \Else 
+%                        \State $CR = \textrm{constructURules}(e, u, F \backslash RM)$
+%                        \State $R = R  \cup CR$
+%                        \State For each $r \in CR$, update $\Pi$ 
+%               \EndIf
+%               \State $RM = RM \cup e$
+%        \EndFor
+%     \EndFor
+%    \EndFor
     \State return $(\Pi,R)$

### 2016-05-10 OSDI/learner.tex
config: alg compact

@@
 
-\begin{algorithm}
+\begin{algorithm}[t]
 \caption{Probabilistically Learn Rules}
 \label{alg:plearn}
+\begin{footnotesize}
   Let $\theta$ be the list of possible types. 
@@
   \end{algorithmic}
+\end{footnotesize}
 \end{algorithm}
 
-\begin{algorithm}
+\begin{algorithm}[t]
 \caption{Construct Template Rules}
 \label{alg:crules}
+\begin{footnotesize}
   \begin{algorithmic}[1]
@@
   \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{Construct Untyped Specification Rules}
-\label{alg:curules}
-  \begin{algorithmic}[1]
-  \State \textbf{constructURules}($e, u, S$):\\
-    Input: entry $e$ from intermediate representation\\ 
-     \qquad \enspace \enspace untyped specification $u$\\
-     \qquad \enspace \enspace set of entries $S$\\
-     $R = \{\}$
-        \State Let $n$ be the arity of $t$.
-        \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$. 
-        \For{each $p \in P$}
-         \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
-           \For{$i = 1:n$}
-           \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $v = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
-           \State $r = \textrm{constructURule}(v)$ 
-            \If{$r$ is satisfied}
-              $R = R \cup r$
-            \EndIf
-          \EndFor
-        \EndFor
-     \State return $R$
-  \end{algorithmic}
+\end{footnotesize}
 \end{algorithm}
@@
 
-\ennan{So far, it is still not clear what does 
-our claimed language model look like?}
-
-\jon{I will include examples for things like mixed type, rule creation, etc after the translation section is finished.}
+\begin{algorithm}[t]
+\caption{Construct Untyped Specification Rules}
+\label{alg:curules}
+\begin{footnotesize}
+  \begin{algorithmic}[1]
+  \State \textbf{constructURules}($e, u, S$):\\
+    Input: entry $e$ from intermediate representation\\ 
+     \qquad \enspace \enspace untyped specification $u$\\
+     \qquad \enspace \enspace set of entries $S$\\
+     $R = \{\}$
+        \State Let $n$ be the arity of $t$.
+        \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$. 
+        \For{each $p \in P$}
+         \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
+           \For{$i = 1:n$}
+           \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $v = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
+           \State $r = \textrm{constructURule}(v)$ 
+            \If{$r$ is satisfied}
+              $R = R \cup r$
+            \EndIf
+          \EndFor
+        \EndFor
+     \State return $R$
+  \end{algorithmic}
+\end{footnotesize}
+\end{algorithm}
 

### 2016-05-10 OSDI/learner.tex
commit more concise algorithm

@@
       \For{each $z \in \theta \cup U$}
-        \If{$z$ is a type} $opt = 1$
-        \ElsIf{$z$ is an untyped spec} $opt = 0$
-        \EndIf
-        \State $Q$ contains candidate entries to pass on %
+        \State $Q$ contains candidate entries to consider
         \State $RM$ contains entries in remove set
-        \If{opt}
-          \State $Q = filter(F,\tau)$ 
+        \If{$z$ is a type} \State $opt = 1$ \State $Q = filter(F,\tau)$
           \State // Q contains $F$ entries with $\tau$ in type list
-          \Else{$\enspace Q = F$}
+        \ElsIf{$z$ is an untyped spec} \State $opt = 0$ \State $Q = F$
         \EndIf
@@
                \Else
-                        \State $Y = \textrm{constructRules}(e, z, opt, Q \backslash RM)$
-                        \State $R = R  \cup Y$
-                        \State For each $r \in Y$, update $\Pi$ 
+                        \State $CR = \textrm{constructRules}(e, z, opt, Q \backslash RM)$
+                        \State $R = R  \cup CR$
+                        \State For each $r \in CR$, update $\Pi$
                \EndIf
@@
     \EndFor
-%      \For{each $u \in U$}
-%        \State $RM$ contains entries in remove set
-%        \For{each entry $e$ in $F$}
-%               \If{$g(e)$ is false}
-%                        \State continue to next entry
-%                        \Else 
-%                        \State $CR = \textrm{constructURules}(e, u, F \backslash RM)$
-%                        \State $R = R  \cup CR$
-%                        \State For each $r \in CR$, update $\Pi$ 
-%               \EndIf
-%               \State $RM = RM \cup e$
-%        \EndFor
-%     \EndFor
-%    \EndFor
     \State return $(\Pi,R)$
@@
 \begin{algorithm}[t]
-\caption{Construct Template Rules}
+\caption{Construct Rules}
 \label{alg:crules}
@@
   \begin{algorithmic}[1]
-  \State \textbf{constructTRules}($e, \tau, S$):\\
+ \State \textbf{constructRules}($e, z, opt, S$):\\
     Input: entry $e$ from intermediate representation\\
-     \qquad \enspace \enspace type $\tau$\\
+     \qquad \enspace \enspace type or untyped specification $z$\\
+     \qquad \enspace \enspace option $opt$, set to 1 if template\\
+     \qquad \qquad \enspace \enspace \enspace \enspace \qquad or 0 if untyped spec\\
      \qquad \enspace \enspace set of entries $S$\\
-     $R = \{\}$
-     \For{each $t \in templates(\tau)$}
-        \State Let $n$ be the arity of $t$.
+     \State $R = \{\}$
+     \State Set $j$ as an iteration variable.
+     \If{opt == 1}
+        \State iterate the following sequence \textbf{L} over all elements of $templates(z)$ 
+        \State \ie, $j \in templates(z)$
+     \ElsIf{opt == 0}
+        \State $j = z$
+     \EndIf
+     \State Beginning of \textbf{L}: 
+     \State Let $n$ be the arity of $j$.
       \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$.
@@
          \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $v = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
-           \State $r = \textrm{constructTRule}(v)$ 
+         \State $r = \textrm{constructRule}(v)$
          \If{$r$ is satisfied}
@@
      \EndFor
-     \EndFor
+     \State End of \textbf{L}. 
      \State return $R$
@@
 
-\begin{algorithm}[t]
-\caption{Construct Untyped Specification Rules}
-\label{alg:curules}
-\begin{footnotesize}
-  \begin{algorithmic}[1]
-  \State \textbf{constructURules}($e, u, S$):\\
-    Input: entry $e$ from intermediate representation\\ 
-     \qquad \enspace \enspace untyped specification $u$\\
-     \qquad \enspace \enspace set of entries $S$\\
-     $R = \{\}$
-        \State Let $n$ be the arity of $t$.
-        \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$. 
-        \For{each $p \in P$}
-         \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
-           \For{$i = 1:n$}
-           \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $v = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
-           \State $r = \textrm{constructURule}(v)$ 
-            \If{$r$ is satisfied}
-              $R = R \cup r$
-            \EndIf
-          \EndFor
-        \EndFor
-     \State return $R$
-  \end{algorithmic}
-\end{footnotesize}
-\end{algorithm}
-
 \subsection{Learning Suspicious Constraints}

### 2016-05-10 OSDI/learner.tex
slight algo edits
add algo description

@@
 
-The first component learns two types of rules: rules that are inferred  using typed templates and 
-rules which we call \emph{untyped specifications}. Those are rules
-that must hold over multiple parts of a configuration file. An example of an
+The first component learns two types of rules: rules that are inferred using templates associated with types 
+and rules which we call \emph{untyped specifications}. An example of an
 untyped specification is the ordering or missing entry constraint.
+%Both are rules that must hold over multiple parts of a configuration file.
 
@@
      \If{opt == 1}
-        \State iterate the following sequence \textbf{L} over all elements of $templates(z)$ 
-        \State \ie, $j \in templates(z)$
+        \State run the following sequence \textbf{L} over all elements of $templates(z)$ 
+        \State \ie, iterate $j$ over $templates(z)$
      \ElsIf{opt == 0}
@@
          \For{$i = 1:n$}
-         \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $v = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
-         \State $r = \textrm{constructRule}(v)$
+         \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $m = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
+         \State $r = \textrm{constructRule}(m)$
          \If{$r$ is satisfied}
@@
 \end{algorithm}
-
-%\begin{algorithm}
-%\caption{constructRule}
-%  \begin{algorithmic}[1]
-%  \State \textbf{constructRule}($u$):\\
-%  Input: a tuple of entries, $u$, denoted by $(e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$ \\
-%    \State return $t(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$.
-%  \end{algorithmic}
-%\end{algorithm}
-
-%each entry is listed as (g,k,v,typelist)
 
@@
 
-Note that the formalism relies on Algorithm~\ref{alg:plearn}. For brevity, Algorithm 1 only considers
-templates without mixed types; that is, the arguments of the template are all of the same type. This is
-demonstrated via the filtration step, which filters rules in a file that are possibly of the same type.  
-Adding support for mixed types would be handled in a branching statement in Algorithm 1.
-Note that in Algorithm~\ref{alg:crules}, constructRule refers to the creation of a rule from a tuple of entries, $u = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
-Then the rule creation is formally represented as $t(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$; in order to 
-determine if the rule satisfied, the relation associated with $t(v(e_1), v(e_2), \ldots, v(e_i), \ldots, v(e_{n-1}))$ is evaluated for truth.
+Note that the formalism relies on Algorithm~\ref{alg:plearn}. The algorithm considers both typed templates and
+untyped specifications. As a similar iteration logic is used for both, an $opt$ flag distinguishes between the two situations.
+constructRule in Algorithm~\ref{alg:crules} refers to the creation of a rule from a tuple of entries, 
+$m = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
+The rule creation is formally represented as $m(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$. 
+In order to determine if the rule satisfied, the relation associated with $m(v(e_1), v(e_2), \ldots, v(e_i), \ldots, v(e_{n-1}))$ is evaluated for truth.
+The rule can be template-generated, for instance {\tt max\_connections} > {\tt mysql.max\_persistent}, or
+it can be untyped-specification-generated rule, for instance {\tt recode.so} must come before 
+{\tt mysql.so}.
+
+For typed templates, we first filter and examine entries associated with a particular type, and then check if
+the template is satisfied over appropriately typed argument entries in the rest of the file. We do something similar for
+untyped specifications.
 

### 2016-05-10 OSDI/learner.tex
add ordering

@@
 The rule can be template-generated, for instance {\tt max\_connections} > {\tt mysql.max\_persistent}, or
-it can be untyped-specification-generated rule, for instance {\tt recode.so} must come before 
+it can be untyped-specification-generated rule, for instance the ordering that {\tt recode.so} must come before 
 {\tt mysql.so}.

### 2016-05-10 OSDI/abs.tex
config: abs and intro
config: abs

@@
 
-\app is capable of detecting various tricky errors that cannot
+\app is capable of detecting various errors that cannot
 be detected by previous efforts,
-including ordering errors, fine-grained value correlation errors, 
-entry missing errors, and environment-related errors. 
-Our experiment shows \app is able to detect 83\% errors from
-a real-world dataset with 261 incorrect MySQL configuration files.
+including entry ordering errors, fine-grained value correlation errors, 
+and entry missing errors. 
+We evaluate \app using a real-world dataset with 261 incorrect 
+MySQL configuration files,
+and \app is able to correctly 
+detect errors (previous work failed to
+detect) in 217 files.

### 2016-05-10 OSDI/intro.tex
config: intro

@@
 cannot be detected by this way. 
-As an illustration of such an error, consider the ordering errors, 
+As an illustration of such an error, consider the entry ordering errors, 
 which happens when some entries are inserted in a wrong order. 
@@
 
-For practical purposes we use the dataset given at~\cite{configdataset}. 
+For practical purposes we use a real-world dataset~\cite{configdataset}. 
 Every file in our dataset contains several errors, 
@@
 
-The learning process works in two phases. In the first phase, 
+The learning process has two phases. In the first phase, 
 \app analyzes the sample dataset and generates a 
@@
 \item We propose the first automatic configuration verification
-framework, \app, that can learn a language model from an example set of 
-correct configuration files, and then use this language model to verify 
+framework, \app, that can learn a language model from a sample
+dataset, and then use this language model to verify 
 configuration files of interest.

### 2016-05-10 OSDI/concl.tex
config: intro
config: concl

@@
 that allows automatic verification of configuration files.
-\app employs translator to parse a sample configuration dataset
-into well-structured and typed intermediate representation,
+\app employs a translator to parse a sample configuration dataset
+into a well-structured and typed intermediate representation,
 and then uses a learner module to derive rules, 
@@
 Our experimental result shows \app is able to
-correctly detect errors in 217 files (\ie, 83\% accuracy).
+correctly detect errors in 217 files.

### 2016-05-10 OSDI/intro.tex
config: intro

@@
 
-Our \app prototype still has a few limitations:
+Our \app prototype still has many limitations:
 for example, we cannot handle configuration errors that can be 
@@
 be detected by previous efforts,
-including ordering errors, fine-grained value correlation errors, 
+including entry ordering errors, fine-grained value correlation errors, 
 entry missing errors, and environment-related errors.
@@
 \item We implement a \app prototype and evaluate it by
-conducting comprehensive experiments.
+conducting comprehensive experiments on real-world dataset.
 

### 2016-05-10 OSDI/abs.tex

@@
 Finally, \app uses the resulting language model to verify $F$.
-\app framework is highly modular, 
+The \app framework is highly modular, 
 does not rely on system source code or templates, and

### 2016-05-10 OSDI/intro.tex
config: intro

@@
 but all of the files in the sample need to be of the same type (such as
-MySQL or httpd configuration files).
+MySQL or HTTPD configuration files).
 From that sample,

### 2016-05-10 OSDI/motiv.tex
config: motiv

@@
 a popular question and answer website for programmers. To better understand problems that users have with 
-configuration files, we explored and analyzed a large number of user forums and on-line discussion sites, focused on misconfigurations.
+configuration files, we explored and analyzed misconfigurations on a large number of user forums and on-line discussion sites.
 
@@
 Apache HTTP Server, most likely the user will take some already existing configuration files and adapt them
-to suite her needs. The configuration file might contain, among others, 
+to suit her needs. The configuration file might contain, among others, 
 the following lines:
@@
 
-This configuration file will cause that the Apache server will
+This configuration file will cause the Apache server to 
 fail to start due to a segmentation fault error. 
@@
 and typically lead to multiple system crash events.
-However, none of existing tools can effectively solve 
+However, no existing tool can effectively solve 
 or detect this problem~\cite{zhang14encore, xu15systems, xu13do}.
@@
 Our next real-world misconfiguration example~\cite{correlation} comes from a discussion on StackOverflow.
-The user has configured his MySQL as the following:
+The user has configured her MySQL as in the following:
 
@@
 
-The user the complains that her MySQL load was very high, causing the website's
-respond speed to be very slow.
+The user complains that her MySQL load was very high, causing the website's
+response speed to be very slow.
 In this case, {\tt key\_buffer\_size} is used by all the threads
@@
 created by each thread for private use; thus, the maximum amount
-of used key buffer, \ie, {\tt key\_buffer\_size} should be larger than 
+of used key buffer, \ie, {\tt key\_buffer\_size}, should be larger than 
 {\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
@@
 
-We can see that during the learning process we do not learn only simple statements, that compare two values, 
-but we also learn more complex correlations. We call them {\em fine-grained value correlations}, and the error
-a fine-grained value correlation
-error. This types of errors are more sophisticated than simple value correlations that some tools can detect~\cite{yin11anempirical, zhang14encore}.
+We can see that during the learning process not only do we learn simple statements that compare two values, 
+but also we learn more complex correlations. We call these more complex relations fine-grained value correlations, and the errors
+\emph{fine-grained value correlation errors}. 
+This type of error is more sophisticated than the simple value correlation that some tools can detect~\cite{yin11anempirical, zhang14encore}.
 A typical value correlation error
@@
 
-Our tool can learn this simple correlations as well, but learning more complex properties requires a different 
+Our tool can learn this simple correlation as well, but learning more complex properties requires a different 
 approach to the learning 
 process. We need to track several variables. It is not enough just to compare them, but we need to learn, as in this particular case, which
-invariant do they have to preserve. It was pointed out by Xu {\em et al.}~\cite{xu15hey} that
+invariant must be preserved. It was pointed out by Xu {\em et al.}~\cite{xu15hey} that
 detecting fine-grained value correlation errors 
@@
 entry was missing in the configuration file. 
-We call such a problem an {\em missing entry error}.
+We call such a problem a {\em missing entry error}.
 In a public misconfiguration dataset~\cite{configdataset},

### 2016-05-10 OSDI/arch.tex
config: arch

@@
 The input of the learner is a set of files that have been translated
-into a well-structured representations of a list of keyword-value pairs (\ie, the translator's
+into well-structured representations (\ie, the translator's
 outputs). The learner module employs a collection of learning algorithms
@@
 rules together, we build a language model for
-configuration verifications.
-Because the translator outputs probabilistic typed entries,
+configuration verification.
+Because the translator outputs probabilistically typed entries,
 the learner is responsible for determining a type for each entry.
@@
 Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
-which needs users or developers to provide explicit templates,
+which requires users or developers to provide explicit templates,
 \app's learner encodes some predefined error-patterns 

### 2016-05-10 OSDI/arch.tex
config: arch

@@
 
-Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
+\com{Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
 which requires users or developers to provide explicit templates,
@@
 that \app should handle: we consider integer constraints, 
-ordering errors, typing errors, correlation errors, etc.
+ordering errors, typing errors, correlation errors, etc.}
 
@@
 checking rule violations and suspicious values, respectively.
-In our experience, we find learned rules could be significantly reused
+In our experience, we found learned rules could be significantly reused
 to check different configuration files, thus improving our usability.

### 2016-05-10 OSDI/learner.tex
lala

@@
 In practice, however, it is difficult to obtain a set of files 
-that is both guaranteed to be without misconfiguration 
-and large enough to learn many rules of configuration files.
+that is both guaranteed to be without errors
+and large enough to learn sufficiently many rules.
 This usually requires manual verification of the learning set, 
@@
 
-In general, each rule can be viewed as a mapping from 
+In general, each rule can be viewed as a mapping from a tuple of 
 entry keys $(k_1, \ldots, k_n)$ in the intermediate representation of a 

### 2016-05-10 OSDI/trans.tex
config: fix
lala

@@
 \begin{table}
+\caption{Table of types, along with associated templates, used in \app}
   \begin{tabular}{| l |  l |}
@@
   \end{tabular}
-\caption{Table of types, along with associated templates, used in \app}
 \label{table:kysymys}
@@
 
-For an entry, we denote the corresponding guard by $g(e)$, the key by $k(e)$, the value by $v(e)$, and the probabilistic
+For an entry $e$, we denote the corresponding guard by $g(e)$, the key by $k(e)$, the value by $v(e)$, and the probabilistic
 type list by $typelist(e)$.

### 2016-05-10 OSDI/learner.tex
lala

@@
 In \app's learner module, the rule learning mechanism is tolerant 
-enough to accept a dataset {\em full of} incorrect configuration files. 
+enough to accept a dataset of possibly incorrect configuration files. 
 Rather than manually correcting each file, 

### 2016-05-10 OSDI/abs.tex

--- 2016-05-10 OSDI/abs.tex
@@
 Finally, \app uses the resulting language model to verify $F$.
-\app framework is highly modular, 
-does not rely on system source code or templates, and
+The \app framework is highly modular, 
+does not rely on system source code, and
 can be applied to any new configuration file type with minimal user input.

### 2016-05-10 OSDI/concl.tex
config: concl and figs

@@
 Our experimental result shows \app is able to
-correctly detect errors in 217 files.
+correctly detect errors in 217 files in that dataset.
+
+Our \app prototype still has many limitations. 
+For example, we cannot handle configuration errors that can be 
+triggered during system execution time, 
+and we cannot detect misconfiguration across software components. 
+Nevertheless, we believe \app represent a practical path
+toward automatic language-based configuration verification.

### 2016-05-10 OSDI/learner.tex

@@
 
-\para{Our approach.}
+\para{Probabilistic approach.}
 In \app's learner module, the rule learning mechanism is tolerant 

### 2016-05-10 OSDI/eval.tex
config: table 2
config: table
config: eval

@@
-\section{Evaluations}
-\label{sec-eval}
-
-We conduct three experiments to evaluate our \app
-prototype. We answer the following
-questions.
-
-\begin{itemize}
-
-\item Whether \app can successfully 
-  detect real-world configuration errors ($\S$\ref{subsec-effectiveness})?
-
-\item Whether \app can correctly detect anomalous values
-($\S$\ref{subsec-anomalous})?
-
-\item How long do training and verification last ($\S$\ref{subsec-time})?
-
-\end{itemize}
-
 \input{table}
 
-\subsection{\app's Effectiveness}
-\label{subsec-effectiveness}
-
-We now apply \app to check against real-world misconfiguration problems.
-We use a real misconfiguration dataset~\cite{configdataset}
-that were collected from several online forums, \eg, 
-Stack Overflow and MySQL forum.
-Each configuration file in this dataset was posted by 
-programmers or system administrators, 
-when they confront the misconfiguration issues in practice.
-This dataset contains 261 incorrect MySQL configuration files.
-
-We apply \app to learn and check the configuration files in this
-dataset. Then, we observe how many errors \app can detect.
-We next manually check whether these detected errors are indeed
-configuration errors.
-For all the 261 configuration files, we found \app is
-able to report all the errors correctly.
-For 217 of the 261 configuration files, we found \app's 
-error detection results are correct and accurate,
-\ie, correctly report the real misconfiguration problems
-and with few false positives.
-For the rest of 44 cases, 
-although \app can detect the errors,
-\app outputs relatively high false positives,
-\eg, higher than 50 false positives,
-which is not very helpful to users in practice.
-The reason is our training set contains too many incorrect configuration
-files, which produce a lot of noises to our learning process,
-thus resulting in so many false positives.
-
-In order to clearly evaluate the effectiveness of \app,
-we extract 20 incorrect configuration files from the dataset.
-\app is able to correctly report these configuration errors,
-and these errors cannot be handled by any existing efforts.
-Table~\ref{table-casestudy} details this information,
-including the problem descriptions of these files, 
-error types, and the outputs produced by \app.
-
-As shown in Table~\ref{table-casestudy},
-we found \app is capable of detecting many configuration errors previous
-efforts, \eg, EnCore~\cite{zhang14encore}, cannot deal with.
-To the best of our knowledge, no existing effort
-is able to detect fine-grained value correlation errors in the 
-MySQL configuration files.
-For example, the third case in Table~\ref{table-casestudy}
-presents \app detects the fine-grained correlation,
-{\tt key\_buffer\_size} should be larger than 
-{\tt sort\_buffer\_size} * {\tt max\_connections}.
-
-\begin{table*}[t]
+\begin{table*}[tpb]
 \centering
-\caption{Sampled benchmarks for anomaly detection}
+\caption{Sampled configuration files for anomaly detection}
 \label{table-anomaly}
-\begin{small}
+\begin{footnotesize}
 \begin{tabular}{|l|l|l|l|}
@@
 \end{tabular}
-\end{small}
+\end{footnotesize}
 \end{table*}
+
+\section{Evaluations}
+\label{sec-eval}
+
+We conduct three experiments to evaluate our \app
+prototype. We answer the following
+questions.
+
+\begin{itemize}
+
+\item Whether \app can successfully 
+  detect real-world configuration errors ($\S$\ref{subsec-effectiveness})?
+
+\item Whether \app can correctly detect anomalous values
+($\S$\ref{subsec-anomalous})?
+
+\item How long do training and verification last ($\S$\ref{subsec-time})?
+
+\end{itemize}
+
+\subsection{\app's Effectiveness}
+\label{subsec-effectiveness}
+
+We now apply \app to check against real-world misconfiguration problems.
+We use a real misconfiguration dataset~\cite{configdataset}
+that was collected from several online forums, \eg, 
+Stack Overflow and MySQL forums.
+Each configuration file in this dataset was posted by 
+programmers or system administrators, 
+when they confronted misconfiguration issues in practice.
+This dataset contains 261 incorrect MySQL configuration files.
+
+We apply \app to learn and check the configuration files in this
+dataset. Then, we observe how many errors \app can detect.
+We next manually check whether these detected errors are indeed
+configuration errors.
+For all the 261 configuration files, we found \app is
+able to report all the errors correctly.
+For 217 of the 261 configuration files, we found \app's 
+error detection results are correct and accurate,
+\ie, we correctly report the real misconfiguration problems
+with few false positives.
+For the rest of the 44 cases, 
+although \app can detect the errors,
+\app outputs relatively high false positives,
+\eg, higher than 50 false positives,
+which is not very helpful to users in practice.
+The reason is our training set contains too many incorrect configuration
+files, which produces a lot of noise in our learning process,
+thus resulting in so many false positives.
+
+In order to clearly evaluate the effectiveness of \app,
+we extract 20 incorrect configuration files from the dataset.
+\app is able to correctly report these configuration errors,
+and these errors cannot be handled by any existing efforts.
+Table~\ref{table-casestudy} details this information,
+including the problem descriptions of these files, 
+error types, and the outputs produced by \app.
+
+As shown in Table~\ref{table-casestudy},
+we found \app is capable of detecting many configuration errors previous
+efforts, \eg, EnCore~\cite{zhang14encore}, cannot deal with.
+To the best of our knowledge, no existing effort
+is able to detect fine-grained value correlation errors in 
+MySQL configuration files.
+For example, the third case in Table~\ref{table-casestudy}
+shows that \app can detect the following fine-grained correlation:
+{\tt key\_buffer\_size} should be larger than 
+{\tt thread\_size} *  {\tt sort\_buffer\_size}.
 
@@
 The purpose of checking anomalous values in configuration files 
-is to avoid potential performance or workload problems. 
+is to avoid potential performance or throughput problems. 
 Checking anomalous values is mainly the responsibility of
@@
 
-We run \app to check 30 real-world benchmarks from Stack Overflow 
+We run \app to check 30 real-world benchmarks from the Stack Overflow 
 website, and found \app is able to report anomalous values in
@@
 anomalous values are correct by comparing our results with
-the answers on Stack Overflow.
+answers on StackOverflow.
 
 Table~\ref{table-anomaly} shows three examples.
-We present the problem description, the link and the output results
+We present the problem description, the link, and the output results
 of \app. We found these anomalous values are very hard for
@@
 \para{Training performance.}
-We first evaluate the training time of \app. Namely, how long
+We first evaluate the training time of \app. Namely, we examine how long
 does \app need to use to generate rules.
@@
 We found the training time of \app is acceptable in practice,
-because 150 files in the training dataset have been able to make
-us obtain good enough rules.
-For 150 files, \app only needs about 7 minutes.
+because we obtained good enough rules on 150 files in the training dataset.
+For 150 files, \app only requires about 7 minutes of runtime.
 Furthermore, even if we train \app with a 200-file dataset,
@@
 We also measure the verification time of \app, and found
-the verification time is very fast. With 232,613 rules,
+that the verification time is very fast. With 232,613 rules,
 \app needs less than one second to verify a MySQL configuration file.
-\app only needs 3 minutes to finish the verifications to
-the real-world dataset~\cite{configdataset}, we used to 
+\app only needs 3 minutes to finish the verification of 
+the real-world dataset~\cite{configdataset} we used to 
 evaluate the effectiveness of \app,

### 2016-05-10 OSDI/learner.tex
update Q

@@
 The rule can be template-generated, for instance {\tt max\_connections} > {\tt mysql.max\_persistent}, or
-it can be untyped-specification-generated rule, for instance the ordering that {\tt recode.so} must come before 
+it can be untyped-specification-generated, for instance the ordering that {\tt recode.so} must come before 
 {\tt mysql.so}.
 
-For typed templates, we first filter and examine entries associated with a particular type, and then check if
-the template is satisfied over appropriately typed argument entries in the rest of the file. We do something similar for
-untyped specifications.
+The candidate entry set $Q$ in Algorithm~\ref{alg:plearn} 
+differs for the two cases.
+For typed templates, due to typing restrictions, 
+we must first filter and examine entries associated with the same type, in order to check that 
+the template is satisfied over appropriately typed argument entries. This manifests itself via $Q = filter(F,\tau)$
+in Algorithm~\ref{alg:plearn}. For
+untyped specifications, we do not need to adhere to this typing restriction, so we simply set $Q = F$.
 

### 2016-05-10 OSDI/trans.tex
config: main balance and trans

@@
     Type &  Template \\ \hline
+    \hline
     Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline

### 2016-05-10 OSDI/intro.tex
missing entry

@@
 \item \app employs a collection of machine learning algorithms to 
-enable powerful rule and constraint inference without assistance 
-from any pre-defined templates.
+enable powerful rule and constraint inference.
 
@@
 including entry ordering errors, fine-grained value correlation errors, 
-entry missing errors, and environment-related errors.
+missing entry errors, and environment-related errors.
 

### 2016-05-10 OSDI/learner.tex
missing entry

@@
 With a configuration file that has been verified against catastrophic
-failures (\eg, entry missing, type, and ordering errors), 
+failures (\eg, missing entry, type, and ordering errors), 
 the user may also want to examine more subtle issues.

### 2016-05-10 OSDI/motiv.tex
missing entry

@@
 missing entry errors.
-Below is a real-world entry missing error example~\cite{yin11anempirical}:
+Below is a real-world missing entry error example~\cite{yin11anempirical}:
 when a user wants to use OpenLDAP to enable her directory access

### 2016-05-10 OSDI/table.tex
config: table 2
missing entry

@@
 \centering
-\caption{Sampled benchmarks for misconfiguration detection}
+\caption{Sampled incorrect configuration files for 
+misconfiguration detection evaluation}
 \label{table-casestudy}
-\begin{small}
+\begin{footnotesize}
 \begin{tabular}{|l|l|l|l|}
@@
 1 & MySQL cannot create test file  
-& Entry Missing 
+& Missing Entry
 & Expected innodb\_force\_recovery=1 in the \\ & & 
@@
 2 & How can my wait\_timeout/interactive\_timeout  
-& Entry Missing
+& Missing Entry
 & Expected set\_time=1 in the same\\ & be ignored 
@@
 10 & Fail to install Percona xtraDB 
-& Entry Missing
+& Missing Entry
 & Expected wsrep\_node\_address[mysqld] \\ & cluster on ubuntu 13.04
@@
 \end{tabular}
-\end{small}
+\end{footnotesize}
 \end{table*}

### 2016-05-10 OSDI/concl.tex
config: concl

@@
 triggered during system execution time, 
-and we cannot detect misconfiguration across software components. 
+and we cannot detect misconfiguration across software components
+maintained by different parties. 
 Nevertheless, we believe \app represent a practical path

### 2016-05-10 OSDI/concl.tex
config: concl

@@
 and then uses a learner module to derive rules, 
-thus building a language model.
+building a language model this way.
 For a given configuration file we want to verify,

### 2016-05-10 OSDI/concl.tex
aa

@@
 building a language model this way.
-For a given configuration file we want to verify,
-\app uses the generated language model to check
-whether any rule is violated.
+\app then uses this generated language model 
+to verify the correctness of
+a given configuration file. The verification is done by
+checking whether any of learned rules is violated.
 We evaluate \app using a real-world dataset~\cite{configdataset}
 which contains 261 incorrect MySQL configuration files.
-Our experimental result shows \app is able to
+Our experimental result shows that \app is able to
 correctly detect errors in 217 files in that dataset.
-
+\com{
 Our \app prototype still has many limitations. 
@@
 maintained by different parties. 
-Nevertheless, we believe \app represent a practical path
-toward automatic language-based configuration verification.
+Nevertheless, w} We believe that \app represent a practical path
+toward fully automated language-based configuration verification.

### 2016-08-19 Travis/main.tex
a plan

%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.

%
% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
%               sigplanconf-guide.pdf
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------

\documentclass{sigplanconf}

% The following \documentclass options may be useful:

% preprint      Remove this option only once the paper is in final form.

% 10pt          To set in 10-point type instead of 9-point.

% 11pt          To set in 11-point type instead of 9-point.

% authoryear    To obtain author/year citation style instead of numeric.

\usepackage{amsmath}
\usepackage{todonotes}
\usepackage{graphicx}\usepackage{color}
\usepackage{csquotes}

\begin{document}

\special{papersize=8.5in,11in}\setlength{\pdfpageheight}{\paperheight}\setlength{\pdfpagewidth}{\paperwidth}
\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} \copyrightyear{20yy} \copyrightdata{978-1-nnnn-nnnn-n/yy/mm} \doi{nnnnnnn.nnnnnnn}

% Uncomment one of the following two, if you are not going for the 
% traditional copyright transfer agreement.

%\exclusivelicense                
% ACM gets exclusive license to publish,                                   
% you retain copyright

%\permissiontopublish           <  
% ACM gets nonexclusive license to publish                                  
% (paid open-access papers,                                   
% short abstracts)
\titlebanner{banner above paper title}        
% These are ignored unless\preprintfooter{short description of paper}   
% 'preprint' option specified.

\title{Detecting TravisCI Misconfiguration}
\subtitle{Plan of Attack}

\authorinfo{Name1}           {Affiliation1}           {Email1}
\authorinfo{Name2\and Name3}           {Affiliation2/3}           {Email2/3}

\maketitle

\begin{abstract}
We can detect TravisCI misconfigurations using ConfigC.
\end{abstract}

%\category{CR-number}{subcategory}{third-level}

% general terms are not compulsory anymore, 
% you may leave them out\termsterm1, term2
%\keywords keyword1, keyword2

\section{Availability of Data}

TravisCI has recently released a metadata api to study their tool\cite{API}.

The first use of this API was analyzing the metadata of builds. It was found that \textasciitilde 15-20\% of failed TravisCI builds are due to "errors". My understanding of the API is that this corresponds to a misconfiguration. This is a large enough number that not only will reducing this be more convenient for users, but it could also significantly reduce server costs for Travis. By using the \verb|tr_duration| field from the API, we can also figure out how much server time we can save\cite{API}.

\section{Feasability Anaysis}
\label{sec:feas}

The language of TravisCI configuration files can likely be handled by ConfigC.
ConfigC works on languages with shallow parse trees, and most of the .travis.yml files is shallow.
However, because .travis.yml allows for bash scripts, some error may be out of scope.
We want to identify the frequency of the types of errors - if too many are related to poorly formed bash scripts, a naive application of ConfigC will not suffice.

To confirm that the types of most misconfigurations are in the scope of ConfigC, we should compile a collection of common misconfigurations. 
Usually such a task requires a domain expert.
However, in this case we may be able to learn the common errors by using the API and the temporal data from the commits.

We might code an error as the diff between a sequential pair of an erroring commit and a passing commit. 
As a new direction, we may also explore how useful this data is for learning/verification directly.
My guess is that is data will be too noisy, but either way, it should give us a sense of the problem.

To build such a database, scrape the .travis.yml files from each commit for a set of repos.
This can be achieved with the \verb|tr_status, git_commit and gh_project_name| fields from the API.

\section{Implementation}

To build the learning set, we will use the API to build tuples of .travis.yml and repo info. 
In addition to the .travis.yml file (collected as above), we will need at a minimum \verb|gh_lang and tr_status|. 
With this \verb|(File,gh_lang,tr_status,...)| tuple, we can then (almost) directly apply ConfigC to detect errors in the shallow part of the tree.

The first (and simplest) requirement is a .travis.yml parser, which is an extension of normal yml parsing to handle travis' ability to include bash scripts.
Second, depending on the results from Sec \ref{sec:feas}, we may also require some extra domain knowledge of the types of errors to be encoded as possible rules.
This is a slightly more involved task that requires writing some non-trivial Haskell code - but it really isn't that bad.

% We recommend abbrvnat bibliography style.

\bibliographystyle{abbrvnat}

% The bibliography should be embedded for final submission.
\bibliography{biblio}

\end{document}

### 2016-08-22 Travis/main.tex
startign on time

@@
 
+\subsection{Learning from Temporal properties}
+
+An intersting extension to ConfigC on a theortical side is to look at the temporal relations between commits.
+In addition to knowledge of which .travis.yml files are correct, we can also know what changes made such a file correct (or incorrect).
+As a rough outline of a formalism, take each commit as a tuple $(T_i , C_i , S_i)$
+
 \section{Implementation}

### 2016-08-25 Travis/main.tex
actually a pretty nice sketch of temporal learning

--- 2016-08-19 Travis/main.tex
@@
 \usepackage{amsmath}
-\usepackage{todonotes}
+%\usepackage{todonotes}
 \usepackage{graphicx}\usepackage{color}
-\usepackage{csquotes}
+% \usepackage{csquotes}
 
@@
 
+\subsection{Learning from Temporal properties}
+
+An intersting extension to ConfigC on a theortical side is to look at the temporal relations between commits.
+The key observation is that with each commit that changes the build status, we can learn highly localized information about our model.
+
+The first step is to build an intermediate representation of the data we will learn.
+For the sake of efficiency, this data must be structured as a shallow tree.
+While the travis.yml file can be taken verbatim, we must use a simplification of the program code.
+Since we are only intrested in the parts of the program effecting build status, we should extract the imported libraries as a list.
+We will call this summary $S_t$, a simplified representation of the program which contains only the information relevant to the learning process.
+The subscript is a tag based on the ordered commit history.
+To handle branches, add a superscript to indicate the branch, and restart the counter on a branch - merging should be handled easily (not exactly sure how yet).
+
+From this summary we can then build a model $M(P_t)$, which is the full set of possible rules derivable from the model.
+These possible rules must be given by the user.
+In \cite{CAV}, these were called Attributes, and express constraints such as, ordering of lines, or substring relations on values.
+
+We will denote the build status of $S_t$ with $B(S_t)$.
+In this application, we consider only the passing and erroring build status, denoted $P$, and $E$ respectivly.
+All status that are not \verb|error|, as defined by the Travis API, will be included as passing.
+For brevity, we denote sequences of build statuses with the following notation:
+
+$S(P_t)=P \land S(P_{t+1})=E \implies S(P_{t,t+1}) = PE$
+
+We know that if a build is passing, then there must not exist any errors.
+That is, the model must not contain any rules which are breaking.
+Note we are not, however, garunteed that any rules from a passing commit are necessary.
+
+$S(P_t)=P \implies \forall r \in M(P_t), r \notin Br$
+
+The key insight is that when we commit a break, we can localize the error to one of the lines that changed.
+Either we removed something that was necessary, or added something that was breaking.
+We use an inclusive disjunction, since a erroring commit can break multiple things at once.
+Expressed formally, where ($\setminus$ is the set difference), that is:
+
+\begin{align*}
+  S(P_{t,t+1}) = PE \implies \\
+  \exists r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \lor \\
+  \exists r \in (M(P_{t+1}) \setminus M(P_{t})), r \in Br
+\end{align*}
+
+We then can combine all these formulas with conjunctions and send it to an SMT solver and magically get an answer.
+While exstential set operations can be expensive in general for an SMT solver, in our application this is not the case.
+Because these sets will be small thanks to the practice of making incremental commits when using source control, these operations will be fairly cheap.
+In fact, the above implication generalizes to $P_{t,t+n}$, but for efficency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is managably small.
+The definition of small here remains to be experimentally determined.
+
+In fact, I think this approach should work generally for any ML problem where we have an oracle (e.g. neural nets, SVMs), but would like justifications for the classification.
+Using this as a second stage of a machine learning algorithm might be really interesting.
+
 \section{Implementation}

### 2016-08-29 Travis/main.tex
consisstent notation

@@
 
-\title{Detecting TravisCI Misconfiguration}
+\title{Rule learning from classified temporal data}
 \subtitle{Plan of Attack}
 
-\authorinfo{Name1}           {Affiliation1}           {Email1}
+\authorinfo{Mark Santolucito}           {Yale University}           {mark.santolucito@yale.edu}
 \authorinfo{Name2\and Name3}           {Affiliation2/3}           {Email2/3}
@@
 \begin{abstract}
-We can detect TravisCI misconfigurations using ConfigC.
+Rule based classification is an effective machine learning technique that yields low misclassification rates.
+However, building a rule based system requires manual creation of large databases of logical constraints.
+We present a method to generate rule based systems from temporally structured data.
+As an demonstration of this algorithm, we implement a learner to automatically generate constraints for the TravisCI testing framework.
+The algorithm runs over Github commit histories to generate logical constraints that allow us to detect potential build errors without actually building, saving valuable programmer and server time.
 \end{abstract}
@@
 %\keywords keyword1, keyword2
+
+\section{Introduction}
 
@@
 However, because .travis.yml allows for bash scripts, some error may be out of scope.
-We want to identify the frequency of the types of errors - if too many are related to poorly formed bash scripts, a naive application of ConfigC will not suffice.
+We want to identify the frequency of the types of errors - if too many are related to poorly formed bash scripts, a naïve application of ConfigC will not suffice.
 
@@
 
-An intersting extension to ConfigC on a theortical side is to look at the temporal relations between commits.
+An interesting extension to ConfigC on a theoretical side is to look at the temporal relations between commits.
 The key observation is that with each commit that changes the build status, we can learn highly localized information about our model.
@@
 While the travis.yml file can be taken verbatim, we must use a simplification of the program code.
-Since we are only intrested in the parts of the program effecting build status, we should extract the imported libraries as a list.
-We will call this summary $S_t$, a simplified representation of the program which contains only the information relevant to the learning process.
+Since we are only interested in the parts of the program effecting build status, we should extract the imported libraries as a list.
+We will call this program summary $P_t$, a simplified representation of the program which contains only the information relevant to the learning process.
 The subscript is a tag based on the ordered commit history.
@@
 
-We will denote the build status of $S_t$ with $B(S_t)$.
-In this application, we consider only the passing and erroring build status, denoted $P$, and $E$ respectivly.
+We will denote the build status of $P_t$ with $B(P_t)$.
+In this application, we consider only the passing and erroring build status, denoted $Pass$, and $Err$ respectively.
 All status that are not \verb|error|, as defined by the Travis API, will be included as passing.
@@
 
-$S(P_t)=P \land S(P_{t+1})=E \implies S(P_{t,t+1}) = PE$
+$S(P_t)=Pass \land S(P_{t+1})=Err \implies S(P_{t,t+1}) = PE$
 
@@
 
-$S(P_t)=P \implies \forall r \in M(P_t), r \notin Br$
+$S(P_t)=Pass \implies \forall r \in M(P_t), r \notin Br$
 
@@
 We then can combine all these formulas with conjunctions and send it to an SMT solver and magically get an answer.
-While exstential set operations can be expensive in general for an SMT solver, in our application this is not the case.
-Because these sets will be small thanks to the practice of making incremental commits when using source control, these operations will be fairly cheap.
-In fact, the above implication generalizes to $P_{t,t+n}$, but for efficency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is managably small.
+While existential set operations can be expensive in general for an SMT solver, in our application this is not the case.
+Thanks to the practice of making incremental commits when using source control, these sets will be small and the SMT will be fairly cheap.
+In fact, the above implication generalizes to $P_{t,t+n}$, but for efficiency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is manageably small.
 The definition of small here remains to be experimentally determined.

### 2016-08-30 Travis/main.tex
intro

@@
 
-\title{Rule learning from classified temporal data}
+\title{Rule learning for verification from temporal data}
 \subtitle{Plan of Attack}
@@
 \authorinfo{Mark Santolucito}           {Yale University}           {mark.santolucito@yale.edu}
-\authorinfo{Name2\and Name3}           {Affiliation2/3}           {Email2/3}
+%\authorinfo{Name2\and Name3}           {Affiliation2/3}           {Email2/3}
 
@@
 We present a method to generate rule based systems from temporally structured data.
-As an demonstration of this algorithm, we implement a learner to automatically generate constraints for the TravisCI testing framework.
-The algorithm runs over Github commit histories to generate logical constraints that allow us to detect potential build errors without actually building, saving valuable programmer and server time.
+As an demonstration of this algorithm, we plan to implement a learner that automatically generates constraints for the TravisCI testing framework.
+The algorithm will utilize Github commit histories to generate logical constraints that allow us to detect potential build errors without actually building, saving valuable programmer and server time.
 \end{abstract}
@@
 \section{Introduction}
+
+Machine learning is a new direction in verification\cite{Santolucito2016,ETH_Guy}.
+However, algorithms such as neural nets and n-gram models lead to probabilistic models of correctness.
+While often effective in practice, these do not provide the true guarantees of a traditional verification approach.
+In addition, these tools often cannot provide a justification for the output.
+Neural nets behave surprisingly similarly to human brains, and providing proofs to conclusions is equally challenging.
+
+Version space learning \cite{lau2000version}.
 
@@
 These possible rules must be given by the user.
-In \cite{CAV}, these were called Attributes, and express constraints such as, ordering of lines, or substring relations on values.
+In \cite{Santolucito2016}, these were called Attributes, and express constraints such as, ordering of lines, or substring relations on values.
 

### 2016-08-30 Travis/secs/abstract.tex
restructure for ieee

--- 2016-08-30 Travis/main.tex
@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-
-%
-% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
-%               sigplanconf-guide.pdf
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
-
-\documentclass{sigplanconf}
-
-% The following \documentclass options may be useful:
-
-% preprint      Remove this option only once the paper is in final form.
-
-% 10pt          To set in 10-point type instead of 9-point.
-
-% 11pt          To set in 11-point type instead of 9-point.
-
-% authoryear    To obtain author/year citation style instead of numeric.
-
-\usepackage{amsmath}
-%\usepackage{todonotes}
-\usepackage{graphicx}\usepackage{color}
-% \usepackage{csquotes}
-
-\begin{document}
-
-\special{papersize=8.5in,11in}\setlength{\pdfpageheight}{\paperheight}\setlength{\pdfpagewidth}{\paperwidth}
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} \copyrightyear{20yy} \copyrightdata{978-1-nnnn-nnnn-n/yy/mm} \doi{nnnnnnn.nnnnnnn}
-
-% Uncomment one of the following two, if you are not going for the
-% traditional copyright transfer agreement.
-
-%\exclusivelicense
-% ACM gets exclusive license to publish,
-% you retain copyright
-
-%\permissiontopublish           <
-% ACM gets nonexclusive license to publish
-% (paid open-access papers,
-% short abstracts)
-\titlebanner{banner above paper title}
-% These are ignored unless\preprintfooter{short description of paper}
-% 'preprint' option specified.
-
-\title{Rule learning for verification from temporal data}
-\subtitle{Plan of Attack}
-
-\authorinfo{Mark Santolucito}           {Yale University}           {mark.santolucito@yale.edu}
-%\authorinfo{Name2\and Name3}           {Affiliation2/3}           {Email2/3}
-
-\maketitle
-
 \begin{abstract}
@@
 \end{abstract}
-
-%\category{CR-number}{subcategory}{third-level}
-
-% general terms are not compulsory anymore,
-% you may leave them out\termsterm1, term2
-%\keywords keyword1, keyword2
-
-\section{Introduction}
-
-Machine learning is a new direction in verification\cite{Santolucito2016,ETH_Guy}.
-However, algorithms such as neural nets and n-gram models lead to probabilistic models of correctness.
-While often effective in practice, these do not provide the true guarantees of a traditional verification approach.
-In addition, these tools often cannot provide a justification for the output.
-Neural nets behave surprisingly similarly to human brains, and providing proofs to conclusions is equally challenging.
-
-Version space learning \cite{lau2000version}.
-
-\section{Availability of Data}
-
-TravisCI has recently released a metadata api to study their tool\cite{API}.
-
-The first use of this API was analyzing the metadata of builds.
-It was found that \textasciitilde 15-20\% of failed TravisCI builds are due to "errors".
-My understanding of the API is that this corresponds to a misconfiguration.
-This is a large enough number that not only will reducing this be more convenient for users, but it could also significantly reduce server costs for Travis.
-By using the \verb|tr_duration| field from the API, we can also figure out how much server time we can save\cite{API}.
-
-\section{Feasability Anaysis}
-\label{sec:feas}
-
-The language of TravisCI configuration files can likely be handled by ConfigC.
-ConfigC works on languages with shallow parse trees, and most of the .travis.yml files is shallow.
-However, because .travis.yml allows for bash scripts, some error may be out of scope.
-We want to identify the frequency of the types of errors - if too many are related to poorly formed bash scripts, a naïve application of ConfigC will not suffice.
-
-To confirm that the types of most misconfigurations are in the scope of ConfigC, we should compile a collection of common misconfigurations.
-Usually such a task requires a domain expert.
-However, in this case we may be able to learn the common errors by using the API and the temporal data from the commits.
-
-We might code an error as the diff between a sequential pair of an erroring commit and a passing commit.
-As a new direction, we may also explore how useful this data is for learning/verification directly.
-My guess is that is data will be too noisy, but either way, it should give us a sense of the problem.
-
-To build such a database, scrape the .travis.yml files from each commit for a set of repos.
-This can be achieved with the \verb|tr_status, git_commit and gh_project_name| fields from the API.
-
-\subsection{Learning from Temporal properties}
-
-An interesting extension to ConfigC on a theoretical side is to look at the temporal relations between commits.
-The key observation is that with each commit that changes the build status, we can learn highly localized information about our model.
-
-The first step is to build an intermediate representation of the data we will learn.
-For the sake of efficiency, this data must be structured as a shallow tree.
-While the travis.yml file can be taken verbatim, we must use a simplification of the program code.
-Since we are only interested in the parts of the program effecting build status, we should extract the imported libraries as a list.
-We will call this program summary $P_t$, a simplified representation of the program which contains only the information relevant to the learning process.
-The subscript is a tag based on the ordered commit history.
-To handle branches, add a superscript to indicate the branch, and restart the counter on a branch - merging should be handled easily (not exactly sure how yet).
-
-From this summary we can then build a model $M(P_t)$, which is the full set of possible rules derivable from the model.
-These possible rules must be given by the user.
-In \cite{Santolucito2016}, these were called Attributes, and express constraints such as, ordering of lines, or substring relations on values.
-
-We will denote the build status of $P_t$ with $B(P_t)$.
-In this application, we consider only the passing and erroring build status, denoted $Pass$, and $Err$ respectively.
-All status that are not \verb|error|, as defined by the Travis API, will be included as passing.
-For brevity, we denote sequences of build statuses with the following notation:
-
-$S(P_t)=Pass \land S(P_{t+1})=Err \implies S(P_{t,t+1}) = PE$
-
-We know that if a build is passing, then there must not exist any errors.
-That is, the model must not contain any rules which are breaking.
-Note we are not, however, garunteed that any rules from a passing commit are necessary.
-
-$S(P_t)=Pass \implies \forall r \in M(P_t), r \notin Br$
-
-The key insight is that when we commit a break, we can localize the error to one of the lines that changed.
-Either we removed something that was necessary, or added something that was breaking.
-We use an inclusive disjunction, since a erroring commit can break multiple things at once.
-Expressed formally, where ($\setminus$ is the set difference), that is:
-
-\begin{align*}
-  S(P_{t,t+1}) = PE \implies \\
-  \exists r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \lor \\
-  \exists r \in (M(P_{t+1}) \setminus M(P_{t})), r \in Br
-\end{align*}
-
-We then can combine all these formulas with conjunctions and send it to an SMT solver and magically get an answer.
-While existential set operations can be expensive in general for an SMT solver, in our application this is not the case.
-Thanks to the practice of making incremental commits when using source control, these sets will be small and the SMT will be fairly cheap.
-In fact, the above implication generalizes to $P_{t,t+n}$, but for efficiency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is manageably small.
-The definition of small here remains to be experimentally determined.
-
-In fact, I think this approach should work generally for any ML problem where we have an oracle (e.g. neural nets, SVMs), but would like justifications for the classification.
-Using this as a second stage of a machine learning algorithm might be really interesting.
-
-\section{Implementation}
-
-To build the learning set, we will use the API to build tuples of .travis.yml and repo info.
-In addition to the .travis.yml file (collected as above), we will need at a minimum \verb|gh_lang and tr_status|.
-With this \verb|(File,gh_lang,tr_status,...)| tuple, we can then (almost) directly apply ConfigC to detect errors in the shallow part of the tree.
-
-The first (and simplest) requirement is a .travis.yml parser, which is an extension of normal yml parsing to handle travis' ability to include bash scripts.
-Second, depending on the results from Sec \ref{sec:feas}, we may also require some extra domain knowledge of the types of errors to be encoded as possible rules.
-This is a slightly more involved task that requires writing some non-trivial Haskell code - but it really isn't that bad.
-
-% We recommend abbrvnat bibliography style.
-
-\bibliographystyle{abbrvnat}
-
-% The bibliography should be embedded for final submission.
-\bibliography{biblio}
-
-\end{document}

### 2016-08-30 Travis/secs/feas.tex
restructure for ieee

--- 2016-08-25 Travis/main.tex
@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-
-%
-% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
-%               sigplanconf-guide.pdf
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
-
-\documentclass{sigplanconf}
-
-% The following \documentclass options may be useful:
-
-% preprint      Remove this option only once the paper is in final form.
-
-% 10pt          To set in 10-point type instead of 9-point.
-
-% 11pt          To set in 11-point type instead of 9-point.
-
-% authoryear    To obtain author/year citation style instead of numeric.
-
-\usepackage{amsmath}
-%\usepackage{todonotes}
-\usepackage{graphicx}\usepackage{color}
-% \usepackage{csquotes}
-
-\begin{document}
-
-\special{papersize=8.5in,11in}\setlength{\pdfpageheight}{\paperheight}\setlength{\pdfpagewidth}{\paperwidth}
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} \copyrightyear{20yy} \copyrightdata{978-1-nnnn-nnnn-n/yy/mm} \doi{nnnnnnn.nnnnnnn}
-
-% Uncomment one of the following two, if you are not going for the
-% traditional copyright transfer agreement.
-
-%\exclusivelicense
-% ACM gets exclusive license to publish,
-% you retain copyright
-
-%\permissiontopublish           <
-% ACM gets nonexclusive license to publish
-% (paid open-access papers,
-% short abstracts)
-\titlebanner{banner above paper title}
-% These are ignored unless\preprintfooter{short description of paper}
-% 'preprint' option specified.
-
-\title{Detecting TravisCI Misconfiguration}
-\subtitle{Plan of Attack}
-
-\authorinfo{Name1}           {Affiliation1}           {Email1}
-\authorinfo{Name2\and Name3}           {Affiliation2/3}           {Email2/3}
-
-\maketitle
-
-\begin{abstract}
-We can detect TravisCI misconfigurations using ConfigC.
-\end{abstract}
-
-%\category{CR-number}{subcategory}{third-level}
-
-% general terms are not compulsory anymore,
-% you may leave them out\termsterm1, term2
-%\keywords keyword1, keyword2
-
-\section{Availability of Data}
-
-TravisCI has recently released a metadata api to study their tool\cite{API}.
-
-The first use of this API was analyzing the metadata of builds.
-It was found that \textasciitilde 15-20\% of failed TravisCI builds are due to "errors".
-My understanding of the API is that this corresponds to a misconfiguration.
-This is a large enough number that not only will reducing this be more convenient for users, but it could also significantly reduce server costs for Travis.
-By using the \verb|tr_duration| field from the API, we can also figure out how much server time we can save\cite{API}.
-
 \section{Feasability Anaysis}
@@
 ConfigC works on languages with shallow parse trees, and most of the .travis.yml files is shallow.
-However, because .travis.yml allows for bash scripts, some error may be out of scope.
-We want to identify the frequency of the types of errors - if too many are related to poorly formed bash scripts, a naive application of ConfigC will not suffice.
-
-To confirm that the types of most misconfigurations are in the scope of ConfigC, we should compile a collection of common misconfigurations.
-Usually such a task requires a domain expert.
 However, in this case we may be able to learn the common errors by using the API and the temporal data from the commits.
@@
 This can be achieved with the \verb|tr_status, git_commit and gh_project_name| fields from the API.
-
-\subsection{Learning from Temporal properties}
-
-An intersting extension to ConfigC on a theortical side is to look at the temporal relations between commits.
-The key observation is that with each commit that changes the build status, we can learn highly localized information about our model.
-
-The first step is to build an intermediate representation of the data we will learn.
-For the sake of efficiency, this data must be structured as a shallow tree.
-While the travis.yml file can be taken verbatim, we must use a simplification of the program code.
-Since we are only intrested in the parts of the program effecting build status, we should extract the imported libraries as a list.
-We will call this summary $S_t$, a simplified representation of the program which contains only the information relevant to the learning process.
-The subscript is a tag based on the ordered commit history.
-To handle branches, add a superscript to indicate the branch, and restart the counter on a branch - merging should be handled easily (not exactly sure how yet).
-
-From this summary we can then build a model $M(P_t)$, which is the full set of possible rules derivable from the model.
-These possible rules must be given by the user.
-In \cite{CAV}, these were called Attributes, and express constraints such as, ordering of lines, or substring relations on values.
-
-We will denote the build status of $S_t$ with $B(S_t)$.
-In this application, we consider only the passing and erroring build status, denoted $P$, and $E$ respectivly.
-All status that are not \verb|error|, as defined by the Travis API, will be included as passing.
-For brevity, we denote sequences of build statuses with the following notation:
-
-$S(P_t)=P \land S(P_{t+1})=E \implies S(P_{t,t+1}) = PE$
-
-We know that if a build is passing, then there must not exist any errors.
-That is, the model must not contain any rules which are breaking.
-Note we are not, however, garunteed that any rules from a passing commit are necessary.
-
-$S(P_t)=P \implies \forall r \in M(P_t), r \notin Br$
-
-The key insight is that when we commit a break, we can localize the error to one of the lines that changed.
-Either we removed something that was necessary, or added something that was breaking.
-We use an inclusive disjunction, since a erroring commit can break multiple things at once.
-Expressed formally, where ($\setminus$ is the set difference), that is:
-
-\begin{align*}
-  S(P_{t,t+1}) = PE \implies \\
-  \exists r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \lor \\
-  \exists r \in (M(P_{t+1}) \setminus M(P_{t})), r \in Br
-\end{align*}
-
-We then can combine all these formulas with conjunctions and send it to an SMT solver and magically get an answer.
-While exstential set operations can be expensive in general for an SMT solver, in our application this is not the case.
-Because these sets will be small thanks to the practice of making incremental commits when using source control, these operations will be fairly cheap.
-In fact, the above implication generalizes to $P_{t,t+n}$, but for efficency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is managably small.
-The definition of small here remains to be experimentally determined.
-
-In fact, I think this approach should work generally for any ML problem where we have an oracle (e.g. neural nets, SVMs), but would like justifications for the classification.
-Using this as a second stage of a machine learning algorithm might be really interesting.
-
-\section{Implementation}
-
-To build the learning set, we will use the API to build tuples of .travis.yml and repo info.
-In addition to the .travis.yml file (collected as above), we will need at a minimum \verb|gh_lang and tr_status|.
-With this \verb|(File,gh_lang,tr_status,...)| tuple, we can then (almost) directly apply ConfigC to detect errors in the shallow part of the tree.
-
-The first (and simplest) requirement is a .travis.yml parser, which is an extension of normal yml parsing to handle travis' ability to include bash scripts.
-Second, depending on the results from Sec \ref{sec:feas}, we may also require some extra domain knowledge of the types of errors to be encoded as possible rules.
-This is a slightly more involved task that requires writing some non-trivial Haskell code - but it really isn't that bad.
-
-% We recommend abbrvnat bibliography style.
-
-\bibliographystyle{abbrvnat}
-
-% The bibliography should be embedded for final submission.
-\bibliography{biblio}
-
-\end{document}

### 2016-08-30 Travis/secs/implementation.tex
restructure for ieee

--- 2016-08-25 Travis/main.tex
@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-
-%
-% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
-%               sigplanconf-guide.pdf
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
-
-\documentclass{sigplanconf}
-
-% The following \documentclass options may be useful:
-
-% preprint      Remove this option only once the paper is in final form.
-
-% 10pt          To set in 10-point type instead of 9-point.
-
-% 11pt          To set in 11-point type instead of 9-point.
-
-% authoryear    To obtain author/year citation style instead of numeric.
-
-\usepackage{amsmath}
-%\usepackage{todonotes}
-\usepackage{graphicx}\usepackage{color}
-% \usepackage{csquotes}
-
-\begin{document}
-
-\special{papersize=8.5in,11in}\setlength{\pdfpageheight}{\paperheight}\setlength{\pdfpagewidth}{\paperwidth}
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} \copyrightyear{20yy} \copyrightdata{978-1-nnnn-nnnn-n/yy/mm} \doi{nnnnnnn.nnnnnnn}
-
-% Uncomment one of the following two, if you are not going for the
-% traditional copyright transfer agreement.
-
-%\exclusivelicense
-% ACM gets exclusive license to publish,
-% you retain copyright
-
-%\permissiontopublish           <
-% ACM gets nonexclusive license to publish
-% (paid open-access papers,
-% short abstracts)
-\titlebanner{banner above paper title}
-% These are ignored unless\preprintfooter{short description of paper}
-% 'preprint' option specified.
-
-\title{Detecting TravisCI Misconfiguration}
-\subtitle{Plan of Attack}
-
-\authorinfo{Name1}           {Affiliation1}           {Email1}
-\authorinfo{Name2\and Name3}           {Affiliation2/3}           {Email2/3}
-
-\maketitle
-
-\begin{abstract}
-We can detect TravisCI misconfigurations using ConfigC.
-\end{abstract}
-
-%\category{CR-number}{subcategory}{third-level}
-
-% general terms are not compulsory anymore,
-% you may leave them out\termsterm1, term2
-%\keywords keyword1, keyword2
-
-\section{Availability of Data}
-
-TravisCI has recently released a metadata api to study their tool\cite{API}.
-
-The first use of this API was analyzing the metadata of builds.
-It was found that \textasciitilde 15-20\% of failed TravisCI builds are due to "errors".
-My understanding of the API is that this corresponds to a misconfiguration.
-This is a large enough number that not only will reducing this be more convenient for users, but it could also significantly reduce server costs for Travis.
-By using the \verb|tr_duration| field from the API, we can also figure out how much server time we can save\cite{API}.
-
-\section{Feasability Anaysis}
-\label{sec:feas}
-
-The language of TravisCI configuration files can likely be handled by ConfigC.
-ConfigC works on languages with shallow parse trees, and most of the .travis.yml files is shallow.
-However, because .travis.yml allows for bash scripts, some error may be out of scope.
-We want to identify the frequency of the types of errors - if too many are related to poorly formed bash scripts, a naive application of ConfigC will not suffice.
-
-To confirm that the types of most misconfigurations are in the scope of ConfigC, we should compile a collection of common misconfigurations.
-Usually such a task requires a domain expert.
-However, in this case we may be able to learn the common errors by using the API and the temporal data from the commits.
-
-We might code an error as the diff between a sequential pair of an erroring commit and a passing commit.
-As a new direction, we may also explore how useful this data is for learning/verification directly.
-My guess is that is data will be too noisy, but either way, it should give us a sense of the problem.
-
-To build such a database, scrape the .travis.yml files from each commit for a set of repos.
-This can be achieved with the \verb|tr_status, git_commit and gh_project_name| fields from the API.
-
-\subsection{Learning from Temporal properties}
-
-An intersting extension to ConfigC on a theortical side is to look at the temporal relations between commits.
-The key observation is that with each commit that changes the build status, we can learn highly localized information about our model.
-
-The first step is to build an intermediate representation of the data we will learn.
-For the sake of efficiency, this data must be structured as a shallow tree.
-While the travis.yml file can be taken verbatim, we must use a simplification of the program code.
-Since we are only intrested in the parts of the program effecting build status, we should extract the imported libraries as a list.
-We will call this summary $S_t$, a simplified representation of the program which contains only the information relevant to the learning process.
-The subscript is a tag based on the ordered commit history.
-To handle branches, add a superscript to indicate the branch, and restart the counter on a branch - merging should be handled easily (not exactly sure how yet).
-
-From this summary we can then build a model $M(P_t)$, which is the full set of possible rules derivable from the model.
-These possible rules must be given by the user.
-In \cite{CAV}, these were called Attributes, and express constraints such as, ordering of lines, or substring relations on values.
-
-We will denote the build status of $S_t$ with $B(S_t)$.
-In this application, we consider only the passing and erroring build status, denoted $P$, and $E$ respectivly.
-All status that are not \verb|error|, as defined by the Travis API, will be included as passing.
-For brevity, we denote sequences of build statuses with the following notation:
-
-$S(P_t)=P \land S(P_{t+1})=E \implies S(P_{t,t+1}) = PE$
-
-We know that if a build is passing, then there must not exist any errors.
-That is, the model must not contain any rules which are breaking.
-Note we are not, however, garunteed that any rules from a passing commit are necessary.
-
-$S(P_t)=P \implies \forall r \in M(P_t), r \notin Br$
-
-The key insight is that when we commit a break, we can localize the error to one of the lines that changed.
-Either we removed something that was necessary, or added something that was breaking.
-We use an inclusive disjunction, since a erroring commit can break multiple things at once.
-Expressed formally, where ($\setminus$ is the set difference), that is:
-
-\begin{align*}
-  S(P_{t,t+1}) = PE \implies \\
-  \exists r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \lor \\
-  \exists r \in (M(P_{t+1}) \setminus M(P_{t})), r \in Br
-\end{align*}
-
-We then can combine all these formulas with conjunctions and send it to an SMT solver and magically get an answer.
-While exstential set operations can be expensive in general for an SMT solver, in our application this is not the case.
-Because these sets will be small thanks to the practice of making incremental commits when using source control, these operations will be fairly cheap.
-In fact, the above implication generalizes to $P_{t,t+n}$, but for efficency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is managably small.
-The definition of small here remains to be experimentally determined.
-
-In fact, I think this approach should work generally for any ML problem where we have an oracle (e.g. neural nets, SVMs), but would like justifications for the classification.
-Using this as a second stage of a machine learning algorithm might be really interesting.
-
 \section{Implementation}
@@
 
-% We recommend abbrvnat bibliography style.
-
-\bibliographystyle{abbrvnat}
-
-% The bibliography should be embedded for final submission.
-\bibliography{biblio}
-
-\end{document}
+\subsection{Limitations}
+In addition to the completness of the program summary $P_t$, and the completness of the relations that can be learned $M(P_t)$, there are challenges in a practical implementation.
+The most difficult is that the configuration language also have multiple versions. 
+We will need to fix a version of TravisCI itself, and ensure we only learn on that version.
+Additionally, this algorithm makes the assumption that TravisCI is bug free.

### 2016-08-30 Travis/secs/intro.tex
restructure for ieee

\section{Introduction}

Machine learning is a new direction in verification\cite{Santolucito2016,ETH_Guy}.
Amoung the popular algorithms are neural nets and n-gram models, which produce to probabilistic models of correctness.
While often effective in practice, these do not provide the guarantees of a traditional verification approach.
In addition, these tools are not designed to provide simple justifications for their classification outputs.

Version space learning \cite{lau2000version}.

As a demonstration of the practical use, We plan to implement our algorithm to check for TravisCI configuration errors.
TravisCI is a continous integration tool that allows programmers to automatically run their test suite on every code update.
A recent usage study of TravisCI found that \textasciitilde 15-20\% of failed TravisCI builds are due to "errors" - which means the configuration file was malformed and the software could not even be built\cite{API}.
Using the data from ~\cite{API}, we can also learn that since the start of 2014, approximately 88,000 hours of server time was used on TravisCI projects that resulted in an error status.
This number not only represents lost server time, but also lost developer time, as programmers must wait to verify that their work does not break the build.
If these malformed projects could be quickly statically checked on the client side, both TravisCI and its users could benefit.

### 2016-08-30 Travis/secs/temporal.tex
restructure for ieee

\section{Learning from Temporal properties}

An interesting extension to ConfigC on a theoretical side is to look at the temporal relations between commits.
The key observation is that with each commit that changes the build status, we can learn highly localized information about our model.

The first step is to build an intermediate representation of the data we will learn.
This data must be structured as a shallow tree for generalizable learning.
This restriction is why this approach is not appropriate for language learning on large grammars (such as a programming language).

While the travis.yml file has a simple structure and can be taken verbatim, we must use a simplification of the program code.
Since we are only interested in the parts of the program effecting build status, we should extract key feautres such as programming language and a list of imported libraries.
We will call this program summary $P_t$, a simplified representation of the repository which contains only the information relevant to the learning process.
The summary must contains every piece of information that might lead to a build error.

The subscript on $P_t$ is a tag based on the ordered commit history.
However, a git history is not a limited to a single linear timeline.
Git features the ability to \textit{branch}, which allows to simultanious commit chains.
To handle the start of a branch, add a superscript to indicate the branch, and restart the counter on a branch.
To handle the merge of two branches $P_{t}^{x}$ and $P_{t'}^{y}$, step to $P_{t+1}^{x}$, where $x$ is the mainline branch.
We then say that $P_{t'}^{y}$ has no successor commit $P_{t'+1}^{y}$.

From this summary we can then build a model $M(P_t)$, which is the full set of possible rules derivable from the program summary.
These possible rules must be given by the user.
In \cite{Santolucito2016}, these were called Attributes, and express constraints such as, ordering of lines, or substring relations on values.

We will denote the build status of $P_t$ with $B(P_t)$.
In this application, we consider only the passing and erroring build status, denoted $Pass$, and $Err$ respectively.
All status that are not \verb|error|, as defined by the Travis API, will be included as passing.
For brevity, we denote sequences of build statuses with the following notation:

\begin{align*}
  S(P_t)=Pass \land S(P_{t+1})=Err \implies S(P_{t,t+1}) = PE
\end{align*}

With this notation, we can formally express the requirement that the program summary is complete.
This is an assumption on the quality of the program summary.

\begin{align*}
  \forall S(P_t)=Err, \exists r \in M(P_t), r \in Br
\end{align*}

From the above we know that if a build is erroring, then there must exist at least one error.
By pushing the negation into the formula, we can also know that if a build is passing, then there must not exist any errors. 
That is, the model of a passing commit must not contain any rules which are breaking. 
Note we are not, however, garunteed that any rules from a passing commit are necessary.

\begin{align}
  S(P_t) = Err \implies \exists r \in  M (P_t), r \in Br \label{eq:E}\\
  S(P_t) = Pass \implies \forall r \in  M (P_t), r \notin Br \label{eq:P}
\end{align}

While Eq. \ref{eq:E} and \ref{eq:P} might build a basic model, they will do not capture all of the available knowledge.
The key insight is that when we commit a break (P E), we can localize the error to one of the lines that changed.
Either we removed something that was necessary, or added something that was breaking. 
We use an inclusive disjunction, since a erroring commit can break multiple things at once. 
Expressed formally, where (\ is the set difference), that is:

\begin{align}
  S(P_{t,t+1}) = PE \implies \nonumber \\
  \exists r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \lor \nonumber \\
  \exists r \in (M(P_{t+1}) \setminus M(P_{t})), r \in Br \label{eq:PE}
\end{align}

We then can combine all these formulas with conjunctions and send it to an SMT solver.
While existential set operations can be expensive on large sets for an SMT solver, in our application this is not the case.
Thanks to the practice of making incremental commits when using source control, these sets will be small and the SMT will be fairly cheap. 
In fact, the above implication generalizes to $P_{t,t+n}$, but for efficiency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is manageably small. 
The definition of small here remains to be experimentally determined.

\subsection{Unsatisfiability}
Note we have made a strong assumption that the summary $P_t$ contains every piece of information that might lead to a build error. 
This is the strongest assumption that we make - however our algorithm is able to detect cases where the summary is incomplete.
If we cannot find a solution for Eq. 3 it means that the set of rules we are looking for is incomplete.

### 2016-08-30 Travis/secs/intro.tex
more writing;

@@
 
-Version space learning \cite{lau2000version}.
+Version space learning is a machine learning strategy for logical constraint classification\cite{mitchell82}. 
+In addition to classification, version spaces have been used for programming-by-example \cite{lau2000version} and error detection \cite{Santolucito2016}.
+This approach learns over a set of examples that have been classified into positive and negative examples.
+We extend this approach to make use of classified examples with temporal structure, specifically by looking at the differences between sequential examples.
 
-As a demonstration of the practical use, We plan to implement our algorithm to check for TravisCI configuration errors.
+As a concrete use case, we plan to implement our algorithm to check for TravisCI configuration errors.
 TravisCI is a continous integration tool that allows programmers to automatically run their test suite on every code update.
-A recent usage study of TravisCI found that \textasciitilde 15-20\% of failed TravisCI builds are due to "errors" - which means the configuration file was malformed and the software could not even be built\cite{API}.
-Using the data from ~\cite{API}, we can also learn that since the start of 2014, approximately 88,000 hours of server time was used on TravisCI projects that resulted in an error status.
+A recent usage study of TravisCI found that 15-20\% of failed TravisCI builds are due to "errors" - which means the configuration file was malformed and the software could not even be built \cite{API}.
+Using the data from \cite{API}, we can also learn that since the start of 2014, approximately 88,000 hours of server time was used on TravisCI projects that resulted in an error status.
 This number not only represents lost server time, but also lost developer time, as programmers must wait to verify that their work does not break the build.

### 2016-08-31 Travis/secs/intro.tex
FMCAD - first draft

@@
 
-Machine learning is a new direction in verification\cite{Santolucito2016,ETH_Guy}.
-Amoung the popular algorithms are neural nets and n-gram models, which produce to probabilistic models of correctness.
+Machine learning is a powerful tool for software analysis and verification \cite{Santolucito2016,gehrpsi,garg2014ice}.
+Among the popular algorithms are neural nets and n-gram models, which produce to probabilistic models of correctness.
 While often effective in practice, these do not provide the guarantees of a traditional verification approach.
@@
 
-Version space learning is a machine learning strategy for logical constraint classification\cite{mitchell82}. 
-In addition to classification, version spaces have been used for programming-by-example \cite{lau2000version} and error detection \cite{Santolucito2016}.
-This approach learns over a set of examples that have been classified into positive and negative examples.
-We extend this approach to make use of classified examples with temporal structure, specifically by looking at the differences between sequential examples.
+In contrast, version space learning is a machine learning strategy for logical constraint classification \cite{mitchell82}, appropriate when the learning set does not contain noise.
+Extensions to version space learning have been used various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
+We first give a formal definition of the algorithm in \cite{Santolucito2016} in terms of version space learning.
+We then extend that work to leverage temporal structure in a learning set, specifically by looking at the differences between sequential examples.
 
 As a concrete use case, we plan to implement our algorithm to check for TravisCI configuration errors.
-TravisCI is a continous integration tool that allows programmers to automatically run their test suite on every code update.
+TravisCI is a continuous integration tool that allows programmers to automatically run their test suite on every code update.
 A recent usage study of TravisCI found that 15-20\% of failed TravisCI builds are due to "errors" - which means the configuration file was malformed and the software could not even be built \cite{API}.

### 2016-08-31 Travis/secs/limits.tex
FMCAD - first draft

\section{Limitations}

\subsection{Unsatisfiability}
Note we have made two assumptions in Eq. \ref{eq:E1}; first that the summary $P_t$ contains every piece of information that might lead to a build error, and second that the model $M(P_t)$ will learn all relations that might lead to a build error.
While these are the strong assumptions - our algorithm is able to detect cases where the summary is incomplete.
If we cannot find a solution for Eq. 3, it means either $P_t$ or $M(P_t)$ has been underspecified.
It is then the user's responsibility to expand the definitions accordingly.

\subsection{Trusted Base}
In addition to the completeness of $P_t$ and $M(P_t)$, we must pick a trusted base.
Since it is possible for TravisCI to have bugs, it is possible that between versions of TravisCI, two identical program summaries may have different build statuses.
Since version space learning is (generally) intolerant of noise, we require that
$P_t = P'_{t'} \implies S(P_t) = S(P'_{t'})$.

### 2016-08-31 Travis/secs/temporal.tex
FMCAD - first draft

@@
 
-An interesting extension to ConfigC on a theoretical side is to look at the temporal relations between commits.
-The key observation is that with each commit that changes the build status, we can learn highly localized information about our model.
+%The first step is to build an intermediate representation of the data we will learn.
+%This data must be structured as a shallow tree for generalizable learning.
+%This restriction is why this approach is not appropriate for language learning on large grammars (such as a programming language).
 
-The first step is to build an intermediate representation of the data we will learn.
-This data must be structured as a shallow tree for generalizable learning.
-This restriction is why this approach is not appropriate for language learning on large grammars (such as a programming language).
+In ConfigC, the configuration files were analyzed as standalone documents.
+Since a TravisCI configuration file is dependent on the code it is trying to build, we must consider a more general sense of configuration file.
+We will call this a program summary $P_t$, which is a representation of the repository which contains the information relevant to the learning process.
+In the case of TravisCI, this include the \verb|.travis.yml| file, as well as extract key code features that may effect build status, such as programming language and a list of imported libraries.
+The summary must contain every piece of information that might lead to a build error.
 
-While the travis.yml file has a simple structure and can be taken verbatim, we must use a simplification of the program code.
-Since we are only interested in the parts of the program effecting build status, we should extract key feautres such as programming language and a list of imported libraries.
-We will call this program summary $P_t$, a simplified representation of the repository which contains only the information relevant to the learning process.
-The summary must contains every piece of information that might lead to a build error.
-
-The subscript on $P_t$ is a tag based on the ordered commit history.
+The subscript on $P_t$ is a time stamp tag based on the ordered commit history.
 However, a git history is not a limited to a single linear timeline.
-Git features the ability to \textit{branch}, which allows to simultanious commit chains.
+Git features the ability to \textit{branch}, which allows to simultaneous commit chains.
 To handle the start of a branch, add a superscript to indicate the branch, and restart the counter on a branch.
@@
 
-From this summary we can then build a model $M(P_t)$, which is the full set of possible rules derivable from the program summary.
-These possible rules must be given by the user.
-In \cite{Santolucito2016}, these were called Attributes, and express constraints such as, ordering of lines, or substring relations on values.
-
-We will denote the build status of $P_t$ with $B(P_t)$.
+We will denote the build status of $P_t$ with $S(P_t)$.
 In this application, we consider only the passing and erroring build status, denoted $Pass$, and $Err$ respectively.
@@
 
+From this summary we can then build a model $M(P_t)$, as in ConfigC, which is the full set of possible relations derivable from the program summary.
+In contrast with ConfigC, we now consider both positive and negative examples and so must introduce the \textit{general boundary}.
+The general boundary is the dual of the specific boundary, and is the most relaxed requirement for a positive classification.
+We denoted specific boundary as the set of necessary relations $Nec$, and now denote the general boundary as the set of breaking relations $Br$.
 With this notation, we can formally express the requirement that the program summary is complete.
-This is an assumption on the quality of the program summary.
 
-\begin{align*}
-  \forall S(P_t)=Err, \exists r \in M(P_t), r \in Br
-\end{align*}
+\begin{align}
+  \forall S(P_t)=Err, \exists r \in M(P_t), r \in Br \label{eq:E1}
+\end{align}
 
@@
 That is, the model of a passing commit must not contain any rules which are breaking.
-Note we are not, however, garunteed that any rules from a passing commit are necessary.
+Note we are not, however, guaranteed that any rules from a passing commit are necessary.
 
@@
 We use an inclusive disjunction, since a erroring commit can break multiple things at once.
-Expressed formally, where (\ is the set difference), that is:
+Expressed formally, where $\setminus$ is the set difference, that is:
 
@@
 The definition of small here remains to be experimentally determined.
-
-\subsection{Unsatisfiability}
-Note we have made a strong assumption that the summary $P_t$ contains every piece of information that might lead to a build error. 
-This is the strongest assumption that we make - however our algorithm is able to detect cases where the summary is incomplete.
-If we cannot find a solution for Eq. 3 it means that the set of rules we are looking for is incomplete.

### 2016-08-31 Travis/secs/vspace_verify.tex
FMCAD - first draft

\section{Version Space for Verification}

Version space learning builds a logical constraint model for binary classification, or membership in a set.
ConfigC uses this approach to identify errors in configuration files for MySQL~\cite{Santolucito2016} .
ConfigC learns a model over a set of configuration files that have been labeled as correct, then reports misconfigurations.

Traditional version space learning will use a series disjunctions of a set of predefined hypotheses.
By instead restricting the model to a series of conjunctions, ConfigC can not only flag misconfigurations, but also give the points of failure for non-membership.

To build the model, ConfigC take a single file and derives all possible relations from each file, such as A comes before B, B before C, and A before C.
The user must provide templates for possible relations.
It is assumed if a file is correct, all relations in that file are necessary for another file to be correct ($Correct(C) \implies \forall r \in M(C), r \in Nec$).
In this way, the initial model is built by creating the strongest conditions for a correct file, called the \textit{specific boundary}.
This model is then iteratively relaxed as more examples are seen, a process called \textit{candidate elimination}.
To relax the model, two sets of relations from two files are merged into a single consistent set.

\begin{lstlisting}
n = {}
for (c in files):
  n1 = M(c)
  n = merge(n, n1)
\end{lstlisting}

### 2016-09-04 Travis/secs/abstract.tex
better flow and motivation

@@
 \begin{abstract}
-Rule based classification is an effective machine learning technique that yields low misclassification rates.
-However, building a rule based system requires manual creation of large databases of logical constraints.
-We present a method to generate rule based systems from temporally structured data.
-As an demonstration of this algorithm, we plan to implement a learner that automatically generates constraints for the TravisCI testing framework.
-The algorithm will utilize Github commit histories to generate logical constraints that allow us to detect potential build errors without actually building, saving valuable programmer and server time.
+In previous work we used version space learning for configuration file verification.
+We extend that work which only works on correct examples, to work on temporally structured correct and incorrect examples by building an SMT formula to find a classification model.
+As an demonstration of this algorithm, we plan to implement it to automatically verify TravisCI configurations.
+The algorithm will utilize Github histories to allow us to detect potential build errors without actually building, saving valuable programmer and server time.
 \end{abstract}

### 2016-09-04 Travis/secs/intro.tex
better flow and motivation

--- 2016-08-30 Travis/secs/intro.tex
@@
 
-Machine learning is a new direction in verification\cite{Santolucito2016,ETH_Guy}.
-Amoung the popular algorithms are neural nets and n-gram models, which produce to probabilistic models of correctness.
-While often effective in practice, these do not provide the guarantees of a traditional verification approach.
-In addition, these tools are not designed to provide simple justifications for their classification outputs.
+Machine learning can be a powerful tool for for software analysis and verification \cite{lau2000version,Santolucito2016,gehrpsi,garg2014ice}.
+However, many popular machine learning algorithms, such as neural nets and n-gram models, are not designed to provide simple justifications for their classification results.
+While effective in practice, the lack of justification for the results limits the applicability.
+In the case of error detection, the system should not only report which files have errors, but also identify the errors.
+Version space learning is a learning strategy for logical constraint classification~\cite{mitchell82}, which can be used to easily provide clear error messages.
 
-Version space learning is a machine learning strategy for logical constraint classification\cite{mitchell82}. 
-In addition to classification, version spaces have been used for programming-by-example \cite{lau2000version} and error detection \cite{Santolucito2016}.
-This approach learns over a set of examples that have been classified into positive and negative examples.
-We extend this approach to make use of classified examples with temporal structure, specifically by looking at the differences between sequential examples.
+%However, many popular machine learning algorithms, such as neural nets and n-gram models, produce probabilistic models of correctness.
+%While effective in practice, these approachs cannot be garunteed to be complete, that is they will always find the error.
+%We use version space learning to address the need for a formal completness garuntee in automated model generation for verification.
 
-As a concrete use case, we plan to implement our algorithm to check for TravisCI configuration errors.
-TravisCI is a continous integration tool that allows programmers to automatically run their test suite on every code update.
+Extensions to version space learning have been used in various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
+In previous work we used machine learning to verify configuration files by automatically learning a language model from a set of correct examples~\cite{Santolucito2016}.
+We give a formal definition of the algorithm in terms of version space learning to show how clear error messages can be produced with this technique.
+%and show that the results are garunteed to be complete.
+
+%Although the results are complete, the approach used previously produces a high false positive rate.
+Although the error messages are clear, the approach used previously produces a high false positive rate (marks correct files as incorrect).
+To decrease this, we propose an extention to the algorithm to handle sets of both incorrect and correct examples, which have a partial order.
+A partial order is common in learning sets for machine learning program analysis, as code does not exist in isolation, but changes over time with development.
+Any analysis that makes use of code from a version control system like Github will have this property.
+We predict this algorithm has the potential to significantly reduce the false positive rate.
+%A learning algorithm that uses the temporal structure of code to create sound classification with a low false positive rate can be used in at least the above listed software analysis techniques.
+
+To test this approach in practice, we plan to implement our algorithm to check for TravisCI configuration errors.
+TravisCI is a continuous integration tool connected to Github that allows programmers to automatically run their test suite on every code update (commit).
+A user adds a configuration file to the repository that enables TravisCI and specifies build conditions, such as which compiler to use, which dependencies are required, and a set of benchmarks to test.
+This ensures the tool can always be automatically built correctly on a fresh machine.
+
 A recent usage study of TravisCI found that 15-20\% of failed TravisCI builds are due to "errors" - which means the configuration file was malformed and the software could not even be built \cite{API}.

### 2016-09-04 Travis/secs/limits.tex
better flow and motivation

@@
 
-\subsection{Unsatisfiability}
+%\subsection{Unsatisfiability}
 Note we have made two assumptions in Eq.
-\ref{eq:E1}; first that the summary $P_t$ contains every piece of information that might lead to a build error, and second that the model $M(P_t)$ will learn all relations that might lead to a build error.
-While these are the strong assumptions - our algorithm is able to detect cases where the summary is incomplete.
-If we cannot find a solution for Eq. 3, it means either $P_t$ or $M(P_t)$ has been underspecified.
+\ref{eq:E1}; first that the summary $P_t$ sufficently detailed, i.e.
+contains every piece of information that might lead to a build error, and second that the model $M(P_t)$ will learn all relations that might lead to a build error, i.e.
+has a templete for all types of errors.
+While these are the strong assumptions - our algorithm is able to detect cases where these assumptions are not met.
+If we cannot find a solution for Eq. \ref{eq:PE}, it means either $P_t$ or $M(P_t)$ has been underspecified.
 It is then the user's responsibility to expand the definitions accordingly.
 
-\subsection{Trusted Base}
-In addition to the completeness of $P_t$ and $M(P_t)$, we must pick a trusted base.
-Since it is possible for TravisCI to have bugs, it is possible that between versions of TravisCI, two identical program summaries may have different build statuses.
-Since version space learning is (generally) intolerant of noise, we require that
-$P_t = P'_{t'} \implies S(P_t) = S(P'_{t'})$.
+%\subsection{Trusted Base}
+%In addition to the completeness of $P_t$ and $M(P_t)$, we must pick a trusted base.
+%Since it is possible for TravisCI to have bugs, it is possible that between versions of TravisCI, two identical program summaries may have different build statuses.
+%Since version space learning is (generally) intolerant of noise, we require that
+%$P_t = P'_{t'} \implies S(P_t) = S(P'_{t'})$.

### 2016-09-04 Travis/secs/temporal.tex
better flow and motivation

@@
 
-In ConfigC, the configuration files were analyzed as standalone documents.
+ConfigC produces clean error messages, but has a high false positive rate.
+However, ConfigC only analyzes correct configuration files, and does not consider any ordering between these correct files.
+We present an extension to ConfigC to decrease the false positive rate in ConfigC by learning on both correct and incorrect examples, as well as temporal structure of these examples.
+Our solution is to buid a logical formula representing the entire history of examples, and use a SMT solver to find a classification model.
+
 Since a TravisCI configuration file is dependent on the code it is trying to build, we must consider a more general sense of configuration file.
 We will call this a program summary $P_t$, which is a representation of the repository which contains the information relevant to the learning process.
-In the case of TravisCI, this include the \verb|.travis.yml| file, as well as extract key code features that may effect build status, such as programming language and a list of imported libraries.
-The summary must contain every piece of information that might lead to a build error.
+The subscript on $P_t$ is a timestamp tag based on the ordered git commit history.
+In the case of TravisCI, this include the \verb|.travis.yml| file, as well as code features that may effect build status, such as programming language and a list of imported libraries.
+The summary must be \textit{sufficently detailed}, that is it must contain every piece of information that might lead to a build error.
 
-The subscript on $P_t$ is a time stamp tag based on the ordered commit history.
-However, a git history is not a limited to a single linear timeline.
-Git features the ability to \textit{branch}, which allows to simultaneous commit chains.
-To handle the start of a branch, add a superscript to indicate the branch, and restart the counter on a branch.
-To handle the merge of two branches $P_{t}^{x}$ and $P_{t'}^{y}$, step to $P_{t+1}^{x}$, where $x$ is the mainline branch.
-We then say that $P_{t'}^{y}$ has no successor commit $P_{t'+1}^{y}$.
+%IMPORTANT, but no space
+%However, a git history is not a limited to a single linear timeline.
+%Git features the ability to \textit{branch}, which allows to simultaneous commit chains.
+%To handle the start of a branch, add a superscript to indicate the branch, and restart the counter on a branch.
+%To handle the merge of two branches $P_{t}^{x}$ and $P_{t'}^{y}$, step to $P_{t+1}^{x}$, where $x$ is the mainline branch.
+%We then say that $P_{t'}^{y}$ has no successor commit $P_{t'+1}^{y}$.
 
-We will denote the build status of $P_t$ with $S(P_t)$.
-In this application, we consider only the passing and erroring build status, denoted $Pass$, and $Err$ respectively.
-All status that are not \verb|error|, as defined by the Travis API, will be included as passing.
+From this summary we can then build a model $M(P_t)$, as in ConfigC, which is the full set of possible relations derivable from the program summary.
+Again, the user must provide templates for the learning process.
+
+Since we now consider both positive and negative examples, we will denote the build status of $P_t$ with $S(P_t)$.
+In this application, we consider all non-erroring build status to be passing, denoted $Pass$ and otherwise $Err$.
 For brevity, we denote sequences of build statuses with the following notation:
-
 \begin{align*}
@@
 
-From this summary we can then build a model $M(P_t)$, as in ConfigC, which is the full set of possible relations derivable from the program summary.
 In contrast with ConfigC, we now consider both positive and negative examples and so must introduce the \textit{general boundary}.
@@
 We denoted specific boundary as the set of necessary relations $Nec$, and now denote the general boundary as the set of breaking relations $Br$.
-With this notation, we can formally express the requirement that the program summary is complete.
-
+With this notation, we can formally express the requirement that the program summary is sufficently detailed.
 \begin{align}
@@
 Note we are not, however, guaranteed that any rules from a passing commit are necessary.
-
 \begin{align}
@@
 While Eq. \ref{eq:E} and \ref{eq:P} might build a basic model, they will do not capture all of the available knowledge.
-The key insight is that when we commit a break (P E), we can localize the error to one of the lines that changed.
+The key insight is that when we commit a break ($PE$), we can localize the error to one of the lines that changed.
 Either we removed something that was necessary, or added something that was breaking.
-We use an inclusive disjunction, since a erroring commit can break multiple things at once.
+Note that this is an inclusive disjunction, since a erroring commit can break multiple things at once.
 Expressed formally, where $\setminus$ is the set difference, that is:
-
 \begin{align}
-  S(P_{t,t+1}) = PE \implies \nonumber \\
-  \exists r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \lor \nonumber \\
-  \exists r \in (M(P_{t+1}) \setminus M(P_{t})), r \in Br \label{eq:PE}
+  S(P_{t,t+1}) &= PE \implies \nonumber \\
+  \exists& r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \nonumber \\
+  \lor \ \exists& r \in (M(P_{t+1}) \setminus M(P_{t})), r \in Br \label{eq:PE}
 \end{align}
 
-We then can combine all these formulas with conjunctions and send it to an SMT solver.
+We then can combine all these formulas with conjunctions and ask a SMT solver for a model satifsying the formula.
 While existential set operations can be expensive on large sets for an SMT solver, in our application this is not the case.

### 2016-09-04 Travis/secs/vspace_verify.tex
better flow and motivation

@@
 
-Version space learning builds a logical constraint model for binary classification, or membership in a set.
-ConfigC uses this approach to identify errors in configuration files for MySQL~\cite{Santolucito2016} .
-ConfigC learns a model over a set of configuration files that have been labeled as correct, then reports misconfigurations.
-
-Traditional version space learning will use a series disjunctions of a set of predefined hypotheses.
+ConfigC~\cite{Santolucito2016} learns a classification model from a set of correct configuration files, then reports misconfigurations.
+Specifically, ConfigC uses version space learing to identify errors in configuration files for MySQL.
+Version space learning builds a logical constraint model for binary classification, or membership in a set~\cite{mitchell82}.
+Traditional version space learning builds a model using a series of disjunctions from a set of predefined hypotheses.
 By instead restricting the model to a series of conjunctions, ConfigC can not only flag misconfigurations, but also give the points of failure for non-membership.
 
-To build the model, ConfigC take a single file and derives all possible relations from each file, such as A comes before B, B before C, and A before C.
-The user must provide templates for possible relations.
-It is assumed if a file is correct, all relations in that file are necessary for another file to be correct ($Correct(C) \implies \forall r \in M(C), r \in Nec$).
-In this way, the initial model is built by creating the strongest conditions for a correct file, called the \textit{specific boundary}.
+Our definition of a configuration file is a file that can be transformed to an ordered list of $(keyword, value)$ pairs, called $Line$s.
+To build the model, ConfigC take a single configuration file, $C$, and derives the set of all possible relations from each file, $M(C)$.
+The classes of relations must be provided by the user as templates.
+A template is a function taking some number of lines and determining a relation on the keywords of the lines ($Line^{n} \rightarrow Rel_{k1,..,kn}$).
+In the case of ordering rules, this function will take two lines and indicate whether the first keyword should come before, after, or have no relation to the second. 
+ConfigC features the following default rules.
+
+\begin{center}
+\begin{tabular} {|c |c |c |}
+ \hline
+ Template & Input  & Relation \\
+\hline
+ ordering & (Line,Line) & Before $\vert$ After $\vert$ None \\
+ \hline
+ integer relation & (Line,Line)  & $< | == | >$  \\
+\hline
+ type & (Line,Line)  & String $\vert$ Int $\vert$ Filepath $\vert$ IP  \\
+\hline
+ missing entry & (Line,Line) & Required $\vert$ Not \\
+\hline
+\end{tabular}
+\end{center}
+
+It is assumed if a file is correct, all relations in that file are in the set of necessary relations for any other file to be correct ($Correct(C) \implies \forall r \in M(C), r \in Nec$).
+In this way, the initial model is built by creating the strongest conditions for a correct file, called the \textit{specific boundary} in version space learning.
 This model is then iteratively relaxed as more examples are seen, a process called \textit{candidate elimination}.
-To relax the model, two sets of relations from two files are merged into a single consistent set.
+Since we maintain the strongest condition for correctness, this approach will identify many correct files as incorrect, called a high false positive rate.
+This is a problem when a user is then asked to manual review many files for errors, when the errors are not truly a problem.
 
-\begin{lstlisting}
-n = {}
-for (c in files):
-  n1 = M(c)
-  n = merge(n, n1)
-\end{lstlisting}
+When the system is run on a new file, one of the relations from the templates will not be satisfied.
+To provide an error message,the system only needs to report which relation is not satisfied.
+For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so" before "extension recode.so"}.
+
+%To relax the model, two sets of relations from two files are merged into a single consistent set.
+%\begin{lstlisting}
+%n = {}
+%for (c in files):
+%  n1 = M(c)
+%  n = merge(n, n1)
+%\end{lstlisting}

### 2016-09-04 Travis/secs/intro.tex
newintro

@@
 
-Machine learning can be a powerful tool for for software analysis and verification \cite{lau2000version,Santolucito2016,gehrpsi,garg2014ice}.
+Machine learing has been used in various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
 However, many popular machine learning algorithms, such as neural nets and n-gram models, are not designed to provide simple justifications for their classification results.
-While effective in practice, the lack of justification for the results limits the applicability.
-In the case of error detection, the system should not only report which files have errors, but also identify the errors.
+While effective in practice, the lack of justification for the results limits the applicability to software analysis, where justification is critical.
+In the case of error detection, the system should not only report which files have errors, but also locate the errors.
 Version space learning is a learning strategy for logical constraint classification~\cite{mitchell82}, which can be used to easily provide clear error messages.
@@
 
-Extensions to version space learning have been used in various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
-In previous work we used machine learning to verify configuration files by automatically learning a language model from a set of correct examples~\cite{Santolucito2016}.
-We give a formal definition of the algorithm in terms of version space learning to show how clear error messages can be produced with this technique.
+In our previous work we used version space learning to verify configuration files from a set of correct examples~\cite{Santolucito2016}.
+The tool, ConfigC, takes examples of correct files, builds a language model, which is then used to check is new configuration files adhear to those rules.
+If a file is incorrect, the tool will identify the location of error, what is incorrect.
+For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so" before "extension recode.so"}.
+We describe here this algorithm in terms of version space learning to show how clear error messages are produced with this technique.
 %and show that the results are garunteed to be complete.
@@
 Although the error messages are clear, the approach used previously produces a high false positive rate (marks correct files as incorrect).
-To decrease this, we propose an extention to the algorithm to handle sets of both incorrect and correct examples, which have a partial order.
-A partial order is common in learning sets for machine learning program analysis, as code does not exist in isolation, but changes over time with development.
-Any analysis that makes use of code from a version control system like Github will have this property.
+To decrease this, in this paper we propose an extention to the algorithm to handle sets of both incorrect and correct examples.
+We also use a commonly avaible, but underutilized structure of learning sets for machine learning for software analysis.
+Because most code does not exist in isolation, but changes over time with development, examples for a learning set can also leverage this temporal structure. 
+This structure is simply a partial order, and any analysis that makes use of code from a version control system like Github will have this property.
 We predict this algorithm has the potential to significantly reduce the false positive rate.

### 2016-09-04 Travis/secs/intro.tex
more

@@
 In our previous work we used version space learning to verify configuration files from a set of correct examples~\cite{Santolucito2016}.
-The tool, ConfigC, takes examples of correct files, builds a language model, which is then used to check is new configuration files adhear to those rules.
-If a file is incorrect, the tool will identify the location of error, what is incorrect.
+The tool, ConfigC, takes examples of correct files, builds a language model, which is then used to check if new a configuration file adhears to those rules.
+If a file is incorrect, the tool will identify the location of error, and tell the user what why it is incorrect.
 For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so" before "extension recode.so"}.

### 2016-09-04 Travis/secs/intro.tex
more

@@
 However, many popular machine learning algorithms, such as neural nets and n-gram models, are not designed to provide simple justifications for their classification results.
-While effective in practice, the lack of justification for the results limits the applicability to software analysis, where justification is critical.
+While effective in practice, the lack of justification for the results limits the applicability to software analysis, where justification is often critical.
 In the case of error detection, the system should not only report which files have errors, but also locate the errors.
-Version space learning is a learning strategy for logical constraint classification~\cite{mitchell82}, which can be used to easily provide clear error messages.
+Version space learning is a technique for logical constraint classification~\cite{mitchell82}, that provides justification, but cannot handle noise.
 
@@
 The tool, ConfigC, takes examples of correct files, builds a language model, which is then used to check if new a configuration file adhears to those rules.
-If a file is incorrect, the tool will identify the location of error, and tell the user what why it is incorrect.
+If a file is incorrect, the tool will identify the location of error, and report what is incorrect.
 For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so" before "extension recode.so"}.
-We describe here this algorithm in terms of version space learning to show how clear error messages are produced with this technique.
+
+In order to better understand how to provide justification as well as classification, we will provide a new description of ConfigC.
+We will describe the algorithm in terms of version space learning, and show how these error messages are produced with this technique.
+This description will also explain the high false positive (marking correct files as incorrect) in ConfigC.
+With this understanding, we then propose an extension to ConfigC that we predict will decrease this high false positive rate.
 %and show that the results are garunteed to be complete.
@@
 %Although the results are complete, the approach used previously produces a high false positive rate.
-Although the error messages are clear, the approach used previously produces a high false positive rate (marks correct files as incorrect).
-To decrease this, in this paper we propose an extention to the algorithm to handle sets of both incorrect and correct examples.
+We propose an algorithm to handle incorrect, as well as correct files in ConfigC.
 We also use a commonly avaible, but underutilized structure of learning sets for machine learning for software analysis.
@@
 This structure is simply a partial order, and any analysis that makes use of code from a version control system like Github will have this property.
-We predict this algorithm has the potential to significantly reduce the false positive rate.
 %A learning algorithm that uses the temporal structure of code to create sound classification with a low false positive rate can be used in at least the above listed software analysis techniques.

### 2016-09-04 Travis/secs/intro.tex
more

@@
 In the case of error detection, the system should not only report which files have errors, but also locate the errors.
-Version space learning is a technique for logical constraint classification~\cite{mitchell82}, that provides justification, but cannot handle noise.
+Version space learning is a technique for logical constraint classification~\cite{mitchell82}.
+As a logical constraint system, version space learning can provide the justification that is difficult to obtain from other methods, but suffer from a weakness that it cannot handle noise.
 
@@
 
-In order to better understand how to provide justification as well as classification, we will provide a new description of ConfigC.
-We will describe the algorithm in terms of version space learning, and show how these error messages are produced with this technique.
-This description will also explain the high false positive (marking correct files as incorrect) in ConfigC.
+In order to better understand how to provide justification as well as classification, in this paper we provide a new description of ConfigC.
+We describe the algorithm in terms of version space learning, and show how these error messages are produced with this technique.
+This description also explains the high false positive (marking correct files as incorrect) in ConfigC.
 With this understanding, we then propose an extension to ConfigC that we predict will decrease this high false positive rate.
@@
 %Although the results are complete, the approach used previously produces a high false positive rate.
-We propose an algorithm to handle incorrect, as well as correct files in ConfigC.
-We also use a commonly avaible, but underutilized structure of learning sets for machine learning for software analysis.
-Because most code does not exist in isolation, but changes over time with development, examples for a learning set can also leverage this temporal structure. 
-This structure is simply a partial order, and any analysis that makes use of code from a version control system like Github will have this property.
+While ConfigC only used correct files in the training set, we propose an algorithm to handle both correct and incorrect files in the training set.
+Additionally, the training set from ConfigC was a random sampling of configuration files, but many training sets have a structure based on version history.
+The algorithm we propose takes advantage of this commonly availible, but underutilized structure of training sets for software analysis.
+Because most code does not exist in isolation, but changes over time with development, any training set of code from a verison control system, like Github, has a rich temporal structure. 
+This structure is simply a partial order, and can be used by our proposed algorithm for more effective learning.
 %A learning algorithm that uses the temporal structure of code to create sound classification with a low false positive rate can be used in at least the above listed software analysis techniques.

### 2016-09-04 Travis/secs/intro.tex
more

@@
 While effective in practice, the lack of justification for the results limits the applicability to software analysis, where justification is often critical.
-In the case of error detection, the system should not only report which files have errors, but also locate the errors.
+For example, in the case of error detection, the system should not only report which files have errors, but also locate the errors.
 Version space learning is a technique for logical constraint classification~\cite{mitchell82}.
-As a logical constraint system, version space learning can provide the justification that is difficult to obtain from other methods, but suffer from a weakness that it cannot handle noise.
+As a logical constraint system, version space learning can provide the justification that is difficult to obtain from other methods, but its main weakness is that it cannot handle noisy data.
 
@@
 
-In our previous work we used version space learning to verify configuration files from a set of correct examples~\cite{Santolucito2016}.
-The tool, ConfigC, takes examples of correct files, builds a language model, which is then used to check if new a configuration file adhears to those rules.
+In our previous work we built a prototype to verify configuration files from a set of correct examples~\cite{Santolucito2016}.
+The tool, ConfigC, takes as a training set, a set correct files and builds a language model.
+This model is then used to check if new a configuration file adhears to those rules.
 If a file is incorrect, the tool will identify the location of error, and report what is incorrect.
 For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so" before "extension recode.so"}.
+While this prototype works well, it can only learn from correct examples and has a high false positive rate (marking correct files as incorrect).
 
-In order to better understand how to provide justification as well as classification, in this paper we provide a new description of ConfigC.
-We describe the algorithm in terms of version space learning, and show how these error messages are produced with this technique.
-This description also explains the high false positive (marking correct files as incorrect) in ConfigC.
-With this understanding, we then propose an extension to ConfigC that we predict will decrease this high false positive rate.
+In order to extend the prototype, in this paper we provide a new description of ConfigC in terms of version space learning.
+This description will allow us understand how the justifications are produced in ConfigC.
+We can the extend ConfigC with a new algorithm to decrease the false positive rate, while maintaning the ability to provide justification.
 %and show that the results are garunteed to be complete.
@@
 %Although the results are complete, the approach used previously produces a high false positive rate.
-While ConfigC only used correct files in the training set, we propose an algorithm to handle both correct and incorrect files in the training set.
-Additionally, the training set from ConfigC was a random sampling of configuration files, but many training sets have a structure based on version history.
-The algorithm we propose takes advantage of this commonly availible, but underutilized structure of training sets for software analysis.
-Because most code does not exist in isolation, but changes over time with development, any training set of code from a verison control system, like Github, has a rich temporal structure. 
+We propose an extension to ConfigC that allows it to handle both correct and incorrect files in the training set.
+Additionally, we extend ConfigC with the ability to use sstructue within the training set.
+While the training set from ConfigC was a random sampling of configuration files, many other training sets have a structure based on version history.
+%The algorithm we propose takes advantage of this commonly availible, but underutilized structure of training sets for software analysis.
+%Because most code does not exist in isolation, but changes over time with development, any training set of code from a verison control system, like Github, has a rich temporal structure. 
 This structure is simply a partial order, and can be used by our proposed algorithm for more effective learning.

### 2016-09-04 Travis/secs/intro.tex
more

@@
 In our previous work we built a prototype to verify configuration files from a set of correct examples~\cite{Santolucito2016}.
-The tool, ConfigC, takes as a training set, a set correct files and builds a language model.
+The tool, ConfigC, takes as a training set a set of correct configuration files and builds a set of rules describing a language model.
 This model is then used to check if new a configuration file adhears to those rules.
@@
 For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so" before "extension recode.so"}.
-While this prototype works well, it can only learn from correct examples and has a high false positive rate (marking correct files as incorrect).
+While this prototype's results are promising, the main weakness are that the learning can only use correct configuration files.
+Additionally, there is a relatively high false positive rate (marking correct files as incorrect).
 
 In order to extend the prototype, in this paper we provide a new description of ConfigC in terms of version space learning.
-This description will allow us understand how the justifications are produced in ConfigC.
-We can the extend ConfigC with a new algorithm to decrease the false positive rate, while maintaning the ability to provide justification.
+This description will allow us to understand how the justifications are produced in ConfigC.
+We can then extend ConfigC with a new algorithm to decrease the false positive rate, while maintaning the ability to provide justification.
 %and show that the results are garunteed to be complete.
@@
 We propose an extension to ConfigC that allows it to handle both correct and incorrect files in the training set.
-Additionally, we extend ConfigC with the ability to use sstructue within the training set.
+Additionally, we extend ConfigC with the ability to use structue within the training set.
 While the training set from ConfigC was a random sampling of configuration files, many other training sets have a structure based on version history.
@@
 
-A recent usage study of TravisCI found that 15-20\% of failed TravisCI builds are due to "errors" - which means the configuration file was malformed and the software could not even be built \cite{API}.
+A recent usage study~\cite{API} of TravisCI found that 15-20\% of failed TravisCI builds are due to "errors" - which is the TravisCI code used to mean the configuration file was malformed and the software could not even be built.
 Using the data from \cite{API}, we can also learn that since the start of 2014, approximately 88,000 hours of server time was used on TravisCI projects that resulted in an error status.
@@
 If these malformed projects could be quickly statically checked on the client side, both TravisCI and its users could benefit.
+
+Our main contributions are then as follow:
+
+\begin{enumerate}
+
+\item We give a description of our prototype tool, ConfigC, in the context of version space learning.
+\item We propose a new algorithm for ConfigC to handle both incorrect and correct training data, as well as internal structure of a training set.
+\item We propose a real-world application of this approach, and outline the steps needed for an implementation.
+
+\end{enumerate}

### 2016-09-04 Travis/secs/temporal.tex
more

@@
 We present an extension to ConfigC to decrease the false positive rate in ConfigC by learning on both correct and incorrect examples, as well as temporal structure of these examples.
-Our solution is to buid a logical formula representing the entire history of examples, and use a SMT solver to find a classification model.
+This extension will buid a logical formula representing the entire history of examples, and use a SMT solver to find a classification model.
 
@@
 
-Since we now consider both positive and negative examples, we will denote the build status of $P_t$ with $S(P_t)$.
+Since we now consider both incorrect and correct data, we will denote the build status of $P_t$ with $S(P_t)$.
 In this application, we consider all non-erroring build status to be passing, denoted $Pass$ and otherwise $Err$.
@@
 
-In contrast with ConfigC, we now consider both positive and negative examples and so must introduce the \textit{general boundary}.
+In contrast with ConfigC, we now consider both incorrect and correct and so must introduce the \textit{general boundary}.
 The general boundary is the dual of the specific boundary, and is the most relaxed requirement for a positive classification.

### 2016-09-04 Travis/secs/vspace_verify.tex
newintro
more

@@
 
-ConfigC~\cite{Santolucito2016} learns a classification model from a set of correct configuration files, then reports misconfigurations.
-Specifically, ConfigC uses version space learing to identify errors in configuration files for MySQL.
 Version space learning builds a logical constraint model for binary classification, or membership in a set~\cite{mitchell82}.
 Traditional version space learning builds a model using a series of disjunctions from a set of predefined hypotheses.
-By instead restricting the model to a series of conjunctions, ConfigC can not only flag misconfigurations, but also give the points of failure for non-membership.
+In ConfigC, we instead restrict the model to a series of conjunctions.
+This way, ConfigC can not only flag misconfigurations, but also give the points of failure for non-membership.
+We now show in detail how this process works.
 
@@
 This model is then iteratively relaxed as more examples are seen, a process called \textit{candidate elimination}.
-Since we maintain the strongest condition for correctness, this approach will identify many correct files as incorrect, called a high false positive rate.
-This is a problem when a user is then asked to manual review many files for errors, when the errors are not truly a problem.
+Since we maintain the strongest condition for correctness, this approach will identify many correct files as incorrect, which we call a high false positive rate.
+This is a problem when a user is then asked to manually review many files for errors, when the files are in fact correct.
 
 When the system is run on a new file, one of the relations from the templates will not be satisfied.
-To provide an error message,the system only needs to report which relation is not satisfied.
-For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so" before "extension recode.so"}.
+To provide an error message, the system only needs to report which relation is not satisfied.
 

### 2016-09-04 Travis/secs/intro.tex
more

@@
 
-Machine learing has been used in various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
+Machine learning has been used in various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
 However, many popular machine learning algorithms, such as neural nets and n-gram models, are not designed to provide simple justifications for their classification results.
@@
 
-In our previous work we built a prototype to verify configuration files from a set of correct examples~\cite{Santolucito2016}.
+In our previous work~\cite{Santolucito2016} we built a prototype to verify configuration files from a set of correct examples.
 The tool, ConfigC, takes as a training set a set of correct configuration files and builds a set of rules describing a language model.
-This model is then used to check if new a configuration file adhears to those rules.
-If a file is incorrect, the tool will identify the location of error, and report what is incorrect.
+This model is then used to check if a new configuration file adhears to those rules.
+If a file is incorrect, the tool identifies the location of error, and reports what is incorrect.
 For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so" before "extension recode.so"}.
@@
 This description will allow us to understand how the justifications are produced in ConfigC.
-We can then extend ConfigC with a new algorithm to decrease the false positive rate, while maintaning the ability to provide justification.
+We can then extend ConfigC with a new algorithm to decrease the false positive rate, while maintaining the ability to provide justification.
 %and show that the results are garunteed to be complete.
@@
 We propose an extension to ConfigC that allows it to handle both correct and incorrect files in the training set.
-Additionally, we extend ConfigC with the ability to use structue within the training set.
-While the training set from ConfigC was a random sampling of configuration files, many other training sets have a structure based on version history.
+Additionally, we extend ConfigC with the ability to use structure within the training set.
+While the previous training set from ConfigC was a random sampling of configuration files, many other training sets have a structure based on version history.
 %The algorithm we propose takes advantage of this commonly availible, but underutilized structure of training sets for software analysis.
@@
 
-To test this approach in practice, we plan to implement our algorithm to check for TravisCI configuration errors.
+To test this approach in practice, we plan to implement our algorithm to check for TravisCI\footnote{http://www.travis-ci.com} configuration errors.
 TravisCI is a continuous integration tool connected to Github that allows programmers to automatically run their test suite on every code update (commit).

### 2016-09-04 Travis/secs/temporal.tex
more

@@
 We present an extension to ConfigC to decrease the false positive rate in ConfigC by learning on both correct and incorrect examples, as well as temporal structure of these examples.
-This extension will buid a logical formula representing the entire history of examples, and use a SMT solver to find a classification model.
+This extension will build a logical formula representing the entire history of examples, and use a SMT solver to find a classification model.
 
@@
 In the case of TravisCI, this include the \verb|.travis.yml| file, as well as code features that may effect build status, such as programming language and a list of imported libraries.
-The summary must be \textit{sufficently detailed}, that is it must contain every piece of information that might lead to a build error.
+The summary must be \textit{sufficiently detailed}, that is it must contain every piece of information that might lead to a build error.
 
@@
 
-Since we now consider both incorrect and correct data, we will denote the build status of $P_t$ with $S(P_t)$.
-In this application, we consider all non-erroring build status to be passing, denoted $Pass$ and otherwise $Err$.
+We will denote the build status returned from TravisCI when run on $P_t$ with $S(P_t)$.
+Any files with a $Pass$ build status are correct, and any files with an $Err$ build status are incorrect.
+%In this application, we consider all non-erroring build status to be passing, denoted $Pass$ and otherwise $Err$.
 For brevity, we denote sequences of build statuses with the following notation:
@@
 We denoted specific boundary as the set of necessary relations $Nec$, and now denote the general boundary as the set of breaking relations $Br$.
-With this notation, we can formally express the requirement that the program summary is sufficently detailed.
+With this notation, we can formally express the requirement that the program summary is sufficiently detailed.
 \begin{align}
@@
 
-We then can combine all these formulas with conjunctions and ask a SMT solver for a model satifsying the formula.
+We then can combine Eq \ref{eq:E}, \ref{eq:P}, and \ref{eq:PE} with conjunctions and ask a SMT solver for a model satifying the formula.
 While existential set operations can be expensive on large sets for an SMT solver, in our application this is not the case.

### 2016-09-04 Travis/secs/vspace_verify.tex
more

@@
 
-Version space learning builds a logical constraint model for binary classification, or membership in a set~\cite{mitchell82}.
-Traditional version space learning builds a model using a series of disjunctions from a set of predefined hypotheses.
-In ConfigC, we instead restrict the model to a series of conjunctions.
+Version space learning builds a logical constraint model for binary classification, which we use to test a configuration file for membership in the set of all correct files~\cite{mitchell82}.
+Traditional version space learning builds a model that tests membership using a series of disjunctions from a set of predefined hypotheses.
+In ConfigC, we instead restrict the model to use a series of conjunctions.
+In other words, rather than describing a correct file by allowable traits, we describe the required traits. 
 This way, ConfigC can not only flag misconfigurations, but also give the points of failure for non-membership.
@@
 
-Our definition of a configuration file is a file that can be transformed to an ordered list of $(keyword, value)$ pairs, called $Line$s.
-To build the model, ConfigC take a single configuration file, $C$, and derives the set of all possible relations from each file, $M(C)$.
-The classes of relations must be provided by the user as templates.
+Our definition of a configuration file, $C$, is a file that can be transformed to an ordered list of $(keyword, value)$ pairs, called $Line$s.
+ConfigC builds a model for a single file, $M(C)$, that is the set of all possible relations between the lines in the file.
+A relation is described by user provided templates.
 A template is a function taking some number of lines and determining a relation on the keywords of the lines ($Line^{n} \rightarrow Rel_{k1,..,kn}$).
-In the case of ordering rules, this function will take two lines and indicate whether the first keyword should come before, after, or have no relation to the second. 
-ConfigC features the following default rules.
+As an example, ConfigC might derive the relation \texttt{extension mysql.so} comes before \texttt{extension recode.so} by using the ordering template.
+ConfigC features the following default templates.
 

### 2016-09-04 Travis/secs/temporal.tex
more

@@
 
-ConfigC produces clean error messages, but has a high false positive rate.
+ConfigC can provide justifications, but has a high false positive rate.
 However, ConfigC only analyzes correct configuration files, and does not consider any ordering between these correct files.
-We present an extension to ConfigC to decrease the false positive rate in ConfigC by learning on both correct and incorrect examples, as well as temporal structure of these examples.
+We present a new algorithm to decrease the false positive rate in ConfigC by learning on both correct and incorrect examples, as well as temporal structure of these examples.
 This extension will build a logical formula representing the entire history of examples, and use a SMT solver to find a classification model.
@@
 We then can combine Eq \ref{eq:E}, \ref{eq:P}, and \ref{eq:PE} with conjunctions and ask a SMT solver for a model satifying the formula.
-While existential set operations can be expensive on large sets for an SMT solver, in our application this is not the case.
-Thanks to the practice of making incremental commits when using source control, these sets will be small and the SMT will be fairly cheap.
-In fact, the above implication generalizes to $P_{t,t+n}$, but for efficiency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is manageably small.
-The definition of small here remains to be experimentally determined.
+The resulting model will be the sets $Nec$, and $Br$, which can be used to check new configuration files.
+Since we used a similar model to ConfigC, we will still be able to provide justifications for the classification results.
+
+%While existential set operations can be expensive on large sets for an SMT solver, in our application this is not the case.
+%Thanks to the practice of making incremental commits when using source control, these sets will be small and the SMT will be fairly cheap.
+%In fact, the above implication generalizes to $P_{t,t+n}$, but for efficiency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is manageably small.
+%The definition of small here remains to be experimentally determined.

### 2016-09-05 Travis/secs/intro.tex
for fmacad;

@@
 
-To test this approach in practice, we plan to implement our algorithm to check for TravisCI\footnote{http://www.travis-ci.com} configuration errors.
+To test this approach in practice, we plan to implement our algorithm to check for TravisCI\footnote{\url{http://www.travis-ci.com}} configuration errors.
 TravisCI is a continuous integration tool connected to Github that allows programmers to automatically run their test suite on every code update (commit).
@@
 
-A recent usage study~\cite{API} of TravisCI found that 15-20\% of failed TravisCI builds are due to "errors" - which is the TravisCI code used to mean the configuration file was malformed and the software could not even be built.
+A recent usage study~\cite{API} of TravisCI found that 15-20\% of failed TravisCI builds are due to "errors" - which is the TravisCI name used to mean the configuration file was malformed and the software could not even be built.
 Using the data from \cite{API}, we can also learn that since the start of 2014, approximately 88,000 hours of server time was used on TravisCI projects that resulted in an error status.

### 2016-09-05 Travis/secs/temporal.tex
for fmacad;

@@
 From the above we know that if a build is erroring, then there must exist at least one error.
-By pushing the negation into the formula, we can also know that if a build is passing, then there must not exist any errors.
+%By pushing the negation into the formula,
+We can also know that if a build is passing, then there must not exist any errors.
 That is, the model of a passing commit must not contain any rules which are breaking.
@@
 
-While Eq. \ref{eq:E} and \ref{eq:P} might build a basic model, they will do not capture all of the available knowledge.
-The key insight is that when we commit a break ($PE$), we can localize the error to one of the lines that changed.
+%While Eq. \ref{eq:E} and \ref{eq:P} might build a basic model, they will do not capture all of the available knowledge.
+%The key insight is that 
+Additionally, when we commit a break ($PE$), we can localize the error to one of the relations that changed.
 Either we removed something that was necessary, or added something that was breaking.

### 2016-10-03 Travis/secs/limits.tex
add old

@@
 
-%\subsection{Trusted Base}
-%In addition to the completeness of $P_t$ and $M(P_t)$, we must pick a trusted base.
-%Since it is possible for TravisCI to have bugs, it is possible that between versions of TravisCI, two identical program summaries may have different build statuses.
-%Since version space learning is (generally) intolerant of noise, we require that
-%$P_t = P'_{t'} \implies S(P_t) = S(P'_{t'})$.
+\subsection{Trusted Base}
+In addition to the completeness of $P_t$ and $M(P_t)$, we must pick a trusted base.
+Since it is possible for TravisCI to have bugs, it is possible that between versions of TravisCI, two identical program summaries may have different build statuses.
+Since version space learning is (generally) intolerant of noise, we require that
+$P_t = P_{t'} \implies S(P_t) = S(P_{t'})$.

### 2016-10-03 Travis/secs/temporal.tex
add old

@@
 %IMPORTANT, but no space
-%However, a git history is not a limited to a single linear timeline.
-%Git features the ability to \textit{branch}, which allows to simultaneous commit chains.
-%To handle the start of a branch, add a superscript to indicate the branch, and restart the counter on a branch.
-%To handle the merge of two branches $P_{t}^{x}$ and $P_{t'}^{y}$, step to $P_{t+1}^{x}$, where $x$ is the mainline branch.
-%We then say that $P_{t'}^{y}$ has no successor commit $P_{t'+1}^{y}$.
+However, a git history is not a limited to a single linear timeline.
+Git features the ability to \textit{branch}, which allows to simultaneous commit chains.
+To handle the start of a branch, add a superscript to indicate the branch, and restart the counter on a branch.
+To handle the merge of two branches $P_{t}^{x}$ and $P_{t'}^{y}$, step to $P_{t+1}^{x}$, where $x$ is the mainline branch.
+We then say that $P_{t'}^{y}$ has no successor commit $P_{t'+1}^{y}$.
+Note the ability to handle branching implies this method is suitable to any learning set which has a partial order.
 
@@
 Any files with a $Pass$ build status are correct, and any files with an $Err$ build status are incorrect.
-%In this application, we consider all non-erroring build status to be passing, denoted $Pass$ and otherwise $Err$.
+In this application, we consider all non-erroring build status to be passing, denoted $Pass$ and otherwise $Err$.
 For brevity, we denote sequences of build statuses with the following notation:
@@
 
-%While existential set operations can be expensive on large sets for an SMT solver, in our application this is not the case.
-%Thanks to the practice of making incremental commits when using source control, these sets will be small and the SMT will be fairly cheap.
-%In fact, the above implication generalizes to $P_{t,t+n}$, but for efficiency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is manageably small.
-%The definition of small here remains to be experimentally determined.
+While existential set operations can be expensive on large sets for an SMT solver, in our application this is not the case.
+Thanks to the practice of making incremental commits when using source control, these sets will be small and the SMT will be fairly cheap.
+In fact, the above implication generalizes to $P_{t,t+n}$, but for efficiency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is manageably small.
+The definition of small here remains to be experimentally determined.

### 2016-10-03 Travis/secs/vspace_verify.tex
for fmacad;
add old

@@
 
-It is assumed if a file is correct, all relations in that file are in the set of necessary relations for any other file to be correct ($Correct(C) \implies \forall r \in M(C), r \in Nec$).
+It is assumed if a file is correct, all relations in that file are in the set of necessary relations, $Nec$, for any other file to be correct ($Correct(C) \implies \forall r \in M(C), r \in Nec$).
 In this way, the initial model is built by creating the strongest conditions for a correct file, called the \textit{specific boundary} in version space learning.
 This model is then iteratively relaxed as more examples are seen, a process called \textit{candidate elimination}.
+To relax the model, two sets of relations from two files are merged into a single consistent set.
+\begin{lstlisting}
+n = {}
+for (c in files):
+  n1 = M(c)
+  n = merge(n, n1)
+\end{lstlisting}
+
 Since we maintain the strongest condition for correctness, this approach will identify many correct files as incorrect, which we call a high false positive rate.
@@
 
-When the system is run on a new file, one of the relations from the templates will not be satisfied.
-To provide an error message, the system only needs to report which relation is not satisfied.
-
-%To relax the model, two sets of relations from two files are merged into a single consistent set.
-%\begin{lstlisting}
-%n = {}
-%for (c in files):
-%  n1 = M(c)
-%  n = merge(n, n1)
-%\end{lstlisting}
+%When the system is run on a new file, one of the relations from the templates will not be satisfied.
+%To provide an error message, the system only needs to report which relation is not satisfied.

### 2016-11-10 Ennan-Proposal/motivation.tex
add proposal

\section{Motivation}
\label{sec:intro}

Configuration errors are one of the most important root causes of
today's software system failures~\cite{xu15systems, yin11anempirical}.
We read in the news that recently there was a problem in accessing  Facebook and Instagram \cite{mashableNews} and a Facebook spokeswoman that this was due to a change to the site's configuration systems.
While program verification is mostly focused on detecting errors 
in code, in their empirical study Yin {\em et al.}~\cite{yin11anempirical} report
that about 31\% of system failures were caused by configuration errors problems and only 20\% were caused by bugs in program code. Configuration 
errors are commonly known in literature under the name misconfigurations.

Misconfigurations, in practice, may result in various
system-wide problems, such as security vulnerabilities, 
application crashes, severe disruptions in software
functionality, and incorrect program executions%
~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.

The systems research community has recognized this as an important
problem. In fact, at this year's OSDI conference (Operating Systems
Design and Implementation, a top-tier system conference) a paper on
detecting configuration errors~\cite{xu16early} received the best paper 
award. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration errors~\cite{attariyan10automating,
su07autobash, whitaker04configuration},
those tools mainly try to understand {\emph{what}} caused the 
error -- they are still not on a level of
automatic verification tools used for regular program 
verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
detect errors without executing the code.

\subsection{Examples}
\label{sec:intro-examples}

We start by presenting two non-trivial configuration errors
extracted from real-world examples. Although the errors are relatively simple, we call them 
non-trivial, because the majority of existing tools, \eg, learning-based checking
tools~\cite{zhang14encore, wang04automatic}, cannot detect
these configuration errors. Most of the presented examples were found on StackOverflow,
a popular question and answer website for programmers.

\para{Example~1: Ordering errors.} 
When a user configures PHP  to run with the Apache HTTP Server, most 
likely the user will take some already existing configuration files and 
adapt them to suit her needs. The configuration file might contain, among 
others,  the following lines:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
extension = mysql.so
...
extension = recode.so
\end{lstlisting} 
In that case the configuration file will cause the Apache server to 
fail to start due to a segmentation fault error. 
This is because, when using PHP in Apache, the extension {\tt mysql.so} 
depends on {\tt recode.so}, and their relative ordering
is crucial. This is an example of so-called {\em ordering error}.
Yin {\em et al.} report that ordering errors widely exist in
many system configurations, \eg, PHP and MySQL,
and typically lead to multiple system crash events.
However, no existing tool in the systems research can effectively solve 
or detect this problem~\cite{zhang14encore, xu15systems, xu13do}.

\para{Example~2: Fine-grained value correlation error.} 
Next example also comes from a discussion on 
StackOverflow~\cite{correlation}.
The user has configured her MySQL as in the following:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
key_buffer_size = 384M
max_heap_table_size = 128M
max_connections = 64
thread_cache_size = 8
...
sort_buffer_size = 32M
join_buffer_size = 32M
read_buffer_size = 32M
read_rnd_buffer_size = 8M
...
\end{lstlisting} 
The user then complained that her MySQL load was very high, causing the website's
response speed to be very slow.
In this case, {\tt key\_buffer\_size} is used by all the threads
cooperatively, while {\tt join\_buffer} and {\tt sort\_buffer} are 
created by each thread for private use; thus, the maximum amount
of used key buffer, \ie, {\tt key\_buffer\_size}, should be larger than 
{\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
Clearly, in the above example, it does not hold, 
so this misconfiguration causes MySQL to load very slowly.
This type of error is more sophisticated than the simple value correlation that some tools can detect~\cite{yin11anempirical, zhang14encore}.

\subsection{Challenges}
\label{sec:intro-chal}

We believe there are two main obstacles 
why we cannot simply apply the existing automatic 
tools and techniques to verification of configuration files are:
\begin{itemize}
\item a lack
of a specification which would describe properties of configuration files
\item a program structure of configuration files -- they
are mainly a sequence of entries assigning some value to system variables. 
\end{itemize}
The language in which configuration files are written does 
not adhere to a specific grammar or syntax. In particular, the
entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries and there
is no explicit structure policy for the entries.
We believe that those are the reasons why there is no automated verification of configuration 
files although the system community expressed that that would be highly
desirable~\cite{wang04automatic, zhang14encore, xu15systems}.

\subsection{Automated Verification of Configuration Files}
\label{sec:intro-goal}

The goal of this proposal is to develop a fully {\bf {automated 
verification  framework for general software configurations}}. We plan to
overcome the above obstacles by first automatically inferring a
specification for configuration files. It is unrealistic to expect the 
users to write a specifications for configuration files on their own. 
This process can easily lead to incomplete or even contradictory 
specifications.  Instead, we will learn specification from 
a large sample of 
configuration files. We start a learning process that takes as input this 
sample. The process will be language-agnostic and should work for any kind 
of configuration files,  but all of the files in the sample need to be of 
the same kind (such as MySQL or 
HTTPD configuration files). From that sample, we will learn an abundant set of rules 
specifying various properties that hold on the given sample. The rules, in general, 
specify which properties variables in configuration files need to satisfy. One can see this learning process as 
a way of deriving  a specification for configuration files. With these  rules we can efficiently check 
the correctness of the configuration files of interest and detect 
potential errors. Errors are reported if the configuration file does not 
adhere to a specification.

For practical purposes we plan to use a real-world dataset~\cite{configdataset}. The 
files in the sample might contain
errors, but they are typically different errors and only appear in a small percentage of 
files. We will, therefore, use probabilistic learning to derive a set of accurate rules.

Building such an automatic verification framework for
configuration files requires addressing several challenges. 
First, in the process of inferring a specification, we have to 
analyze mainly with an untyped, unstructured sequence of assignments.
Thus, we need to develop a suitable language model. We do that by 
``guessing'' a type of variables and then deriving formulas that
describe relationships between these variables. However, the
type of a variable cannot always be fully determined 
from a single value. 
For example, an entry {\tt something = 1} assigns 
\ruzica{here, something is 1 which is int, but it is actually a Boolean}
\ruzica{more story here}
Some existing type inference 
work would report this is an error, because {\tt temp\_dir} should be assigned
an integer~\cite{zhang14encore}. We address this problem by introducing the concept of
{\emph{probabilistic types}}.
Rather than assigning only one variable to a single type, 
we assign several types over a probability distribution. 
Using probabilistic types,
we aim to generate a more accurate language model,
thus significantly improving our verification capabilities.

Second, we will learn patterns describing variables and their relations. We will associate with each type a set of very general templates. The user does not need to provide any templates -- they are internally associated to the types.
Nevertheless, in addition to those general templates, we still need specific algorithms to learn
rules that cannot be easily templated.

From a practical perspective, we do not want to introduces any additional burden 
to the user: they can simply use \app to check for errors in their
configuration files. However, they can also easily extend the framework
themselves. The system is designed to be highly modular. If there is a
class of rules that \app is not currently learning, the user can develop
her own templates and learners for that class. The new learner can be
added to \app and this way it can check an additional new set of
errors.

Our \app prototype still has many limitations:
for example, we cannot handle configuration errors that can be 
triggered during system execution time.
Nevertheless, we believe \app may suggest a practical path
toward automatic and modular language-based configuration verification.
To summarize, this tool paper makes the following contributions:

\begin{enumerate}

\item We propose the first automatic configuration verification
framework, \app, that can learn a language model from a sample
dataset, and then use this language model to verify 
configuration files of interest.

\item \app proposes probabilistic types to assign a confidence 
distribution over a set of types to each entry, 
while generating the intermediate representation.

\item \app employs a collection of machine learning algorithms to 
enable powerful rule and constraint inference.

\item \app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including entry ordering errors, fine-grained value correlation errors, 
missing entry errors, and environment-related errors.

\item We implement a \app prototype and evaluate it by
conducting comprehensive experiments on real-world dataset.

\end{enumerate}

### 2016-11-10 Ennan-Proposal/related.tex
add proposal

--- 2016-05-10 OSDI/rel.tex
@@
 
-\para{Configuration languages.}
+\paragraph{Configuration languages.}
 There have been several language support efforts proposed for preventing
@@
 
-\para{Misconfiguration detection.}
+\paragraph{Misconfiguration detection.}
 Misconfiguration detection techniques aim at checking configuration
@@
 
-\para{Misconfiguration diagnosis.}
+\paragraph{Misconfiguration diagnosis.}
 Many misconfiguration diagnosis approaches have been proposed%
@@
 diagnosis efforts aim at finding errors after system
-failures occur, which typically leads to prolonged recovery time.
+failures occur, which leads to prolonged recovery time.
 
-\para{Misconfiguration tolerance.}
+\paragraph{Misconfiguration tolerance.}
 There have been several efforts proposed to test whether systems are 
@@
 Our work belongs to the latter case, which is used to 
-prevent configuration errors before system failures occur.
+prevent configuration errors before system outages.

### 2016-11-10 Ennan-Proposal/travis.tex
add proposal

\section{Extending \app Via Version Space Learning}
\label{sec:travis}

The current design of \app does not have any assumptions on whether the
configuration files in the training sets are correct or 
incorrect, thus making \app more general and practical.
Nevertheless, some cases in practice 
may allow us to assume some of configuration 
files in the training sets are guaranteed to be correct.
For example, TravisCI is a famous system connected 
to Github, and it allows programmers to automatically run 
their test suites on every code commit. 
Thus, a TravisCI user needs to add a configuration file 
to the repository that 
enables TravisCI and specifies build conditions, 
such as which dependencies are required, 
and a set of benchmarks to test. This ensures 
the tool to be automatically built correctly on a fresh machine.
Such a configuration file management scheme, in fact, guarantees 
the configuration file versions in the commit history to be 
correct -- otherwise, TravisCI should not work correctly in the past.
\ennan{Need one or two sentences to describe TravisCI misconfiguration
problem is important.}

Driven by the above motivating example, 
we propose an extension to \app that
learns a given training set with pre-knowledge that 
this training set contains some configuration files 
guaranteed to be correct.
Such an extension employs a new algorithm, named version space learning,
to significantly decrease the false positive rate while maintaining 
the detection capability of \app.

\subsection{Version Space For Verification}

Version space learning builds a logical constraint model for binary
classification, which we use to test a configuration file for membership
in the set of all correct files~\cite{mitchell82}.
Traditional version space learning builds a model that tests membership
using a series of disjunctions from a set of predefined hypotheses.
In the extended \app, rather than describing a correct file by allowable 
traits, we describe the required traits. 
This way, our system can not only flag misconfigurations, 
but also give the points of failure for non-membership.
We now show in detail how this process works.

Our definition of a configuration file, $C$, is a file that can be
transformed to an ordered list of $(keyword, value)$ pairs, called
$Line$s. \app builds a model for a single file, $M(C)$, 
that is the set of all possible relations between the lines in the file.
A relation is described by user provided templates.
A template is a function taking some number of lines and determining 
a relation on the keywords of 
the lines ($Line^{n} \rightarrow Rel_{k1,..,kn}$).
For example, we may derive the relation \texttt{extension mysql.so} comes before \texttt{extension recode.so} by using the ordering template.
ConfigC features the following default templates.

\begin{center}
\begin{tabular} {|c|c|c|}
 \hline
 Template & Input  & Relation \\
\hline
\hline
 ordering & (Line,Line) & Before $\vert$ After $\vert$ None \\
 \hline
 integer relation & (Line,Line)  & $< | == | >$  \\
\hline
 type & (Line,Line)  & String $\vert$ Int $\vert$ Filepath $\vert$ IP  \\
\hline
 missing entry & (Line,Line) & Required $\vert$ Not \\
\hline
\end{tabular}
\end{center}

It is assumed if a file is correct, all relations in that file are in the set of necessary relations for any other file to be correct ($Correct(C) \implies \forall r \in M(C), r \in Nec$).
In this way, the initial model is built by creating the strongest conditions for a correct file, called the \textit{specific boundary} in version space learning.
This model is then iteratively relaxed as more examples are seen, a process called \textit{candidate elimination}.
Since we maintain the strongest condition for correctness, this approach will identify many correct files as incorrect, which we call a high false positive rate.
This is a problem when a user is then asked to manually review many files for errors, when the files are in fact correct.

\subsection{Learning From Temporal Properties}

%ConfigC can provide justifications, but has a high false positive rate.
%However, ConfigC only analyzes correct configuration files, and does not consider any ordering between these correct files.
We now present a new algorithm to decrease the false positive rate 
by learning on both correct and incorrect examples, 
as well as temporal structure of these examples.
This extension will build a logical formula representing the entire 
history of examples, and use an SMT solver to find a classification model.

Since a configuration file (\eg, TravisCI configuration file) is dependent
on the code it is trying to build, 
we must consider a more general sense of configuration file.
We will call this a program summary $P_t$, which is a representation 
of the repository which contains the information 
relevant to the learning process.
The subscript on $P_t$ is a timestamp tag based on 
the ordered git commit history.
In the case of TravisCI, this include the \verb|.travis.yml| file, 
as well as code features that may effect build status, 
such as programming language and a list of imported libraries.
The summary must be \textit{sufficiently detailed}, that is it must contain every piece of information that might lead to a build error.

%IMPORTANT, but no space
%However, a git history is not a limited to a single linear timeline.
%Git features the ability to \textit{branch}, which allows to simultaneous commit chains.
%To handle the start of a branch, add a superscript to indicate the branch, and restart the counter on a branch.
%To handle the merge of two branches $P_{t}^{x}$ and $P_{t'}^{y}$, step to $P_{t+1}^{x}$, where $x$ is the mainline branch.
%We then say that $P_{t'}^{y}$ has no successor commit $P_{t'+1}^{y}$.

From this summary we can then build a model $M(P_t)$, as in \app, 
which is the full set of possible relations derivable 
from the program summary.
Again, the user must provide templates for the learning process.

We will denote the build status returned from TravisCI when run on $P_t$ with $S(P_t)$.
Any files with a $Pass$ build status are correct, and any files with an $Err$ build status are incorrect.
%In this application, we consider all non-erroring build status to be passing, denoted $Pass$ and otherwise $Err$.
For brevity, we denote sequences of build statuses with the following notation:
\begin{align*}
  S(P_t)=Pass \land S(P_{t+1})=Err \implies S(P_{t,t+1}) = PE
\end{align*}

We now consider both incorrect and correct 
and so must introduce the \textit{general boundary}.
The general boundary is the dual of the specific boundary, and is the most relaxed requirement for a positive classification.
We denoted specific boundary as the set of necessary relations $Nec$, and now denote the general boundary as the set of breaking relations $Br$.
With this notation, we can formally express the requirement that the program summary is sufficiently detailed.
\begin{align}
  \forall S(P_t)=Err, \exists r \in M(P_t), r \in Br \label{eq:E1}
\end{align}

From the above we know that if a build is erroring, then there must exist at least one error.
%By pushing the negation into the formula,
We can also know that if a build is passing, then there must not exist any errors.
That is, the model of a passing commit must not contain any rules which are breaking.
Note we are not, however, guaranteed that any rules from a passing commit are necessary.
\begin{align}
  S(P_t) = Err \implies \exists r \in  M (P_t), r \in Br \label{eq:E}\\
  S(P_t) = Pass \implies \forall r \in  M (P_t), r \notin Br \label{eq:P}
\end{align}

%While Eq. \ref{eq:E} and \ref{eq:P} might build a basic model, they will do not capture all of the available knowledge.
%The key insight is that 
Additionally, when we commit a break ($PE$), we can localize the error to one of the relations that changed.
Either we removed something that was necessary, or added something that was breaking.
Note that this is an inclusive disjunction, since a erroring commit can break multiple things at once.
Expressed formally, where $\setminus$ is the set difference, that is:
\begin{align}
  S(P_{t,t+1}) &= PE \implies \nonumber \\
  \exists& r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \nonumber \\
  \lor \ \exists& r \in (M(P_{t+1}) \setminus M(P_{t})), r \in Br \label{eq:PE}
\end{align}

We then can combine Eq \ref{eq:E}, \ref{eq:P}, and \ref{eq:PE} with
conjunctions and ask a SMT solver for a model satisfying the formula.
The resulting model will be the sets $Nec$, and $Br$, which can be used to check new configuration files.
Since we used a similar model to \app, we will still be able to provide justifications for the classification results.

### 2016-11-10 Ennan-Proposal/travis.tex
no pdf of main

@@
 guaranteed to be correct.
-Such an extension employs a new algorithm, named version space learning,
+Such an extension employs an existsing technique from the machine learning community, named version space learning,
 to significantly decrease the false positive rate while maintaining 

### 2016-11-10 Ennan-Proposal/motivation.tex
stuff

@@
 specification for configuration files. It is unrealistic to expect the 
-users to write a specifications for configuration files on their own. 
+users to write an entire specifications for configuration files on their own. 
 This process can easily lead to incomplete or even contradictory 
@@
 a large sample of 
-configuration files. We start a learning process that takes as input this 
+configuration files. A learning process will take as input this 
 sample. The process will be language-agnostic and should work for any kind 
@@
 from a single value. 
-For example, an entry {\tt something = 1} assigns 
-\ruzica{here, something is 1 which is int, but it is actually a Boolean}
-\ruzica{more story here}
+An entry {\tt general\_log = 1} assigns an integer to the 
+variable {\tt general\_log}. However, 1 here is a Boolean variable,
+which denotes that there will be a general log file.
+Another example, which shows how this can easily lead to an error, is 
+that sometimes a configuration files 
+contain the following entry {\tt general\_log = /var/log/mysql/mysql.log}. This will cause    
+\ruzica{what will actually happen in this case}
 Some existing type inference 

### 2016-11-10 Ennan-Proposal/arch.tex

--- 2016-05-10 OSDI/arch.tex
@@
 \section{The \app Framework Overview}
-
-\begin{figure*}[tbp] \centering
-\includegraphics[width=0.88\textwidth]{figs/overview}
-\caption{\app's workflow. The green components represent configuration 
-  files, including both sample configuration datasets and users' input
-  configuration files to verify. 
-  The purple components are the modules of \app.
-  Because template DB is not necessarily used, we use dashed
-  arrow between it and the learner.
-  Red boxes are sub-modules within the checker.
-  The yellow components are results generated by \app's modules.}
-\label{fig-overview}
-\end{figure*}
 
@@
 
-\para{Initial phase.}
+\paragraph{Initial phase.}
 We start with the assumption 
@@
 
-\para{Translator.}
+\paragraph{Translator.}
 The translator module first parses the input sample 
@@
 
-\para{Learning.}
+\begin{figure*}[tbp] \centering
+\includegraphics[width=0.95\textwidth]{figs/overview}
+\caption{\app's workflow. The green components represent configuration 
+  files, including both sample configuration datasets and users' input
+  configuration files to verify. 
+  The purple components are the modules of \app.
+  Because template DB is not necessarily used, we use dashed
+  arrow between it and the learner.
+  Red boxes are sub-modules within the checker.
+  The yellow components are results generated by \app's modules.}
+\label{fig-overview}
+\end{figure*}
+
+\paragraph{Learning.}
 The input of the learner is a set of files that have been translated
@@
 
-Although the learner does necessarily rely on templates,
+Although the learner does not necessarily rely on templates,
 \app still offers a database containing many templates,
@@
 
-\para{Checking.}
+\paragraph{Checking.}
 The checker is used to detect rule violations in the configuration

### 2016-11-10 Ennan-Proposal/prelim.tex

\section{Our Previous Work: ConfigC}
\label{sec:prelim}

We have proposed and developed a preliminary system, named
ConfigC~\cite{santolucitoCAV}, which is (to the best of
our knowledge) the first systematic effort capable of automatically
verifying configuration files before the configuration files
are deployed and installed.
In particular, ConfigC is a framework that first automatically
analyzes datasets of correct configuration files, 
and then derives rules for building a language model 
from the give datasets.
Finally, the resulting language model could be used to verify 
new configuration files (called target configuration files) and 
detect errors in these target configuration files.
The configuration errors ConfigC can deal with cover:
entry missing errors, ordering errors, type errors and
value correlation.
To our knowledge, there is no existing effort that is able to detect
the above errors, because they are very tricky to identify in
practice.

ConfigC can detect the above errors by overcoming 
main technical challenges against automatic configuration verification.
First, because writing specifications for configuration verification
is difficult -- especially for specifying the above
tricky configuration errors, \eg, missing entry and ordering errors,
ConfigC employs a set of machine learning algorithms to
automate the specification writing. Machine learning based approach
employed by ConfigC enables the process of specification writing to become
automatic. As long as a set of configuration files are provided,
ConfigC can automatically generate a set of rules that could be used
as specifications.
Second, because existing configuration files do not have any language
structures and grammar, it is difficult to verify configuration files.
ConfigC proposes a new language model and transforms target configuration
files into the proposed language model. In other words, ConfigC uses
the language model as a uniform representation and parses the 
configuration files to verify into such a representation.
With the uniform representation and specifications in hand,
ConfigC is able to verify whether the given configuration files
meet the specification.

\paragraph{Evaluations on ConfigC.}
We implemented a prototype system by following 
our ConfigC design~\cite{santolucitoCAV}.
In order to demonstrate the capability of ConfigC,
we evaluated the ConfigC prototype based on real-world
MySQL configuration files~\cite{configdataset} 
containing tricky misconfiguration errors,
such as entry missing errors, ordering errors, and
value correlation errors.
We extracted 20 MySQL configuration files to detect, 
and grouped them into four categories according to their
error types: missing entry, type error, ordering error
and value correlation.
Table~\ref{table:res} shows the evaluation results we use
ConfigC to detect configuration errors in these 20 real-world
configuration files.
As shown in Table~\ref{table:res},
ConfigC is able to successfully report the misconfiguration problems.

\begin{table}[h]
\centering
\caption{Evaluation results on misconfiguration detection of ConfigC}
\label{table:res}
\begin{tabular}{|l|l|l|}
\hline
Error Type       & Passing Tests & False Positives  \\ 
\hline
\hline
Missing Entry      & 5/5           & 1, 0, 0, 0, 4        \\ \hline
Type Error         & 5/5           & 0, 0, 0, 0, 0          \\ \hline
Ordering Error     & 5/5           & 0, 2, 1, 0, 6       \\ \hline
Value Correlation  & 4/5           & 0, 0, 0, 1, 0        \\ 
\hline
\end{tabular}
\end{table}

\paragraph{Limitations.}
ConfigC still has the following limitations.

\begin{enumerate}

\item ConfigC requires the datasets of configuration files for training 
  have to be correct, which is hard to achieve in practice, since 
  it is difficult for administrators or users to offer a
  set of 100\% correct configuration files for training.

\item The language model of ConfigC is still a starting point. It
  is hard to formulate a uniform representation for diverse
  configuration files.\ennan{we still need to put one more sentence
  here to distinguish why our current language model is better
  than ConfigC's language model}

\item ConfigC can only offer coarse-grained value correlation errors,
  \eg, $\texttt{max\_connections} > \texttt{mysql.max\_persistent}$.
  In practice, many software outages were caused by more tricky, called
  fine-grained value correlation~\cite{correlation}. For example, 
  in a MySQL configuration file, $\texttt{key\_buffer\_size}$ should be 
  higher than $\texttt{max\_connections} \times 
  \texttt{sort\_buffer\_size}$~\cite{correlation};
  otherwise, the MySQL load will be very high.

\item ConfigC cannot check singular value anomalies. For example,
  a parameter relating to memory in MySQL configuration files is
  setted too large, exhausting the RAM and causing extreme slowness
  or even a crash. Such an anomalous value does not violate any
  constraints (\eg, type error and value ordering error), but 
  it makes system behave wrongly.

\end{enumerate}

This proposal aims to address the above limitations.

### 2016-11-10 Ennan-Proposal/proposal.tex

--- 2016-05-01 OSDI/main.tex
@@
-\documentclass[letterpaper,twocolumn,10pt]{article}
+\documentclass[11pt]{article}
+\usepackage[margin=1in,includefoot]{geometry}
 
-\usepackage{times}            % standard fixed width font
-\usepackage{usenix}
+\usepackage{color}
+\usepackage{tikz}
+\usepackage{mathtools}
+\usepackage{mathpartir}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{url}
+%\usepackage{bnf}
+\usepackage{local}
+\usepackage{xspace}
+\usepackage{graphicx}
+\graphicspath{ {images/} }
+\usepackage{fancyvrb}
+\usepackage[margin=1in]{geometry}
 
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{xspace}
-\usepackage{footnote}
-\usepackage{cite}
-\usepackage{amsfonts}
-\usepackage{subfig}
-%\usepackage{natbib}
+\usepackage{listings}
 \usepackage{balance}
-\usepackage{hhline}
-%\usepackage{multirow}
-\usepackage{setspace} 
-\usepackage{epsfig}
-\usepackage[hyphens]{url}
-\usepackage[colorlinks,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
-\usepackage[hyphenbreaks]{breakurl}
-\usepackage{booktabs}
-%\usepackage[compact]{titlesec}
-\usepackage{xcolor}
-%\usepackage[algoruled,vlined,ruled,linesnumbered]{algorithm2e}
-\usepackage{lipsum}
-%\usepackage{courier}
-\usepackage{listings}
+
 \lstset{
-  language=C,
-	basicstyle=\footnotesize\ttfamily,breaklines=true
+  basicstyle=\footnotesize\ttfamily,
+  breaklines=true,
+  frame=none,
+  language=haskell,
+  %identifierstyle=\color{identifierColor},
+  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
+  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
+  %captionpos=b,                    % sets the caption-position to bottom
+  %commentstyle=\color{mygreen},    % comment style
+  %frame=single,	                   % adds a frame around the code
+  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
+  keywordstyle=\color{blue},       % keyword style
+  otherkeywords={*,let, Server, Replication, FaultGraph, rankRCG, print, fialProb, goal, ...},           % if you want to add more keywords to the set
+  numbers=none,                    % where to put the line-numbers; possible values are (none, left, right)
+  numbersep=5pt,                   % how far the line-numbers are from the code
+  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
+  showtabs=false,                  % show tabs within strings adding particular underscores
+  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
+  %title=\lstname                  % show the filename of files included with \lstinputlisting; also try caption instead of title
+  mathescape=true,
+  tabsize=3,
+  literate=*{->}{{\textcolor{blue}{$\to$}}}{1}
+           {<-}{{\textcolor{blue}{$\leftarrow$}}}{1}
 }
 
-%\usepackage[T1]{fontenc}
-%\usepackage[scaled=0.78]{DejaVuSansMono}
+\begin{document}
+\input{macros}
 
-\clubpenalty=10000      % penalty for creating a club line at end of line.
-\widowpenalty=10000     % penalty for creating a widow line at top of page.
+%\input{overview}
 
-% Select one or other if want to see comments.
-% \com is sometimes displayed during draft.
-\long\def\com#1{}
-%\long\def\com#1{{\bf \sc comment: }{\small [#1]}{\bf \sc\ endcomment}\newline}
+\newpage
+\pagenumbering{arabic}
+\setcounter{page}{1}
 
-\long\def\ennan#1{{\color{blue}{\bf Ennan: }{\small [#1]}}}
-\long\def\ruzica#1{{\color{red}{\bf Ruzica: }{\small [#1]}}}
-%\long\def\xxx#1{}
+\input{motivation}
+\input{prelim}
+\input{arch}
+\input{language}
+\input{solutions}
+\input{travis}
+\input{related}
+\newpage
 
-% Use this macro to force page breaks where ugly widows/orphans occur;
-% be sure to recheck all uses after any significant change to the text!
-\def\widowpage{\pagebreak}
-
-% Choose abbreviated or long-version alternatives in paper
-%\long\def\abbr#1#2{#1}			% abbreviated version
-\long\def\abbr#1#2{#2}			% long version
-
-% Choose abbreviations or long names/titles in bibliography
-%\def\bibbrev#1#2{#1}			% short version
-%\def\bibbrev#1#2{#2}			% long version
-\def\bibbrev#1#2{\abbr{#1}{#2}}		% follow abbr macro
-
-% Abbreviated or full citation lists: \abcite{basic}{others}
-\newcommand{\abcite}[2]{\abbr{\cite{#1}}{\cite{#1,#2}}}
-
-% Conference abbreviations: \bibconf[Nth]{SOSP}{Symposium on ...}
-\newcommand{\bibconf}[3][]{#1 \bibbrev{#2}{#3 (#2)}}
-
-\newcommand{\ie}{{\em i.e.\xspace}}
-\newcommand{\eg}{{\em e.g.\xspace}}
-
-% system related terms
-\newcommand{\app}{ConfigC\xspace}
-
-% Fault graph terms
-
-\newcommand{\para}[1]{\smallskip\noindent {\bf #1}}
-
-\begin{document}
-
-\special{papersize=8.5in,11in}
-\setlength{\pdfpageheight}{\paperheight}
-\setlength{\pdfpagewidth}{\paperwidth}
-
-% Uncomment one of the following two, if you are not going for the 
-% traditional copyright transfer agreement.
-
-%\exclusivelicense                % ACM gets exclusive license to publish, 
-                                  % you retain copyright
-
-%\permissiontopublish             % ACM gets nonexclusive license to publish
-                                  % (paid open-access papers, 
-                                  % short abstracts)
-
-%\titlebanner{banner above paper title}        % These are ignored unless
-%\preprintfooter{short description of paper}   % 'preprint' option specified.
-
-\title{Probabilistic Automated Language Learning for Configuration Files}
-
-\author{~}
-
-\maketitle
-%\vspace{-50pt}
-
-\input{abs}
-
-\input{intro}
-\input{motiv}
-%\input{system}
-\input{arch}
-\input{trans}
-\input{learner}
-\input{check}
-\input{limit}
-\input{eval}
-\input{rel}
-\input{concl}
-
-%\newpage
-
+\setcounter{page}{1}
 \bibliographystyle{plain}

### 2016-11-10 Ennan-Proposal/remaining_stuff.tex

--- 2016-05-10 OSDI/intro.tex
@@
-\section{Introduction}
-\label{sec-intro}
-
-Configuration errors are one of the most important root causes of
-today's software system failures~\cite{xu15systems, yin11anempirical}.
-In their empirical study Yin {\em et al.}~\cite{yin11anempirical} report
-that about 31\% of system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code. 
-Misconfigurations, in practice, may result in various
-system-wide problems, such as security vulnerabilities, 
-application crashes, severe disruptions in software
-functionality, and incorrect program executions%
-~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.
-
-While many efforts have been proposed 
-to check, troubleshoot, diagnose, and repair configuration errors%
-~\cite{attariyan10automating,
-su07autobash, whitaker04configuration},
-those tools mainly try to understand {\emph{what}} caused the 
-error -- they are still not on a level of
-automatic verification tools used for regular program 
-verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
-detect errors without executing the code.
-Two main obstacles why we cannot simply apply the existing automatic 
-tools and techniques to verification of configuration files are: 1) a lack
-of a specification which would describe properties of configuration files, and 2) a program structure of configuration files -- they
-are mainly a sequence of entries assigning some value to system variables. The language in which configuration files are written does 
-not adhere to a specific grammar or syntax. In particular, the
-entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries and there
-is no explicit structure policy for the entries.
-Thus, automated verification of configuration 
-files would be highly
-desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
-
 To overcome these obstacles, researchers proposed approaches based on
@@
 ~\cite{wang04automatic, zhang14encore, yuan11context}
-that try to infer the rules and policies 
+that try to infer rules and policies about 
 how configuration files are constructed.
@@
 
-The downside of these approaches is that their learning approaches 
+The downside of these is that their learning approaches 
 are limited to simplistic configuration errors, 
@@
 heavily rely on template-based inference~\cite{zhang14encore}.
-%As we mentioned earlier, 
-%because configuration files are not written in a typed language 
-%with a fixed syntax,
-%type errors and syntax errors are relatively rare and easy to detect. 
+
 Many sophisticated configuration errors, 
 which are difficult to template in practice, 
-cannot be detected by this way. 
-As an illustration of such an error, consider the entry ordering errors, 
+cannot be detected in this way. 
+As an illustration of such an error, consider entry ordering errors, 
 which happens when some entries are inserted in a wrong order. 
@@
 %for configuration verification is non-trivial in practice.
-
-In this paper, we present \app, the first automatic verification framework
-for general software configurations. \app is based on a collection of powerful learning 
-algorithms, that do not necessarily depend on templates. The learning process takes as input a
- large sample of configuration files. The process is language-agnostic and it works for any type of configuration files, 
-but all of the files in the sample need to be of the same type (such as
-MySQL or HTTPD configuration files).
-From that sample,
-\app learns an abundant set of rules specifying various properties that hold on the given sample. The files in the sample might contain
-errors -- we are, therefore, using probabilistic learning to derive a set of accurate rules.
-
-For practical purposes we use a real-world dataset~\cite{configdataset}. 
-Every file in our dataset contains several errors, 
-but they are typically different errors and only appear 
-in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
-accurate set of rules. The rules, in general, specify which properties do variables need to satisfy. One can see this learning process as a
-way of deriving  
-a specification for configuration files.  Once there is a specification, we can do a formal verification. With these 
-rules we can efficiently check the correctness of the configuration files
-of interest and detect potential errors.
-
-The learning process has two phases. In the first phase, 
-\app analyzes the sample dataset and generates a 
-well-structured and probabilistically-typed 
-intermediate representation. 
-In the second phase, \app derives rules and constraints by analyzing
-the intermediate representations.  Every learned rule is annotated with a probability depicting in
-which percentage of the files the rule was seen as correct. We only accept those rules whose 
-correctness probability is above the given threshold.
-
-Finally, while the learned rules establish correlations between two or more variables, using \app one can also detect whether a
-single variable has an appropriate value assigned to it. We do that by measuring the values, that are typically assigned to that variable 
-and reporting if the current value deviates too much from the recorded values.
-
-Building such an automatic verification framework for
-configuration files, nevertheless, requires addressing several challenges. 
-%First, for variables of one type 
-%we learn different rules than for variables of different types. 
-%For example, for integer variables $X$ and $Y$, 
-%we can learn that $X \leq Y$, while 
-%for strings we might want to learn a substring relation. 
-First, we need to assign a type to every variable in a configuration file during the transformation phase.
-However,
-the type of a variable cannot always be fully determined 
-from a single value. 
-For example, an entry {\tt temp\_dir = 300} assigns to variable {\tt temp\_dir} either a directory named ``300'' or sets the size of that directory to 300 (an integer).
-Some of existing type inference 
-work would report this is an error, because {\tt temp\_dir} should be assigned
-an integer~\cite{zhang14encore}. We address this problem by introducing the concept of
-{\emph{probabilistic types}}.
-Rather than assigning only one variable to a single type, 
-we assign several types with their probability distributions. 
-The entry in the above example might be assigned 
-the following probabilistic type
-{\tt \{temp\_dir, 300, [(File, 60\%), (Int, 40\%)]\}}.
-Using the probabilistic types model,
-we can generate a more accurate language model,
-thus significantly improving our verification capabilities.
-
-Second, when learning rules we use very general templates to 
-infer them. The user does not need to provide any templates -- they are internally associated to the types.
-Nevertheless, in addition to those general templates, we still need specific algorithms to learn
-rules that cannot be easily templated.
-
-From a practical perspective, 
-\app introduces no additional burden 
-to the users: they can simply use \app to check for errors in their
-configuration files. However, they can also easily extend the framework
-themselves. The system is designed to be highly modular. If there is a
-class of rules that \app is not currently learning, the user can develop
-her own templates and learners for that class. The new learner can be
-added to \app and this way it can check an additional new set of
-errors.
-
-Our \app prototype still has many limitations:
-for example, we cannot handle configuration errors that can be 
-triggered during system execution time.
-Nevertheless, we believe \app may suggest a practical path
-toward automatic and modular language-based configuration verification.
-To summarize, this tool paper makes the following contributions:
-
-\com{
-Finally, from a systems perspective this is the first approach that {\emph{proactively}} checks 
- the correctness of configuration files. All previous work
-~\cite{xu15systems,zhang14encore,yuan11context, wang04automatic,attariyan10automating,
-su07autobash,whitaker04configuration} tries to identify the problem after the
-failure occurred.
-Our approach isolates potential errors before the system failure occurs, e.g.
-before the installation.
-We can also see \app as a tool that can run in conjunction with existing tools.
-Pre-analyzed configuration files are already free from language-based errors, and this way the workloads of post-failure forensics at the runtime
-is significantly reduced, thus making these tools truly practical.
-}
-
-\begin{enumerate}
-
-\item We propose the first automatic configuration verification
-framework, \app, that can learn a language model from a sample
-dataset, and then use this language model to verify 
-configuration files of interest.
-
-\item \app proposes probabilistic types to assign a confidence 
-distribution over a set of types to each entry, 
-while generating the intermediate representation.
-
-\item \app employs a collection of machine learning algorithms to 
-enable powerful rule and constraint inference.
-
-\item \app is capable of detecting various tricky errors that cannot
-be detected by previous efforts,
-including entry ordering errors, fine-grained value correlation errors, 
-missing entry errors, and environment-related errors.
-
-\item We implement a \app prototype and evaluate it by
-conducting comprehensive experiments on real-world dataset.
-
-\end{enumerate}

### 2016-11-10 Ennan-Proposal/solutions.tex

\section{Learning More Accurate Specification}
\label{sec:learnin}

\ruzica{this is actually an OSDI summary and learning from incorrect files}

### 2016-11-10 Travis/secs/completeConfigC.tex

This algorithm is complete but unsound.
We first define the set of incorrect files based on ground truth $Inc_{gt}$, and the set of files which are predicted by the model to be incorrect, $Inc_{prd}$.
To define $Inc_{gt}$, we will introduce the set of relations that are necessary and breaking based on ground truth, $Nec_{gt}$ and $Br_{gt}$ respectivly.
The definition of $Inc_{prd}$ follows from the description of the algorithm.

\begin{align}
Inc_{gt} = \{&\forall C, \exists r \in Nec_{gt}, r \notin M(C)\\ \nonumber
 &\lor \exists r \in Br_{gt}, r \in M(C)\} \\
Inc_{prd} = \{&\forall C, \exists r \in Nec, r \notin M(C)\}
\end{align}

Our definition of sound and complete are as follows:

\begin{align}
&\forall C \in Inc_{gt}, C \in Inc_{prd} \text{  Complete} \\
&\not \exists C \in Inc_{prd}, C \notin Inc_{gt} \text{  Sound}
\end{align}

To show completness we show that the $Inc_{gt} \subseteq Inc_{prd}$.

\begin{align*}
Nec \subseteq Nec_{gt}
%Nec \disjoint Br_{gt}
%\forall C \in {Incorrect(C)}, C \in system(Inc,C)   Nec_{True}, r \in Nec_{Learned} - (Nec_{Learned} \contains Nec_{True})
%\not \exists C \in SysInc(C), C \notin {Incorrect(C)} 
%\Nec_{Learned} \contains Nec_{Observable}
%\forall r \in Br, r \notin Incorrect(C) \implies \exists r \in Nec_{True}, r \notin M(C)
%Incorrect(C) \implies \exists r \in Nec, r \notin M(C)
\end{align*}

%The algorithm is complete if, for any file which breaks a relation for which we have a template (a misconfiguration) and have seen an correct example, the system will mark that file as incorrect.
%Since the model always maintins the strongest conditions for correctness for any file, the algorithm is clearly complete.
%Completness cooresponds to no false negatives.
%This algorithm is however unsound, some correct file may be marked as incorrect, a false postive.
%We have a high false postive rate since the model is an overappoximation of the true model.

### 2016-11-10 Travis/secs/implementation.tex

@@
 This is a slightly more involved task that requires writing some non-trivial Haskell code - but it really isn't that bad.
-
-\subsection{Limitations}
-In addition to the completness of the program summary $P_t$, and the completness of the relations that can be learned $M(P_t)$, there are challenges in a practical implementation.
-The most difficult is that the configuration language also have multiple versions. 
-We will need to fix a version of TravisCI itself, and ensure we only learn on that version.
-Additionally, this algorithm makes the assumption that TravisCI is bug free.

### 2016-11-10 Ennan-Proposal/travis.tex
autocommit

--- 2016-11-10 Ennan-Proposal/travis.tex
@@
 incorrect, thus making \app more general and practical.
-Nevertheless, some cases in practice 
-may allow us to assume some of configuration 
-files in the training sets are guaranteed to be correct.
-For example, TravisCI is a famous system connected 
-to Github, and it allows programmers to automatically run 
-their test suites on every code commit. 
-Thus, a TravisCI user needs to add a configuration file 
-to the repository that 
-enables TravisCI and specifies build conditions, 
-such as which dependencies are required, 
-and a set of benchmarks to test. This ensures 
-the tool to be automatically built correctly on a fresh machine.
-Such a configuration file management scheme, in fact, guarantees 
-the configuration file versions in the commit history to be 
-correct -- otherwise, TravisCI should not work correctly in the past.
-\ennan{Need one or two sentences to describe TravisCI misconfiguration
-problem is important.}
+We show in Sec~\ref{sec:correctExten} how adding set of known correct files to 
+the learning process can improve the false positive rate.
+In fact, we occasionally have a training set labelled as both correct and incorrect files.
+Furthermore, such a training set may have more embedded information that can be leveraged, such as temporal structure.
+Temporal structure in training sets is available when code has a change history, such as in version control.
 
-Driven by the above motivating example, 
-we propose an extension to \app that
-learns a given training set with pre-knowledge that 
-this training set contains some configuration files 
-guaranteed to be correct.
-Such an extension employs a new algorithm, named version space learning,
-to significantly decrease the false positive rate while maintaining 
-the detection capability of \app.
+One such example of such a training set of configuration files is TravisCI~\cite{travis}.
+TravisCI, a popular integration and build testing service connected to Github.
+TravisCI allows programmers to automatically run their test suite on a fresh virtual machine every time they commit their code.
+A TravisCI user must add a configuration file to the repository that specifies build conditions, 
+such as which dependencies are required, and a set of benchmarks to test. 
+The results of these tests (indicating either passing, failing, or misconfiguration) 
+are saved by TravisCI on a publicly available database~\cite{API}.
 
-\subsection{Version Space For Verification}
+TravisCI misconfigurations are important to fix because of the developer time cost. 
+In addition to being time consuming to fix, a misconfiguration can cause a test suite to run up to 20 mins, only to report a misconfiguration~\cite{API}.
+The developer will need to wait to get such a report back to begin even identifying the error.
+
+Driven by the above motivating example, we propose an extension to \app that
+learns over a training set with both correct and incorrect examples, as well as a temporal structure.
+Such an extension employs an existing technique from the machine learning community, called version space learning,
+to significantly decrease the false positive rate while maintaining the detection capability of \app.
+
+\subsection{Version Space Learning with Temporal Properties}
 
 Version space learning builds a logical constraint model for binary
-classification, which we use to test a configuration file for membership
-in the set of all correct files~\cite{mitchell82}.
+classification~\cite{mitchell82}, which we use to test a configuration file for membership
+in the set of all correct files~.
 Traditional version space learning builds a model that tests membership
 using a series of disjunctions from a set of predefined hypotheses.
-In the extended \app, rather than describing a correct file by allowable 
-traits, we describe the required traits. 
-This way, our system can not only flag misconfigurations, 
-but also give the points of failure for non-membership.
-We now show in detail how this process works.
-
-Our definition of a configuration file, $C$, is a file that can be
-transformed to an ordered list of $(keyword, value)$ pairs, called
-$Line$s. \app builds a model for a single file, $M(C)$, 
-that is the set of all possible relations between the lines in the file.
-A relation is described by user provided templates.
-A template is a function taking some number of lines and determining 
-a relation on the keywords of 
-the lines ($Line^{n} \rightarrow Rel_{k1,..,kn}$).
-For example, we may derive the relation \texttt{extension mysql.so} comes before \texttt{extension recode.so} by using the ordering template.
-ConfigC features the following default templates.
-
-\begin{center}
-\begin{tabular} {|c|c|c|}
- \hline
- Template & Input  & Relation \\
-\hline
-\hline
- ordering & (Line,Line) & Before $\vert$ After $\vert$ None \\
- \hline
- integer relation & (Line,Line)  & $< | == | >$  \\
-\hline
- type & (Line,Line)  & String $\vert$ Int $\vert$ Filepath $\vert$ IP  \\
-\hline
- missing entry & (Line,Line) & Required $\vert$ Not \\
-\hline
-\end{tabular}
-\end{center}
-
-It is assumed if a file is correct, all relations in that file are in the set of necessary relations for any other file to be correct ($Correct(C) \implies \forall r \in M(C), r \in Nec$).
-In this way, the initial model is built by creating the strongest conditions for a correct file, called the \textit{specific boundary} in version space learning.
-This model is then iteratively relaxed as more examples are seen, a process called \textit{candidate elimination}.
-Since we maintain the strongest condition for correctness, this approach will identify many correct files as incorrect, which we call a high false positive rate.
-This is a problem when a user is then asked to manually review many files for errors, when the files are in fact correct.
-
-\subsection{Learning From Temporal Properties}
-
-%ConfigC can provide justifications, but has a high false positive rate.
-%However, ConfigC only analyzes correct configuration files, and does not consider any ordering between these correct files.
-We now present a new algorithm to decrease the false positive rate 
-by learning on both correct and incorrect examples, 
-as well as temporal structure of these examples.
+Here we will instead use a conjuctions to convey that a configuration file must meet the learned criteria.
 This extension will build a logical formula representing the entire 
@@
 
-Since a configuration file (\eg, TravisCI configuration file) is dependent
-on the code it is trying to build, 
+Since a TravisCI configuration file is dependent
+on the code and system it is trying to build, 
 we must consider a more general sense of configuration file.
@@
 conjunctions and ask a SMT solver for a model satisfying the formula.
-The resulting model will be the sets $Nec$, and $Br$, which can be used to check new configuration files.
+The resulting model will be the sets of necessary rules ($Nec$), and the set of breaking rules ($Br$), which can be used to check new configuration files.
 Since we used a similar model to \app, we will still be able to provide justifications for the classification results.

### 2016-11-10 Ennan-Proposal/solutions.tex
config: learn

@@
-\section{Learning More Accurate Specification}
-\label{sec:learnin}
+\section{Learner}
+\label{sec-learn}
 
-\ruzica{this is actually an OSDI summary and learning from incorrect files}
+The goal of the learner module is to derive rules and constraints from
+the intermediate representation generated by the translator.
+In general, the learner module has two components.
+The first component (Sec.~\ref{subsec-rules}) 
+learns rules for checking configuration errors like
+missing entry errors, ordering errors, 
+and fine-grained value correlation errors. 
+These errors tend to cause total system failures.
+%Once the configuration file has been validated against such rules, 
+%the user may choose to invoke a more sensitive constraint checker. 
+The second component (Sec.~\ref{subsec-constraints}) aims to derive 
+constraints on entries to check for suspicious (or anomalous) values 
+that may violate standard practice. These anomalies can cause partial 
+degradation of the system, 
+such as significant reduction in performance, or even 
+total failure~\cite{zhang14encore}.
+
+\subsection{Derivation of Probabilistic Rules}
+\label{subsec-rules}
+
+The first component is responsible for learning two categories of rules: 
+1) rules that are inferred using templates associated with types 
+and 2) rules which we call \emph{untyped specifications},
+such as ordering or missing entry constraint.
+%Both are rules that must hold over multiple parts of a configuration file.
+
+\para{A strawman solution.}
+We first present a strawman solution (employed by 
+our existing work ConfigC~\cite{santolucitoCAV}) that uses 
+a set of correct configuration files as a learning set, 
+from which it is possible to derive rules 
+that must hold with absolute certainty. 
+%However, as mentioned in Sec.~\ref{sec:prelim}, 
+%it is difficult to obtain a set of files 
+%that is both guaranteed to be without errors
+%and large enough to learn sufficiently many rules.
+%This usually requires manual verification of the learning set, 
+%which is prone to error.
+Under such an assumption, the strawman solution
+only considers a rule if it holds over exactly every file in 
+the learning set. This behavior can be formally described as follows:
+\begin{small}
+\begin{align*}
+C :=&\ \text{Correct Learning Set}\\
+LR :=&\ \text{Learned Rules} :: \{\textrm{Rule}\}\\
+RR :=&\ \text{Reported Rules} :: \{\textrm{Rule}\}\\ 
+C =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
+LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file)\} \\
+RR =&\ \{ r\ \mid r \in LR \ \land \neg\ holds(r,\textrm{user file}) \}\\
+\end{align*}
+\end{small}
+
+where, the $:: \{Rule\}$ indicates that $LR$ (\ie, the learned rule set) 
+and $RR$ (\ie, the reported rule set) are sets of rules.
+A rule is only committed to the learned rule set, $LR$, if 
+the rule holds on all files in the training set $C$, 
+as denoted by the $\forall$ quantifier. 
+A broken rule is reported to the user in the $RR$ rule set if the rule is in $LR$, 
+but does not hold on the input user file.
+
+In general, each rule can be viewed as a mapping from a tuple of 
+entry keys $(k_1, \ldots, k_n)$ in the intermediate representation of a 
+configuration file to a probability function, $P_{rel}$. 
+This can be represented by a rule
+$r := (k_1, \ldots, k_n) \rightarrow P_{rel}$.
+$P_{rel}$ is a probability function specific to the relation to assess.
+The problem with the strawman solution is that the probability functions are restricted to be 
+boolean, which is to say that the relation can either be unsatisfied or satisfied, either 0 or 1. 
+For instance, for the rule that the value of {\tt max\_connections} must 
+be higher than the value of {\tt mysql.max\_persistent}, 
+the rule is denoted by
+({\tt max\_connections}, {\tt mysql.max\_persistent}) $\to 1$, where 
+$B_{>}$ is set to 1. In our approach (see below), 
+we permit the probability functions to take on any value from 0 to 1.
+
+\para{Probabilistic approach.}
+In \app's learner module, we release the assumption in the above
+strawman solution, which means the rule learning mechanism is tolerant 
+enough to accept a dataset of possibly incorrect configuration files. 
+Rather than manually correcting each file, 
+we extend the previous formalism to run probabilistic learning
+on our intermediate representations (generated by the translator).
+
+\begin{algorithm}[t]
+\caption{Probabilistically Learn Rules: \textbf{learnRules()}}
+\label{alg:plearn}
+\begin{footnotesize}
+  \KwIn{$\theta$ is the list of possible types.}
+  \KwIn{$U$ is the list of possible untyped specifications.}
+  \KwIn{$C$ is a set containing intermediate representations
+     of configuration files}
+
+  Let $R = \{\}$ be {\em rule set}\;
+  Let $\Pi$ be {\em probabilities associated with rule set}\;
+  \For{each file $F$ in $C$}{
+      Initialize $opt$ flag\;
+      \For{each $z \in \theta \cup U$}{
+          $Q$ contains candidate entries to consider\;
+          $RM$ contains entries in remove set\;
+          \If{$z$ is a type}{
+              $opt = 1$\; 
+              $Q = filter(F,\tau)$\; /* {\em Q contains $F$ entries with
+$\tau$ in type list} */\\
+          }\ElseIf{$z$ is an untyped spec}{
+              $opt = 0$\;
+              $Q = F$\;
+          }
+          %\EndIf
+          \For{each entry $e$ in $Q$}{
+              \If{$g(e)$ is false}{
+                  continue to next entry\;
+              }\Else{
+                  $CR = \textrm{constructRules}(e, z, opt, Q \backslash
+RM)$\;
+                  $R = R  \cup CR$\;
+                  For each $r \in CR$, update $\Pi$\;
+              }
+              $RM = RM \cup e$\;
+          }
+        }
+  }
+  return $(\Pi,R)$\;
+\end{footnotesize}
+\end{algorithm}
+
+\com{
+\begin{algorithm}[t]
+\caption{Construct Rules: constructRules($e, z, opt, S$)}
+\label{alg:crules}
+\begin{footnotesize} 
+    \KwIn{entry $e$ from intermediate representation.}
+    \KwIn{type or untyped specification $z$}
+    \KwIn{option $opt$, set to 1 if template or 0 if untyped spec}
+    \KwIn{set of entries $S$}
+
+    $R = \{\}$\;
+    Set $j$ as an iteration variable\;
+    \If{opt = 1}{
+        run the following sequence \textbf{L} over 
+        all elements of $templates(z)$\;
+    }\ElseIf{opt = 0}{
+        $j = z$\;
+    }
+    Beginning of \textbf{L}: 
+     \State Let $n$ be the arity of $j$.
+      \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$.
+      \For{each $p \in P$}
+        \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
+         \For{$i = 1:n$}
+         \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $m = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
+         \State $r = \textrm{constructRule}(m)$
+         \If{$r$ is satisfied}
+                $R = R \cup r$
+         \EndIf
+        \EndFor
+     \EndFor
+     \State End of \textbf{L}. 
+     \State return $R$
+  \end{algorithmic}
+\end{footnotesize}
+\end{algorithm}
+}
+
+Our probabilistic approaches for learning missing entry, 
+ordering, and fine-grained value correlation rules stem 
+from existing work with building 
+non-probabilistic versions of these rule-learning algorithms. 
+For each of these rules, 
+we consider all possible permutations of keys that appear in every 
+file which are appropriately typed, and for our learning process, calculate the likelihood that each of 
+these permutations constitute a rule. 
+Rule patterns in the example set that appear frequently are accepted,
+so they can be used to evaluate new files.
+
+More formally, this approach can be defined as follows:
+
+\begin{small}
+\begin{flalign*}
+I\ \ :=&\ \text{Incorrect Learning Set}\\
+LP :=&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
+RP :=&\ \text{Reported Probabilistic Rules :: \{P\_Rule\}}\\
+I =&\  \text{\{Configuration Files in Intermediate Representation\}}\\
+(\Pi, LP) =&\ \text{learnRules}(I)\\
+RP =&\ \{ r\ \mid r \in LP\ \land \Pi(r)>p \land \neg holds(r, userfile) \}
+\end{flalign*}
+\end{small}
+
+Note that the formalism relies on Algorithm~\ref{alg:plearn}. The algorithm considers both typed templates and
+untyped specifications. As a similar iteration logic is used for both, an $opt$ flag distinguishes between the two situations.
+constructRule in Algorithm~\ref{alg:crules} refers to the creation of a rule from a tuple of entries, 
+$m = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
+The rule creation is formally represented as $m(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$. 
+In order to determine if the rule satisfied, the relation associated with $m(v(e_1), v(e_2), \ldots, v(e_i), \ldots, v(e_{n-1}))$ is evaluated for truth.
+The rule can be template-generated, for instance {\tt max\_connections} > {\tt mysql.max\_persistent}, or
+it can be untyped-specification-generated, for instance the ordering that {\tt recode.so} must come before 
+{\tt mysql.so}.
+
+The candidate entry set $Q$ in Algorithm~\ref{alg:plearn} 
+differs for the two cases.
+For typed templates, due to typing restrictions, 
+we must first filter and examine entries associated with the same type, in order to check that 
+the template is satisfied over appropriately typed argument entries. This manifests itself via $Q = filter(F,\tau)$
+in Algorithm~\ref{alg:plearn}. For
+untyped specifications, we do not need to adhere to this typing restriction, so we simply set $Q = F$.
+
+%probability set associated with the rules, $\Pi$, contains values
+%ranging from 0 to 1, which are then compared against an acceptance threshold for the final output.
+%\[
+%\{ P\_Rule = (a_j, a_k) | j \neq k \} \rightarrow \{ (R_1, R_2, ... , R_n) \}
+%\]
+
+%We can think of each of these $(a_j, a_k)$ as possibly having a different relationship, defined by the set $\{ R_i \}$, which cover the entire outcome space of possible relationships between the two values $(a_j, a_k)$.
+
+%For the entry missing rules, we define $R_1$ as the event that $a_j$ and
+%$a_k$ appear together, and $R_2$ to be the event that $a_j$ appears
+%without $a_k$, or by the transitive equivalent, $a_k$ appears without
+%$a_j$. For the ordering rules, we define $R_1$ as the event that
+%$a_j$ appears before $a_k$ and $R_2$ be the event that $a_k$ appears
+%before $a_j$. For the value correlation rules, we define $R_1$ as the
+%event that $a_j \leq a_k$, $R_2$ the event that $a_j = a_k$, and $R_3$
+%the case that $a_j \geq a_k$. Notice that the $R_i$ do not have to be
+%disjoint, but only have to union to the entire probability space.
+
+%By examining the learning set, we will derive a distribution of the set $\{R_i\}$ based on how many times we observe an occurrence of each relation.
+This distribution will then be used at checking time to determine if a user's configuration has broken a likely rule.
+
+A rule $r$ will be reported as broken if the probability the rule is
+correct, $\Pi(r)$, is greater than some user defined constant, $p$. This
+constant can be adjust to the user's preference. A small $p$ will
+increase the likelihood of finding an error, but also increase the
+number of false positives that are reported.
+
+\subsection{Learning Suspicious Constraints}
+\label{subsec-constraints}
+
+With a configuration file that has been verified against catastrophic
+failures (\eg, missing entry, type, and ordering errors), 
+the user may also want to examine more subtle issues.
+Anomalous values can cause tricky, but impactful, performance and memory
+issues that are hard to debug, as discussed in Example 4 of 
+$\S$\ref{sec-motiv}. 
+Consequently, anomalous values should be flagged and a warning returned
+to the user indicating the violation.
+
+We now describe the technique we use to detect anomalous values for 
+numerical attributes. Let $A$ be the set of attributes contained in the 
+configuration files in the sample dataset. 
+Let $A_n$ be the subset of attributes of $A$ which are numerically typed. 
+Then, for each attribute $a \in A_n$, we construct a vector $v_a$ of the 
+values corresponding to attribute $a$, seen over the entire sample dataset.
+For each $v_a$, we compute 
+an interval  $$[\hat{v_a} - 50*MAD(v_a), \hat{v_a} + 50*MAD(v_a)],$$ 
+where $\hat{v_a}$ represents the median over the values 
+in $v_a$ and $MAD(v_a$) refers to the 
+median absolute deviation. 
+This is a variant of a standard outlier detection test, namely the Hampel identifier.\footnote{Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation 
+for a normal distribution.} 
+In the checking phase, as long as the checker finds a value for a numerical 
+attribute in the checked file outside of this interval, 
+a warning would be printed to the user indicating the violating value, 
+the attribute, and the upper or lower Hampel threshold.
+
+The intuition behind this is that if the user has input a value 
+that falls outside of an interval containing values that are considered 
+``normal'' over the entire sample dataset, 
+that value will probably cause an error, in particular for performance. 
+We cannot know for sure if this value will cause an issue. 
+For instance, a user might have a machine with 
+particularly high-end hardware, 
+in which case a value beyond the upper Hampel threshold may be appropriate.

### 2016-11-10 Ennan-Proposal/solutions.tex
autocommit

@@
 
-\subsection{Derivation of Probabilistic Rules}
+\subsection{Derivation of ConfigC Rules}
 \label{subsec-rules}
@@
 
-\para{A strawman solution.}
-We first present a strawman solution (employed by 
-our existing work ConfigC~\cite{santolucitoCAV}) that uses 
-a set of correct configuration files as a learning set, 
-from which it is possible to derive rules 
-that must hold with absolute certainty. 
 %However, as mentioned in Sec.~\ref{sec:prelim}, 
@@
 %which is prone to error.
-Under such an assumption, the strawman solution
-only considers a rule if it holds over exactly every file in 
-the learning set. This behavior can be formally described as follows:
+This only considers a rule if it holds over exactly every file in 
+the learning set. This behavior can be formally described in Fig~\ref{fig:configC}.
+
+\begin{figure}[!h]
 \begin{small}
+\belowdisplayskip=-15pt
+\abovedisplayskip=-2pt
 \begin{align*}
 C :=&\ \text{Correct Learning Set}\\
+C =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
 LR :=&\ \text{Learned Rules} :: \{\textrm{Rule}\}\\
-RR :=&\ \text{Reported Rules} :: \{\textrm{Rule}\}\\ 
-C =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
-LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file)\} \\
-RR =&\ \{ r\ \mid r \in LR \ \land \neg\ holds(r,\textrm{user file}) \}\\
+LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file) \\
+&\qquad \ \exists file \in C,\ nontriviallyHolds(r,file)\} 
 \end{align*}
 \end{small}
+\caption{The definition of which rules should be learned by ConfigC}
+\label{fig:configC}
+\end{figure}
 
 where, the $:: \{Rule\}$ indicates that $LR$ (\ie, the learned rule set) 
-and $RR$ (\ie, the reported rule set) are sets of rules.
-A rule is only committed to the learned rule set, $LR$, if 
-the rule holds on all files in the training set $C$, 
-as denoted by the $\forall$ quantifier. 
-A broken rule is reported to the user in the $RR$ rule set if the rule is in $LR$, 
-but does not hold on the input user file.
+is a sets of rules.
+The predicate $holds$ indicates that the rule should always be true -
+  for instance {\tt max\_connections} $>$ {\tt max\_persistent}.
+The predicate $nontriviallyHolds$ indicates that the rule should be true in a meaningful way.
+For instance, a file may only contain the keyword {\tt max\_connections} - the previous rule then holds vacuously,
+ because we say {\tt max\_connections} is always greater than {\tt max\_persistent} if no value is provided for {\tt max\_persistent} in that file.
 
-In general, each rule can be viewed as a mapping from a tuple of 
-entry keys $(k_1, \ldots, k_n)$ in the intermediate representation of a 
-configuration file to a probability function, $P_{rel}$. 
-This can be represented by a rule
-$r := (k_1, \ldots, k_n) \rightarrow P_{rel}$.
-$P_{rel}$ is a probability function specific to the relation to assess.
-The problem with the strawman solution is that the probability functions are restricted to be 
-boolean, which is to say that the relation can either be unsatisfied or satisfied, either 0 or 1. 
-For instance, for the rule that the value of {\tt max\_connections} must 
-be higher than the value of {\tt mysql.max\_persistent}, 
-the rule is denoted by
-({\tt max\_connections}, {\tt mysql.max\_persistent}) $\to 1$, where 
-$B_{>}$ is set to 1. In our approach (see below), 
-we permit the probability functions to take on any value from 0 to 1.
-
-\para{Probabilistic approach.}
+\subsection{Derivation of ConfigV Rules}
 In \app's learner module, we release the assumption in the above
-strawman solution, which means the rule learning mechanism is tolerant 
+solution, which means the rule learning mechanism is tolerant 
 enough to accept a dataset of possibly incorrect configuration files. 
@@
 on our intermediate representations (generated by the translator). 
-
-\begin{algorithm}[t]
-\caption{Probabilistically Learn Rules: \textbf{learnRules()}}
-\label{alg:plearn}
-\begin{footnotesize}
-  \KwIn{$\theta$ is the list of possible types.}
-  \KwIn{$U$ is the list of possible untyped specifications.}
-  \KwIn{$C$ is a set containing intermediate representations
-     of configuration files}
-
-  Let $R = \{\}$ be {\em rule set}\;
-  Let $\Pi$ be {\em probabilities associated with rule set}\;
-  \For{each file $F$ in $C$}{
-      Initialize $opt$ flag\;
-      \For{each $z \in \theta \cup U$}{
-          $Q$ contains candidate entries to consider\;
-          $RM$ contains entries in remove set\;
-          \If{$z$ is a type}{
-              $opt = 1$\; 
-              $Q = filter(F,\tau)$\; /* {\em Q contains $F$ entries with
-$\tau$ in type list} */\\
-          }\ElseIf{$z$ is an untyped spec}{
-              $opt = 0$\;
-              $Q = F$\;
-          }
-          %\EndIf
-          \For{each entry $e$ in $Q$}{
-              \If{$g(e)$ is false}{
-                  continue to next entry\;
-              }\Else{
-                  $CR = \textrm{constructRules}(e, z, opt, Q \backslash
-RM)$\;
-                  $R = R  \cup CR$\;
-                  For each $r \in CR$, update $\Pi$\;
-              }
-              $RM = RM \cup e$\;
-          }
-        }
-  }
-  return $(\Pi,R)$\;
-\end{footnotesize}
-\end{algorithm}
-
-\com{
-\begin{algorithm}[t]
-\caption{Construct Rules: constructRules($e, z, opt, S$)}
-\label{alg:crules}
-\begin{footnotesize} 
-    \KwIn{entry $e$ from intermediate representation.}
-    \KwIn{type or untyped specification $z$}
-    \KwIn{option $opt$, set to 1 if template or 0 if untyped spec}
-    \KwIn{set of entries $S$}
-
-    $R = \{\}$\;
-    Set $j$ as an iteration variable\;
-    \If{opt = 1}{
-        run the following sequence \textbf{L} over 
-        all elements of $templates(z)$\;
-    }\ElseIf{opt = 0}{
-        $j = z$\;
-    }
-    Beginning of \textbf{L}: 
-     \State Let $n$ be the arity of $j$.
-      \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$.
-      \For{each $p \in P$}
-        \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
-         \For{$i = 1:n$}
-         \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $m = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
-         \State $r = \textrm{constructRule}(m)$
-         \If{$r$ is satisfied}
-                $R = R \cup r$
-         \EndIf
-        \EndFor
-     \EndFor
-     \State End of \textbf{L}. 
-     \State return $R$
-  \end{algorithmic}
-\end{footnotesize}
-\end{algorithm}
-}
-
 Our probabilistic approaches for learning missing entry, 
@@
 
-More formally, this approach can be defined as follows:
+\begin{figure}[!h]
+\begin{small}
+\belowdisplayskip=-15pt
+\abovedisplayskip=-2pt
+\begin{align*}
+U\ :=&\ \text{Unlabeled Learning Set}\\
+U =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
+LP :=&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
+LR =&\ \{ r\ \mid \Pi file \in C,\ holds(r,file)\ \land \\
+&\qquad  \ \Psi file \in C,\ nontriviallyHolds(r,file)\} 
+\end{align*}
+\end{small}
+\caption{The definition of which rules should be learned by ConfigV when learning over a set of possibly correct, and possibly incorrect files.}
+\label{fig:configV}
+\end{figure}
 
-\begin{small}
-\begin{flalign*}
-I\ \ :=&\ \text{Incorrect Learning Set}\\
-LP :=&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
-RP :=&\ \text{Reported Probabilistic Rules :: \{P\_Rule\}}\\
-I =&\  \text{\{Configuration Files in Intermediate Representation\}}\\
-(\Pi, LP) =&\ \text{learnRules}(I)\\
-RP =&\ \{ r\ \mid r \in LP\ \land \Pi(r)>p \land \neg holds(r, userfile) \}
-\end{flalign*}
-\end{small}
+We use $\Pi$ and $\Psi$ in Fig~\ref{fig:configV} to indicate that the rule holds for some critical portion of the files.
+The inuition behind these quantifiers are that we want to consider rules which are true in majority of cases ($\Pi$), 
+and for which we have at least some examples for which that rule is nontrivially true ($\Psi$).
+The exact definition of $\Pi$ and $\Psi$ is a research question still to be solved.
+What exactly is the cutoff value that will yield the best results in learning.
+We plan to try multiple strategies to find these values.
+One approach may be to use machine learning for program optimization, with a tool like OpenTuner~\cite{ansel:pact:2014}.
+It is also possible that this value differs depending on the quality of the learning set and/or the particular type of rule being learned.
 
+\iffalse
 Note that the formalism relies on Algorithm~\ref{alg:plearn}. The algorithm considers both typed templates and
@@
 number of false positives that are reported.
+\fi
 

### 2016-11-11 Ennan-Proposal/motivation.tex
stuff

@@
 from a single value. 
-An entry {\tt general\_log = 1} assigns an integer to the 
+An entry {\tt general\_log = 1} in a MySQL configuration file assigns an integer to the 
 variable {\tt general\_log}. However, 1 here is a Boolean variable,
 which denotes that there will be a general log file.
-Another example, which shows how this can easily lead to an error, is 
-that sometimes a configuration files 
-contain the following entry {\tt general\_log = /var/log/mysql/mysql.log}. This will cause    
-\ruzica{what will actually happen in this case}
-Some existing type inference 
-work would report this is an error, because {\tt temp\_dir} should be assigned
-an integer~\cite{zhang14encore}. We address this problem by introducing the concept of
-{\emph{probabilistic types}}.
-Rather than assigning only one variable to a single type, 
-we assign several types over a probability distribution. 
-Using probabilistic types,
-we aim to generate a more accurate language model,
-thus significantly improving our verification capabilities.
+Another example, which often appears in practice, shows how variable names and 
+their ``types'' can easily lead to an error. Consider the
+following entry {\tt general\_log = /var/log/mysql/mysql.log}. Although this statement 
+alone might look correct, this is actually a typing error and as a result MySQL log cannot be correctly written.
 
@@
 Nevertheless, in addition to those general templates, we still need specific algorithms to learn
-rules that cannot be easily templated.
+rules that cannot be easily templated (such as ordering rules).
 
-From a practical perspective, we do not want to introduces any additional burden 
-to the user: they can simply use \app to check for errors in their
-configuration files. However, they can also easily extend the framework
-themselves. The system is designed to be highly modular. If there is a
-class of rules that \app is not currently learning, the user can develop
-her own templates and learners for that class. The new learner can be
-added to \app and this way it can check an additional new set of
-errors.
-
-Our \app prototype still has many limitations:
-for example, we cannot handle configuration errors that can be 
-triggered during system execution time.
-Nevertheless, we believe \app may suggest a practical path
-toward automatic and modular language-based configuration verification.
-To summarize, this tool paper makes the following contributions:
-
-\begin{enumerate}
-
-\item We propose the first automatic configuration verification
-framework, \app, that can learn a language model from a sample
-dataset, and then use this language model to verify 
-configuration files of interest.
-
-\item \app proposes probabilistic types to assign a confidence 
-distribution over a set of types to each entry, 
-while generating the intermediate representation.
-
-\item \app employs a collection of machine learning algorithms to 
-enable powerful rule and constraint inference.
-
-\item \app is capable of detecting various tricky errors that cannot
-be detected by previous efforts,
-including entry ordering errors, fine-grained value correlation errors, 
-missing entry errors, and environment-related errors.
-
-\item We implement a \app prototype and evaluate it by
-conducting comprehensive experiments on real-world dataset.
-
-\end{enumerate}
+We will implement this verification framework and call it \app (for continuity reasons
+-- our preliminary tool was called ConfigC, cf. next section).

### 2016-11-11 Ennan-Proposal/prelim.tex
stuff

@@
 
-We have proposed and developed a preliminary system, named
-ConfigC~\cite{santolucitoCAV}, which is (to the best of
-our knowledge) the first systematic effort capable of automatically
-verifying configuration files before the configuration files
-are deployed and installed.
-In particular, ConfigC is a framework that first automatically
+Based on our own experience with misconfigurations,
+we have proposed and developed a simple tool for verification of 
+configuration files, named
+ConfigC~\cite{santolucitoCAV}. Motivated by promising preliminary
+results, which we obtained with ConfigC, we believe that automated 
+verification of configuration files, before they
+are deployed and installed, is possible and that it should be further studied.
+
+From ConfigC we drew the main inspiration for this proposal. In particular, 
+ConfigC is a framework that first automatically
 analyzes datasets of correct configuration files, 
 and then derives rules for building a language model 
-from the give datasets.
+from the given datasets.
 Finally, the resulting language model could be used to verify 

### 2016-11-11 Ennan-Proposal/prelim.tex
stuff

@@
 results, which we obtained with ConfigC, we believe that automated 
-verification of configuration files, before they
-are deployed and installed, is possible and that it should be further studied.
+verification of configuration files is possible and that it should be further studied.
 
-From ConfigC we drew the main inspiration for this proposal. In particular, 
-ConfigC is a framework that first automatically
+From ConfigC we drew the main inspiration for this proposal. We now briefly
+outline how does ConfigC work. It first automatically
 analyzes datasets of correct configuration files, 
@@
 from the given datasets.
-Finally, the resulting language model could be used to verify 
-new configuration files (called target configuration files) and 
-detect errors in these target configuration files.
-The configuration errors ConfigC can deal with cover:
+
+The algorithm can be summarized as follows: we identified several basic types, 
+such Boolean, Integer, File. With each of these files we associated a list 
+of templates. We then analyze {\emph {correct}} configuration files. When we 
+detect that a certain variable (or a pair of variable
+
+\begin{figure}
+	\centering
+\begin{minipage}{0.9\textwidth}
+\begin{parcolumns}{2}
+\colchunk{\begin{lstlisting}[language=C, frame=tb, xleftmargin=.01\textwidth]
+File 1:
+max_connections=300
+general_log=1
+...
+mysql.max_persistent=200
+\end{lstlisting}}
+
+\colchunk{\begin{lstlisting}[language=C, frame=tb, xleftmargin=.01\textwidth]
+File 2:
+max_connections=400
+general_log=0
+...
+mysql.max_persistent=200
+\end{lstlisting}}
+
+\colplacechunks
+\end{parcolumns}
+\end{minipage}
+	\caption{Fragments of two configuration files for configuring PHP on MySQL}
+\end{figure}
+
+The resulting language model, together with accompanying rules, 
+is then used to detect errors in new configuration files.
+ConfigC can detect the following errors in configuration files:
 entry missing errors, ordering errors, type errors and
-value correlation.
+simple value correlation. Running ConfigC on Example~1 from 
+Sec.~\ref{sec:intro-examples} returns the following output:
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
+ORDERING ERROR: Expected extension "recode.so" BEFORE 
+extension "mysql.so"
+\end{lstlisting} 
+ConfigC could not detect an error present in Example~2 since it can detect 
+only simple comparison-based relations.
+
 To our knowledge, there is no existing effort that is able to detect

### 2016-11-11 Ennan-Proposal/related.tex
config: f

@@
 
-Language support has been considered a promising way  
-to tackle configuration problems~\cite{xu15systems}.
-Nevertheless, a practical language-based misconfiguration
-detection approach still remains an open problem.
+Verification support to configuration files 
+has been considered a promising way  
+to tackle misconfiguration problems~\cite{xu15systems}.
+Nevertheless, a practical misconfiguration
+verification approach still remains an open problem.
 

### 2016-11-11 Ennan-Proposal/prelim.tex
stuff

@@
 From ConfigC we drew the main inspiration for this proposal. We now briefly
-outline how does ConfigC work. It first automatically
-analyzes datasets of correct configuration files, 
-and then derives rules for building a language model 
-from the given datasets.
+outline how does ConfigC work on two configuration files given in 
+Fig.~\ref{fig:twoFiles}. ConfigC first automatically
+analyzes a dataset of correct configuration files to derive
+ rules for describing a specification. Before that process even starts,
+we identified several basic types, 
+such Boolean, Integer, File. With each of these files we associated a list 
+of templates. We then analyze {\emph {correct}} configuration files. When analyzing
+a file, we first do type-checking, \ie we assign a type to every variable. 
+We next instantiate each template with the typed variables and we save the learned set 
+of rules. For instance, with integers we associate comparison templates, so after 
+analyzing File$_1$, the set of learned rules will contain:
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
+max_connections=300
+mysql.max_persistent=200
+max_connections > mysql.max_persistent
+\end{lstlisting}
+The set of learned rules is changing with every file that we analyze: contradicting 
+files are removed and new rules are added. In practice, this process is done 
+in parallel.
 
-The algorithm can be summarized as follows: we identified several basic types, 
-such Boolean, Integer, File. With each of these files we associated a list 
-of templates. We then analyze {\emph {correct}} configuration files. When we 
-detect that a certain variable (or a pair of variable
+After analyzing File$_2$ the rule \texttt{max\_connections = 300} is removed.
 
@@
 \colchunk{\begin{lstlisting}[language=C, frame=tb, xleftmargin=.01\textwidth]
-File 1:
+File_1:
 max_connections=300
@@
 \colchunk{\begin{lstlisting}[language=C, frame=tb, xleftmargin=.01\textwidth]
-File 2:
+File_2:
 max_connections=400
@@
 	\caption{Fragments of two configuration files for configuring PHP on MySQL}
+	\label{fig:twoFiles}
 \end{figure}
 
-The resulting language model, together with accompanying rules, 
-is then used to detect errors in new configuration files.
-ConfigC can detect the following errors in configuration files:
-entry missing errors, ordering errors, type errors and
-simple value correlation. Running ConfigC on Example~1 from 
+Once this preprocessing of training data is done, the resulting language model, 
+together with accompanying rules, 
+is used to detect errors in new configuration files given by the user.
+
+Additional to the described process we also developed algorithms for the 
+misconfigurations that cannot easily be templated. All together, ConfigC 
+can detect the following errors:
+missing entries, ordering errors, type errors and
+simple value correlations. Running ConfigC on Example~1 from 
 Sec.~\ref{sec:intro-examples} returns the following output:

### 2016-11-11 Ennan-Proposal/arch.tex
config: ss

@@
 \section{The \app Framework Overview}
+\label{sec:overview}
 
-We propose \app, an automatic verification framework for 
+We propose to build \app, an automatic verification framework for 
 software configuration files.
-In particular, \app can solve many sophisticated 
+In particular, \app is built upon ConfigC and aims at addressing
+all the limitations of ConfigC (mentioned in Sec.~\ref{sec:prelim}).
+\app is capable of detecting many sophisticated 
 configuration errors (\eg, ordering errors, missing entry errors,
-and fine-grained value correlation errors) that previous efforts cannot 
-detect. As depicted in Figure~\ref{fig-overview}, 
-a typical \app verification workflow has three steps:
+and fine-grained value correlation errors) that the
+state-of-art efforts cannot detect. 
+Figure~\ref{fig-overview} presents
+a typical \app verification workflow which contains three steps:
 translation, learning, and checking. In this section, we briefly
@@
 that we are given a number of (not necessarily correct) 
-configuration files, called {\em sample dataset}, 
+configuration files, called {\em training set} (or sample dataset), 
 belonging to the same system, such as MySQL or Apache. 
@@
 
-\paragraph{Translator.}
-The translator module first parses the input sample 
-dataset (containing both configuration files and system environment
+\paragraph{Translator (Sec.~\ref{sec:lang}).}
+The translator module first parses the input training 
+set (containing both configuration files and system environment
 information), and then transforms them into a more structured
@@
 
-\paragraph{Learning.}
+\paragraph{Learning (Sec.~\ref{sec-learn}).}
 The input of the learner is a set of files that have been translated

### 2016-11-11 Ennan-Proposal/prelim.tex
stuff

@@
 From ConfigC we drew the main inspiration for this proposal. We now briefly
-outline how does ConfigC work on two configuration files given in 
-Fig.~\ref{fig:twoFiles}. ConfigC first automatically
+outline how does ConfigC work. It first automatically
 analyzes a dataset of correct configuration files to derive
@@
 we identified several basic types, 
-such Boolean, Integer, File. With each of these files we associated a list 
-of templates. We then analyze {\emph {correct}} configuration files. When analyzing
-a file, we first do type-checking, \ie we assign a type to every variable. 
-We next instantiate each template with the typed variables and we save the learned set 
-of rules. For instance, with integers we associate comparison templates, so after 
-analyzing File$_1$, the set of learned rules will contain:
+such Boolean, Integer, File. With each of these files we associated a 
+list of templates. We then analyze the given training data set of 
+correct configuration files and derive rules describing variable 
+relations. We demonstrate how it works on two fragments of configuration 
+files given in Fig.~\ref{fig:twoFiles}.  When analyzing
+a file, we first do type-checking, \ie we assign a type to every variable. After that we instantiate each template with the typed variables and we save the learned set 
+of rules. For instance, with the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 
+analyzing File\_1, the set of learned rules will contain the following rules:
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]

### 2016-11-11 Ennan-Proposal/prelim.tex
stuff

@@
 we identified several basic types, 
-such Boolean, Integer, File. With each of these files we associated a 
+such Boolean, Integer, File. With each of these types we associated a 
 list of templates. We then analyze the given training data set of 
 correct configuration files and derive rules describing variable 
-relations. We demonstrate how it works on two fragments of configuration 
+relations. We illustrate how it is done on two fragments of configuration 
 files given in Fig.~\ref{fig:twoFiles}.  When analyzing

### 2016-11-11 Ennan-Proposal/motivation.tex
stuff

@@
 \item a program structure of configuration files -- they
-are mainly a sequence of entries assigning some value to system variables. 
+are mainly a sequence of entries assigning some value to system keywords. 
 \end{itemize}
@@
 specifying various properties that hold on the given sample. The rules, in general, 
-specify which properties variables in configuration files need to satisfy. One can see this learning process as 
+specify which properties keywords in configuration files need to satisfy. One can see this learning process as 
 a way of deriving  a specification for configuration files. With these  rules we can efficiently check 
@@
 Thus, we need to develop a suitable language model. We do that by 
-``guessing'' a type of variables and then deriving formulas that
-describe relationships between these variables. However, the
-type of a variable cannot always be fully determined 
+``guessing'' a type of keywords and then deriving formulas that
+describe relationships between these keywords. However, the
+type of a keyword cannot always be fully determined 
 from a single value. 
 An entry {\tt general\_log = 1} in a MySQL configuration file assigns an integer to the 
-variable {\tt general\_log}. However, 1 here is a Boolean variable,
+keyword {\tt general\_log}. However, 1 here is a Boolean variable,
 which denotes that there will be a general log file.
-Another example, which often appears in practice, shows how variable names and 
+Another example, which often appears in practice, shows how keyword names and 
 their ``types'' can easily lead to an error. Consider the
@@
 
-Second, we will learn patterns describing variables and their relations.
+Second, we will learn patterns describing keywords and their relations.
 We will associate with each type a set of very general templates.

### 2016-11-11 Ennan-Proposal/prelim.tex
stuff

@@
 correct configuration files and derive rules describing variable 
-relations. We illustrate how it is done on two fragments of configuration 
-files given in Fig.~\ref{fig:twoFiles}.  When analyzing
-a file, we first do type-checking, \ie we assign a type to every variable. After that we instantiate each template with the typed variables and we save the learned set 
+relations. We illustrate how is this done on two fragments of 
+configuration files given in Fig.~\ref{fig:twoFiles}.  When analyzing
+a file, we first assign a type to every 
+variable. After that we instantiate each template with the typed 
+variables and we save the learned set 
 of rules. For instance, with the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 

### 2016-11-11 Ennan-Proposal/arch.tex

@@
 configuration errors (\eg, ordering errors, missing entry errors,
-and fine-grained value correlation errors) that the
-state-of-art efforts cannot detect. 
+and fine-grained value correlation errors) that existing
+efforts cannot detect. 
 Figure~\ref{fig-overview} presents
@@
 that we are given a number of (not necessarily correct) 
-configuration files, called {\em training set} (or sample dataset), 
-belonging to the same system, such as MySQL or Apache. 
-These files, therefore, follow similar patterns.
+configuration files, called {\em sample dataset}, 
+belonging to the same system (\eg, MySQL or Apache)
+as the configuration file we want to verify (called as target
+configuration file). Thus, these files (including sample set
+and the target configure file) follow similar configuration patterns.
 %In the following steps,
@@
 \paragraph{Translator (Sec.~\ref{sec:lang}).}
-The translator module first parses the input training 
-set (containing both configuration files and system environment
+The translator module first parses the input sample dataset 
+(containing both configuration files and system environment
 information), and then transforms them into a more structured
-and typed intermediate representation.
+and typed intermediate representation, which follows
+our defined language model (see Sec.~\ref{sec:lang} 
+for more language model definition details).
 When we infer the types of entries in a configuration file, 
 the type of an entry cannot always be fully determined from 
-a single value, since it is very hard to understand
+a single value, because: 1) it is very hard to understand
 the purposes of key-value entries in modern
-software configuration files~\cite{xu15hey}.
-We address this problem 
+software configuration files~\cite{xu15hey},
+and 2) configuration files in the given sample dataset may contain 
+many incorrect entries.
+We, therefore, address this problem 
 by introducing {\em probabilistic types}.
@@
 we assign several types over a probability distribution. 
-We can later use these more structured files
-as a training set to learn the rules.
+We can later (in the learner module) use these more structured files
+(represented in our defined language model) 
+as a training set to determine those probabilistic types, 
+thus finally learning the rules.
 
 \begin{figure*}[tbp] \centering
-\includegraphics[width=0.95\textwidth]{figs/overview}
+\includegraphics[width=0.9\textwidth]{figs/overview}
 \caption{\app's workflow. The green components represent configuration 
@@
 and will be used by the checker to detect errors later.
-By combining the translated representations and the learned
-rules together, we build a language model for
-configuration verification.
 Because the translator outputs probabilistically typed entries,
@@
 
-Although the learner does not necessarily rely on templates,
+\com{
+Although the learner has been capable of generating ruldoes not necessarily rely on templates,
 \app still offers a database containing many templates,
@@
 the learner needs a template DB to provide environment information,
-thus detecting system environment-related configuration errors.
+thus detecting system environment-related configuration errors.}
 
@@
 The checker is used to detect rule violations in the configuration
-files of interest. The inputs of the checker are the learned rules 
+files of interest. The inputs of the checker are the learned rules,
 and the target configuration file to verify.
-It generates a report (as shown in $\S$\ref{sec-motiv}) about 
-whether it finds any error, \eg, rule violations 
-or some suspicious values (\eg, singular value anomaly).
+First, the checker translates the target configuration file into
+the representation in our language model, and
+then reports whether it has errors by checking it with the
+learned rules. 
+The checker generates a report (as shown in Sec.~\ref{sec:prelim}) about 
+what errors the target configuration file has.
 As shown in Figure~\ref{fig-overview},

### 2016-11-11 Ennan-Proposal/solutions.tex
details in learner

@@
 \begin{align*}
-C :=&\ \text{Correct Learning Set}\\
+C ::&\ \text{Correct Learning Set}\\
 C =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
-LR :=&\ \text{Learned Rules} :: \{\textrm{Rule}\}\\
+LR ::&\ \text{Learned Rules} :: \{\textrm{Rule}\}\\
 LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file) \\
@@
  because we say {\tt max\_connections} is always greater than {\tt max\_persistent} if no value is provided for {\tt max\_persistent} in that file.
+
+We chose to employ this approach in our earlier work~\cite{santolucitoCAV} because any rule produced is guaranteed to be a correct rule.
+As opposed to a traditional machine learning approach, we have here a formal guarantee of rule coverage.
+Furthermore, by design this approach gives a justification (error location) for the classification of a user file as correct or misconfiguration.
+This approach is most closely related to version space learning~\cite{mitchell77}, which we discuss further in Sec.~\ref{sec:travis}.
 
@@
 \begin{align*}
-U\ :=&\ \text{Unlabeled Learning Set}\\
+U ::&\ \text{Unlabeled Learning Set}\\
 U =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
-LP :=&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
-LR =&\ \{ r\ \mid \Pi file \in C,\ holds(r,file)\ \land \\
+LP ::&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
+LP =&\ \{ r\ \mid \Pi file \in C,\ holds(r,file)\ \land \\
 &\qquad  \ \Psi file \in C,\ nontriviallyHolds(r,file)\} 
@@
 We use $\Pi$ and $\Psi$ in Fig~\ref{fig:configV} to indicate that the rule holds for some critical portion of the files.
-The inuition behind these quantifiers are that we want to consider rules which are true in majority of cases ($\Pi$), 
+The intuition behind these quantifiers are that we want to consider rules which are true in majority of cases ($\Pi$), 
 and for which we have at least some examples for which that rule is nontrivially true ($\Psi$).
-The exact definition of $\Pi$ and $\Psi$ is a research question still to be solved.
-What exactly is the cutoff value that will yield the best results in learning.
+The exact definition and implementation of $\Pi$ and $\Psi$ is a research question still to be solved.
+Even taking a simple majority voting approach, we must find the cutoff value that will yield the best results in learning.
 We plan to try multiple strategies to find these values.
-One approach may be to use machine learning for program optimization, with a tool like OpenTuner~\cite{ansel:pact:2014}.
-It is also possible that this value differs depending on the quality of the learning set and/or the particular type of rule being learned.
+One approach may be to use machine learning for program autotuning, with a tool like OpenTuner~\cite{ansel:pact:2014}.
+This requires creating some cost function for which the autotuning can optimize.
+Additionally, it is possible that $\Pi$ and $\Psi$ differ depending on the quality of the learning set and/or the particular type of rule being learned.
+Building a clear formalization and a modular tool to explore these questions is major task.
+
+Note that this approach differs from a unsupervised learning setting~\cite{hastie2009unsupervised} where the training set is completely unlabelled and seeks to discover some hidden underlying strucutre.
+Although still unlabelled, we make the assumption that some majority of the training set must be correct.
+We are again learning a model which will provide clear justification (error locations) for the classification.
+However, now we do not have the formal guarantees of the ConfigC approach.
+From previous work, we believe this is a worthwhile trade-off in order to decrease the fasle positive rate.
 

### 2016-11-11 Ennan-Proposal/travis.tex
details in learner

@@
 
-One such example of such a training set of configuration files is TravisCI~\cite{travis}.
+One such example of such a training set of configuration files is TravisCI~\cite{API}.
 TravisCI, a popular integration and build testing service connected to Github.
@@
 Version space learning builds a logical constraint model for binary
-classification~\cite{mitchell82}, which we use to test a configuration file for membership
+classification~\cite{mitchell77}, which we use to test a configuration file for membership
 in the set of all correct files~.

### 2016-11-11 Ennan-Proposal/prelim.tex

@@
 a file, we first assign a type to every 
-variable. After that we instantiate each template with the typed 
-variables and we save the learned set 
+keyword. After that we instantiate each type-associated template with 
+the concrete keywords and we save the learned set 
 of rules. For instance, with the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 

### 2016-11-11 Ennan-Proposal/exampleLearn.tex
autocommit

\begin{tikzpicture}[%
    >=stealth' % here you can choose the arrow tip of your choice
		]
\tikzset{% define styles for the different boxes, adjust parameters to wish
  base/.style={align=center, minimum height=5mm, minimum width=10mm, draw=black,thick},
	circ/.style={align=center, minimum width=4mm, circle, draw=black,thick},
	% coord node style is used for drawing the arrows i.e. invisible nodes
  coord/.style={coordinate},
}

\matrix [column sep=10mm, row sep=14mm, every node/.style={
    shape=rectangle,
    text width=2.75cm,
    text centered,
    very thick,
    draw=none,
}] {
\node (a) {file 1}; &
\node (b) {file 2};
};

\node [base,minimum width=12mm,minimum height=9mm,above=0mm of a,draw=black,dotted,thin](abox) {f};
\node [base,above left=2mm and 3mm of b.north](bbox1) {a1};
\node [base,above right=2mm and 3mm of b.north](bbox2) {a2};
\node [base,above=4mm of c](cbox) {a};
\node [base,above=4mm of d](dbox) {a};

\tikzset{% define styles for the different boxes, adjust parameters to wish
  base/.style={align=center, minimum height=5mm, minimum width=10mm, draw=black,dotted},
	circ/.style={align=center, minimum width=5mm, circle, draw=black,thick},
	% coord node style is used for drawing the arrows i.e. invisible nodes
  coord/.style={coordinate},
}

% add large box to two boxes in b
\node [base, minimum width=28mm,minimum height=9mm, above=0mm of a](bboxLarge){};

% add larger box to c and d
\node [base, minimum width=24mm, minimum height =10.5mm, above=0mm of c](cboxLarge){};
\node [base, minimum width=24mm, minimum height =10.5mm, above=0mm of d](dboxLarge){};

% add coordinates to allow for drawing of the arrows
\node [coord,left=7mm of acirc](c_a1){};
\node [coord,right=7mm of acirc](c_a2){};
\node [coord,left=6mm of bbox1](c_b1){};
\node [coord,right=6mm of bbox2](c_b2){};
\node [coord,left=10mm of cbox](c_c1){};
\node [coord,right=10mm of cbox](c_c2){};
\node [coord,left=10mm of dbox](c_d1){};
\node [coord,right=10mm of dbox](c_d2){};

% finally add the arrows
\begin{scope}[->, thick]
\draw (c_a1) -- (acirc.west);
\draw (acirc.east) -- (c_a2);

\draw (c_b1) -- (bbox1);
\draw (bbox1) -- (bbox2);
\draw (bbox2) -- (c_b2);

\draw (c_c1) -- (cbox);
\draw (cbox) -- (c_c2);
\draw ([yshift=-4mm]c_c1) -- ([yshift=-4mm]c_c2);

\draw ([yshift=1mm]c_d1.east) -- ([yshift=1mm]dbox.west);
\draw ([yshift=1mm]dbox.east) -- ([yshift=1mm]c_d2.west);
\draw ([yshift=-1mm]dbox.east) to [out=346,in=194,looseness=6] ([yshift=-1mm]dbox.west);
\end{scope}

\end{tikzpicture}

### 2016-11-11 Ennan-Proposal/solutions.tex
autocommit

@@
 LR ::&\ \text{Learned Rules} :: \{\textrm{Rule}\}\\
-LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file) \\
+LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file) \land \\
 &\qquad \ \exists file \in C,\ nontriviallyHolds(r,file)\} 
@@
  because we say {\tt max\_connections} is always greater than {\tt max\_persistent} if no value is provided for {\tt max\_persistent} in that file.
+
+\begin{figure}[!h]
+%\begin{subfigure}{.3\textwidth}
+%\begin{lstlisting}[mathescape=true]
+%n = {}
+%for (c in $C$):
+%  n1 = M(c)
+%  n = merge(n, n1)
+%\end{lstlisting}
+%\end{subfigure}%
+\begin{subfigure}{.07\textwidth}
+\underline{File 1}
+\begin{lstlisting}[mathescape=true]
+A
+B
+C
+\end{lstlisting}
+\end{subfigure}%
+\begin{subfigure}{.07 \textwidth}
+\phantom{R}
+\begin{lstlisting}[mathescape=true]
+AB
+AC
+BC
+\end{lstlisting}
+\end{subfigure}%
+\begin{subfigure}{.1\textwidth}
+\underline{File 2}
+\begin{lstlisting}[mathescape=true]
+A
+C
+B
+\end{lstlisting}
+\end{subfigure}%
+\end{figure}
+As an example of this process consider the situation where the training set contains two files, and the only rule we consider is ordering.
+File 1 contains keywords in the order $[A,B,C]$, and file 2 contains the ordred keywords $[A,C,B]$.
+File 1 will produce the set of possible rules $AB, BC, AC$ - and file 2 will produce $AC, CB, BC$.
+The only rule that holds for all the files in the training set is then $AC$, so only that rule will be included.
 

### 2016-11-11 Ennan-Proposal/prelim.tex
stuff

@@
 a file, we first assign a type to every 
-keyword. After that we instantiate each type-associated template with 
-the concrete keywords and we save the learned set 
+keyword. After that we instantiate each type-annotated template with 
+concrete keywords and we save the learned set 
 of rules. For instance, with the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 
@@
 The set of learned rules is changing with every file that we analyze: contradicting 
-files are removed and new rules are added. In practice, this process is done 
+files are removed and new rules are added. After analyzing File\_2 the rule \texttt{max\_connections = 300} is removed. In practice, this process is done 
 in parallel.
-
-After analyzing File$_2$ the rule \texttt{max\_connections = 300} is removed.
 
@@
 
-Once this preprocessing of training data is done, the resulting language model, 
+Additionally to the described process, we also developed algorithms for 
+the misconfigurations that cannot easily be templated. All together, 
+ConfigC can detect the following errors:
+missing entries, ordering errors, type errors and
+simple value correlations. Once this preprocessing of training data is 
+done, the resulting language model, 
 together with accompanying rules, 
@@
 
-Additional to the described process we also developed algorithms for the 
-misconfigurations that cannot easily be templated. All together, ConfigC 
-can detect the following errors:
-missing entries, ordering errors, type errors and
-simple value correlations. Running ConfigC on Example~1 from 
+Running ConfigC on Example~1 from 
 Sec.~\ref{sec:intro-examples} returns the following output:
@@
 
-To our knowledge, there is no existing effort that is able to detect
-the above errors, because they are very tricky to identify in
-practice.
+\iffalse
 
@@
 
-\paragraph{Evaluations on ConfigC.}
-We implemented a prototype system by following 
-our ConfigC design~\cite{santolucitoCAV}.
-In order to demonstrate the capability of ConfigC,
-we evaluated the ConfigC prototype based on real-world
-MySQL configuration files~\cite{configdataset} 
-containing tricky misconfiguration errors,
-such as entry missing errors, ordering errors, and
-value correlation errors.
-We extracted 20 MySQL configuration files to detect, 
-and grouped them into four categories according to their
-error types: missing entry, type error, ordering error
-and value correlation.
-Table~\ref{table:res} shows the evaluation results we use
-ConfigC to detect configuration errors in these 20 real-world
-configuration files.
-As shown in Table~\ref{table:res},
-ConfigC is able to successfully report the misconfiguration problems.
+\fi
 
@@
 
-\paragraph{Limitations.}
-ConfigC still has the following limitations.
+We implemented a prototype and evaluated it on 
+real-world MySQL configuration files~\cite{configdataset}.
+We manually extracted 20 files that contained errors which our tool 
+can detect and grouped them into four categories according to their
+error types: missing entry, type error, ordering error
+and value correlation. The evaluation results are shown in 
+Table~\ref{table:res}. We can see that the our tool can detect most of 
+the errors, with a low number of false positives. We believe that further
+studies in this direction will bring us better results
+
+\subsection{Limitations of ConfigC}
+Despite promising early results, ConfigC was a first experimental attempt 
+into formal verification of configuration files, and as such it still has several limitations.
 
@@
 
-\item ConfigC requires the datasets of configuration files for training 
-  have to be correct, which is hard to achieve in practice, since 
+\item ConfigC works on the premise that training dataset consists only 
+of correct files, which is hard to achieve in practice. In the 
+prototype we manually checked every file in the prototype. Clearly, this approach will not scale and  since 
   it is difficult for administrators or users to offer a

### 2016-11-11 Ennan-Proposal/travis.tex
autocommit

@@
 
-Driven by the above motivating example, we propose an extension to \app that
-learns over a training set with both correct and incorrect examples, as well as a temporal structure.
-Such an extension employs an existing technique from the machine learning community, called version space learning,
-to significantly decrease the false positive rate while maintaining the detection capability of \app.
+%Driven by the above motivating example, we propose an extension to \app that
+%learns over a training set with both correct and incorrect examples, as well as a temporal structure.
+%Such an extension employs an existing technique from the machine learning community, called version space learning,
+%to significantly decrease the false positive rate while maintaining the detection capability of \app.
 
@@
 using a series of disjunctions from a set of predefined hypotheses.
-Here we will instead use a conjuctions to convey that a configuration file must meet the learned criteria.
+Here we will instead use a conjunctions to convey that a configuration file must meet the learned criteria.
 This extension will build a logical formula representing the entire 
@@
 the ordered git commit history.
-In the case of TravisCI, this include the \verb|.travis.yml| file, 
-as well as code features that may effect build status, 
-such as programming language and a list of imported libraries.
-The summary must be \textit{sufficiently detailed}, that is it must contain every piece of information that might lead to a build error.
+%In the case of TravisCI, this include the \verb|.travis.yml| file, 
+%as well as code features that may effect build status, 
+%such as programming language and a list of imported libraries.
+%The summary must be \textit{sufficiently detailed}, that is it must contain every piece of information that might lead to a build error.
 
@@
 
-We now consider both incorrect and correct 
+We now consider both incorrect and correct files in the training set 
 and so must introduce the \textit{general boundary}.
@@
 From the above we know that if a build is erroring, then there must exist at least one error.
-%By pushing the negation into the formula,
 We can also know that if a build is passing, then there must not exist any errors.

### 2016-11-11 Ennan-Proposal/solutions.tex

@@
 
+\com{
 \begin{figure}[!h]
@@
 \end{figure}
-As an example of this process consider the situation where the training set contains two files, and the only rule we consider is ordering.
-File 1 contains keywords in the order $[A,B,C]$, and file 2 contains the ordred keywords $[A,C,B]$.
-File 1 will produce the set of possible rules $AB, BC, AC$ - and file 2 will produce $AC, CB, BC$.
-The only rule that holds for all the files in the training set is then $AC$, so only that rule will be included.
+}
+
+As an example of this process, consider the situation 
+where the training set contains two files F1 and F2, 
+and the only rule we consider is ordering.
+F1 contains keywords in the order $[A,B,C]$, 
+and F2 contains the ordered keywords $[A,C,B]$.
+F1 will produce the set of possible rules $AB, BC, AC$, 
+and F2 will produce $AC, CB, BC$.
+The only rule that holds for all the files in the training set is 
+then $AC$, so only that rule will be included.
 
@@
 With a configuration file that has been verified against catastrophic
-failures (\eg, missing entry, type, and ordering errors), 
-the user may also want to examine more subtle issues.
-Anomalous values can cause tricky, but impactful, performance and memory
-issues that are hard to debug, as discussed in Example 4 of 
-$\S$\ref{sec-motiv}. 
+configuration errors (\eg, missing entry, type, and ordering errors), 
+the user may also want to examine some anomalous values,
+which may also cause tricky and critical performance
+issues that are hard to debug.
 Consequently, anomalous values should be flagged and a warning returned

### 2016-11-12 Ennan-Proposal/motivation.tex
config: motiv

@@
 today's software system failures~\cite{xu15systems, yin11anempirical}.
-We read in the news that recently there was a problem in accessing  Facebook and Instagram \cite{mashableNews} and a Facebook spokeswoman that this was due to a change to the site's configuration systems.
-While program verification is mostly focused on detecting errors 
-in code, in their empirical study Yin {\em et al.}~\cite{yin11anempirical} report
-that about 31\% of system failures were caused by configuration errors problems and only 20\% were caused by bugs in program code. Configuration 
-errors are commonly known in literature under the name misconfigurations.
+We read in the news that recently there was a problem in accessing  
+Facebook and Instagram~\cite{mashableNews}, 
+and a Facebook spokeswoman reported that 
+this was caused by a change to the site's configuration systems.
+In a recent software system failures study~\cite{yin11anempirical},
+researchers revealed that about 31\% of system failures were caused by 
+configuration errors, which is higher than the percentage of
+failures resulting from program bugs (20\%). 
+%(which and only 20\% were caused by bugs in program code 
+%While program verification is mostly focused on detecting errors 
+%in code, in their empirical study 
+%Yin {\em et al.}~\cite{yin11anempirical} report
+%that about 31\% of system failures were caused by configuration errors problems and only 20\% were caused by bugs in program code. 
+Configuration errors are commonly known in literature 
+under the name misconfigurations.
 
@@
 We start by presenting two non-trivial configuration errors
-extracted from real-world examples. Although the errors are relatively simple, we call them 
-non-trivial, because the majority of existing tools, \eg, learning-based checking
-tools~\cite{zhang14encore, wang04automatic}, cannot detect
-these configuration errors. Most of the presented examples were found on StackOverflow,
-a popular question and answer website for programmers.
+extracted from real-world examples. 
+Although the errors are relatively simple, we call them 
+non-trivial, because the majority of existing misconfiguration
+checking tools~\cite{zhang14encore, wang04automatic} cannot detect
+these configuration errors. 
+Most of the presented examples were found on
+StackOverflow~\cite{stackoverflow},
+a popular Q\&A website for programmers.
 
@@
 \item a lack
-of a specification which would describe properties of configuration files
+of a specification describing properties of configuration files
 \item a program structure of configuration files -- they
-are mainly a sequence of entries assigning some value to system keywords. 
+are mainly a sequence of entries assigning some value to system
+variables (called {\emph {keywords}}). 
 \end{itemize}

### 2016-11-12 Ennan-Proposal/agenda.tex
config: agenda and impact

\section{Research Agenda}

The primary work involved in this project
falls into three broad categories:
(i) defining a more comprehensive language model,
(ii) developing new learning algorithms, and
(iii) developing and evaluating \app
  in real-world configuration files.

\subsection{Defining A More Comprehensive Language Model}

While we feel our proposed language model to be relatively comprehensive
to capture many tricky misconfiguration cases,
we will need to define a better language model to represent more types of
configuration files. The configuration files of some of software systems, 
\eg, squid, are not limited to the key-value parameters; thus,
we need to extend the current language model in order to represent
the configuration files of these systems.
In addition, some other types of latent configuration errors 
have been exposed by recent work~\cite{xu16early}.
For example, the path parameter in a MySQL configuration file
has an unknown user account. Such an error cannot be represented in
our proposed language model. Thus, we need to improve it to capture
more error types.

\subsection{Proposing New Learning Algorithms}

We are planning to develop new learning algorithm capable of extracting
rules more accurately and efficiently. We plan to first investigate 
some existing learning algorithms for learning program rules, \eg,
Raychev {\em et al.}~\cite{raychev15predicting, raychev16learning},
and then adapt these algorithms to our scenario, \ie, learning 
the configuration file rules.

\subsection{Deploying and Evaluating \app In Real-World Services}

The project's third main task is to prototype \app and make \app
practical to real-world misconfiguration verification,
thus making \app become a useful tool in practice.
We plan to evaluate the \app prototype's efficiency, usability, and
accuracy using a variety of micro- and macrobenchmarks.
For example, we can evaluate the efficiency and accuracy of 
each module of \app, thus understanding \app's practicality.
More importantly, we will use \app to detect real-world configuration
files~\cite{configdataset}, and then manually check whether \app is able
to successfully detect potential configuration files.

### 2016-11-12 Ennan-Proposal/impact.tex
config: agenda and impact

\section{Broader Impact}

If successful, \app could have the following broader impacts:

\begin{itemize}

\item {\bf Opening the door of language-based configuration verification.}
  Today's misconfiguration checking approaches are still using {\em ad hoc}
  algorithms to detect potential misconfiguration root causes. On the
  contrary, \app could open the door of configuration verification,
  which rigorously verifies whether the target configuration files meet
  specifications. In other words, \app enables users 
  to verify configuration files like verifying programs. Such a capability
  cannot be offered by any of existing efforts.

\item {\bf Preventing configuration errors without adding any additional
  burden to users.} Because \app employs automatic machine learning 
  algorithms to extract rules, users or system administrators do not need
  to manually write their specifications, which significantly reduce the
  burden of users and system administrators. Such a way not only
  makes the configuration verification process become much easier and more 
  usable, but also decreases the potential issues of writing 
  specifications.

\item {\bf Complementing post-failure error diagnosis efforts.}
  There have been many diagnosis and troubleshooting efforts to localizing
  the root causes of configuration errors after system failures occur.
  We call these approaches as post-failure error diagnosis efforts.
  On the contrary, \app offers a pre-failure error checking effort,
  which could be looked as a preliminary checking before installing
  systems. Because \app is able to find out many sophisticated 
  configuration errors, it removes many labors of 
  the post-failure error diagnosis tools. In addition, the results
  output by \app could be used as a guidance for all the post-failure
  error diagnosis approaches, making these approaches more efficient.

\item {\bf Benefiting other communities, \eg, network misconfiguration.} 
  Besides software misconfiguration, network community has the same 
  misconfiguration problems. In particular, many recent service outage 
  reports exposed network-level configuration error will lead to
  very critical service outages. \app could be extended to reason about
  network-level configuration errors.

\end{itemize}

### 2016-11-12 Ennan-Proposal/prelim.tex
stuff

@@
 
-\item ConfigC works on the premise that training dataset consists only 
-of correct files, which is hard to achieve in practice. In the 
-prototype we manually checked every file in the prototype. Clearly, this approach will not scale and  since 
-  it is difficult for administrators or users to offer a
-  set of 100\% correct configuration files for training.
+\item ConfigC works on the premise that the training dataset consists 
+only of correct files, which is hard to achieve in practice. In the 
+prototype we manually checked every file in the prototype. Clearly, this 
+approach will not scale in practice. There exist a large set of 
+real-world misconfigurations~\cite{configdataset}. Nevertheless, the 
+errors are distributed through the files and do not all appear at the 
+same spot. We believe that it should be possible to construct a correct
+specification from the rules that hold in a significant majority of the 
+files.
 
-\item The language model of ConfigC is still a starting point. It
-  is hard to formulate a uniform representation for diverse
-  configuration files.\ennan{we still need to put one more sentence
-  here to distinguish why our current language model is better
-  than ConfigC's language model}
+\item A language model used in ConfigC cannot handle a simple version of 
+the {\tt {if-then}} command that sometimes appears in some configuration
+files (such as Apache HTTPD). We already pointed out some issues with 
+parsing and possible wrong typing. We need to develop a more 
+accurate model which will be a uniform representation for diverse
+  configuration files.
 
-\item ConfigC can only offer coarse-grained value correlation errors,
-  \eg, $\texttt{max\_connections} > \texttt{mysql.max\_persistent}$.
-  In practice, many software outages were caused by more tricky, called
-  fine-grained value correlation~\cite{correlation}. For example, 
-  in a MySQL configuration file, $\texttt{key\_buffer\_size}$ should be 
-  higher than $\texttt{max\_connections} \times 
-  \texttt{sort\_buffer\_size}$~\cite{correlation};
-  otherwise, the MySQL load will be very high.
+\item ConfigC offers only a limited number of templates to to detect 
+correlation errors on keywords. It can detect, for example, 
+keyword comparisons, but in practice many software outages were 
+caused by more complex correlations (also called
+  fine-grained correlations~\cite{correlation}). As an illustration,
+  ConfigC cannot find an error in Example~2 in 
+Sec.~\ref{sec:intro-examples}. However, to detect more complex rules, we will need to use tools like SMT solvers \cite{z3, cvc4}.
 
-\item ConfigC cannot check singular value anomalies. For example,
-  a parameter relating to memory in MySQL configuration files is
-  setted too large, exhausting the RAM and causing extreme slowness
-  or even a crash. Such an anomalous value does not violate any
-  constraints (\eg, type error and value ordering error), but 
+\item ConfigC cannot check for anomalies in a value set for one particular keyword. For example,
+  setting a parameter, which relates memory in MySQL configuration 
+  files, too large can cause exhausting the RAM and causing extreme 
+  slowness or even a crash. Such an anomalous value does not violate any
+  previously mentioned constraints (such as type errors or ordering errors), but yet 
   it makes system behave wrongly.
@@
 
-This proposal aims to address the above limitations.
+This proposal aims to address all the above limitations.

### 2016-11-12 Ennan-Proposal/motivation.tex
stuff

@@
 Design and Implementation, a top-tier system conference) a paper on
-detecting configuration errors~\cite{xu16early} received the best paper 
+detecting configuration errors by emulating the late execution
+ ~\cite{xu16early} received the best paper 
 award. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration errors~\cite{attariyan10automating,
@@
 verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
-detect errors without executing the code.
+detect errors without executing the code. Our proposal offers 
+automated verification of configuration files: we are analyzing 
+files and proactively reporting potential errors, without waiting for them to happen.
 
@@
 specify which properties keywords in configuration files need to satisfy. One can see this learning process as 
-a way of deriving  a specification for configuration files. With these  rules we can efficiently check 
+a way of deriving  a specification for configuration files. 
+It is also hard to talk here about a complete specification, but 
+still having some specification is better than none, and we plan to 
+increase the preciseness of a specification as we gain a better 
+understanding of the formalism needed for its description.
+Having a specification, we can efficiently check 
 the correctness of the configuration files of interest and detect 
 potential errors. Errors are reported if the configuration file does not 
-adhere to a specification.
+adhere to the derived specification.
 

### 2016-11-12 Ennan-Proposal/arch.tex
stuff

@@
 We propose to build \app, an automatic verification framework for 
-software configuration files.
-In particular, \app is built upon ConfigC and aims at addressing
-all the limitations of ConfigC (mentioned in Sec.~\ref{sec:prelim}).
-\app is capable of detecting many sophisticated 
-configuration errors (\eg, ordering errors, missing entry errors,
-and fine-grained value correlation errors) that existing
-efforts cannot detect. 
-Figure~\ref{fig-overview} presents
+software configuration files, by exploring further the insights we 
+obtained when building ConfigC. Figure~\ref{fig-overview} presents
 a typical \app verification workflow which contains three steps:
-translation, learning, and checking. In this section, we briefly
-describe how each step works.
+translation into an intermediary representation, a specification 
+learning, and checking the correctness of a given configuration file.
 
-\paragraph{Initial phase.}
-We start with the assumption 
-that we are given a number of (not necessarily correct) 
-configuration files, called {\em sample dataset}, 
-belonging to the same system (\eg, MySQL or Apache)
-as the configuration file we want to verify (called as target
-configuration file). Thus, these files (including sample set
-and the target configure file) follow similar configuration patterns.
-%In the following steps,
-%we will exploit in a collection of learning algorithms 
-%to build rules that describe a language model for the files.
-
-\paragraph{Translator (Sec.~\ref{sec:lang}).}
-The translator module first parses the input sample dataset 
-(containing both configuration files and system environment
-information), and then transforms them into a more structured
-and typed intermediate representation, which follows
-our defined language model (see Sec.~\ref{sec:lang} 
-for more language model definition details).
-When we infer the types of entries in a configuration file, 
-the type of an entry cannot always be fully determined from 
-a single value, because: 1) it is very hard to understand
-the purposes of key-value entries in modern
-software configuration files~\cite{xu15hey},
-and 2) configuration files in the given sample dataset may contain 
-many incorrect entries.
-We, therefore, address this problem 
-by introducing {\em probabilistic types}.
-In particular, rather than giving a variable a single type, 
-we assign several types over a probability distribution. 
-We can later (in the learner module) use these more structured files
-(represented in our defined language model) 
-as a training set to determine those probabilistic types, 
-thus finally learning the rules.
-
-\begin{figure*}[tbp] \centering
+\begin{figure*}[htbp] \centering
 \includegraphics[width=0.9\textwidth]{figs/overview}
@@
 
-\paragraph{Learning (Sec.~\ref{sec-learn}).}
-The input of the learner is a set of files that have been translated
-into well-structured representations (\ie, the translator's
-outputs). The learner module employs a collection of learning algorithms
-to generate various rules and constraints,
+\paragraph{Learning Specifications.}
+Similarly as before, we start with an assumption 
+that we are given a number of 
+configuration files belonging to the same system (\eg, MySQL or Apache).
+Additionally, we assume that files in this data set are 
+not necessarily correct, but if there are errors they appear only in some
+file. We then translate that dataset into a more structured
+and typed intermediate representation, which follows
+our defined language model (cf. Sec.~\ref{sec:lang}).
+Since the type of an entry cannot be fully determined from 
+the entry value, we introduce {\em probabilistic types}, which is
+a more flexible type notion: to a indefinite keyword it 
+assigns a list of possible types together with their probability 
+distribution. The learner module employs a collection of learning
+ algorithms to generate various rules and constraints.
+It uses type-annotated templates to infer the rules. In addition, 
+there are algorithms for detecting ordering errors and missing entry
+errors, which do not depend on templates. However, this time, 
+since the input set is not necessarily correct, the learned rules are
+also annotated with the probability indicating the likelihood of being 
+correct.
+
 potentially used to handle different types of configuration errors.

### 2016-11-12 Ennan-Proposal/arch.tex
stuff

@@
 
-potentially used to handle different types of configuration errors.
-These rules and constraints are the outputs of the learner, 
-and will be used by the checker to detect errors later.
-Because the translator outputs probabilistically typed entries,
-the learner is responsible for determining a type for each entry.
+\iffalse
+There were some previous efforts to use templates for configuration files, \eg, EnCore~\cite{zhang14encore},
+which requires users or developers to provide explicit templates. The
+\app user does not need to provide any t 
+addition they could not detect errors
+Our approach is to use
 
-\com{Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
-which requires users or developers to provide explicit templates,
  \app's learner encodes some predefined error-patterns 
@@
 that \app should handle: we consider integer constraints, 
-ordering errors, typing errors, correlation errors, etc.}
+ordering errors, typing errors, correlation errors, etc.
 
-\com{
 Although the learner has been capable of generating ruldoes not necessarily rely on templates,
@@
 the learner needs a template DB to provide environment information,
-thus detecting system environment-related configuration errors.}
+thus detecting system environment-related configuration errors.
 
-\paragraph{Checking.}
-The checker is used to detect rule violations in the configuration
-files of interest. The inputs of the checker are the learned rules,
-and the target configuration file to verify.
-First, the checker translates the target configuration file into
-the representation in our language model, and
-then reports whether it has errors by checking it with the
-learned rules. 
+\fi
+
+\paragraph{Correctness Checking.}
+The checker takes as input a configuration files and reports 
+it the file adheres to the learned specification. In addition, it 
+will also check if the keyword values fall into a certain range and they are not significantly different than the value usually used.
 The checker generates a report (as shown in Sec.~\ref{sec:prelim}) about 
-what errors the target configuration file has.
-As shown in Figure~\ref{fig-overview},
-there are two sub-modules in the checker. They are responsible for
-checking rule violations and suspicious values, respectively.
-In our experience, we found learned rules could be significantly reused
-to check different configuration files, thus improving our usability.
+found errors.

### 2016-11-12 Ennan-Proposal/language.tex
stuff

--- 2016-05-10 OSDI/trans.tex
@@
-\section{Translator}
-\label{sec-trans}
+\subsection{A Language Model for Configuration Files}
+\label{sec:lang}
 
-The translator takes as input a sample dataset of configuration files and transforms it into another set of files written in
-typed and well-structured representations.
-The translator can be seen a parser, and it is only
-used to generate an intermediate representation for post-processing, 
-such as learning rules (see $\S$\ref{sec-learn}).
-Coupled with rules generated by learner module,
-we will have a complete language model to verify configuration files
-of our interest.
+There are several types of configuration 
+files and each has different representation. Our goal is to find a good 
+intermediary representation that will be language-agnostic. In general,
+one can complain that a design of configuration files is pretty low 
+level and that we need a new programming language for them. We agree with 
+that assertion, and actually our intermediary representation can be seen
+as a new programming paradigm for writing configuration files, but this
+is not the focus of this proposal. Previously, Huang {\em et al.}~\cite{huang15confvalley} proposed a 
+language, ConfValley, to validate 
+whether given configuration files meet administrators' specifications. 
+However, ConfValley cannot check for misconfiguration checking 
+capability, since it is only a library. In ConfValley the administrator 
+still needs to write specifications manually, which is an error-prone
+process. On the contrary, \app does not require users to manually
+write anything.
+
+The translator is a part of \app. It takes as input a sample dataset of configuration files and transforms it into another set of files written in a
+typed and well-structured form.
+The translator can be seen a parser, and it is
+used to translate files into an intermediate representation.
 
@@
 and HDFS, we need to develop different parsers to handle each of them,
-respectively. \app allows users to 
-provide extra help to the translator
-for their specific system configurations,
-but it is not required.
-
-The majority of entries in a configuration files are assignments. Our first attempt was to simply
+respectively. Configuration files mainly consists of assignments of the form {\tt {keyword = value}}. Our first attempt was to simply
 translate every key-value entry {\tt {k = v}} into a triple $(k, v, \tau)$, where $\tau$ is a type of 
@@
 Consider the following example.
-
-\noindent{\tt {foo = 300}}\\
-{\tt {bar = 300.txt}}
-
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
+foo = 300
+bar = 300.txt
+\end{lstlisting} 
 Most likely {\tt foo} should be an integer, but it could also be a string.
@@
 the probability of all other types is set to zero, 
-and the associated rules are withdrawn.
+and the associated rules are withdrawn. With the help of probabilistic types, we addressed ambiguities during the parsing phase.
 
-In \app, the set $\mathcal{T}$ contains strings, integers, file paths, 
+In \app, the set $\mathcal{T}$ should contains strings, integers, file paths, 
 sizes, and IP addresses. With every type, we associate a list of templates 
@@
 In general, the templates works as follows: if there are two entries ${\tt {k1 = v1}}$ and 
-${\tt {k2 = v2}}$, let $t(X, Y)$ be a template that can be applied to those values (w.r.t. their types).
+${\tt {k2 = v2}}$, and let $t(X, Y)$ be a template that can be applied to those values (w.r.t. their types).
 If $t(v1, v2)$ holds, \ie, the template condition is valid for those concrete values, then we will add a rule
-$t(k1, k2)$ to a list of potentially correct specifications. Note that the rule expresses a relation between variables.
+$t(k1, k2)$ to a list of potentially correct specifications. Note that the rule expresses a relation between keywords, and not values.
 
-With the help of probabilistic types, we addressed ambiguities during the parsing phase. Another problem that we need to solve
+Another problem that we need to address
 is that configuration files sometimes contain a simple version of the {\tt {if-then}}, such as in Apache HTTPD, that 
-sets conditions for which an action should be applied. Therefore, we also add this guard to our entry 
-during the parsing phase. We first check if the guard is true before deriving a rule; otherwise, we skip the entry.
+sets conditions for which an action should be applied. Therefore, we also add this guard $g$ to our entry 
+during the parsing phase.
 
-To summarize, the translator translates every entity ${\tt {k = v}}$ in a configuration file into a quadruple entry
+With guards in the picture, when instantiating the rules, we first check
+ if the guard is true. If it is not, we simply skip that entry.
+
+To summarize, the translator translates every entry ${\tt {k = v}}$ in a configuration file into a quadruple entry
 $$(g,k,v,\textsf{List}[p_1:\tau_1, \ldots, p_n:\tau_n])$$
-
-For an entry $e$, we denote the corresponding guard by $g(e)$, the key by $k(e)$, the value by $v(e)$, and the probabilistic
-type list by $typelist(e)$.
-
-\com{Note that typing is also a system module than 
-can be easily extended to support more types. 
-In that case the user will need to provide rules for type inference 
-and probability distributions for values where type inference is ambiguous.
-}

### 2016-11-12 Ennan-Proposal/related.tex
stuff

@@
 the checked configuration files do not satisfy these rules.
-
-Huang {\em et al.}~\cite{huang15confvalley} proposed a 
-language, ConfValley, to validate 
-whether given configuration files meet administrators' specifications. 
-Different from \app, ConfValley does not
-have inherent misconfiguration checking capability, since it only offers
-a language representation and requires administrators to
-manually write specifications, which is an error-prone
-process. On the contrary, \app does not need users to manually
-write anything.
 

### 2016-11-12 Ennan-Proposal/solutions.tex
stuff

@@
-\section{Learner}
+\section{The Learner Module}
 \label{sec-learn}
@@
 
+\iffalse
 \subsection{Derivation of ConfigC Rules}
-\label{subsec-rules}
 
@@
 
-We chose to employ this approach in our earlier work~\cite{santolucitoCAV} because any rule produced is guaranteed to be a correct rule.
+\fi
+
+The approach in our earlier work~\cite{santolucitoCAV} is guaranteed to produced only correct rules.
 As opposed to a traditional machine learning approach, we have here a formal guarantee of rule coverage.
@@
 \subsection{Derivation of ConfigV Rules}
+\label{subsec-rules}
+
 In \app's learner module, we release the assumption in the above
@@
 Rather than manually correcting each file, 
-we extend the previous formalism to run probabilistic learning
-on our intermediate representations (generated by the translator).
+we extend the ConfigC formalism to run probabilistic learning
+on the intermediate representations.
 Our probabilistic approaches for learning missing entry, 
@@
 these permutations constitute a rule. 
-Rule patterns in the example set that appear frequently are accepted,
-so they can be used to evaluate new files.
+Broadly speaking, we accept rule patterns that appear frequently enough.
 
-\begin{figure}[!h]
-\begin{small}
-\belowdisplayskip=-15pt
-\abovedisplayskip=-2pt
+We now describe a formalism how to compute the set of learned
+probabilistic rules, denoted with $\mathcal{PR}$.
+With $\mathcal{U}$ we denote a set of configuration files in the 
+intermediate representation. If a template can be instantiated with
+keywords from file $f$ and the obtained rule $r$ holds, we state that with the predicate 
+$\mathit{appears}(r,f)$.
+If a template is instantiated and we obtain rule $r$, with  the predicate 
+$\mathit{holds}(r,f)$ we state that either $\mathit{appears}(r,f)$ holds, or $r$ could not be instantiated with keywords from $f$. With every 
+rule $r$ we define two sets:
 \begin{align*}
-U ::&\ \text{Unlabeled Learning Set}\\
-U =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
-LP ::&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
-LP =&\ \{ r\ \mid \Pi file \in C,\ holds(r,file)\ \land \\
-&\qquad  \ \Psi file \in C,\ nontriviallyHolds(r,file)\} 
+S_A(r)& =\{ \ f\ | \ \mathit{appears}(r,f)\  \} \\
+S_H(r)& =\{ \ f\  | \ \mathit{holds}(r,f) \ \}
 \end{align*}
-\end{small}
-\caption{The definition of which rules should be learned by ConfigV when learning over a set of possibly correct, and possibly incorrect files.}
-\label{fig:configV}
-\end{figure}
+We define then set $\mathcal{PR}$ as
+$$\mathcal{PR} = \{\ r \ \mid \ |S_A(r)| > T_1 \land |S_H(r)| > T_2 \ \} $$
+where $T_1$ is a threshold value for considering rules which are true in 
+majority of cases, and $T_2$ is a threshold value for considering rules 
+for which we have at least some examples that that rule is will 
+appear in the files.
 
+\ruzica{Read this and weep, Santolucito!}
 We use $\Pi$ and $\Psi$ in Fig~\ref{fig:configV} to indicate that the rule holds for some critical portion of the files.

### 2016-11-12 Ennan-Proposal/arch.tex
Grammatical changes.:

@@
 a typical \app verification workflow which contains three steps:
-translation into an intermediary representation, a specification 
-learning, and checking the correctness of a given configuration file.
+translation into an intermediary representation, learning of a specification,
+and checking the correctness of a given configuration file.
 
@@
 \paragraph{Learning Specifications.}
-Similarly as before, we start with an assumption 
+As with ConfigC, we start with an assumption 
 that we are given a number of 
 configuration files belonging to the same system (\eg, MySQL or Apache).
-Additionally, we assume that files in this data set are 
+Additionally, we assume that files in this dataset are 
 not necessarily correct, but if there are errors they appear only in some
-file. We then translate that dataset into a more structured
+files. We then translate the dataset into a more structured
 and typed intermediate representation, which follows
@@
 Since the type of an entry cannot be fully determined from 
-the entry value, we introduce {\em probabilistic types}, which is
-a more flexible type notion: to a indefinite keyword it 
-assigns a list of possible types together with their probability 
+the entry value, we introduce {\em probabilistic types}, which are
+a more flexible type notion: to an indefinite keyword it 
+assigns a list of possible types, along with their probability 
 distribution. The learner module employs a collection of learning
@@
 \paragraph{Correctness Checking.}
-The checker takes as input a configuration files and reports 
-it the file adheres to the learned specification. In addition, it 
-will also check if the keyword values fall into a certain range and they are not significantly different than the value usually used.
+The checker takes as input a configuration file and reports 
+if the file adheres to the learned specification. In addition, it 
+will also check that the keyword values fall into a certain range and they are not significantly different than the value usually used.
 The checker generates a report (as shown in Sec.~\ref{sec:prelim}) about 

### 2016-11-12 Ennan-Proposal/language.tex
Grammatical changes.:

@@
 There are several types of configuration 
-files and each has different representation. Our goal is to find a good 
+files, and each has a different representation. Our goal is to find a good 
 intermediary representation that will be language-agnostic. In general,
-one can complain that a design of configuration files is pretty low 
-level and that we need a new programming language for them. We agree with 
+one could argue that the design of configuration files is pretty low 
+level, and that we need a new programming language for them. We agree with 
 that assertion, and actually our intermediary representation can be seen
@@
 Translating or parsing is system dependent. In other words, for MySQL
-and HDFS, we need to develop different parsers to handle each of them,
-respectively. Configuration files mainly consists of assignments of the form {\tt {keyword = value}}. Our first attempt was to simply
+and HDFS, we need to develop different parsers.
+Configuration files mainly consists of assignments of the form {\tt {keyword = value}}. Our first attempt was to simply
 translate every key-value entry {\tt {k = v}} into a triple $(k, v, \tau)$, where $\tau$ is a type of 
@@
 
-In \app, the set $\mathcal{T}$ should contains strings, integers, file paths, 
+In \app, the set $\mathcal{T}$ should contain strings, integers, file paths, 
 sizes, and IP addresses. With every type, we associate a list of templates 
@@
 In general, the templates works as follows: if there are two entries ${\tt {k1 = v1}}$ and 
-${\tt {k2 = v2}}$, and let $t(X, Y)$ be a template that can be applied to those values (w.r.t. their types).
+${\tt {k2 = v2}}$, such that $t(X, Y)$ is a template that can be applied to those values (w.r.t. their types).
 If $t(v1, v2)$ holds, \ie, the template condition is valid for those concrete values, then we will add a rule

### 2016-11-12 Ennan-Proposal/motivation.tex
Grammatical changes.:

@@
 today's software system failures~\cite{xu15systems, yin11anempirical}.
-We read in the news that recently there was a problem in accessing  
+Recently, there was a problem in accessing  
 Facebook and Instagram~\cite{mashableNews}, 
@@
 \end{lstlisting} 
-In that case the configuration file will cause the Apache server to 
+In this case, the configuration file will cause the Apache server to 
 fail to start due to a segmentation fault error. 
@@
 depends on {\tt recode.so}, and their relative ordering
-is crucial. This is an example of so-called {\em ordering error}.
+is crucial. This is an example of an {\em ordering error}.
 Yin {\em et al.} report that ordering errors widely exist in
@@
 and typically lead to multiple system crash events.
-However, no existing tool in the systems research can effectively solve 
+However, no existing tool in the systems research area can effectively solve 
 or detect this problem~\cite{zhang14encore, xu15systems, xu13do}.
@@
 \para{Example~2: Fine-grained value correlation error.} 
-Next example also comes from a discussion on 
+Our next example also comes from a discussion on 
 StackOverflow~\cite{correlation}.
-The user has configured her MySQL as in the following:
+The user has configured her MySQL as follows:
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
@@
 \end{lstlisting} 
-The user then complained that her MySQL load was very high, causing the website's
+The user complained that her MySQL load was very high, causing the website's
 response speed to be very slow.
@@
 {\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
-Clearly, in the above example, it does not hold, 
+Clearly, in the above example, this does not hold, 
 so this misconfiguration causes MySQL to load very slowly.
@@
 We believe there are two main obstacles 
-why we cannot simply apply the existing automatic 
-tools and techniques to verification of configuration files are:
+to simply applying the existing automatic 
+tools and techniques to verification of configuration files:
 \begin{itemize}
-\item a lack
+\item the lack
 of a specification describing properties of configuration files
-\item a program structure of configuration files -- they
+\item the structure of configuration files -- they
 are mainly a sequence of entries assigning some value to system
@@
 not adhere to a specific grammar or syntax. In particular, the
-entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries and there
+entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries, and there
 is no explicit structure policy for the entries.
-We believe that those are the reasons why there is no automated verification of configuration 
-files although the system community expressed that that would be highly
-desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
+We believe these to be the reason for the %that those are the reasons why there is no
+lack of automated verification of configuration 
+files,% although the system community expressed that that would be highly desirable
+despite the systems community desires for such verification~\cite{wang04automatic, zhang14encore, xu15systems}.
 
@@
 a large sample of 
-configuration files. A learning process will take as input this 
-sample. The process will be language-agnostic and should work for any kind 
+configuration files,%A learning process will take as input this sample.
+which will be taken by the learning process as input.
+The process will be language-agnostic and should work for any kind 
 of configuration files,  but all of the files in the sample need to be of 
@@
 a way of deriving  a specification for configuration files. 
-It is also hard to talk here about a complete specification, but 
+It is hard to talk here about a complete specification, but 
 still having some specification is better than none, and we plan to 
@@
 understanding of the formalism needed for its description.
-Having a specification, we can efficiently check 
+With a specification, we can efficiently check 
 the correctness of the configuration files of interest and detect 
@@
 their ``types'' can easily lead to an error. Consider the
-following entry {\tt general\_log = /var/log/mysql/mysql.log}. Although this statement 
-alone might look correct, this is actually a typing error and as a result MySQL log cannot be correctly written.
+entry {\tt general\_log = /var/log/mysql/mysql.log}. Although this statement 
+alone might look correct, this is actually a typing error which will prevent the MySQL log from being correctly written.
 
@@
 The user does not need to provide any templates -- they are internally associated to the types.
-Nevertheless, in addition to those general templates, we still need specific algorithms to learn
+In addition to those general templates, we still need specific algorithms to learn
 rules that cannot be easily templated (such as ordering rules).

### 2016-11-12 Ennan-Proposal/prelim.tex
Grammatical changes.:

@@
 From ConfigC we drew the main inspiration for this proposal. We now briefly
-outline how does ConfigC work. It first automatically
+outline how ConfigC works. It first automatically
 analyzes a dataset of correct configuration files to derive
@@
 \end{lstlisting}
-The set of learned rules is changing with every file that we analyze: contradicting 
-files are removed and new rules are added. After analyzing File\_2 the rule \texttt{max\_connections = 300} is removed. In practice, this process is done 
+The set of learned rules changes with every analyzed file: contradicting 
+rules are removed and new rules are added. After analyzing File\_2 the rule \texttt{max\_connections = 300} is removed. In practice, this process is done 
 in parallel.
@@
 
-Additionally to the described process, we also developed algorithms for 
-the misconfigurations that cannot easily be templated. All together, 
+Additionally, we also developed algorithms for 
+misconfigurations that cannot easily be templated. All together, 
 ConfigC can detect the following errors:
@@
 \end{lstlisting} 
-ConfigC could not detect an error present in Example~2 since it can detect 
+ConfigC could not detect the error present in Example~2 since it can detect 
 only simple comparison-based relations.
@@
 prototype we manually checked every file in the prototype. Clearly, this 
-approach will not scale in practice. There exist a large set of 
+approach will not scale. There exist a large set of 
 real-world misconfigurations~\cite{configdataset}. Nevertheless, the 
@@
 
-\item A language model used in ConfigC cannot handle a simple version of 
-the {\tt {if-then}} command that sometimes appears in some configuration
+\item The language model used in ConfigC cannot handle a simple version of 
+the {\tt {if-then}} command that appears in some configuration
 files (such as Apache HTTPD). We already pointed out some issues with 
-parsing and possible wrong typing. We need to develop a more 
+parsing and possible incorrect typing. We need to develop a more 
 accurate model which will be a uniform representation for diverse
@@
 correlation errors on keywords. It can detect, for example, 
-keyword comparisons, but in practice many software outages were 
+keyword comparisons, but in practice many software outages are 
 caused by more complex correlations (also called
@@
   setting a parameter, which relates memory in MySQL configuration 
-  files, too large can cause exhausting the RAM and causing extreme 
+  files, too large can exhaust the RAM, leading to extreme 
   slowness or even a crash. Such an anomalous value does not violate any
-  previously mentioned constraints (such as type errors or ordering errors), but yet 
-  it makes system behave wrongly.
+  previously mentioned constraints (such as type errors or ordering errors), but 
+  it makes system behave incorrectly.
 

### 2016-11-13 Ennan-Proposal/solutions.tex
intro, with news

@@
 
-In \app's learner module, we release the assumption in the above
-solution, which means the rule learning mechanism is tolerant 
+In \app's learner module we need to develop a learning mechanism
+that is tolerant 
 enough to accept a dataset of possibly incorrect configuration files.
@@
 \begin{align*}
-S_A(r)& =\{ \ f\ | \ \mathit{appears}(r,f)\  \} \\
-S_H(r)& =\{ \ f\  | \ \mathit{holds}(r,f) \ \}
+S_A(r)& =\{ \ f \in \mathcal{U}\ | \ \mathit{appears}(r,f)\  \} \\
+S_H(r)& =\{ \ f \in \mathcal{U}\  | \ \mathit{holds}(r,f) \ \}
 \end{align*}
@@
 for which we have at least some examples that that rule is will 
-appear in the files.
-
-\ruzica{Read this and weep, Santolucito!}
-We use $\Pi$ and $\Psi$ in Fig~\ref{fig:configV} to indicate that the rule holds for some critical portion of the files.
-The intuition behind these quantifiers are that we want to consider rules which are true in majority of cases ($\Pi$), 
-and for which we have at least some examples for which that rule is nontrivially true ($\Psi$).
-The exact definition and implementation of $\Pi$ and $\Psi$ is a research question still to be solved.
+appear in the files. Finding the exact values of $T_1$ and $T_2$ is 
+and their connection to $|\mathcal{U}|$
+is a question still to be solved.
 Even taking a simple majority voting approach, we must find the cutoff value that will yield the best results in learning.
@@
 This requires creating some cost function for which the autotuning can optimize.
-Additionally, it is possible that $\Pi$ and $\Psi$ differ depending on the quality of the learning set and/or the particular type of rule being learned.
+Additionally, it is possible that $T_1$ and $T_2$ differ depending on the quality of the learning set and/or the particular type of rule being learned.
 Building a clear formalization and a modular tool to explore these questions is major task.
 
-Note that this approach differs from a unsupervised learning setting~\cite{hastie2009unsupervised} where the training set is completely unlabelled and seeks to discover some hidden underlying strucutre.
-Although still unlabelled, we make the assumption that some majority of the training set must be correct.
+Note that this approach differs from a unsupervised learning setting~\cite{hastie2009unsupervised} where the training set is completely unlabeled and seeks to discover some hidden underlying structure.
+Although our set is also unlabeled, we make the assumption that some majority of the training set must be correct for their biggest part.
 We are again learning a model which will provide clear justification (error locations) for the classification.
-However, now we do not have the formal guarantees of the ConfigC approach.
+However, with this approach we will not have the formal guarantees of the ConfigC approach.
 From previous work, we believe this is a worthwhile trade-off in order to decrease the fasle positive rate.
@@
 
-With a configuration file that has been verified against catastrophic
-configuration errors (\eg, missing entry, type, and ordering errors), 
-the user may also want to examine some anomalous values,
-which may also cause tricky and critical performance
-issues that are hard to debug.
+In addition to checking for correlation, type- or ordering errors, 
+the user may also want to examine if there are anomalous values that 
+a keyword is assigned to. Such errors may also cause tricky and critical performance issues that are hard to debug.
 Consequently, anomalous values should be flagged and a warning returned
@@
 
-We now describe the technique we use to detect anomalous values for 
+We now describe a technique that we plan to 
+explore to detect anomalous values for 
 numerical attributes. Let $A$ be the set of attributes contained in the 
@@
 median absolute deviation. 
-This is a variant of a standard outlier detection test, namely the Hampel identifier.\footnote{Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation 
-for a normal distribution.} 
+This is a variant of a standard outlier detection test, namely the Hampel identifier. (Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation 
+for a normal distribution.) 
 In the checking phase, as long as the checker finds a value for a numerical 

### 2016-11-13 Ennan-Proposal/travis.tex
config: small tweak
intro, with news

@@
 incorrect, thus making \app more general and practical.
-We show in Sec~\ref{sec:correctExten} how adding set of known correct files to 
-the learning process can improve the false positive rate.
-In fact, we occasionally have a training set labelled as both correct and incorrect files.
+%We show in Sec~\ref{sec:correctExten} how adding set of known correct files to 
+%the learning process can improve the false positive rate.
+In fact, we occasionally have a training set labeled as both correct and incorrect files.
 Furthermore, such a training set may have more embedded information that can be leveraged, such as temporal structure.

### 2016-11-13 Ennan-Proposal/travis.tex
intro, with news

@@
-\section{Extending \app Via Version Space Learning}
+\section{Extending \app and Applying it to Real-World Configurations}
 \label{sec:travis}
 
-The current design of \app does not have any assumptions on whether the
-configuration files in the training sets are correct or 
-incorrect, thus making \app more general and practical.
-%We show in Sec~\ref{sec:correctExten} how adding set of known correct files to 
-%the learning process can improve the false positive rate.
-In fact, we occasionally have a training set labeled as both correct and incorrect files.
-Furthermore, such a training set may have more embedded information that can be leveraged, such as temporal structure.
-Temporal structure in training sets is available when code has a change history, such as in version control.
-
-One such example of such a training set of configuration files is TravisCI~\cite{API}.
-TravisCI, a popular integration and build testing service connected to Github.
+TravisCI~\cite{API} is a popular integration and build testing service 
+connected to Github. It has been used on more than 17 
+millions of projects. 
 TravisCI allows programmers to automatically run their test suite on a fresh virtual machine every time they commit their code.
@@
 
-TravisCI misconfigurations are important to fix because of the developer time cost. 
-In addition to being time consuming to fix, a misconfiguration can cause a test suite to run up to 20 mins, only to report a misconfiguration~\cite{API}.
+TravisCI misconfigurations are important to detect and correct 
+because of any failed compilation can costs developer significant amount 
+of time. A misconfiguration can cause a test suite to run up to 20 
+minutes, only to report a misconfiguration~\cite{API}.
 The developer will need to wait to get such a report back to begin even identifying the error.
+
+A new challenge here is that we need to reason about a 
+temporal component too. Having an entire TravisCI log for a given
+project we can examine the sequence of changes of a configuration file
+and we can detect what has changed so that we switched from a failing 
+compilation to successful compilation.
 
@@
 classification~\cite{mitchell77}, which we use to test a configuration file for membership
-in the set of all correct files~.
-Traditional version space learning builds a model that tests membership
-using a series of disjunctions from a set of predefined hypotheses.
-Here we will instead use a conjunctions to convey that a configuration file must meet the learned criteria.
+in the set of all correct files.
+Traditionally, version space learning builds a model that defines membership using a series of disjunctions from a set of predefined hypotheses.
+However, we need  to use conjunctions to convey that a configuration file is only correct if it satisfies all the learned relations, as
+
+\begin{figure}[!tbh]
+  \centering
+  \begin{tikzpicture}
+    \draw (2,0) rectangle (6,2); \draw (2.5,0.5) rectangle (5.5,1.5);
+  \end{tikzpicture}
+  \caption{System architecture of }
+  \label{fig:screenshot1}
+\end{figure}
+
+ Adding this temporal component, 
 This extension will build a logical formula representing the entire 

### 2016-11-13 Ennan-Proposal/related.tex
intro, with news

@@
 
-Verification support to configuration files 
-has been considered a promising way  
-to tackle misconfiguration problems~\cite{xu15systems}.
-Nevertheless, a practical misconfiguration
-verification approach still remains an open problem.
+We now position our work to already existing work. Most of the 
+work falls into, what is traditionally considered, system's research.
 
@@
 
-Huang {\em et al.} proposed a specification for configuration validation%
-~\cite{huang15confvalley}. We will 
-discuss this work in the misconfiguration
-detection part.
+We previously discussed ConfValley by Huang {\em et al.} proposed a specification for configuration validation%
+~\cite{huang15confvalley}.
 

### 2016-11-13 Ennan-Proposal/travis.tex
intro, with news

@@
 Traditionally, version space learning builds a model that defines membership using a series of disjunctions from a set of predefined hypotheses.
-However, we need  to use conjunctions to convey that a configuration file is only correct if it satisfies all the learned relations, as
+
+We extend the \app's functionality
+
+However, we need  to use conjunctions to convey that a configuration file is only correct if it satisfies all the learned relations, and disjunctions are used to state that it one compile if 
+it satisfies one (or more
 

### 2016-11-13 Ennan-Proposal/related.tex
Grammar

@@
 
-We now position our work to already existing work. Most of the 
-work falls into, what is traditionally considered, system's research.
+We will now compare our work to existing work. Most of this 
+work falls into what is traditionally considered system's research.
 
@@
 Compared with these existing efforts, 
-our work mainly focused on software systems, \eg, MySQL and Apache,
+our work is mainly focused on software systems, \eg, MySQL and Apache,
 rather than network configurations. In addition, we do not need 
@@
 
-We previously discussed ConfValley by Huang {\em et al.} proposed a specification for configuration validation%
+We previously discussed ConfValley by Huang {\em et al.}, which proposed a specification for configuration validation%
 ~\cite{huang15confvalley}.
@@
 Several machine learning-based misconfiguration detection efforts 
-also have been proposed~\cite{yuan11context, zhang14encore}.
+have been proposed~\cite{yuan11context, zhang14encore}.
 EnCore~\cite{zhang14encore} is the work closest to \app.
@@
 The learning process is guided by a set of predefined rule templates
-that enforce learning to focus on patterns of interest.
+that force learning to focus on patterns of interest.
 In this way, EnCore filters out irrelevant information and reduces
@@
 Finally, \app is a language framework, which can 
-even be used to write configuration files, but EnCore is only a 
+even be used to write configuration files, whereas EnCore is only a 
 misconfiguration detection tool.
@@
 SPEX~\cite{xu13do} takes a white-box testing approach to automatically
-extract configuration parameter constraints from source code and generates 
+extract configuration parameter constraints from source code, and generates 
 misconfigurations to test whether systems can tolerate potential

### 2016-11-13 Ennan-Proposal/solutions.tex
Grammar

@@
 We now describe a formalism how to compute the set of learned
-probabilistic rules, denoted with $\mathcal{PR}$.
+probabilistic rules, denoted by $\mathcal{PR}$.
 With $\mathcal{U}$ we denote a set of configuration files in the 
@@
 Note that this approach differs from a unsupervised learning setting~\cite{hastie2009unsupervised} where the training set is completely unlabeled and seeks to discover some hidden underlying structure.
-Although our set is also unlabeled, we make the assumption that some majority of the training set must be correct for their biggest part.
+Although our set is also unlabeled, we make the assumption that some majority of the training set must be correct.% for their biggest part.
 We are again learning a model which will provide clear justification (error locations) for the classification.
 However, with this approach we will not have the formal guarantees of the ConfigC approach.
-From previous work, we believe this is a worthwhile trade-off in order to decrease the fasle positive rate.
+From previous work, we believe this is a worthwhile trade-off in order to decrease the false positive rate.
 
@@
 
-In addition to checking for correlation, type- or ordering errors, 
+In addition to checking for correlation, type, or ordering errors, 
 the user may also want to examine if there are anomalous values that 
@@
 for a normal distribution.) 
-In the checking phase, as long as the checker finds a value for a numerical 
+In the checking phase, if the checker finds a value for a numerical 
 attribute in the checked file outside of this interval, 

### 2016-11-14 Ennan-Proposal/travis.tex
intro, with news

--- 2016-11-13 Ennan-Proposal/travis.tex
@@
 in the set of all correct files.
-Traditionally, version space learning builds a model that defines membership using a series of disjunctions from a set of predefined hypotheses.
-However, we need  to use conjunctions to convey that a configuration file is only correct if it satisfies all the learned relations, as
+
+We extend the \app's functionality to first learn the rules that have 
+to hold for correct TravisCI configuration files. Traditionally, 
+version space 
+learning builds a model that defines membership using a series of 
+disjunctions from a set of predefined hypotheses.  However, we need  to 
+use conjunctions to convey that a configuration file is only correct if 
+it satisfies all the learned relations. Those rules can be seen as
+positive examples in classifying correct files. In addition, we will have
+so-called {\emph {breaking rules}} which are derived from the files 
+that do not compile, \ie negative examples. Breaking rules are specified 
+using disjunctions.
 

### 2016-11-14 Ennan-Proposal/solutions.tex
stuff

@@
 If a template is instantiated and we obtain rule $r$, with  the predicate 
-$\mathit{holds}(r,f)$ we state that either $\mathit{appears}(r,f)$ holds, or $r$ could not be instantiated with keywords from $f$. With every 
+$\mathit{holds}(r,f)$ we state that either predicate $\mathit{appears}(r,f)$ holds, or 
+$r$ could not be instantiated with keywords from $f$ (namely, rule $r$ is irrelevant 
+for $f$ and then trivially holds). With every 
 rule $r$ we define two sets:

### 2016-11-14 Ennan-Proposal/solutions.tex
stuff

@@
 majority of cases, and $T_2$ is a threshold value for considering rules 
-for which we have at least some examples that that rule is will 
-appear in the files. Finding the exact values of $T_1$ and $T_2$ is 
+for which there is sufficiently enough files where the rule
+appears. Finding the exact values of $T_1$ and $T_2$ is 
 and their connection to $|\mathcal{U}|$

### 2016-11-14 Ennan-Proposal/solutions.tex
clarify thresholds

@@
 We define then set $\mathcal{PR}$ as
-$$\mathcal{PR} = \{\ r \ \mid \ |S_A(r)| > T_1 \land |S_H(r)| > T_2 \ \} $$
-where $T_1$ is a threshold value for considering rules which are true in 
-majority of cases, and $T_2$ is a threshold value for considering rules 
-for which there is sufficiently enough files where the rule
-appears. Finding the exact values of $T_1$ and $T_2$ is 
+$$\mathcal{PR} = \{\ r \ \mid \ |S_A(r)| > T_1 \land |S_H(r)|/|\mathcal{U}| > T_2 \ \} $$
+We use $T_1$ to act as an integer threshold value so any accepted rule must appear in sufficiently enough files where the rule appears. 
+We use $T_2$ to act as a percentage threshold value so that any accepted rule must be true in a majority of cases. 
+Finding the exact values of $T_1$ and $T_2$
 and their connection to $|\mathcal{U}|$

### 2016-11-14 Ennan-Proposal/travis.tex
stuff

@@
 
-TravisCI misconfigurations are important to detect and correct 
-because of any failed compilation can costs developer significant amount 
+TravisCI misconfigurations are important to detect and correct before execution,
+because any failed compilation can costs developer significant amount 
 of time. A misconfiguration can cause a test suite to run up to 20 
-minutes, only to report a misconfiguration~\cite{API}.
-The developer will need to wait to get such a report back to begin even identifying the error.
+minutes, only to report that the whole computation failed~\cite{API}.
+If developer would have this information prior to the compilation attempt, they could
+ identifying and correct potential misconfigurations.
 
@@
 
-Version space learning builds a logical constraint model for binary
-classification~\cite{mitchell77}, which we use to test a configuration file for membership
-in the set of all correct files.
+We plan to use version space learning and SMT solvers to detect errors in 
+TravisCI configurations files. Version space learning 
+builds a logical constraint model for binary
+classification~\cite{mitchell77}, which we use to test a configuration file for 
+membership in the set of all correct files.
 
-We extend the \app's functionality to first learn the rules that have 
+Figure~\ref{fig:versionSL} outlines our proposed approach. We first apply the standard \app's approach to learn the rules that have 
 to hold for correct TravisCI configuration files. Traditionally, 
-version space 
-learning builds a model that defines membership using a series of 
+version space learning builds a model that defines membership using a series of 
 disjunctions from a set of predefined hypotheses.  However, we need  to 
@@
   \begin{tikzpicture}
+   \draw[help lines]
     \draw (2,0) rectangle (6,2); \draw (2.5,0.5) rectangle (5.5,1.5);
@@
   \caption{System architecture of }
-  \label{fig:screenshot1}
+  \label{fig:versionSL}
 \end{figure}
+
+Necessary = 
+ { Keyword, value pair "language:node_js" requires Keyword "node_js"}
+
+where keyword "node_js" sets a version value (e.g. "node_js: 0.8")
+
+Breaking =
+  { Keyword "node_js" cannot have value <= 0 }
 

### 2016-11-14 Ennan-Proposal/travis.tex
intro, with news
autocommit

@@
   \begin{tikzpicture}
-   \draw[help lines]
-    \draw (2,0) rectangle (6,2); \draw (2.5,0.5) rectangle (5.5,1.5);
+    \draw (0,0) rectangle (9,4); 
+    \node [align=left] at (1.5,3.5) {Breaking Rules: \\ \footnotesize ``node\_js $\le$ 0''};
+    \draw (4,1) rectangle (8,3);
+    \node [align=left] at (5.6,2.2) {Necessary Rules: \\ \footnotesize ``language:node\_js \\ \footnotesize $\ \land$ node\_js:version''};
   \end{tikzpicture}
-  \caption{System architecture of }
+  \caption{An example set of necessary and breaking rules.}
   \label{fig:versionSL}
 \end{figure}
-
-Necessary = 
- { Keyword, value pair "language:node_js" requires Keyword "node_js"}
-
-where keyword "node_js" sets a version value (e.g. "node_js: 0.8")
-
-Breaking =
-  { Keyword "node_js" cannot have value <= 0 }
 

### 2016-11-14 Ennan-Proposal/travis.tex
autocommit

--- 2016-11-14 Ennan-Proposal/travis.tex
@@
 so-called {\emph {breaking rules}} which are derived from the files 
-that do not compile, \ie negative examples. Breaking rules are specified 
+that do not compile, \ie~negative examples. Breaking rules are specified 
 using disjunctions.
@@
   \begin{tikzpicture}
-   \draw[help lines]
-    \draw (2,0) rectangle (6,2); \draw (2.5,0.5) rectangle (5.5,1.5);
+    \draw (0,0) rectangle (6,4); 
+    \node [align=left] at (1.5,3.2) {\footnotesize \textbf{Breaking Rules}: \\ \footnotesize node\_js $\le$ 0 \\ \footnotesize \ldots};
+    \draw (1.5,0.2) rectangle (5,2.2);
+    \node [align=left] at (3,1.3) {\footnotesize \textbf{Necessary Rules}: \\ \footnotesize node\_js $\ge$ 0.4 \\ \footnotesize \ldots};
   \end{tikzpicture}
-  \caption{System architecture of }
+  \caption{An example set of necessary and breaking rules if we have seen a failing file with {\footnotesize node\_js: 0}, and a passing file with {\footnotesize node\_js: 0.4.}}
   \label{fig:versionSL}
 \end{figure}
-
-Necessary = 
- { Keyword, value pair "language:node_js" requires Keyword "node_js"}
-
-where keyword "node_js" sets a version value (e.g. "node_js: 0.8")
-
-Breaking =
-  { Keyword "node_js" cannot have value <= 0 }
 

### 2016-11-14 Ennan-Proposal/travis.tex
autocommit

@@
   \begin{tikzpicture}
-    \draw (0,0) rectangle (6,4); 
-    \node [align=left] at (1.5,3.2) {\footnotesize \textbf{Breaking Rules}: \\ \footnotesize node\_js $\le$ 0 \\ \footnotesize \ldots};
-    \draw (1.5,0.2) rectangle (5,2.2);
-    \node [align=left] at (3,1.3) {\footnotesize \textbf{Necessary Rules}: \\ \footnotesize node\_js $\ge$ 0.4 \\ \footnotesize \ldots};
+    \draw (0,0) rectangle (6,3.7); 
+    \node [align=left] at (1.5,2.9) {\footnotesize \textbf{Breaking Rules}: \\ \footnotesize node\_js $\le$ 0 \\ \footnotesize \ldots};
+    \draw (1.6,0.2) rectangle (5,2.2);
+    \node [align=left] at (3.3,1.3) {\footnotesize \textbf{Necessary Rules}: \\ \footnotesize node\_js $\ge$ 0.4 \\ \footnotesize \ldots};
   \end{tikzpicture}

### 2016-11-14 Ennan-Proposal/travis.tex
autocommit

@@
 
+The breaking rules will describe the conditions for an incorrect file based on examples we have seen of incorrect files.
+Likewise, the necessary rules will describe the conditions for a correct file based on examples we have seen of correct files.
+As shown in Figure~\ref{fig:versionSL}, this can result in a space where a file may contain relations that cannot be classified as either breaking or necessary.
+Part of the research task will be to find an optimal treatment for such cases.
+
 \begin{figure}[!tbh]
@@
   \begin{tikzpicture}
-    \draw (0,0) rectangle (6,3.7); 
+    \draw (0,0) rectangle (7,3.7); 
     \node [align=left] at (1.5,2.9) {\footnotesize \textbf{Breaking Rules}: \\ \footnotesize node\_js $\le$ 0 \\ \footnotesize \ldots};
-    \draw (1.6,0.2) rectangle (5,2.2);
-    \node [align=left] at (3.3,1.3) {\footnotesize \textbf{Necessary Rules}: \\ \footnotesize node\_js $\ge$ 0.4 \\ \footnotesize \ldots};
+    \draw (2.3,0.2) rectangle (6.2,2.2);
+    \node [align=left] at (3.9,1.4) {\footnotesize \textbf{Necessary Rules}: \\ \footnotesize node\_js $\ge$ 0.4 \\ \footnotesize \ldots};
   \end{tikzpicture}

### 2016-11-14 Ennan-Proposal/prior.tex
stuff

\section{Prior Results from the NSF Support}

The PI received NSF CAREER Award for synthesis in live programming environment
(CCF-1553168 ). In addition, the PI was the publicity chair or the organizer of various
conferences and summer school and she received three grants to support students' visit 
to those venues. The most relevant NSF support for this proposal is the
NSF award ``SHF: Medium: Collaborative Research: FRP for Real'',
(CCF-1302327); \$866,000 (10/01/13-09/30/17), which the PI overtook  from 
Paul Hudak, due to his untimely death. Intellectual Merit: The
proposed work will contribute to a better understanding of declarative models
of time and interaction. Broader Impacts: The proposed work will further broaden
the applicability of FRP, improving implementation making FRP more suitable for
compute-intensive applications, such as interactive 3D graphics and real-time audio
processing. As the part of that grant we also developed and published ConfigC
(acknowledgments to the grant were given). Publications: M. Santolucito, 
E. Zhai, R. Piskac: ``Probabilistic Automated Language Learning for Configuration Files''
(July 2016), CAV 2016, Pages 80-87, DOI: 10.1007/978-3-319-41540-6\_5.

### 2016-11-14 Ennan-Proposal/impact.tex
stuff

@@
 \section{Broader Impact}
+
+Since her beginning of teaching at Yale, the PI is actively including topics from her 
+research into her courses (such as ``Software Analysis and Verification''). This way
+she motivates undergraduate student to get involved in the research. Until this day 
+she supervised 29 undergraduate student projects. Two students (Reinking, Cai) 
+who did an undergraduate research projects with her are now PhD students at 
+UC Berkeley, and two more students are applying (Anklessaria, La) to graduate schools 
+this year.
 

### 2016-11-14 Ennan-Proposal/intro.tex
add intro from pdf

Configuration errors (i.e., misconfigurations) have become one of the major causes of software failures, resulting in security vulnerabilities, application outages, and incorrect program executions [9, 10]. 
For example, Yin et al. [10] reported that configuration errors were the dominant failure cause in storage systems, while Rabkin and Katz [3] revealed misconfigurations were the main cause of Hadoop cluster failures. 
Although many techniques have been proposed to automate configuration error diagnosis and analysis [6, 1, 5, 7], these approaches heavily rely on manual efforts to understand the failure symptoms, which is hard, since the structures and logics in configuration files are very tricky and implicit [10, 11]. 
On the other hand, current configuration correctness checkers [11, 12] and validation schemes [2] require the users to explicitly define rules and constraints to check, which is also impractical, because entries in configuration files are hard to understand for users [8].

Based on the above insight, we argue that the fundamental reasons causing configuration files error-prone and making misconfiguration troubleshooting difficult are: 1) entries in configuration files are untyped assignments, 2) there is no explicit structure policy for the entries in configuration files, and 3) there are surprisingly few rules specifying the entries’ constraints. 
In other words, we do not have capabilities of writing, debugging and verifying configuration files like using programming languages. 
Therefore, the language support should be a necessary means of tackling misconfiguration problems in practice.

In this proposal, we propose a language-based framework to verify configuration files. 
The core idea of this framework is to analyze many (most-likely correct) datasets of configuration files and derive rules for building a language model, and then to use the resulting language model to verify new configuration files.

Achieving the above goal, however, requires addressing two challenges. 
First, because the “language” in configuration files is untyped and unstructured, it is difficult to automatically build our language model. 
We address this challenge by splitting the language model generation process into two phases. 
In the first phase, we parse the given dataset containing many configuration files, and transform them into more structured, intermediary representations. 
However, because the type of a variable may not always be fully determined based on a single value, and these given configuration files may not be correct, we introduce probabalistic types for the intermediary representation transformation. 
Namely, rather than giving a variable a single type, we assign each variable a list of types with their probability distributions. 
In the second phase, we use these more structured representations as a training set to learn the rules for building our language model. 
Our approach does not rely on whether the given configuration files are correct or not, since every learned rule has been assigned probability. 
Only when we need to check new files, we only consider rules that have a probability above some threshold.

The second key challenge is the learned rules from correct configuration files may not be enough to check tricky configuration errors related to system context and environments [12]. 
We address this challenge by introducing template-based mechanism, which specifies the possible system context and environment rules, (e.g., system path correlation and file ownership).
Existing efforts in other domains [4] have demonstrated templates for such system context constraints could be automatically generated and can significantly identify context-based errors. 
Thus, we can detect more comprehensive configuration errors violating the learned constraints and template-based constraints in the files given by the user.

A preliminary evaluation based upon our current prototype shows our approach can successfully detect configuration errors in 20 real-world configuration files covering four types of representative misconfigura- tion problems, within an acceptable learning time (≤ 30 seconds) and verification time (≤ 5 seconds).

\paragraph{Intellectual Merit:} This work’s key intellectual contributions are: (1) to design and develop a new framework that can learn a language model from an example set of correct configuration files, and the model is used to verify new configuration files; (2) to propose probabilistic types to assign a confidence distribution over a set of types to a value; (3) to define an interface for describing a verification attribute in a learning context, making it easy to add new rules. 
(4) to introduce a template-based mechanism for checking system environment-aware misconfigurations.

\paragraph{Broader Impact:} If successful, our effort could open the door of language-based configuration verification, could significantly prevent configuration errors without adding any additional burden to users and system developers, could complement post-failure error diagnosis efforts, and could benefit other verification domains, such as network traffic verification.

### 2016-11-14 Ennan-Proposal/intro.tex
autocommit

@@
 For example, Yin et al.
-[10] reported that configuration errors were the dominant failure cause in storage systems, while Rabkin and Katz [3] revealed misconfigurations were the main cause of Hadoop cluster failures.
-Although many techniques have been proposed to automate configuration error diagnosis and analysis [6, 1, 5, 7], these approaches heavily rely on manual efforts to understand the failure symptoms, which is hard, since the structures and logics in configuration files are very tricky and implicit [10, 11].
-On the other hand, current configuration correctness checkers [11, 12] and validation schemes [2] require the users to explicitly define rules and constraints to check, which is also impractical, because entries in configuration files are hard to understand for users [8].
+[10] reported that configuration errors were the dominant failure cause in storage systems, while Rabkin and Katz [3] reported  misconfigurations were the main cause of Hadoop cluster failures.
+Although many techniques have been proposed to automate configuration error diagnosis and analysis [6, 1, 5, 7], these approaches rely heavily on manual efforts to understand the failure symptoms, 
+However, since the structures and logics in configuration files are often subtle and implicit, this is a time consuming and error prone task.
+On the other hand, current configuration correctness checkers and validation schemes require the users to explicitly define rules and constraints to check, which is also impractical, because entries in configuration files can be hard to understand for users.
 
-Based on the above insight, we argue that the fundamental reasons causing configuration files error-prone and making misconfiguration troubleshooting difficult are: 1) entries in configuration files are untyped assignments, 2) there is no explicit structure policy for the entries in configuration files, and 3) there are surprisingly few rules specifying the entries’ constraints.
-In other words, we do not have capabilities of writing, debugging and verifying configuration files like using programming languages. 
+Based on the above insight, we argue that the fundamental reasons causing configuration files error-prone and making misconfiguration troubleshooting difficult are: 
+  1) entries in configuration files are untyped assignments, 
+  2) there is no explicit structure policy for the entries in configuration files, and 
+  3) there are surprisingly few rules specifying any constraints on configuration entries. 
+Because of these characteristics, configuration files cannot leverage existing research for writing, debugging and verifying configuration files like using programming languages. 
 Therefore, the language support should be a necessary means of tackling misconfiguration problems in practice.

### 2016-11-14 Ennan-Proposal/impact.tex

--- 2016-11-12 Ennan-Proposal/impact.tex
@@
 \section{Broader Impact}
+
+Since her beginning of teaching at Yale, the PI is actively including topics from her 
+research into her courses (such as ``Software Analysis and Verification''). This way
+she motivates undergraduate students to get involved in the research. Until now 
+she supervised more than 20 undergraduate student projects. Two students (Reinking, Cai) 
+who did an undergraduate research projects with her, are now PhD students at 
+UC Berkeley, and two more students are applying (Anklessaria, La) to graduate schools 
+this year. Additionally, there are two student startups, which are now supported
+by YCombinator, that started under her supervision. Those startup are PatientBank
+and Py, an app for learning Python. Some
+
+The PI will continue to involve the undergraduate student into 
+this project as well, spreading this way the project ideas to a broader community.
+In addition, we plan to disseminate the results via publications and giving talks 
+to the communities of PL/Verification researchers and System researchers.
 

### 2016-11-14 Ennan-Proposal/figs/version.tex
autocommit

--- 2016-11-14 Ennan-Proposal/travis.tex
@@
-\section{Extending \app and Applying it to Real-World Configurations}
-\label{sec:travis}
-
-TravisCI~\cite{API} is a popular integration and build testing service 
-connected to Github. It has been used on more than 17 
-millions of projects. 
-TravisCI allows programmers to automatically run their test suite on a fresh virtual machine every time they commit their code.
-A TravisCI user must add a configuration file to the repository that specifies build conditions, 
-such as which dependencies are required, and a set of benchmarks to test. 
-The results of these tests (indicating either passing, failing, or misconfiguration) 
-are saved by TravisCI on a publicly available database~\cite{API}.
-
-TravisCI misconfigurations are important to detect and correct before execution,
-because any failed compilation can costs developer significant amount 
-of time. A misconfiguration can cause a test suite to run up to 20 
-minutes, only to report that the whole computation failed~\cite{API}.
-If developer would have this information prior to the compilation attempt, they could
- identifying and correct potential misconfigurations.
-
-A new challenge here is that we need to reason about a 
-temporal component too. Having an entire TravisCI log for a given
-project we can examine the sequence of changes of a configuration file
-and we can detect what has changed so that we switched from a failing 
-compilation to successful compilation.
-
-%Driven by the above motivating example, we propose an extension to \app that
-%learns over a training set with both correct and incorrect examples, as well as a temporal structure.
-%Such an extension employs an existing technique from the machine learning community, called version space learning,
-%to significantly decrease the false positive rate while maintaining the detection capability of \app.
-
-\subsection{Version Space Learning with Temporal Properties}
-
-We plan to use version space learning and SMT solvers to detect errors in 
-TravisCI configurations files. Version space learning 
-builds a logical constraint model for binary
-classification~\cite{mitchell77}, which we use to test a configuration file for 
-membership in the set of all correct files.
-
-Figure~\ref{fig:versionSL} outlines our proposed approach. We first apply the standard \app's approach to learn the rules that have 
-to hold for correct TravisCI configuration files. Traditionally, 
-version space learning builds a model that defines membership using a series of 
-disjunctions from a set of predefined hypotheses.  However, we need  to 
-use conjunctions to convey that a configuration file is only correct if 
-it satisfies all the learned relations. Those rules can be seen as
-positive examples in classifying correct files. In addition, we will have
-so-called {\emph {breaking rules}} which are derived from the files 
-that do not compile, \ie~negative examples. Breaking rules are specified 
-using disjunctions.
-
 \begin{figure}[!tbh]
@@
 \end{figure}
-
- Adding this temporal component, 
-This extension will build a logical formula representing the entire 
-history of examples, and use an SMT solver to find a classification model.
-
-Since a TravisCI configuration file is dependent
-on the code and system it is trying to build, 
-we must consider a more general sense of configuration file.
-We will call this a program summary $P_t$, which is a representation 
-of the repository which contains the information 
-relevant to the learning process.
-The subscript on $P_t$ is a timestamp tag based on 
-the ordered git commit history.
-%In the case of TravisCI, this include the \verb|.travis.yml| file, 
-%as well as code features that may effect build status, 
-%such as programming language and a list of imported libraries.
-%The summary must be \textit{sufficiently detailed}, that is it must contain every piece of information that might lead to a build error.
-
-%IMPORTANT, but no space
-%However, a git history is not a limited to a single linear timeline.
-%Git features the ability to \textit{branch}, which allows to simultaneous commit chains.
-%To handle the start of a branch, add a superscript to indicate the branch, and restart the counter on a branch.
-%To handle the merge of two branches $P_{t}^{x}$ and $P_{t'}^{y}$, step to $P_{t+1}^{x}$, where $x$ is the mainline branch.
-%We then say that $P_{t'}^{y}$ has no successor commit $P_{t'+1}^{y}$.
-
-From this summary we can then build a model $M(P_t)$, as in \app,
-which is the full set of possible relations derivable 
-from the program summary.
-Again, the user must provide templates for the learning process.
-
-We will denote the build status returned from TravisCI when run on $P_t$ with $S(P_t)$.
-Any files with a $Pass$ build status are correct, and any files with an $Err$ build status are incorrect.
-%In this application, we consider all non-erroring build status to be passing, denoted $Pass$ and otherwise $Err$.
-For brevity, we denote sequences of build statuses with the following notation:
-\begin{align*}
-  S(P_t)=Pass \land S(P_{t+1})=Err \implies S(P_{t,t+1}) = PE
-\end{align*}
-
-We now consider both incorrect and correct files in the training set 
-and so must introduce the \textit{general boundary}.
-The general boundary is the dual of the specific boundary, and is the most relaxed requirement for a positive classification.
-We denoted specific boundary as the set of necessary relations $Nec$, and now denote the general boundary as the set of breaking relations $Br$.
-With this notation, we can formally express the requirement that the program summary is sufficiently detailed.
-\begin{align}
-  \forall S(P_t)=Err, \exists r \in M(P_t), r \in Br \label{eq:E1}
-\end{align}
-
-From the above we know that if a build is erroring, then there must exist at least one error.
-We can also know that if a build is passing, then there must not exist any errors.
-That is, the model of a passing commit must not contain any rules which are breaking.
-Note we are not, however, guaranteed that any rules from a passing commit are necessary.
-\begin{align}
-  S(P_t) = Err \implies \exists r \in  M (P_t), r \in Br \label{eq:E}\\
-  S(P_t) = Pass \implies \forall r \in  M (P_t), r \notin Br \label{eq:P}
-\end{align}
-
-%While Eq. \ref{eq:E} and \ref{eq:P} might build a basic model, they will do not capture all of the available knowledge.
-%The key insight is that 
-Additionally, when we commit a break ($PE$), we can localize the error to one of the relations that changed.
-Either we removed something that was necessary, or added something that was breaking.
-Note that this is an inclusive disjunction, since a erroring commit can break multiple things at once.
-Expressed formally, where $\setminus$ is the set difference, that is:
-\begin{align}
-  S(P_{t,t+1}) &= PE \implies \nonumber \\
-  \exists& r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \nonumber \\
-  \lor \ \exists& r \in (M(P_{t+1}) \setminus M(P_{t})), r \in Br \label{eq:PE}
-\end{align}
-
-We then can combine Eq \ref{eq:E}, \ref{eq:P}, and \ref{eq:PE} with
-conjunctions and ask a SMT solver for a model satisfying the formula.
-The resulting model will be the sets of necessary rules ($Nec$), and the set of breaking rules ($Br$), which can be used to check new configuration files.
-Since we used a similar model to \app, we will still be able to provide justifications for the classification results.

### 2016-11-14 Ennan-Proposal/travis.tex
autocommit

--- 2016-11-14 Ennan-Proposal/travis.tex
@@
 
+\begin{wrapfigure}{l}{0.5\textwidth}
+  \includegraphics[width=0.45\textwidth]{figs/Version_space}
+  \caption{\small Red circles are failing files, and green pluses are passing files.}
+  \label{fig:versionSL}
+\end{wrapfigure}
+
 Figure~\ref{fig:versionSL} outlines our proposed approach. We first apply the standard \app's approach to learn the rules that have 
@@
 
-\begin{figure}[!tbh]
-  \centering
-  \begin{tikzpicture}
-    \draw (0,0) rectangle (6,4); 
-    \node [align=left] at (1.5,3.2) {\footnotesize \textbf{Breaking Rules}: \\ \footnotesize node\_js $\le$ 0 \\ \footnotesize \ldots};
-    \draw (1.5,0.2) rectangle (5,2.2);
-    \node [align=left] at (3,1.3) {\footnotesize \textbf{Necessary Rules}: \\ \footnotesize node\_js $\ge$ 0.4 \\ \footnotesize \ldots};
-  \end{tikzpicture}
-  \caption{An example set of necessary and breaking rules if we have seen a failing file with {\footnotesize node\_js: 0}, and a passing file with {\footnotesize node\_js: 0.4.}}
-  \label{fig:versionSL}
-\end{figure}
+Figure~\ref{fig:versionSL} shows an example set of necessary and breaking rules that would be learn if the training set contains a failing file with {\small node\_js: 0}, and a passing file with {\small node\_js: 0.4.}
+The breaking rules will describe the conditions for an incorrect file based on examples we have seen of incorrect files (red circles).
+Likewise, the necessary rules will describe the conditions for a correct file based on examples we have seen of correct files (green pluses).
+This results in a space (green stripes) where a file may contain relations that cannot be classified as either breaking or necessary.
+Part of the research task will be to find an optimal treatment for such cases.
 

### 2016-11-14 Ennan-Proposal/impact.tex
stuff

@@
 by YCombinator, that started under her supervision. Those startup are PatientBank
-and Py, an app for learning Python. Some
+and Py, an app for learning Python.
 
@@
 
-If successful, \app could have the following broader impacts:
+We believe that \app could have the following broader impacts:
 
@@
 
-\item {\bf Opening the door of language-based configuration verification.}
+\item {\bf Enabling language-based configuration verification.}
   Today's misconfiguration checking approaches are still using {\em ad hoc}
-  algorithms to detect potential misconfiguration root causes. On the
-  contrary, \app could open the door of configuration verification,
-  which rigorously verifies whether the target configuration files meet
-  specifications. In other words, \app enables users 
-  to verify configuration files like verifying programs. Such a capability
-  cannot be offered by any of existing efforts.
-
-\item {\bf Preventing configuration errors without adding any additional
-  burden to users.} Because \app employs automatic machine learning 
-  algorithms to extract rules, users or system administrators do not need
-  to manually write their specifications, which significantly reduce the
-  burden of users and system administrators. Such a way not only
-  makes the configuration verification process become much easier and more 
-  usable, but also decreases the potential issues of writing 
-  specifications.
+  algorithms to detect potential misconfiguration root causes. \app 
+  should enable more rigorous verification of configuration files. By verification we
+  mean checking that the given configuration file adheres to a
+  specification.
+%\item {\bf Preventing configuration errors without adding any additional
+%  burden to users.} Because \app employs automatic machine learning 
+%  algorithms to extract rules, users or system administrators do not need
+%  to manually write their specifications, which significantly reduce the
+%  burden of users and system administrators. Such a way not only
+%  makes the configuration verification process become much easier and more 
+%  usable, but also decreases the potential issues of writing 
+%  specifications.
 
@@
   We call these approaches as post-failure error diagnosis efforts.
-  On the contrary, \app offers a pre-failure error checking effort,
+  \app will offer a pre-failure error checking
   which could be looked as a preliminary checking before installing

### 2016-11-14 Ennan-Proposal/travis.tex
stuff

@@
 
-Figure~\ref{fig:versionSL} outlines our proposed approach. We first apply the standard \app's approach to learn the rules that have 
+Figure~\ref{fig:versionSL} outlines our proposed approach. We first apply the standard ConfigC approach to learn the rules that have 
 to hold for correct TravisCI configuration files. Traditionally, 
@@
 
-Figure~\ref{fig:versionSL} shows an example set of necessary and breaking rules that would be learn if the training set contains a failing file with {\small node\_js: 0}, and a passing file with {\small node\_js: 0.4.}
-The breaking rules will describe the conditions for an incorrect file based on examples we have seen of incorrect files (red circles).
-Likewise, the necessary rules will describe the conditions for a correct file based on examples we have seen of correct files (green pluses).
+Figure~\ref{fig:versionSL} shows an example set of necessary and breaking rules that would be learned if the training set contains a failing file indicating that 
+{\small node\_js} version is 0.2, and a passing file has its version set to 0.4.
+With red dots we depict incorrect files that do not compile, and the green crosses show correct files.
+From both types of files, we extract breaking and necessary rules, which define borders between those two sets of files.
 This results in a space (green stripes) where a file may contain relations that cannot be classified as either breaking or necessary.
-Part of the research task will be to find an optimal treatment for such cases.
+For example, if a user provides a file which specifies version 0.3 of {\small node\_js}, this file will fall in the green striped space.
+Part of the research task will be to find an optimal classification for such cases.
 
- Adding this temporal component, 
-This extension will build a logical formula representing the entire 
-history of examples, and use an SMT solver to find a classification model.
-
-Since a TravisCI configuration file is dependent
-on the code and system it is trying to build, 
-we must consider a more general sense of configuration file.
-We will call this a program summary $P_t$, which is a representation 
-of the repository which contains the information 
+The success or failure of a TravisCI configuration file is dependent
+not only on the configuration file itself (namely, a .travis.yml file) but it also depends on system information such as programming languages and a list of imported libraries.
+For this reason, we call this extended configuration files a program summary, denoted with $P_t$. This is a representation 
+of the repository which contains any information 
 relevant to the learning process.

### 2016-11-14 Ennan-Proposal/intro.tex
autocommit

@@
-Configuration errors (i.e., misconfigurations) have become one of the major causes of software failures, resulting in security vulnerabilities, application outages, and incorrect program executions [9, 10].
-For example, Yin et al.
-[10] reported that configuration errors were the dominant failure cause in storage systems, while Rabkin and Katz [3] reported  misconfigurations were the main cause of Hadoop cluster failures.
-Although many techniques have been proposed to automate configuration error diagnosis and analysis [6, 1, 5, 7], these approaches rely heavily on manual efforts to understand the failure symptoms, 
+Configuration errors (i.e., misconfigurations) have become one of the major causes of software failures, resulting in security vulnerabilities, application outages, and incorrect program executions. 
+Configuration errors accounted for the largest portion of failures in storage systems in a 2014 industry survey, and misconfigurations were also independently reported as the main cause of Hadoop cluster failures.
+Although many techniques have been proposed to automate configuration error diagnosis and analysis, these approaches rely heavily on manual effort to understand the failure symptoms. 
 However, since the structures and logics in configuration files are often subtle and implicit, this is a time consuming and error prone task.
-On the other hand, current configuration correctness checkers and validation schemes require the users to explicitly define rules and constraints to check, which is also impractical, because entries in configuration files can be hard to understand for users.
+On the other hand, current configuration correctness checkers and validation schemes require the users to explicitly define rules and constraints to check.
+Unfortunately, this approach is also impractical because entries in configuration files can be hard cryptic and under documented for end users.
 
@@
   3) there are surprisingly few rules specifying any constraints on configuration entries.
-Because of these characteristics, configuration files cannot leverage existing research for writing, debugging and verifying configuration files like using programming languages. 
-Therefore, the language support should be a necessary means of tackling misconfiguration problems in practice.
+Because of these unique difficulties, configuration files cannot leverage existing techniques for writing, debugging and verifying files as used in programming languages. 
+Therefore, the language support is a necessary means of tackling misconfiguration problems in practice.
 
@@
 Achieving the above goal, however, requires addressing two challenges. 
-First, because the “language” in configuration files is untyped and unstructured, it is difficult to automatically build our language model. 
+First, because the configuration files are untyped and unstructured, it is difficult to automatically learn a language model to be used in verification of a user's file.
 We address this challenge by splitting the language model generation process into two phases. 
 In the first phase, we parse the given dataset containing many configuration files, and transform them into more structured, intermediary representations. 
-However, because the type of a variable may not always be fully determined based on a single value, and these given configuration files may not be correct, we introduce probabalistic types for the intermediary representation transformation.
+However, because the type of a variable may not always be fully determined based on a single value, and these given configuration files may not be correct, we introduce probabilistic types for the intermediary representation transformation.
 Namely, rather than giving a variable a single type, we assign each variable a list of types with their probability distributions. 
@@
 The second key challenge is the learned rules from correct configuration files may not be enough to check tricky configuration errors related to system context and environments [12]. 
-We address this challenge by introducing template-based mechanism, which specifies the possible system context and environment rules, (e.g., system path correlation and file ownership).
-Existing efforts in other domains [4] have demonstrated templates for such system context constraints could be automatically generated and can significantly identify context-based errors. 
+We address this challenge by introducing a template-based mechanism, which specifies the possible system context and environment rules, (e.g., system path correlation and file ownership).
+Existing efforts in other domains [4] have demonstrated templates for such system context constraints can be automatically generated and can significantly identify context-based errors.
 Thus, we can detect more comprehensive configuration errors violating the learned constraints and template-based constraints in the files given by the user.
 
-A preliminary evaluation based upon our current prototype shows our approach can successfully detect configuration errors in 20 real-world configuration files covering four types of representative misconfigura- tion problems, within an acceptable learning time (≤ 30 seconds) and verification time (≤ 5 seconds).
+A preliminary evaluation based upon our current prototype shows our approach can successfully detect configuration errors in 20 real-world configuration files covering four types of representative misconfiguration problems, within an acceptable learning time (≤ 30 seconds) and verification time ($\le$ 5 seconds).
 
-\paragraph{Intellectual Merit:} This work’s key intellectual contributions are: (1) to design and develop a new framework that can learn a language model from an example set of correct configuration files, and the model is used to verify new configuration files; (2) to propose probabilistic types to assign a confidence distribution over a set of types to a value; (3) to define an interface for describing a verification attribute in a learning context, making it easy to add new rules.
+\paragraph{Intellectual Merit:} This work’s key intellectual contributions are: 
+   (1) to design and develop a new framework that can learn a language model from an example set of correct configuration files, and the model is used to verify new configuration files;
+   (2) to propose probabilistic types to assign a confidence distribution over a set of types to a value; 
+   (3) to define an interface for describing a verification attribute in a learning context, making it easy to add new rules.
    (4) to introduce a template-based mechanism for checking system environment-aware misconfigurations.
 
-\paragraph{Broader Impact:} If successful, our effort could open the door of language-based configuration verification, could significantly prevent configuration errors without adding any additional burden to users and system developers, could complement post-failure error diagnosis efforts, and could benefit other verification domains, such as network traffic verification.
+\paragraph{Broader Impact:} This work will open the door for language-based configuration verification, which could significantly prevent configuration errors without adding any additional burden to users and system developers.
+It would complement existing post-failure error diagnosis efforts, and could benefit other verification domains, such as network traffic verification.

### 2016-11-14 Ennan-Proposal/intro.tex
autocommit

@@
 Configuration errors accounted for the largest portion of failures in storage systems in a 2014 industry survey, and misconfigurations were also independently reported as the main cause of Hadoop cluster failures.
-Although many techniques have been proposed to automate configuration error diagnosis and analysis, these approaches rely heavily on manual effort to understand the failure symptoms. 
-However, since the structures and logics in configuration files are often subtle and implicit, this is a time consuming and error prone task.
-On the other hand, current configuration correctness checkers and validation schemes require the users to explicitly define rules and constraints to check.
-Unfortunately, this approach is also impractical because entries in configuration files can be hard cryptic and under documented for end users.
+Although many techniques have been proposed to automate configuration error detection, these approaches rely heavily on manual efforts. 
+Since the dependencies and constraints in configuration files are often subtle and implicit, this is a time consuming and error prone task to do by hand.
+Current configuration verification tools require the users to explicitly define constraints, and equally onerous task.
 
-Based on the above insight, we argue that the fundamental reasons causing configuration files error-prone and making misconfiguration troubleshooting difficult are: 
-  1) entries in configuration files are untyped assignments, 
+We identify the following fundamental reasons that configuration files are error-prone and troubleshooting is difficult. 
+  1) entries in configuration files are untyped, 
   2) there is no explicit structure policy for the entries in configuration files, and 
-  3) there are surprisingly few rules specifying any constraints on configuration entries.
-Because of these unique difficulties, configuration files cannot leverage existing techniques for writing, debugging and verifying files as used in programming languages. 
-Therefore, the language support is a necessary means of tackling misconfiguration problems in practice.
+  3) there are little to no existing constraints, or even documentation on configuration entries.
+Because of these unique characteristics of configuration files, we cannot directly leverage existing techniques for verification as used in programming languages. 
+In this proposal, we address each of these issues individually through a new verification framework.
+The core idea is to analyze many examples of configuration files from widely available datasets and derive a language model (a set of constraints) that can be used to verify new configuration files.
 
-In this proposal, we propose a language-based framework to verify configuration files. 
-The core idea of this framework is to analyze many (most-likely correct) datasets of configuration files and derive rules for building a language model, and then to use the resulting language model to verify new configuration files.
+In our previous work we learned constraints for configuration files based on a dataset correct files.
+This dataset was difficult to curate, as it required manual verification by a domain expert on every file.
+Instead, in this work, we propose to learn over a dataset of configuration files where we only know that most are correct.
+To make curation of these datasets as easy as possible, we do not even require that the files are labelled as correct or incorrect.
 
-Achieving the above goal, however, requires addressing two challenges. 
-First, because the configuration files are untyped and unstructured, it is difficult to automatically learn a language model to be used in verification of a user's file.
-We address this challenge by splitting the language model generation process into two phases. 
-In the first phase, we parse the given dataset containing many configuration files, and transform them into more structured, intermediary representations. 
-However, because the type of a variable may not always be fully determined based on a single value, and these given configuration files may not be correct, we introduce probabilistic types for the intermediary representation transformation.
-Namely, rather than giving a variable a single type, we assign each variable a list of types with their probability distributions. 
-In the second phase, we use these more structured representations as a training set to learn the rules for building our language model. 
-Our approach does not rely on whether the given configuration files are correct or not, since every learned rule has been assigned probability. 
-Only when we need to check new files, we only consider rules that have a probability above some threshold.
+To handle the unstructured nature of configuration files we split the language model generation process into two phases. 
+In the first phase, we parse the given training dataset of many (possibly incorrect) configuration files and transform the files into a more structured, intermediary representation. 
+Because configuration files are untyped, we introduce probabilistic types for the intermediary representation transformation. 
+Namely, rather than giving a variable a single type, we assign each variable a list of types with their probability distributions based on evidence from the dataset. 
+In the second phase, we use the more structured, intermediate representation to learn the rules for our verification model.
 
-The second key challenge is the learned rules from correct configuration files may not be enough to check tricky configuration errors related to system context and environments [12]. 
+The second key challenge is the learned rules from correct configuration files may not be enough to check tricky configuration errors related to system context and environments. 
 We address this challenge by introducing a template-based mechanism, which specifies the possible system context and environment rules, (e.g., system path correlation and file ownership).
-Existing efforts in other domains [4] have demonstrated templates for such system context constraints can be automatically generated and can significantly identify context-based errors.
+Existing efforts in other domains have demonstrated templates for such system context constraints can be automatically generated and can significantly identify context-based errors.
 Thus, we can detect more comprehensive configuration errors violating the learned constraints and template-based constraints in the files given by the user.

### 2016-11-14 Ennan-Proposal/intro.tex
stuff

@@
-Configuration errors (i.e., misconfigurations) have become one of the major causes of software failures, resulting in security vulnerabilities, application outages, and incorrect program executions. 
-Configuration errors accounted for the largest portion of failures in storage systems in a 2014 industry survey, and misconfigurations were also independently reported as the main cause of Hadoop cluster failures.
-Although many techniques have been proposed to automate configuration error detection, these approaches rely heavily on manual efforts. 
+Configuration errors (also known as misconfigurations) have become one of the major causes of system failures, resulting in security vulnerabilities, application outages, and incorrect program executions.
+Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey.
+Although many techniques have been proposed to automate configuration error detection, these approaches mainly /aaosksadjklsal
+
+rely heavily on manual efforts. 
 Since the dependencies and constraints in configuration files are often subtle and implicit, this is a time consuming and error prone task to do by hand.

### 2016-11-14 Ennan-Proposal/travis.tex
stuff

@@
 
-From this summary we can then build a model $M(P_t)$, as in \app,
-which is the full set of possible relations derivable 
-from the program summary.
-Again, the user must provide templates for the learning process.
+From these summaries we will build a model $M(P_t)$, using the same techniques as in 
+\app. $M(P_t)$ actually is a set of all possible relations derivable 
+from the program summary. As previously, we need to construct templates for the 
+learning process, since the level of specification details depends on them.
 
-We will denote the build status returned from TravisCI when run on $P_t$ with $S(P_t)$.
-Any files with a $Pass$ build status are correct, and any files with an $Err$ build status are incorrect.
-%In this application, we consider all non-erroring build status to be passing, denoted $Pass$ and otherwise $Err$.
-For brevity, we denote sequences of build statuses with the following notation:
+We now outline how we plan to use SMT solvers to find the sets of necessary rules ($Nec$), and the set of breaking rules ($Br$).
+
+Let $S(P_t)$ be the build status returned from TravisCI when run on $P_t$.
+It can be either $Pass$ or $Err$. We define shorthand $S(P_{t,t+1}) = PE$ to 
+state that the program was compiling before and now it does not:
 \begin{align*}
-  S(P_t)=Pass \land S(P_{t+1})=Err \implies S(P_{t,t+1}) = PE
+  S(P_{t,t+1}) = PE :\Leftrightarrow S(P_t)=Pass \land S(P_{t+1})=Err 
 \end{align*}
@@
 
-We then can combine Eq \ref{eq:E}, \ref{eq:P}, and \ref{eq:PE} with
+We then can combine \eqref{eq:E}, \eqref{eq:P}, and  \eqref{eq:PE} with
 conjunctions and ask a SMT solver for a model satisfying the formula.

### 2016-11-14 Ennan-Proposal/travis.tex
stuff

@@
 Let $S(P_t)$ be the build status returned from TravisCI when run on $P_t$.
-It can be either $Pass$ or $Err$. We define shorthand $S(P_{t,t+1}) = PE$ to 
-state that the program was compiling before and now it does not:
+It can be either $Pass$ or $Err$. We define shorthand $S(P_{t,t+1}) = PE$ (also called a break state), to 
+express that the program was compiling before and now it does not:
 \begin{align*}
@@
 
-We now consider both incorrect and correct files in the training set 
-and so must introduce the \textit{general boundary}.
-The general boundary is the dual of the specific boundary, and is the most relaxed requirement for a positive classification.
-We denoted specific boundary as the set of necessary relations $Nec$, and now denote the general boundary as the set of breaking relations $Br$.
-With this notation, we can formally express the requirement that the program summary is sufficiently detailed.
-\begin{align}
-  \forall S(P_t)=Err, \exists r \in M(P_t), r \in Br \label{eq:E1}
-\end{align}
-
-From the above we know that if a build is erroring, then there must exist at least one error.
-We can also know that if a build is passing, then there must not exist any errors.
-That is, the model of a passing commit must not contain any rules which are breaking.
+If executing a TravisCI file fails, then there must exist at least one rule that is
+causing that error. Similarly, if a build is passing, then there must not exist any error.
+That is, the model of a passing commit must not contain any breaking rules.
 Note we are not, however, guaranteed that any rules from a passing commit are necessary.
 \begin{align}
-  S(P_t) = Err \implies \exists r \in  M (P_t), r \in Br \label{eq:E}\\
-  S(P_t) = Pass \implies \forall r \in  M (P_t), r \notin Br \label{eq:P}
+  S(P_t) = Err \Rightarrow \exists r \in  M (P_t), r \in Br \label{eq:E}\\
+  S(P_t) = Pass \Rightarrow \forall r \in  M (P_t), r \notin Br \label{eq:P}
 \end{align}
@@
 \begin{align}
-  S(P_{t,t+1}) &= PE \implies \nonumber \\
+  S(P_{t,t+1}) &= PE \Rightarrow \nonumber \\
   \exists& r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \nonumber \\
@@
 
-We then can combine \eqref{eq:E}, \eqref{eq:P}, and  \eqref{eq:PE} with
-conjunctions and ask a SMT solver for a model satisfying the formula.
-The resulting model will be the sets of necessary rules ($Nec$), and the set of breaking rules ($Br$), which can be used to check new configuration files.
+We then create a conjunction of \eqref{eq:E}, \eqref{eq:P}, and  \eqref{eq:PE} with
+conjunctions and invoke an SMT solver to find a model for that formula.
+The resulting model will define sets of necessary rules ($Nec$), and the set of breaking rules ($Br$), which can be used to check new configuration files.
 Since we used a similar model to \app, we will still be able to provide justifications for the classification results.
+
+We also believe that this approach will work in practice since travis.yml files are relatively small and changes in the files are often at most 1-2 lines.

### 2016-11-14 Ennan-Proposal/figs/overview.tex
autocommit

\section*{Cooperative Programming: Integrating Software Synthesis with the Live Paradigm}
\paragraph{Overview:} Live programming is an emerging paradigm that is promising a vast change in the techniques used to develop modern software. A live programming environment allows a programmer to immediately see the effects of changes to a program on its outputs and effectively eliminates the edit-run-debug cycle that dominates programming workflows today. Our work seeks to develop new synthesis techniques that make use of the real-time feedback loop provided by a live programming environment. We will develop a system that allows a user to track a set of examples and synthesize subroutines to fit that set. When combined with fault localization techniques, programmers will be able to quickly find incorrect sections of code and initiate repairs that leverage information gleaned from the provided examples. While current  development tools provide tangible benefits to programmers skilled enough to use them, we aim to develop an accessible, first-of-its-kind, \textit{cooperative programming} environment that provides feedback in the form of generating representative examples and allowing changes to the code to be made through adjustments to these examples.

\paragraph{Intellectual Merits:} There are several open-ended problems that will be explored as a part of this research. In particular, we will need to:

\begin{itemize}
\item Create novel, real-time algorithms to synthesize code within a live programming environment.
\item Investigate methods to evaluate the quality of an example set and methods to produce high quality example sets for a given program.
\item Build a formal theoretical framework for synthesis in a feedback loop.
\item Integrate these developments in a unified environment for a modern, major programming language - namely, Haskell.
\end{itemize}

\paragraph{Broader Impact:} We believe that cooperative programming environments will increase programmer productivity while simultaneously lowering the barriers for entry for newcomers to computer programming. As we develop the theory behind the techniques needed to realize this environment, the our approach will be informed by the needs of programmers, for whom these systems are ultimately built. We will publish our theoretical developments, open source our code, and maintain the tools we produce to foster community involvement while at the same time visiting universities, industrial labs, and top conferences to gain collaborators and share our work with fellow researchers in the field.

In addition to our proposed theoretical developments, we aim to introduce our environment to novice programmers in secondary educational programs. We have promised support from the Connecticut Computer Science Teachers Association, and we are excited to work with them to build a cooperative programming environment that is approachable and useful to beginner and expert programmers alike.

### 2016-11-14 Ennan-Proposal/intro.tex
autocommit

@@
 Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey. 
-Although many techniques have been proposed to automate configuration error detection, these approaches mainly /aaosksadjklsal
-
-rely heavily on manual efforts. 
-Since the dependencies and constraints in configuration files are often subtle and implicit, this is a time consuming and error prone task to do by hand.
-Current configuration verification tools require the users to explicitly define constraints, and equally onerous task.
-
-We identify the following fundamental reasons that configuration files are error-prone and troubleshooting is difficult. 
-  1) entries in configuration files are untyped, 
-  2) there is no explicit structure policy for the entries in configuration files, and 
-  3) there are little to no existing constraints, or even documentation on configuration entries.
-Because of these unique characteristics of configuration files, we cannot directly leverage existing techniques for verification as used in programming languages. 
-In this proposal, we address each of these issues individually through a new verification framework.
+Although many techniques have been proposed to for configuration error detection, these approaches mainly can only be applied after an error has occurred.
+Tools which detect misconfigurations at compile time often require the user to explicitly define constraints, a time consuming and error prone task.
+We propose a framework to statically verify configuration files based on automatically generated constraints.
 The core idea is to analyze many examples of configuration files from widely available datasets and derive a language model (a set of constraints) that can be used to verify new configuration files.
@@
 
-To handle the unstructured nature of configuration files we split the language model generation process into two phases. 
-In the first phase, we parse the given training dataset of many (possibly incorrect) configuration files and transform the files into a more structured, intermediary representation. 
-Because configuration files are untyped, we introduce probabilistic types for the intermediary representation transformation. 
-Namely, rather than giving a variable a single type, we assign each variable a list of types with their probability distributions based on evidence from the dataset. 
-In the second phase, we use the more structured, intermediate representation to learn the rules for our verification model.
+\paragraph{Intellectual Merits:} There are several open-ended problems that will be explored as a part of this research. In particular, we will need to:
 
-The second key challenge is the learned rules from correct configuration files may not be enough to check tricky configuration errors related to system context and environments. 
-We address this challenge by introducing a template-based mechanism, which specifies the possible system context and environment rules, (e.g., system path correlation and file ownership).
-Existing efforts in other domains have demonstrated templates for such system context constraints can be automatically generated and can significantly identify context-based errors.
-Thus, we can detect more comprehensive configuration errors violating the learned constraints and template-based constraints in the files given by the user.
+\begin{itemize}
+\item Design a new framework that can learn a language model from a only partially correct set of configuration files
+\item Investigate methods to handle the untyped and unstructured nature of configuration files
+\item Find techniques to optimize learning parameters to handle the probabilistic nature of the training set
+\item Develop a modular tool for further work in configuration verification using Haskell
+\end{itemize}
 
-A preliminary evaluation based upon our current prototype shows our approach can successfully detect configuration errors in 20 real-world configuration files covering four types of representative misconfiguration problems, within an acceptable learning time (≤ 30 seconds) and verification time ($\le$ 5 seconds).
-
-\paragraph{Intellectual Merit:} This work’s key intellectual contributions are: 
-   (1) to design and develop a new framework that can learn a language model from an example set of correct configuration files, and the model is used to verify new configuration files;
-   (2) to propose probabilistic types to assign a confidence distribution over a set of types to a value; 
-   (3) to define an interface for describing a verification attribute in a learning context, making it easy to add new rules.
-   (4) to introduce a template-based mechanism for checking system environment-aware misconfigurations.
-
-\paragraph{Broader Impact:} This work will open the door for language-based configuration verification, which could significantly prevent configuration errors without adding any additional burden to users and system developers.
+\paragraph{Broader Impact:} 
+Because configuration files are untyped, unstructured, and mostly undocumented, we are not directly leverage existing techniques for verification as used in programming languages.
+Making progress towards verification in such environments, will open the door for work in other domain which have previously been to noisy to handle with existing techniques.
 It would complement existing post-failure error diagnosis efforts, and could benefit other verification domains, such as network traffic verification. 
+This could significantly reduce large scale system failures without adding any additional burden to users and system developers.

### 2016-11-14 Ennan-Proposal/intro.tex
stuff

@@
+\section*{\app: Automated Verification of Configuration Files}
+\paragraph{Overview:} 
 Configuration errors (also known as misconfigurations) have become one of the major causes of system failures, resulting in security vulnerabilities, application outages, and incorrect program executions.

### 2016-11-14 Ennan-Proposal/intro.tex
autocommit

--- 2016-11-14 Ennan-Proposal/intro.tex
@@
 Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey. 
-Although many techniques have been proposed to for configuration error detection, these approaches mainly can only be applied after an error has occurred.
+Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred.
 Tools which detect misconfigurations at compile time often require the user to explicitly define constraints, a time consuming and error prone task.
-We propose a framework to statically verify configuration files based on automatically generated constraints.
+We propose a framework to statically verify configuration files based on automatically generated constraints that define a correct file.
 The core idea is to analyze many examples of configuration files from widely available datasets and derive a language model (a set of constraints) that can be used to verify new configuration files.
 
-In our previous work we learned constraints for configuration files based on a dataset correct files.
-This dataset was difficult to curate, as it required manual verification by a domain expert on every file.
-Instead, in this work, we propose to learn over a dataset of configuration files where we only know that most are correct.
-To make curation of these datasets as easy as possible, we do not even require that the files are labelled as correct or incorrect.
+There are many datasets of configuration files online, but we only know that most are correct - some may be incorrect.
+These files will be unlabelled so we do not know if a particular file is correct or incorrect.
+Furthermore, both the syntax and semantics of configuration files are notoriously underspecified
+Since we are building a general tool to work with any configuration language, \app must be able to handle probabilistic learning in many dimensions.
 
-\paragraph{Intellectual Merits:} There are several open-ended problems that will be explored as a part of this research. In particular, we will need to:
+\paragraph{Intellectual Merits:} In order to advance the state of the art in configuration verification, we will need to:
 

### 2016-11-14 Ennan-Proposal/impact.tex
stuff

@@
 \item {\bf Complementing post-failure error diagnosis efforts.}
-  There have been many diagnosis and troubleshooting efforts to localizing
+  There have been many diagnosis and troubleshooting efforts to localize
   the root causes of configuration errors after system failures occur.

### 2016-11-14 Ennan-Proposal/intro.tex
stuff

@@
 
-\paragraph{Intellectual Merits:} In order to advance the state of the art in configuration verification, we will need to:
-
+\paragraph{Intellectual Merits:} This work's key intellectual contributions are:
 \begin{itemize}
-\item Design a new framework that can learn a language model from a only partially correct set of configuration files
-\item Investigate methods to handle the untyped and unstructured nature of configuration files
-\item Find techniques to optimize learning parameters to handle the probabilistic nature of the training set
-\item Develop a modular tool for further work in configuration verification using Haskell
+\item A design of a new framework that can learn a language model from an only partially correct set of configuration files
+\item Investigating methods to handle the untyped and unstructured nature of configuration files
+\item Finding techniques to optimize learning parameters to handle the probabilistic nature of the training set
+\item Developing a modular tool for further work in configuration verification
 \end{itemize}

### 2016-11-14 Ennan-Proposal/intro.tex
autocommit

@@
 Configuration errors (also known as misconfigurations) have become one of the major causes of system failures, resulting in security vulnerabilities, application outages, and incorrect program executions.
-Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey. 
-Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred.
+Configuration errors were reported to be the largest fraction of failures in a 2014 industry survey about storage systems. 
+Although many techniques have been proposed for configuration error detection, most of these approaches can only be applied after an error has occurred.
 Tools which detect misconfigurations at compile time often require the user to explicitly define constraints, a time consuming and error prone task.
@@
 \paragraph{Broader Impact:} 
-Because configuration files are untyped, unstructured, and mostly undocumented, we are not directly leverage existing techniques for verification as used in programming languages.
-Making progress towards verification in such environments, will open the door for work in other domain which have previously been to noisy to handle with existing techniques.
+Because configuration files are untyped and unstructured, our work represents a new direction that will complement existing techniques for verification as used in programming languages. 
+Making progress towards verification in such environments, will enable work in other domains which have previously been to noisy to handle with existing techniques.
 It would complement existing post-failure error diagnosis efforts, and could benefit other verification domains, such as network traffic verification. 

### 2016-11-14 Ennan-Proposal/agenda.tex
stuff

@@
-\section{Research Agenda}
+\section{Project Timeline}
 
-The primary work involved in this project
-falls into three broad categories:
-(i) defining a more comprehensive language model,
-(ii) developing new learning algorithms, and
-(iii) developing and evaluating \app
-  in real-world configuration files.
-
-\subsection{Defining A More Comprehensive Language Model}
-
-While we feel our proposed language model to be relatively comprehensive
-to capture many tricky misconfiguration cases,
-we will need to define a better language model to represent more types of
-configuration files. The configuration files of some of software systems, 
-\eg, squid, are not limited to the key-value parameters; thus,
-we need to extend the current language model in order to represent
-the configuration files of these systems.
-In addition, some other types of latent configuration errors 
-have been exposed by recent work~\cite{xu16early}.
-For example, the path parameter in a MySQL configuration file
-has an unknown user account. Such an error cannot be represented in
-our proposed language model. Thus, we need to improve it to capture
-more error types.
-
-\subsection{Proposing New Learning Algorithms}
-
-We are planning to develop new learning algorithm capable of extracting
-rules more accurately and efficiently. We plan to first investigate 
-some existing learning algorithms for learning program rules, \eg,
-Raychev {\em et al.}~\cite{raychev15predicting, raychev16learning},
-and then adapt these algorithms to our scenario, \ie, learning 
-the configuration file rules.
-
-\subsection{Deploying and Evaluating \app In Real-World Services}
-
-The project's third main task is to prototype \app and make \app
-practical to real-world misconfiguration verification,
-thus making \app become a useful tool in practice.
-We plan to evaluate the \app prototype's efficiency, usability, and
-accuracy using a variety of micro- and macrobenchmarks.
-For example, we can evaluate the efficiency and accuracy of 
-each module of \app, thus understanding \app's practicality.
-More importantly, we will use \app to detect real-world configuration
-files~\cite{configdataset}, and then manually check whether \app is able
-to successfully detect potential configuration files.
+The proposed project is supposed to last three years. We have identified three main 
+goals of the project, each of them taking approximately a year:
+\begin{description}
+\item[Language Model] 
+Our language model has to be expressive enough to be able to express and detect 
+many non-trivial misconfiguration cases.
+We will, therefore, need to define a more comprehensive language model (than the one presented).  The configuration files of some of software systems, 
+\eg, squid, are not limited to the keyword-value parameters; thus,
+we need to extend the current language model.
+\item [Learning Algorithms]
+We outlined basic learning algorithms. However, those are just outlines and
+many details are left unspecified.
+As we pointed out, especially in the 
+probabilistic learner case finding the right thresholds will be one of the main tasks.
+We plan to investigate some existing learning algorithms for programs, \eg,
+Raychev {\em et al.}~\cite{raychev15predicting, raychev16learning}. 
+However, the configuration files have a specific structure and directly applying 
+existing rules will not be possible. We will try to adapt some of these algorithms 
+to our problem.
+\item [Real-Wolrd Evaluation]
+Finally, we will implement and evaluate \app on real world misconfigurations.
+In addition to evaluating \app on TravisCI files, during the development process 
+we will empirically  evaluate efficiency, usability, and
+accuracy of \app. We plan to use the existing publicly available dataset of 
+misconfigurations~\cite{configdataset}. The set is large enough to use some parts as a  training data and some parts for evaluation.
+\end{description}

### 2016-11-14 Ennan-Proposal/impact.tex
stuff

@@
 \item {\bf Complementing post-failure error diagnosis efforts.}
-  There have been many diagnosis and troubleshooting efforts to localize
+  There is a number of diagnosis and troubleshooting efforts to localize
   the root causes of configuration errors after system failures occur.
-  We call these approaches as post-failure error diagnosis efforts.
-  \app will offer a pre-failure error checking
-  which could be looked as a preliminary checking before installing
-  systems. Because \app is able to find out many sophisticated 
-  configuration errors, it removes many labors of 
-  the post-failure error diagnosis tools. In addition, the results
-  output by \app could be used as a guidance for all the post-failure
-  error diagnosis approaches, making these approaches more efficient.
+  \app's approach of pre-failure error checking
+  can be seen as a preliminary checking before installing a
+  system. Because \app cab detect many non-trivial
+  configuration errors, it simplifies work for
+  post-failure error diagnosis tools. Additionally, the output results
+  of \app can be used as a guidance for post-failure
+  error diagnosis approaches, making them more efficient.
 

### 2016-11-14 Ennan-Proposal/intro.tex
stuff

--- 2016-11-14 Ennan-Proposal/intro.tex
@@
 Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred.
-Tools which detect misconfigurations at compile time often require the user to explicitly define constraints, a time consuming and error prone task.
-We propose a framework to statically verify configuration files based on automatically generated constraints that define a correct file.
-The core idea is to analyze many examples of configuration files from widely available datasets and derive a language model (a set of constraints) that can be used to verify new configuration files.
+We cannot simply apply techniques that exist for software verification: configuration files mainly consists of sequences of assigning some values to system variables.
+Additionally, there is no formal specification describing properties of configuration files.
 
-There are many datasets of configuration files online, but we only know that most are correct - some may be incorrect.
-These files will be unlabelled so we do not know if a particular file is correct or incorrect.
-Furthermore, both the syntax and semantics of configuration files are notoriously underspecified
-Since we are building a general tool to work with any configuration language, \app must be able to handle probabilistic learning in many dimensions.
+We propose a framework for automated verification of configuration files. We first automatically derive a specification, and the we check if a given configuration 
+file adheres to that specification.
+The main idea is to analyze a large number of configuration files from publicly available datasets and derive a corresponding specification.
+To do that we first develop a language model for configuration files.
+One question we
+need to address is what if there is an error in the given training set. Our proposed framework 
+is general enough that it can still derive a correct specification, under 
+the assumption that the same error does not appear in a significant amount of files.
 

### 2016-11-14 Ennan-Proposal/agenda.tex
stuff

@@
 \item [Learning Algorithms]
-We outlined basic learning algorithms. However, those are just outlines and
-many details are left unspecified.
-As we pointed out, especially in the 
-probabilistic learner case finding the right thresholds will be one of the main tasks.
+We outlined basic learning algorithms. However,
+many details are left unspecified and finding the right thresholds will be one of the main tasks.
 We plan to investigate some existing learning algorithms for programs, \eg,
 Raychev {\em et al.}~\cite{raychev15predicting, raychev16learning}. 
-However, the configuration files have a specific structure and directly applying 
-existing rules will not be possible. We will try to adapt some of these algorithms 
+The configuration files have a specific structure and directly applying 
+existing rules will not be possible. Still we will try to adapt some of these 
+algorithms and ideas
 to our problem.

### 2016-11-14 Ennan-Proposal/impact.tex
stuff

@@
   can be seen as a preliminary checking before installing a
-  system. Because \app cab detect many non-trivial
+  system. Because \app can detect many non-trivial
   configuration errors, it simplifies work for
@@
   Besides software misconfiguration, network community has the same 
-  misconfiguration problems. In particular, many recent service outage 
-  reports exposed network-level configuration error will lead to
-  very critical service outages. \app could be extended to reason about
+  misconfiguration problems. The ideas presented here could be extended to reason about
   network-level configuration errors.

### 2016-11-14 Ennan-Proposal/intro.tex
stuff

@@
 Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred.
-We cannot simply apply techniques that exist for software verification: configuration files mainly consists of sequences of assigning some values to system variables.
-Additionally, there is no formal specification describing properties of configuration files.
 
-We propose a framework for automated verification of configuration files. We first automatically derive a specification, and the we check if a given configuration 
+We propose a framework for automated verification of configuration files. 
+Verifying configuration files is different than verifying standard programs: configuration
+files are missing a program structure, but also a specification. They are written in a
+very low level programming paradigm: they mainly consists of sequences of assignments 
+of some 
+values to system variables. In such framework, writing a specification is complex task, 
+since it is not clear how should the specification look like and which properties should 
+it address. Our framework works as follows: in the pre-processing stage, 
+we first automatically derive a specification. Once we have a specification, 
+we check if a given configuration 
 file adheres to that specification.
-The main idea is to analyze a large number of configuration files from publicly available datasets and derive a corresponding specification.
-To do that we first develop a language model for configuration files.
-One question we
-need to address is what if there is an error in the given training set. Our proposed framework 
+The idea about deriving a specification is to analyze a large number of configuration files from publicly available 
+datasets and recognize patterns and keyword correlations. We derive from those findings 
+a corresponding specification. To do that we first develop a language model for configuration files. One question we 
+need to address is: what if there is an error in the given training set? Our proposed framework 
 is general enough that it can still derive a correct specification, under 
 the assumption that the same error does not appear in a significant amount of files.
+We plan to evaluate our framework on real-world configuration files 
+used in the TravisIC tool.
 
@@
 \paragraph{Broader Impact:} 
-Because configuration files are untyped, unstructured, and mostly undocumented, we are not directly leverage existing techniques for verification as used in programming languages.
-Making progress towards verification in such environments, will open the door for work in other domain which have previously been to noisy to handle with existing techniques.
-It would complement existing post-failure error diagnosis efforts, and could benefit other verification domains, such as network traffic verification. 
-This could significantly reduce large scale system failures without adding any additional burden to users and system developers.
+Our main goal is to help to reduce large scale system failures without adding any additional burden to users and system developers. 
+Making progress towards verification of configuration files, will enable a static analysis of configuration files. This way potentially disastrous errors can be 
+detected before they appear.
+We envision \app to complement already existing post-failure error diagnosis efforts.
+In addition, this work will also benefit other verification domains, such as network traffic verification.

### 2016-11-14 Ennan-Proposal/prior.tex
stuff

@@
-\section{Prior Results from the NSF Support}
+\section{Prior Results from NSF Support}
 
 The PI received NSF CAREER Award for synthesis in live programming environment
-(CCF-1553168 ). In addition, the PI was the publicity chair or the organizer of various
-conferences and summer school and she received three grants to support students' visit 
-to those venues. The most relevant NSF support for this proposal is the
+(CCF-1553168 ). In addition, the PI received some student travel grants to support students' visit 
+to conferences or summer schools. The most relevant NSF support for this proposal is the
 NSF award ``SHF: Medium: Collaborative Research: FRP for Real'',

### 2016-11-14 Ennan-Proposal/language.tex
stuff

@@
 that assertion, and actually our intermediary representation can be seen
-as a new programming paradigm for writing configuration files, but this
-is not the focus of this proposal. Previously, Huang {\em et al.}~\cite{huang15confvalley} proposed a 
+as a new programming language for writing configuration files, but this
+is not the main focus of this proposal. Previously, Huang {\em et al.}~\cite{huang15confvalley} proposed a 
 language, ConfValley, to validate 

### 2016-11-14 Ennan-Proposal/prelim.tex
stuff

@@
 relations. We illustrate how is this done on two fragments of 
-configuration files given in Fig.~\ref{fig:twoFiles}.  When analyzing
-a file, we first assign a type to every 
-keyword. After that we instantiate each type-annotated template with 
-concrete keywords and we save the learned set 
-of rules. For instance, with the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 
+configuration files given in Fig.~\ref{fig:twoFiles}. For simplicity, let us 
+assume that all visible
+keywords are integers. With the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 
 analyzing File\_1, the set of learned rules will contain the following rules:

### 2016-11-14 Ennan-Proposal/intro.tex
stuff

@@
 Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey. 
-Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred.
+Although many techniques have been proposed for a configuration error detection, these approaches mainly can be applied after an error has occurred.
 
@@
 file adheres to that specification.
-The idea about deriving a specification is to analyze a large number of configuration files from publicly available 
-datasets and recognize patterns and keyword correlations. We derive from those findings 
+Deriving a specification is based on analyzing a large number of configuration files from publicly available 
+datasets. We recognize patterns and keyword correlations and from those findings we derive 
 a corresponding specification. To do that we first develop a language model for configuration files. One question we 

### 2016-11-14 Ennan-Proposal/travis.tex
Grammar in Travis

@@
 connected to Github. It has been used on more than 17 
-millions of projects. 
+million projects. 
 TravisCI allows programmers to automatically run their test suite on a fresh virtual machine every time they commit their code.
@@
 minutes, only to report that the whole computation failed~\cite{API}.
-If developer would have this information prior to the compilation attempt, they could
+If a developer had this information prior to the compilation attempt, they could
  identifying and correct potential misconfigurations.
@@
 project we can examine the sequence of changes of a configuration file
-and we can detect what has changed so that we switched from a failing 
+and detect what has changed, so that we switched from a failing 
 compilation to successful compilation.
@@
 
-We then create a conjunction of \eqref{eq:E}, \eqref{eq:P}, and  \eqref{eq:PE} with
-conjunctions and invoke an SMT solver to find a model for that formula.
+We then create a conjunction of \eqref{eq:E}, \eqref{eq:P}, and  \eqref{eq:PE} and invoke an SMT solver to find a model for that formula.
 The resulting model will define sets of necessary rules ($Nec$), and the set of breaking rules ($Br$), which can be used to check new configuration files.

### 2016-11-14 Ennan-Proposal/intro.tex
Grammar

@@
 Verifying configuration files is different than verifying standard programs: configuration
-files are missing a program structure, but also a specification. They are written in a
+files are missing a program structure and a specification. They are written in a
 very low level programming paradigm: they mainly consists of sequences of assignments 
 of some 
-values to system variables. In such framework, writing a specification is complex task, 
-since it is not clear how should the specification look like and which properties should 
+values to system variables. In such a framework, writing a specification is a complex task, 
+since it is not clear what the specification should look like and which properties should 
 it address. Our framework works as follows: in the pre-processing stage, 

### 2017-01-18 code2/src/Convert.hs
keyword coor working properly

@@ -21,8 +21,8 @@ case M.lookup keyword tyMap of
 Just configType -> IRLine{..}
 Nothing -> IRLine{configType = emptyConfigQType,..}-}
 
+-- | Main function of this file - translate configFile to intermediate rep
 
-    -- | Main function of this file - translate configFile to intermediate rep
 -- | If the user wants to give hints to how to parse a config file based on filetype they go here
 convert :: ConfigFile Language -> [IRLine] --[(Keyword,Val)]
 convert (f, t, l) =
@@ -32,8 +32,9 @@ convert (f, t, l) =
     noEmptyAsKV = map seperateVals noEmpty
     noDups = makeUniq l noEmptyAsKV
   in
-    map (\(k,v)-> IRLine{keyword=k,value=v}) noDups -- noEmptyAsKV
-    --noDups
+    --NB replace _ with - in keywords
+    map (\(k,v)-> IRLine{keyword=(T.replace "_" "-" k),value=v}) noDups 
+    
 
 makeUniq :: Language -> [(Keyword,Val)] -> [(Keyword,Val)]
 makeUniq lang ls = case lang of

### 2017-01-18 code2/src/Learners/KeywordCoor.hs

@@ -5,6 +5,7 @@
 module Learners.KeywordCoor where
 
 import Types.IR
+import Types.Common
 import Types.Errors
 import Types.Rules 
 import Types.Countable
@@ -12,6 +13,7 @@ import Types.Countable
 import qualified Types.Rules as R
 
 import qualified Data.Map as M
+import qualified Data.Bits as B
 import           System.Directory
 
 import Learners.Common
@@ -25,35 +27,26 @@ maxFalse = 1
 instance Learnable R.KeywordCoor AntiRule where
 
   buildRelations f = let
+    keyCounts :: M.Map Keyword Int 
+    keyCounts = foldl (\rs ir-> M.insertWith (+) (keyword ir) 1 rs) M.empty f
     --order pairs consistently
     toKC (ir1,ir2) = 
       if keyword ir1 > keyword ir2
       then KeywordCoor (keyword ir1, keyword ir2) 
       else KeywordCoor (keyword ir2, keyword ir1) 
     irPairs = pairs' f
+    -- tot = # times x + # times y
+    totalTimes = embedWith keyCounts $ M.fromList $ embedOnce $ map toKC irPairs 
    in
-     M.fromList $ embedOnce $ map toKC irPairs 
-  
+    totalTimes
+
   merge rs = let 
-      addEvi k rd rs = if 
-          | M.member k rs || M.member (flipped k) rs -> addT rd
-          | hasKey k rs -> addF rd
-          | otherwise -> rd
-      updateExisting newRs sumRs = M.mapWithKey (\k rd -> addEvi k rd newRs) sumRs
-
-      -- if the rule does not have an entry already
-      -- add it
-      addNewR oldRs rs k rd  = 
-        if not $ hasKey k oldRs
-        then M.insert k rd rs
-        else rs
-      addNewRs newRs sumRs = M.foldlWithKey (addNewR sumRs) sumRs newRs
-
-      rsUpdated = foldl (\sumRs newRs -> addNewRs newRs $ updateExisting newRs sumRs) M.empty rs
-      
+      rsAdded = M.unionsWith add rs
+      -- false = total - (true *2) b/c total counted both ks
+      rsWithFalse = M.map (\r -> r{fls=(tot r)-((tru r)*2)}) rsAdded
[…]

### 2017-01-18 code2/src/Learners/TypeErr.hs

@@ -30,9 +30,10 @@ instance Learnable TypeErr QType where
       QType {
          string = fromEnum ((T.length $ T.takeWhile C.isAlpha v) > 1)
         ,path = fromEnum ((T.isInfixOf "/" v) || (T.isInfixOf "." v))
-        ,int = fromEnum (all C.isNumber $T.unpack v)
         ,bool = fromEnum (v == "")--flag keywords have no values
-        ,size = fromEnum ((or $ map (\x-> T.isSuffixOf x v) ["G","g","M","m","K","k"]) && (C.isNumber $ T.head v) ) --TODO are lower case allowed?
+        ,int = fromEnum (all C.isNumber $T.unpack v)
+        ,size = fromEnum ((or $ map (\x-> T.isSuffixOf x v) ["G","g","M","m","K","k"]) && 
+                          (T.length $ T.takeWhile C.isNumber v) == (T.length v -1) ) 
       }
     --NB on takeWhile, types of keywords do not depend on context
     -- this creates a problem with the Chekcer tho...

### 2017-01-18 CAV16/motiv.tex
add paper

--- 2016-05-01 CAV/motiv1.tex
@@
 \section{Motivating Examples}
-\label{sec:motiv}
 
-When writing configuration files, users usually take already existing
-files and modify the files, with little knowledge of the system. 
-The non-expert user can then easily introduce in errors.
-Even worse, the original file may already corrupted and the errors are propagated further. 
-Below we show some real worlds examples of the errors commonly found in configuration files.
-All these examples are extracted from real-world reports%
-~\cite{yin11anempirical,xu15hey}.
-The deep, domain specific knowledge needed to identify these error manually is strong motivation for a tool such as \app.
-
-\para{Example~1: Ordering Errors.} When configuring PHP to run with the
-Apache HTTP Server, the user writes, among others, the following lines:\\
- \texttt{
- \hspace*{3em}extension = mysql.so\\
- \hspace*{3em}...\\
- \hspace*{3em}extension = recode.so}\\
-This file caused the Apache server to fail to start due to a segmentation fault error.
-When using PHP in Apache, the extension ``mysql.so'' depends on ``recode.so'' and the relative ordering of two of them is crucial. 
-\app would inform the user that ``recode.so'' should appear before ``mysql.so'', and return the error:\\
- \texttt{
-ORDERING ERROR: Expected "extension"recode.so"\\
-   BEFORE "extension""mysql.so"
-  }
-
-\para{Example~2: Entry Missing Errors.} If the user wants to use OpenLDAP to enable her directory access
-protocol, she needs to use the password policy overlay. This is usually
-done through the following entries in the OpenLDAP configuration file:\\
-\texttt{
- \hspace*{3em}include schema/ppolicy.schema\\
- \hspace*{3em}overlay ppolicy\\}
-When using the password policy overlay in OpenLDAP, we have to first include the related schema.
-Leaving out the ``include'' statement will cause the failure of 
-this LDAP. Running \app on such a misconfiguration file would return:\\
-\texttt{
-MISSING KEYWORD ERROR: Expected "overlay""ppolicy"\\ 
-in the same file as: "include""schema/ppolicy.schema"}
-
-\para{Example~3: Type Errors.} If the user tries to install MySQL, she first needs to initiate the path for the log information generated by MySQL. 
-A user may put the following code in the MySQL configuration file:\\
-\texttt{
- \hspace*{3em}general\_log = /var/log/mysql/mysql.log\\}
-However, the entry ``general\_log'' should be an integer, not a string.
- In MySQL, there is another entry named ``general\_log\_file'' which is used to specify the log path.  
-After \app analyzes this configuration file, it correctly identifies the error:\\
-\texttt{
-TYPE ERROR: Expected a Int with P=1.0 for "general\_log[mysqld]"
-}
-
-\vspace{-10pt}
-\para{Example~4: Value Correlation Errors.} When configuring PHP on MySQL, the user may write the following lines of entries in both the PHP and MySQL configuration files:\\
-\texttt{
- \hspace*{3em}mysql's config\\
- \hspace*{3em}max\_connections = 300\\
- \hspace*{3em}...\\
- \hspace*{3em}php's config\\
- \hspace*{3em}mysql.max\_persistent = 400\\}
-This could cause MySQL to abort with the error information: ``too many connections''.
-In this case, the ``mysql.max\_persistent'' in PHP should be no larger than the ``max\_connections'' in MySQL configuration file.
-Another rule we have implemented is learning inequality relations between integers.
-Running \app on this combined configuration file would return:
-\texttt{
-INTEGER RELATION ERROR: \\
-Expected "max\_connections">="mysql.max\_persistent"}
-
-\com{
 \begin{figure}[t] \centering
@@
 into five groups: 1) format error; 2) entry missing error; 3) value type
-error; and 4) ordering error
-The examples in Fig.~\ref{fig-example} correspond to the above four
+error; 4) ordering error; and 5) value correlation error.
+The five examples in Fig.~\ref{fig-example} correspond to the above five
 groups, respectively.
-
-}

### 2017-01-18 CAV16/quantum.tex
add paper

--- 2016-02-11 ProbabalisticTypes/quantum.tex
@@
 This idea is closely related to exstentially quantified types.
-
-Here is what we know:
-- When parsing unstructured (plaintext) data, we may not be given, or able to fully determine, the type of a value.
-- We can guess types based on regular expressions over a value.*
-- Guessing a concrete type can be overly restrictive. In ConfigC is prematurely pruning the rule search.
-- By guessing a set of types with probabilities, we can continously update the distribution, and decide on a concrete type later when we have more information.
-
-Here are things we need to know:
-- In ConfigC, we are building probabilistic types, but only operate (i.e.
-build rules) over the component, concrete types.
-Can we also operate over probabilistic types and maintain type safety?
-Fundamentally, we ask "What do we need to add to the simply typed lambda calculus to express probabilistic types?"
-- How is this related to existentially quantified types (another "heterogeneous collection" type). Can/should we use this for an implementation?
-- How is this related to a value-level probabilistic lambda calculus (where probabilities are on value).
-- Does this type system need to be tied to the specific machine learning techniques used in infering types?
-- Can we do inference based on more interesting things than just regular expression (something a bit like **, maybe which types generate better rules)
-- We might also ask, is there any good reason to operate over probabilistic types? What are other situations when we might need/encounter probabilistic types?
-
-*This focuses mostly on using regular expression to infer concrete types. http://people.csail.mit.edu/rishabh/papers/popl16-semantic.pdf
-** http://conf.researchr.org/event/POPL-2016/popl-2016-papers-estimating-types-in-binaries-using-predictive-modeling

### 2017-01-18 CAV16/roadmap.tex
add paper

\section*{Outline}

\begin{itemize}

\item Introduction:

\item Motivating examples: Put two or three misconfiguration
  examples here, and show why they are incorrect.

\item \app Design: 
  \begin{itemize}
  \item Present an architecture of \app with a fig. Briefly describe 
    how it works (step by step).
  \item Detail learner part
  \item Merge
  \item Check 
  \item Limitations
  \end{itemize}

\item Implementation and Evaluation:
  First, briefly describe how we implemented \app.
  Then, show a few results, \eg, benchmark including learning time,
  checking time (with different size of configuration file).
  Case study?  I am not sure.

\end{itemize}

### 2017-01-18 CAV17/secs/intro.tex
add paper

--- 2016-05-10 OSDI/intro.tex
@@
 which are difficult to template in practice, 
-cannot be detected by this way. 
-As an illustration of such an error, consider the entry ordering errors, 
+cannot be detected in this way. 
+As an illustration of such an error, consider entry ordering errors, 
 which happens when some entries are inserted in a wrong order. 
@@
 for general software configurations. \app is based on a collection of powerful learning 
-algorithms, that do not necessarily depend on templates. The learning process takes as input a
- large sample of configuration files. The process is language-agnostic and it works for any type of configuration files, 
-but all of the files in the sample need to be of the same type (such as
+algorithms that do not necessarily depend on templates. The learning process takes as input a
+ large sample of configuration files. The process is language-agnostic and works for any kind of configuration file, 
+but all of the files in the sample need to be of the same kind (such as
 MySQL or HTTPD configuration files).
@@
 in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
-accurate set of rules. The rules, in general, specify which properties do variables need to satisfy. One can see this learning process as a
+accurate set of rules. The rules, in general, specify which properties variables need to satisfy. One can see this learning process as a
 way of deriving  
-a specification for configuration files.  Once there is a specification, we can do a formal verification. With these 
+a specification for configuration files.  Once there is a specification, we can do formal verification. With these 
 rules we can efficiently check the correctness of the configuration files
@@
 In the second phase, \app derives rules and constraints by analyzing
-the intermediate representations.  Every learned rule is annotated with a probability depicting in
-which percentage of the files the rule was seen as correct. We only accept those rules whose 
+the intermediate representations.  Every learned rule is annotated with a probability 
+depicting which percentage of the files the rule was seen as correct. We only accept those rules whose 
 correctness probability is above the given threshold.
 
-Finally, while the learned rules establish correlations between two or more variables, using \app one can also detect whether a
-single variable has an appropriate value assigned to it. We do that by measuring the values, that are typically assigned to that variable 
+Finally, while the learned rules establish correlations between two or more variables, using \app, one can also detect whether a
+single variable has an appropriate value assigned to it. We do that by measuring the values that are typically assigned to that variable 
 and reporting if the current value deviates too much from the recorded values.
@@
 For example, an entry {\tt temp\_dir = 300} assigns to variable {\tt temp\_dir} either a directory named ``300'' or sets the size of that directory to 300 (an integer).
-Some of existing type inference 
+Some existing type inference 
 work would report this is an error, because {\tt temp\_dir} should be assigned
@@
 Rather than assigning only one variable to a single type, 
-we assign several types with their probability distributions. 
+we assign several types over a probability distribution. 
 The entry in the above example might be assigned 
@@
 {\tt \{temp\_dir, 300, [(File, 60\%), (Int, 40\%)]\}}.
-Using the probabilistic types model,
+Using probabilistic types,
 we can generate a more accurate language model,
@@
 \app introduces no additional burden 
-to the users: they can simply use \app to check for errors in their
+to the user: they can simply use \app to check for errors in their
 configuration files. However, they can also easily extend the framework

### 2017-01-19 CAV17/secs/abs.tex
start on fine grained

\begin{abstract}

We verify configuration files.
While previous attempts to learn a model for these highly unstructured files have focused on machine learning, we instead take a probabilistic logic approach.
Probabilistic logic allows us to provide justification for our learning results, giving proof of the verification task.
Because the resulting model has a clear logical structure, as opposed traditional machine learning techniques such as neural nets, we can do further analysis on the model that improves our results.

\end{abstract}

### 2017-01-19 code2/Xinyu.hs

@@ -1,0 +1,219 @@
+{-# LANGUAGE TupleSections #-}
+{-# LANGUAGE FlexibleInstances #-}
+{-# LANGUAGE RecordWildCards #-}
+{-# LANGUAGE OverloadedStrings#-}
+{-# LANGUAGE MultiParamTypeClasses#-}
+{-# LANGUAGE MultiWayIf #-}
+
+module Learners.IntRel where
+
+import Types
+import qualified Data.Text as T
+import qualified Data.Text.IO as T
+import qualified Data.List as L
+import qualified Data.Map as M
+import Data.Maybe
+import Data.Char
+import Data.Tuple
+
+import Debug.Trace
+
+
+-- I haven't found a nice package for SMTLIB format in haskell yet, its out there tho, im sure
+
+instance Attribute (M.Map (Keyword,Keyword)) Formula where
+  -- | this has the problem that order is important
+  --   (foo,bar,==) is different than (bar,foo,==)
+  learn ts =
+    let
+      ts' = pairs $ filter couldBeInt ts
+      rules = foldr (\p rs -> findeqRules p ++ rs) [] ts'
+    in
+      M.fromList rules
+  check rs f =
+    let
+     relevantRules' = M.filterWithKey (\k v->isJust v && hasRuleFor f k) (rs)
+     relevantRules = M.foldrWithKey makeFlips relevantRules' relevantRules'
+     fRules' = learn f :: IntRelMap
+     fRules = M.foldrWithKey makeFlips fRules' fRules'
+     diff = M.differenceWith compRules relevantRules fRules --diff is the rules we should have met, but didnt
+    in
+     if M.null diff then Nothing else Just diff
+
+  -- merge curr new = foldl removeConflicts [] $ L.union curr (traceShow (length curr) new)
+  merge curr new =
+    let
+      u = M.unionWith removeConflicts curr new
+    in u
+
+
+---- newly added for triple pair
+instance Attribute (M.Map (Keyword, Keyword, Keyword)) Formula where
+  learn ts = 
+    let
+      tss = filter couldBeInt ts
+      ts' = triPairs $ permutation tss $ combinations 2 tss
+      rules = foldr (\p rs -> findeqTriRules p ++ rs) [] ts'
+    in
[…]

### 2017-01-19 code2/src/Benchmarks.hs

@@ -125,5 +125,5 @@ group6 = map (map makeError) [
 
 testBenchSet :: [ErrorReport]
 testBenchSet = map (map makeError) [
-    [(("benchmarkSet/group5-value-correlation/test","a[mysqld]"),("benchmarkSet/group5-value-correlation/test","b[mysqld]"),INTREL)]
+    [(("benchmarkSet/test/test1.cnf","a[mysqld]"),("benchmarkSet/test/test1.cnf","b[mysqld]"),INTREL)]
   ]

### 2017-01-19 code2/src/Learners/FineGrained.hs

@@ -1,0 +1,100 @@
+{-# LANGUAGE TypeSynonymInstances, FlexibleInstances, InstanceSigs #-}
+{-# LANGUAGE MultiParamTypeClasses #-} 
+{-# LANGUAGE MultiWayIf #-} 
+{-# LANGUAGE OverloadedStrings #-} 
+
+module Learners.FineGrained where
+
+import Types.IR
+import Types.Errors
+import Types.Rules 
+import Types.Countable
+import qualified Types.Rules as R
+import Learners.Common
+
+
+import qualified Data.Map as M
+import qualified Data.Text as T
+import qualified Data.Char as C
+import           Data.Maybe 
+import           System.Directory
+
+import Debug.Trace
+
+-- | We assume that all IRConfigFiles have a set of unique keywords
+--   this should be upheld by the tranlsation from ConfigFile to IRConfigFile
+--   this means we cannot derive both (a,b) and (b,a) from one file
+instance Learnable R.FineGrained MultiFormula where
+
+  buildRelations f = let
+    rs = mapMaybe intLike f 
+    --dont want anything with these
+    xs = ["dir","socket","port"]
+    rs' = triples $ filter (\ir -> not $ any (\k -> T.isInfixOf k (keyword ir)) xs) rs
+    eqs = map toFineGrained rs'
+   in
+    M.fromList $ eqs
+
+  -- unionsWith work by Ord, so just providing a custom instance of Eq wont work, also need Ord
+  -- ord is too sensitive, since traversal might miss an EQ
+  -- instead just rebuild the whole map with combineFlips (only happens once so shouldnt be too bad
+  merge rs = let
+    rs' = M.unionsWith add rs
+   in
+    rs'
+--    M.foldlWithKey combineFlips M.empty rs'
+ 
+  check _ r1 r2 = if
+    | gt r1 > 3 && lt r1 > 3 -> Nothing --ignore rules if they dont have a clear tendancy
+    | eq r2 == 1 && (lt r1 > 3 || gt r1 > 3) && eq r1 < 3 -> Just r1
+    | lt r2 == 1 && gt r1 > 3 && lt r1 < 2-> Just r1
+    | gt r2 == 1 && lt r1 > 3 && gt r1 < 2-> Just r1
+    | otherwise -> Nothing
+    
+    
[…]

### 2017-01-19 code2/src/Main.hs

@@ -55,6 +55,7 @@ runVerify rules vTargets  = do
     then zipWithM reportBenchmarkPerformance benchmarks errors 
     else mapM reportUserPerformance $ L.sortOn (\(f,es) -> length es) (zip (map (\(x,y,z)->x) vTargets) errors) 
   print $ fitnesses
+  print $ length $ filter (>0) fitnesses
   return $ sum fitnesses
 
 

### 2017-01-19 CAV17/concl.tex
cav17: first commit

--- 2016-05-10 OSDI/concl.tex
@@
 and then uses a learner module to derive rules, 
-building a language model this way.
+building a language model in this way.
 \app then uses this generated language model 
@@
 a given configuration file. The verification is done by
-checking whether any of learned rules is violated.
+checking whether any of the learned rules is violated.
 We evaluate \app using a real-world dataset~\cite{configdataset}
@@
 maintained by different parties. 
-Nevertheless, w} We believe that \app represent a practical path
+Nevertheless, w} We believe that \app represents a practical path
 toward fully automated language-based configuration verification.

### 2017-01-19 CAV17/rel.tex
cav17: first commit

--- 2016-05-10 OSDI/rel.tex
@@
 diagnosis efforts aim at finding errors after system
-failures occur, which typically leads to prolonged recovery time.
+failures occur, which leads to prolonged recovery time.
 

### 2017-01-19 CAV17/secs/intro.tex

@@
 
-Configuration errors are one of the most important root causes of
-today's software system failures~\cite{xu15systems, yin11anempirical}.
-In their empirical study Yin {\em et al.}~\cite{yin11anempirical} report
-that about 31\% of system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code. 
-Misconfigurations, in practice, may result in various
-system-wide problems, such as security vulnerabilities, 
-application crashes, severe disruptions in software
-functionality, and incorrect program executions%
-~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.
-
-While many efforts have been proposed 
-to check, troubleshoot, diagnose, and repair configuration errors%
-~\cite{attariyan10automating,
-su07autobash, whitaker04configuration},
-those tools mainly try to understand {\emph{what}} caused the 
-error -- they are still not on a level of
-automatic verification tools used for regular program 
-verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
-detect errors without executing the code.
-Two main obstacles why we cannot simply apply the existing automatic 
-tools and techniques to verification of configuration files are: 1) a lack
-of a specification which would describe properties of configuration files, and 2) a program structure of configuration files -- they
-are mainly a sequence of entries assigning some value to system variables. The language in which configuration files are written does 
-not adhere to a specific grammar or syntax. In particular, the
-entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries and there
-is no explicit structure policy for the entries.
-Thus, automated verification of configuration 
-files would be highly
-desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
-
-To overcome these obstacles, researchers proposed approaches based on
-statistical analysis and learning%
-~\cite{wang04automatic, zhang14encore, yuan11context}
-that try to infer rules and policies about 
-how configuration files are constructed.
-Rather than explicitly specifying entries' types or rules, 
-these efforts focused on learning policies from a sample dataset.
-The learned rules are usually constructed in the following way: 
-for every entry in a configuration file, 
-they check if it deviates from a ``typical'' value, \ie, 
-a value computed from a large training set 
-consisting of configuration files.
-If the entry is significantly different from a typical value, 
-they suspect that it could be a potential configuration error.
-
-The downside of these is that their learning approaches 
-are limited to simplistic configuration errors, 
-such as type errors and syntax errors, or they 
-heavily rely on template-based inference~\cite{zhang14encore}. 
-%As we mentioned earlier, 
-%because configuration files are not written in a typed language 
-%with a fixed syntax,
-%type errors and syntax errors are relatively rare and easy to detect. 
-Many sophisticated configuration errors, 
-which are difficult to template in practice, 
-cannot be detected in this way. 
-As an illustration of such an error, consider entry ordering errors, 
-which happens when some entries are inserted in a wrong order. 
-For example, if in a PHP configuration file 
-an entry {\tt extension = mysql.so} appears 
-before {\tt extension = recode.so},  
-it would lead to a crash error, where the Apache server cannot start 
-due to the segmentation fault error. The correct ordering 
-should be {\tt extension = recode.so} before 
-{\tt extension = mysql.so}~\cite{yin11anempirical}.
-These types of errors cannot be detected by existing
-learning efforts, 
-since it is hard to build a corresponding template~\cite{xu15systems}. 
-%we would need to capture ordering relations of all the entries. 
-%Some of them can appear in an arbitrary ordering, 
-%and the resulting templates would be too large 
-%and not efficient for a practical use.
-
-%Offering automatic verification to configuration files -- like
-%what we did to programs -- has been advocated as a reasonable means
-%to check the correctness of configuration files of interest.
-%Nevertheless, it is still an open problem, because 
-%1) software configurations are typically written in poorly structured 
-%and untyped languages, and 2) writing specifications or constraints
-%for configuration verification is non-trivial in practice.
-
-In this paper, we present \app, the first automatic verification framework
-for general software configurations. \app is based on a collection of powerful learning 
-algorithms that do not necessarily depend on templates. The learning process takes as input a
- large sample of configuration files. The process is language-agnostic and works for any kind of configuration file, 
-but all of the files in the sample need to be of the same kind (such as
-MySQL or HTTPD configuration files).
-From that sample,
-\app learns an abundant set of rules specifying various properties that hold on the given sample. The files in the sample might contain
-errors -- we are, therefore, using probabilistic learning to derive a set of accurate rules.
-
-For practical purposes we use a real-world dataset~\cite{configdataset}. 
-Every file in our dataset contains several errors, 
-but they are typically different errors and only appear 
-in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
-accurate set of rules. The rules, in general, specify which properties variables need to satisfy. One can see this learning process as a
-way of deriving  
-a specification for configuration files.  Once there is a specification, we can do formal verification. With these 
-rules we can efficiently check the correctness of the configuration files
-of interest and detect potential errors.
-
-The learning process has two phases. In the first phase, 
-\app analyzes the sample dataset and generates a 
-well-structured and probabilistically-typed 
-intermediate representation. 
-In the second phase, \app derives rules and constraints by analyzing
-the intermediate representations.  Every learned rule is annotated with a probability 
-depicting which percentage of the files the rule was seen as correct. We only accept those rules whose 
-correctness probability is above the given threshold.
-
-Finally, while the learned rules establish correlations between two or more variables, using \app, one can also detect whether a
-single variable has an appropriate value assigned to it. We do that by measuring the values that are typically assigned to that variable 
-and reporting if the current value deviates too much from the recorded values.
-
-Building such an automatic verification framework for
-configuration files, nevertheless, requires addressing several challenges. 
-%First, for variables of one type 
-%we learn different rules than for variables of different types. 
-%For example, for integer variables $X$ and $Y$, 
-%we can learn that $X \leq Y$, while 
-%for strings we might want to learn a substring relation. 
-First, we need to assign a type to every variable in a configuration file during the transformation phase.
-However,
-the type of a variable cannot always be fully determined 
-from a single value. 
-For example, an entry {\tt temp\_dir = 300} assigns to variable {\tt temp\_dir} either a directory named ``300'' or sets the size of that directory to 300 (an integer).
-Some existing type inference 
-work would report this is an error, because {\tt temp\_dir} should be assigned
-an integer~\cite{zhang14encore}. We address this problem by introducing the concept of
-{\emph{probabilistic types}}.
-Rather than assigning only one variable to a single type, 
-we assign several types over a probability distribution. 
-The entry in the above example might be assigned 
-the following probabilistic type
-{\tt \{temp\_dir, 300, [(File, 60\%), (Int, 40\%)]\}}.
-Using probabilistic types,
-we can generate a more accurate language model,
-thus significantly improving our verification capabilities.
-
-Second, when learning rules we use very general templates to 
-infer them. The user does not need to provide any templates -- they are internally associated to the types.
-Nevertheless, in addition to those general templates, we still need specific algorithms to learn
-rules that cannot be easily templated.
-
-From a practical perspective, 
-\app introduces no additional burden 
-to the user: they can simply use \app to check for errors in their
-configuration files. However, they can also easily extend the framework
-themselves. The system is designed to be highly modular. If there is a
-class of rules that \app is not currently learning, the user can develop
-her own templates and learners for that class. The new learner can be
-added to \app and this way it can check an additional new set of
-errors.
-
-Our \app prototype still has many limitations:
-for example, we cannot handle configuration errors that can be 
-triggered during system execution time.
-Nevertheless, we believe \app may suggest a practical path
-toward automatic and modular language-based configuration verification.
-To summarize, this tool paper makes the following contributions:
-
-\com{
-Finally, from a systems perspective this is the first approach that {\emph{proactively}} checks 
- the correctness of configuration files. All previous work
-~\cite{xu15systems,zhang14encore,yuan11context, wang04automatic,attariyan10automating,
-su07autobash,whitaker04configuration} tries to identify the problem after the
-failure occurred.
-Our approach isolates potential errors before the system failure occurs, e.g.
-before the installation.
-We can also see \app as a tool that can run in conjunction with existing tools.
-Pre-analyzed configuration files are already free from language-based errors, and this way the workloads of post-failure forensics at the runtime
-is significantly reduced, thus making these tools truly practical.
-}
+Our main contributions are as follows:
 
@@
 
-\item We propose the first automatic configuration verification
-framework, \app, that can learn a language model from a sample
-dataset, and then use this language model to verify 
-configuration files of interest.
+\item Using a probabilistic logical inference approach to the learning task, which builds a more informative structure than state of the art machine learning algorithms
 
-\item \app proposes probabilistic types to assign a confidence 
-distribution over a set of types to each entry, 
-while generating the intermediate representation.
+\item A basic application of graph analysis on the learned model to improve results in a way not available to traditional machine learning approaches
 
-\item \app employs a collection of machine learning algorithms to 
-enable powerful rule and constraint inference.
-
-\item \app is capable of detecting various tricky errors that cannot
-be detected by previous efforts,
-including entry ordering errors, fine-grained value correlation errors, 
-missing entry errors, and environment-related errors.
-
-\item We implement a \app prototype and evaluate it by
-conducting comprehensive experiments on real-world dataset.
-
+\item An open-source implementation, \app, of this approach applied to a set of 256 real world benchmarks. \app identify XX new misconfigurations errors on YY of these files.
 \end{enumerate}

### 2017-01-20 CAV17/secs/intro.tex
from osdi

--- 2017-01-18 CAV17/secs/intro.tex
@@
 
-Configuration errors are one of the most important root causes of
-today's software system failures~\cite{xu15systems, yin11anempirical}.
-In their empirical study Yin {\em et al.}~\cite{yin11anempirical} report
-that about 31\% of system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code. 
-Misconfigurations, in practice, may result in various
-system-wide problems, such as security vulnerabilities, 
-application crashes, severe disruptions in software
-functionality, and incorrect program executions%
-~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.
+Configuration errors are one of the most important root causes of today's software system failures~\cite{xu15systems, yin11anempirical}.
+In their empirical study, Yin {\em et al.}~\cite{yin11anempirical} report that about 31\% of system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code.
+Misconfigurations, result in various system-wide problems, such as security vulnerabilities, application crashes, severe disruptions in software functionality, and incorrect program executions~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.
 
-While many efforts have been proposed 
-to check, troubleshoot, diagnose, and repair configuration errors%
-~\cite{attariyan10automating,
-su07autobash, whitaker04configuration},
-those tools mainly try to understand {\emph{what}} caused the 
-error -- they are still not on a level of
-automatic verification tools used for regular program 
-verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
-detect errors without executing the code.
-Two main obstacles why we cannot simply apply the existing automatic 
-tools and techniques to verification of configuration files are: 1) a lack
-of a specification which would describe properties of configuration files, and 2) a program structure of configuration files -- they
-are mainly a sequence of entries assigning some value to system variables. The language in which configuration files are written does 
-not adhere to a specific grammar or syntax. In particular, the
-entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries and there
-is no explicit structure policy for the entries.
-Thus, automated verification of configuration 
-files would be highly
-desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
+While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration errors~\cite{attariyan10automating,su07autobash, whitaker04configuration},
+  those tools mainly post-factum and cannot give the safety guarantees available from powerful static analysis tools in program verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15}.
+Existing techniques for program verification do not fit this application domain, as configuration files often lack specifications and structure.
+There are rarely formal, or any, specifications on the constraints of the key values.
+In the case of MySQL, the canonical specification is a 5240 page reference manual~\cite{mysql-manual15} to describe valid configurations and behavior.
+We aim to automatically learn a formal specification the encodes this information by examining a set of example configuration files.
+
+In previous work~\cite{santolucitoCAV}, we used a set of manually verified files by an domain expert order to learn specifications.
+This approach is expensive and still prone to error by the expert.
+Related work on configuration verification has used machine learning
+
+While the grammar of configuration files tends to be simple (a series of key value pairs with some additional context), the keys and values themselves lack often structure and are untyped plain text.
+
+   1) lack of a specification which would describe properties of configuration files, and 
+   2) a program structure of configuration files -- they are mainly a sequence of entries assigning some value to system variables. 
+The language in which configuration files are written does not adhere to a specific grammar or syntax. 
+In particular, the entries in configuration files are untyped. 
+Moreover, there are surprisingly few rules specifying constraints on entries and there is no explicit structure policy for the entries.
+Thus, automated verification of configuration files would be highly desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
 
@@
 \end{enumerate}
+
+Our main contributions are as follows:
+
+\begin{enumerate}
+
+\item Using a probabilistic logical inference approach to the learning task, which builds a more informative structure than state of the art machine learning algorithms
+
+\item A basic application of graph analysis on the learned model to improve results in a way not available to traditional machine learning approaches
+
+\item An open-source implementation, \app, of this approach applied to a set of 256 real world benchmarks. \app identify XX new misconfigurations errors on YY of these files.
+\end{enumerate}

### 2017-01-20 CAV17/abs.tex

--- 2016-05-10 OSDI/abs.tex
@@
 including entry ordering errors, fine-grained value correlation errors, 
-and entry missing errors. 
+and missing entry errors. 
 We evaluate \app using a real-world dataset with 261 incorrect 

### 2017-01-20 CAV17/motiv.tex

--- 2016-05-10 OSDI/motiv.tex
@@
 
-In this section we illustrate functionality of \app on several non-trivial configuration errors
-extracted from real-world examples. Although the errors are relatively simple, we call them 
-non-trivial, because the majority of existing tools, \eg, learning-based checking
-tools~\cite{zhang14encore, wang04automatic}, cannot detect
-these configuration errors. Most of the presented examples were found on StackOverflow,
-a popular question and answer website for programmers. To better understand problems that users have with 
-configuration files, we explored and analyzed misconfigurations on a large number of user forums and on-line discussion sites.
+In this section we present the capability of \app through 
+detecting errors in several real-world misconfiguration examples. 
+These examples were non-trivial configuration errors
+that were reported on StackOverflow~\cite{stackoverflow},
+a popular question and answer website for programmers and administrators. 
+%To better understand these problems, 
+%we explored and analyzed misconfigurations 
+%on a large number of user forums and on-line discussion sites.
 
@@
 the following lines:
+
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
@@
 should appear before {\tt mysql.so}, as shown
-below:
+below: \ennan{Mark, please update all the motivating examples'
+output results according
+to our newest version implementation.}
 
@@
 \para{Example~2: Fine-grained value correlation error.} 
-Our next real-world misconfiguration example~\cite{correlation} comes from a discussion on StackOverflow.
+Our second misconfiguration example~\cite{correlation} 
+comes from a discussion on StackOverflow.
 The user has configured her MySQL as in the following:
@@
 
-The user complains that her MySQL load was very high, causing the website's
+The user complains that her MySQL load was very high, 
+causing the website's
 response speed to be very slow.
@@
 task than the normal value correlation problem.
-
 To the best of our knowledge, \app is the first tool that
@@
 Many critical system outages result from the fact that an important
-entry was missing in the configuration file. 
+entry was missing from the configuration file. 
 We call such a problem a {\em missing entry error}.
@@
 
-\para{Example~4: Singular value anomalies.} 
-Many system performance problems are caused by the
-anomaly that a value is set either too high or too low.
-For example, a parameter relating to memory might be too large,
-exhausting the RAM and causing extreme slowness or even a crash. 
-Consider the following real-world misconfiguration file%
-~\cite{singleValue}: a user was experiencing the ``My SQL Server 
-has gone away" error.  
-This is difficult to debug, since the error message is not specific.
-It turns out the following line in her configuration file was problematic:
+\para{Example~4: Type errors.} 
+Many system performance problems are caused by 
+assigning incorrect type of values to some key in configuration
+files. Consider the following real-world misconfiguration file: 
+a user tries to install MySQL and she needs to initiate the path
+of the log information generated by MySQL.
+This user puts the following assignment in her MySQL
+configuration file:
 
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-max_allowed_packet = 100M
+    general_log = /var/log/mysql/mysql.log
 \end{lstlisting}
 
-The user eventually resolved the issue by replacing the above line with {\tt max\_allowed\_packet=2M}.
-One possible way to reach this conclusion more quickly is to determine that the original value, 100 MB, 
-is statistically deviant and extremely large for the {\tt max\_allowed\_packet} attribute. 
-ConfigV can detect these
-outliers. Run on the user's original configuration file, ConfigV would output:
+Unbeknowest to this user, the entry ``general\_log'' should be an 
+integer, not a string. In MySQL, there is another entry named
+``general\_log\_file'' used to specify the log path.
+With \app, this user can get the following result:
 
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-WARNING: Violated Upper Hampel Rule for max_allowed_packet with value 104857600 
+    TYPE ERROR: Expected a Int with P=1.0 for
+    "general_log [mysql]"
 \end{lstlisting}
 
-In the above, 104857600 represents the integer value of 100 megabytes. The idea is to output
-a warning to the user that her value falls outside of a range considered normal, so that she
-can make the appropriate adjustment to the value herself. In the above situation, it is 
-prudent to set the value of {\tt max\_allowed\_packet} lower. We call such a value a 
-\emph{singular value anomaly}.
-
-\para{Other errors.}
-In addition to the given motivating examples \app can also detect and report configuration errors that can be exposed by
-existing work, such as EnCore~\cite{zhang14encore} and
-CODE~\cite{yuan11context} (a full scope of \app's capabilities is given in $\S$\ref{sec-eval}).
-A recently reported configuration error made the MySQL
-daemon fail to start~\cite{syserror}.
-One entry was written as 
-{\tt datadir=/root/appfinder/mysql}, and the type, as well as 
-format, seemed correct.
-However, the problem is that this directory should not 
-contain the root directory; the correct entry
-should be {\tt datadir=/appfinder/mysql}.
-Such an error is called a system environment-related configuration error.
-Both \app and EnCore can handle misconfigurations concerning system execution.
-Furthermore, \app is also able to detect type errors and syntax errors
-in configuration files. An example of a type error is assigning to a variable {\tt {general\_log}} 
-a file path {\tt {/var/log/mysql/mysql.log}}. \app successfully reports this typing error: 
-\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-TYPE ERROR: Expected a Int with P=1.0 for "general_log[mysqld]"
-\end{lstlisting}
+%The above result means that we need to assign an integer value to
+%the entry ``general\_log''.

### 2017-01-20 CAV17/secs/abs.tex
reorganize and add main points

@@
 
+\app is capable of detecting various errors that cannot
+be detected by previous efforts,
+including entry ordering errors, fine-grained value correlation errors, 
+and missing entry errors.
+
+System failures resulting from configuration errors 
+are major reasons for compromised availability and
+reliability of today's software systems.
+Although many misconfiguration handling techniques
+such as checking, troubleshooting, and repair
+have been proposed, 
+offering automatic verification for configuration files -- as often  
+done for regular programs -- is still an open problem.
+This is because software configurations are typically written in
+poorly structured and untyped ``languages'', and 
+specifying constraints and rules for configuration 
+verification is non-trivial in practice.
+
+This paper presents \app, the first automatic verification framework for
+general software configurations.
+\app verifies a target configuration file $F$ through three steps.
+Firstly, \app analyzes a dataset containing many sample configuration 
+files belonging to the same system as $F$,
+translating these sample files to a
+well-structured and probabilistically-typed 
+intermediate representation.
+Secondly, \app derives rules and constraints by analyzing
+this intermediate representation, thus building a
+sophisticated language model.
+Finally, \app uses the resulting language model to verify $F$.
+The \app framework is highly modular, 
+does not rely on system source code, and
+can be applied to any new configuration file type with minimal user input.
+
 \end{abstract}

### 2017-01-20 CAV17/secs/check.tex
reorganize and add main points

\section{Checker}
\label{sec-checker}

With the learned rules and constraints in hand (generated
by the learner module),
\app checks whether any entry in a target configuration file
violates the learned rules and constraints.
For a given configuration file, \app parses it the same
way employed in the translator, thus obtaining a structured
and typed representation for the target configuration file.
Then, the checker uses two sub-modules (shown in 
Figure~\ref{fig-overview}) to check the target
configuration file based on rules and constraints.

\para{Error detecting.}
The first sub-module of our checker,
named error detecting in Figure~\ref{fig-overview}, 
is able to detect the following errors:
missing entry errors, ordering errors, 
correlation errors (including fine-grained value correlation errors),
type errors, and system environment errors (depending on templates).
In particular, the checker simply sees whether the representations 
parsed from the target configuration files violate our
learned rules.

\para{Anomaly checking.}
This checking occurs in the second sub-module of the checker.
Different from the previous checking tasks,
a suspicious warning detects whether some value
is overly different from the same entries in the
training dataset. Even if some values are statistically different
from the ones in the training dataset, 
it does not mean such a value is incorrect;
thus \app, in this case, throw out a warning to the user who
enters the target configuration file, and a report containing 
normal values in the training dataset.
\app allows users to choose whether they want to change 
the values according to ones in the training configuration
files.

### 2017-01-20 CAV17/secs/intro.tex
reorganize and add main points

@@
 \label{sec-intro}
+
+Our main contributions are as follows:
+
+\begin{enumerate}
+
+% Encore also used association rule learning, but did not describe why it is useful for verification in particular,
+%   or how it contrasts with other ML techniques that are less appropriate for verification (NN).
+\item Describing the logical foundation of using association rule learning to build a probabilistic specification for configuration files. 
+      We contrast this with the application of other machine learning techniques, such as neural networks, in verification.
+
+% We can analyze the rules we have learned as a graph to sort the errors, not just by weight, but also importance
+% need one more thing we can do with this graph
+% This is only possible when we have learned association rules, not possible with NN
+\item Analyzing the learned model to further refine the generated specification. 
+      We highlight why these analysis techniques are uniquely possible in an association rule learning approach.
+
+% The problem is intractable for off-the-shelf data mining solutions (see Encore).
+% In addition to the optimizations Encore used, we add new ones that make our tool even better.  
+\item An open-source implementation, \app, of this approach, which uses various domain specific optimizations to make the solution efficient. 
+      We also evaluate \app on a set of 256 real world benchmarks, and identify XX new misconfigurations errors on YY of these files.
+\end{enumerate}
 
@@
 \end{enumerate}
-
-Our main contributions are as follows:
-
-\begin{enumerate}
-
-\item Using a probabilistic logical inference approach to the learning task, which builds a more informative structure than state of the art machine learning algorithms
-
-\item A basic application of graph analysis on the learned model to improve results in a way not available to traditional machine learning approaches
-
-\item An open-source implementation, \app, of this approach applied to a set of 256 real world benchmarks. \app identify XX new misconfigurations errors on YY of these files.
-\end{enumerate}

### 2017-01-20 CAV17/secs/learner.tex
reorganize and add main points

--- 2016-05-10 OSDI/learner.tex
@@
 on our intermediate representations (generated by the translator).
-
-\begin{algorithm}[t]
-\caption{Probabilistically Learn Rules}
-\label{alg:plearn}
-\begin{footnotesize}
-  Let $\theta$ be the list of possible types.
-  Let $U$ be the list of possible untyped specifications.
-  \begin{algorithmic}[1]
-  \State \textbf{learnRules}($C$):\\
-
-  Input: set $C$ contains intermediate representations\\
-     \qquad \enspace \enspace of configuration files\\
-
-    \State $R = \{\}$ // rule set
-    \State $\Pi$ // probabilities associated with rule set
-    \For{each file $F$ in $C$}
-      \State Initialize $opt$ flag.
-      \For{each $z \in \theta \cup U$}
-        \State $Q$ contains candidate entries to consider
-        \State $RM$ contains entries in remove set
-        \If{$z$ is a type} \State $opt = 1$ \State $Q = filter(F,\tau)$
-          \State // Q contains $F$ entries with $\tau$ in type list
-        \ElsIf{$z$ is an untyped spec} \State $opt = 0$ \State $Q = F$
-        \EndIf
-        \For{each entry $e$ in $Q$}
-               \If{$g(e)$ is false}
-                        \State continue to next entry
-               \Else
-                        \State $CR = \textrm{constructRules}(e, z, opt, Q \backslash RM)$
-                        \State $R = R  \cup CR$
-                        \State For each $r \in CR$, update $\Pi$
-               \EndIf
-               \State $RM = RM \cup e$
-        \EndFor
-     \EndFor
-    \EndFor
-    \State return $(\Pi,R)$
-  \end{algorithmic}
-\end{footnotesize}
-\end{algorithm}
-
-\begin{algorithm}[t]
-\caption{Construct Rules}
-\label{alg:crules}
-\begin{footnotesize}
-  \begin{algorithmic}[1]
- \State \textbf{constructRules}($e, z, opt, S$):\\
-    Input: entry $e$ from intermediate representation\\
-     \qquad \enspace \enspace type or untyped specification $z$\\
-     \qquad \enspace \enspace option $opt$, set to 1 if template\\
-     \qquad \qquad \enspace \enspace \enspace \enspace \qquad or 0 if untyped spec\\
-     \qquad \enspace \enspace set of entries $S$\\
-     \State $R = \{\}$
-     \State Set $j$ as an iteration variable.
-     \If{opt == 1}
-        \State run the following sequence \textbf{L} over all elements of $templates(z)$ 
-        \State \ie, iterate $j$ over $templates(z)$
-     \ElsIf{opt == 0}
-        \State $j = z$
-     \EndIf
-     \State Beginning of \textbf{L}: 
-     \State Let $n$ be the arity of $j$.
-      \State Let $P$ be the set of permutations of distinct entries from $S$, of size $n-1$.
-      \For{each $p \in P$}
-        \State Let $p$ be represented by $(e_1, e_2, \ldots, e_{n-1})$.
-         \For{$i = 1:n$}
-         \State Create a $n$-tuple by placing $e$ at the $i$-th position and filling the remaining entries with $p$, in order. Let this $n$-tuple be $m = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
-         \State $r = \textrm{constructRule}(m)$
-         \If{$r$ is satisfied}
-                $R = R \cup r$
-         \EndIf
-        \EndFor
-     \EndFor
-     \State End of \textbf{L}. 
-     \State return $R$
-  \end{algorithmic}
-\end{footnotesize}
-\end{algorithm}
 

### 2017-01-20 CAV17/secs/limit.tex
reorganize and add main points

\section{Discussion and Limitations}

This section discusses a few of \app's limitations
and possible solutions.

\para{Legal misconfigurations.}
While \app can check for diverse configuration errors without
human intervention, most of the existing proactive 
misconfiguration detection techniques,
including \app, cannot handle configuration errors
resulting from events that occurred during system runtime.
Such configuration errors are referred to as {\em legal misconfigurations}%
~\cite{yin11anempirical}. In particular, 
many parameter misconfigurations have 
perfectly legal types and values, 
but do not deliver the functionality intended by users. 
For example, after a website's traffic significantly increases,
the parameter {\tt key\_buffer\_size} in MySQL may not 
be able to handle increasingly more data traffic,
thus leading to outage of the whole system.
These cases are more difficult to detect by
automatic checkers and may require more user training or
better configuration design.
A potential solution is to combine existing misconfiguration diagnosis
tools, \eg, X-ray~\cite{attariyan12x-ray} 
and ConfAid~\cite{attariyan10automating},
with \app in order to enhance 
misconfiguration checking capability.

\para{Misconfiguration across software components.}
As exposed by Yin {\em et al.}~\cite{yin11anempirical},
cross-software configuration correlation problems also account
for a considerable number of misconfiguration cases.
For example, in a LAMP-based Web server, one entry in the
PHP configuration file, {\tt mysql.max\_persistent = 400},
may make users encounter a ``too many connections'' error,
because a correlated entry in the underlying MySQL configuration
file assigns {\tt max\_connection} to 300, which is less
than the MySQL connection number in the PHP configuration file (\ie, 400).
It is quite difficult to detect such tricky errors
through learning approaches, because not only are users or engineers 
unaware of the hidden interactions~\cite{xu15systems},
but also it is hard to obtain global knowledge of the entire
configuration due to the business privacy concerns of
each software provider.
One possible solution to this problem might be to introduce
some cryptographic protocol, \eg, private set
intersection~\cite{kissner05privacy}, to privately extract the
overlapping entries, \eg, {\tt mysql.max\_connection} in the 
above MySQL and PHP case, for double-checking.

\para{Network configuration verification.}
\app mainly focuses on software configurations, \eg, MySQL and Apache,
so that our approach is limited to support network configuration
verification. This is because network configurations have quite
different representations, format, and rules from software configurations,
since network configurations are typically written in 
more domain-specific policy languages.
In fact, many network verification tools, 
\eg, NoD~\cite{lopes15checking} and 
Dobrescu {\em et al.}~\cite{dobrescu14software},
have been proposed to check whether network configurations
meet their specifications.

\para{More complex configuration structure.}
Currently, \app mainly targets key-value configuration files,
but in practice many systems, \eg, OpenStack~\cite{OpenStack},
employ very complex configuration format and structure,
which \app cannot handle.
Verifying such structurally complex configurations typically requires 
\app to learn a much more sophisticated language model,
which is challenging in practice.
Recent efforts~\cite{raychev15predicting, raychev16learning} 
may present possible solutions to this limitation.
These techniques can learn a call-graph from a training program set,
and check a new program based on properties extracted from this
generated call-graph. If we examine a structurally complex configuration 
file as a program with these tools, we may be able to use similar techniques 
to verify whether the configuration file violates a property of interest.

### 2017-01-20 CAV17/secs/check.tex
redo trans and remove junk

@@
 learned rules.
-
-\para{Anomaly checking.}
-This checking occurs in the second sub-module of the checker.
-Different from the previous checking tasks,
-a suspicious warning detects whether some value
-is overly different from the same entries in the
-training dataset. Even if some values are statistically different
-from the ones in the training dataset, 
-it does not mean such a value is incorrect;
-thus \app, in this case, throw out a warning to the user who
-enters the target configuration file, and a report containing 
-normal values in the training dataset.
-\app allows users to choose whether they want to change 
-the values according to ones in the training configuration
-files.

### 2017-01-20 CAV17/secs/learner.tex
redo trans and remove junk

@@
 total failure as in Example~4 of $\S$\ref{sec-motiv}.
-
-\subsection{Derivation of Probabilistic Rules}
-\label{subsec-rules}
-
-The first component learns two types of rules: rules that are inferred using templates associated with types 
-and rules which we call \emph{untyped specifications}. An example of an
-untyped specification is the ordering or missing entry constraint.
-%Both are rules that must hold over multiple parts of a configuration file.
-
-\para{A strawman solution.}
-We first present a strawman solution (employed by
-previous work~\cite{santolucitoCAV}) that uses 
-a set of correct configuration files as a learning set, 
-from which it is possible to derive rules 
-that must hold with absolute certainty. 
-In practice, however, it is difficult to obtain a set of files 
-that is both guaranteed to be without errors
-and large enough to learn sufficiently many rules.
-This usually requires manual verification of the learning set, 
-which is prone to error.
-
-As a result of this restriction, 
-these efforts only consider a rule if it holds over exactly every file in 
-the learning set. This behavior can be formally described as follows:
-\begin{small}
-\begin{align*}
-C :=&\ \text{Correct Learning Set}\\
-LR :=&\ \text{Learned Rules} :: \{\textrm{Rule}\}\\
-RR :=&\ \text{Reported Rules} :: \{\textrm{Rule}\}\\ 
-C =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
-LR =&\ \{ r\ \mid \forall file \in C,\ holds(r,file)\} \\
-RR =&\ \{ r\ \mid r \in LR \ \land \neg\ holds(r,\textrm{user file}) \}\\
-\end{align*}
-\end{small}
-In the above, the ":: \{Rule\}" notation indicates that $LR$, the learned rule set, 
-and $RR$, the reported rule set, are sets of rules.
-A rule is only committed to the $LR$ learned rule set if 
-the rule holds on all files in the training set $C$, as denoted by the $\forall$ quantifier. 
-A broken rule is reported to the user in the $RR$ rule set if the rule is in $LR$, 
-but does not hold on the input user file.
-
-In general, each rule can be viewed as a mapping from a tuple of 
-entry keys $(k_1, \ldots, k_n)$ in the intermediate representation of a 
-configuration file to a probability function, $P_{rel}$. This can be represented by a rule
-$r := (k_1, \ldots, k_n) \rightarrow P_{rel}$.
-$P_{rel}$ is a probability function specific to the relation to assess.
-The problem with the strawman solution is that the probability functions are restricted to be 
-boolean, which is to say that the relation can either be unsatisfied or satisfied, either 0 or 1. 
-For instance, for the rule that {\tt max\_connections} must 
-be greater than {\tt mysql.max\_persistent}, the rule is denoted by
-({\tt max\_connections}, {\tt mysql.max\_persistent}) $\to 1$, where 
-$B_{>}$ is set to 1. In our approach, we permit the probability functions to take on any value from 0 to 1.
-
-\para{Probabilistic approach.}
-In \app's learner module, the rule learning mechanism is tolerant 
-enough to accept a dataset of possibly incorrect configuration files. 
-Rather than manually correcting each file, 
-we extend the previous formalism to run probabilistic learning
-on our intermediate representations (generated by the translator).
-
-Our probabilistic approaches for learning missing entry, 
-ordering, and fine-grained value correlation rules stem 
-from existing work with building 
-non-probabilistic versions of these rule-learning algorithms. 
-For each of these rules, 
-we consider all possible permutations of keys that appear in every 
-file which are appropriately typed, and for our learning process, calculate the likelihood that each of 
-these permutations constitute a rule. 
-Rule patterns in the example set that appear frequently are accepted,
-so they can be used to evaluate new files.
-
-More formally, this approach can be defined as follows:
-
-\begin{small}
-\begin{flalign*}
-I\ \ :=&\ \text{Incorrect Learning Set}\\
-LP :=&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
-RP :=&\ \text{Reported Probabilistic Rules :: \{P\_Rule\}}\\
-I =&\  \text{\{Configuration Files in Intermediate Representation\}}\\
-(\Pi, LP) =&\ \text{learnRules}(I)\\
-RP =&\ \{ r\ \mid r \in LP\ \land \Pi(r)>p \land \neg holds(r, userfile) \}
-\end{flalign*}
-\end{small}
-
-Note that the formalism relies on Algorithm~\ref{alg:plearn}. The algorithm considers both typed templates and
-untyped specifications. As a similar iteration logic is used for both, an $opt$ flag distinguishes between the two situations.
-constructRule in Algorithm~\ref{alg:crules} refers to the creation of a rule from a tuple of entries, 
-$m = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
-The rule creation is formally represented as $m(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$. 
-In order to determine if the rule satisfied, the relation associated with $m(v(e_1), v(e_2), \ldots, v(e_i), \ldots, v(e_{n-1}))$ is evaluated for truth.
-The rule can be template-generated, for instance {\tt max\_connections} > {\tt mysql.max\_persistent}, or
-it can be untyped-specification-generated, for instance the ordering that {\tt recode.so} must come before 
-{\tt mysql.so}.
-
-The candidate entry set $Q$ in Algorithm~\ref{alg:plearn} 
-differs for the two cases.
-For typed templates, due to typing restrictions, 
-we must first filter and examine entries associated with the same type, in order to check that 
-the template is satisfied over appropriately typed argument entries. This manifests itself via $Q = filter(F,\tau)$
-in Algorithm~\ref{alg:plearn}. For
-untyped specifications, we do not need to adhere to this typing restriction, so we simply set $Q = F$.
-
-%probability set associated with the rules, $\Pi$, contains values
-%ranging from 0 to 1, which are then compared against an acceptance threshold for the final output.
-%\[
-%\{ P\_Rule = (a_j, a_k) | j \neq k \} \rightarrow \{ (R_1, R_2, ... , R_n) \}
-%\]
-
-%We can think of each of these $(a_j, a_k)$ as possibly having a different relationship, defined by the set $\{ R_i \}$, which cover the entire outcome space of possible relationships between the two values $(a_j, a_k)$.
-
-%For the entry missing rules, we define $R_1$ as the event that $a_j$ and
-%$a_k$ appear together, and $R_2$ to be the event that $a_j$ appears
-%without $a_k$, or by the transitive equivalent, $a_k$ appears without
-%$a_j$. For the ordering rules, we define $R_1$ as the event that
-%$a_j$ appears before $a_k$ and $R_2$ be the event that $a_k$ appears
-%before $a_j$. For the value correlation rules, we define $R_1$ as the
-%event that $a_j \leq a_k$, $R_2$ the event that $a_j = a_k$, and $R_3$
-%the case that $a_j \geq a_k$. Notice that the $R_i$ do not have to be
-%disjoint, but only have to union to the entire probability space.
-
-%By examining the learning set, we will derive a distribution of the set $\{R_i\}$ based on how many times we observe an occurrence of each relation.
-This distribution will then be used at checking time to determine if a user's configuration has broken a likely rule.
-
-A rule $r$ will be reported as broken if the probability the rule is
-correct, $\Pi(r)$, is greater than some user defined constant, $p$. This
-constant can be adjust to the user's preference. A small $p$ will
-increase the likelihood of finding an error, but also increase the
-number of false positives that are reported.
-
-\subsection{Learning Suspicious Constraints}
-\label{subsec-constraints}
-
-With a configuration file that has been verified against catastrophic
-failures (\eg, missing entry, type, and ordering errors), 
-the user may also want to examine more subtle issues.
-Anomalous values can cause tricky, but impactful, performance and memory
-issues that are hard to debug, as discussed in Example 4 of 
-$\S$\ref{sec-motiv}. 
-Consequently, anomalous values should be flagged and a warning returned
-to the user indicating the violation.
-
-We now describe the technique we use to detect anomalous values for 
-numerical attributes. Let $A$ be the set of attributes contained in the 
-configuration files in the sample dataset. 
-Let $A_n$ be the subset of attributes of $A$ which are numerically typed. 
-Then, for each attribute $a \in A_n$, we construct a vector $v_a$ of the 
-values corresponding to attribute $a$, seen over the entire sample dataset.
-For each $v_a$, we compute 
-an interval  $$[\hat{v_a} - 50*MAD(v_a), \hat{v_a} + 50*MAD(v_a)],$$ 
-where $\hat{v_a}$ represents the median over the values 
-in $v_a$ and $MAD(v_a$) refers to the 
-median absolute deviation. 
-This is a variant of a standard outlier detection test, namely the Hampel identifier.\footnote{Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation 
-for a normal distribution.} 
-In the checking phase, as long as the checker finds a value for a numerical 
-attribute in the checked file outside of this interval, 
-a warning would be printed to the user indicating the violating value, 
-the attribute, and the upper or lower Hampel threshold.
-
-The intuition behind this is that if the user has input a value 
-that falls outside of an interval containing values that are considered 
-``normal'' over the entire sample dataset, 
-that value will probably cause an error, in particular for performance. 
-We cannot know for sure if this value will cause an issue. 
-For instance, a user might have a machine with 
-particularly high-end hardware, 
-in which case a value beyond the upper Hampel threshold may be appropriate.

### 2017-01-20 CAV17/secs/trans.tex
redo trans and remove junk

\section{Translator}
\label{sec-trans}

The translator takes as input a sample dataset of configuration files and transforms it into a typed and well-structured intermediate representation.
The translator can be seen a parser used to generate an intermediate representation for learning rules (see $\S$\ref{sec-learn}).
Translating or parsing is system dependent since each configuration language (MySQL, Apache, PHP) uses a different grammar.
\app allows users to provide extra help to the translator for their specific system configurations.

The translator will convert each key-value assignment {\tt k=v} in the configuration file to a triple, $(k, v, \tau)$, where $\tau$ is a type of $v$. 
There are two major challenges in this step.
First is that configuration files' keywords are not necessarily unique and may have some additional context (modules or conditionals).
To solve this, we rely on the fact that keywords in a configuration file must be unique within their context, and rename all keywords with their context.
They keys for the sample configuration \ref{lst:mysql.cnf} would then be [``{\tt foo[server]}'',``{\tt bar[client]}''] internally to the intermediate representation.

\begin{lstlisting} [caption={A sample MySQL configuration file},label={lst:mysql.cnf},language=C]
  #mysql.cnf
  [server]
  foo = False
  [client]
  bar = 1
\end{lstlisting}

An additional challenge is that it is not always possible to fully determine the type of key based on a single example value. 
For this reason, we introduce {\emph {probabilistic types}}.
Taking the configuration \ref{lst:mysql.cnf}, we can assume \tt{bar} is a boolean type by the grammar of MySQL,
  but the keyword {\tt bar} could either be a integer type or a Boolean type.
Now considering the rule that the keywords should have the same values ($\texttt{foo}==\texttt{bar}$), we have two potential situations.
If {\tt bar::int}, we do not learn the above rule, but in the second case where {\tt bar::bool}, the rule is valid.
To resolve this ambiguity, instead of immediately assigning one type to a value, the translator assigns a distribution of types to a value based on examples from the learning set.
% an idea closely related to existentially quantified types~\cite{Launchbury93lazyfunctional}.

Formally, we define probabilistic types as follows: let $\mathcal{T}$ be a set of basic types.
In \app, the set $\mathcal{T}$ contains strings, file paths, integers, sizes, and booleans. 
A probabilistic type is a set of pairs $\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$. 
The count for $\tau_i$ is incremented each time a new example value that might be type $\tau_i$ is encountered for a particular key.

For example, if the training set contained [(``bar",1),(``bar",ON)], the resulting type would be bar::[bool=2,int=1] (considering that the literal 1 may act as either an int or a boolean).
This probabilistic type can then be collapsed in the final type inference stage based on domain knowledge of the types and the training set.
For instance, we might choose to treat bar as a boolean, and only learn rules on that rule type.
We could also choose to leave the type unresolved for lack of evidence, and learn rules on both types.

Note that in \app, typing is implemented as a learning module than can be easily extended to support more types.

### 2017-01-20 CAV17/secs/learner.tex
start on prob types

@@
 missing entry errors, ordering errors, and fine-grained value correlation errors. 
-These errors tend to cause total system failures.
-%Once the configuration file has been validated against such rules, 
-%the user may choose to invoke a more sensitive constraint checker. 
-The second component ($\S$\ref{subsec-constraints}) 
-aims to derive 
-constraints on entries to check for suspicious (or anomalous) values 
-that may violate standard practice. These anomalies can cause partial 
-degradation of the system, 
-such as significant reduction in performance, or even 
-total failure as in Example~4 of $\S$\ref{sec-motiv}.
+These errors tend to cause total system failures, but can also be more insidious and slow down the system only when the load increase beyond a certain threshold.
+
+Note that in \app, probabilistic typing is implemented as a learning module than can be easily extended to support more types.

### 2017-01-20 CAV17/secs/trans.tex
start on prob types

@@
 For this reason, we introduce {\emph {probabilistic types}}.
-Taking the configuration \ref{lst:mysql.cnf}, we can assume \tt{bar} is a boolean type by the grammar of MySQL,
+Taking the configuration \ref{lst:mysql.cnf}, we can assume {\tt bar} is a boolean type by the grammar of MySQL,
   but the keyword {\tt bar} could either be a integer type or a Boolean type.
@@
 In \app, the set $\mathcal{T}$ contains strings, file paths, integers, sizes, and booleans. 
-A probabilistic type is a set of pairs $\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$. 
+A probabilistic type, $\tilde{\tau} \in \tilde{\mathcal{T}}$, is a set of pairs $\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$. 
+A keyword may have a probabilistic type , expressed $k::\tau$, where 
 The count for $\tau_i$ is incremented each time a new example value that might be type $\tau_i$ is encountered for a particular key.
@@
 
-Note that in \app, typing is implemented as a learning module than can be easily extended to support more types.
+\begin{mathpar}
+\inferrule* [Right=Bar,width=8em]
+{(k,v) \in C \\ v="1"}
+{k::[int}
+\and
+\inferrule* [lab=XX]
+{uu \\ vv}{ww}
+\end{mathpar}

### 2017-01-21 CAV17/secs/arch.tex
cav17: arch and new figure

--- 2016-05-10 OSDI/arch.tex
@@
   configuration files to verify.
-  The purple components are the modules of \app.
-  Because template DB is not necessarily used, we use dashed
-  arrow between it and the learner.
-  Red boxes are sub-modules within the checker.
-  The yellow components are results generated by \app's modules.}
+  The blue dashed box is \app. 
+  The yellow components are key modules of \app.
+  The purple circle is a checker for checking whether the target
+  configuration file violates any rule.}
 \label{fig-overview}
@@
 software configuration files.
-In particular, \app can solve many sophisticated 
-configuration errors (\eg, ordering errors, missing entry errors,
-and fine-grained value correlation errors) that previous efforts cannot 
-detect. As depicted in Figure~\ref{fig-overview}, 
+In particular, \app can detect many sophisticated configuration errors, 
+including ordering errors, missing entry errors,
+type errors and integer correlation errors. 
+As depicted in Figure~\ref{fig-overview}, 
 a typical \app verification workflow has three steps:
-translation, learning, and checking. In this section, we briefly
+translation, learning, and rule refinement. In this section, we briefly
 describe how each step works.
@@
 The translator module first parses the input sample 
-dataset (containing both configuration files and system environment
-information), and then transforms them into a more structured
-and typed intermediate representation.
+dataset of configuration files, and then transforms them into 
+a more structured and typed intermediate representation.
 When we infer the types of entries in a configuration file, 
@@
 by introducing {\em probabilistic types}.
-In particular, rather than giving a variable a single type, 
+Rather than giving a variable a single type, 
 we assign several types over a probability distribution. 
@@
 The input of the learner is a set of files that have been translated
-into well-structured representations (\ie, the translator's
-outputs). The learner module employs a collection of learning algorithms
-to generate various rules and constraints,
-potentially used to handle different types of configuration errors.
-These rules and constraints are the outputs of the learner, 
-and will be used by the checker to detect errors later.
-By combining the translated representations and the learned
-rules together, we build a language model for
-configuration verification.
-Because the translator outputs probabilistically typed entries,
-the learner is responsible for determining a type for each entry.
+into well-structured intermediate representations. 
+The learner employs a learning algorithm named {\em rule association 
+algorithm} to generate various rules,
+potentially used to handle different types of configuration errors,
+including ordering errors, missing entry errors,
+type errors and integer correlation errors.
+These rules are the outputs of the learner, 
+and will be used to detect errors later.
+Because the translator gives the learner probabilistically typed entries,
+the learner is also responsible for determining a type for each entry.
 
-\com{Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
-which requires users or developers to provide explicit templates,
-\app's learner encodes some predefined error-patterns 
-to generate rules. 
-As an illustration of a simple rule that we can learn,
-consider an encoded pattern $X_1 \le X_2$, where $X_1$ and $X_2$ are
-integer variables. The learner may derive the rule stating that
-$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. 
-There is a classification and taxonomy of configuration errors in the 
-existing work on automated configuration troubleshooting%
-~\cite{yin11anempirical, configdataset}. 
-Each class can be viewed as an error-pattern 
-that \app should handle: we consider integer constraints, 
-ordering errors, typing errors, correlation errors, etc.}
-
-Although the learner does necessarily rely on templates,
-\app still offers a database containing many templates,
-as shown in Figure~\ref{fig-overview}.
-Some of these templates are responsible for offering
-specific system executional environment information.
-A learning algorithm cannot derive rules 
-related to environment violations, \eg,
-whether the current account is 
-the owner of a certain path, without information 
-about the environment. 
-In order to deal with comprehensive misconfiguration problems,
-the learner needs a template DB to provide environment information,
-thus detecting system environment-related configuration errors.
-
-\para{Checking.}
+\para{Rule refinement.}
 The checker is used to detect rule violations in the configuration

### 2017-01-21 CAV17/secs/trans.tex
type rules
more on prob types

@@
 
-The translator will convert each key-value assignment {\tt k=v} in the configuration file to a triple, $(k, v, \tau)$, where $\tau$ is a type of $v$. 
+The translator will convert each key-value assignment $k=v$ in the configuration file to a triple, $(k, v, \tau)$, where $\tau$ is the type of $v$. 
 There are two major challenges in this step.
@@
 To solve this, we rely on the fact that keywords in a configuration file must be unique within their context, and rename all keywords with their context.
-They keys for the sample configuration \ref{lst:mysql.cnf} would then be [``{\tt foo[server]}'',``{\tt bar[client]}''] internally to the intermediate representation.
+The keys for the sample configuration \ref{lst:1.cnf} would then be [``{\tt foo[server]}'',``{\tt bar[client]}''] internally to the intermediate representation.
 
-\begin{lstlisting} [caption={A sample MySQL configuration file},label={lst:mysql.cnf},language=C]
-  #mysql.cnf
+\begin{figure}[!htb]
+    \caption{A learning set of configuration files}
+    \centering
+    \begin{minipage}{.25\textwidth}
+	\begin{lstlisting} [label={lst:1.cnf},language=C,caption={1.cnf}]
 [server]
-  foo = False
+foo = ON
 [client]
@@
 	\end{lstlisting}
+    \end{minipage}%
+    \hspace{1cm}
+    \begin{minipage}{0.25\textwidth}
+	\begin{lstlisting} [label={lst:2.cnf},language=C,caption={2.cnf}]
+[server]
+foo = ON
+[client]
+bar = ON
+	\end{lstlisting}
+    \end{minipage}
+    \hspace{1cm}
+    \begin{minipage}{0.25\textwidth}
+	\begin{lstlisting} [label={lst:2.cnf},language=C,caption={3.cnf}]
+[server]
+foo = OFF
+[client]
+bar = OFF
+	\end{lstlisting}
+    \end{minipage}
+\end{figure}
 
@@
 For this reason, we introduce {\emph {probabilistic types}}.
-Taking the configuration \ref{lst:mysql.cnf}, we can assume {\tt bar} is a boolean type by the grammar of MySQL,
+Taking the configuration \ref{lst:1.cnf}, we can assume {\tt foo} is a boolean type by the grammar of MySQL,
   but the keyword {\tt bar} could either be a integer type or a Boolean type.
-Now considering the rule that the keywords should have the same values ($\texttt{foo}==\texttt{bar}$), we have two potential situations.
-If {\tt bar::int}, we do not learn the above rule, but in the second case where {\tt bar::bool}, the rule is valid.
+Consider that we would like to learn a rule that the boolean keywords should have the same values ($eq(\texttt{foo},\texttt{bar})$).
+We then have two potential situations; in the first case where {\tt bar:int}, we do not learn the above rule, but in the second case where {\tt bar:bool}, the rule is valid.
 To resolve this ambiguity, instead of immediately assigning one type to a value, the translator assigns a distribution of types to a value based on examples from the learning set.
@@
 A probabilistic type, $\tilde{\tau} \in \tilde{\mathcal{T}}$, is a set of pairs $\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$. 
-A keyword may have a probabilistic type , expressed $k::\tau$, where 
+A keyword may have a probabilistic type, expressed $k:\tilde{\tau}$.
 The count for $\tau_i$ is incremented each time a new example value that might be type $\tau_i$ is encountered for a particular key.
 
-For example, if the training set contained [(``bar",1),(``bar",ON)], the resulting type would be bar::[bool=2,int=1] (considering that the literal 1 may act as either an int or a boolean).
-This probabilistic type can then be collapsed in the final type inference stage based on domain knowledge of the types and the training set.
-For instance, we might choose to treat bar as a boolean, and only learn rules on that rule type.
-We could also choose to leave the type unresolved for lack of evidence, and learn rules on both types.
+\begin{mathpar}
+\hspace{-0.4cm} %no idea why, but this is better than \centering here
+\inferrule* [Right=bool\_int]
+{(k,v) \in C \\ v \in \{0,1\}}
+{k:[int\pluseq 1,bool\pluseq 1]}
+\and
+\inferrule* [Right=eq\_rule]
+{k1 : \tau \\ k2 : \tau \\ \tau \in \mathcal{T}}
+{eq(k1,k2) : Rule}
+\and
+\inferrule* [Right=bool\_resolve]
+{k:\tilde{\tau} \\ \tilde{\tau} \vdash bool \geq 2 \land \ast \leq 1}
+{k : bool}
+\and
+\\
+\inferrule* [Right=bool]
+{(k,v) \in C \\ v \in \{ON,OFF\}}
+{k:[bool\pluseq 1,string\pluseq 1]}
+\end{mathpar}
+
+In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $\in \tilde{\mathcal{T}}$ can be resolved to a basic type $\in \mathcal{T}$ with enough evidence.
+The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
+In this case, we allow a probabilistic type to resolve to a boolean if we have two counts for boolean, and no more than one count for any other type.
+While a user may implement overlapping inference rules, this are resolved by assigning the keyword a list of types.
+This is then effectively a subtyping relation.
 
 \begin{mathpar}
-\inferrule* [Right=Bar,width=8em]
-{(k,v) \in C \\ v="1"}
-{k::[int}
+%\centering 
+\inferrule* [Right=int\_resolve]
+{k:[int \geq 1]}
+{k : int}
 \and
-\inferrule* [lab=XX]
-{uu \\ vv}{ww}
+\\
+\inferrule* [Right=int\_bool\_resolve]
+{k:[bool \geq 2, \ast \leq 1] \\ k:[int \geq 1]}
+{k : [bool,int]}
 \end{mathpar}
+
+Note that we do not have an application rule over probabilistic types - types must be resolved to learn a rule over a keyword.
+In the case that there is not enough evidence to resolve a type, no type-dependent rules may be learned over that keyword.
+
+Taking the example type inference rules above, we can run an example inference.
+For example, if the training set contained [(``bar",1),(``bar",ON)], the resulting type would be bar::[bool=2,int=1] (considering that the literal 1 may act as either an int or a boolean).

### 2017-01-21 CAV17/secs/arch.tex
cav17: updated small

@@
 \para{Rule refinement.}
-The checker is used to detect rule violations in the configuration
-files of interest. The inputs of the checker are the learned rules 
-and the target configuration file to verify.
-It generates a report (as shown in $\S$\ref{sec-motiv}) about 
-whether it finds any error, \eg, rule violations 
-or some suspicious values (\eg, singular value anomaly).
-As shown in Figure~\ref{fig-overview},
-there are two sub-modules in the checker. They are responsible for
-checking rule violations and suspicious values, respectively.
-In our experience, we found learned rules could be significantly reused
-to check different configuration files, thus improving our usability.
+\ennan{It seems so far I do not know how exactly this part works. 
+Maybe we can write through this part after finish the 
+section 6.}

### 2017-01-21 CAV17/secs/arch.tex
cav17: training set

@@
 \caption{\app's workflow. The green components represent configuration 
-  files, including both sample configuration datasets and users' input
+  files, including both training set of configuration files and users' input
   configuration files to verify.
@@
 that we are given a number of (not necessarily correct) 
-configuration files, called {\em sample dataset}, 
+configuration files, called {\em training set}, 
 belonging to the same system, such as MySQL or Apache. 
@@
 \para{Translator.}
-The translator module first parses the input sample 
-dataset of configuration files, and then transforms them into 
+The translator module first parses the input training  
+set of configuration files, and then transforms them into 
 a more structured and typed intermediate representation.

### 2017-01-21 CAV17/secs/eval.tex
reorganize and add main points
remove old - add strucure

--- 2016-05-10 OSDI/eval.tex
@@
-\section{Evaluations}
-\label{sec-eval}
+\section{Evaluation}
 
-We conduct three experiments to evaluate our \app
-prototype. Our experiments aim to answer the following
-questions.
-
-\begin{itemize}
-
-\item Whether \app can successfully 
-  detect real-world configuration errors ($\S$\ref{subsec-effectiveness})?
-
-\item Whether \app can correctly detect anomalous values
-($\S$\ref{subsec-anomalous})?
-
-\item How long do training and verification last ($\S$\ref{subsec-time})?
-
-\end{itemize}
-
-\input{table}
-
-\subsection{\app's Effectiveness}
-\label{subsec-effectiveness}
-
-We now apply \app to check against real-world misconfiguration problems.
-We use a real misconfiguration dataset~\cite{configdataset}
-that are collected from several online forums, \eg, 
-Stack Overflow and MySQL forum.
-Each configuration file in this dataset was posted by 
-programmers or system administrators, 
-when they confront the misconfiguration issues in practice.
-This dataset contains 261 incorrect MySQL configuration files.
-
-We apply \app to learn and check the configuration files in this
-dataset. Then, we observe how many errors \app can detect,
-and manually check whether these detected errors are indeed
-configuration errors.
-For all the 261 configuration files, we found \app is
-able to report all the errors correctly.
-For 217 of the 261 configuration files, we found \app's 
-error detection results are correct and accurate,
-\ie, correctly report the real misconfiguration problem.
-However, for 44 of them, \app outputs relatively high false positives,
-\eg, higher than 50 false positives,
-which is not very helpful to users in practice.
-The reason is our training set contains too many incorrect configuration
-files, which produce a lot of noises to our learning process,
-thus resulting in so many false positives.
-
-In order to clearly evaluate the effectiveness of \app,
-we extract 20 incorrect configuration files from the dataset.
-As a case study, we present the problem descriptions of these files, 
-the types of their errors, and the outputs produced by \app.
-Table~\ref{table-casestudy} details this information.
-
-As shown in Table~\ref{table-casestudy},
-we found \app is capable of detecting many configuration errors previous
-efforts, \eg, EnCore~\cite{zhang14encore}, cannot deal with.
-To the best of our knowledge, no existing effort
-is able to detect fine-grained value correlation errors in the 
-MySQL configuration files.
-For example, the third case in Table~\ref{table-casestudy}
-presents \app detects the fine-grained correlation,
-{\tt key\_buffer\_size} should be larger than 
-{\tt sort\_buffer\_size} * {\tt max\_connections}.
-
-\begin{table*}[t]
+\begin{table}[h]
 \centering
-\caption{Sampled benchmarks for anomaly detection}
-\label{table-anomaly}
-\begin{small}
-\begin{tabular}{|l|l|l|l|}
+\caption{Results of Learning}
+\label{table-training}
+\begin{tabular}{|c|c|c|c|}
 \hline
-{\bf ID} & {\bf Problem Description} & {\bf URL} & 
-{\bf \app Report}  \\ 
+{\bf Class of Error } & {\bf Total Rules Learned from Training Set} & {\bf Rules Detected on Benchmark set} & {\bf Thresholds}\\ 
 \hline
 \hline
-1 & MySQL Server has gone away error in Wamp 
-& goo.gl/axnezi  
-& WARNING: Violated Upper Hampel Rule for 
-\\ &  & 
-& {\tt max\_allowed\_packet} with value 104857600 
- \\ \hline
+10   & 2.997     & &  \\ \hline
+50   & 46.4208   & &  \\ \hline
+100  & 206.7798  & &  \\ \hline
+150  & 431.7772  & &  \\ \hline
+200  & 856.6383  & &  \\ 
+\hline
+\end{tabular}
+\end{table}
 
-2 &  MySQL has abnormally high load for CPU 
-& goo.gl/JrRLrR
-& WARNING: Violated Upper Hampel Rule for  
-\\ & & 
-& {\tt sort\_buffer\_size} with value 1048576000 \\
-& & & WARNING: Violated Upper Hampel Rule for  
-\\ & & 
-& {\tt read\_rnd\_buffer\_size} with value 283115520 \\ \hline
-
-3 & User is having performance issues with MySQL 
-& goo.gl/34jTB5
-& WARNING: Violated Upper Hampel Rule for  
-\\ & & 
-& {\tt query\_cache\_limit} with value 134217728 \\ \hline
-
-\end{tabular}
-\end{small}
-\end{table*}
-
-\subsection{Detecting Anomalous Values}
-\label{subsec-anomalous}
-
-The purpose of checking anomalous values in configuration files 
-is to avoid potential performance or workload problems. 
-Checking anomalous values is mainly the responsibility of
-the second sub-module checker of \app (see $\S$\ref{sec-checker}).
-
-We run \app to check 30 real-world benchmarks from Stack Overflow 
-website, and found \app is able to report anomalous values in
-these configurations. We also manually check whether these
-anomalous values are correct by comparing our results with
-the answers on Stack Overflow.
-
-Table~\ref{table-anomaly} shows three examples.
-We present the problem description, the link and the output results
-of \app. We found these anomalous values are very hard for
-administrators or users to detect, because they look correct.
-However, as shown in the links posted in Table~\ref{table-anomaly},
-such anomalous values typically lead to critical performance
-problems in practice.
-
-\subsection{Training \& Verification Performance}
-\label{subsec-time}
-
-We run our experiments measuring the run-time of training and
-verification of \app.
-Our experiments were run on a machine equipped with
-64-bit Intel Core i7-4790 CPU @ 3.60GHz and 8 GB of RAM.
-
-\para{Training performance.}
-We first evaluate the training time of \app. Namely, how long
-does \app need to use to generate rules.
-We vary the number of configuration files in our training dataset
-between 10 and 200, and record the corresponding time.
-Table~\ref{table-training} presents our evaluational results.
-We found the training time of \app is acceptable in practice,
-because 150 files in the training dataset have been able to make
-us obtain good enough rules.
-For 150 files, \app only needs about 7 minutes.
-Furthermore, even if we train \app with a 200-file dataset,
-we need less than 15 minutes, but such a training dataset
-can generate about 200,000 rules.
-
-\para{Verification performance.}
-We also measure the verification time of \app, and found
-the verification time is very fast. With 232,613 rules,
-\app needs less than one second to verify a MySQL configuration file.
-\app only needs 3 minutes to finish the verifications to
-the real-world dataset~\cite{configdataset}, we used to 
-evaluate the effectiveness of \app,
-which contains 261 misconfiguration files.
-
-\begin{table}[t]
+\begin{table}[h]
 \centering
@@
 \label{table-training}
-\begin{tabular}{|c|c|}
+\begin{tabular}{|c|c|c|}
 \hline
-{\bf The \# of Files for Training}       & {\bf Training Time (sec.)}  \\ 
+{\bf The \# of Files for Training} & {\bf Training Time ConfigC (sec.)} & {\bf Training Time \app (sec.)}\\ 
 \hline
 \hline
-10   & 2.997        \\ \hline
-50   & 46.4208          \\ \hline
-100  & 206.7798       \\ \hline
-150  & 431.7772        \\ \hline
-200  & 856.6383  \\ 
+10   & 2.997     &   \\ \hline
+50   & 46.4208   &   \\ \hline
+100  & 206.7798  &   \\ \hline
+150  & 431.7772  &   \\ \hline
+200  & 856.6383  &   \\ 
 \hline

### 2017-01-21 CAV17/secs/intro.tex
type rules
remove old - add strucure

@@
 
-In this paper, we present \app, the first automatic verification framework
-for general software configurations. \app is based on a collection of powerful learning 
-algorithms that do not necessarily depend on templates. The learning process takes as input a
- large sample of configuration files. The process is language-agnostic and works for any kind of configuration file, 
-but all of the files in the sample need to be of the same kind (such as
-MySQL or HTTPD configuration files).
-From that sample,
-\app learns an abundant set of rules specifying various properties that hold on the given sample. The files in the sample might contain
-errors -- we are, therefore, using probabilistic learning to derive a set of accurate rules.
-
 For practical purposes we use a real-world dataset~\cite{configdataset}. 
@@
 
-The learning process has two phases. In the first phase, 
-\app analyzes the sample dataset and generates a 
-well-structured and probabilistically-typed 
-intermediate representation. 
-In the second phase, \app derives rules and constraints by analyzing
-the intermediate representations.  Every learned rule is annotated with a probability 
-depicting which percentage of the files the rule was seen as correct. We only accept those rules whose 
-correctness probability is above the given threshold.
-
-Finally, while the learned rules establish correlations between two or more variables, using \app, one can also detect whether a
-single variable has an appropriate value assigned to it. We do that by measuring the values that are typically assigned to that variable 
-and reporting if the current value deviates too much from the recorded values.
-
-Building such an automatic verification framework for
-configuration files, nevertheless, requires addressing several challenges. 
-%First, for variables of one type 
-%we learn different rules than for variables of different types. 
-%For example, for integer variables $X$ and $Y$, 
-%we can learn that $X \leq Y$, while 
-%for strings we might want to learn a substring relation. 
-First, we need to assign a type to every variable in a configuration file during the transformation phase.
-However,
-the type of a variable cannot always be fully determined 
-from a single value. 
-For example, an entry {\tt temp\_dir = 300} assigns to variable {\tt temp\_dir} either a directory named ``300'' or sets the size of that directory to 300 (an integer).
-Some existing type inference 
-work would report this is an error, because {\tt temp\_dir} should be assigned
-an integer~\cite{zhang14encore}. We address this problem by introducing the concept of
-{\emph{probabilistic types}}.
-Rather than assigning only one variable to a single type, 
-we assign several types over a probability distribution. 
-The entry in the above example might be assigned 
-the following probabilistic type
-{\tt \{temp\_dir, 300, [(File, 60\%), (Int, 40\%)]\}}.
-Using probabilistic types,
-we can generate a more accurate language model,
-thus significantly improving our verification capabilities.
-
-Second, when learning rules we use very general templates to 
-infer them. The user does not need to provide any templates -- they are internally associated to the types.
-Nevertheless, in addition to those general templates, we still need specific algorithms to learn
-rules that cannot be easily templated.
-
 From a practical perspective, 
@@
 errors.
-
-Our \app prototype still has many limitations:
-for example, we cannot handle configuration errors that can be 
-triggered during system execution time.
-Nevertheless, we believe \app may suggest a practical path
-toward automatic and modular language-based configuration verification.
-To summarize, this tool paper makes the following contributions:
-
-\com{
-Finally, from a systems perspective this is the first approach that {\emph{proactively}} checks 
- the correctness of configuration files. All previous work
-~\cite{xu15systems,zhang14encore,yuan11context, wang04automatic,attariyan10automating,
-su07autobash,whitaker04configuration} tries to identify the problem after the
-failure occurred.
-Our approach isolates potential errors before the system failure occurs, e.g.
-before the installation.
-We can also see \app as a tool that can run in conjunction with existing tools.
-Pre-analyzed configuration files are already free from language-based errors, and this way the workloads of post-failure forensics at the runtime
-is significantly reduced, thus making these tools truly practical.
-}
 

### 2017-01-21 CAV17/secs/learner.tex
remove old - add strucure

@@
 
-The goal of the learner module is to derive rules and constraints from
-the intermediate representation generated by the translator.
-In general, the learner module has two components.
-The first component ($\S$\ref{subsec-rules}) 
-learns rules for checking configuration errors like
-missing entry errors, ordering errors, and fine-grained value correlation errors. 
-These errors tend to cause total system failures, but can also be more insidious and slow down the system only when the load increase beyond a certain threshold.
+The goal of the learner is to derive rules from the intermediate representation of the training set generated by the translator.
+We an interface for uses to define rules that should be learned.
+Each instance of the interface corresponds to a different class of of configuration errors, such as missing entry errors, ordering errors, and fine-grained value correlation errors. 
+These errors can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
 
-Note that in \app, probabilistic typing is implemented as a learning module than can be easily extended to support more types.
+\para{Type}
+In \app, probabilistic typing is implemented as an instance of the learning interface than can be easily extended to support more types. 
+It
+
+\para{Order}
+
+\para{Missing}
+
+\para{Integer Correlation}
+Fine grained errors (Aaron)
+
+\subsection{Checker}
+\label{sec-checker}
+
+With the learned rules and constraints in hand (generated
+by the learner module),
+\app checks whether any entry in a target configuration file
+violates the learned rules and constraints.
+For a given configuration file, \app parses it the same
+way employed in the translator, thus obtaining a structured
+and typed representation for the target configuration file.
+Then, the checker uses two sub-modules (shown in 
+Figure~\ref{fig-overview}) to check the target
+configuration file based on rules and constraints.
+
+\subsection{Implementation}
+
+\app is primarily implemented in Haskell, with a bit of mongo.
+The translator is developed as a parser for the grammar described in $\S$\ref{sec-trans}. 
+The learner and checker module fully implemented the design in $\S$\ref{sec-learn} and $\S$\ref{sec-checker}, respectively.
+
+The learning and checking modules are developed to allow
+for customized extensibility. In order to verify a configuration file
+against a new type of error, a user only needs to provide a new type
+that is an instance of the \textit{Attribute} typeclass (\ie, define some
+functions over that type). 
+In particular, for each type of error the users
+wish to detect, they must implement three functions;
+\lstinline{learn}, \lstinline{merge}, and \lstinline{check}.
+
+The source code for our implementation is available at {\em (URL omitted for blind review)}.

### 2017-01-21 CAV17/secs/postanal.tex
remove old - add strucure

% Graph Analysis
% Rahul

\section{Post Analysis}

\subsection{Rule Ordering}

\subsection{Complexity Measure}

### 2017-01-22 CAV17/secs/arch.tex
add section on post analysis

@@
 
-\para{Rule refinement.}
-\ennan{It seems so far I do not know how exactly this part works. 
-Maybe we can write through this part after finish the 
-section 6.}
+\para{Post Analysis.}
+Finally, the intermediate representation generated by the learner is
+analyzed to further refine the rules. One natural transformation
+presented in the paper is to interpret generated (option, relation, option)
+rules as the edges of a graph. We analyze the properties of this graph to
+construct an ordering of rules by their importance in the system being
+configured, as well as to produce a measure of complexity for any configuration
+of the target system. Note that particular metrics developed in this paper are
+not exhaustive. We believe the information contained in the intermediate
+representation, unavailable to previous neural-network based techniques,
+to contain vast potential for further inquiry.

### 2017-01-22 CAV17/secs/arch.tex
nit change wording and clarify terminology

@@
 Finally, the intermediate representation generated by the learner is
-analyzed to further refine the rules. One natural transformation
-presented in the paper is to interpret generated (option, relation, option)
+analyzed to further refine the rules. One transformation
+presented in the paper is to interpret generated
+(keyword, relation, keyword) % TODO: replace with formal keyword def'n
 rules as the edges of a graph. We analyze the properties of this graph to
@@
 not exhaustive. We believe the information contained in the intermediate
-representation, unavailable to previous neural-network based techniques,
-to contain vast potential for further inquiry.
+representation, unavailable to neural-network based techniques,
+contains vast potential for further inquiry.

### 2017-01-22 CAV17/secs/trans.tex
cav17: figure 2 caption
fixing type rules
use double colon for basic types

@@
 \begin{figure}[!htb]
-    \caption{A learning set of configuration files}
     \centering
@@
     \end{minipage}
+
+    \caption{A learning set of configuration files}
 \end{figure}
@@
 \inferrule* [Right=eq\_rule]
-{k1 : \tau \\ k2 : \tau \\ \tau \in \mathcal{T}}
-{eq(k1,k2) : Rule}
+{k1 :: \tau \\ k2 :: \tau \\ \tau \in \mathcal{T}}
+{eq(k1,k2) :: Rule}
 \and
@@
 {k:\tilde{\tau} \\ \tilde{\tau} \vdash bool \geq 2 \land \ast \leq 1}
-{k : bool}
+{k :: bool}
 \and
@@
 
-In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $\in \tilde{\mathcal{T}}$ can be resolved to a basic type $\in \mathcal{T}$ with enough evidence.
+In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \tilde{\tau} \in \tilde{\mathcal{T}}$ can be resolved to a basic type (expressed with the double colon $ k :: \tau \in \mathcal{T}$) with enough evidence.
 The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
 In this case, we allow a probabilistic type to resolve to a boolean if we have two counts for boolean, and no more than one count for any other type.
-While a user may implement overlapping inference rules, this are resolved by assigning the keyword a list of types.
-This is then effectively a subtyping relation.
+
+A user may implement overlapping inference rules, for example in {\scriptsize INT\_RESOLVE}.
+This not a subtyping relation, as the predicates over the counts may not be strictly overlapping.
+We simply allow the double colon (::) to type a single keyword in multiple ways.
+Because the only typing judgments on a basic type are terminal, {\scriptsize EQ\_RULE}, there is no problem with ambiguity as we would have in a traditional lambda calculus that included function application.
 
@@
 \inferrule* [Right=int\_resolve]
-{k:[int \geq 1]}
-{k : int}
-\and
-\\
-\inferrule* [Right=int\_bool\_resolve]
-{k:[bool \geq 2, \ast \leq 1] \\ k:[int \geq 1]}
-{k : [bool,int]}
+{k:\tilde{\tau} \\ \tilde{\tau} \vdash int \geq 1}
+{k :: int}
 \end{mathpar}

### 2017-01-22 CAV17/secs/postanal.tex
WIP add notes and structure for section on post-analysis processing

@@
 
+VeriConf can output the series of learned rules extracted from its training
+set as described in $\S$\ref{sec-learn}.
+
 \subsection{Rule Ordering}
 
+\iffalse
+
+Define a graph with labeled, weighted edges $G = (V,E)$ such that:
+
+    V \def { keywords }
+
+Where
+
+    E \def { (v_1, v_2, l, w) }
+
+Where the label $l$ defines the relationship, and the weight $w$ is
+defined as $w = \frac{true - false}{total}$ for that relationship.
+Note that due to support / confidence assertions in the learner, we
+may be assured that all weights in the graph are positive.
+
+Structure:
+    - Definition
+        > Degree (in-degree + out-degree) for each node
+
+        Define in-degree and out-degree in the usual way:
+
+            IN_DEGREE(k) = ||
+
+            \forall keyword k \in rules, in_degree()
+
+        Note that we will be summing in-degree and out-degree over all
+        relationships $l$ to determine the total importance of
+        a keyword $k$ in the configuration space. We are restricted
+        by the total set of learning modules from which to derive
+        relationships $l$. If a keyword were highly constrained by some
+        relationship to other keywords in a way that might not be
+        measurable by current techniques, the learner (and therefore
+        consequently the graph) will show these keywords as being
+        unrelated.
+
+    - Semantics
+        > Intuitively, keywords that are seen together more often
+          with defined relationships
+          are more likely to generate rules within the learner.
+          (it would be nice to show this with a quick derivation)
+
+          for a rule to be considered *true*, two conditions must hold:
+
+            - adequate support
+                we have seen the keywords together x number of times
+
+            - adequate confidence
+                how many times out of the x number of times 
+                was the relationship true?
+
+    - Open Questions
+        > What is the difference between {\it important} rules and
+          {\it rules we are more sure about}?
+
+        > Why doesn't everything just sum to zero?
+
 \subsection{Complexity Measure}
+
+INCLUDE SHORT BACKGROUND ON CODE COMPLEXITY. We define a measurement
+of complexity based on the calculated correlation. The presented
+metric is a heuristic that intends to approximate the quetion, 
+{\it how much redundancy exists in a configuration file, when considering
+probabilistic constraints imposed by the problem domain}?
+
+it may be possible in the future to have interpreted predicates,
+such that these heuristics may more accurately reflect the informational
+content of a constrained configuration file.
+
+\fi

### 2017-01-22 CAV17/secs/trans.tex
mostly done with prob types
TODO revisit this to fix so called ambiguity in rules

@@
 
-The translator takes as input a sample dataset of configuration files and transforms it into a typed and well-structured intermediate representation.
+The translator takes as input a training set of configuration files and transforms it into a typed and well-structured intermediate representation.
 The translator can be seen a parser used to generate an intermediate representation for learning rules (see $\S$\ref{sec-learn}).
@@
     \end{minipage}
-
     \caption{A learning set of configuration files}
+    \label{fig:tset}
 \end{figure}
@@
 An additional challenge is that it is not always possible to fully determine the type of key based on a single example value. 
-For this reason, we introduce {\emph {probabilistic types}}.
+For this reason, we introduce \textit{probabilistic types}, as contrasted with \textit{basic types}.
+In \app, the set of basic types contains strings, file paths, integers, sizes, and booleans. 
 Taking the configuration \ref{lst:1.cnf}, we can assume {\tt foo} is a boolean type by the grammar of MySQL,
@@
 Consider that we would like to learn a rule that the boolean keywords should have the same values ($eq(\texttt{foo},\texttt{bar})$).
-We then have two potential situations; in the first case where {\tt bar:int}, we do not learn the above rule, but in the second case where {\tt bar:bool}, the rule is valid.
+We then have two potential situations; in the first case where {\tt bar}$::int$, we do not learn the above rule, but in the second case where {\tt bar}$::bool$, the rule is valid.
 To resolve this ambiguity, instead of immediately assigning one type to a value, the translator assigns a distribution of types to a value based on examples from the learning set.
@@
 
-Formally, we define probabilistic types as follows: let $\mathcal{T}$ be a set of basic types.
-In \app, the set $\mathcal{T}$ contains strings, file paths, integers, sizes, and booleans. 
+Formally, a probabilistic types is a set of counts over a set $\mathcal{T}$ of basic types.
 A probabilistic type, $\tilde{\tau} \in \tilde{\mathcal{T}}$, is a set of pairs $\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$. 
-A keyword may have a probabilistic type, expressed $k:\tilde{\tau}$.
-The count for $\tau_i$ is incremented each time a new example value that might be type $\tau_i$ is encountered for a particular key.
+A keyword has a probabilistic type, expressed $k:\tilde{\tau}$, which without any evidence remains as {\scriptsize EMPTY}.
+The count for $(\tau_i,c_i) \in \tilde{\tau}$ is incremented each time a new example value that matches to type $\tau_i$ is encountered for a particular key, as shown in the {\scriptsize BOOL\_INT} and {\scriptsize BOOL} rules.
 
@@
 \hspace{-0.4cm} %no idea why, but this is better than \centering here
+\inferrule* [Right=Empty]
+{\\}
+{k:[\ast = 0]}
+\and
 \inferrule* [Right=bool\_int]
@@
 {k:[int\pluseq 1,bool\pluseq 1]}
+\\
+\and
+\inferrule* [Right=bool\_resolve]
+{k:\tilde{\tau} \\ \tilde{\tau} \models bool \geq 2 \land \ast \leq 1}
+{k :: bool}
+\\
+\and
+\inferrule* [Right=bool]
+{(k,v) \in C \\ v \in \{ON,OFF\}}
+{k:[bool\pluseq 1]}
 \and
@@
 {eq(k1,k2) :: Rule}
-\and
-\inferrule* [Right=bool\_resolve]
-{k:\tilde{\tau} \\ \tilde{\tau} \vdash bool \geq 2 \land \ast \leq 1}
-{k :: bool}
-\and
-\\
-\inferrule* [Right=bool]
-{(k,v) \in C \\ v \in \{ON,OFF\}}
-{k:[bool\pluseq 1,string\pluseq 1]}
 \end{mathpar}
 
-In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \tilde{\tau} \in \tilde{\mathcal{T}}$ can be resolved to a basic type (expressed with the double colon $ k :: \tau \in \mathcal{T}$) with enough evidence.
+In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \tilde{\tau} \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
 The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
-In this case, we allow a probabilistic type to resolve to a boolean if we have two counts for boolean, and no more than one count for any other type.
+In this case, we allow a probabilistic type to resolve to a boolean if we have two counts for boolean, and no more than one count for any other basic type ($\ast$).
+We use the notation, $\tilde{\tau} \models p$, to denote a probabilistic type whose counts hold on the predicate $p$.
+Taking the type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
+We would derive the probabilistic type \texttt{bar}$:[bool=3,int=1]$, which then resolves to \texttt{bar}$::bool$.
 
@@
 This not a subtyping relation, as the predicates over the counts may not be strictly overlapping.
+%TODO this make no sense - address ambiguity more clearly
 We simply allow the double colon (::) to type a single keyword in multiple ways.
@@
 \begin{mathpar}
-%\centering 
+\hspace{-0.8cm} %no idea why, but this is better than \centering here
 \inferrule* [Right=int\_resolve]
-{k:\tilde{\tau} \\ \tilde{\tau} \vdash int \geq 1}
+{k:\tilde{\tau} \\ \tilde{\tau} \models int \geq 1}
 {k :: int}
+\and
+\inferrule* [Right=order\_rule]
+{k1,k2 \in C \\ k1 \neq k2}
+{ord(k1,k2) :: Rule}
 \end{mathpar}
 
-Note that we do not have an application rule over probabilistic types - types must be resolved to learn a rule over a keyword.
-In the case that there is not enough evidence to resolve a type, no type-dependent rules may be learned over that keyword.
-
-Taking the example type inference rules above, we can run an example inference.
-For example, if the training set contained [(``bar",1),(``bar",ON)], the resulting type would be bar::[bool=2,int=1] (considering that the literal 1 may act as either an int or a boolean).
+In the case that there is not enough evidence to resolve a probabilistic type, no type-dependent rules may be learned over that keyword.
+We are still able to learn rules such as {\scriptsize ORDER}, which do not depend on resolved typed.

### 2017-01-22 CAV17/secs/learner.tex
more learner and commands

@@
 The goal of the learner is to derive rules from the intermediate representation of the training set generated by the translator.
-We an interface for uses to define rules that should be learned.
-Each instance of the interface corresponds to a different class of of configuration errors, such as missing entry errors, ordering errors, and fine-grained value correlation errors. 
+We describe an interface to define the different classes of rules that should be learned.
+Each instance of the interface corresponds to a different class of of configuration errors, such as missing entry errors, ordering errors, and integer correlation errors. 
 These errors can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
+
+%TODO define rule
+
+We use an approach similar to \textit{association rule learning}~\cite{agrawal1993mining}, a technique that can be summarized as inductive machine learning.
+Association rule learning is best suited to learn rules over sets of keys, which in the configuration domain are integer correlation and missing keyword rules.
+Sequence mining~\cite{} is a more appropriate technique for learning ordering rules, and again another approach may be a better fit for rules over a single keyword, as is needed for probabilistic types.
+We highlight here only two key metrics from these approaches that are most relevant to verification tasks; \textit{support} and \textit{confidence}.
+
+Support is the number of times the set of keywords in the proposed rule will be 
+Confidence is
+
+\para{Order}
+
+\para{Missing}
 
@@
 It
-
-\para{Order}
-
-\para{Missing}
 

### 2017-01-22 CAV17/secs/postanal.tex
more learner and commands

@@
 
+Define a graph with labeled, weighted edges $G = (V,E)$ such that:
 \iffalse
-
-Define a graph with labeled, weighted edges $G = (V,E)$ such that:
-
     V \def { keywords }
@@
     E \def { (v_1, v_2, l, w) }
+\fi
 
@@
 
-Structure:
-    - Definition
-        > Degree (in-degree + out-degree) for each node
+\para {Definition}
+Degree (in-degree + out-degree) for each node
 
@@
 
-            IN_DEGREE(k) = ||
+\iffalse    IN_DEGREE(k) = ||
 
-            \forall keyword k \in rules, in_degree()
+    $\forall keyword k \in rules, in\_degree()$
+\fi
 
@@
 
-    - Semantics
-        > Intuitively, keywords that are seen together more often
-          with defined relationships
-          are more likely to generate rules within the learner.
+\para {Semantics}
+Intuitively, keywords that are seen together more often with defined relationships are more likely to generate rules within the learner.
  (it would be nice to show this with a quick derivation)
@@
 
-            - adequate support
-                we have seen the keywords together x number of times
+1) adequate support -we have seen the keywords together x number of times
 
-            - adequate confidence
-                how many times out of the x number of times 
-                was the relationship true?
+2) adequate confidence - how many times out of the x number of times was the relationship true?
 
+\iffalse
 - Open Questions
@@
 
+\fi
 \subsection{Complexity Measure}
@@
 metric is a heuristic that intends to approximate the quetion, 
-{\it how much redundancy exists in a configuration file, when considering
-probabilistic constraints imposed by the problem domain}?
+ how much redundancy exists in a configuration file, when considering
+probabilistic constraints imposed by the problem domain?
 
@@
 content of a constrained configuration file.
-
-\fi

### 2017-01-22 CAV17/secs/trans.tex
more learner and commands

@@
 
-Formally, a probabilistic types is a set of counts over a set $\mathcal{T}$ of basic types.
-A probabilistic type, $\tilde{\tau} \in \tilde{\mathcal{T}}$, is a set of pairs $\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$. 
-A keyword has a probabilistic type, expressed $k:\tilde{\tau}$, which without any evidence remains as {\scriptsize EMPTY}.
-The count for $(\tau_i,c_i) \in \tilde{\tau}$ is incremented each time a new example value that matches to type $\tau_i$ is encountered for a particular key, as shown in the {\scriptsize BOOL\_INT} and {\scriptsize BOOL} rules.
+A probabilistic type is a set of counts over a set $\mathcal{T}$ of basic types.
+Formally, we define a space of probabilistic types $\tilde{\mathcal{T}}$, where $\ptype=\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$ is a set of pairs, such that $\ptype \in \tilde{\mathcal{T}}, \tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$.
+Every keyword has a probabilistic type, expressed $k:\ptype$, which, without any evidence, remains {\scriptsize EMPTY}.
+The count for $(\tau_i,c_i) \in \ptype$ is incremented each time a new example value that matches to type $\tau_i$ is encountered for a particular key, using the update notation $\update$.
 
@@
 \inferrule* [Right=bool\_int]
-{(k,v) \in C \\ v \in \{0,1\}}
-{k:[int\pluseq 1,bool\pluseq 1]}
+{(k,v) \in C \\ v \in \{0,1\} \\ k:\ptype}
+{k:\ptype\update[int\pluseq 1,bool\pluseq 1]}
+\and
+\inferrule* [Right=bool]
+{(k,v) \in C \\ v \in \{ON,OFF\} \\ k:\ptype}
+{k:\ptype\update[bool\pluseq 1]}
 \\
@@
 \inferrule* [Right=bool\_resolve]
-{k:\tilde{\tau} \\ \tilde{\tau} \models bool \geq 2 \land \ast \leq 1}
+{k:\ptype \\ \ptype \models bool \geq 2 \land \ast \leq 1}
 {k :: bool}
 \\
-\and
-\inferrule* [Right=bool]
-{(k,v) \in C \\ v \in \{ON,OFF\}}
-{k:[bool\pluseq 1]}
 \and
@@
 
-In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \tilde{\tau} \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
+In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
 The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
 In this case, we allow a probabilistic type to resolve to a boolean if we have two counts for boolean, and no more than one count for any other basic type ($\ast$).
-We use the notation, $\tilde{\tau} \models p$, to denote a probabilistic type whose counts hold on the predicate $p$.
+We use the notation, $\ptype \models p$, to denote a probabilistic type whose counts hold on the predicate $p$.
 Taking the type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
@@
 \inferrule* [Right=int\_resolve]
-{k:\tilde{\tau} \\ \tilde{\tau} \models int \geq 1}
+{k:\ptype \\ \ptype \models int \geq 1}
 {k :: int}

### 2017-01-22 CAV17/secs/arch.tex
reword to academic stlye

--- 2017-01-21 CAV17/secs/arch.tex
@@
 
-\para{Rule refinement.}
-\ennan{It seems so far I do not know how exactly this part works. 
-Maybe we can write through this part after finish the 
-section 6.}
+\para{Post Analysis.}
+Finally, the logically structured representation of learned rules allows for a further post analysis stage.
+This novel extension infers knowledge on the accepted rules that can improve the output of the system..
+As a case study, we build a graph to model the learned rules.
+We analyze the properties of this graph to construct an ordering of rules by their importance, 
+  as well as to produce a measure of complexity for any configuration of the target system.
+While the metrics in used in \app are effective, they are not intended to be exhaustive.
+The information contained in the structured representation of the learned rules, 
+  is a unique benefit of the learning algorithm, as contrasted with other machine learning techniques.

### 2017-01-22 CAV17/secs/limit.tex
did we try to get this paper rejected last time?

@@
 \para{Legal misconfigurations.}
-While \app can check for diverse configuration errors without
-human intervention, most of the existing proactive 
-misconfiguration detection techniques,
-including \app, cannot handle configuration errors
-resulting from events that occurred during system runtime.
-Such configuration errors are referred to as {\em legal misconfigurations}%
-~\cite{yin11anempirical}. In particular, 
-many parameter misconfigurations have 
-perfectly legal types and values, 
-but do not deliver the functionality intended by users. 
-For example, after a website's traffic significantly increases,
-the parameter {\tt key\_buffer\_size} in MySQL may not 
-be able to handle increasingly more data traffic,
+Most of the existing proactive misconfiguration detection techniques, cannot handle configuration errors resulting from events that occurred during system runtime.
+Such configuration errors are referred to as {\em legal misconfigurations}~\cite{yin11anempirical}. 
+In particular, many parameter misconfigurations have perfectly legal types and values, but do not deliver the functionality intended by users. 
+For example, after a website's traffic significantly increases, the parameter {\tt key\_buffer\_size} in MySQL may not  be able to handle increasingly more data traffic,
    thus leading to outage of the whole system.
-These cases are more difficult to detect by
-automatic checkers and may require more user training or
-better configuration design.
-A potential solution is to combine existing misconfiguration diagnosis
-tools, \eg, X-ray~\cite{attariyan12x-ray} 
-and ConfAid~\cite{attariyan10automating},
-with \app in order to enhance 
-misconfiguration checking capability.
+While \app does not explicitly use any runtime information, we are still able to detect such errors, for example Sec.~\ref{sec:motiv4}.
+Since \app relies on the collective knowledge of the training set, as long as the training set is mostly correct with respect to legal misconfigurations, these can still be detected.
 

### 2017-01-22 CAV17/secs/arch.tex
2/3 of learner maybe

@@
 
-\para{Initial phase.}
+\para{Initial phase}
 We start with the assumption 
@@
 
-\para{Translator.}
+\para{Translator}
 The translator module first parses the input training  
@@
 
-\para{Learning.}
+\para{Learning}
 The input of the learner is a set of files that have been translated
@@
 
-\para{Post Analysis.}
+\para{Post Analysis}
 Finally, the logically structured representation of learned rules allows for a further post analysis stage.
-This novel extension infers knowledge on the accepted rules that can improve the output of the system..
+This novel extension infers knowledge on the accepted rules that can improve the output of the system.
 As a case study, we build a graph to model the learned rules.

### 2017-01-22 CAV17/secs/learner.tex
2/3 of learner maybe

--- 2017-01-21 CAV17/secs/learner.tex
@@
 The goal of the learner is to derive rules from the intermediate representation of the training set generated by the translator.
-We an interface for uses to define rules that should be learned.
-Each instance of the interface corresponds to a different class of of configuration errors, such as missing entry errors, ordering errors, and fine-grained value correlation errors. 
+We describe an interface to define the different classes of rules that should be learned.
+Each instance of the interface corresponds to a different class of of configuration errors, such as missing entry errors, ordering errors, and integer correlation errors. 
 These errors can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
 
+A rule is an implication relationship, $X \implies p(X,Y)$, between two possibly empty sets of keywords $X,Y \subset \keys$, where $\keys$ is the set of unique keys from the training set and the predicate $p$ is the one of the classes of configuration errors (order, missing, etc).
+Implicitly we interpret this to means that if the keywords $X\cup Y$ appear in a configuration file, we expect the predicate $p$ to hold.
+The task of the learning algorithm is to transform a training set to a set of rules, weighted with \textit{support} and \textit{confidence}.
+These two key metrics are taken from \textit{association rule learning}~\cite{agrawal1993mining}, a technique that can be summarized as inductive machine learning.
+In the configuration verification domain, standard association rule learning is best suited to learn integer correlation and missing keyword rules.
+In fact, a more specialized technique for learning ordering rules would be sequence mining~\cite{}, and again another approach may be a better fit for rules over a single keyword, as is needed for probabilistic types.
+Since the full algorithm details are out-of-scope of this paper, here we only describe in detail the metrics which are most relevant to verification.
+
+%TODO math def of support and confidence
+Each power set of keywords, $\{X,Y\}$, is assigned a support and confidence measure during the learning process.
+Support is the number of times the set of keywords in the proposed rule have been seen the in the training set.
+Confidence is the number of times the rule predicate has held true over the given keywords.
+In the learning process, these are given threshold, below which a rule will be reject for lack of evidence.
+
+\para{Order}
+Ordering errors take the form $X \implies order(X,Y)$, where $|X|,|Y|=1$ and the keyword $X$ must come before the keyword $Y$ in any configuration file.
+
+\para{Missing}
+$X \implies missing(X,Y)$, where $|X|,|Y|=1$ and the keyword $X$ must appear in the same file as the keyword $Y$ in any configuration file.
+
 \para{Type}
-In \app, probabilistic typing is implemented as an instance of the learning interface than can be easily extended to support more types. 
+The type rule is a set of rules over multiple predicates, which take the form $X \implies isType\ast(X)$, where $|X|=1, |Y|=0$ and $\ast$ matches all the basic types (string, int, etc).
+In \app, probabilistic typing is implemented as an instance of the learning interface.
+This module will specify the counting and resolution type judgments from Sec.~\ref{sec:ptypes}.
 It
 
-\para{Order}
-
-\para{Missing}
-
 \para{Integer Correlation}
-Fine grained errors (Aaron)
+\app supports two types of integer correlation rules, coarse-grained and fine-grained.
+Coarse-grained rules follow $X \implies compare(X,Y)$, where $|X|,|Y|=1$ and $compare \in \{<,=,>\}$, such that $X$ must hold $compare$ to $Y$.
+Fine-grained rules follow $X \implies compare(X,Y)$, where $|X|=2,|Y|=1$ and $compare \in \{<,=,>\}$, such that for $k_1,\ k_2 \in X,\ k1*k2$ must hold $compare$ to $Y$.
+These rules also implement a typing judgment over the keywords probabilistic type.
+To avoid learning too many false positives, we restrict this rule to either $size*int=size$, $int*size=size$, or $int*int = int$.
+Without probabilistic typing, we would also learn, for example, $int*int=size$.
+%TODO Aaron
 

### 2017-01-22 CAV17/secs/limit.tex
2/3 of learner maybe

@@
 
-\para{Legal misconfigurations.}
+%TODO move this - it is not a limitation
+\para{Legal misconfigurations}
 Most of the existing proactive misconfiguration detection techniques, cannot handle configuration errors resulting from events that occurred during system runtime.
@@
    thus leading to outage of the whole system.
-While \app does not explicitly use any runtime information, we are still able to detect such errors, for example Sec.~\ref{sec:motiv4}.
+While \app does not explicitly use any runtime information, we are still able to detect such errors, for example Sec.~\ref{ex:fine}.
 Since \app relies on the collective knowledge of the training set, as long as the training set is mostly correct with respect to legal misconfigurations, these can still be detected.
 
-\para{Misconfiguration across software components.}
-As exposed by Yin {\em et al.}~\cite{yin11anempirical},
+\para{Misconfiguration across software components}
+As reported by Yin {\em et al.}~\cite{yin11anempirical},
 cross-software configuration correlation problems also account
@@
 
-\para{Network configuration verification.}
+\para{Network configuration verification}
 \app mainly focuses on software configurations, \eg, MySQL and Apache,
@@
 
-\para{More complex configuration structure.}
+\para{More complex configuration structure}
 Currently, \app mainly targets key-value configuration files,

### 2017-01-22 CAV17/secs/motiv.tex
2/3 of learner maybe

--- 2017-01-20 CAV17/motiv.tex
@@
 
-\para{Example~1: Ordering error.} 
+\para{Example~1: Ordering error} 
 Ordering errors were reported by Yin {\em et al.}~\cite{yin11anempirical} and our first
@@
 
-\para{Example~2: Fine-grained value correlation error.} 
+%TODO would be nice to have these as subsection or somehow be able to ref specific examples
+\para{Example~2: Fine-grained value correlation error}
+\label{ex:fine}
 Our second misconfiguration example~\cite{correlation} 
@@
 
-\para{Example~3: Missing entry error.} 
+\para{Example~3: Missing entry error} 
 Many critical system outages result from the fact that an important
@@
 
-\para{Example~4: Type errors.} 
+\para{Example~4: Type errors} 
 Many system performance problems are caused by 

### 2017-01-22 CAV17/secs/trans.tex
2/3 of learner maybe

@@
 To solve this, we rely on the fact that keywords in a configuration file must be unique within their context, and rename all keywords with their context.
-The keys for the sample configuration \ref{lst:1.cnf} would then be [``{\tt foo[server]}'',``{\tt bar[client]}''] internally to the intermediate representation.
+The set of unique keys, $\keys$, for the sample training set in Figure ~\ref{fig:tset} would then be [``{\tt foo[server]}'',``{\tt bar[client]}''] internally to the intermediate representation.
+We will call the set of key-value pairs $C$.
 
@@
 
+\subsection{Probabilistic Types}
+\label{sec:ptypes}
 An additional challenge is that it is not always possible to fully determine the type of key based on a single example value. 
@@
 Formally, we define a space of probabilistic types $\tilde{\mathcal{T}}$, where $\ptype=\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$ is a set of pairs, such that $\ptype \in \tilde{\mathcal{T}}, \tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$.
-Every keyword has a probabilistic type, expressed $k:\ptype$, which, without any evidence, remains {\scriptsize EMPTY}.
+Every keyword $k\in\keys$ has a probabilistic type, expressed $k:\ptype$, which, without any evidence, remains {\scriptsize EMPTY}.
 The count for $(\tau_i,c_i) \in \ptype$ is incremented each time a new example value that matches to type $\tau_i$ is encountered for a particular key, using the update notation $\update$.

### 2017-01-22 CAV17/secs/eval.tex
strucutre for evaluation

@@
 \section{Evaluation}
+
+We evaluate this approach using our implementation, \app.
+We use two training sets, a preexisting set of MySQL configuration from~\cite{xu15systems} of 256 files,
+ and our own set of collected MySQL configuration from Github of 1120 files.
+In our evaluation we focus on MySQL for consistency, but any configuration language (that can be parsed to the intermediate representation from Sec.~\ref{sec:trans}) can be used.
+
+We run \app on 80\% as our collected configuration files, selected at random, as a training set to generate rules.
+The remaining 20\% is used as a testing set to be verified by the learned rules.
+We report the number of rules learned and number of errors detected in Table~\ref{table:learning}.
+Note that in contrast to program verification, we do not have an oracle for determining if a reported error is a true error, or a false positive.
+When learning a specification for a program, that specification can be checked by violating said specification and testing the program.
+Because misconfigurations are dependent on the rest of the system, the available hardware, and the usage patterns, we cannot simulate the all conditions to determine if a reported error will cause system failure.
+Indeed, as evidenced by Example~\ref{ex:fine}, some misconfigurations will only cause greater than expected performance degradation.
+In this case, the very definition of a true error is necessarily imprecise.
 
@@
 \caption{Results of Learning}
-\label{table-training}
-\begin{tabular}{|c|c|c|c|}
+\label{table:learning}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-{\bf Class of Error } & {\bf Total Rules Learned from Training Set} & {\bf Rules Detected on Benchmark set} & {\bf Thresholds}\\ 
+{\bf Class of Error } & {\bf \# Rules Learned} & {\bf \# Rules Detected} & {\bf Support} & {\bf Confidence}\\ 
 \hline
 \hline
-10   & 2.997     & &  \\ \hline
-50   & 46.4208   & &  \\ \hline
-100  & 206.7798  & &  \\ \hline
-150  & 431.7772  & &  \\ \hline
-200  & 856.6383  & &  \\ 
+Order        & 2.997     & &  & \\ 
+Missing      & 46.4208   & &  & \\ 
+Type         & 206.7798  & &  & \\ 
+Fine-Grain   & 431.7772  & &  & \\ 
+Coarse-Grain & 856.6383  & &  & \\ 
 \hline
@@
 
+The errors reported may have a varying impact on the system, ranging from failing to start, runtime crash, or performance degradation.
+Since this is a probablistic system, it is also that some errors are false positives, a violation of the rule has no effect on the system.
+It it therefore desirable to sort the reported errors in order of severity. 
+To achieve this we use the post analysis metric described in Sec.~\ref{sec:ruleorder}.
+To estimate the impact of this metric, we track the rank of known true positives with, and without, the augmented rule ordering in Table~\ref{table:order}.
+
+\begin{table}[h]
+\centering
+\caption{Effect of Post Analysis Rule Ordering for known true positives}
+\label{table:order}
+\begin{tabular}{|c|c|c|c|}
+\hline
+{\bf Class of Error} & {\bf Reference} & {\bf Rank w/o} & {\bf Rank w/} \\
+\hline
+\hline
+Order        & Ex.~\ref{ex:order}   & & \\ 
+Missing      & Ex.~\ref{ex:miss}    & & \\ 
+Type         & Ex.~\ref{ex:type}    & & \\ 
+Fine-Grain   & Ex.~\ref{ex:fine}    & & \\ 
+Coarse-Grain & Ex.~\ref{ex:coarse}  & & \\ 
+\hline
+\end{tabular}
+\end{table}
+
+The checker stage of \app is the only one facing an end user that wants to verify a new configuration file.
+However, the user may also want to interface with the previous stages as well. 
+We have only build rules for MySQL, a relatively well documented language, but any configuration language can be analyzed with \app given a training set.
+In this case, the user will need to rebuild the rule set.
+A user also may want to update the support of confidence threshold to report more or fewer error, as is needed for their application.
+It is then important that the learning process is reasonably fast.
+The times reported in Table~\ref{table:training} were run on a single thread of a Intel i5-3450 CPU @ 3.10GHz with 16GB of RAM.
+
 \begin{table}[h]
@@
 \caption{Training time for different datasets}
-\label{table-training}
+\label{table:training}
 \begin{tabular}{|c|c|c|}
 \hline
-{\bf The \# of Files for Training} & {\bf Training Time ConfigC (sec.)} & {\bf Training Time \app (sec.)}\\ 
+{\bf The \# of Files for Training} & {\bf ConfigC Training Time (s)} & {\bf \app Training Time (s)}\\ 
 \hline

### 2017-01-22 CAV17/secs/learner.tex
strucutre for evaluation

@@
 
-With the learned rules and constraints in hand (generated
-by the learner module),
-\app checks whether any entry in a target configuration file
-violates the learned rules and constraints.
-For a given configuration file, \app parses it the same
-way employed in the translator, thus obtaining a structured
-and typed representation for the target configuration file.
-Then, the checker uses two sub-modules (shown in 
-Figure~\ref{fig-overview}) to check the target
-configuration file based on rules and constraints.
+With the learned rules generates by the learner module,
+  \app checks whether any entry in a target configuration file violates the learned rules and constraints.
+\app parses a verification target configuration file the same way employed in the translator for learning,
+  obtaining a structured and typed representation.
+Then, the checker applies the learner to build the set of relations observed in the file.
+For any relation that violates a known rule, the checker will output the predicate and keyword sets associated with that rule, as well as the learned support and confidence values.
+Since the tool is probabilistic, we provide the user with these values to determine if they rule must be satisfied in their application on a case-by-case basis.
+For instance, the \texttt{key\_buffer} misconfiguration from Sec.
+\ref{ex:fine} will only be noticeable if the application experiences a heavy traffic load, so the user may choose to ignore this error if they are confident this will not be an issue.
 

### 2017-01-22 CAV17/secs/postanal.tex
strucutre for evaluation

@@
 
-VeriConf can output the series of learned rules extracted from its training
-set as described in $\S$\ref{sec-learn}.
+VeriConf can output the set of learned rules from the training set as described in $\S$\ref{sec-learn}.
+Note that the ability to inspect the learned rule set is a special property of this technique.
+The core task, building a model from unlabeled examples to classify files as either correct or incorrect, is also a classic problem for other machine learning techniques such as neural networks~\cite{nn1,nn2,nn3}.
+When applying machine learning to verification of configuration files, this is not, however, an ideal approach.
+The resulting model from a neural network is easily not amenable to analysis~\cite{nnAnalysis1,nnAnalysis2}.
+The simple structure of rules with weights from an association rule learning-like approach, will instead allows us to do further inference on the resulting model.
 
 \subsection{Rule Ordering}
+\label{sec:ruleorder}
 

### 2017-01-22 CAV17/secs/eval.tex
small stuff

@@
 \label{table:learning}
+\setlength{\tabcolsep}{0.5em}
 \begin{tabular}{|c|c|c|c|c|}
@@
 \label{table:order}
+\setlength{\tabcolsep}{1em}
 \begin{tabular}{|c|c|c|c|}
@@
 The times reported in Table~\ref{table:training} were run on a single thread of a Intel i5-3450 CPU @ 3.10GHz with 16GB of RAM.
+We see the drastic difference in times here because ConfigC assumes a correct training set, and learns every relation derivable.
+With \app, we instead only process rule that meet the required support and confidence, reducing the cost of resolve to a consistent set of rules.
 
@@
 \label{table:training}
+\setlength{\tabcolsep}{1em}
 \begin{tabular}{|c|c|c|}
 \hline
-{\bf The \# of Files for Training} & {\bf ConfigC Training Time (s)} & {\bf \app Training Time (s)}\\ 
+{\bf The \# of Files for Training} & {\bf ConfigC (s)} & {\bf \app (s)}\\ 
 \hline

### 2017-01-22 CAV17/secs/related.tex
small stuff

--- 2017-01-19 CAV17/rel.tex
@@
 
-\para{Configuration languages.}
+\para{Configuration languages}
 There have been several language support efforts proposed for preventing
@@
 
-\para{Misconfiguration detection.}
+\para{Misconfiguration detection}
 Misconfiguration detection techniques aim at checking configuration
@@
 
-\para{Misconfiguration diagnosis.}
+\para{Misconfiguration diagnosis}
 Many misconfiguration diagnosis approaches have been proposed%
@@
 
-\para{Misconfiguration tolerance.}
+\para{Misconfiguration tolerance}
 There have been several efforts proposed to test whether systems are 

### 2017-01-22 CAV17/secs/trans.tex
strucutre for evaluation
small stuff

@@
 \section{Translator}
-\label{sec-trans}
+\label{sec:trans}
 
@@
 Taking the configuration \ref{lst:1.cnf}, we can assume {\tt foo} is a boolean type by the grammar of MySQL,
-  but the keyword {\tt bar} could either be a integer type or a Boolean type.
+  but the keyword {\tt bar} could either be a integer type or a boolean type.
 Consider that we would like to learn a rule that the boolean keywords should have the same values ($eq(\texttt{foo},\texttt{bar})$).
@@
 The count for $(\tau_i,c_i) \in \ptype$ is incremented each time a new example value that matches to type $\tau_i$ is encountered for a particular key, using the update notation $\update$.
+We also denote a keyword value pair that exists in some configuration file as $(k,v) \in C$.
 
+\begin{figure}
 \begin{mathpar}
-\hspace{-0.4cm} %no idea why, but this is better than \centering here
+\hspace{-1cm} %no idea why, but this is better than \centering here
 \inferrule* [Right=Empty]
@@
 \end{mathpar}
+\caption{Type judgments for boolean equality rules with probabilistic types}
+\label{fig:ptypes}
+\end{figure}
 
@@
 Taking the type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
-We would derive the probabilistic type \texttt{bar}$:[bool=3,int=1]$, which then resolves to \texttt{bar}$::bool$.
+Using the rules from Fig.~\ref{fig:ptypes}, we would derive the probabilistic type \texttt{bar}$:[bool=3,int=1]$, which then resolves to \texttt{bar}$::bool$.
 
@@
 
-In the case that there is not enough evidence to resolve a probabilistic type, no type-dependent rules may be learned over that keyword.
-We are still able to learn rules such as {\scriptsize ORDER}, which do not depend on resolved typed.
+In the case that there is not enough evidence to resolve a probabilistic type to a basic type, no type-dependent rules may be learned over that keyword.
+We are still able to learn rules such as {\scriptsize ORDER}, which do not require any resolved type.

### 2017-01-22 CAV17/secs/learner.tex
small stuff
add definitions to post-analysis section
and comment hook for \rahul{}

@@
 These errors can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
+
+\rahul{and we may even be able to say that these insidiuous issues are much
+harder to pin down by the standard delta-debugging technique of starting a
+system multiple times with different configuration settings}
 
@@
 Without probabilistic typing, we would also learn, for example, $int*int=size$.
-%TODO Aaron
+%TODO include exactly how many false positive we prune with types over our training set? Here or in eval?
+
+%TODO Aaron - add to learinign module section describe implemetnation?
+
+\app is primarily implemented in Haskell.
+The source code for our implementation is available at {\em (URL omitted for blind review)}.
+
+The learning and checking modules are developed to allow
+for customized extensibility. In order to verify a configuration file
+against a new type of error, a user only needs to provide a new type
+that is an instance of the \textit{Attribute} typeclass (\ie, define some
+functions over that type). 
+In particular, for each type of error the users
+wish to detect, they must implement three functions;
+\lstinline{learn}, \lstinline{merge}, and \lstinline{check}.
 
@@
 \subsection{Implementation}
-
-\app is primarily implemented in Haskell, with a bit of mongo.
-The translator is developed as a parser for the grammar described in $\S$\ref{sec-trans}. 
-The learner and checker module fully implemented the design in $\S$\ref{sec-learn} and $\S$\ref{sec-checker}, respectively.
-
-The learning and checking modules are developed to allow
-for customized extensibility. In order to verify a configuration file
-against a new type of error, a user only needs to provide a new type
-that is an instance of the \textit{Attribute} typeclass (\ie, define some
-functions over that type). 
-In particular, for each type of error the users
-wish to detect, they must implement three functions;
-\lstinline{learn}, \lstinline{merge}, and \lstinline{check}.
-
-The source code for our implementation is available at {\em (URL omitted for blind review)}.

### 2017-01-22 CAV17/secs/postanal.tex
add definitions to post-analysis section
and comment hook for \rahul{}

@@
 Define a graph with labeled, weighted edges $G = (V,E)$ such that:
-\iffalse
-    V \def { keywords }
 
-Where
+    $$V = \{ keywords \}$$
 
-    E \def { (v_1, v_2, l, w) }
-\fi
+and
 
-Where the label $l$ defines the relationship, and the weight $w$ is
-defined as $w = \frac{true - false}{total}$ for that relationship.
+    $$E = \{ (v_1, v_2, l, w) \}$$
+
+Where the label $l \in L$ indicates the predicate $p$ extracted by the learner,
+$L$ is the set of all predicates learned,
+and the weight $w$ is defined as
+
+    $$w = \frac{true - false}{total}$$
+
+for that relationship. For notational convenience later in this section
+we will refer to $w_{v_1, v_2, l}$ as referring to the weight of the
+edge $(v_1, v_2, l, w)$. We will refer to this graph as the {\bf Rule Graph}
+in further analysis.
+
 Note that due to support / confidence assertions in the learner, we
@@
 \para {Definition}
-Degree (in-degree + out-degree) for each node
+We define a measure of degree for each node as the sum of in-degree
+and out-degree defined in the usual way. Explicitly, for a vertex $x \in V$:
 
-Define in-degree and out-degree in the usual way:
+    $$DEGREE(x) = OUT\_DEGREE(x) + IN\_DEGREE(x)$$
 
-\iffalse    IN_DEGREE(k) = ||
+    $$DEGREE(x) = \sum_{l \in L} \sum_{v \in V} w_{x, v, l} + \sum_{l \in L} \sum_{v \in V} w_{v, x, l}$$
 
-    $\forall keyword k \in rules, in\_degree()$
-\fi
+The more rules of high confidence extracted for a keyword by the learner, 
+the higher the $DEGREE$ of the corresponding vertex in the Rule Graph.
+We may use this measurement to examine which keywords in the configuration
+space examined by the learner are most important - which keyword configurations
+are the most constrained / most constraining.
 

### 2017-01-22 CAV17/secs/eval.tex
scraping fomr github

@@
 To estimate the impact of this metric, we track the rank of known true positives with, and without, the augmented rule ordering in Table~\ref{table:order}.
+We compare how close the updated rank is compared to the ideal rank, which was calculated by ennan and estimates the potential severity of an error related to those keywords.
+Maybe we actually compare measure the distance from the ideal rank, so that a value of 0 is good.
 
@@
 \setlength{\tabcolsep}{1em}
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-{\bf Class of Error} & {\bf Reference} & {\bf Rank w/o} & {\bf Rank w/} \\
+{\bf Class of Error} & {\bf Reference} & {\bf Rank w/o} & {\bf Rank w/} & {\bf Ideal Rank}\\
 \hline

### 2017-01-22 code2/download.sh

@@ -1,0 +1,29 @@
+PASS=$1
+
+if [ "" == "$PASS" ] 
+then 
+  echo "need password"
+  exit
+fi
+
+for i in {1..2}
+do
+# get the lists of cnf files
+  filename="results$i.txt"
+  curl --user santolucito:$PASS "https://api.github.com/search/code?q=mysql+extension:cnf+size:>100&page=$i&per_page=100" | jq '.items | map(.html_url)' > $filename
+  
+ 
+# clean the format of the lists
+  sed -i -e 's/github/raw\.githubusercontent/g' "$filename"
+  sed -i -e 's/blob\///g' "$filename"
+  sed -i -e 's/\"//g' "$filename"
+  sed -i -e 's/\,//g' "$filename"
+
+# wget the files
+  while read l; do
+    NEW_ID=$(cat /dev/urandom | tr -dc 'a-z0-9' | fold -w 32 | head -n 1)
+    wget -O "downloads/$NEW_ID.cnf" $l
+  done <$filename
+  #sleep 5m #api has rate limit
+done
+

### 2017-01-22 code2/src/Benchmarks.hs

@@ -19,7 +19,8 @@ learnTarget :: [ConfigFile Language]
 learnTarget = case Settings.pROBRULES of
     Settings.Test -> genSet "testLearn/"
     Settings.NonProb -> genSet "benchmarkSet/correctMySQL/"
-    Settings.Prob -> genSet "learningSet/MySQL/"
+    --Settings.Prob -> genSet "learningSet/MySQL/"
+    Settings.Prob -> take 500 $ genSet "trainingDownload/downloads/"
   where
     genSet s =
       map (\x -> (s++x,u $ T.readFile (s++x), MySQL))
@@ -125,5 +126,5 @@ group6 = map (map makeError) [
 
 testBenchSet :: [ErrorReport]
 testBenchSet = map (map makeError) [
-    [(("benchmarkSet/test/test1.cnf","a[mysqld]"),("benchmarkSet/test/test1.cnf","b[mysqld]"),INTREL)]
+    [(("benchmarkSet/test","a[mysqld]"),("benchmarkSet/test/test1.cnf","b[mysqld]"),INTREL)]
   ]

### 2017-01-22 code2/src/Main.hs

@@ -67,17 +67,17 @@ printSummary ers fitnesses = do
   putStrLn "Table of results"
   putStrLn "Error Class, Number, Support Threshold, Confidence Threshold"
   putStrLn $ (numOfClass TYPE)++", - , - "
-  putStrLn $ numOfClass INTREL++", "++(show (Settings.intRelSupport `percent` length fitnesses))++"%, "++(show ((Settings.intRelSupport -Settings.intRelConfidence) `percent` Settings.intRelSupport))++"%"
-  putStrLn $ numOfClass FINEGRAINED++", "++(show (Settings.fineGrainSupport `percent` length fitnesses))++"%, "++(show ((Settings.fineGrainSupport -Settings.fineGrainConfidence) `percent` Settings.fineGrainSupport))++"%"
-  putStrLn $ numOfClass MISSING++", "++(show (Settings.keywordCoorSupport `percent` length fitnesses))++"%, "++(show ((Settings.keywordCoorSupport -Settings.keywordCoorConfidence) `percent` Settings.keywordCoorSupport))++"%"
-  putStrLn $ numOfClass ORDERING++", "++(show (Settings.orderSupport `percent` length fitnesses))++"%, "++(show ((Settings.orderSupport -Settings.orderConfidence) `percent` Settings.orderSupport))++"%"
+  putStrLn $ numOfClass INTREL++", "++(show (Settings.intRelSupport `percent` 256))++"%, "++(show ((Settings.intRelSupport -Settings.intRelConfidence) `percent` Settings.intRelSupport))++"%"
+  putStrLn $ numOfClass FINEGRAINED++", "++(show (Settings.fineGrainSupport `percent` 256))++"%, "++(show ((Settings.fineGrainSupport -Settings.fineGrainConfidence) `percent` Settings.fineGrainSupport))++"%"
+  putStrLn $ numOfClass MISSING++", "++(show (Settings.keywordCoorSupport `percent` 256))++"%, "++(show ((Settings.keywordCoorSupport -Settings.keywordCoorConfidence) `percent` Settings.keywordCoorSupport))++"%"
+  putStrLn $ numOfClass ORDERING++", "++(show (Settings.orderSupport `percent` 256))++"%, "++(show ((Settings.orderSupport -Settings.orderConfidence) `percent` Settings.orderSupport))++"%"
   putStrLn $ "Total, "++(show $sum fitnesses)++", -, -"
   putStrLn "------------"
[…]

### 2017-01-22 code2/src/Settings.hs

@@ -17,17 +17,39 @@ module Settings where
   -- an abusive of notation here, we use slightly different interprtation of the words - same idea in the end
   --TODO unify numerical comutations to be consistent with true interpretation of support and confidence
 
-  --support and maxFalse
-  intRelSupport = 30 :: Int 
-  intRelConfidence = 2 :: Int
+  --TODO this should really be read from training set dir
+  totalFiles = 1120
+
+  --TODO use confidence instead of maxFalse everytwhere
+  thresholds  :: (Double,Double) -> (Int,Int)
+  thresholds (s,c) = (support,conf)
+   where
+    support = floor $ s * (fromIntegral totalFiles)
+    conf =  support - (floor $ c*fromIntegral support)
 
   --support and maxFalse
-  fineGrainSupport = 55 :: Int
-  fineGrainConfidence = 1 :: Int
+  intRelSupport = 
+    --fst $ thresholds(0.1,0.9) 
+    30 :: Int 
+  intRelConfidence = 
+    --snd $ thresholds(0.1,0.9) 
+    2 :: Int
+
+  --support and maxFalse
+  fineGrainSupport = 
+    -- fst $ thresholds(0.1,0.9)  
+    45 :: Int
+  fineGrainConfidence = 
+    --snd $ thresholds(0.1,0.9)  
+    3 :: Int
 
   --minTrue (actually minTrue is Support, well kind of) and maxFalse
-  keywordCoorSupport =  7 :: Int 
-  keywordCoorConfidence = 2 :: Int
+  keywordCoorSupport = 
+    --fst $ thresholds(0.1,0.9)  
+    7 :: Int 
+  keywordCoorConfidence = 
+    --snd $ thresholds(0.1,0.9) 
+    2 :: Int
 
 {-  
   typeSupport =
@@ -35,6 +57,10 @@ module Settings where
 -}
 
   --minTrue and maxFalse
-  orderSupport = 30  :: Int
-  orderConfidence = 1 :: Int
+  orderSupport = 
+    --fst $ thresholds(0.1,0.9) 
+    30  :: Int
+  orderConfidence = 
+    --snd $ thresholds(0.1,0.9)  
+    1 :: Int
 

### 2017-01-22 code2/trainingDownload/download.sh

@@ -1,0 +1,30 @@
+PASS=$1
+
+if [ "" == "$PASS" ] 
+then 
+  echo "need password"
+  exit
+fi
+
+for i in {10..20}
+do
+# get the lists of cnf files
+  filename="results-innodb-$i.txt"
+  curl --user santolucito:$PASS "https://api.github.com/search/code?q=innodb+extension:cnf+size:>100&page=$i&per_page=100" | jq '.items | map(.html_url)' > $filename
+  
+# if the api call fails, you end up with an empty file, and dont do any wgets, just wait 5m 
+# clean the format of the lists
+  sed -i -e 's/github/raw\.githubusercontent/g' "$filename"
+  sed -i -e 's/blob\///g' "$filename"
+  sed -i -e 's/\"//g' "$filename"
+  sed -i -e 's/\,//g' "$filename"
+
+# wget the files
+  while read l; do
+    NEW_ID=$(cat /dev/urandom | tr -dc 'a-z0-9' | fold -w 32 | head -n 1)
+    wget -O "downloads/$NEW_ID.cnf" $l
+  done <$filename
+  sleep 5m #api has rate limit
+done
+
+# this will generate duplicates, remove duplicates with 'fdupes -d -N'

### 2017-01-22 CAV17/secs/related.tex
cav17: related work

@@
 
-Language support has been considered a promising way  
-to tackle configuration problems~\cite{xu15systems}.
-Nevertheless, a practical language-based misconfiguration
-detection approach still remains an open problem.
+Configuration verification has been considered a promising way  
+to tackle misconfiguration problems~\cite{xu15systems}.
+Nevertheless, a practical and automatic configuration
+verification approach still remains an open problem.
 
-\para{Configuration languages}
-There have been several language support efforts proposed for preventing
+\para{Language-support misconfiguration checking.}
+There have been several language-support efforts proposed for preventing
 configuration errors introduced by fundamental deficiencies in
 either untyped or low-level languages. For example, in the network
-configuration management area, it is easy for administrators to
+configuration management area, administrators often
 produce configuration errors in their routing configuration files.
@@
 services for convenient network reasoning and management.
+Compared with the above efforts, \app mainly focuses on software systems, 
+\eg, MySQL and Apache, and our main purpose is to automate configuration
+verification rather than proposing new languages 
+to convenient configuration-file writing.
 
-Compared with these existing efforts, 
-our work mainly focused on software systems, \eg, MySQL and Apache,
-rather than network configurations. In addition, we do not need 
-the user of \app to manually write a configuration file with the proposed
-language, since \app can automatically parse a target configuration
-file into our proposed representation.
-
-Huang {\em et al.} proposed a specification for configuration validation%
-~\cite{huang15confvalley}. We will 
-discuss this work in the misconfiguration
-detection part.
+The closest effort to \app is ConfigC~\cite{santolucitoCAV},
+which aims to learn configuration-checking rules from a given training
+set. Compared with \app, ConfigC has the following disadvantages.
+First, ConfigC requires the configuration files in the training set must 
+be correct, which is quite impractical, because it is very difficult to
+determine a correct configuration set in reality.
+Second, ConfigC can only cover less types of misconfigurations than \app. 
+Finally, the training time of ConfigC is much longer than \app.
 
@@
 the checked configuration files do not satisfy these rules.
-
-Huang {\em et al.}~\cite{huang15confvalley} proposed a 
+Huang {\em et al.}~\cite{huang15confvalley},
+for example, proposed a 
 language, ConfValley, to validate 
@@
 also have been proposed~\cite{yuan11context, zhang14encore}.
-EnCore~\cite{zhang14encore} is the work closest to \app.
-It introduces a template-based
+EnCore~\cite{zhang14encore} is one of representative work in this area.
+EnCore introduces a template-based
 learning approach to improve the accuracy of their learning results.
@@
 techniques cannot handle.
-Compared to EnCore, \app has the following advantages.
-Firstly, \app does not rely on 100\% correctness in the files of the given configuration set. 
-Secondly, \app not only covers many more types of 
-misconfigurations, but also introduces probabilistic types.
-Finally, \app is a language framework, which can 
-even be used to write configuration files, but EnCore is only a 
-misconfiguration detection tool.
+Compared with EnCore, \app has the following advantages.
+First, \app does not rely on any template. 
+Second, EnCore cannot detect missing entry errors, type errors,
+ordering errors and fine-grained integer correlation errors,
+but \app can detect all of them.
+Finally, \app is a very automatic system, but
+EnCore needs significant human interventions, \eg, system parameters
+and templates.
 
@@
 tolerant to misconfigurations~\cite{xu13do}. 
-%ConfErr~\cite{} uses a human error hodel from psychology and
-%linguistics to inject misconfigurations into systems.
-SPEX~\cite{xu13do} takes a white-box testing approach to automatically
+SPEX~\cite{xu13do}, for example, takes 
+a white-box testing approach to automatically
 extract configuration parameter constraints from source code and generates 
@@
 
-Making systems gracefully handle misconfigurations and eliminating
+\com{Making systems gracefully handle misconfigurations and eliminating
 configuration errors are two orthogonal directions.
@@
 Our work belongs to the latter case, which is used to 
-prevent configuration errors before system outages.
+prevent configuration errors before system outages.}

### 2017-01-22 CAV17/secs/limit.tex
cav17: limitation

@@
 and possible solutions.
-
-%TODO move this - it is not a limitation
-\para{Legal misconfigurations}
-Most of the existing proactive misconfiguration detection techniques, cannot handle configuration errors resulting from events that occurred during system runtime.
-Such configuration errors are referred to as {\em legal misconfigurations}~\cite{yin11anempirical}. 
-In particular, many parameter misconfigurations have perfectly legal types and values, but do not deliver the functionality intended by users. 
-For example, after a website's traffic significantly increases, the parameter {\tt key\_buffer\_size} in MySQL may not  be able to handle increasingly more data traffic,
-   thus leading to outage of the whole system.
-While \app does not explicitly use any runtime information, we are still able to detect such errors, for example Sec.~\ref{ex:fine}.
-Since \app relies on the collective knowledge of the training set, as long as the training set is mostly correct with respect to legal misconfigurations, these can still be detected.
 

### 2017-01-23 CAV17/secs/learner.tex
writing some things on implementation
more comments

@@
 
-%TODO Aaron - add to learinign module section describe implemetnation?
-
 \app is primarily implemented in Haskell.
@@
 
-The learning and checking modules are developed to allow
-for customized extensibility. In order to verify a configuration file
-against a new type of error, a user only needs to provide a new type
-that is an instance of the \textit{Attribute} typeclass (\ie, define some
-functions over that type). 
-In particular, for each type of error the users
-wish to detect, they must implement three functions;
-\lstinline{learn}, \lstinline{merge}, and \lstinline{check}.
+We have developed \app to be easily extendable and customizable. Each of the rules are implemented as an instance of the \textit{Learnable} typeclass:
+
+\begin{lstlisting}[language=Haskell, xleftmargin=.01\textwidth]
+class (Eq a, Show a, Ord a, Countable b) => Learnable a b where
+  buildRelations :: IRConfigFile -> RuleDataMap a b
+  merge :: Countable b => [RuleDataMap a b] -> RuleDataMap a b
+  check :: a -> b -> b -> Maybe b
+  toError :: FilePath -> (a, b) -> Error
+\end{lstlisting}
+
+Each of the rules that check for a particular type of error are implemented in three functions, \textit{buildRelations} for constructing a map of possible observations to a count of how often they are observed, a \textit{merge} function for taking multiple sets of built relations from different files and combining them into one set of relations (weighted accordingly), and finally, a \textit{check} that takes an individual relation mapping from our built set of relations, the observation in the file we are verifying, and whether there is a violation of that particular observation of the relation.
+(There is a fourth \textit{toError} function that serves as a helper function to pretty-print the output of \app.) Hence, if we can define how to build the relations to verify against a new type of error, a system for combining these relations with weights across multiple files that are seen, along with a mechanism for checking whether each individual relation was violated or not, we can extend \app to check for new types of errors.
+Furthermore, the approach of defining a method to build relations from a single file as well as a method to combine these relations facilitates the parallelization of our implementation, since each of the \textit{buildRelations} calls can work parlellely on each file before the results are combined with the \textit{merge} step.
+
+Each of the outputs of the \textit{buildRelations} is in the form \textit{RuleDataMap a b}, where \textit{a} is a group of entities between which we want to define a relation (for example, a pair of keywords for Missing, Order, and Integer Correlation) and \textit{Countable b} is a tally of likelihoods of each possible outcome of the relation that can be weighted and combined over multiple files (for example, a count of files that exhibit the relation versus not for Missing or a count of files that exhibit less than, equals, or greater than between a pair of keywords for Ordering or a set of probabilities for Type rules).
+
+Once the program has finished merging together a set of built relations over every example file in the learning set, we have implemented a \textit{check} function for each of the rules, where we input the group of entities under which a relation is defined, the expected observation on that relation, and the actually observed observation in the file we are checking.
+If the observed instance is inconsistent with the relations built from our training set files, then we would see it reported.
+In the probablistic setting of our tool, we would implement cutoffs to tune our \textit{check} to ignore observed relations under a certain significance level.
 

### 2017-01-23 code2/src/Benchmarks.hs
parallel merge for fineGrain and filter bad *.cnf

@@ -20,7 +20,7 @@ learnTarget = case Settings.pROBRULES of
     Settings.Test -> genSet "testLearn/"
     Settings.NonProb -> genSet "benchmarkSet/correctMySQL/"
     --Settings.Prob -> genSet "learningSet/MySQL/"
-    Settings.Prob -> take 500 $ genSet "trainingDownload/downloads/"
+    Settings.Prob -> take 250 $ genSet "trainingDownload/downloads/"
   where
     genSet s =
       map (\x -> (s++x,u $ T.readFile (s++x), MySQL))

### 2017-01-23 code2/src/Convert.hs

@@ -48,9 +48,12 @@ makeUniq lang ls = case lang of
     in
       f (head ls) ls
 
+-- TODO strip "set-variable ="
 stripComment :: Language -> T.Text -> T.Text
 stripComment l t = case l of
-  MySQL -> T.filter (/=';') $ T.takeWhile (/='#') t
+  MySQL ->  if any ((flip T.isInfixOf) t) ["<%","%>i","{%","%}"] 
+            then ""
+            else T.takeWhile (\x-> x/='#' && x/=';') t
   HTTPD -> T.takeWhile  (/=';') t
 
 -- | for now we are just using spaces and = to seperate keywords and values
@@ -61,7 +64,9 @@ seperateVals t =
     hasDelim = any isDelimeter $ T.unpack t
     ts = T.split isDelimeter (T.strip t)
     isDelimeter c = (c=='=') || (c==' ')
+    rmSetVar = (T.dropWhile (=='=')). T.strip. fst. T.breakOn "set-variable"
+    clean = rmSetVar. T.toLower. T.strip
   in
     if hasDelim
-    then (T.strip $ head ts, T.strip $ last ts)
-    else (t,"")
+    then (clean $ head ts, clean$ last ts)
+    else (clean t,"")

### 2017-01-23 code2/src/Learners/FineGrained.hs

@@ -16,11 +16,14 @@ import Settings
 
 import qualified Data.Map as M
 import qualified Data.Text as T
+import qualified Data.Text.Read as T
 import qualified Data.Char as C
 import qualified Data.List as L
 import qualified Data.Bits as B
 import           Data.Maybe 
 import           System.Directory
+
+import Control.Parallel
 
 import Debug.Trace
 
@@ -83,10 +86,21 @@ instance Learnable R.FineGrained Formula where
     ,errMsg = "FINE GRAINED ERROR: Expected "++(show k1)++" * "++(show k2)++(show rd)++(show k3)
     }
 
+{- 
+paralleize the merge?a-}
+pfold full  = let
+  ms' = M.splitRoot full
+  ms = map pfold ms'
+  mappend m1 m2 = M.foldlWithKey combineFlips m1 m2
+ in
+  if M.size full < 25 
+  then M.empty `mappend` full
+  else (head ms `par` last ms) `pseq` (foldl1 mappend ms) 
+
 --all IRLines must have only ints as values (filtered out by this point)
 toFineGrained :: (IRLine,IRLine,IRLine) -> (FineGrained,Formula)
 toFineGrained (IRLine k1 v1, IRLine k2 v2, IRLine k3 v3) = let
-    asInt v = (read $ T.unpack (fst $ T.partition C.isNumber v)) * (fromMaybe 1 $ units v)
+    asInt v = ((either (\x->0) fst $T.decimal v) * (fromMaybe 1 $ units v)) ::Int
     formula v1 v2 v3 = if
      | v1*v2 < v3  -> Formula {gt=0,eq=0,lt=1}
      | v1*v2 == v3 -> Formula {gt=0,eq=1,lt=0}
@@ -102,6 +116,8 @@ toFineGrained (IRLine k1 v1, IRLine k2 v2, IRLine k3 v3) = let
 combineFlips :: RuleDataMap FineGrained Formula -> FineGrained -> Formula -> RuleDataMap FineGrained Formula
 combineFlips old (FineGrained k1 k2 k3) v = if 
   | M.member (FineGrained k1 k2 k3) old -> M.adjust (add v) (FineGrained k1 k2 k3) old
+  --since we have a custom Eq instance, which already accounts for order, we shouldnt hit the second check, 
+  -- but we do (checked wiht trace), so I leave it in
[…]

### 2017-01-23 code2/src/LearningEngine.hs

@@ -16,6 +16,8 @@ import Control.DeepSeq
 import qualified Data.Text.IO as T
 import qualified Data.Map.Strict as M
 
+import Debug.Trace
+
 -- | collect contraints from each file indepentantly
 -- this should be parmap
 learnRules :: [ConfigFile Language] -> RuleSet
@@ -33,14 +35,14 @@ learnRules fs = let
 -- | use the learning module instances to decide probabiliity cutoff and the sort
 resolveRules :: [RuleSet] -> RuleSet
 resolveRules rs = RuleSet
-  { order   = f order
-  , missing = f missing
-  , intRel  = f intRel
-  , typeErr = f typeErr
-  , fineInt = f fineInt
+  { order   = f "o" order
+  , missing = f "m" missing
+  , intRel  = f "i" intRel
+  , typeErr = f "t" typeErr
+  , fineInt = f "f"fineInt
   }
  where
-  f classOfErr =  merge (map classOfErr rs)
+  f s classOfErr =  trace s $ merge (map classOfErr rs)
 
 -- | call each of the learning modules
 buildAllRelations :: M.Map Keyword Int -> IRConfigFile -> RuleSet

### 2017-01-23 code2/src/Types/Rules.hs

@@ -97,9 +97,9 @@ data FineGrained = FineGrained Keyword Keyword Keyword
   deriving (Show,Ord,Generic,ToJSON,FromJSON,NFData)
 instance Eq FineGrained where
   (==) (FineGrained k1 k2 k3) (FineGrained k1' k2' k3')= 
+     k3 == k3' &&
      ((k1==k1' && k2==k2') || 
-     (k1==k2' && k2==k1')) &&
-     k3 == k3'
+     (k1==k2' && k2==k1'))
 
 instance Locatable FineGrained where
   keys (FineGrained k1 k2 k3) = [k1,k2,k3]

### 2017-01-23 code2/trainingDownload/interactiveRemove.sh

@@ -1,0 +1,16 @@
+cnt=1
+for filename in downloads/*.cnf 
+do
+  clear
+  cat $filename
+  echo
+  echo "-------------------------"
+  echo "file $cnt"
+  cnt=$[cnt + 1]
+  echo "Press Enter to Accept, or N to delete"
+  read input </dev/tty
+  if [ "$input" == "N" ]
+  then
+    rm $filename
+  fi
+done

### 2017-01-23 CAV17/secs/concl.tex

\section{Conclusion}

In this paper, we introduce \app, a highly modular framework 
that allows automatic verification of configuration files.
\app employs a translator to parse a training set
of configuration files into an intermediate representation,
and then uses a learner module to derive rules.
\app finally uses post analysis module to refine these learned
rules, enabling users to verify the configuration files of
their interest.
Our evaluation based on a real-world misconfiguration
dataset~\cite{configdataset} shows that \app is able to
correctly detect configuration errors
including ordering, missing entry, integer correlation
and type errors.

### 2017-01-23 CAV17/secs/postanal.tex
expand post-analysis section

@@
 When applying machine learning to verification of configuration files, this is not, however, an ideal approach.
-The resulting model from a neural network is easily not amenable to analysis~\cite{nnAnalysis1,nnAnalysis2}.
+The resulting model from a neural network is not easily amenable to analysis~\cite{nnAnalysis1,nnAnalysis2}.
 The simple structure of rules with weights from an association rule learning-like approach, will instead allows us to do further inference on the resulting model.
@@
 
-    $$w = \frac{true - false}{total}$$
+    $$w = \frac{true}{total}$$
 
@@
 
-The more rules of high confidence extracted for a keyword by the learner, 
-the higher the $DEGREE$ of the corresponding vertex in the Rule Graph.
-We may use this measurement to examine which keywords in the configuration
-space examined by the learner are most important - which keyword configurations
-are the most constrained / most constraining.
+\iffalse
 
@@
 
+\fi
+
 \para {Semantics}
+
+The more rules of high confidence extracted for a keyword by the learner, 
+the higher the $DEGREE$ of the corresponding vertex in the Rule Graph.
+We may use this measurement to examine which keywords in the configuration
+space examined by the learner are most important - which keyword configurations
+are the most constrained / most constraining.
+
+Note that since the Rule Graph, as it is formulated in this paper, weights edges
+by a {\it ratio} of predicate hits to total keyword observations, the weight
+of an edge is {\bf dependent only on the confidence of the corresponding rule
+and independent of the support}. We address this issue by pruning nodes of
+inadequate support in the learner, but an alternative formulation of the rule
+graph (in particular the  of edges in the graph) may provide additional
+power for graph analysis techniques to take support into account
+as well as confidence.
+
+\rahul{Not sure how important this last point about alternative Rule Graph
+formulation is - we certainly want to make sure the reader understands that
+this is an area that can be easily expanded on, but don't want to distract
+from the fundamental semantics here.}
+
+It is also worth noting that how good of a heuristic the $DEGREE$ metric is for
+\"importance of a configuration parameter\" is dependent on the coverage
+of the learnable predicate set encompassed by $L$. The more this predicate
+set covers the true configuration parameter relationships in the system,
+the better the heuristic.
+
+\iffalse
+
 Intuitively, keywords that are seen together more often with defined relationships are more likely to generate rules within the learner.
@@
 2) adequate confidence - how many times out of the x number of times was the relationship true?
+
+\fi
 
@@
 
+A common goal for software projects is managing complexity. As
+constraints accumulate over the lifecycle of a project additional
+configuration file complexity often grows, with the danger of
+making code brittle and unwieldy. For code, Kolomogrov complexity
+can be a good indicator of whether a solution is bloated and 
+needs to be refactored.
+
+The intermediate representation produced VeriConf's learner stage
+may be used to analyze the complexity of a configuration file.
+
 INCLUDE SHORT BACKGROUND ON CODE COMPLEXITY. We define a measurement
@@
 content of a constrained configuration file.
+
+\iffalse
+
+Use the listing in figure 2 to put together an example of why the
+naive implementation of complexity doesn't give as much of an idea
+of what is going on as our heuristic.
+
+\fi

### 2017-01-23 code2/src/Learners/FineGrained.hs
oh wait, parallel is junk - doesnt help at all

@@ -86,14 +86,15 @@ instance Learnable R.FineGrained Formula where
     ,errMsg = "FINE GRAINED ERROR: Expected "++(show k1)++" * "++(show k2)++(show rd)++(show k3)
     }
 
-{- 
+{-
+TODO this doesnt help at all, whyyyy 
 paralleize the merge?a-}
 pfold full  = let
   ms' = M.splitRoot full
   ms = map pfold ms'
   mappend m1 m2 = M.foldlWithKey combineFlips m1 m2
  in
-  if M.size full < 25 
+  if M.size full < 50 
   then M.empty `mappend` full
   else (head ms `par` last ms) `pseq` (foldl1 mappend ms) 
 

### 2017-01-23 code2/src/LearningEngine.hs

@@ -30,7 +30,7 @@ learnRules fs = let
   keyCounts = foldl (\rs ir-> M.insertWith (+) (keyword ir) 1 rs) M.empty (concat fs')
   rs = map (buildAllRelations keyCounts) fs'
  in
-  resolveRules rs --`using` parRuleSet
+  resolveRules rs `using` parRuleSet
 
 -- | use the learning module instances to decide probabiliity cutoff and the sort
 resolveRules :: [RuleSet] -> RuleSet

### 2017-01-23 CAV17/secs/motiv.tex
cav17: motivating examples

@@
 should appear before {\tt mysql.so}, as shown
-below: \ennan{Mark, please update all the motivating examples'
-output results according
-to our newest version implementation.}
+below:
 
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-    ORDERING ERROR: Expected "extension" "recode.so"
-    BEFORE "extension" "mysql.so"
+    ORDERING ERROR: Expected "extension=recode.so"
+    BEFORE "extension=mysql.so"
 \end{lstlisting}
@@
 %TODO would be nice to have these as subsection or somehow be able to ref specific examples
-\para{Example~2: Fine-grained value correlation error}
+\para{Example~2: Fine-grained integer correlation error}
 \label{ex:fine}
@@
 cooperatively, while {\tt join\_buffer} and {\tt sort\_buffer} are 
-created by each thread for private use; thus, the maximum amount
-of used key buffer, \ie, {\tt key\_buffer\_size}, should be larger than 
+created by each thread for private use; thus, {\tt key\_buffer\_size},
+\ie, the maximum amount of used key buffer, should be larger than 
 {\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
-Clearly, in the above example, it does not hold, 
-so this misconfiguration causes MySQL to load very slowly.
+In the above example, however, it does not hold.
 
@@
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-    INTEGER RELATION ERROR:
-    Expected "key_buffer_size" >= "max_connections" * "sort_buffer_size"
+  FINE GRAINED INTEGER RELATION ERROR:
+  Expected "max_connections" * "sort_buffer_size"
+               =< "key_buffer_size"
 \end{lstlisting}
 
-We can see that during the learning process not only do we learn simple statements that compare two values, 
-but also we learn more complex correlations. We call these more complex relations fine-grained value correlations, and the errors
-\emph{fine-grained value correlation errors}. 
-This type of error is more sophisticated than the simple value correlation that some tools can detect~\cite{yin11anempirical, zhang14encore}.
-A typical value correlation error
-states that one entry's value should have a certain correlation with
-another entry's value. For example, in MySQL,
-the value of {\tt max\_connections} should be higher than
-{\tt mysql.max\_persistent}.
-
-Our tool can learn this simple correlation as well, but learning more complex properties requires a different 
-approach to the learning 
-process. We need to track several variables. It is not enough just to compare them, but we need to learn, as in this particular case, which
-invariant must be preserved. It was pointed out by Xu {\em et al.}~\cite{xu15hey} that
-detecting fine-grained value correlation errors 
-is a much more challenging
-task than the normal value correlation problem.
-To the best of our knowledge, \app is the first tool that
-is able to check such fine-grained value correlation problems.
+The above example is a complex integer correlation, which implicitly
+includes a computational correlation among different entries
+in the configuration file.
+We call these complex integer correlations as 
+{\em fine-grained integer correlations}. 
+Our tool can detect simple integer correlation---one entry's
+value should have a certain correlation with another entry's 
+value---as well.
+For example, in MySQL, the value of {\tt max\_connections} 
+should be higher than {\tt mysql.max\_persistent}.
+While few existing tools~\cite{yin11anempirical, zhang14encore}
+can detect the simple integer correlation errors,
+to the best of our knowledge, \app is the first effort capable of
+detecting fine-grained integer correlation problems.
 
@@
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-    MISSING KEYWORD ERROR: Expected "overlay" "ppolicy"
+    MISSING ENTRY ERROR: Expected "overlay" "ppolicy"
     in the same file: "include" "schema/ppolicy.schema"
@@
 \para{Example~4: Type errors} 
-Many system performance problems are caused by 
+Many system availability problems are caused by 
 assigning incorrect type of values to some key in configuration
-files. Consider the following real-world misconfiguration file: 
+files. Consider the following real-world misconfiguration
+file~\cite{typeerror}: 
 a user tries to install MySQL and she needs to initiate the path
 of the log information generated by MySQL.
-This user puts the following assignment in her MySQL
+This user puts the following entry assignment in her MySQL
 configuration file:
@@
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-    general_log = /var/log/mysql/mysql.log
+    slow-query-log = /var/log/mysql/slow.log
 \end{lstlisting}
 
-Unbeknowest to this user, the entry ``general\_log'' should be an 
-integer, not a string. In MySQL, there is another entry named
-``general\_log\_file'' used to specify the log path.
+Unbeknowest to this user, the entry ``slow-query-log'' should be an 
+integer, not a string. This misconfiguration will lead to 
+MySQL fails to start~\cite{querylog}. In MySQL, there is another entry 
+named ``slow-query-log-file'' used to specify the log path.
 With \app, this user can get the following result:
@@
     TYPE ERROR: Expected a Int with P=1.0 for
-    "general_log [mysql]"
+    "slow-query-log"
 \end{lstlisting}

### 2017-01-23 code2/src/Benchmarks.hs
final learning results - many small bug fixes

@@ -14,17 +14,20 @@ import qualified Data.Text.IO     as T
 import           System.Directory
 import           System.IO.Unsafe
 
+import Debug.Trace
 
 learnTarget :: [ConfigFile Language]
 learnTarget = case Settings.pROBRULES of
     Settings.Test -> genSet "testLearn/"
     Settings.NonProb -> genSet "benchmarkSet/correctMySQL/"
-    --Settings.Prob -> genSet "learningSet/MySQL/"
-    Settings.Prob -> take 250 $ genSet "trainingDownload/downloads/"
+    Settings.Prob -> genSet "learningSet/MySQL/"
+    --Settings.Prob -> genSet "trainingDownload/downloads/"
   where
     genSet s =
       map (\x -> (s++x,u $ T.readFile (s++x), MySQL))
       (u (listDirectory s))
+
+traceMe cs = trace (concatMap (\(f,t,l) -> (show f++"\n")) cs) cs
 
 -- verification file paths
 vFilePaths :: [FilePath]
@@ -32,7 +35,7 @@ vFilePaths = if Settings.bENCHMARKS
     then benchmarkFiles
     else userFiles
   where
-    userFiles = map ("user/"++) $ u $ listDirectory "user"
+    userFiles = map ("user2/"++) $ u $ listDirectory "user2"
     benchmarkFiles = map getFileName $ concat benchmarks
 
 benchmarks :: [ErrorReport]

### 2017-01-23 code2/src/Checker.hs

@@ -15,6 +15,7 @@ import qualified Data.Map.Merge.Strict as M
 import qualified Data.Map.Strict as M
 import           System.Directory
 
+import qualified Data.Text as T
 import Debug.Trace
 
 verifyOn :: RuleSet -> ConfigFile Language -> ErrorReport
@@ -41,14 +42,17 @@ filterRules fKs rs = RuleSet {
        order   = f order
       ,missing = f' missing 
       ,intRel  = f intRel 
-      ,typeErr = f typeErr 
+      ,typeErr = f'' typeErr 
       ,fineInt = f fineInt
      }
    where
      f classOfErr  =  M.filterWithKey (\e _ -> keysMatch (keys e)) (classOfErr rs)
      f' classOfErr =  M.filterWithKey (\e _ -> oneKeyMatch (keys e)) (classOfErr rs)
+     f'' classOfErr=  M.filterWithKey (\(e::TypeErr) _ -> keyPartMatch (keys e)) (classOfErr rs)
      keysMatch ks   = and $ map (\k->elem k fKs) ks
      oneKeyMatch ks = or $ map (\k->elem k fKs) ks
+     keyPartMatch ks = elem (T.takeWhile (/='[') $head ks) (map (T.takeWhile (/='[')) fKs) 
+
 
 --TODO apply to each rule type in a rule set individually
 --TODO make Ruleset an instance of functor or something? 

### 2017-01-23 code2/src/Convert.hs

@@ -63,7 +63,7 @@ seperateVals t =
   let
     hasDelim = any isDelimeter $ T.unpack t
     ts = T.split isDelimeter (T.strip t)
-    isDelimeter c = (c=='=') || (c==' ')
+    isDelimeter c = (c=='=') -- || (c==' ')
     rmSetVar = (T.dropWhile (=='=')). T.strip. fst. T.breakOn "set-variable"
     clean = rmSetVar. T.toLower. T.strip
   in

### 2017-01-23 code2/src/Learners/Common.hs

@@ -27,7 +27,7 @@ showErr rawEs printFxn =
 -}
 
 --embedOnce :: Learnable a => [a] -> [(a,RuleData AntiRule)]
-embedOnce = map (\r -> (r, (AntiRule 1 0 1)))
+embedOnce = map (\r -> (r, (AntiRule {tru=1, fls=0, tot=1})))
 
 combine :: AntiRule -> AntiRule -> AntiRule
 combine (AntiRule tru fls tot) (AntiRule truOp flsOp totOp)
@@ -66,7 +66,13 @@ scale c = if
   | C.toUpper c == 'G' -> 1000000
   | otherwise -> 1 
 
-getMod = fst. T.breakOn "_". keyword
+emptyMod ir= (==) "" $ (snd$ T.breakOn c$ keyword ir)
+  where
+    c = if T.isInfixOf "_" $ keyword ir then "_" else "-"
+getMod ir = fst$ T.breakOn c $ keyword ir
+  where
+    c = if T.isInfixOf "_" $ keyword ir then "_" else "-"
+getContext = snd. T.breakOn "[". keyword
 
 -- does the pair contain just no socket/port, or both
 sockport (ir1,ir2) = not $
@@ -78,11 +84,11 @@ sockport (ir1,ir2) = not $
 --according to Ennan modules do not interact with anything except themselves for Ordering
 --so take the string before the first '_' as the module and only compare those that have equal modules
 --if no modules, the keys are in the same module
+--Additoianlly restict the context, eg [mysql], to be the same
 --Are these lines in the same moudle
 sameConfigModule :: (IRLine,IRLine) -> Bool
 sameConfigModule (ir1,ir2) = let
-  emptyMod x = (==) "" $ (snd$ T.breakOn "_"$ keyword x)
-  sameMod = (emptyMod ir1 && emptyMod ir2) || (getMod ir1 == getMod ir2)
+  sameMod = ((emptyMod ir1 && emptyMod ir2) || (getMod ir1 == getMod ir2)) && (getContext ir1 == getContext ir2)
   --special case for socket and port
   --cant be the same module if only one is socket or port
  in
@@ -90,10 +96,11 @@ sameConfigModule (ir1,ir2) = let
 
 
 --TYPES
-validAsString v = (((T.length $ T.takeWhile C.isAlpha v) > 1) || (T.length v>=3 && T.head v == '"' && T.last v == '"'))
[…]

### 2017-01-23 code2/src/Learners/FineGrained.hs

@@ -68,6 +68,7 @@ instance Learnable R.FineGrained Formula where
   -- instead just rebuild the whole map with combineFlips (only happens once so shouldnt be too bad
   merge rs = let
     rs' = M.unionsWith add rs
+    --merged = M.mapKeysWith add (\fg@(FineGrained k1 k2 k3)-> if k2 > k1 then (FineGrained k2 k1 k3) else fg) rs'
     merged = M.foldlWithKey combineFlips M.empty rs'
     validRule r = (gt r + lt r + eq r)>Settings.fineGrainSupport &&  (gt r <= Settings.fineGrainConfidence || lt r <= Settings.fineGrainConfidence)
    in

### 2017-01-23 code2/src/Learners/KeywordCoor.hs

@@ -66,7 +66,7 @@ instance Learnable R.KeywordCoor AntiRule where
        else True--fls r1 > tru r1
    in
      if (not $agrees rd1 rd2)
-     then Nothing --Just rd1
+     then Just rd1
      else Nothing
 
   toError fname ((KeywordCoor (k1,k2)),rd) = Error{
@@ -91,8 +91,6 @@ embedWith counts rules =
 addCount :: M.Map Keyword Int -> KeywordCoor -> AntiRule -> AntiRule
 addCount counts (KeywordCoor (k1,k2)) rd = let
   kcount k = M.findWithDefault 0 k counts
-  addTotal :: Int -> AntiRule -> AntiRule
-  addTotal i r = r{tot=i}
  in
-  addTotal (kcount k1 + kcount k2) rd
+  rd{tot=(kcount k1 + kcount k2)}
   

### 2017-01-23 code2/src/Learners/TypeErr.hs

@@ -36,8 +36,8 @@ instance Learnable TypeErr QType where
     --NB on takeWhile, types of keywords do not depend on context
     -- this creates a problem with the Chekcer tho...
     toTypeErr :: IRLine -> (TypeErr,QType)
-    toTypeErr ir = (TypeErr (keyword ir),getQType $ value ir)
-    --toTypeErr ir = (TypeErr (T.takeWhile (/= '[') $ keyword ir),getQType $ value ir)
+    --toTypeErr ir = (TypeErr (keyword ir),getQType $ value ir)
+    toTypeErr ir = (TypeErr (T.takeWhile (/= '[') $ keyword ir),getQType $ value ir)
     xs = ["set-variable"]
     f' = filter (\ir -> not $ any (\k -> T.isInfixOf k (keyword ir)) xs) f
    in
@@ -48,17 +48,17 @@ instance Learnable TypeErr QType where
 
   -- 
   check _ rd1 rd2 = let
-     tot = fromIntegral $ sum [string rd1, int rd1, size rd1] 
+     tot = fromIntegral $ sum [string rd1, int rd1, size rd1, bool rd1, path rd1] 
      toProb x = if tot > 10
        then (fromIntegral .x)rd1 / tot 
        else 1
    in
      if --TODO allow 1/0 in place of bool 
-       string rd2 == 1 && toProb string > 0.7 ||
-       path   rd2 == 1 && toProb path> 0.7 ||
-       bool   rd2 == 1 && toProb bool> 0.7 ||
-       int    rd2 == 1 && (toProb int + toProb size > 0.7) ||
-       size   rd2 == 1 && toProb size> 0.7 ||
+       (string rd2 == 1 && toProb string > 0.7) ||
+       (path   rd2 == 1 && (toProb string+ toProb path) > 0.7) ||
+       (bool   rd2 == 1 && (toProb bool + toProb int) > 0.7) ||
+       (int    rd2 == 1 && ((toProb int + toProb size > 0.7) || (toProb int + toProb bool > 0.7))) ||
+       (size   rd2 == 1 && toProb size> 0.7) ||
        tot == 0
      then Nothing
      else Just rd1
@@ -68,4 +68,22 @@ instance Learnable TypeErr QType where
     ,errIdent = TYPE
     ,errMsg = "TYPE ERROR: Expected a "++(show rd)++" for "++(show k)}
[…]

### 2017-01-23 code2/src/LearningEngine.hs

@@ -30,7 +30,7 @@ learnRules fs = let
   keyCounts = foldl (\rs ir-> M.insertWith (+) (keyword ir) 1 rs) M.empty (concat fs')
   rs = map (buildAllRelations keyCounts) fs'
  in
-  resolveRules rs `using` parRuleSet
+  resolveRules rs --`using` parRuleSet
 
 -- | use the learning module instances to decide probabiliity cutoff and the sort
 resolveRules :: [RuleSet] -> RuleSet

### 2017-01-23 code2/src/Settings.hs

@@ -30,18 +30,18 @@ module Settings where
   --support and maxFalse
   intRelSupport = 
     --fst $ thresholds(0.1,0.9) 
-    30 :: Int 
+    27 :: Int 
   intRelConfidence = 
     --snd $ thresholds(0.1,0.9) 
-    2 :: Int
+    1 :: Int
 
   --support and maxFalse
   fineGrainSupport = 
     -- fst $ thresholds(0.1,0.9)  
-    45 :: Int
+    65 :: Int
   fineGrainConfidence = 
     --snd $ thresholds(0.1,0.9)  
-    3 :: Int
+    1 :: Int
 
   --minTrue (actually minTrue is Support, well kind of) and maxFalse
   keywordCoorSupport = 
@@ -59,7 +59,7 @@ module Settings where
   --minTrue and maxFalse
   orderSupport = 
     --fst $ thresholds(0.1,0.9) 
-    30  :: Int
+    17  :: Int
   orderConfidence = 
     --snd $ thresholds(0.1,0.9)  
     1 :: Int

### 2017-01-23 code2/src/Types/IR.hs

@@ -19,7 +19,7 @@ import Types.Common
 import Control.DeepSeq
 
 type ConfigFile a = (FilePath,T.Text, a)
-data Language = MySQL | HTTPD
+data Language = MySQL | HTTPD deriving (Show)
 
 
 

### 2017-01-23 CAV17/secs/arch.tex

@@
 \begin{figure*}[tbp] \centering
-\includegraphics[width=0.88\textwidth]{figs/overview}
+\includegraphics[width=0.84\textwidth]{figs/overview}
 \caption{\app's workflow. The green components represent configuration 
@@
 software configuration files.
-In particular, \app can detect many sophisticated configuration errors, 
-including ordering errors, missing entry errors,
+As shown in Sec.~\ref{sec-motiv}, \app can detect many sophisticated 
+configuration errors, including ordering errors, missing entry errors,
 type errors and integer correlation errors. 
-As depicted in Figure~\ref{fig-overview}, 
-a typical \app verification workflow has three steps:
-translation, learning, and rule refinement. In this section, we briefly
-describe how each step works.
+Figure~\ref{fig-overview} shows
+a typical \app verification workflow with three steps:
+translation, learning, and rule refinement. This section briefly
+describes how each step works.
 
@@
 the type of an entry cannot always be fully determined from 
-a single value, since it is very hard to understand
+a single value, since it is difficult to understand
 the purposes of key-value entries in modern
@@
 we assign several types over a probability distribution. 
-We can later use these more structured files
-as a training set to learn the rules.
+We can later use these well-structured files
+as a ``true'' training set to learn the rules.
 
 \para{Learning}
-The input of the learner is a set of files that have been translated
-into well-structured intermediate representations. 
-The learner employs a learning algorithm named {\em rule association 
-algorithm} to generate various rules,
+The learner reads a set of configuration  files that have been translated
+into well-structured representations. 
+The learner employs a learning algorithm, {\em rule association 
+algorithm}, to generate various rules,
 potentially used to handle different types of configuration errors,
@@
 Because the translator gives the learner probabilistically typed entries,
-the learner is also responsible for determining a type for each entry.
+the learner is also responsible for determining types for these entries.
 

### 2017-01-23 CAV17/secs/motiv.tex

@@
 
-\para{Example~1: Ordering error} 
-Ordering errors were reported by Yin {\em et al.}~\cite{yin11anempirical} and our first
-example illustrates how ordering errors can cause a system to crash. When a user configures PHP 
-to run with the
-Apache HTTP Server, most likely the user will take some already existing configuration files and adapt them
-to suit her needs. The configuration file might contain, among others, 
-the following lines:
+\para{Example~1: Missing entry error} 
+Many critical system outages result from the fact that an important
+entry was missing from the configuration file. 
+We call such a problem a {\em missing entry error}.
+In a public misconfiguration dataset~\cite{configdataset},
+many misconfiguration issues were caused by
+missing entry errors.
+Below is a real-world missing entry error example~\cite{missingentry}:
+when a user wants to configure her PHP and PostgreSQL,
+she needs to use both {\tt pgsql.so} and {\tt curl.so}
+in her {\tt /ctc/php5/conf.d/curl.ini} file.
+Specifically, this is usually
+achieved by the following entries in 
+the curl configuration file:
 
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-    extension = mysql.so
-        ...
-    extension = recode.so
+    extension=pgsql.so
+    extension=curl.so
 \end{lstlisting}
 
-This configuration file will cause the Apache server to 
-fail to start due to a segmentation fault error. 
-This is because, when using PHP in Apache, the extension {\tt mysql.so} 
-depends on {\tt recode.so}, and their relative ordering
-is crucial. 
-We call the above example of a misconfiguration file
-an {\em ordering error}.
-Yin {\em et al.} report that ordering errors widely exist in
-many system configurations, \eg, PHP and MySQL,
-and typically lead to multiple system crash events.
-However, no existing tool can effectively solve 
-or detect this problem~\cite{zhang14encore, xu15systems, xu13do}.
-
-By invoking \app, the user can detect such a configuration error.
-In particular, \app reports that {\tt recode.so} 
-should appear before {\tt mysql.so}, as shown
-below:
+Nevertheless, in this example, the user 
+left out the {\tt extension=pgsql.so} entry, 
+as done by many users~\cite{yin11anempirical, missingentry}, 
+causing a segmentation fault. 
+If the user runs \app on such a misconfiguration file,
+\app would return:
 
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-    ORDERING ERROR: Expected "extension=recode.so"
-    BEFORE "extension=mysql.so"
+    MISSING ENTRY ERROR: Expected "extension=pgsal.so"
+    in the same file: "extension=curl.so"
 \end{lstlisting}
@@
 
-\para{Example~3: Missing entry error} 
-Many critical system outages result from the fact that an important
-entry was missing from the configuration file. 
-We call such a problem a {\em missing entry error}.
-In a public misconfiguration dataset~\cite{configdataset},
-many MySQL failure reports were caused by
-missing entry errors.
-Below is a real-world missing entry error example~\cite{yin11anempirical}:
-when a user wants to use OpenLDAP to enable her directory access
-protocol, she needs to use the password policy overlay. This is usually
-achieved via the following entries in the OpenLDAP configuration file:
-
-\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-    include schema/ppolicy.schema
-    overlay ppolicy
-\end{lstlisting}
-
-When using the password policy overlay in OpenLDAP, 
-users must first include the related schema.
-Leaving out the {\tt include schema/ppolicy.schema} entry, 
-as done by many users~\cite{yin11anempirical}, 
-causes the failure of LDAP. 
-If the user runs \app on such a misconfiguration file,
-\app would return:
-
-\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-    MISSING ENTRY ERROR: Expected "overlay" "ppolicy"
-    in the same file: "include" "schema/ppolicy.schema"
-\end{lstlisting}
-
-\para{Example~4: Type errors} 
+\para{Example~3: Type errors} 
 Many system availability problems are caused by 
@@
 
+\para{Example~4: Ordering error} 
+Ordering errors were reported by Yin {\em et al.}~\cite{yin11anempirical} and our first
+example illustrates how ordering errors can cause a system to crash. When a user configures PHP 
+to run with the
+Apache HTTP Server, most likely the user will take some already existing configuration files and adapt them
+to suit her needs. The configuration file might contain, among others, 
+the following lines:
+
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
+    extension = mysql.so
+        ...
+    extension = recode.so
+\end{lstlisting}
+
+This configuration file will cause the Apache server to 
+fail to start due to a segmentation fault error. 
+This is because, when using PHP in Apache, the extension {\tt mysql.so} 
+depends on {\tt recode.so}, and their relative ordering
+is crucial. 
+We call the above example of a misconfiguration file
+an {\em ordering error}.
+Yin {\em et al.} report that ordering errors widely exist in
+many system configurations, \eg, PHP and MySQL,
+and typically lead to multiple system crash events.
+However, no existing tool can effectively solve 
+or detect this problem~\cite{zhang14encore, xu15systems, xu13do}.
+
+By invoking \app, the user can detect such a configuration error.
+In particular, \app reports that {\tt recode.so} 
+should appear before {\tt mysql.so}, as shown
+below:
+
+\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
+    ORDERING ERROR: Expected "extension=recode.so"
+    BEFORE "extension=mysql.so"
+\end{lstlisting}
+
 %The above result means that we need to assign an integer value to

### 2017-01-23 code2/src/Benchmarks.hs
use user folder to test

@@ -35,7 +35,7 @@ vFilePaths = if Settings.bENCHMARKS
     then benchmarkFiles
     else userFiles
   where
-    userFiles = map ("user2/"++) $ u $ listDirectory "user2"
+    userFiles = map ("user/"++) $ u $ listDirectory "user"
     benchmarkFiles = map getFileName $ concat benchmarks
 
 benchmarks :: [ErrorReport]

### 2017-01-23 CAV17/secs/motiv.tex
fix fine grain

@@
     max_heap_table_size = 128M
-    max_connections = 64
+    max_connections = 8
     thread_cache_size = 8
@@
 
-The user complains that her MySQL load was very high, 
-causing the website's
-response speed to be very slow.
-In this case, {\tt key\_buffer\_size} is used by all the threads
-cooperatively, while {\tt join\_buffer} and {\tt sort\_buffer} are 
-created by each thread for private use; thus, {\tt key\_buffer\_size},
-\ie, the maximum amount of used key buffer, should be larger than 
-{\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
-In the above example, however, it does not hold.
-
-If we run \app on this configuration file, \app  would return:
+The user complains that her MySQL load was very high, causing the website's response speed to be very slow.
+The accepted answer to the post reveals that {\tt key\_buffer\_size} is used by all the threads cooperatively, 
+  while {\tt join\_buffer} and {\tt sort\_buffer} are created by each thread for private use.
+By further consulting the MySQL manual, we are instructed that when setting {\tt key\_buffer\_size} we should consider the memory requirement of other storage engines.
+In a very indirect manner, we have learned that there is a correlation between {\tt key\_buffer\_size} and other buffer sizes of the system.
+\app is able to learn a specific constraint, \ie {\tt key\_buffer\_size} should not be greater than {\tt sort\_buffer\_size} * {\tt max\_connections}.
+If we run \app on the above configuration file, \app will give an explicit answer:
 
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-  FINE GRAINED INTEGER RELATION ERROR:
+  FINE GRAINED ERROR:
   Expected "max_connections" * "sort_buffer_size"
-               =< "key_buffer_size"
+               > "key_buffer_size"
 \end{lstlisting}
@@
 in the configuration file.
-We call these complex integer correlations as 
-{\em fine-grained integer correlations}. 
+We call these {\em fine-grained integer correlations}. 
 Our tool can detect simple integer correlation---one entry's
@@
 should be higher than {\tt mysql.max\_persistent}.
-While few existing tools~\cite{yin11anempirical, zhang14encore}
-can detect the simple integer correlation errors,
-to the best of our knowledge, \app is the first effort capable of
-detecting fine-grained integer correlation problems.
+Few existing tools~\cite{yin11anempirical, zhang14encore}
+can detect simple integer correlation errors,
+but to the best of our knowledge, \app is the first capable of
+detecting fine-grained integer correlation errors.
 
@@
 file~\cite{typeerror}:
+\markk{did this come stackoverflow?} 
 a user tries to install MySQL and she needs to initiate the path
@@
 
-Unbeknowest to this user, the entry ``slow-query-log'' should be an 
+Unbeknownst to this user, the entry {\tt slow-query-log} should be an 
 integer, not a string. This misconfiguration will lead to 
@@
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-    TYPE ERROR: Expected a Int with P=1.0 for
-    "slow-query-log"
+TYPE ERROR: Expected a PType {string = 2, path = 0, int = 37, bool = 7, size = 0} 
+  for "slow-query-log"
 \end{lstlisting}
@@
 Ordering errors were reported by Yin {\em et al.}~\cite{yin11anempirical} and our first
-example illustrates how ordering errors can cause a system to crash. When a user configures PHP 
-to run with the
-Apache HTTP Server, most likely the user will take some already existing configuration files and adapt them
-to suit her needs. The configuration file might contain, among others, 
-the following lines:
+example illustrates how ordering errors can cause a system to crash.
+
+The configuration file might contain, among others, the following lines:
 
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-    extension = mysql.so
      ...
-    extension = recode.so
 \end{lstlisting}
 
-This configuration file will cause the Apache server to 
-fail to start due to a segmentation fault error. 
-This is because, when using PHP in Apache, the extension {\tt mysql.so} 
-depends on {\tt recode.so}, and their relative ordering
-is crucial. 
-We call the above example of a misconfiguration file
-an {\em ordering error}.
-Yin {\em et al.} report that ordering errors widely exist in
-many system configurations, \eg, PHP and MySQL,
-and typically lead to multiple system crash events.
-However, no existing tool can effectively solve 
-or detect this problem~\cite{zhang14encore, xu15systems, xu13do}.
-
 By invoking \app, the user can detect such a configuration error.
-In particular, \app reports that {\tt recode.so} 
-should appear before {\tt mysql.so}, as shown
+In particular, \app reports that {\tt innodb-home-dir} 
+should appear before {\tt innodb-data-file-path}, as shown
 below:
@@
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-    ORDERING ERROR: Expected "extension=recode.so"
-    BEFORE "extension=mysql.so"
+ORDERING ERROR: Expected "innodb-data-home-dir[mysqld]" BEFORE "innodb-data-file-path[mysqld]" 
+  w/ confidence {tru = 17, fls = 1}
 \end{lstlisting}

### 2017-01-23 CAV17/secs/motiv.tex
clarify motiv

@@
     in the same file: "extension=curl.so"
+    w/ confidence ...
 \end{lstlisting}
@@
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-    key_buffer_size = 384M
+  max_connections               = 64
+  thread_cache_size             = 8
+  thread_concurrency            = 8
+
+  key_buffer_size               = 4G
   max_heap_table_size           = 128M
-    max_connections = 8
-    thread_cache_size = 8
-        ...
+
+  join_buffer_size              = 32M
   sort_buffer_size              = 32M    
-    join_buffer_size = 32M
-    read_buffer_size = 32M
-    read_rnd_buffer_size = 8M
-        ...
 \end{lstlisting}

### 2017-01-24 CAV17/secs/motiv.tex
cav17: motivating example

@@
 We call such a problem a {\em missing entry error}.
-In a public misconfiguration dataset~\cite{configdataset},
-many misconfiguration issues were caused by
-missing entry errors.
+In a public misconfiguration 
+dataset~\cite{configdataset}, many misconfiguration issues were 
+reported as missing entry errors.
 Below is a real-world missing entry error example~\cite{missingentry}:
-when a user wants to configure her PHP and PostgreSQL,
-she needs to use both {\tt pgsql.so} and {\tt curl.so}
-in her {\tt /ctc/php5/conf.d/curl.ini} file.
+when a user configures her PHP and PostgreSQL,
+she needs to use both \code{pgsql.so} and \code{curl.so}
+in her \code{/ctc/php5/conf.d/curl.ini} file.
 Specifically, this is usually
@@
     extension=curl.so
+    ...
 \end{lstlisting}
@@
 Nevertheless, in this example, the user 
-left out the {\tt extension=pgsql.so} entry, 
+left out the \code{extension=pgsql.so} entry, 
 as done by many users~\cite{yin11anempirical, missingentry}, 
@@
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
+  ...
   max_connections               = 64
@@
   sort_buffer_size              = 32M    
+  ...
 \end{lstlisting}
 
-The user complains that her MySQL load was very high, causing the website's response speed to be very slow.
-The accepted answer to the post reveals that {\tt key\_buffer\_size} is used by all the threads cooperatively, 
-  while {\tt join\_buffer} and {\tt sort\_buffer} are created by each thread for private use.
-By further consulting the MySQL manual, we are instructed that when setting {\tt key\_buffer\_size} we should consider the memory requirement of other storage engines.
-In a very indirect manner, we have learned that there is a correlation between {\tt key\_buffer\_size} and other buffer sizes of the system.
-\app is able to learn a specific constraint, \ie {\tt key\_buffer\_size} should not be greater than {\tt sort\_buffer\_size} * {\tt max\_connections}.
+The user complains that her MySQL load was very high, 
+causing the website's response speed to be very slow.
+The accepted answer to the post reveals that \code{key\_buffer\_size} 
+is used by all the threads cooperatively, 
+while \code{join\_buffer} and \code{sort\_buffer} are created 
+by each thread for private use.
+By further consulting the MySQL manual, 
+we are instructed that when setting \code{key\_buffer\_size} we should consider the memory requirement of other storage engines.
+In a very indirect manner, we have learned that there is a correlation
+between \code{key\_buffer\_size} and other buffer sizes of the system.
+\app is able to learn a specific constraint, \ie
+\code{key\_buffer\_size} should not be greater than
+\code{sort\_buffer\_size} * \code{max\_connections}.
 If we run \app on the above configuration file, \app will give an explicit answer:
@@
 value---as well.
-For example, in MySQL, the value of {\tt max\_connections} 
-should be higher than {\tt mysql.max\_persistent}.
+For example, in MySQL, the value of \code{key\_buffer} 
+should be larger than \code{max\_allowed\_packet}.
 Few existing tools~\cite{yin11anempirical, zhang14encore}
@@
 files. Consider the following real-world misconfiguration
-file~\cite{typeerror}:
-\markk{did this come stackoverflow?} 
+file in github~\cite{typeerror}:
 a user tries to install MySQL and she needs to initiate the path
@@
 
-Unbeknownst to this user, the entry {\tt slow-query-log} should be an 
+Unbeknownst to this user, the entry \code{slow-query-log} should be an 
 integer, not a string. This misconfiguration will lead to 
@@
 \para{Example~4: Ordering error} 
-Ordering errors were reported by Yin {\em et al.}~\cite{yin11anempirical} and our first
-example illustrates how ordering errors can cause a system to crash.
-
-The configuration file might contain, among others, the following lines:
+Ordering errors in software configurations were first reported by 
+Yin {\em et al.}~\cite{yin11anempirical}, but little existing work
+can detect such sophisticated errors. The following example
+illustrates how the ordering error in a MySQL configuration file
+can cause the system to crash~\cite{innod-ordering}. 
+%The configuration file might contain, among others, the following lines:
 
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
+  innodb_data_file_path          = ibdata1:10M:autoextend
+  innodb_data_home_dir           = /var/lib/mysql
+  innodb_flush_log_at_trx_commit = 1
+  innodb_lock_wait_timeout       = 50
   ... 
@@
 
-By invoking \app, the user can detect such a configuration error.
-In particular, \app reports that {\tt innodb-home-dir} 
-should appear before {\tt innodb-data-file-path}, as shown
+By invoking \app, the user can detect an ordering error in the
+above configuration file.
+In particular, \app reports that \code{innodb\_home\_dir} 
+should appear before \code{innodb\_data\_file\_path}, as shown
 below:
@@
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-ORDERING ERROR: Expected "innodb-data-home-dir[mysqld]" BEFORE "innodb-data-file-path[mysqld]" 
+ORDERING ERROR: Expected "innodb_data_home_dir[mysqld]" BEFORE
+"innodb_data_file_path[mysqld]" 
   w/ confidence {tru = 17, fls = 1}

### 2017-01-24 CAV17/secs/motiv.tex
fix output for rule

@@
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-  FINE GRAINED ERROR:
-  Expected "max_connections" * "sort_buffer_size"
-               > "key_buffer_size"
+[FINE GRAINED ERROR: Expected "max-connections[mysqld]" * "sort-buffer-size[mysqld]"
+  {gt = 63, lt = 5, eq = 0} "key-buffer-size[mysqld]"
 \end{lstlisting}

### 2017-01-24 code2/src/Benchmarks.hs
update final results very slightly
also renamecase studies in test so easier to id

@@ -21,7 +21,6 @@ learnTarget = case Settings.pROBRULES of
     Settings.Test -> genSet "testLearn/"
     Settings.NonProb -> genSet "benchmarkSet/correctMySQL/"
     Settings.Prob -> genSet "learningSet/MySQL/"
-    --Settings.Prob -> genSet "trainingDownload/downloads/"
   where
     genSet s =
       map (\x -> (s++x,u $ T.readFile (s++x), MySQL))

### 2017-01-24 code2/src/Learners/FineGrained.hs

@@ -75,10 +75,9 @@ instance Learnable R.FineGrained Formula where
     M.filter validRule merged
  
   check _ r1 r2 = if
-    | gt r1 > 3 && lt r1 > 3 -> Nothing --ignore rules if they dont have a clear tendancy
     | eq r2 == 1 && (lt r1 > 3 || gt r1 > 3) && eq r1 < 3 -> Just r1
-    | lt r2 == 1 && gt r1 > 3 && lt r1 < 2-> Just r1
-    | gt r2 == 1 && lt r1 > 3 && gt r1 < 2-> Just r1
+    | lt r2 == 1 && gt r1 > Settings.fineGrainSupport && lt r1 <= Settings.fineGrainConfidence -> Just r1
+    | gt r2 == 1 && lt r1 > Settings.fineGrainSupport && gt r1 <= Settings.fineGrainConfidence-> Just r1
     | otherwise -> Nothing
 
   toError fname ((FineGrained k1 k2 k3), rd) = Error{

### 2017-01-24 code2/src/Settings.hs

@@ -38,10 +38,10 @@ module Settings where
   --support and maxFalse
   fineGrainSupport = 
     -- fst $ thresholds(0.1,0.9)  
-    65 :: Int
+    62 :: Int
   fineGrainConfidence = 
     --snd $ thresholds(0.1,0.9)  
-    1 :: Int
+    5 :: Int
 
   --minTrue (actually minTrue is Support, well kind of) and maxFalse
   keywordCoorSupport = 

### 2017-01-24 CAV17/secs/table2.tex
cav17: table 2

\begin{table*}[tbp]
\centering
\caption{Sampled misconfiguration files for error detection evaluation.}
\label{table-casestudy}
\begin{footnotesize}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Error Type} & {\bf Problem Description} & 
{\bf \app Report}  & {\bf Rank w/o} & {\bf Rank w/}\\ 
\hline
\hline
Order & Cannot allocate memory for the buffer pool~\cite{innod-ordering}  
& \ennan{example 4}
& ~ & ~ \\ \hline

Missing & MySQL missing key\_buffer in my.cnf~\cite{missing}
& \ennan{missing key\_buffer}
& ~ & ~ \\ \hline

Type & MySQL cannot start~\cite{querylog}
& \ennan{example 3}
& ~
& ~ \\ \hline

Fine-Grain & MySQL load is very high~\cite{correlation}   
& \ennan{results in example 2) }
& ~ 
& ~ \\ \hline

Coarse-Grain & MySQL server has gone away error~\cite{coarse-grain}
& \ennan{results}
& ~ 
& ~ \\ \hline

\end{tabular}
\end{footnotesize}
\end{table*}

### 2017-01-24 CAV17/secs/postanal.tex

@@
 
-Define a graph with labeled, weighted edges $G = (V,E)$ such that:
+Define a directed hypergraph with labeled, weighted edges $H = (V,E)$ such that:
 
@@
 
-    $$E = \{ (v_1, v_2, l, w) \}$$
+    $$E = \{ (V_s, V_t, l, w) \}$$
 
-Where the label $l \in L$ indicates the predicate $p$ extracted by the learner,
-$L$ is the set of all predicates learned,
-and the weight $w$ is defined as
+Where $V_s$ and $V_t$ are sets of vertices. Intuitively, we may think of the
+hyper-edge as being directed from $V_s$ to $V_t$. The label $l \in L$ indicates
+the predicate $p$ extracted by the learner, where $L$ is the set of all
+predicates learned. The weight $w$ is defined as:
 
@@
 
-for that relationship. For notational convenience later in this section
-we will refer to $w_{v_1, v_2, l}$ as referring to the weight of the
-edge $(v_1, v_2, l, w)$. We will refer to this graph as the {\bf Rule Graph}
+as measured by the learner for that relationship. For notational
+convenience, later in this section
+we shall define $w_{V_1, V_2, l}$ as the weight of the
+hyperedge $(V_1, V_2, l, w)$, and $s_{v_1, v_2, l}$ as the sum of weights
+over all hyperedges where $v_1 \in V_1$ and $v_2 \in V_2$.
+We will refer to this hypergraph as the {\bf Rule Graph}
 in further analysis.
@@
 
-    $$DEGREE(x) = \sum_{l \in L} \sum_{v \in V} w_{x, v, l} + \sum_{l \in L} \sum_{v \in V} w_{v, x, l}$$
+    $$DEGREE(x) = \sum_{l \in L} \sum_{v \in V} s_{x, v, l} + \sum_{l \in L} \sum_{v \in V} s_{v, x, l}$$
 
@@
 relationship to other keywords in a way that might not be
-measurable by current techniques, the learner (and therefore
-consequently the graph) will show these keywords as being
+measurable by current techniques, the learner (and
+consequently the rule graph) will show these keywords as being
 unrelated.
@@
 
-The more rules of high confidence extracted for a keyword by the learner, 
+The more rules of high confidence are extracted for a keyword by the learner, 
 the higher the $DEGREE$ of the corresponding vertex in the Rule Graph.
@@
 inadequate support in the learner, but an alternative formulation of the rule
-graph (in particular the  of edges in the graph) may provide additional
-power for graph analysis techniques to take support into account
-as well as confidence.
+graph (in particular an alternative weighting of edges)
+could provide additional
+information for graph analysis techniques to take support into account
+beyond rule confidence.
 
@@
 
-INCLUDE SHORT BACKGROUND ON CODE COMPLEXITY. We define a measurement
-of complexity based on the calculated correlation. The presented
-metric is a heuristic that intends to approximate the quetion, 
+\para {Definition}
+
+We define a measurement of complexity based on the calculated correlation.
+For a configuration file with a set of keywords $K$ for a system
+with a Rule Hypergraph $H = (V, E)$, we first define $E_{source}(V_s, V_t)$ as
+the set of all hyperedges where a vertex $v_1 \in V_s$ is in the source set and
+a vertex $v_2 \in V_t$ is in the target. Finally we define the size
+of an edge set $|E|$ to be the sum over all weights in the edge set.
+
+and may now define our complexity measure:
+
+\begin{equation}
+    COMPLEXITY(K, H) = \sum_{k \in K} \
+        \begin{cases}
+            1 * (1 - \frac{|E(k, K)|}{|E(k, V)|}) & \text{if}\ \ |E(k, V)| > 0 \\
+            1 & \text{otherwise}
+        \end{cases}
+\end{equation}
+
+\para {Semantics}
+
+The presented metric is a heuristic that intends to approximate the question: 
 how much redundancy exists in a configuration file, when considering
-probabilistic constraints imposed by the problem domain?
+probabilistic constraints imposed by the problem domain? It does this by
+expanding on a naive metric of complexity - the number of configuration 
+parameters. Consider the following set of configuration files, drawing from
+an example presented earlier in this paper.
+
+\begin{figure}[!htb]
+    \centering
+    \begin{minipage}{.25\textwidth}
+    \begin{lstlisting} [label={lst:1.cnf},language=C,caption={1.cnf}]
+[server]
+foo = ON
+[client]
+bar = 1
+    \end{lstlisting}
+    \end{minipage}%
+    \hspace{1cm}
+    \begin{minipage}{0.25\textwidth}
+    \begin{lstlisting} [label={lst:2.cnf},language=C,caption={2.cnf}]
+[server]
+foo = ON
+[client]
+bar = ON
+    \end{lstlisting}
+    \end{minipage}
+    \hspace{1cm}
+    \begin{minipage}{0.25\textwidth}
+    \begin{lstlisting} [label={lst:2.cnf},language=C,caption={3.cnf}]
+[server]
+pot = ON
+[client]
+cat = ON
+    \end{lstlisting}
+    \end{minipage}
+    \caption{A learning set of configuration files}
+    \label{fig:complexityset}
+\end{figure}
+
+From our learner, we determined that the parameters $foo$ and $bar$ are
+highly correlated with each other, by an equality relation. In fact, this
+is the only relation learned for $foo$ and $bar$ within the configuration
+space. $pot$ and $cat$ on the other hand, were determined to be unrelated
+by the learner. If using the naive counting measure of complexity, all 
+three of these configuration files would have the same measure of $2$.
+
+However, we know that $foo$ and $bar$ are not independent settings.
+The fact that they are both set to a truthy value communicates less
+information than the settings for the file with $pot$ and $cat$.
+
+Our defined complexity measure would evaluate to $1$ on the
+configuration file with $foo$ and $bar$, while evaluating to $2$ on
+the configuration file with $pot$ and $cat$, more accurately representing
+the amount of information actually conveyed by these settings. Note,
+however that our metric does not actually consider the {\it values}
+of the configuration settings when determining complexity. In the
+future, it may be possible in the future to have interpreted predicates,
+such that these heuristics may even more closely reflect the informational
+content of a constrained configuration file.
+
+We hope that further researchers will expand on the foundation we lay
+here to extract more useful information from the intermediate
+representation built by the VeriConf learner.
+
+\iffalse
 
@@
 
-\iffalse
-
 Use the listing in figure 2 to put together an example of why the
@@
 
+Additional refinement of a complexity metric could take into account
+when learned rules are violated (indicating potentially brittle
+configuration state)
+
 \fi

### 2017-01-24 CAV17/secs/postanal.tex
notes for rahul

@@
 \section{Post Analysis}
+
+RULE GRAPH
 
@@
 
-Define a directed hypergraph with labeled, weighted edges $H = (V,E)$ such that:
+Define a directed hypergraph with $H = (V,E)$ labeled, weighted edges such that:
 
@@
 over all hyperedges where $v_1 \in V_1$ and $v_2 \in V_2$.
+\markk{define s explicity as a sum, using E notation from complexity}
 We will refer to this hypergraph as the {\bf Rule Graph}
@@
 
+Talk more about hyperedges or some shit
 \iffalse
@@
 It is also worth noting that how good of a heuristic the $DEGREE$ metric is for
-\"importance of a configuration parameter\" is dependent on the coverage
+importance of a configuration parameter is dependent on the coverage
 of the learnable predicate set encompassed by $L$. The more this predicate
@@
 
+Waste less time explaining the example (that should be maybe 1 or 2 paragraphs) and more time explaining the complexity measure.
 \para {Semantics}

### 2017-01-24 CAV17/secs/eval.tex
a few results

@@
 
+\markk{TODO rewrite all this}
 We evaluate this approach using our implementation, \app.
 We use two training sets, a preexisting set of MySQL configuration from~\cite{xu15systems} of 256 files,
- and our own set of collected MySQL configuration from Github of 1120 files.
+ and our own set of collected MySQL configuration from Github of 973 files.
 In our evaluation we focus on MySQL for consistency, but any configuration language (that can be parsed to the intermediate representation from Sec.~\ref{sec:trans}) can be used.
 
-We run \app on 80\% as our collected configuration files, selected at random, as a training set to generate rules.
-The remaining 20\% is used as a testing set to be verified by the learned rules.
+We run \app on 256 files from Tianyin, as a training set to generate rules.
+We scraped github for 973 mysql config files as a test set.
 We report the number of rules learned and number of errors detected in Table~\ref{table:learning}.
@@
 \centering
-\caption{Results of Learning}
+\caption{Results of \app}
 \label{table:learning}
@@
 \hline
-Order        & 2.997     & &  & \\ 
-Missing      & 46.4208   & &  & \\ 
-Type         & 206.7798  & &  & \\ 
-Fine-Grain   & 431.7772  & &  & \\ 
-Coarse-Grain & 856.6383  & &  & \\ 
+Order        & 13  & 389  &  & \\ 
+Missing      & 53  & 237  &  & \\ 
+Type         & 92  & 1367 &  & \\ 
+Fine-Grain   & 327 & 55   &  & \\ 
+Coarse-Grain & 97  & 63   &  & \\ 
 \hline 

### 2017-01-24 code2/graphAnalysis/calc_degree.py
sorting by degree

@@ -45,7 +45,7 @@ for v in vertices:
 
 # prune nodes without context and add their degrees
 # to context-bearing nodes
-
+'''
 to_delete = []
 
 for d1 in degrees:
@@ -58,7 +58,7 @@ for d1 in degrees:
 
 for d in to_delete:
     degrees.pop(d, None)
-
+'''
 # done pruning
 
 sorted_degrees = sorted(degrees.items(), key=operator.itemgetter(1))

### 2017-01-24 code2/src/Benchmarks.hs

@@ -48,7 +48,7 @@ u = unsafePerformIO
 getFileName = fst . head . errLocs
 
 makeError (errLoc1,errLoc2,errIdent) =
-  Error {errMsg=(show errIdent)++" SPEC - "++(show$snd errLoc1)++" AND "++(show$snd errLoc2),errLocs=[errLoc1,errLoc2],..}
+  Error {errMsg=(show errIdent)++" SPEC - "++(show$snd errLoc1)++" AND "++(show$snd errLoc2),errLocs=[errLoc1,errLoc2],errSupport=0,..}
 
 newSet :: [ErrorReport]
 newSet = map (map makeError) [

### 2017-01-24 code2/src/Learners/FineGrained.hs

@@ -84,7 +84,7 @@ instance Learnable R.FineGrained Formula where
      errLocs = map (\x->(fname, x)) [k1, k2, k3]
     ,errIdent = FINEGRAINED
     ,errMsg = "FINE GRAINED ERROR: Expected "++(show k1)++" * "++(show k2)++(show rd)++(show k3)
-    }
+    ,errSupport = gt rd + lt rd + eq rd}
 
 {-
 TODO this doesnt help at all, whyyyy 

### 2017-01-24 code2/src/Learners/IntRel.hs

@@ -58,6 +58,7 @@ instance Learnable R.IntRel Formula where
      errLocs = map (\x->(fname, x)) [k1,k2]
     ,errIdent = INTREL
     ,errMsg = "INTEGER RELATION ERROR: Expected "++(show k1)++(show rd)++(show k2)
+    ,errSupport = gt rd + lt rd + eq rd
     }
 
 combineFlips :: M.Map IntRel Formula -> IntRel -> Formula -> M.Map IntRel Formula

### 2017-01-24 code2/src/Learners/KeywordCoor.hs

@@ -72,7 +72,8 @@ instance Learnable R.KeywordCoor AntiRule where
   toError fname ((KeywordCoor (k1,k2)),rd) = Error{
      errLocs= [(fname,k1),(fname,k2)]
     ,errIdent = MISSING
-    ,errMsg = "MISSING ERROR: Expected "++(show k1)++" WITH "++(show k2) ++ " CONF. = " ++ (show rd)}
+    ,errMsg = "MISSING ERROR: Expected "++(show k1)++" WITH "++(show k2) ++ " CONF. = " ++ (show rd)
+    ,errSupport = tru rd + fls rd}
 
 pairs' :: [IRLine]  -> [(IRLine,IRLine)]
 pairs' [] = []

### 2017-01-24 code2/src/Learners/Ordering.hs

@@ -61,5 +61,6 @@ instance Learnable Ordering AntiRule where
   toError fname ((Ordering (k1,k2)),rd) = Error{
      errLocs = map (fname,) [k1,k2]
     ,errIdent = ORDERING
-    ,errMsg = "ORDERING ERROR: Expected "++(show k1)++" BEFORE "++(show k2)++" w/ confidence "++(show rd)}
+    ,errMsg = "ORDERING ERROR: Expected "++(show k1)++" BEFORE "++(show k2)++" w/ confidence "++(show rd)
+    ,errSupport = tru rd + fls rd}
 

### 2017-01-24 code2/src/Learners/TypeErr.hs

@@ -44,13 +44,12 @@ instance Learnable TypeErr QType where
      M.fromList $ map toTypeErr f'
 
   merge rs = 
-     M.unionsWith add rs
+     M.filter (\rd -> totalC rd > 15) $ M.unionsWith add rs
 
   -- 
   check _ rd1 rd2 = let
-     tot = fromIntegral $ sum [string rd1, int rd1, size rd1, bool rd1, path rd1] 
-     toProb x = if tot > 10
-       then (fromIntegral .x)rd1 / tot 
+     toProb x = if (totalC rd1) > 10
+       then (fromIntegral .x)rd1 / (fromIntegral $totalC rd1)
        else 1
    in
      if --TODO allow 1/0 in place of bool 
@@ -59,15 +58,18 @@ instance Learnable TypeErr QType where
        (bool   rd2 == 1 && (toProb bool + toProb int) > 0.7) ||
        (int    rd2 == 1 && ((toProb int + toProb size > 0.7) || (toProb int + toProb bool > 0.7))) ||
        (size   rd2 == 1 && toProb size> 0.7) ||
-       tot == 0
+       totalC rd1 == 0
      then Nothing
      else Just rd1
 
-  toError fname (TypeErr k,rd) = Error{
+  toError fname (TypeErr k,rd1) = Error{
      errLocs = [(fname,k)]
     ,errIdent = TYPE
-    ,errMsg = "TYPE ERROR: Expected a "++(show rd)++" for "++(show k)}
+    ,errMsg = "TYPE ERROR: Expected a "++(show rd1)++" for "++(show k)
+    ,errSupport = totalC rd1}
     --".Found value " ++(show $ findVal f' $ fst x) ++ " of type " ++ (show $ assignProbs $ findVal f' $ fst x) }
+
+totalC rd1 = sum [string rd1, int rd1, size rd1, bool rd1, path rd1] 
 
 p = QType {
   string =1

### 2017-01-24 code2/src/Main.hs

@@ -1,10 +1,12 @@
 {-# LANGUAGE OverloadedStrings #-}
+{-# LANGUAGE MultiWayIf #-}
 
 module Main where
 
 import           Data.Aeson
 import qualified Data.ByteString.Lazy  as B
 import qualified Data.List             as L
+import qualified Data.Map             as M
 import           Data.Maybe
 import qualified Data.Text             as T
 import qualified Data.Text.IO          as T
@@ -26,8 +28,10 @@ import           Checker
 import qualified Settings
 import Types.Rules
 import Types.IR
+import Types.Common
 import Types.JSON
 import Types.Errors
+
 
 rules = learnRules learnTarget
 
@@ -35,6 +39,10 @@ main = do
   G.setLocaleEncoding utf8
   G.setFileSystemEncoding utf8
   G.setForeignEncoding utf8  
+  
+  degrees <- ((M.fromList. fromJust. decode) <$> B.readFile "graphAnalysis/sorted_degrees.json") :: IO (M.Map Keyword Double)
+  print degrees
+ 
   vFiles <- mapM T.readFile vFilePaths :: IO [T.Text]
   let vTargets = map (\(f,v) -> (f,v,MySQL)) (zip vFilePaths vFiles) :: [ConfigFile Language]
   unless Settings.uSE_CACHE $ B.writeFile "cachedRules.json" $ encode ((toLists $ learnRules learnTarget):: RuleSetLists)
@@ -43,17 +51,17 @@ main = do
   --to check integrity of cache
   --when (rules /= (fromLists. fromJust $ decode c)) (fail  "error in json cache")
 
-  fitness <- runVerify cached vTargets
+  fitness <- runVerify cached degrees vTargets
   return ()
 
 
-runVerify ::  RuleSet -> [ConfigFile Language] -> IO Int
-runVerify rules vTargets  = do
+runVerify ::  RuleSet -> M.Map Keyword Double -> [ConfigFile Language] -> IO Int
+runVerify rules ds vTargets  = do
   let errors =  map (verifyOn rules) vTargets
   fitnesses <- 
     if Settings.bENCHMARKS 
     then zipWithM reportBenchmarkPerformance benchmarks errors 
-    else mapM reportUserPerformance $ L.sortOn (\(f,es) -> length es) (zip (map (\(x,y,z)->x) vTargets) errors) 
[…]

### 2017-01-24 code2/src/Settings.hs

@@ -4,7 +4,7 @@ module Settings where
   vERBOSE = True
 
   --use the prebuilt cache, if false, will overwrite cache using this run
-  uSE_CACHE = True
+  uSE_CACHE = False
 
   --verify benchmarks and report # passing or verify files in 'user' dir
   bENCHMARKS = False

### 2017-01-24 code2/src/Types/Errors.hs

@@ -10,6 +10,7 @@ data Error = Error{
     errLocs  :: [(FilePath, Keyword)]
   , errIdent :: ErrorType
   , errMsg   :: String
+  , errSupport :: Int
 }
 
 instance Show Error where

### 2017-01-24 CAV17/secs/arch.tex
stuff

@@
 \begin{figure*}[tbp] \centering
-\includegraphics[width=0.84\textwidth]{figs/overview}
-\caption{\app's workflow. The green components represent configuration 
-  files, including both training set of configuration files and users' input
-  configuration files to verify.
-  The blue dashed box is \app. 
-  The yellow components are key modules of \app.
-  The purple circle is a checker for checking whether the target
-  configuration file violates any rule.}
+\includegraphics[width=0.99\textwidth]{figs/overview}
+\caption{\app's workflow.
+  The dashed box is the specification learning module. 
+  The yellow components are key modules of \app.}
 \label{fig-overview}
@@
 
-We propose \app, an automatic verification framework for 
-software configuration files.
-As shown in Sec.~\ref{sec-motiv}, \app can detect many sophisticated 
-configuration errors, including ordering errors, missing entry errors,
-type errors and integer correlation errors. 
-Figure~\ref{fig-overview} shows
-a typical \app verification workflow with three steps:
-translation, learning, and rule refinement. This section briefly
-describes how each step works.
+Figure~\ref{fig-overview} gives an overview of the \app framework.
+The biggest part is dedicated to 
+learning and inferring the specification for configuration 
+files. This process is done offline, before the user even starts 
+to use \app. There are three main steps in the process:
+translation, learning, and rule refinement.
 
 \para{Initial phase}
-We start with the assumption 
-that we are given a number of (not necessarily correct) 
-configuration files, called {\em training set}, 
-belonging to the same system, such as MySQL or Apache. 
-These files, therefore, follow similar patterns.
+Since there is no proper formal specification for configuration 
+files, we learn the specification from a large number of 
+(not necessarily correct) configuration files belonging to the same 
+system, such as MySQL or Apache. These files are our training set.
+
 %In the following steps,
@@
 a more structured and typed intermediate representation.
-When we infer the types of entries in a configuration file, 
-the type of an entry cannot always be fully determined from 
-a single value, since it is difficult to understand
-the purposes of key-value entries in modern
-software configuration files~\cite{xu15hey}.
+Most of entries in a configuration file follow a key-value pattern, 
+where some environmental variable (``key'') is assigned  a value.
+Looking at a single entry, by inspecting the value
+we cannot always fully determine the type of the key~\cite{xu15hey}.
 We address this problem 
@@
 we assign several types over a probability distribution.
-We can later use these well-structured files
-as a ``true'' training set to learn the rules.
 
@@
 into well-structured representations. 
-The learner employs a learning algorithm, {\em rule association 
-algorithm}, to generate various rules,
-potentially used to handle different types of configuration errors,
-including ordering errors, missing entry errors,
-type errors and integer correlation errors.
+It employs a learning algorithm, {\em rule association 
+algorithm}, to generate a list of rules, describing properties 
+of configuration files. In a nutshell, the learning algorithm 
+takes a set of rule interfaces and instantiate them with the concrete
+values that appear in the training set. Since there are no guarantees 
+that the files in the training set are correct, our main assumption
+is that even if a file contains an error, majority of the files do not 
+have the same error and our learning process should detect these
+
+generate concrete instances of t
+
+\ruzica{i need to read the rest of the paper first}
+
 These rules are the outputs of the learner, 

### 2017-01-24 CAV17/secs/postanal.tex
clarify some stuff and restructure definitions

@@
 
-as measured by the learner for that relationship. For notational
-convenience, later in this section
-we shall define $w_{V_1, V_2, l}$ as the weight of the
-hyperedge $(V_1, V_2, l, w)$, and $s_{v_1, v_2, l}$ as the sum of weights
-over all hyperedges where $v_1 \in V_1$ and $v_2 \in V_2$.
-\markk{define s explicity as a sum, using E notation from complexity}
+as measured by the learner for that relationship. We will also denote
+$E_{V_1, V_2}$ as
+the set of all hyperedges where a vertex $v_1 \in V_s$ is in the 
+source set and a vertex $v_2 \in V_t$ is in the target. Sometimes we
+will write a single vertex $v$ in our subscript, as notational convenience
+for the singleton set containing $v$.
+
+The size of an edge set is the sum of all weights in that set, so:
+
+    $$|E_{v_1, v_2}| = \sum_{(X, Y, l, w) \in E_{v_1, v_2}} w$$
+
 We will refer to this hypergraph as the {\bf Rule Graph}
@@
 
-Note that due to support / confidence assertions in the learner, we
-may be assured that all weights in the graph are positive.
+We note that support and confidence assertions in the learner ensure
+that all weights are positive.
 
@@
 
-    $$DEGREE(x) = \sum_{l \in L} \sum_{v \in V} s_{x, v, l} + \sum_{l \in L} \sum_{v \in V} s_{v, x, l}$$
+    $$DEGREE(x) = \sum_{v \in V} |E_{x, v}| + \sum_{v \in V} |E_{v, x}|$$
 
@@
 For a configuration file with a set of keywords $K$ for a system
-with a Rule Hypergraph $H = (V, E)$, we first define $E_{source}(V_s, V_t)$ as
-the set of all hyperedges where a vertex $v_1 \in V_s$ is in the source set and
-a vertex $v_2 \in V_t$ is in the target. Finally we define the size
-of an edge set $|E|$ to be the sum over all weights in the edge set.
+with a Rule Hypergraph $H = (V, E)$.
 
@@
         \begin{cases}
-            1 * (1 - \frac{|E(k, K)|}{|E(k, V)|}) & \text{if}\ \ |E(k, V)| > 0 \\
+            1 * (1 - \frac{|E_{k, K}|}{|E_{k, V}|}) & \text{if}\ \ |E_{k, V}| > 0 \\
             1 & \text{otherwise}
@@
 \end{equation}
+
+Since all weights are positive, $|E_{k, V}| > 0$ if there is at least one 
+edge in $E_{k, V}$. Examining $\frac{|E_{k, K}|}{|E_{k, V}|}$, we may think of this
+term as the ratio of {\it possible} constraints on a keyword $k$ by all keywords
+in the configuration space ($V$) to the {\it actual} constraints imposed in the
+examined configuration file ($K$).
 

### 2017-01-24 CAV17/secs/eval.tex
fxing learner

@@
 \hline
-{\bf Class of Error } & {\bf \# Rules Learned} & {\bf \# Rules Detected} & {\bf Support} & {\bf Confidence}\\ 
+{\bf Class of Error } & {\bf \# Rules Learned} & {\bf \# Errors Detected} & {\bf Support} & {\bf Confidence}\\ 
 \hline
@@
 \setlength{\tabcolsep}{1em}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|}
 \hline
-{\bf Class of Error} & {\bf Reference} & {\bf Rank w/o} & {\bf Rank w/} & {\bf Ideal Rank}\\
+{\bf Class of Error} & {\bf Reference} & {\bf Rank w/o} & {\bf Rank w/}\\
 \hline
@@
 The checker stage of \app is the only one facing an end user that wants to verify a new configuration file.
-However, the user may also want to interface with the previous stages as well. 
-We have only build rules for MySQL, a relatively well documented language, but any configuration language can be analyzed with \app given a training set.
-In this case, the user will need to rebuild the rule set.
-A user also may want to update the support of confidence threshold to report more or fewer error, as is needed for their application.
-It is then important that the learning process is reasonably fast.
-The times reported in Table~\ref{table:training} were run on a single thread of a Intel i5-3450 CPU @ 3.10GHz with 16GB of RAM.
-We see the drastic difference in times here because ConfigC assumes a correct training set, and learns every relation derivable.
-With \app, we instead only process rule that meet the required support and confidence, reducing the cost of resolve to a consistent set of rules.
+Once a set of rules has been learned, it is not necessary to rerun the learner.
+However, we have only used \app to build rules for MySQL, but any configuration language can be analyzed with \app given a training set.
+In an industrial setting, the available training set may be much larger than ours as well, so is important that the learning process scales.
+We see in Table~\ref{table:training} that \app scales roughly linearly.
+
+\markk{TODO rewrite}
+We also compare \app to prior work in configuration verification, ConfigC~\cite{santolucitoCAV}.
+ConfigC scales exponentially because the learning algorithm assumes a completely correct training set, and learns every derivable relation.
+With \app, we instead only process rules that meet the required support and confidence, reducing the cost of resolving to a consistent set of rules. 
+The times reported in Table~\ref{table:training} were run on four cores of a Kaby Lake Intel Core i7-7500U CPU @ 2.70GHz on 16GB RAM and Fedora 25.
 
@@
 \centering
-\caption{Training time for different datasets}
+\caption{Time for training over various training set sizes}
 \label{table:training}
@@
 \hline
-{\bf The \# of Files for Training} & {\bf ConfigC (s)} & {\bf \app (s)}\\ 
+{\bf \# of Files for Training} & {\bf ConfigC (sec)} & {\bf \app (sec)}\\ 
 \hline
 \hline
-10   & 2.997     &   \\ \hline
-50   & 46.4208   &   \\ \hline
-100  & 206.7798  &   \\ \hline
-150  & 431.7772  &   \\ \hline
-200  & 856.6383  &   \\ 
+0    & 0.051    & 0.51  \\ \hline
+50   & 1.815    & 1.638  \\ \hline
+100  & 13.331   & 4.119  \\ \hline
+150  & 95.547   & 4.231  \\ \hline
+200  & 192.882  & 12.271  \\ \hline
+256  & 766.904  & 15.627  \\ 
 \hline

### 2017-01-24 CAV17/secs/intro.tex
fxing learner

@@
 \label{sec-intro}
+
+\markk{maybe we can use these lines in the intro somewhere.}
+These errors can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
+Since these runtime errors may only be triggered after some time in a deployment environment, the standard delta-debugging technique~\cite{x} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.
 

### 2017-01-24 CAV17/secs/learner.tex
fix fine grain
fxing learner

@@
 We describe an interface to define the different classes of rules that should be learned.
-Each instance of the interface corresponds to a different class of of configuration errors, such as missing entry errors, ordering errors, and integer correlation errors. 
-These errors can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
+Each instance of the interface corresponds to a different class of configuration errors, as described in Sec.~\ref{sec:motiv}.
 
-\rahul{and we may even be able to say that these insidiuous issues are much
-harder to pin down by the standard delta-debugging technique of starting a
-system multiple times with different configuration settings}
+To learn rules over sets of configuration files, we use a generalization of \textit{association rule learning}~\cite{agrawal1993mining}, a technique that can be summarized as inductive machine learning.
+Association rule learning is a technique to learn how frequently items of a set appear together.
+For example, by examining a list of food store receipts, we would learn that when a customer buys bread and peanut butter, the set of purchased items is also likely to include jelly.
+Since configuration files have complex relations, we extend these association relationships to generalized predicates.
 
-A rule is an implication relationship, $X \implies p(X,Y)$, between two possibly empty sets of keywords $X,Y \subset \keys$, where $\keys$ is the set of unique keys from the training set and the predicate $p$ is the one of the classes of configuration errors (order, missing, etc).
-Implicitly we interpret this to means that if the keywords $X\cup Y$ appear in a configuration file, we expect the predicate $p$ to hold.
+A \textit{rule}, $r$, is then an implication relationship, $r = X \implies p(X,Y)$, between two possibly empty sets of keywords $X,Y \subset \keys$, where $\keys$ is the set of unique keys from the training set (denoted \trainingSet) and the predicate $p$ is one of the classes of configuration errors.
+Implicitly we interpret a rule to mean that if the keywords $X\cup Y$ appear in a configuration file, the predicate $p$ should hold.
 The task of the learning algorithm is to transform a training set to a set of rules, weighted with \textit{support} and \textit{confidence}.
-These two key metrics are taken from \textit{association rule learning}~\cite{agrawal1993mining}, a technique that can be summarized as inductive machine learning.
-In the configuration verification domain, standard association rule learning is best suited to learn integer correlation and missing keyword rules.
-In fact, a more specialized technique for learning ordering rules would be sequence mining~\cite{}, and again another approach may be a better fit for rules over a single keyword, as is needed for probabilistic types.
-Since the full algorithm details are out-of-scope of this paper, here we only describe in detail the metrics which are most relevant to verification.
+The set of rules learned from training set \trainingSet constitutes a specification, $Spec(\trainingSet)$, for a configuration file to be considered correct.
 
 %TODO math def of support and confidence
-Each power set of keywords, $\{X,Y\}$, is assigned a support and confidence measure during the learning process.
-Support is the number of times the set of keywords in the proposed rule have been seen the in the training set.
+The two metrics support and confidence are used in association rule learning, as well as other rule based machine learning techniques~\cite{han2007frequent,langley1995applications}.
+We use slightly modified definitions of support and confidence to handle arbitrary predicates as rules.
+Each rule is assigned a support and confidence to measure the truth of the rule during the learning process.
+%
+\begin{equation}
+ support(p,X,Y) = \frac{|\{C \in \trainingSet \mid X \cup Y \subseteq C\}|} {|\trainingSet|}
+\end{equation}
+\begin{equation}
+ confidence(p,X,Y) = \frac{|\{C \in \trainingSet \mid p(X,Y) \subseteq C\}| } {support(X,Y)*|\trainingSet|}
+\end{equation}
+
+Support is the frequency that the that set of keywords in the proposed rule, $X \cup Y$, have been seen in the configuration files $C$ in the training set \trainingSet.
+Notice support does not consider the predicate itself, only how many times the predicate had the chance to be evaluated.
 Confidence is the number of times the rule predicate has held true over the given keywords.
-In the learning process, these are given threshold, below which a rule will be reject for lack of evidence.
+In the learning process, each class of rule is manually assigned a support and confidence threshold, below which a rule will be rejected for lack of evidence.
+The set of learned rules is then:
 
-\para{Order}
+\begin{equation}
+  Spec(\trainingSet) = \forall X,Y \subset \keys. {r | support(p,X,Y) > t_s \land confidence(p,X,Y) > t_c}
+\end{equation}
+
+\subsection{Error Classes}
 Ordering errors take the form $X \implies order(X,Y)$, where $|X|,|Y|=1$ and the keyword $X$ must come before the keyword $Y$ in any configuration file.
-
-\para{Missing}
-$X \implies missing(X,Y)$, where $|X|,|Y|=1$ and the keyword $X$ must appear in the same file as the keyword $Y$ in any configuration file.
+Missing keyword entries take the form $X \implies missing(X,Y)$, where $|X|,|Y|=1$ and the keyword $X$ must appear in the same file as the keyword $Y$ in any configuration file.
 
@@
 
-We have developed \app to be easily extendable and customizable. Each of the rules are implemented as an instance of the \textit{Learnable} typeclass:
+We have developed \app to be easily extendable and customizable. Each of the rules are implemented as an instance of the \textit{Learnable} interface (a typeclass in Haskell):
 
@@
 
-With the learned rules generates by the learner module,
-  \app checks whether any entry in a target configuration file violates the learned rules and constraints.
-\app parses a verification target configuration file the same way employed in the translator for learning,
-  obtaining a structured and typed representation.
+With the rules generated by the learner module, \app checks whether any entry in a target configuration file violates the learned rules and constraints.
+\app parses a verification target configuration file the same way employed in the translator for learning to obtain a set of key-value pairs $C$.
 Then, the checker applies the learner to build the set of relations observed in the file.

### 2017-01-24 CAV17/secs/eval.tex
fix table 1, wrong order

@@
 \hline
-{\bf Class of Error } & {\bf \# Rules Learned} & {\bf \# Errors Detected} & {\bf Support} & {\bf Confidence}\\ 
+{\bf Class of Error } & {\bf \# Rules Learned} & {\bf \# Errors Detected} & {\bf Support (\%)} & {\bf Confidence (\%)}\\ 
 \hline
 \hline
-Order        & 13  & 389  &  & \\ 
-Missing      & 53  & 237  &  & \\ 
-Type         & 92  & 1367 &  & \\ 
-Fine-Grain   & 327 & 55   &  & \\ 
-Coarse-Grain & 97  & 63   &  & \\ 
+Order        & 13  & 62   & 6 & 94 \\ 
+Missing      & 53  & 55   & 2  & 71 \\ 
+Type         & 92  & 389  & -  & -  \\ 
+Fine-Grain   & 327 & 1367 & 24 & 91 \\ 
+Coarse-Grain & 97  & 237  & 10 & 96\\ 
 \hline 
@@
 \hline
-0    & 0.051    & 0.51  \\ \hline
+0    & 0.051    & 0.051  \\ \hline
 50   & 1.815    & 1.638  \\ \hline

### 2017-01-24 CAV17/secs/table2.tex
cav17: translator section

@@
 \begin{footnotesize}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|}
 \hline
-{\bf Error Type} & {\bf Problem Description} & 
-{\bf \app Report}  & {\bf Rank w/o} & {\bf Rank w/}\\ 
+{\bf Errors} & {\bf URLs} & {\bf Rank w/o} & {\bf Rank w/}\\ 
 \hline
 \hline
-Order & Cannot allocate memory for the buffer pool~\cite{innod-ordering}  
-& \ennan{example 4}
-& ~ & ~ \\ \hline
+\multirow{3}{*}{MISSING ERROR: Expected "key-buffer"} & url & 7 & 8 \\
+\multirow{3} & url & 9 & 10 \\ 
+& url & 11 & 12 \\ 
+\hline
 
-Missing & MySQL missing key\_buffer in my.cnf~\cite{missing}
-& \ennan{missing key\_buffer}
-& ~ & ~ \\ \hline
+\multirow{3}{*}{Ordering} & url & 7 & 8 \\ & url & 9 & 10 \\
+& url & 11 & 12 \\  
+\hline
 
-Type & MySQL cannot start~\cite{querylog}
-& \ennan{example 3}
-& ~
-& ~ \\ \hline
+\multirow{3}{*}{Type error} & url & 7 & 8 \\ & url & 9 & 10 \\  
+& url & 11 & 12 \\
+\hline
 
-Fine-Grain & MySQL load is very high~\cite{correlation}   
-& \ennan{results in example 2) }
-& ~ 
-& ~ \\ \hline
+\multirow{3}{*}{fine-grained} & url & 7 & 8 \\ & url & 9 & 10 \\  
+& url & 11 & 12 \\
+\hline
 
-Coarse-Grain & MySQL server has gone away error~\cite{coarse-grain}
-& \ennan{results}
-& ~ 
-& ~ \\ \hline
+\multirow{3}{*}{int correlation} & url & 7 & 8 \\ & url & 9 & 10 \\  
+& url & 11 & 12 \\
+\hline
 

### 2017-01-24 CAV17/secs/trans.tex
cav17: translator section

@@
 
+{
+\setlength{\belowcaptionskip}{-15pt}
 \begin{figure}[!htb]
@@
 \end{figure}
+}
 
-\subsection{Probabilistic Types}
-\label{sec:ptypes}
+\para{Probabilistic types}
+%\label{sec:ptypes}
 An additional challenge is that it is not always possible to fully determine the type of key based on a single example value. 
@@
 In \app, the set of basic types contains strings, file paths, integers, sizes, and booleans. 
-Taking the configuration \ref{lst:1.cnf}, we can assume {\tt foo} is a boolean type by the grammar of MySQL,
+Taking the configuration \ref{lst:1.cnf} \ennan{configuration 1.4 is too
+far away from this place}, we can assume {\tt foo} is a boolean type by the grammar of MySQL,
   but the keyword {\tt bar} could either be a integer type or a boolean type.
@@
 
+{
+\setlength{\abovecaptionskip}{-.05pt}
+\setlength{\belowcaptionskip}{-15pt}
 \begin{figure}

### 2017-01-24 CAV17/secs/abs.tex
cav17: title and abs

--- 2017-01-19 CAV17/secs/abs.tex
@@
 
-We verify configuration files.
-While previous attempts to learn a model for these highly unstructured files have focused on machine learning, we instead take a probabilistic logic approach.
-Probabilistic logic allows us to provide justification for our learning results, giving proof of the verification task.
-Because the resulting model has a clear logical structure, as opposed traditional machine learning techniques such as neural nets, we can do further analysis on the model that improves our results.
+System failures resulting from configuration errors 
+are major reasons for compromised reliability of today's software
+systems. Although a lot of program verification techniques 
+have been proposed, verifying configuration files is still 
+an open problem,
+because 1) software configurations are typically written in
+poorly structured and untyped ``languages'', and 
+2) specifying rules for configuration 
+verification is challenging in practice.
+
+This paper presents \app, the first automatic verification framework for
+general software configurations.
+\app verifies a target configuration file $F$ through three steps.
+First, \app parses a training set of configuration 
+files (not necessarily correct) belonging to the same system as $F$,
+translating these files to a
+well-structured and probabilistically-typed 
+intermediate representation.
+Second, \app derives configuration rules by learning
+these intermediate representations.
+Finally, \app employs rule graph analysis to refine the 
+resulting rules, and uses the refined rules to verify $F$.
+
+\app is capable of detecting various configuration errors,
+including ordering errors, integer correlation errors, type errors,
+and missing entry errors. We evaluated \app by verifying 
+public configuration files on github, and detected the above 
+configuration errors in these widely-deployed files.
 

### 2017-01-24 CAV17/secs/learner.tex
restructuing learner

@@
 
-A \textit{rule}, $r$, is then an implication relationship, $r = X \implies p(X,Y)$, between two possibly empty sets of keywords $X,Y \subset \keys$, where $\keys$ is the set of unique keys from the training set (denoted \trainingSet) and the predicate $p$ is one of the classes of configuration errors.
+A \textit{rule} $r$, is then an implication relationship, $r = X \implies p(X,Y)$, between two possibly empty sets of keywords $X,Y \subset \keys$, where $\keys$ is the set of unique keys from the training set (denoted \trainingSet) and the predicate $p$ is one of the classes of configuration errors.
 Implicitly we interpret a rule to mean that if the keywords $X\cup Y$ appear in a configuration file, the predicate $p$ should hold.
@@
 
-%TODO math def of support and confidence
-The two metrics support and confidence are used in association rule learning, as well as other rule based machine learning techniques~\cite{han2007frequent,langley1995applications}.
-We use slightly modified definitions of support and confidence to handle arbitrary predicates as rules.
-Each rule is assigned a support and confidence to measure the truth of the rule during the learning process.
+The two metrics, support and confidence, are used in association rule learning, as well as other rule based machine learning techniques~\cite{han2007frequent,langley1995applications}.
+We use slightly modified definitions of of these to handle arbitrary predicates as rules.
+During the learning process, each rule is assigned a support and confidence to measure the amount and quality of evidence for the rule.
 %
@@
 Support is the frequency that the that set of keywords in the proposed rule, $X \cup Y$, have been seen in the configuration files $C$ in the training set \trainingSet.
-Notice support does not consider the predicate itself, only how many times the predicate had the chance to be evaluated.
+%Notice support does not consider the predicate itself, only how many times the predicate had the chance to be evaluated.
 Confidence is the number of times the rule predicate has held true over the given keywords.
-In the learning process, each class of rule is manually assigned a support and confidence threshold, below which a rule will be rejected for lack of evidence.
-The set of learned rules is then:
+In the learning process, each class of rule is manually assigned a support and confidence threshold, $t_s$ and $t_c$ respectively, below which a rule will be rejected for lack of evidence.
+The set rules that are learned and included as part of the final specification are as follows:
 
-\begin{equation}
-  Spec(\trainingSet) = \forall X,Y \subset \keys. {r | support(p,X,Y) > t_s \land confidence(p,X,Y) > t_c}
-\end{equation}
+\begin{align*}
+Spec(\trainingSet) = \{r | \ &support(p,X,Y) > t_s\ \land \\
+    & confidence(p,X,Y) > t_c\ \land \\
+    & X,\ Y \subset \keys\}
+\end{align*}
 
 \subsection{Error Classes}
-Ordering errors take the form $X \implies order(X,Y)$, where $|X|,|Y|=1$ and the keyword $X$ must come before the keyword $Y$ in any configuration file.
-Missing keyword entries take the form $X \implies missing(X,Y)$, where $|X|,|Y|=1$ and the keyword $X$ must appear in the same file as the keyword $Y$ in any configuration file.
+Each class of error forms a rule with a predicate $p$, and additional restrictions on the sets $X, Y$.
+Ordering errors have $|X|, |Y| = 1$ and use the predicate $order$ to mean the keyword $X$ must come before the keyword $Y$ in any configuration file.
+Missing keyword entry errors also require $|X|, |Y| = 1$ and use the predicate $missing$ to mean the keyword $X$ must appear in the same file as the keyword $Y$ in any configuration file.
+The type rule is a set of rules over multiple predicates, which take the form $X \implies isType\ast(X)$, where $|X|=1, |Y|=0$ and $\ast$ matches all the basic types (string, int, etc).
 
-\para{Type}
-The type rule is a set of rules over multiple predicates, which take the form $X \implies isType\ast(X)$, where $|X|=1, |Y|=0$ and $\ast$ matches all the basic types (string, int, etc).
-In \app, probabilistic typing is implemented as an instance of the learning interface.
-This module will specify the counting and resolution type judgments from Sec.~\ref{sec:ptypes}.
-It
-
-\para{Integer Correlation}
-\app supports two types of integer correlation rules, coarse-grained and fine-grained.
-Coarse-grained rules follow $X \implies compare(X,Y)$, where $|X|,|Y|=1$ and $compare \in \{<,=,>\}$, such that $X$ must hold $compare$ to $Y$.
-Fine-grained rules follow $X \implies compare(X,Y)$, where $|X|=2,|Y|=1$ and $compare \in \{<,=,>\}$, such that for $k_1,\ k_2 \in X,\ k1*k2$ must hold $compare$ to $Y$.
-These rules also implement a typing judgment over the keywords probabilistic type.
+\app also supports two types of integer correlation rules, coarse-grained and fine-grained.
+Both integer correlation rules are set of rules over the predicates $\{<,=,>\}$.
+Coarse grain rules require $|X|, |Y| = 1$, and the predicates have the typical interpretation.
+Fine-grained rules use $|X|=2,|Y|=1$, and interpret the predicates such that for $k_1,\ k_2 \in X,\ k1*k2$ must have the predicate relation to $Y$.
+The integer correlation rules also use probabilistic types to prune the search space.
 To avoid learning too many false positives, we restrict this rule to either $size*int=size$, $int*size=size$, or $int*int = int$.
-Without probabilistic typing, we would also learn, for example, $int*int=size$.
+Without probabilistic typing, we would also learn, for example, $size*size=size$, which is an invalid interpretation.
 %TODO include exactly how many false positive we prune with types over our training set? Here or in eval?
-
-\app is primarily implemented in Haskell.
-The source code for our implementation is available at {\em (URL omitted for blind review)}.
-
-We have developed \app to be easily extendable and customizable. Each of the rules are implemented as an instance of the \textit{Learnable} interface (a typeclass in Haskell):
-
-\begin{lstlisting}[language=Haskell, xleftmargin=.01\textwidth]
-class (Eq a, Show a, Ord a, Countable b) => Learnable a b where
-  buildRelations :: IRConfigFile -> RuleDataMap a b
-  merge :: Countable b => [RuleDataMap a b] -> RuleDataMap a b
-  check :: a -> b -> b -> Maybe b
-  toError :: FilePath -> (a, b) -> Error
-\end{lstlisting}
-
-Each of the rules that check for a particular type of error are implemented in three functions, \textit{buildRelations} for constructing a map of possible observations to a count of how often they are observed, a \textit{merge} function for taking multiple sets of built relations from different files and combining them into one set of relations (weighted accordingly), and finally, a \textit{check} that takes an individual relation mapping from our built set of relations, the observation in the file we are verifying, and whether there is a violation of that particular observation of the relation.
-(There is a fourth \textit{toError} function that serves as a helper function to pretty-print the output of \app.) Hence, if we can define how to build the relations to verify against a new type of error, a system for combining these relations with weights across multiple files that are seen, along with a mechanism for checking whether each individual relation was violated or not, we can extend \app to check for new types of errors.
-Furthermore, the approach of defining a method to build relations from a single file as well as a method to combine these relations facilitates the parallelization of our implementation, since each of the \textit{buildRelations} calls can work parlellely on each file before the results are combined with the \textit{merge} step.
-
-Each of the outputs of the \textit{buildRelations} is in the form \textit{RuleDataMap a b}, where \textit{a} is a group of entities between which we want to define a relation (for example, a pair of keywords for Missing, Order, and Integer Correlation) and \textit{Countable b} is a tally of likelihoods of each possible outcome of the relation that can be weighted and combined over multiple files (for example, a count of files that exhibit the relation versus not for Missing or a count of files that exhibit less than, equals, or greater than between a pair of keywords for Ordering or a set of probabilities for Type rules).
-
-Once the program has finished merging together a set of built relations over every example file in the learning set, we have implemented a \textit{check} function for each of the rules, where we input the group of entities under which a relation is defined, the expected observation on that relation, and the actually observed observation in the file we are checking.
-If the observed instance is inconsistent with the relations built from our training set files, then we would see it reported.
-In the probablistic setting of our tool, we would implement cutoffs to tune our \textit{check} to ignore observed relations under a certain significance level.
 
@@
 \subsection{Implementation}
+
+\app is primarily implemented in Haskell.
+The source code for our implementation is available at {\em (URL omitted for blind review)}.
+We have developed \app to be easily extendable and customizable. Each of the classes of rules are implemented as an instance of the \textit{Learnable} interface (a typeclass in Haskell):
+
+\begin{lstlisting}[language=Haskell, xleftmargin=.01\textwidth]
+class (Eq a, Show a, Ord a, Countable b) => Learnable a b where
+  buildRelations :: IRConfigFile -> RuleDataMap a b
+  merge :: Countable b => [RuleDataMap a b] -> RuleDataMap a b
+  check :: a -> b -> b -> Maybe b
+  toError :: FilePath -> (a, b) -> Error
+\end{lstlisting}
+
+Each of the rules that check for a particular type of error are implemented in three functions;
+   \textit{buildRelations} for constructing a map of possible observations to a count of how often they are observed, 
+   \textit{merge} function for taking multiple sets of built relations from different files and combining them into one set of relations (weighted accordingly), 
+   and finally, a \textit{check} that takes an individual relation mapping from our built set of relations, the observation in the file we are verifying, and whether there is a violation of that particular observation of the relation.
+(There is a fourth \textit{toError} function that serves as a helper function to pretty-print the output of \app.) 
+Hence, if we can define how to build the relations to verify against a new type of error, a system for combining these relations with weights across multiple files that are seen, along with a mechanism for checking whether each individual relation was violated or not, we can extend \app to check for new types of errors.
+Furthermore, the approach of defining a method to build relations from a single file as well as a method to combine these relations facilitates the parallelization of our implementation, since each of the \textit{buildRelations} calls can work parlellely on each file before the results are combined with the \textit{merge} step.
+
+Each of the outputs of the \textit{buildRelations} is in the form \textit{RuleDataMap a b}, where \textit{a} is a group of entities between which we want to define a relation (for example, a pair of keywords for Missing, Order, and Integer Correlation) and \textit{Countable b} is a tally of likelihoods of each possible outcome of the relation that can be weighted and combined over multiple files (for example, a count of files that exhibit the relation versus not for Missing or a count of files that exhibit less than, equals, or greater than between a pair of keywords for Ordering or a set of probabilities for Type rules).
+
+Once the program has finished merging together a set of built relations over every example file in the learning set, we have implemented a \textit{check} function for each of the rules, where we input the group of entities under which a relation is defined, the expected observation on that relation, and the actually observed observation in the file we are checking.
+If the observed instance is inconsistent with the relations built from our training set files, then we would see it reported.
+In the probablistic setting of our tool, we would implement cutoffs to tune our \textit{check} to ignore observed relations under a certain significance level.

### 2017-01-24 CAV17/secs/motiv.tex
fxing learner
cav17: motiv

--- 2017-01-24 CAV17/secs/motiv.tex
@@
 \section{Motivating Examples}
-\label{sec-motiv}
+\label{sec:motiv}
 
@@
     in the same file: "extension=curl.so"
-    w/ confidence ...
 \end{lstlisting}
@@
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-  FINE GRAINED ERROR:
-  Expected "max_connections" * "sort_buffer_size"
-               > "key_buffer_size"
+FINE GRAINED ERROR: Expected 
+  "max_connections" * "sort_buffer_size" >= "key_buffer_size"
 \end{lstlisting}
@@
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-TYPE ERROR: Expected a PType {string = 2, path = 0, int = 37, bool = 7, size = 0} 
-  for "slow-query-log"
+TYPE ERROR: Expected an integer type for "slow-query-log"
 \end{lstlisting}
@@
   "innodb_data_file_path[mysqld]" 
-  w/ confidence {tru = 17, fls = 1}
 \end{lstlisting}

### 2017-01-24 CAV17/secs/abs.tex
cav17: motivating example section done

@@
 systems. Although a lot of program verification techniques 
-have been proposed, verifying configuration files is still 
+have been proposed, verifying configuration files is, nevertheless, 
 an open problem,

### 2017-01-24 CAV17/secs/motiv.tex
cav17: motivating example section done

@@
 
-The above example is a complex integer correlation, which implicitly
+This example is a tricky configuration error, which implicitly
 includes a computational correlation among different entries
 in the configuration file.
-We call these {\em fine-grained integer correlations}. 
-Our tool can detect simple integer correlation---one entry's
+We call these errors as {\em fine-grained integer correlations}. 
+\app can also detect simple integer correlation: one entry's
 value should have a certain correlation with another entry's 
-value---as well.
-For example, in MySQL, the value of \code{key\_buffer} 
+value.
+For instance, in MySQL, the value of \code{key\_buffer} 
 should be larger than \code{max\_allowed\_packet}.
-Few existing tools~\cite{yin11anempirical, zhang14encore}
+While several existing tools~\cite{yin11anempirical, zhang14encore}
 can detect simple integer correlation errors,
-but to the best of our knowledge, \app is the first capable of
+\app is, to the best of our knowledge, the first effort capable of
 detecting fine-grained integer correlation errors.

### 2017-01-24 CAV17/secs/postanal.tex

@@
 \section{Post Analysis}
+
+\iffalse
+
+# Structure and Core Points]
+#
+# @author rahuldhodapkar
+#
+#   Below is a structured summary from which I tried to write my section.
+#   I have tried to include points of emphasis and a general argumentative
+#   flow from which to work.
+#
+#   This should be used as a rubric to determine if we have hit all of
+#   the critical beats of this section, or if there are core points
+#   still missing.
+#
+
+[Problem Definition]
+
+    - What is the intermediate representation?
+        -> why can / should we interpret it as a graph?
+        -> what benefits does this give over neural-networks?
+
+    - What is the problem faced by the verification field?
+        -> how can we be more intelligent about detecting false-positives?
+        -> introduce the degree metric concept.
+
+    - What are some problems outside the verification field that this can
+      help answer?
+        -> Introduce the idea of algorithmic complexity.
+        -> We introduce a heuristic to measure the complexity of configuration
+           files, drawn from information in the rule graph.
+
+[The degree metric]
+
+    - Definition of the degree metric.
+        -> Sub-definition of edge slice sets.
+        -> Sub-definition of edge set size => |*| operator
+
+    - How will the degree metric be used to prune false-positive rules?
+        -> specific definition of the weighting procedure.
+
+[A heuristic for complexity of configuration files]
+
+    - Definition of the complexity heuristic.
+
+    - Example of the complexity heuristic on a graph (? space permitting)
+
+    - Additional interpretations of the Rule Graph
+
+\fi
 

### 2017-01-24 CAV17/secs/trans.tex

@@
 The translator takes as input a training set of configuration files and transforms it into a typed and well-structured intermediate representation.
-The translator can be seen a parser used to generate an intermediate representation for learning rules (see $\S$\ref{sec-learn}).
+The translator can be seen a parser used to generate an intermediate representation for the learner module (cf. Sec.~\ref{sec-learn}).
 Translating or parsing is system dependent since each configuration language (MySQL, Apache, PHP) uses a different grammar.
@@
 
-The translator will convert each key-value assignment $k=v$ in the configuration file to a triple, $(k, v, \tau)$, where $\tau$ is the type of $v$. 
+The translator converts each key-value assignment $k=v$ in the configuration file to a triple $(k, v, \tau)$, where $\tau$ is the type of $v$. 
 There are two major challenges in this step.
@@
 To solve this, we rely on the fact that keywords in a configuration file must be unique within their context, and rename all keywords with their context.
-The set of unique keys, $\keys$, for the sample training set in Figure ~\ref{fig:tset} would then be [``{\tt foo[server]}'',``{\tt bar[client]}''] internally to the intermediate representation.
-We will call the set of key-value pairs $C$.
+The set of unique keys, $\keys$, for the sample training set in Figure~\ref{fig:tset} would then be [``{\tt foo[server]}'',``{\tt bar[client]}''].
 
@@
     \begin{minipage}{.25\textwidth}
-	\begin{lstlisting} [label={lst:1.cnf},language=C,caption={1.cnf}]
+	\begin{lstlisting} [label={lst:file1.cnf},language=C,caption={file1.cnf}]
 [server]
@@
     \begin{minipage}{0.25\textwidth}
-	\begin{lstlisting} [label={lst:2.cnf},language=C,caption={2.cnf}]
+	\begin{lstlisting} [label={lst:file2.cnf},language=C,caption={file2.cnf}]
 [server]
@@
     \begin{minipage}{0.25\textwidth}
-	\begin{lstlisting} [label={lst:2.cnf},language=C,caption={3.cnf}]
+	\begin{lstlisting} [label={lst:file3.cnf},language=C,caption={file3.cnf}]
 [server]
@@
     \end{minipage}
-    \caption{A learning set of configuration files}
+    \caption{A sample training set of configuration files}
     \label{fig:tset}
@@
 
-\para{Probabilistic types}
+\para{Probabilistic Types}
 %\label{sec:ptypes}
@@
 For this reason, we introduce \textit{probabilistic types}, as contrasted with \textit{basic types}.
-In \app, the set of basic types contains strings, file paths, integers, sizes, and booleans. 
-Taking the configuration \ref{lst:1.cnf} \ennan{configuration 1.4 is too
-far away from this place}, we can assume {\tt foo} is a boolean type by the grammar of MySQL,
-  but the keyword {\tt bar} could either be a integer type or a boolean type.
-Consider that we would like to learn a rule that the boolean keywords should have the same values ($eq(\texttt{foo},\texttt{bar})$).
-We then have two potential situations; in the first case where {\tt bar}$::int$, we do not learn the above rule, but in the second case where {\tt bar}$::bool$, the rule is valid.
+In \app, the set of basic types contains strings, file paths, integers, sizes, and Booleans. 
+Taking the configuration \ref{lst:file1.cnf}, we can assume {\tt foo} is a Boolean type by the grammar of MySQL,
+  but the keyword {\tt bar} could either be a integer type or a Boolean type.
+Let us assume that there is a rule stating that the Boolean keywords should have the same values ($eq(\texttt{foo},\texttt{bar})$).
+Then there are two potential situations; in the first case where {\tt bar}$::int$, we do not learn the above rule, but in the second case where {\tt bar}$::bool$, the rule is valid.
 To resolve this ambiguity, instead of immediately assigning one type to a value, the translator assigns a distribution of types to a value based on examples from the learning set.
-% an idea closely related to existentially quantified types~\cite{Launchbury93lazyfunctional}.
 
 A probabilistic type is a set of counts over a set $\mathcal{T}$ of basic types.
-Formally, we define a space of probabilistic types $\tilde{\mathcal{T}}$, where $\ptype=\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$ is a set of pairs, such that $\ptype \in \tilde{\mathcal{T}}, \tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$.
+Formally, we define a space of probabilistic types $\tilde{\mathcal{T}}$, where $\ptype \in \tilde{\mathcal{T}}$ has a form $\ptype=\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$.
 Every keyword $k\in\keys$ has a probabilistic type, expressed $k:\ptype$, which, without any evidence, remains {\scriptsize EMPTY}.
 The count for $(\tau_i,c_i) \in \ptype$ is incremented each time a new example value that matches to type $\tau_i$ is encountered for a particular key, using the update notation $\update$.
-We also denote a keyword value pair that exists in some configuration file as $(k,v) \in C$.
+We also denote the set of key-value pairs with $C$ and a keyword value pair that exists in some configuration file as $(k,v) \in C$.
 
@@
 \end{mathpar}
-\caption{Type judgments for boolean equality rules with probabilistic types}
+\caption{Type judgments for Boolean equality rules with probabilistic types}
 \label{fig:ptypes}
@@
 The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
-In this case, we allow a probabilistic type to resolve to a boolean if we have two counts for boolean, and no more than one count for any other basic type ($\ast$).
+In this case, we allow a probabilistic type to resolve to a Boolean if we have two counts for Boolean, and no more than one count for any other basic type ($\ast$).
 We use the notation, $\ptype \models p$, to denote a probabilistic type whose counts hold on the predicate $p$.

### 2017-01-24 CAV17/secs/eval.tex
all sorting data

@@
 Type         & 92  & 389  & -  & -  \\ 
-Fine-Grain   & 327 & 1367 & 24 & 91 \\ 
+Fine-Grain   & 213 & 324  & 24 & 91 \\ 
 Coarse-Grain & 97  & 237  & 10 & 96\\ 
@@
 \end{table}
+
+Without ptypes - finegrained = 327 rules and 1367 detections
 
@@
 
-\begin{table}[h]
-\centering
-\caption{Effect of Post Analysis Rule Ordering for known true positives}
-\label{table:order}
-\setlength{\tabcolsep}{1em}
-\begin{tabular}{|c|c|c|c|}
-\hline
-{\bf Class of Error} & {\bf Reference} & {\bf Rank w/o} & {\bf Rank w/}\\
-\hline
-\hline
-Order        & Ex.~\ref{ex:order}   &  & \\ 
-Missing      & Ex.~\ref{ex:miss}    &  & \\ 
-Type         & Ex.~\ref{ex:type}    &  & \\ 
-Fine-Grain   & Ex.~\ref{ex:fine}    &  & \\ 
-Coarse-Grain & Ex.~\ref{ex:coarse}  &  & \\ 
-\hline
-\end{tabular}
-\end{table}
+\input{secs/table2}
 

### 2017-01-24 CAV17/secs/table2.tex
all sorting data

@@
+\newcommand{\tablewidth}{6cm}
+\definecolor{Gray}{gray}{0.80}
+\newcolumntype{g}{>{\columncolor{Gray}}c}
+
 \begin{table*}[tbp]
@@
 \label{table-casestudy}
+\setlength{\tabcolsep}{0.5em}
 \begin{footnotesize}
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|c|g|g|c|}
 \hline
-{\bf Errors} & {\bf URLs} & {\bf Rank w/o} & {\bf Rank w/}\\ 
+{\bf Errors} & {\bf URLs} & {\bf None} & {\bf PA} & {\bf PT} & {\bf PT$\land$ PA}\\ 
 \hline
 \hline
-\multirow{3}{*}{MISSING ERROR: Expected "key-buffer"} & url & 7 & 8 \\
-\multirow{3} & url & 9 & 10 \\ 
-& url & 11 & 12 \\ 
+\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize ORDERING ERROR: Expected ``innodb\_data\_home\_dir'' BEFORE ``innodb\_data\_file\_path''} }
+& url & 12/12 & 3/12 & 5/5 & 3/5 \\
+& url & 11/11 & 2/11 & 3/3 & 3/3 \\ 
+& url & 9/9   & 3/9  & 4/4 & 3/4 \\ 
 \hline
 
-\multirow{3}{*}{Ordering} & url & 7 & 8 \\ & url & 9 & 10 \\
-& url & 11 & 12 \\  
+\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize MISSING ERROR: Expected ``key\_buffer'' WITH [isamchk]} }
+& url & 6/10 & 2/10 & 2/4 & 2/4 \\ 
+& url & 2/3 & 3/3 & 2/3 & 3/3 \\
+& url & 2/3 & 3/3 & 2/2 & 3/3 \\  
 \hline
 
-\multirow{3}{*}{Type error} & url & 7 & 8 \\ & url & 9 & 10 \\  
-& url & 11 & 12 \\
+\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize TYPE ERROR: Expected an integer for “slow\_query\_log”}}
+& url & 32/34 & 1/34 & 5/7   & 1/7 \\ 
+& url & 9/20  & 2/20 & 10/11 & 2/11 \\  
+& url & 9/19  & 2/19 & 10/11 & 2/11 \\
 \hline
 
-\multirow{3}{*}{fine-grained} & url & 7 & 8 \\ & url & 9 & 10 \\  
-& url & 11 & 12 \\
+\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize FINE GRAINED ERROR: Expected \\ ``max\_connections'' * ``sort\_buffer\_size'' $\geq$ ``key\_buffer\_size''}}
+& url & 30/34 & 18/24 & 6/7 & 3/7 \\ 
+& url & 23/25 & 9/25  & 8/9 & 3/9 \\  
+& url & 20/23 & 14/23 & 6/7 & 5/7 \\
 \hline
 
-\multirow{3}{*}{int correlation} & url & 7 & 8 \\ & url & 9 & 10 \\  
-& url & 11 & 12 \\
+\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize INTEGER CORRELATION ERROR: Expected ``max\_allowed\_packet'' $<$ ``innodb\_buffer\_pool\_size''} }
+& url & 29/32 & 8/32 & 11/14 & 4/14 \\ 
+& url & 22/23 & 2/23 & 9/10  & 2/10 \\  
+& url & 10/12 & 4/12 & 4/4   & 2/4 \\
 \hline

### 2017-01-24 code2/src/Learners/FineGrained.hs

@@ -59,7 +59,7 @@ instance Learnable R.FineGrained Formula where
     -- TODO should use learning result from TypeErr module
     rs' = filter (\(ir1,ir2,ir3)-> ((validAsSize $ value ir1) `B.xor` (validAsSize $ value ir2) && (validAsSize $ value ir3)) ||
                                     all (validAsInt.value) [ir1,ir2,ir3]) tris
-    eqs = map toFineGrained tris
+    eqs = map toFineGrained rs' --tris
    in
     M.fromList $ eqs
 

### 2017-01-24 code2/src/Settings.hs

@@ -4,7 +4,7 @@ module Settings where
   vERBOSE = True
 
   --use the prebuilt cache, if false, will overwrite cache using this run
-  uSE_CACHE = True
+  uSE_CACHE = False
 
   --verify benchmarks and report # passing or verify files in 'user' dir
   bENCHMARKS = False
@@ -17,7 +17,7 @@ module Settings where
   -- an abusive of notation here, we use slightly different interprtation of the words - same idea in the end
   --TODO unify numerical comutations to be consistent with true interpretation of support and confidence
 
-  sortingStyle  = RuleGraphDegree
+  sortingStyle  =  RuleGraphDegree
   data SortStyles = Support | RuleGraphDegree deriving (Eq)
 
   --TODO this should really be read from training set dir

### 2017-01-24 CAV17/secs/trans.tex
stuff

@@
 Formally, we define a space of probabilistic types $\tilde{\mathcal{T}}$, where $\ptype \in \tilde{\mathcal{T}}$ has a form $\ptype=\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$.
-Every keyword $k\in\keys$ has a probabilistic type, expressed $k:\ptype$, which, without any evidence, remains {\scriptsize EMPTY}.
+Every keyword $k\in\keys$ has a probabilistic type, expressed $k:\ptype$.
 The count for $(\tau_i,c_i) \in \ptype$ is incremented each time a new example value that matches to type $\tau_i$ is encountered for a particular key, using the update notation $\update$.
 We also denote the set of key-value pairs with $C$ and a keyword value pair that exists in some configuration file as $(k,v) \in C$.
+
+Fig.~\ref{fig:ptypes} provides a fragment of a calculus for type judgments for deriving Boolean equality rules with probabilistic types.
+We use the notation, $\ptype \models p$, to denote a probabilistic type whose counts hold on the predicate $p$. For a $\ptype$ with $|\tau_i|$ 
+we denote $c_i$, and $*$ is shorthand for all basic types.
+When there is no evidence for a type $\tau$ we call this empty type ({\scriptsize EMPTY}).
+Initially, before we count any type, all types are set to empty.
+In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
+The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
 
@@
 \inferrule* [Right=bool\_resolve]
-{k:\ptype \\ \ptype \models bool \geq 2 \land \ast \leq 1}
+{k:\ptype \\ \ptype \models |bool| \geq M \land |\ast| \leq N}
 {k :: bool}
@@
 \inferrule* [Right=eq\_rule]
-{k1 :: \tau \\ k2 :: \tau \\ \tau \in \mathcal{T}}
-{eq(k1,k2) :: Rule}
+{k_1 :: \tau \\ k_2 :: \tau \\ \tau \in \mathcal{T}}
+{eq(k_1,k_2) :: Rule}
 \end{mathpar}
@@
 
-In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
-The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
-In this case, we allow a probabilistic type to resolve to a Boolean if we have two counts for Boolean, and no more than one count for any other basic type ($\ast$).
-We use the notation, $\ptype \models p$, to denote a probabilistic type whose counts hold on the predicate $p$.
-Taking the type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
-Using the rules from Fig.~\ref{fig:ptypes}, we would derive the probabilistic type \texttt{bar}$:[bool=3,int=1]$, which then resolves to \texttt{bar}$::bool$.
+Taking these type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
+The result is the probabilistic type \texttt{bar}$:[bool=3,int=1]$.
+By setting $M=3, N=1$, we resolve it to \texttt{bar}$::bool$.
 

### 2017-01-24 CAV17/secs/postanal.tex
add restructure of post-analysis section

@@
 % Rahul
-
-\section{Post Analysis}
 
@@
 
-    - What is the intermediate representation?
+    - What is the intermediate representation from the learner?
         -> why can / should we interpret it as a graph?
@@
 
-RULE GRAPH
+\section{Post Analysis}
 
-VeriConf can output the set of learned rules from the training set as described in $\S$\ref{sec-learn}.
-Note that the ability to inspect the learned rule set is a special property of this technique.
-The core task, building a model from unlabeled examples to classify files as either correct or incorrect, is also a classic problem for other machine learning techniques such as neural networks~\cite{nn1,nn2,nn3}.
-When applying machine learning to verification of configuration files, this is not, however, an ideal approach.
-The resulting model from a neural network is not easily amenable to analysis~\cite{nnAnalysis1,nnAnalysis2}.
-The simple structure of rules with weights from an association rule learning-like approach, will instead allows us to do further inference on the resulting model.
+VeriConf can output the set of learned rules from the training set as
+described in $\S$\ref{sec-learn}, recalling that a rule is 
+an implication relationship of the form $r = X \implies p(X,Y)$.
+This data is sufficient for VeriConf to perform its core task of
+configuration file validation, but can be used for more than 
+simple rule checking. By re-interpreting
+rules as being the edges of a {\bf Rule Graph}, we use tools from network
+theory to extract information
+about the configuration space. We inspect properties of the Rule Graph 
+to triage reported errors by those most likely to be valid,
+and even to estimate the complexity of configuration settings.
+
+Accessibility of the Rule Graph is a hallmark of the association rule
+learning technique applied by VeriConf \cite{someOtherGraphStuff}.
+In contrast, the model output from a neural network is not as easily 
+amenable to analysis \cite{nnAnalysis1, nnAnalysis2}, making it harder
+to build on the work of previously developed methods and tools.
+
+The following section provides a precise definition of the Rule Graph
+and the metrics derived for the purposes of ranking reported errors
+and complexity analysis.
 
@@
 
-Define a directed hypergraph with $H = (V,E)$ labeled, weighted edges such that:
+We formally define the {\bf Rule Graph} as a directed hypergraph 
+$H = (V,E)$ with labeled, weighted edges such that:
 
@@
 
-Where $V_s$ and $V_t$ are sets of vertices. Intuitively, we may think of the
-hyper-edge as being directed from $V_s$ to $V_t$. The label $l \in L$ indicates
-the predicate $p$ extracted by the learner, where $L$ is the set of all
-predicates learned. The weight $w$ is defined as:
+Where $V_s$ and $V_t$ are sets of vertices. Intuitively, we may think
+of each ``hyperedge'' as being directed from $V_s$ to $V_t$. 
+The label $l \in L$ indicates the predicate $p$ extracted by the learner,
+where $L$ is the set of all predicates learned. 
+The weight $w$ is defined as:
 
@@
 
-as measured by the learner for that relationship. We will also denote
-$E_{V_1, V_2}$ as
-the set of all hyperedges where a vertex $v_1 \in V_s$ is in the 
-source set and a vertex $v_2 \in V_t$ is in the target. Sometimes we
-will write a single vertex $v$ in our subscript, as notational convenience
-for the singleton set containing $v$.
+as measured by the learner for that relationship.
+
+We will also denote $E_{V_1, V_2} \subset E$ as the ``slice set'' of $E$ over $V_1, V_2$:
+
+    $$E_{V_1, V_2} = \{ \left( V_s, V_t, l, w \right) \in E \ \mid \ \exists v_1 \in V_1, V_s \land \exists v_2 \in V_2, V_t \}$$
+
+Sometimes we will write a single vertex $v$ in our subscript, as
+notational convenience for the singleton set containing $v$.
 
@@
 
-We will refer to this hypergraph as the {\bf Rule Graph}
-in further analysis.
-
 We note that support and confidence assertions in the learner ensure
-that all weights are positive.
+that all weights in the Rule Graph are positive.
 
@@
 
-Talk more about hyperedges or some shit
-\iffalse
-
-Note that we will be summing in-degree and out-degree over all
-relationships $l$ to determine the total importance of
-a keyword $k$ in the configuration space. We are restricted
-by the total set of learning modules from which to derive
-relationships $l$. If a keyword were highly constrained by some
-relationship to other keywords in a way that might not be
-measurable by current techniques, the learner (and
-consequently the rule graph) will show these keywords as being
-unrelated.
-
-\fi
-
-\para {Semantics}
+\para {Discussion}
 
@@
 the higher the $DEGREE$ of the corresponding vertex in the Rule Graph.
-We may use this measurement to examine which keywords in the configuration
-space examined by the learner are most important - which keyword configurations
-are the most constrained / most constraining.
+By classifying keywords in this way, we may extract a simple way to
+order the {\it errors} reported by VeriConf by estimated importance.
 
-Note that since the Rule Graph, as it is formulated in this paper, weights edges
-by a {\it ratio} of predicate hits to total keyword observations, the weight
-of an edge is {\bf dependent only on the confidence of the corresponding rule
-and independent of the support}. We address this issue by pruning nodes of
-inadequate support in the learner, but an alternative formulation of the rule
-graph (in particular an alternative weighting of edges)
-could provide additional
-information for graph analysis techniques to take support into account
-beyond rule confidence.
+We hypothesize that keywords (specifically their corresponding vertices)
+of low $DEGREE$ will be rarer configuration
+parameters where rules learned are more likely to be governed by 
+tehchnical necessity, rather than industry convention. As such, errors
+reported involving low-degree keywords are more likely to be errors
+of high significance and should be presented with high importance
+to users of VeriConf.
 
-\rahul{Not sure how important this last point about alternative Rule Graph
-formulation is - we certainly want to make sure the reader understands that
-this is an area that can be easily expanded on, but don't want to distract
-from the fundamental semantics here.}
+Specifically, for an error reported by VeriConf on a rule $r$ involving
+keywords $K$, we may rank the errors simply by:
 
-It is also worth noting that how good of a heuristic the $DEGREE$ metric is for
-importance of a configuration parameter is dependent on the coverage
-of the learnable predicate set encompassed by $L$. The more this predicate
-set covers the true configuration parameter relationships in the system,
-the better the heuristic.
+    $$RANK(r) = avg( DEGREE(K) )$$
 
-\iffalse
+The results from ranking errors in this way are presented later in
+the paper.
 
-Intuitively, keywords that are seen together more often with defined relationships are more likely to generate rules within the learner.
- (it would be nice to show this with a quick derivation)
-
-for a rule to be considered *true*, two conditions must hold:
-
-1) adequate support -we have seen the keywords together x number of times
-
-2) adequate confidence - how many times out of the x number of times was the relationship true?
-
-\fi
-
-\iffalse
-- Open Questions
-> What is the difference between {\it important} rules and
-  {\it rules we are more sure about}?
-
-> Why doesn't everything just sum to zero?
-
-\fi
 \subsection{Complexity Measure}
 
-A common goal for software projects is managing complexity. As
-constraints accumulate over the lifecycle of a project additional
-configuration file complexity often grows, with the danger of
-making code brittle and unwieldy. For code, Kolomogrov complexity
-can be a good indicator of whether a solution is bloated and 
-needs to be refactored.
-
-The intermediate representation produced VeriConf's learner stage
-may be used to analyze the complexity of a configuration file.
+We may also use the Rule Graph to advance our general knowledge
+of the configuration space, outside the strict confines of a
+verification system. As an example, we briefly present a heuristic
+for configuration file complexity based on the topology of the
+Rule Graph. This measure of complexity could be used by software
+organizations to manage configuration files in much the same way
+as Kolomogrov complexity is used to manage code - identifying
+potentially brittle configurations for targeted refactoring.
 
@@
 
-We define a measurement of complexity based on the calculated correlation.
 For a configuration file with a set of keywords $K$ for a system
-with a Rule Hypergraph $H = (V, E)$.
-
-and may now define our complexity measure:
+and a Rule Graph $H = (V, E)$, we define our complexity measure:
 
@@
 
-Since all weights are positive, $|E_{k, V}| > 0$ if there is at least one 
-edge in $E_{k, V}$. Examining $\frac{|E_{k, K}|}{|E_{k, V}|}$, we may think of this
-term as the ratio of {\it possible} constraints on a keyword $k$ by all keywords
-in the configuration space ($V$) to the {\it actual} constraints imposed in the
-examined configuration file ($K$).
+\para {Discussion}
 
-Waste less time explaining the example (that should be maybe 1 or 2 paragraphs) and more time explaining the complexity measure.
-\para {Semantics}
+The $COMPLEXITY$ measure can be thought of as an
+extension of the na\"ive line-counting measure of complexity.
+When a keyword in the configuration file is present in the Rule Graph,
+we may consider the set $E_{k, K}$ to be all learned rules involving
+keyword $k$ that
+are {\it relevant} to the configuration file being examined. the set
+$E_{k, V}$ denotes {\it all} learned rules involving $k$.
+Given these sets, we may think of $\frac{|E_{k, K}|}{|E_{k, V}|}$
+as representing the amount that $k$ is constrained in the current
+configuration file relative to how much it could be constrained
+in the global configuration space. The more constrained a configuration
+keyword in a particular configuration file, the {\it less} it should
+contribute to the complexity (hence $1 * (1 - \frac{|E_{k, K}|}{|E_{k, V}|})$).
 
-The presented metric is a heuristic that intends to approximate the question: 
-how much redundancy exists in a configuration file, when considering
-probabilistic constraints imposed by the problem domain? It does this by
-expanding on a naive metric of complexity - the number of configuration 
-parameters. Consider the following set of configuration files, drawing from
-an example presented earlier in this paper.
-
-\begin{figure}[!htb]
-    \centering
-    \begin{minipage}{.25\textwidth}
-    \begin{lstlisting} [label={lst:1.cnf},language=C,caption={1.cnf}]
-[server]
-foo = ON
-[client]
-bar = 1
-    \end{lstlisting}
-    \end{minipage}%
-    \hspace{1cm}
-    \begin{minipage}{0.25\textwidth}
-    \begin{lstlisting} [label={lst:2.cnf},language=C,caption={2.cnf}]
-[server]
-foo = ON
-[client]
-bar = ON
-    \end{lstlisting}
-    \end{minipage}
-    \hspace{1cm}
-    \begin{minipage}{0.25\textwidth}
-    \begin{lstlisting} [label={lst:2.cnf},language=C,caption={3.cnf}]
-[server]
-pot = ON
-[client]
-cat = ON
-    \end{lstlisting}
-    \end{minipage}
-    \caption{A learning set of configuration files}
-    \label{fig:complexityset}
-\end{figure}
-
-From our learner, we determined that the parameters $foo$ and $bar$ are
-highly correlated with each other, by an equality relation. In fact, this
-is the only relation learned for $foo$ and $bar$ within the configuration
-space. $pot$ and $cat$ on the other hand, were determined to be unrelated
-by the learner. If using the naive counting measure of complexity, all 
-three of these configuration files would have the same measure of $2$.
-
-However, we know that $foo$ and $bar$ are not independent settings.
-The fact that they are both set to a truthy value communicates less
-information than the settings for the file with $pot$ and $cat$.
-
-Our defined complexity measure would evaluate to $1$ on the
-configuration file with $foo$ and $bar$, while evaluating to $2$ on
-the configuration file with $pot$ and $cat$, more accurately representing
-the amount of information actually conveyed by these settings. Note,
-however that our metric does not actually consider the {\it values}
-of the configuration settings when determining complexity. In the
-future, it may be possible in the future to have interpreted predicates,
-such that these heuristics may even more closely reflect the informational
-content of a constrained configuration file.
-
-We hope that further researchers will expand on the foundation we lay
-here to extract more useful information from the intermediate
-representation built by the VeriConf learner.
-
-\iffalse
-
-it may be possible in the future to have interpreted predicates,
-such that these heuristics may more accurately reflect the informational
-content of a constrained configuration file.
-
-Use the listing in figure 2 to put together an example of why the
-naive implementation of complexity doesn't give as much of an idea
-of what is going on as our heuristic.
-
-Additional refinement of a complexity metric could take into account
-when learned rules are violated (indicating potentially brittle
-configuration state)
-
-\fi
+If a keyword is not constrained at all in the current configuration
+file or is not present in the Rule Graph, we revert to the standard
+counting metric of complexity.

### 2017-01-24 CAV17/secs/learner.tex
add extra timing results

@@
 
-A \textit{rule} $r$, is then an implication relationship, $r = X \implies p(X,Y)$, between two possibly empty sets of keywords $X,Y \subset \keys$, where $\keys$ is the set of unique keys from the training set (denoted \trainingSet) and the predicate $p$ is one of the classes of configuration errors.
+A \textit{rule}, $r$, is then an implication relationship, $r = X \implies p(X,Y)$, between two possibly empty sets of keywords $X,Y \subset \keys$, where $\keys$ is the set of unique keys from the training set (denoted \trainingSet) and the predicate $p$ is one of the classes of configuration errors.
 Implicitly we interpret a rule to mean that if the keywords $X\cup Y$ appear in a configuration file, the predicate $p$ should hold.
 The task of the learning algorithm is to transform a training set to a set of rules, weighted with \textit{support} and \textit{confidence}.
-The set of rules learned from training set \trainingSet constitutes a specification, $Spec(\trainingSet)$, for a configuration file to be considered correct.
+The set of rules learned from training set \trainingSet constitutes a specification for a configuration file to be considered correct.
 
@@
 %
-\begin{equation}
- support(p,X,Y) = \frac{|\{C \in \trainingSet \mid X \cup Y \subseteq C\}|} {|\trainingSet|}
-\end{equation}
-\begin{equation}
- confidence(p,X,Y) = \frac{|\{C \in \trainingSet \mid p(X,Y) \subseteq C\}| } {support(X,Y)*|\trainingSet|}
-\end{equation}
+\begin{equation*}
+ support(r) = \frac{|\{C \in \trainingSet \mid X_r \cup Y_r \subseteq C\}|} {|\trainingSet|}
+\end{equation*}
+\begin{equation*}
+ confidence(r) = \frac{|\{C \in \trainingSet \mid p_r(X_r,Y_r) \subseteq C\}| } {support(r)*|\trainingSet|}
+\end{equation*}
 
@@
 In the learning process, each class of rule is manually assigned a support and confidence threshold, $t_s$ and $t_c$ respectively, below which a rule will be rejected for lack of evidence.
-The set rules that are learned and included as part of the final specification are as follows:
+The denote the set rules that are learned and included as part of the final specification are as follows:
 
-\begin{align*}
-Spec(\trainingSet) = \{r | \ &support(p,X,Y) > t_s\ \land \\
-    & confidence(p,X,Y) > t_c\ \land \\
-    & X,\ Y \subset \keys\}
-\end{align*}
+\begin{align}
+Learn(\trainingSet) = \{r | \ &support(r) > t_s\ \land \nonumber \\
+    & confidence(r) > t_c\ \land \label{eq:learn}\\ 
+    & X,\ Y \subset \keys\} \nonumber
+\end{align}
 
@@
 With the rules generated by the learner module, \app checks whether any entry in a target configuration file violates the learned rules and constraints.
-\app parses a verification target configuration file the same way employed in the translator for learning to obtain a set of key-value pairs $C$.
-Then, the checker applies the learner to build the set of relations observed in the file.
+\app parses a verification target configuration file with the translator from Sec.~\ref{sec:trans}  to obtain a set of key-value pairs, $\mathcal{V}$, for that file.
+Then, the checker applies the learner from Eq.~\ref{eq:learn}, $Learn(\mathcal{V})$ to build the set of relations observed in the file, with the thresholds $t_s,t_c = 100\%$. 
+The checker will then report the following set of errors:
+
+\begin{align*}
+Errors(\mathcal{V}) = \{ r\ |\ & X_r \cup Y_r \in \mathcal{V} \ \land \\
+                               & r \in Learn(\trainingSet) \ \land \\
+                               & r \notin Learn(\mathcal{V})
+\end{align*}
+
 For any relation that violates a known rule, the checker will output the predicate and keyword sets associated with that rule, as well as the learned support and confidence values.
-Since the tool is probabilistic, we provide the user with these values to determine if they rule must be satisfied in their application on a case-by-case basis.
+Since this is a probabilistic approach, in our implementation \app, we provide the user with these values to determine if they rule must be satisfied in their application on a case-by-case basis.
 For instance, the \texttt{key\_buffer} misconfiguration from Sec.

### 2017-01-24 CAV17/secs/table2.tex
add extra timing results

@@
 \multirow{3}{*}{\parbox{\tablewidth} {\scriptsize FINE GRAINED ERROR: Expected \\ ``max\_connections'' * ``sort\_buffer\_size'' $\geq$ ``key\_buffer\_size''}}
-& url & 30/34 & 18/24 & 6/7 & 3/7 \\ 
+& url & 30/34 & 18/34 & 6/7 & 3/7 \\ 
 & url & 23/25 & 9/25  & 8/9 & 3/9 \\  

### 2017-01-24 CAV17/secs/postanal.tex
update notation

@@
 
-VeriConf can output the set of learned rules from the training set as
+\app can output the set of learned rules from the training set as
 described in $\S$\ref{sec-learn}, recalling that a rule is 
 an implication relationship of the form $r = X \implies p(X,Y)$.
-This data is sufficient for VeriConf to perform its core task of
+This data is sufficient for \app to perform its core task of
 configuration file validation, but can be used for more than 
@@
 Accessibility of the Rule Graph is a hallmark of the association rule
-learning technique applied by VeriConf \cite{someOtherGraphStuff}.
+learning technique applied by \app \cite{someOtherGraphStuff}.
 In contrast, the model output from a neural network is not as easily 
@@
 
-We formally define the {\bf Rule Graph} as a directed hypergraph 
-$H = (V,E)$ with labeled, weighted edges such that:
+We define the \textit{Rule Graph} as a directed hypergraph $H = (V,E)$,
+   with vertices $V = \{ keywords \}$ and labeled, weighted edges $E = \{ (V_s, V_t, l, w) \}$.
+The set of edges is constructed from the learned rules, using the keyword sets as source and targets, the predicates as labels, and the confidence as weights:
 
-    $$V = \{ keywords \}$$
+\begin{align*}
+\forall r \in & Learn(\trainingSet).\ \exists e\ \in E.\\
+              & V_s = X_r \land V_t=Y_r \land l=p_r \land w = confidence(r)
+\end{align*}
 
-and
-
-    $$E = \{ (V_s, V_t, l, w) \}$$
-
-Where $V_s$ and $V_t$ are sets of vertices. Intuitively, we may think
-of each ``hyperedge'' as being directed from $V_s$ to $V_t$. 
-The label $l \in L$ indicates the predicate $p$ extracted by the learner,
-where $L$ is the set of all predicates learned. 
-The weight $w$ is defined as:
-
-    $$w = \frac{true}{total}$$
-
-as measured by the learner for that relationship.
-
-We will also denote $E_{V_1, V_2} \subset E$ as the ``slice set'' of $E$ over $V_1, V_2$:
+We will also denote $E_{V_1, V_2} \subset E$ as the \textit{slice set} of $E$ over $V_1, V_2$:
 
@@
 
-We note that support and confidence assertions in the learner ensure
+The use of the support and confidence thresholds $t_s$ and $t_c$ in the learner ensure 
 that all weights in the Rule Graph are positive.
@@
 \para {Definition}
-We define a measure of degree for each node as the sum of in-degree
+We define a measure of degree $\mathcal{D}(v)$ for each vertex $v$ as the sum of in-degree
 and out-degree defined in the usual way. Explicitly, for a vertex $x \in V$:
 
-    $$DEGREE(x) = OUT\_DEGREE(x) + IN\_DEGREE(x)$$
-
-    $$DEGREE(x) = \sum_{v \in V} |E_{x, v}| + \sum_{v \in V} |E_{v, x}|$$
+    $$\mathcal{D}(x) = \sum_{v \in V} |E_{x, v}| + \sum_{v \in V} |E_{v, x}|$$
 
@@
 By classifying keywords in this way, we may extract a simple way to
-order the {\it errors} reported by VeriConf by estimated importance.
+order the {\it errors} reported by \app by estimated importance.
 
@@
 of high significance and should be presented with high importance
-to users of VeriConf.
+to users of \app.
 
-Specifically, for an error reported by VeriConf on a rule $r$ involving
+Specifically, for an error reported by \app on a rule $r$ involving
 keywords $K$, we may rank the errors simply by:
@@
 organizations to manage configuration files in much the same way
-as Kolomogrov complexity is used to manage code - identifying
+as Kolomogrov complexity~\cite{kolomogrov} is used to manage code - identifying
 potentially brittle configurations for targeted refactoring.
@@
 \begin{equation}
-    COMPLEXITY(K, H) = \sum_{k \in K} \
+    \mathcal{C}(K, H) = \sum_{k \in K} \
         \begin{cases}
@@
 
-The $COMPLEXITY$ measure can be thought of as an
+The complexity measure, $\mathcal{C}$, can be thought of as an
 extension of the na\"ive line-counting measure of complexity.

### 2017-01-25 CAV17/secs/eval.tex

@@
 \hline
-{\bf Class of Error } & {\bf \# Rules Learned} & {\bf \# Errors Detected} & {\bf Support (\%)} & {\bf Confidence (\%)}\\ 
+{\bf Class of Error } & {\bf \# Rules Learned} & {\bf \# Errors Detected} & {\bf Support} & {\bf Confidence}\\ 
 \hline
 \hline
-Order        & 13  & 62   & 6 & 94 \\ 
-Missing      & 53  & 55   & 2  & 71 \\ 
+Order        & 13  & 62   & 6 \% & 94 \% \\ 
+Missing      & 53  & 55   & 2 \%  & 71\% \\ 
 Type         & 92  & 389  & -  & -  \\ 
-Fine-Grain   & 213 & 324  & 24 & 91 \\ 
-Coarse-Grain & 97  & 237  & 10 & 96\\ 
+Fine-Grain   & 213 & 324  & 24 \% & 91\%  \\ 
+Coarse-Grain & 97  & 237  & 10 \% & 96\% \\ 
 \hline 
@@
 100  & 13.331   & 4.119  \\ \hline
-150  & 95.547   & 4.231  \\ \hline
+150  & 95.547   & 10.232  \\ \hline
 200  & 192.882  & 12.271  \\ \hline

### 2017-01-25 CAV17/secs/motiv.tex

@@
 
-In this section we present the capability of \app through 
-detecting errors in several real-world misconfiguration examples. 
-These examples were non-trivial configuration errors
+In this section we illustrate capabilities of \app by 
+using several real-world misconfiguration examples. 
+These examples are non-trivial configuration errors
 that were reported on StackOverflow~\cite{stackoverflow},
-a popular question and answer website for programmers and administrators. 
-%To better understand these problems, 
-%we explored and analyzed misconfigurations 
-%on a large number of user forums and on-line discussion sites.
+a popular forum for programmers and administrators.
 
-\para{Example~1: Missing entry error} 
+\para{Example~1: Missing Entry Error} 
 Many critical system outages result from the fact that an important
@@
 dataset~\cite{configdataset}, many misconfiguration issues were 
-reported as missing entry errors.
+reported exactly to be missing entry errors.
 Below is a real-world missing entry error example~\cite{missingentry}:
@@
 she needs to use both \code{pgsql.so} and \code{curl.so}
-in her \code{/ctc/php5/conf.d/curl.ini} file.
-Specifically, this is usually
+in the \code{/ctc/php5/conf.d/curl.ini} configuration file.
+This is usually
 achieved by the following entries in 
@@
 
-Nevertheless, in this example, the user 
+However, in this example the user accidentally
 left out the \code{extension=pgsql.so} entry, 
@@
 causing a segmentation fault. 
-If the user runs \app on such a misconfiguration file,
-\app would return:
+If the user would run \app on her file,
+our tool returns:
 
@@
 comes from a discussion on StackOverflow.
-The user has configured her MySQL as in the following:
+The user has configured her MySQL as follows:
 
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
-  ...
   max_connections               = 64
@@
   sort_buffer_size              = 32M    
-  ...
 \end{lstlisting}
 
-The user complains that her MySQL load was very high, 
+The user then complains that her MySQL load was very high, 
 causing the website's response speed to be very slow.
-The accepted answer to the post reveals that \code{key\_buffer\_size} 
+The accepted answer to the post reveals that the value \code{key\_buffer\_size} 
 is used by all the threads cooperatively, 

### 2017-01-25 CAV17/secs/abs.tex

--- 2017-01-24 CAV17/secs/abs.tex
@@
 systems. Although a lot of program verification techniques 
-have been proposed, verifying configuration files is still 
-an open problem,
+have been proposed, verifying configuration files is, nevertheless, 
+a challenging problem,
 because 1) software configurations are typically written in

### 2017-01-25 CAV17/secs/intro.tex

@@
 \label{sec-intro}
+
+Configuration errors are one of the most important root causes of today's 
+software system failures~\cite{xu15systems, yin11anempirical}.
+In their empirical study, Yin {\em et al.}~\cite{yin11anempirical} report 
+that about 31\% of system failures were caused by misconfiguration problems
+and only 20\% were caused by bugs in program code. 
+Misconfigurations, in practice, may result in various system-wide problems,
+including security vulnerabilities, application crashes, severe disruptions
+in software functionality, 
+and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}.  
+Therefore, how to automatically verify configuration files is an open
+problem~\cite{xu15systems}.
+
+To the best of our knowledge, there have been several prior 
+efforts that attempt to verify 
+configuration files~\cite{santolucitoCAV, xu16early,
+zhang14encore, huang15confvalley}.
+However, state-of-the-art efforts either are impractical to be used
+in reality, or can only deal with simplistic configuration errors.
+In general, these efforts fall into two categories.
+
+\squishlist
+
+\item On the one hand are tools that can detect sophisticated 
+configuration errors, \eg, ConfigC~\cite{santolucitoCAV}. 
+However, these tools heavily rely on datasets containing 100\% 
+correct configuration files to extract configuration rules.
+Existing investigation studies~\cite{wang04automatic, yin11anempirical}
+have demonstrated determining or obtaining 100\% correct configuration
+files to drive rules is almost impossible in reality. 
+Without 100\% correct datasets, these tools would, unfortunately, 
+work poorly.
+
+\item On the other hand, practical efforts, 
+\eg, EnCore~\cite{zhang14encore} and
+ConfValley~\cite{huang15confvalley}, can only 
+detect simplistic configuration errors (\eg, value range errors 
+and simple integer correlation errors), but cannot detect
+sophisticated configuration errors. 
+Consider entry ordering errors, 
+which happen when some entries are inserted in a wrong order
+in the configuration files. 
+For example, in a PHP configuration file, 
+an entry \code{extension=mysql.so} appears 
+before \code{extension=recode.so},  
+it would cause Apache server to crash. The correct ordering 
+should be \code{extension=recode.so} before 
+\code{extension=mysql.so}~\cite{yin11anempirical}.
+Nevertheless, these types of errors cannot be detected by above existing
+efforts.
+
+\squishend
+
+The goal of this work is to propose and build a {\em practical} 
+configuration
+verification tool capable of checking {\em sophisticated} 
+configuration errors (more details
+for sophisticated configuration errors in Sec.~\ref{sec:motiv}).
+Achieving this goal requires us addressing two main obstacles:
+1) the lack of a specification describing properties of configuration
+files, and 2) the structure of configuration files---they are 
+mainly a sequence of entries assigning some values to system
+parameters (called keywords).
+In other words, the ``language'' in which configuration 
+files are written does not adhere to any specific grammar or syntax. 
+Moreover, the entries in configuration files 
+lack type or rules specifying constraints on entries, 
+and there is no explicit structure policy for these entries.
+
+This paper presents \app, the first automatic verification framework
+for general software configurations, by overcoming the above two
+obstacles. In general, \app verifies a given configuration file $F$ 
+through three steps:
+
+\para{Step~1: Translator}
+\app takes as input a large training set of configuration files
+belonging the same system as $F$,
+and we do not have any assumption on the correctness of these files.
+\app analyzes the training set, and generates a well-structured and
+probabilistically-typed intermediate representations.
+
+\para{Step~2: Learning}
+\app derives configuration rules by running {\em rule association
+learning} algorithm to learn the generated intermediate representations.
+The insight of our design is: every file in the training set
+contains several different errors and these errors only appear 
+in a small percentage of files. Based on this insight,
+we are able, with the help of the probabilistic cutoff, to learn a
+set of configuration rules. These rules, in general, specify 
+which properties the entries in configuration files need to satisfy. 
+One can see this learning process as a way of deriving  
+a specification for configuration files.  
+Once a specification is obtained, we can do verification that 
+uses these learned rules to check the correctness of 
+the configuration files
+of interest and detect potential errors.
+
+\para{Step~3: Rule graph analysis}
+To ensure the learned rules are good enough,
+\app employs a further analysis stage to refine the learned rules.
+In general, \app builds a graph to model the learned rules,
+and analyzes this graph's properties, ranking the importance
+and relevance of these rules. Finally, \app outputs
+a set of refined rules as the eventual specification
+to check the target configuration file $F$.
+
+We have implemented a \app prototype, and evaluated it based on
+real-world datasets. In our verification experiments, 
+we first use a public configuration dataset~\cite{configdataset}, which
+contains 261 incorrect MySQL configuration files, as our
+training set. We then use \app to learn rules from this training set
+and refine these rules. Finally, we check sophisticated 
+errors of real configuration files crawled from github,
+and detect many errors in these widely-used configuration files.
+
+In summary, we make the following contributions.
+
+\com{
 
@@
 
-Configuration errors are one of the most important root causes of today's software system failures~\cite{xu15systems, yin11anempirical}.
-In their empirical study, Yin {\em et al.}~\cite{yin11anempirical} report that about 31\% of system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code.
-Misconfigurations, result in various system-wide problems, such as security vulnerabilities, application crashes, severe disruptions in software functionality, and incorrect program executions~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.
-
-While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration errors~\cite{attariyan10automating,su07autobash, whitaker04configuration},
-  those tools mainly post-factum and cannot give the safety guarantees available from powerful static analysis tools in program verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15}.
-Existing techniques for program verification do not fit this application domain, as configuration files often lack specifications and structure.
-There are rarely formal, or any, specifications on the constraints of the key values.
-In the case of MySQL, the canonical specification is a 5240 page reference manual~\cite{mysql-manual15} to describe valid configurations and behavior.
-We aim to automatically learn a formal specification the encodes this information by examining a set of example configuration files.
-
-In previous work~\cite{santolucitoCAV}, we used a set of manually verified files by an domain expert order to learn specifications.
-This approach is expensive and still prone to error by the expert.
-Related work on configuration verification has used machine learning
-
-While the grammar of configuration files tends to be simple (a series of key value pairs with some additional context), the keys and values themselves lack often structure and are untyped plain text.
-
-   1) lack of a specification which would describe properties of configuration files, and 
-   2) a program structure of configuration files -- they are mainly a sequence of entries assigning some value to system variables. 
-The language in which configuration files are written does not adhere to a specific grammar or syntax. 
-In particular, the entries in configuration files are untyped. 
-Moreover, there are surprisingly few rules specifying constraints on entries and there is no explicit structure policy for the entries.
-Thus, automated verification of configuration files would be highly desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
-
-To overcome these obstacles, researchers proposed approaches based on
-statistical analysis and learning%
-~\cite{wang04automatic, zhang14encore, yuan11context}
-that try to infer rules and policies about 
-how configuration files are constructed.
-Rather than explicitly specifying entries' types or rules, 
-these efforts focused on learning policies from a sample dataset.
-The learned rules are usually constructed in the following way: 
-for every entry in a configuration file, 
-they check if it deviates from a ``typical'' value, \ie, 
-a value computed from a large training set 
-consisting of configuration files.
-If the entry is significantly different from a typical value, 
-they suspect that it could be a potential configuration error.
-
-The downside of these is that their learning approaches 
-are limited to simplistic configuration errors, 
-such as type errors and syntax errors, or they 
-heavily rely on template-based inference~\cite{zhang14encore}. 
-%As we mentioned earlier, 
-%because configuration files are not written in a typed language 
-%with a fixed syntax,
-%type errors and syntax errors are relatively rare and easy to detect. 
-Many sophisticated configuration errors, 
-which are difficult to template in practice, 
-cannot be detected in this way. 
-As an illustration of such an error, consider entry ordering errors, 
-which happens when some entries are inserted in a wrong order. 
-For example, if in a PHP configuration file 
-an entry {\tt extension = mysql.so} appears 
-before {\tt extension = recode.so},  
-it would lead to a crash error, where the Apache server cannot start 
-due to the segmentation fault error. The correct ordering 
-should be {\tt extension = recode.so} before 
-{\tt extension = mysql.so}~\cite{yin11anempirical}.
-These types of errors cannot be detected by existing
-learning efforts, 
-since it is hard to build a corresponding template~\cite{xu15systems}. 
-%we would need to capture ordering relations of all the entries. 
-%Some of them can appear in an arbitrary ordering, 
-%and the resulting templates would be too large 
-%and not efficient for a practical use.
+%Therefore, automated verification of configuration 
+%files would be highly
+%desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
 
@@
 \end{enumerate}
+
+}

### 2017-01-25 CAV17/secs/postanal.tex
comment out implementation

@@
 \app can output the set of learned rules from the training set as
-described in $\S$\ref{sec-learn}, recalling that a rule is 
+described in $\S$\ref{sec-learn}. Recall that a rule is 
 an implication relationship of the form $r = X \implies p(X,Y)$.
@@
 configuration file validation, but can be used for more than 
-simple rule checking. By re-interpreting
-rules as being the edges of a {\bf Rule Graph}, we use tools from network
-theory to extract information
-about the configuration space. We inspect properties of the Rule Graph 
-to triage reported errors by those most likely to be valid,
-and even to estimate the complexity of configuration settings.
+simple rule checking. By interpreting the rules as a graph (which
+we call the {\bf Rule Graph}), we can 
+use tools from graph theory to extract information
+about the configuration space. We inspect properties of this 
+Rule Graph to sort reported errors by those most likely to be valid.
+To demonstrate the additional value of the Rule Graph, we
+also use it to estimate the complexity of configuration settings.
 
-Accessibility of the Rule Graph is a hallmark of the association rule
-learning technique applied by \app \cite{someOtherGraphStuff}.
+Accessibility of the Rule Graph is a useful property of the association 
+rule learning technique applied by \app.
 In contrast, the model output from a neural network is not as easily 
@@
 to build on the work of previously developed methods and tools.
-
 The following section provides a precise definition of the Rule Graph
@@
    with vertices $V = \{ keywords \}$ and labeled, weighted edges $E = \{ (V_s, V_t, l, w) \}$.
-The set of edges is constructed from the learned rules, using the keyword sets as source and targets, the predicates as labels, and the confidence as weights:
-
+The set of edges is constructed from the learned rules, using the source and target keyword sets as sources and targets respectively, the predicates as labels, and the confidence as weights:
+%
 \begin{align*}
@@
 
-    $$E_{V_1, V_2} = \{ \left( V_s, V_t, l, w \right) \in E \ \mid \ \exists v_1 \in V_1, V_s \land \exists v_2 \in V_2, V_t \}$$
+\begin{align*}
+    E_{V_1, V_2} = \{ \left( V_s, V_t, l, w \right) \in E \ \mid \ & \exists v_1 \in V_1 \land v_1 \in V_s \\
+    & \land \exists v_2 \in V_2 \land v_2 \in V_t \}
+\end{align*}
 
-Sometimes we will write a single vertex $v$ in our subscript, as
-notational convenience for the singleton set containing $v$.
+We can think of $E_{V_1, V_2}$ as being the subset of edges in $E$ 
+such that each source set $V_s$ shares a vertex with $V_1$
+and each target set $V_t$ shares a vertex with $V_2$.
+We denote a naked vertex $v$ in our subscripts as notational 
+convenience for the singleton set containing that vertex $v$.
 
@@
 
-    $$|E_{v_1, v_2}| = \sum_{(X, Y, l, w) \in E_{v_1, v_2}} w$$
+    $$|E| = \sum_{(X, Y, l, w) \in E} w$$
 
@@
 
-\para {Definition}
-We define a measure of degree $\mathcal{D}(v)$ for each vertex $v$ as the sum of in-degree
-and out-degree defined in the usual way. Explicitly, for a vertex $x \in V$:
+We define a measure of degree $\mathcal{D}(v)$ for each vertex $v$ as the sum of 
+in-degree and out-degree. Explicitly, for a vertex $x \in V$:
 
@@
 
-\para {Discussion}
+We may now use this measure to rank our errors.
+The more rules of high confidence are extracted for a keyword by the learner, 
+the higher the $\mathcal{D}(v)$ of the corresponding vertex in the Rule Graph.
+In our final analysis, we use this classification to
+order the reported {\it errors} by estimated importance.
 
-The more rules of high confidence are extracted for a keyword by the learner, 
-the higher the $DEGREE$ of the corresponding vertex in the Rule Graph.
-By classifying keywords in this way, we may extract a simple way to
-order the {\it errors} reported by \app by estimated importance.
-
-We hypothesize that keywords (specifically their corresponding vertices)
-of low $DEGREE$ will be rarer configuration
+Keywords (specifically their corresponding vertices)
+of low $\mathcal{D}(v)$ may be rarer configuration
 parameters where rules learned are more likely to be governed by 
@@
 Specifically, for an error reported by \app on a rule $r$ involving
-keywords $K$, we may rank the errors simply by:
+keywords $K$, we rank the errors by:
 
-    $$RANK(r) = avg( DEGREE(K) )$$
+    $$RANK(r) = \frac{\sum_{k \in K} \mathcal{D}(k)}{|K|}$$
 
@@
 of the configuration space, outside the strict confines of a
-verification system. As an example, we briefly present a heuristic
+verification system. As an example, we present a heuristic
 for configuration file complexity based on the topology of the
@@
 
-For a configuration file with a set of keywords $K$ for a system
+For a configuration file with a set of keywords $K$
 and a Rule Graph $H = (V, E)$, we define our complexity measure:
@@
 keyword $k$ that
-are {\it relevant} to the configuration file being examined. the set
-$E_{k, V}$ denotes {\it all} learned rules involving $k$.
+are {\it relevant} to the configuration file being examined. 
+The set $E_{k, V}$ denotes {\it all} learned rules involving $k$.
 Given these sets, we may think of $\frac{|E_{k, K}|}{|E_{k, V}|}$
@@
 contribute to the complexity (hence $1 * (1 - \frac{|E_{k, K}|}{|E_{k, V}|})$).
-
 If a keyword is not constrained at all in the current configuration
@@
 counting metric of complexity.
+
+While an in-depth evaluation of the complexity metric presented here
+is out of scope for this paper, we use this measure to
+demonstrate the flexibility of the rule graph, and potential
+for further applications.

### 2017-01-25 CAV17/secs/learner.tex
autocommit

@@
 
-For any relation that violates a known rule, the checker will output the predicate and keyword sets associated with that rule, as well as the learned support and confidence values.
-Since this is a probabilistic approach, in our implementation \app, we provide the user with these values to determine if they rule must be satisfied in their application on a case-by-case basis.
+For any relation from the verification target that violates a known rule, the checker will report the predicate and keyword sets associated with that rule as an error.
+Since this is a probabilistic approach, in our tool \app, we provide the user with the support and confidence values as well to help the user determine if the rule must be satisfied in their particular system.
 For instance, the \texttt{key\_buffer} misconfiguration from Sec.
-\ref{ex:fine} will only be noticeable if the application experiences a heavy traffic load, so the user may choose to ignore this error if they are confident this will not be an issue.
+\ref{ex:fine} will only be noticeable if the system experiences a heavy traffic load, so the user may choose to ignore this error if they are confident this will not be an issue.
 
+\iffalse
 \subsection{Implementation}
@@
 In the probablistic setting of our tool, we would implement cutoffs to tune our \textit{check} to ignore observed relations under a certain significance level.
+\fi

### 2017-01-25 CAV17/secs/postanal.tex

@@
 
-We will also denote $E_{V_1, V_2} \subset E$ as the \textit{slice set} of $E$ over $V_1, V_2$:
+We will also denote $E_{V_1, V_2} \subset E$ as the \textit{slice set} 
+of $E$ over $V_1, V_2$.
+We can think of $E_{V_1, V_2}$ as being the subset of edges in $E$ 
+such that each source set $V_s$ shares a vertex with $V_1$
+and each target set $V_t$ shares a vertex with $V_2$.
+Formally:
 
@@
 
-We can think of $E_{V_1, V_2}$ as being the subset of edges in $E$ 
-such that each source set $V_s$ shares a vertex with $V_1$
-and each target set $V_t$ shares a vertex with $V_2$.
-We denote a naked vertex $v$ in our subscripts as notational 
+We denote a standalone vertex $v$ in our subscripts as notational 
 convenience for the singleton set containing that vertex $v$.

### 2017-01-25 CAV17/secs/eval.tex
fix wriing

@@
 
-\markk{TODO rewrite all this}
 We evaluate this approach using our implementation, \app.
-We use two training sets, a preexisting set of MySQL configuration from~\cite{xu15systems} of 256 files,
- and our own set of collected MySQL configuration from Github of 973 files.
-In our evaluation we focus on MySQL for consistency, but any configuration language (that can be parsed to the intermediate representation from Sec.~\ref{sec:trans}) can be used.
+For our training set, \trainingSet, we use a preexisting set of 256 industrial MySQL configuration files collected in previous configuration analysis work~\cite{xu15systems}.
+For our test set we collected 1000 MySQL configuration from Github, and filtered the poorly formatted files out for a final total of 973 files.
+In our evaluation we focus on MySQL for consistency, but \app can handle any configuration language (that can be parsed to the intermediate representation from Sec.~\ref{sec:trans}).
+We report the number of rules learned from the training set and number of errors detected in the test set in Table~\ref{table:learning}.
 
-We run \app on 256 files from Tianyin, as a training set to generate rules.
-We scraped github for 973 mysql config files as a test set.
-We report the number of rules learned and number of errors detected in Table~\ref{table:learning}.
-Note that in contrast to program verification, we do not have an oracle for determining if a reported error is a true error, or a false positive.
-When learning a specification for a program, that specification can be checked by violating said specification and testing the program.
+Note that in contrast to program verification, we do not have an oracle for determining if a reported error is a true error, or a false positive, where a false positive means an error that has no impact on the system.
+While we can run program to determine the effect a specification has on success of compiling or running the program, no such test exists for configuration files.
 Because misconfigurations are dependent on the rest of the system, the available hardware, and the usage patterns, we cannot simulate the all conditions to determine if a reported error will cause system failure.
-Indeed, as evidenced by Example~\ref{ex:fine}, some misconfigurations will only cause greater than expected performance degradation.
-In this case, the very definition of a true error is necessarily imprecise.
+As evidenced by Example~\ref{ex:fine}, some misconfigurations will only cause greater than expected performance degradation, and only under particular traffic loads.
+In this case, the definition of a true error is necessarily imprecise.
+
+However, we are able to manually determine that some errors are true positives by search forums like StackOverflow for records that particular configuration settings have cause problems on real-world systems.
 

### 2017-01-25 CAV17/secs/postanal.tex
cav17: sec 6

@@
 
-\section{Post Analysis}
+\section{Rule Graph Analysis}
+\label{sec-post}
 
-\app can output the set of learned rules from the training set as
-described in $\S$\ref{sec-learn}. Recall that a rule is 
+\app can output the set of learned rules from the training set (as
+described in Sec.~\ref{sec-learn}). Recall that a rule is 
 an implication relationship of the form $r = X \implies p(X,Y)$.
 This data is sufficient for \app to perform its core task of
-configuration file validation, but can be used for more than 
+configuration file verification, but can be used for more than 
 simple rule checking. By interpreting the rules as a graph (which
@@
 In contrast, the model output from a neural network is not as easily 
-amenable to analysis \cite{nnAnalysis1, nnAnalysis2}, making it harder
+amenable to analysis~\cite{nnAnalysis1, nnAnalysis2}, making it harder
 to build on the work of previously developed methods and tools.
@@
 \forall r \in & Learn(\trainingSet).\ \exists e\ \in E.\\
-              & V_s = X_r \land V_t=Y_r \land l=p_r \land w = confidence(r)
+              & V_s = X_r \land V_t=Y_r \land l=p_r \land w =
+\textit{confidence(r)}
 \end{align*}
@@
 
-    $$RANK(r) = \frac{\sum_{k \in K} \mathcal{D}(k)}{|K|}$$
+    $$\textit{RANK(r)} = \frac{\sum_{k \in K} \mathcal{D}(k)}{|K|}$$
 

### 2017-01-25 CAV17/secs/motiv.tex
stuff

@@
 
-\para{Example~1: Missing Entry Error} 
+\para{Example~1: Missing Entry Errors} 
 Many critical system outages result from the fact that an important
@@
 %TODO would be nice to have these as subsection or somehow be able to ref specific examples
-\para{Example~2: Fine-grained integer correlation error}
+\para{Example~2: Fine-grained Integer Correlation Errors}
 \label{ex:fine}
@@
 between \code{key\_buffer\_size} and other buffer sizes of the system.
-\app is able to learn a specific constraint, \ie
+\app learns a specific constraint, \ie
 \code{key\_buffer\_size} should not be greater than
@@
 
-This example is a tricky configuration error, which implicitly
-includes a computational correlation among different entries
-in the configuration file.
+%This example is a tricky configuration error, which implicitly
+%includes a computational correlation among different entries
+%in the configuration file.
 We call these errors as {\em fine-grained integer correlations}. 
-\app can also detect simple integer correlation: one entry's
+\app can also detect simpler integer correlation: one entry's
 value should have a certain correlation with another entry's 
@@
 should be larger than \code{max\_allowed\_packet}.
-While several existing tools~\cite{yin11anempirical, zhang14encore}
+While several existing tools~\cite{santolucitoCAV, zhang14encore}
 can detect simple integer correlation errors,
-\app is, to the best of our knowledge, the first effort capable of
-detecting fine-grained integer correlation errors.
+\app is, to the best of our knowledge, the first system capable of
+detecting such complex fine-grained integer correlation errors.
 
-\para{Example~3: Type errors} 
+\para{Example~3: Type Errors} 
 Many system availability problems are caused by 
-assigning incorrect type of values to some key in configuration
-files. Consider the following real-world misconfiguration
-file in github~\cite{typeerror}:
+assigning incorrect type of values. Consider the following  misconfiguration
+file from github~\cite{typeerror}:
 a user tries to install MySQL and she needs to initiate the path
@@
 
-Unbeknownst to this user, the entry \code{slow-query-log} should be an 
-integer, not a string. This misconfiguration will lead to 
-MySQL fails to start~\cite{querylog}. In MySQL, there is another entry 
-named ``slow-query-log-file'' used to specify the log path.
-With \app, this user can get the following result:
+This misconfiguration will lead to 
+MySQL fails to start~\cite{querylog}. With \app, this user can get the following result:
 
@@
 \end{lstlisting} 
+This was indeed the error, since in MySQL there is another entry 
+named ``slow-query-log-file'' used to specify the log path.
 
-\para{Example~4: Ordering error} 
+\para{Example~4: Ordering Errors} 
 Ordering errors in software configurations were first reported by 
-Yin {\em et al.}~\cite{yin11anempirical}, but little existing work
-can detect such sophisticated errors. The following example
-illustrates how the ordering error in a MySQL configuration file
-can cause the system to crash~\cite{innod-ordering}. 
+Yin {\em et al.}~\cite{yin11anempirical}, but not many existing tools
+can detect them. The following example
+contains an ordering error in a MySQL configuration file
+that causes the system to crash~\cite{innod-ordering}. 
 %The configuration file might contain, among others, the following lines:
-
 \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
@@
   innodb_lock_wait_timeout       = 50
-  ... 
 \end{lstlisting}
 
-By invoking \app, the user can detect an ordering error in the
-above configuration file.
-In particular, \app reports that \code{innodb\_home\_dir} 
+By invoking \app  the user receives a correct report that \code{innodb\_home\_dir} 
 should appear before \code{innodb\_data\_file\_path}, as shown
 below:
-
  \begin{lstlisting}[language=C, xleftmargin=.01\textwidth]

### 2017-01-25 CAV17/secs/eval.tex
cav17: eval and learner

@@
-\section{Evaluation}
+\section{Implementation and Evaluation}
 
-We evaluate this approach using our implementation, \app.
-For our training set, \trainingSet, we use a preexisting set of 256 industrial MySQL configuration files collected in previous configuration analysis work~\cite{xu15systems}.
-For our test set we collected 1000 MySQL configuration from Github, and filtered the poorly formatted files out for a final total of 973 files.
-In our evaluation we focus on MySQL for consistency, but \app can handle any configuration language (that can be parsed to the intermediate representation from Sec.~\ref{sec:trans}).
+We have implemented a \app prototype, and evaluated it based on
+real-world configuration datasets.
+
+\subsection{Prototype Implementation}
+
+\ennan{put the implementation as one or more paragraphs.}
+
+\subsection{Evaluation}
+
+To evaluate our \app prototype, we need to have two datasets:
+1)a training set and 2) a dataset for testing. 
+For our training set, \trainingSet, we use a preexisting set of 256 
+industrial MySQL configuration files collected in previous configuration 
+analysis work~\cite{configdataset}.
+The majority of configuration files in this training set are incorrect.
+For our evaluation, we collected 1000 MySQL configuration files 
+from Github, and filtered the poorly formatted files out for a final 
+total of 973 files, called as {\em test set}.
+In our evaluation we focus on MySQL for consistency, 
+but \app can handle any configuration language (that can be parsed to 
+the intermediate representation from Sec.~\ref{sec:trans}).
 We report the number of rules learned from the training set and number of errors detected in the test set in Table~\ref{table:learning}.
@@
 
-However, we are able to manually determine that some errors are true positives by search forums like StackOverflow for records that particular configuration settings have cause problems on real-world systems.
+However, we are able to manually determine that some errors are true
+positives by searching forums like StackOverflow for records that
+particular configuration settings have cause problems on real-world
+systems.
 

### 2017-01-25 CAV17/secs/learner.tex
cav17: eval and learner

@@
 \begin{equation*}
- support(r) = \frac{|\{C \in \trainingSet \mid X_r \cup Y_r \subseteq C\}|} {|\trainingSet|}
+ \textit{support(r)} = \frac{|\{C \in \trainingSet \mid X_r \cup Y_r \subseteq C\}|} {|\trainingSet|}
 \end{equation*}
 \begin{equation*}
- confidence(r) = \frac{|\{C \in \trainingSet \mid p_r(X_r,Y_r) \subseteq C\}| } {support(r)*|\trainingSet|}
+ \textit{confidence(r)} = \frac{|\{C \in \trainingSet \mid p_r(X_r,Y_r) \subseteq C\}| } {support(r)*|\trainingSet|}
 \end{equation*}
@@
 Learn(\trainingSet) = \{r | \ &support(r) > t_s\ \land \nonumber \\
-    & confidence(r) > t_c\ \land \label{eq:learn}\\ 
+    & \textit{confidence(r)} > t_c\ \land \label{eq:learn}\\ 
     & X,\ Y \subset \keys\} \nonumber
@@
 Missing keyword entry errors also require $|X|, |Y| = 1$ and use the predicate $missing$ to mean the keyword $X$ must appear in the same file as the keyword $Y$ in any configuration file.
-The type rule is a set of rules over multiple predicates, which take the form $X \implies isType\ast(X)$, where $|X|=1, |Y|=0$ and $\ast$ matches all the basic types (string, int, etc).
+The type rule is a set of rules over multiple predicates, which take the
+form $X \implies \textit{isType}\ast(X)$, where $|X|=1, |Y|=0$ and $\ast$ matches all the basic types (string, int, etc).
 
@@
 \app parses a verification target configuration file with the translator from Sec.~\ref{sec:trans}  to obtain a set of key-value pairs, $\mathcal{V}$, for that file.
-Then, the checker applies the learner from Eq.~\ref{eq:learn}, $Learn(\mathcal{V})$ to build the set of relations observed in the file, with the thresholds $t_s,t_c = 100\%$. 
+Then, the checker applies the learner from Eq.~\ref{eq:learn},
+$\textit{Learn}(\mathcal{V})$ to build the set of relations observed in the file, with the thresholds $t_s,t_c = 100\%$. 
 The checker will then report the following set of errors:
@@
 \begin{align*}
-Errors(\mathcal{V}) = \{ r\ |\ & X_r \cup Y_r \in \mathcal{V} \ \land \\
-                               & r \in Learn(\trainingSet) \ \land \\
-                               & r \notin Learn(\mathcal{V})
+\textit{Errors}(\mathcal{V}) = \{ r\ |\ & X_r \cup Y_r \in \mathcal{V} \ \land \\
+                               & r \in \textit{Learn}(\trainingSet) \ \land \\
+                               & r \notin \textit{Learn}(\mathcal{V})
 \end{align*}

### 2017-01-25 CAV17/secs/postanal.tex
fix beginning of rule graph part

--- 2017-01-25 CAV17/secs/postanal.tex
@@
 
-\app can output the set of learned rules from the training set as
-described in $\S$\ref{sec-learn}. Recall that a rule is 
+The learner outputs a set of rules learned from the training set as
+described in Sec.~\ref{sec-learn}. Recall that a rule is 
 an implication relationship of the form $r = X \implies p(X,Y)$.
-This data is sufficient for \app to perform its core task of
-configuration file validation, but can be used for more than 
-simple rule checking. By interpreting the rules as a graph (which
+This data is necessary to perform the core verification task,
+but can also be used for further analysis. By interpreting the rules as a graph (which
 we call the {\bf Rule Graph}), we can 
 use tools from graph theory to extract information
-about the configuration space. We inspect properties of this 
+about the configuration space that can improve the quality of the learned model.
+We inspect properties of this 
 Rule Graph to sort reported errors by those most likely to be valid.
 To demonstrate the additional value of the Rule Graph, we
-also use it to estimate the complexity of configuration settings.
+also use it to estimate the complexity of a configuration file.
 
@@
 rule learning technique applied by \app.
-In contrast, the model output from a neural network is not as easily 
-amenable to analysis \cite{nnAnalysis1, nnAnalysis2}, making it harder
-to build on the work of previously developed methods and tools.
+While it is possible to analyze the models from other machine learning techniques such as neural networks~\cite{lei2016rationalizing} and
+conditional random fields~\cite{raychev2015predicting}, these analyses require a deep knowledge of the applied techniques.
+In contrast the Rule Graph is a relatively simple, yet information rich, representation of the learned model.
 The following section provides a precise definition of the Rule Graph
-and the metrics derived for the purposes of ranking reported errors
+and demonstrates useful metrics we derive for the purposes of ranking reported errors
 and complexity analysis.

### 2017-01-25 CAV17/secs/motiv.tex

@@
 using several real-world misconfiguration examples. 
-These examples are non-trivial configuration errors
+These examples are sophisticated configuration errors
 that were reported on StackOverflow~\cite{stackoverflow},

### 2017-01-25 CAV17/secs/postanal.tex

@@
 
-\section{Post Analysis}
+\section{Rule Graph Analysis}
+\label{sec-post}
 
@@
 rule learning technique applied by \app.
-While it is possible to analyze the models from other machine learning techniques such as neural networks~\cite{lei2016rationalizing} and
+While it is possible to analyze the models from other machine learning techniques, such as neural networks~\cite{lei2016rationalizing} and
 conditional random fields~\cite{raychev2015predicting}, these analyses require a deep knowledge of the applied techniques.

### 2017-01-25 CAV17/secs/trans.tex
trans

@@
 Fig.~\ref{fig:ptypes} provides a fragment of a calculus for type judgments for deriving Boolean equality rules with probabilistic types.
-We use the notation, $\ptype \models p$, to denote a probabilistic type whose counts hold on the predicate $p$. For a $\ptype$ with $|\tau_i|$ 
-we denote $c_i$, and $*$ is shorthand for all basic types.
-When there is no evidence for a type $\tau$ we call this empty type ({\scriptsize EMPTY}).
-Initially, before we count any type, all types are set to empty.
+We use the notation, $\ptype \models p$, to denote a probabilistic type whose counts hold on the predicate $p$. 
+For a probabilistic type, $\ptype$, we use the notation $|\tau_i|$ to select from $\ptype$, the $c_i$.
+We use $*$ as a wildcard selector for all basic types in a $\ptype$.
+When there is no evidence for a type $\tau$ we call this the empty type ({\scriptsize EMPTY}). 
+Initially, all keywords are set to the empty set.
 In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
@@
 The result is the probabilistic type \texttt{bar}$:[bool=3,int=1]$.
-By setting $M=3, N=1$, we resolve it to \texttt{bar}$::bool$.
+If in this example, the user had set $M=3, N=1$, we resolve the probabilistic type of \texttt{bar} to \texttt{bar}$::bool$.
+
+\ruzica{Mark, please argue better about this}
 

### 2017-01-25 CAV17/secs/intro.tex
stuff

@@
 \label{sec-intro}
+
+Configuration errors (also known as misconfigurations) have become
+one of the major causes of system failures, resulting in security vulnerabilities,
+application outages, and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}. Recently, there was a problem in accessing  
+Facebook and Instagram~\cite{mashableNews}, 
+and a Facebook spokeswoman reported that 
+this was caused by a change to the site's configuration systems.
+In a recent software system failures study~\cite{yin11anempirical},
+researchers revealed that about 31\% of system failures were caused by 
+configuration errors, which is higher than the percentage of
+failures resulting from program bugs (20\%).
+
+The systems research community has recognized this as an important
+problem~\cite{xu16early}. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration 
+errors~\cite{attariyan10automating,
+su07autobash, whitaker04configuration},
+those tools mainly try to understand {\emph{what}} caused the 
+error -- they are still not on a level of
+automatic verification tools used for regular program 
+verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
+detect errors without executing the code. In this paper we propose
+a framework for automated verification of configuration files: we are analyzing 
+files and proactively reporting potential errors, without waiting for them to happen.
+
+Configuration errors were
+reported to be the largest fraction of failures in storage systems in a 2014 industry
+survey~\cite{yin11anempirical}.
 

### 2017-01-25 CAV17/secs/learner.tex

@@
 
-A \textit{rule}, $r$, is then an implication relationship, $r = X \implies p(X,Y)$, between two possibly empty sets of keywords $X,Y \subset \keys$, where $\keys$ is the set of unique keys from the training set (denoted \trainingSet) and the predicate $p$ is one of the classes of configuration errors.
-Implicitly we interpret a rule to mean that if the keywords $X\cup Y$ appear in a configuration file, the predicate $p$ should hold.
+A \textit{rule}, $r$, is then an implication relationship, $r = S \implies p(S,T)$, between two possibly empty sets of keywords $S,T \subset \keys$, which we call the source and target keyword sets.
+The set $\keys$ is the set of unique keys from the training set (denoted \trainingSet) and the predicate $p$ is one of the classes of configuration errors.
+Implicitly we interpret a rule to mean that if the keywords $S\cup T$ appear in a configuration file, the predicate $p$ should hold.
 The task of the learning algorithm is to transform a training set to a set of rules, weighted with \textit{support} and \textit{confidence}.
@@
 \begin{equation*}
- \textit{support(r)} = \frac{|\{C \in \trainingSet \mid X_r \cup Y_r \subseteq C\}|} {|\trainingSet|}
+ \textit{support(r)} = \frac{|\{C \in \trainingSet \mid S_r \cup T_r \subseteq C\}|} {|\trainingSet|}
 \end{equation*}
 \begin{equation*}
- \textit{confidence(r)} = \frac{|\{C \in \trainingSet \mid p_r(X_r,Y_r) \subseteq C\}| } {support(r)*|\trainingSet|}
+ \textit{confidence(r)} = \frac{|\{C \in \trainingSet \mid p_r(S_r,T_r) \subseteq C\}| } {support(r)*|\trainingSet|}
 \end{equation*}
 
-Support is the frequency that the that set of keywords in the proposed rule, $X \cup Y$, have been seen in the configuration files $C$ in the training set \trainingSet.
+Support is the frequency that the that set of keywords in the proposed rule, $S \cup T$, have been seen in the configuration files $C$ in the training set \trainingSet.
 %Notice support does not consider the predicate itself, only how many times the predicate had the chance to be evaluated.
@@
     & \textit{confidence(r)} > t_c\ \land \label{eq:learn}\\ 
-    & X,\ Y \subset \keys\} \nonumber
+    & S,\ T \subset \keys\} \nonumber
 \end{align}
@@
 \subsection{Error Classes}
-Each class of error forms a rule with a predicate $p$, and additional restrictions on the sets $X, Y$.
-Ordering errors have $|X|, |Y| = 1$ and use the predicate $order$ to mean the keyword $X$ must come before the keyword $Y$ in any configuration file.
-Missing keyword entry errors also require $|X|, |Y| = 1$ and use the predicate $missing$ to mean the keyword $X$ must appear in the same file as the keyword $Y$ in any configuration file.
+Each class of error forms a rule with a predicate $p$, and additional restrictions on the sets $S, T$.
+Ordering errors have $|S|, |T| = 1$ and use the predicate $order$ to mean the keyword $S$ must come before the keyword $T$ in any configuration file.
+Missing keyword entry errors also require $|S|, |T| = 1$ and use the predicate $missing$ to mean the keyword $S$ must appear in the same file as the keyword $T$ in any configuration file.
 The type rule is a set of rules over multiple predicates, which take the
-form $X \implies \textit{isType}\ast(X)$, where $|X|=1, |Y|=0$ and $\ast$ matches all the basic types (string, int, etc).
+form $S \implies \textit{isType}\ast(S)$, where $|S|=1, |T|=0$ and $\ast$ matches all the basic types (string, int, etc).
 
@@
 Both integer correlation rules are set of rules over the predicates $\{<,=,>\}$.
-Coarse grain rules require $|X|, |Y| = 1$, and the predicates have the typical interpretation.
-Fine-grained rules use $|X|=2,|Y|=1$, and interpret the predicates such that for $k_1,\ k_2 \in X,\ k1*k2$ must have the predicate relation to $Y$.
+Coarse grain rules require $|S|, |T| = 1$, and the predicates have the typical interpretation.
+Fine-grained rules use $|S|=2,|T|=1$, and interpret the predicates such that for $k_1,\ k_2 \in S,\ k1*k2$ must have the predicate relation to $T$.
 The integer correlation rules also use probabilistic types to prune the search space.
@@
 \begin{align*}
-\textit{Errors}(\mathcal{V}) = \{ r\ |\ & X_r \cup Y_r \in \mathcal{V} \ \land \\
+\textit{Errors}(\mathcal{V}) = \{ r\ |\ & S_r \cup T_r \in \mathcal{V} \ \land \\
                                & r \in \textit{Learn}(\trainingSet) \ \land \\

### 2017-01-25 CAV17/secs/postanal.tex

@@
 described in Sec.~\ref{sec-learn}. Recall that a rule is 
-an implication relationship of the form $r = X \implies p(X,Y)$.
+an implication relationship of the form $r = S \implies p(S,T)$.
 This data is necessary to perform the core verification task,
 but can also be used for further analysis. By interpreting the rules as a graph (which
-we call the {\bf Rule Graph}), we can 
+we call the \textit{Rule Graph}), we can 
 use tools from graph theory to extract information
@@
 \forall r \in & Learn(\trainingSet).\ \exists e\ \in E.\\
-              & V_s = X_r \land V_t=Y_r \land l=p_r \land w =
+              & V_s = S_r \land V_t=T_r \land l=p_r \land w =
 \textit{confidence(r)}
@@
 
-    $$|E| = \sum_{(X, Y, l, w) \in E} w$$
+    $$|E| = \sum_{(S, T, l, w) \in E} w$$
 

### 2017-01-25 CAV17/secs/table2.tex
cav17: tabl2

--- 2017-01-24 CAV17/secs/table2.tex
@@
 \label{table-casestudy}
+\setlength{\tabcolsep}{0.5em}
 \begin{footnotesize}
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|c|g|g|c|}
 \hline
-{\bf Errors} & {\bf URLs} & {\bf Rank w/o} & {\bf Rank w/}\\ 
+{\bf Errors} & {\bf URLs} & {\bf None} & {\bf PA} & {\bf PT} & {\bf PT$\land$ PA}\\ 
 \hline
 \hline
-\multirow{3}{*}{MISSING ERROR: Expected "key-buffer"} & url & 7 & 8 \\
-\multirow{3} & url & 9 & 10 \\ 
-& url & 11 & 12 \\ 
+\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize ORDERING ERROR: Expected ``innodb\_data\_home\_dir'' BEFORE ``innodb\_data\_file\_path''} }
+& \cite{order1} & 12/12 & 3/12 & 5/5 & 3/5 \\
+& \cite{order2} & 11/11 & 2/11 & 3/3 & 3/3 \\ 
+& \cite{order3} & 3/9  & 4/4 & 3/4 \\ 
 \hline
 
-\multirow{3}{*}{Ordering} & url & 7 & 8 \\ & url & 9 & 10 \\
-& url & 11 & 12 \\  
+\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize MISSING ERROR: Expected ``key\_buffer'' WITH [isamchk]} }
+& \cite{missing1} & 6/10 & 2/10 & 2/4 & 2/4 \\ 
+& \cite{missing2} & 2/3 & 3/3 & 2/3 & 3/3 \\
+& \cite{missing3} & 2/3 & 3/3 & 2/2 & 3/3 \\  
 \hline
 
-\multirow{3}{*}{Type error} & url & 7 & 8 \\ & url & 9 & 10 \\  
-& url & 11 & 12 \\
+\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize TYPE ERROR: Expected an integer for “slow\_query\_log”}}
+& \cite{type1} & 32/34 & 1/34 & 5/7   & 1/7 \\ 
+& \cite{type2} & 9/20  & 2/20 & 10/11 & 2/11 \\  
+& \cite{type3} & 9/19  & 2/19 & 10/11 & 2/11 \\
 \hline
 
-\multirow{3}{*}{fine-grained} & url & 7 & 8 \\ & url & 9 & 10 \\  
-& url & 11 & 12 \\
+\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize FINE GRAINED ERROR: Expected \\ ``max\_connections'' * ``sort\_buffer\_size'' $\geq$ ``key\_buffer\_size''}}
+& \cite{fine1} & 30/34 & 18/34 & 6/7 & 3/7 \\ 
+& \cite{fine2} & 23/25 & 9/25  & 8/9 & 3/9 \\  
+& \cite{fine3} & 20/23 & 14/23 & 6/7 & 5/7 \\
 \hline
 
-\multirow{3}{*}{int correlation} & url & 7 & 8 \\ & url & 9 & 10 \\  
-& url & 11 & 12 \\
+\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize INTEGER CORRELATION ERROR: Expected ``max\_allowed\_packet'' $<$ ``innodb\_buffer\_pool\_size''} }
+& \cite{int1} & 29/32 & 8/32 & 11/14 & 4/14 \\ 
+& \cite{int2} & 22/23 & 2/23 & 9/10  & 2/10 \\  
+& \cite{int3} & 10/12 & 4/12 & 4/4   & 2/4 \\
 \hline

### 2017-01-25 CAV17/secs/table2.tex
cav17: table2

@@
 & \cite{order2} & 11/11 & 2/11 & 3/3 & 3/3 \\ 
-& \cite{order3} & 3/9  & 4/4 & 3/4 \\ 
+& \cite{order3} & 9/9 & 3/9  & 4/4 & 3/4 \\ 
 \hline

### 2017-01-25 CAV17/secs/eval.tex
cav17: eval
finish eval

@@
 
-We have implemented a \app prototype, and evaluated it based on
-real-world configuration datasets.
-
-\subsection{Prototype Implementation}
-
-\ennan{put the implementation as one or more paragraphs.}
+We have implemented a tool, \app, and evaluated it based on real-world configuration files taken from Github.
+\app is written in Haskell and is available open source at \textit{url redacted for anonymity}.
+Thanks to the Haskell's powerful type system, the implementation can easily be extended with with new rule classes or applied to different configuration languages with minimal change to the rest of the code base.
 
@@
 
-To evaluate our \app prototype, we need to have two datasets:
-1)a training set and 2) a dataset for testing. 
+To evaluate our \app prototype, we require a separate training set and test set. 
 For our training set, \trainingSet, we use a preexisting set of 256 
@@
 analysis work~\cite{configdataset}.
-The majority of configuration files in this training set are incorrect.
-For our evaluation, we collected 1000 MySQL configuration files 
-from Github, and filtered the poorly formatted files out for a final 
-total of 973 files, called as {\em test set}.
-In our evaluation we focus on MySQL for consistency, 
-but \app can handle any configuration language (that can be parsed to 
-the intermediate representation from Sec.~\ref{sec:trans}).
+This is an unlabeled training set, though most of the files have some errors.
+For our test set, we collected 1000 MySQL configuration files 
+from Github, and filtered the incorrectly formatted files out for a final 
+total of 973 files.
+In our evaluation we focus on MySQL for comparability of results, but \app can handle any configuration language (that can be parsed to the intermediate representation from Sec.~\ref{sec:trans}).
+
 We report the number of rules learned from the training set and number of errors detected in the test set in Table~\ref{table:learning}.
+We also provide the support and confidence thresholds, $t_s, t_c$, used in this evaluation.
+These number can be adjusted by the user as a slider to control the level of assurance that their file is correct.
+Since these settings depend on both the user preference and training set quality, we simply choose values for which \app reports reasonably sized output.
 
-Note that in contrast to program verification, we do not have an oracle for determining if a reported error is a true error, or a false positive, where a false positive means an error that has no impact on the system.
-While we can run program to determine the effect a specification has on success of compiling or running the program, no such test exists for configuration files.
-Because misconfigurations are dependent on the rest of the system, the available hardware, and the usage patterns, we cannot simulate the all conditions to determine if a reported error will cause system failure.
-As evidenced by Example~\ref{ex:fine}, some misconfigurations will only cause greater than expected performance degradation, and only under particular traffic loads.
-In this case, the definition of a true error is necessarily imprecise.
+We record the histogram of errors across the test set in Fig.~\ref{fig:histo}.
+This is intuitively an expected result from randomly sampling Github - most repositories will have few errors, with an increasingly small number of repositories having many errors.
 
-However, we are able to manually determine that some errors are true
-positives by searching forums like StackOverflow for records that
-particular configuration settings have cause problems on real-world
-systems.
+\begin{figure}[h]
+\includegraphics[width=\textwidth]{figs/histogram.png}
+\caption{Histogram of errors - 14 errors were detected in 1 file}
+\label{fig:histo}
+\end{figure}
 
@@
 
-Without ptypes - finegrained = 327 rules and 1367 detections
+The errors reported may have varying impacts on the system, ranging from failing to start, runtime crash, or performance degradation.
+However, since \app is a probabilistic system, it is also possible that some errors are false positives, a violation of the rule has no effect on the system.
+Note that in contrast to program verification, we do not have an oracle for determining if a reported error is a true error or a false positive.
+While we can run a program to determine the effect a specification has on the success of compiling/running the program, no such test exists for configuration files.
+Because configurations are dependent on the rest of the system (\ie the available hardware, the network speed, and the usage patterns), we cannot simulate the all conditions to determine if a reported error will cause system failure.
+As evidenced by Example~\ref{ex:fine}, some misconfigurations will only cause greater than expected performance degradation, and only under particular traffic loads.
+In light of this, the definition of a true error is necessarily imprecise.
 
-The errors reported may have a varying impact on the system, ranging from failing to start, runtime crash, or performance degradation.
-Since this is a probablistic system, it is also that some errors are false positives, a violation of the rule has no effect on the system.
-It it therefore desirable to sort the reported errors in order of severity. 
-To achieve this we use the post analysis metric described in Sec.~\ref{sec:ruleorder}.
-To estimate the impact of this metric, we track the rank of known true positives with, and without, the augmented rule ordering in Table~\ref{table:order}.
-We compare how close the updated rank is compared to the ideal rank, which was calculated by ennan and estimates the potential severity of an error related to those keywords.
-Maybe we actually compare measure the distance from the ideal rank, so that a value of 0 is good.
+Although we cannot identify false positives, we can identify true positives by examining online forums, like StackOverflow, for record that
+particular configuration settings have caused problems on real-world systems.
+Furthermore, any error for which we can find evidence online is likely to be more problematic than errors that do not have an online record, 
+  using the reasoning that this error has caused enough problems for people to seek help online.
+In this case, we would like \app to can sort the errors by their importance or potential severity.
+To achieve this sorting we use the Rule Graph analysis metric described in Sec.~\ref{sec:ruleorder}.
+
+To estimate the impact of this metric, we track the rank of known true positives with, and without, the augmented rule ordering in Table~\ref{table-casestudy}.
+For this table, we picked the known true positive rules, listed in the Errors column, and pick configuration files in the test set that have these errors.
+We picked 3 files for each true positive by choosing the files the most total errors to most clearly observe the effects of our optimizations.
+We test the following conditions; just Rule Graph analysis (RG) to sort the errors, just probabilistic types to filter the rules (PT), and both optimizations at the same time (RG $\land$ PT).
+For each entry we list X/Y, where X is the rank of the known true positive, and Y is the total number of errors found on that file.
+%Here we also compare the effect of probabilistic types - without probablitic types we learned 327 fin grainedrules and 1367 detections
 
@@
 
-The checker stage of \app is the only one facing an end user that wants to verify a new configuration file.
-Once a set of rules has been learned, it is not necessary to rerun the learner.
-However, we have only used \app to build rules for MySQL, but any configuration language can be analyzed with \app given a training set.
-In an industrial setting, the available training set may be much larger than ours as well, so is important that the learning process scales.
+We also evaluate the speed of \app.
+Generally, once a set of rules has been learned, it is not necessary to rerun the learner.
+However, we have only used \app to build rules for MySQL, but any configuration language can be analyzed with \app given a training set, which requires rerunning the learner.
+Additionally, in an industrial setting, the available training set may be much larger than ours, so is important that the learning process scales.
 We see in Table~\ref{table:training} that \app scales roughly linearly.
 
-\markk{TODO rewrite}
-We also compare \app to prior work in configuration verification, ConfigC~\cite{santolucitoCAV}.
+We compare \app to prior work in configuration verification, ConfigC~\cite{santolucitoCAV}.
 ConfigC scales exponentially because the learning algorithm assumes a completely correct training set, and learns every derivable relation.

### 2017-01-25 CAV17/secs/postanal.tex
finish eval

@@
 \begin{align*}
-    E_{V_1, V_2} = \{ \left( V_s, V_t, l, w \right) \in E \ \mid \ & \exists v_1 \in V_1 \land v_1 \in V_s \\
-    & \land \exists v_2 \in V_2 \land v_2 \in V_t \}
+    E_{V_1, V_2} = \{ \left( V_s, V_t, l, w \right) \in E \ \mid \ & \exists v_1 \in V_1 \land v_1 \in V_s \ \land\\
+    & \exists v_2 \in V_2 \land v_2 \in V_t \}
 \end{align*}
@@
 organizations to manage configuration files in much the same way
-as Kolomogrov complexity~\cite{kolomogrov} is used to manage code - identifying
+as Kolomogrov complexity~\cite{kolmogorov1965} is used to manage code - identifying
 potentially brittle configurations for targeted refactoring.
-
-\para {Definition}
 
@@
 \end{equation}
-
-\para {Discussion}
 

### 2017-01-25 CAV17/secs/related.tex
cav17: related work and concl
cav17: related
finish eval

@@
 
-\para{Language-support misconfiguration checking.}
+\para{Language-support misconfiguration checking}
 There have been several language-support efforts proposed for preventing
@@
 to convenient configuration-file writing. 
-
 The closest effort to \app is ConfigC~\cite{santolucitoCAV},
@@
 
+\com{
 \para{Misconfiguration tolerance}
@@
 
-\com{Making systems gracefully handle misconfigurations and eliminating
+Making systems gracefully handle misconfigurations and eliminating
 configuration errors are two orthogonal directions.

### 2017-01-25 CAV17/secs/table2.tex
finish eval

@@
-\newcommand{\tablewidth}{6cm}
+\newcommand{\tablewidth}{5.9cm}
 \definecolor{Gray}{gray}{0.80}
@@
 \hline
-{\bf Errors} & {\bf URLs} & {\bf None} & {\bf PA} & {\bf PT} & {\bf PT$\land$ PA}\\ 
+{\bf Errors} & {\bf URLs} & {\bf None} & {\bf RG} & {\bf PT} & {\bf RG$\land$ PA}\\ 
 \hline
@@
 
-\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize FINE GRAINED ERROR: Expected \\ ``max\_connections'' * ``sort\_buffer\_size'' $\geq$ ``key\_buffer\_size''}}
+\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize FINE GRAINED ERROR: Expected \\ ``max\_connections'' * ``sort\_buffer\_size'' $>$ ``key\_buffer\_size''}}
 & \cite{fine1} & 30/34 & 18/34 & 6/7 & 3/7 \\ 

### 2017-01-25 CAV17/secs/intro.tex
stuff

@@
 a framework for automated verification of configuration files: we are analyzing 
-files and proactively reporting potential errors, without waiting for them to happen.
+files and proactively reporting potential errors, without waiting for them to happen. We developed a tool, called \app, and tested it on 
+almost a thousand file from github.
 
-Configuration errors were
-reported to be the largest fraction of failures in storage systems in a 2014 industry
-survey~\cite{yin11anempirical}.
+We believe there are two main obstacles 
+to why we cannot simply apply  the existing automatic 
+tools and techniques to verification of configuration files:
+1) the lack
+of a specification describing properties of configuration files;
+2) the structure of configuration files -- they
+are mainly a sequence of entries assigning some value to system
+variables (called {\emph {keywords}}). 
+The language in which configuration files are written does 
+not adhere to a specific grammar or syntax. In particular, the
+entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries, and there
+is no explicit structure policy for the entries.
 
-Configuration errors are one of the most important root causes of today's 
-software system failures~\cite{xu15systems, yin11anempirical}.
-In their empirical study, Yin {\em et al.}~\cite{yin11anempirical} report 
-that about 31\% of system failures were caused by misconfiguration problems
-and only 20\% were caused by bugs in program code. 
-Misconfigurations, in practice, may result in various system-wide problems,
-including security vulnerabilities, application crashes, severe disruptions
-in software functionality, 
-and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}.  
-Therefore, how to automatically verify configuration files is an open
-problem~\cite{xu15systems}.
+\app overcomes the above obstacles by first automatically inferring a
+specification for configuration files. It is unrealistic to expect the 
+users to write an entire specification for configuration files on their own. 
+This process can easily lead to incomplete or even contradictory 
+specifications. Instead, we learn specification from 
+a large sample of 
+configuration files~\cite{configdataset}. The first step is to 
+translate this training set into a more structured typed representation.
+We then apply the learning process and we learn an abundant set of rules 
+specifying various properties that hold on the given sample. The rules, in general, 
+specify which properties keywords in configuration files need to satisfy.
+The learning process is language-agnostic and works for any kind 
+of configuration files,  but all of the files in the sample need to be of 
+the same kind (such as MySQL or HTTPD configuration files).
+We see this learning process as 
+a way of deriving  a specification for configuration files. 
+It is hard to talk here about a complete specification, but it is still
+a set of formal rules describing the properties that configuration files need to satisfy.
 
-To the best of our knowledge, there have been several prior 
-efforts that attempt to verify 
+Having a specification, \app can then efficiently check 
+the correctness of the configuration files of interest and detect 
+potential errors. Errors are reported if the configuration file does not 
+adhere to the derived specification.
+
+There have been several prior efforts that attempt to verify 
 configuration files~\cite{santolucitoCAV, xu16early,
@@
 in reality, or can only deal with simplistic configuration errors.
-In general, these efforts fall into two categories.
-
-\squishlist
-
-\item On the one hand are tools that can detect sophisticated 
+In general, these efforts fall into two categories.\begin{itemize}
+\item On the one hand there are tools that can detect sophisticated 
 configuration errors, \eg, ConfigC~\cite{santolucitoCAV}. 
@@
 files to drive rules is almost impossible in reality. 
-Without 100\% correct datasets, these tools would, unfortunately, 
-work poorly.
-
-\item On the other hand, practical efforts, 
+Without 100\% correct datasets, these tools do not work.
+\item On the other hand there are tools, 
 \eg, EnCore~\cite{zhang14encore} and
-ConfValley~\cite{huang15confvalley}, can only 
-detect simplistic configuration errors (\eg, value range errors 
+ConfValley~\cite{huang15confvalley}, that can only 
+detect rather simplistic configuration errors (\eg, value range errors 
 and simple integer correlation errors), but cannot detect
-sophisticated configuration errors. 
-Consider entry ordering errors, 
-which happen when some entries are inserted in a wrong order
-in the configuration files. 
-For example, in a PHP configuration file, 
-an entry \code{extension=mysql.so} appears 
-before \code{extension=recode.so},  
-it would cause Apache server to crash. The correct ordering 
-should be \code{extension=recode.so} before 
-\code{extension=mysql.so}~\cite{yin11anempirical}.
+more complex configuration errors, such as ordering errors or 
 Nevertheless, these types of errors cannot be detected by above existing
 efforts.
-
-\squishend
-
-The goal of this work is to propose and build a {\em practical} 
-configuration
-verification tool capable of checking {\em sophisticated} 
-configuration errors (more details
-for sophisticated configuration errors in Sec.~\ref{sec:motiv}).
-Achieving this goal requires us addressing two main obstacles:
-1) the lack of a specification describing properties of configuration
-files, and 2) the structure of configuration files---they are 
-mainly a sequence of entries assigning some values to system
-parameters (called keywords).
-In other words, the ``language'' in which configuration 
-files are written does not adhere to any specific grammar or syntax. 
-Moreover, the entries in configuration files 
-lack type or rules specifying constraints on entries, 
-and there is no explicit structure policy for these entries.
+\end{itemize}
 

### 2017-01-25 CAV17/secs/intro.tex
stuff

@@
 
-This paper presents \app, the first automatic verification framework
-for general software configurations, by overcoming the above two
-obstacles. In general, \app verifies a given configuration file $F$ 
-through three steps:
+Our learning algorithm surmounts all of difficulties present in 
+existing tools.  \app implements a learning
+algorithm inspired by {\em rule association
+learning}~\cite{agrawal1993mining}. It analyzes a large training set of configuration  files~\cite{configdataset}. Those are real-world reported misconfigurations. A file in the training set might 
+contain several different errors and these errors only appear 
+in a small percentage of files. We first translate those file into an 
+intermediary typed language. With with every type we associate 
+a set of very general templates. The user does not
+need to provide any templates, they are internally associated to the types.
 
-\para{Step~1: Translator}
-\app takes as input a large training set of configuration files
-belonging the same system as $F$,
-and we do not have any assumption on the correctness of these files.
-\app analyzes the training set, and generates a well-structured and
-probabilistically-typed intermediate representations.
-
-\para{Step~2: Learning}
-\app derives configuration rules by running {\em rule association
-learning} algorithm to learn the generated intermediate representations.
+ algorithm to learn the generated intermediate representations.
 The insight of our design is: every file in the training set

### 2017-01-25 CAV17/secs/trans.tex

--- 2017-01-24 CAV17/secs/trans.tex
@@
 Fig.~\ref{fig:ptypes} provides a fragment of a calculus for type judgments for deriving Boolean equality rules with probabilistic types.
-We use the notation, $\ptype \models p$, to denote a probabilistic type whose counts hold on the predicate $p$. For a $\ptype$ with $|\tau_i|$ 
-we denote $c_i$, and $*$ is shorthand for all basic types.
-When there is no evidence for a type $\tau$ we call this empty type ({\scriptsize EMPTY}).
-Initially, before we count any type, all types are set to empty.
-In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
+When there is no evidence for a type $\tau$ we call this the empty type. 
+Initially, all keywords are set to the empty set ({\scriptsize EMPTY}).
+In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to a basic type when the $\ptype$ satisfies the predicate $p_{bool}$, \ie\ the type has enough evidence.
 The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
@@
 \and
+\inferrule* [Right=int\_resolve]
+{k:\ptype \\ p_{int}(\ptype)}
+{k :: int}
+\and
 \inferrule* [Right=bool\_resolve]
-{k:\ptype \\ \ptype \models |bool| \geq M \land |\ast| \leq N}
+{k:\ptype \\ p_{bool}(\ptype)}
 {k :: bool}
@@
 \end{mathpar}
-\caption{Type judgments for Boolean equality rules with probabilistic types}
+\caption{Type judgments for a probabilistic type system with $\mathcal{T} = \{bool,int\}$ and an equality rule}
 \label{fig:ptypes}
@@
 
-Taking these type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
-The result is the probabilistic type \texttt{bar}$:[bool=3,int=1]$.
-By setting $M=3, N=1$, we resolve it to \texttt{bar}$::bool$.
+In order to define predicates, we use the notation $|\tau_i\ptype|$ to select $c_i$ from a $\ptype \in \tilde{\mathcal{T}}$, 
+  and the symbol $*$ as a wildcard selector for all basic types in a $\ptype$.
+As an example, we can set the predicate $p_{bool}(\ptype)= |bool\ptype| \geq 3 \land |\ast\ptype| \leq 1$.
+Then taking these type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
+The result is the probabilistic type \texttt{bar}$:[bool=3,int=1]$, which is then resolved to \texttt{bar}$::bool$.
 
-A user may implement overlapping inference rules, for example in {\scriptsize INT\_RESOLVE}.
-This not a subtyping relation, as the predicates over the counts may not be strictly overlapping.
-%TODO this make no sense - address ambiguity more clearly
+A user may pick predicates for probabilistic type resolution that result in overlapping inference rules
+For example, if a user picks $p_{int}(\ptype)= |int\ptype| \geq 1$, then {\scriptsize INT\_RESOLVE} overlaps with {\scriptsize BOOL\_RESOLVE}.
+This not a not simply a subtyping relation, as the predicates over the counts may not be strictly overlapping.
 We simply allow the double colon (::) to type a single keyword in multiple ways.
@@
 
+In the case that there is not enough evidence to resolve a probabilistic type to a basic type, no type-dependent rules may be learned over that keyword.
+However, we are still able to learn rules such as {\scriptsize ORDER}, which do not require any resolved type.
+
 \begin{mathpar}
 \hspace{-0.8cm} %no idea why, but this is better than \centering here
-\inferrule* [Right=int\_resolve]
-{k:\ptype \\ \ptype \models int \geq 1}
-{k :: int}
 \and
@@
 \end{mathpar}
-
-In the case that there is not enough evidence to resolve a probabilistic type to a basic type, no type-dependent rules may be learned over that keyword.
-We are still able to learn rules such as {\scriptsize ORDER}, which do not require any resolved type.

### 2017-01-25 CAV17/secs/postanal.tex
fix overview and lower case rule graph

@@
 
-    - Additional interpretations of the Rule Graph
+    - Additional interpretations of the rule graph
 
@@
 
-\section{Rule Graph Analysis}
+\section{rule graph Analysis}
 \label{sec-post}
@@
 but can also be used for further analysis. By interpreting the rules as a graph (which
-we call the \textit{Rule Graph}), we can 
+we call the \textit{rule graph}), we can 
 use tools from graph theory to extract information
@@
 We inspect properties of this 
-Rule Graph to sort reported errors by those most likely to be valid.
-To demonstrate the additional value of the Rule Graph, we
+rule graph to sort reported errors by those most likely to be valid.
+To demonstrate the additional value of the rule graph, we
 also use it to estimate the complexity of a configuration file.
 
-Accessibility of the Rule Graph is a useful property of the association 
+Accessibility of the rule graph is a useful property of the association 
 rule learning technique applied by \app.
@@
 conditional random fields~\cite{raychev2015predicting}, these analyses require a deep knowledge of the applied techniques.
-In contrast the Rule Graph is a relatively simple, yet information rich, representation of the learned model.
-The following section provides a precise definition of the Rule Graph
+In contrast the rule graph is a relatively simple, yet information rich, representation of the learned model.
+The following section provides a precise definition of the rule graph
 and demonstrates useful metrics we derive for the purposes of ranking reported errors
@@
 
-We define the \textit{Rule Graph} as a directed hypergraph $H = (V,E)$,
+We define the \textit{rule graph} as a directed hypergraph $H = (V,E)$,
    with vertices $V = \{ keywords \}$ and labeled, weighted edges $E = \{ (V_s, V_t, l, w) \}$.
@@
 The use of the support and confidence thresholds $t_s$ and $t_c$ in the learner ensure 
-that all weights in the Rule Graph are positive.
+that all weights in the rule graph are positive.
 
@@
 The more rules of high confidence are extracted for a keyword by the learner, 
-the higher the $\mathcal{D}(v)$ of the corresponding vertex in the Rule Graph.
+the higher the $\mathcal{D}(v)$ of the corresponding vertex in the rule graph.
 In our final analysis, we use this classification to
@@
 
-We may also use the Rule Graph to advance our general knowledge
+We may also use the rule graph to advance our general knowledge
 of the configuration space, outside the strict confines of a
@@
 for configuration file complexity based on the topology of the
-Rule Graph. This measure of complexity could be used by software
+rule graph. This measure of complexity could be used by software
 organizations to manage configuration files in much the same way
@@
 For a configuration file with a set of keywords $K$
-and a Rule Graph $H = (V, E)$, we define our complexity measure:
+and a rule graph $H = (V, E)$, we define our complexity measure:
 
@@
 extension of the na\"ive line-counting measure of complexity.
-When a keyword in the configuration file is present in the Rule Graph,
+When a keyword in the configuration file is present in the rule graph,
 we may consider the set $E_{k, K}$ to be all learned rules involving
@@
 If a keyword is not constrained at all in the current configuration
-file or is not present in the Rule Graph, we revert to the standard
+file or is not present in the rule graph, we revert to the standard
 counting metric of complexity.

### 2017-01-25 CAV17/secs/intro.tex
stuff

@@
 files and proactively reporting potential errors, without waiting for them to happen. We developed a tool, called \app, and tested it on 
-almost a thousand file from github.
+almost a thousand file from Github.
 
@@
 intermediary typed language. With with every type we associate 
-a set of very general templates. The user does not
-need to provide any templates, they are internally associated to the types.
+a set of very general interfaces. An \app's user does not
+need to provide them, they are internally associated to the types. The 
+learner then instantiates those interfaces with the keywords appearing in 
+the training set. However, since files might also contain errors we take 
+this into account when learning correct rules. All learned rules are 
+annotated with the probability of correctness.  
+To ensure the learned rules are good enough,
+\app employs a further analysis to refine the learned rules.
+In general, \app builds a graph modeling the learned rules,
+and then analyzes this graph to rank the importance
+and relevance of the learned rules.
 
- algorithm to learn the generated intermediate representations.
-The insight of our design is: every file in the training set
-contains several different errors and these errors only appear 
-in a small percentage of files. Based on this insight,
-we are able, with the help of the probabilistic cutoff, to learn a
-set of configuration rules. These rules, in general, specify 
-which properties the entries in configuration files need to satisfy. 
-One can see this learning process as a way of deriving  
-a specification for configuration files.  
-Once a specification is obtained, we can do verification that 
-uses these learned rules to check the correctness of 
-the configuration files
-of interest and detect potential errors.
-
-\para{Step~3: Rule graph analysis}
-To ensure the learned rules are good enough,
-\app employs a further analysis stage to refine the learned rules.
-In general, \app builds a graph to model the learned rules,
-and analyzes this graph's properties, ranking the importance
-and relevance of these rules. Finally, \app outputs
-a set of refined rules as the eventual specification
-to check the target configuration file $F$.
+\ruzica{mark, please put here summary of evaluation resuls}
 
@@
 and refine these rules. Finally, we check sophisticated 
-errors of real configuration files crawled from github,
+errors of real configuration files crawled from Github,
 and detect many errors in these widely-used configuration files.

### 2017-01-25 CAV17/secs/arch.tex

@@
 Figure~\ref{fig-overview} gives an overview of the \app framework.
-The biggest part is dedicated to 
+The main part is dedicated to 
 learning and inferring the specification for configuration 
@@
 
-\para{Initial phase}
-Since there is no proper formal specification for configuration 
-files, we learn the specification from a large number of 
-(not necessarily correct) configuration files belonging to the same 
-system, such as MySQL or Apache. These files are our training set.
-
-%In the following steps,
-%we will exploit in a collection of learning algorithms 
-%to build rules that describe a language model for the files.
-
 \para{Translator}
 The translator module first parses the input training  
-set of configuration files, and then transforms them into 
-a more structured and typed intermediate representation.
-Most of entries in a configuration file follow a key-value pattern, 
+set of configuration files and transforms them into 
+a typed intermediate representation.
+Entries in a configuration file follow a key-value pattern, 
 where some environmental variable (``key'') is assigned a value.
-Looking at a single entry, by inspecting the value
-we cannot always fully determine the type of the key~\cite{xu15hey}.
+However, it is not always possible to fully determine the type of the key
+by inspecting the value at a single entry~\cite{xu15hey}.
 We address this problem 
@@
 Rather than giving a variable a single type, 
-we assign several types over a probability distribution.
+we assign several types over a probability distribution that can later be resolved to type upon which we will learn rules.
 
 \para{Learning}
-The learner reads a set of configuration files that have been translated
-into well-structured representations. 
-It employs a learning algorithm, {\em rule association 
-algorithm}, to generate a list of rules, describing properties 
-of configuration files. In a nutshell, the learning algorithm 
-takes a set of rule interfaces and instantiate them with the concrete
-values that appear in the training set. Since there are no guarantees 
-that the files in the training set are correct, our main assumption
-is that even if a file contains an error, majority of the files do not 
-have the same error and our learning process should detect these
-
-generate concrete instances of t
-
-\ruzica{i need to read the rest of the paper first}
-
-These rules are the outputs of the learner, 
-and will be used to detect errors later.
-Because the translator gives the learner probabilistically typed entries,
-the learner is also responsible for determining types for these entries.
+The learner converts the intermediate representation from the translator to a set of rules.
+It employs variation on the {\em rule association 
+algorithm}~\cite{agrawal1993mining}, to generate this list of rules, which describe properties of a correct configuration file. 
+This is a probabilistic verification approach that learns a specification for a correct file over an unlabeled training set of both correct and incorrect configurations files.
+The learning algorithm uses various instances of a rule interface to learn different classes of rules, such as ordering or integer relations.
+These rules are then considered to be required for any configuration files to be correct, and can be used for verification.
 
 \para{Post Analysis}
-Finally, the logically structured representation of learned rules allows for a further post analysis stage.
-This novel extension infers knowledge on the accepted rules that can improve the output of the system.
-As a case study, we build a graph to model the learned rules.
+Finally, the logically structured representation of learned rules allows for a further \textit{rule graph analysis}.
+We introduce the concept of a rule graph that can be built from the output of the modified association rule learning algorithm.
 We analyze the properties of this graph to construct an ordering of rules by their importance, 
@@
 The information contained in the structured representation of the learned rules, 
-  is a unique benefit of the learning algorithm, as contrasted with other machine learning techniques.
+  is a unique benefit of the learning algorithm, that has potential to be leveraged in many new ways.

### 2017-01-25 CAV17/secs/eval.tex
fix overview and lower case rule graph
total rewrite of ptypes

@@
 Thanks to the Haskell's powerful type system, the implementation can easily be extended with with new rule classes or applied to different configuration languages with minimal change to the rest of the code base.
+A user only needs to provide the functions for the rule interface (a typeclass in Haskell) to 1) learn relations from a single file 2) merge two sets of rules and 3) check a file given some set of rules.
 
@@
 Missing      & 53  & 55   & 2 \%  & 71\% \\ 
-Type         & 92  & 389  & -  & -  \\ 
+Type         & 92  & 389  & 12 \% & 70\%  \\ 
 Fine-Grain   & 213 & 324  & 24 \% & 91\%  \\ 
@@
 In this case, we would like \app to can sort the errors by their importance or potential severity.
-To achieve this sorting we use the Rule Graph analysis metric described in Sec.~\ref{sec:ruleorder}.
+To achieve this sorting we use the rule graph analysis metric described in Sec.~\ref{sec:ruleorder}.
 
@@
 We picked 3 files for each true positive by choosing the files the most total errors to most clearly observe the effects of our optimizations.
-We test the following conditions; just Rule Graph analysis (RG) to sort the errors, just probabilistic types to filter the rules (PT), and both optimizations at the same time (RG $\land$ PT).
+We test the following conditions; just rule graph analysis (RG) to sort the errors, just probabilistic types to filter the rules (PT), and both optimizations at the same time (RG $\land$ PT).
 For each entry we list X/Y, where X is the rank of the known true positive, and Y is the total number of errors found on that file.

### 2017-01-25 CAV17/secs/trans.tex
total rewrite of ptypes

@@
 Taking the configuration \ref{lst:file1.cnf}, we can assume {\tt foo} is a Boolean type by the grammar of MySQL,
-  but the keyword {\tt bar} could either be a integer type or a Boolean type.
-Let us assume that there is a rule stating that the Boolean keywords should have the same values ($eq(\texttt{foo},\texttt{bar})$).
-Then there are two potential situations; in the first case where {\tt bar}$::int$, we do not learn the above rule, but in the second case where {\tt bar}$::bool$, the rule is valid.
-To resolve this ambiguity, instead of immediately assigning one type to a value, the translator assigns a distribution of types to a value based on examples from the learning set.
+  but the keyword {\tt bar} could many types.
+If we choose the type on the first example it will be a integer type, if we choose a type that fits all examples it will be a string, or we might somehow select the Boolean type.
+Let us assume that there is a critical rule we must learn that the Boolean keywords should have the same values, $eq(\texttt{foo},\texttt{bar})$.
+If we take {\tt bar}$::int$, we do not learn the above rule, nor do we learn this rule with {\tt bar}$::string$ - only with {\tt bar}$::bool$ is the rule is valid.
+To resolve this ambiguity, and choose the best type, the translator assigns a distribution of types to a keyword based on examples from the training set (denoted \trainingSet).
 
@@
 Formally, we define a space of probabilistic types $\tilde{\mathcal{T}}$, where $\ptype \in \tilde{\mathcal{T}}$ has a form $\ptype=\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$.
-Every keyword $k\in\keys$ has a probabilistic type, expressed $k:\ptype$.
-The count for $(\tau_i,c_i) \in \ptype$ is incremented each time a new example value that matches to type $\tau_i$ is encountered for a particular key, using the update notation $\update$.
-We also denote the set of key-value pairs with $C$ and a keyword value pair that exists in some configuration file as $(k,v) \in C$.
+Every keyword $k \in \keys$ has a probabilistic type, expressed $k:\ptype$, as opposed to the basic type notation $k::\tau$.
+The count for $(\tau_i,c_i) \in \ptype$ should be equal to the number of times a key in \trainingSet has a potential match to type $\tau_i$.
+%We also denote the set of key-value pairs with $C$ and a keyword value pair that exists in some configuration file as $(k,v) \in C$.
 
-Fig.~\ref{fig:ptypes} provides a fragment of a calculus for type judgments for deriving Boolean equality rules with probabilistic types.
-When there is no evidence for a type $\tau$ we call this the empty type. 
-Initially, all keywords are set to the empty set ({\scriptsize EMPTY}).
-In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to a basic type when the $\ptype$ satisfies the predicate $p_{bool}$, \ie\ the type has enough evidence.
+Fig.~\ref{fig:ptypes} provides a calculus for type judgments for deriving equality rules with probabilistic types.
+We use the notation $\ptype[\tau=N]$ to create a probabilistic type with the count of $N$ for $\tau$ in {\scriptsize PTYPE}.
+This rule simply counts the regex matches for each key value pair.
+In the {\scriptsize BOOL} judgment, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to the basic type $bool$ when the $\ptype$ satisfies the predicate $p_{bool}$, \ie\ the probabilistic type has enough evidence.
 The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
@@
 \hspace{-1cm} %no idea why, but this is better than \centering here
-\inferrule* [Right=Empty]
-{\\}
-{k:[\ast = 0]}
-\and
-\inferrule* [Right=bool\_int]
-{(k,v) \in C \\ v \in \{0,1\} \\ k:\ptype}
-{k:\ptype\update[int\pluseq 1,bool\pluseq 1]}
-\and
-\inferrule* [Right=bool]
-{(k,v) \in C \\ v \in \{ON,OFF\} \\ k:\ptype}
-{k:\ptype\update[bool\pluseq 1]}
-\\
-\and
-\inferrule* [Right=int\_resolve]
+\inferrule* [Right=ptype]
+{c_{int} = |\{\forall C \in \trainingSet.\ \forall (k,v) \in C.\ v \in \mathbb{Z}\}| \\ c_{bool} = |\{\forall C \in \trainingSet.\ \forall (k,v) \in C.\ v \in \{0,1,ON,OFF\}\}| }
+{k : \ptype[int = c_{int}, bool = c_{bool}]}
+\and\\
+\inferrule* [Right=int]
 {k:\ptype \\ p_{int}(\ptype)}
@@
 \and
-\inferrule* [Right=bool\_resolve]
+\inferrule* [Right=bool]
 {k:\ptype \\ p_{bool}(\ptype)}
 {k :: bool}
-\\
 \and
 \inferrule* [Right=eq\_rule]
-{k_1 :: \tau \\ k_2 :: \tau \\ \tau \in \mathcal{T}}
+{k_1 :: \tau \\ k_2 :: \tau}
 {eq(k_1,k_2) :: Rule}
@@
 
-In order to define predicates, we use the notation $|\tau_i\ptype|$ to select $c_i$ from a $\ptype \in \tilde{\mathcal{T}}$, 
-  and the symbol $*$ as a wildcard selector for all basic types in a $\ptype$.
-As an example, we can set the predicate $p_{bool}(\ptype)= |bool\ptype| \geq 3 \land |\ast\ptype| \leq 1$.
+In order to define predicates, we use the notation $|\tau_i\ptype|$ to select $c_i$ from a $\ptype \in \tilde{\mathcal{T}}$.
+As an example, we can set the predicate $p_{bool}(\ptype)= |bool\ptype| \geq 3 \land |int\ptype| \leq 1$,
 Then taking these type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
-The result is the probabilistic type \texttt{bar}$:[bool=3,int=1]$, which is then resolved to \texttt{bar}$::bool$.
+The resultant probabilistic type \texttt{bar}$:[bool=3,int=1]$ is then resolved to \texttt{bar}$::bool$.
 
-A user may pick predicates for probabilistic type resolution that result in overlapping inference rules
-For example, if a user picks $p_{int}(\ptype)= |int\ptype| \geq 1$, then {\scriptsize INT\_RESOLVE} overlaps with {\scriptsize BOOL\_RESOLVE}.
-This not a not simply a subtyping relation, as the predicates over the counts may not be strictly overlapping.
-We simply allow the double colon (::) to type a single keyword in multiple ways.
-Because the only typing judgments on a basic type are terminal, {\scriptsize EQ\_RULE}, there is no problem with ambiguity as we would have in a traditional lambda calculus that included function application.
-
-In the case that there is not enough evidence to resolve a probabilistic type to a basic type, no type-dependent rules may be learned over that keyword.
-However, we are still able to learn rules such as {\scriptsize ORDER}, which do not require any resolved type.
+A user may pick predicates for probabilistic type resolution that result in overlapping inference rules.
+For example, if a user picks $p_{int}(\ptype)= |int\ptype| \geq 1$, then {\scriptsize INT} overlaps with {\scriptsize BOOL}.
+To resolve the ambiguity in this case we must add a new rule {\scriptsize INTBOOL} that introduces a new type $intbool$.
+This type is only a place holder to be used in the additional subtyping relations $intbool <: int$ and $intbool <: bool$.
+These subtype relations allow the $intbool$ to take the place of either $int$ or $bool$ when determining if two keyswords may be compared in the {\scriptsize EQ\_RULE}.
 
@@
 \hspace{-0.8cm} %no idea why, but this is better than \centering here
+\inferrule* [Right=intbool]
+{k:\ptype \\ p_{bool}(\ptype) \\ p_{int}(\ptype)}
+{k :: intbool}
 \and
@@
 \end{mathpar}
+
+In the case that there is not enough evidence to resolve a probabilistic type to a basic type, no type-dependent rules may be learned over that keyword.
+However, we are still able to learn rules such as {\scriptsize ORDER}, which do not require any resolved type.

### 2017-01-25 CAV17/secs/eval.tex
autocommit

@@
 We report the number of rules learned from the training set and number of errors detected in the test set in Table~\ref{table:learning}.
+One interesting note is that without probabilistic types we learned 327 fine grained rules and detected 1367 errors.
+By introducing probabilistic types, we remove 114 rules and 1023 false positives.
+We can be guaranteed these are all false positives since there cannot be a rule of type $size*size=size$ because of the semantic interpretation of the $size$ units.
+
 We also provide the support and confidence thresholds, $t_s, t_c$, used in this evaluation.
@@
 For each entry we list X/Y, where X is the rank of the known true positive, and Y is the total number of errors found on that file.
-%Here we also compare the effect of probabilistic types - without probablitic types we learned 327 fin grainedrules and 1367 detections
 
@@
 
-\begin{table}[h]
+\begin{table}[h!]
 \centering

### 2017-01-25 CAV17/secs/intro.tex
autocommit

@@
 
-We have implemented a \app prototype, and evaluated it based on
-real-world datasets. In our verification experiments, 
+We have implemented a tool, \app, and evaluated it on almost 1000 real-world configuration files from Github.
+We demonstrate that we are able to detect known errors, based on StackOverflow posts, in this data set.
+Furthermore, we find compelling evidence that out optimizations are effective, for example using probabilistic types removes 1023 false positives errors reports to reduce the total error reports to 324.
+The rule graph analysis drastically improves the ranking of importance of the error reports, which allows users to more quickly fix the most critical misconfigurations.
+Additionally, \app scales linearly, whereas a previous tool~\cite{santolucitoCAV} showed exponential slow downs on the same benchmark set.
+
+\markk{see above}
+
+datasets. In our verification experiments, 
 we first use a public configuration dataset~\cite{configdataset}, which

### 2017-01-25 CAV17/secs/intro.tex
stuff

@@
 
-The systems research community has recognized this as an important
+In this paper we propose
+a framework for automated verification of configuration files: we are analyzing 
+files and proactively reporting potential errors, without waiting for them to happen. We developed a tool, called \app, and tested it on 
+almost a thousand file from Github. The systems research community has recognized this as an important
 problem~\cite{xu16early}. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration 
@@
 error -- they are still not on a level of
-automatic verification tools used for regular program 
+automated verification tools used for regular program 
 verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
-detect errors without executing the code. In this paper we propose
-a framework for automated verification of configuration files: we are analyzing 
-files and proactively reporting potential errors, without waiting for them to happen. We developed a tool, called \app, and tested it on 
-almost a thousand file from Github.
+detect errors without executing the code.
 
@@
 
-\ruzica{mark, please put here summary of evaluation resuls}
-
 We have implemented a tool, \app, and evaluated it on almost 1000 real-world configuration files from Github.
@@
 Additionally, \app scales linearly, whereas a previous tool~\cite{santolucitoCAV} showed exponential slow downs on the same benchmark set.
-
-\markk{see above}
-
-datasets. In our verification experiments, 
-we first use a public configuration dataset~\cite{configdataset}, which
-contains 261 incorrect MySQL configuration files, as our
-training set. We then use \app to learn rules from this training set
-and refine these rules. Finally, we check sophisticated 
-errors of real configuration files crawled from Github,
-and detect many errors in these widely-used configuration files.
 

### 2017-01-25 CAV17/secs/concl.tex
cav17: stuff

@@
 of configuration files into an intermediate representation,
-and then uses a learner module to derive rules.
-\app finally uses post analysis module to refine these learned
+and then uses a learner module that employs
+the association rule learning algorithm to derive rules.
+\app finally uses rule graph analysis module to refine these learned
 rules, enabling users to verify the configuration files of

### 2017-01-25 CAV17/secs/eval.tex
cav17: stuff

@@
 
-We record the histogram of errors across the test set in Fig.~\ref{fig:histo}.
+We record the histogram of errors across the test set in Figure~\ref{fig:histo}.
 This is intuitively an expected result from randomly sampling Github - most repositories will have few errors, with an increasingly small number of repositories having many errors.
@@
 While we can run a program to determine the effect a specification has on the success of compiling/running the program, no such test exists for configuration files.
-Because configurations are dependent on the rest of the system (\ie the available hardware, the network speed, and the usage patterns), we cannot simulate the all conditions to determine if a reported error will cause system failure.
+Because configurations are dependent on the rest of the system (\ie, the available hardware, the network speed, and the usage patterns), we cannot simulate the all conditions to determine if a reported error will cause system failure.
 As evidenced by Example~\ref{ex:fine}, some misconfigurations will only cause greater than expected performance degradation, and only under particular traffic loads.

### 2017-01-25 CAV17/secs/intro.tex
stuff

@@
 
+The errors found can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
+Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging 
+techniques~\cite{Zeller:2005:WPF:1077048} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.
+
 There have been several prior efforts that attempt to verify 
@@
 existing tools.  \app implements a learning
-algorithm inspired by {\em rule association
+algorithm inspired by {\em association rule
 learning}~\cite{agrawal1993mining}. It analyzes a large training set of configuration  files~\cite{configdataset}. Those are real-world reported misconfigurations. A file in the training set might 
@@
 
-We have implemented a tool, \app, and evaluated it on almost 1000 real-world configuration files from Github.
-We demonstrate that we are able to detect known errors, based on StackOverflow posts, in this data set.
-Furthermore, we find compelling evidence that out optimizations are effective, for example using probabilistic types removes 1023 false positives errors reports to reduce the total error reports to 324.
-The rule graph analysis drastically improves the ranking of importance of the error reports, which allows users to more quickly fix the most critical misconfigurations.
-Additionally, \app scales linearly, whereas a previous tool~\cite{santolucitoCAV} showed exponential slow downs on the same benchmark set.
+We have implemented a tool, \app, and evaluated it on almost 1000 real-
+world configuration files from Github.
+We demonstrate that we are able to detect known errors, based on 
+StackOverflow posts, in this data set.
+Furthermore, we find compelling evidence that out optimizations are 
+effective, for example using probabilistic types removes 1023 false 
+positives errors reports to reduce the total error reports to 324.
+The rule graph analysis drastically improves the ranking of importance of 
+the error reports, which allows users to more quickly fix the most 
+critical misconfigurations.
+Additionally, \app scales linearly, whereas 
+a previous tool~\cite{santolucitoCAV} showed exponential slow downs on 
+the same benchmark set.
 
-In summary, we make the following contributions.
+In summary, we make the following contributions:
+\begin{itemize}
+\item We propose the automated configuration verification
+framework, \app, that can learn a language model from a sample
+dataset, and then use this language model to verify 
+configuration files of interest.
+\item We describing the logical foundation of using association rule learning to build a probabilistic specification for configuration files. 
+\item We analyze the learned model to further refine the generated specification and we empirically show the usefulness of this approach.
+\item We implement a \app prototype and evaluate it by
+conducting comprehensive experiments on real-world dataset.
+
+\end{itemize}
 
 \com{
-
-\markk{maybe we can use these lines in the intro somewhere.}
-These errors can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
-Since these runtime errors may only be triggered after some time in a deployment environment, the standard delta-debugging technique~\cite{x} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.
-
-Our main contributions are as follows:
-
-\begin{enumerate}
 
@@
 
-\item We implement a \app prototype and evaluate it by
-conducting comprehensive experiments on real-world dataset.
-
 \end{enumerate}

### 2017-01-25 CAV17/secs/intro.tex
cav17: intro

@@
 a framework for automated verification of configuration files: we are analyzing 
-files and proactively reporting potential errors, without waiting for them to happen. We developed a tool, called \app, and tested it on 
-almost a thousand file from Github. The systems research community has recognized this as an important
-problem~\cite{xu16early}. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration 
+configuration files of interest and proactively reporting potential errors, without waiting for them to happen. We developed a tool, called \app, 
+and evaluated it on 
+almost a thousand configuration files from Github. The systems research community has recognized this as an important
+problem~\cite{xu16early}. While many efforts have been proposed to
+check, troubleshoot, and diagnose configuration 
 errors~\cite{attariyan10automating,
 su07autobash, whitaker04configuration},
-those tools mainly try to understand {\emph{what}} caused the 
-error -- they are still not on a level of
+those tools heavily rely on analyzing the source code of 
+the target systems and need to run these systems
+multiple times to understand where is the error---\ie,
+they are still not on a level of
 automated verification tools used for regular program 
@@
 specifications. Instead, we learn specification from 
-a large sample of 
+a large training set of 
 configuration files~\cite{configdataset}. The first step is to 
@@
 We then apply the learning process and we learn an abundant set of rules 
-specifying various properties that hold on the given sample. The rules, in general, 
+specifying various properties that hold on the given training set. The rules, in general, 
 specify which properties keywords in configuration files need to satisfy.
 The learning process is language-agnostic and works for any kind 
-of configuration files,  but all of the files in the sample need to be of 
+of configuration files,  but all of the files in the training set need to be of 
 the same kind (such as MySQL or HTTPD configuration files).
@@
 
-There have been several prior efforts that attempt to verify 
+To our knowledge, there have been several prior efforts that attempt to verify 
 configuration files~\cite{santolucitoCAV, xu16early,
@@
 \item We propose the automated configuration verification
-framework, \app, that can learn a language model from a sample
-dataset, and then use this language model to verify 
+framework, \app, that can learn a language model from a training set
+of configuration files, and then use this language model to verify 
 configuration files of interest.
-\item We describing the logical foundation of using association rule learning to build a probabilistic specification for configuration files. 
+\item We describe the logical foundation of using association rule learning to build a probabilistic specification for configuration files. 
 \item We analyze the learned model to further refine the generated specification and we empirically show the usefulness of this approach.

### 2017-01-25 CAV17/secs/intro.tex
cav17: title and intro

@@
 \item We propose the automated configuration verification
-framework, \app, that can learn a language model from a training set
-of configuration files, and then use this language model to verify 
+framework, \app, that can learn specifications (rules) from a training set
+of configuration files, and then use the specifications to verify 
 configuration files of interest.
 \item We describe the logical foundation of using association rule learning to build a probabilistic specification for configuration files. 
-\item We analyze the learned model to further refine the generated specification and we empirically show the usefulness of this approach.
+\item We analyze the learned rules to further refine the generated specification and we empirically show the usefulness of this approach.
 \item We implement a \app prototype and evaluate it by
-conducting comprehensive experiments on real-world dataset.
+detecting sophisticated configuration errors 
+from real-world dataset.
 

### 2017-01-25 CAV17/secs/trans.tex
cav17: stuff
fix typos in translaor

@@
 The translator takes as input a training set of configuration files and transforms it into a typed and well-structured intermediate representation.
-The translator can be seen a parser used to generate an intermediate representation for the learner module (cf. Sec.~\ref{sec-learn}).
+The translator can be seen as a parser used to generate an intermediate representation for the learner module (cf. Sec.~\ref{sec-learn}).
 Translating or parsing is system dependent since each configuration language (MySQL, Apache, PHP) uses a different grammar.
@@
 Taking the configuration \ref{lst:file1.cnf}, we can assume {\tt foo} is a Boolean type by the grammar of MySQL,
-  but the keyword {\tt bar} could many types.
-If we choose the type on the first example it will be a integer type, if we choose a type that fits all examples it will be a string, or we might somehow select the Boolean type.
+  but the keyword {\tt bar} could be many types.
+If we choose the type based on the first example, {\tt bar} will be a integer type.
+If we choose a type that fits all examples, {\tt bar} will be a string.
+However the correct classification needed is a Boolean type.
 Let us assume that there is a critical rule we must learn that the Boolean keywords should have the same values, $eq(\texttt{foo},\texttt{bar})$.
 If we take {\tt bar}$::int$, we do not learn the above rule, nor do we learn this rule with {\tt bar}$::string$ - only with {\tt bar}$::bool$ is the rule is valid.
-To resolve this ambiguity, and choose the best type, the translator assigns a distribution of types to a keyword based on examples from the training set (denoted \trainingSet).
+To resolve this ambiguity, and choose the best type, the translator assigns a distribution of types to a keyword based on examples from the training set of configuration files (denoted $\trainingSet=\{C\}$).
 
 A probabilistic type is a set of counts over a set $\mathcal{T}$ of basic types.
-Formally, we define a space of probabilistic types $\tilde{\mathcal{T}}$, where $\ptype \in \tilde{\mathcal{T}}$ has a form $\ptype=\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$.
-Every keyword $k \in \keys$ has a probabilistic type, expressed $k:\ptype$, as opposed to the basic type notation $k::\tau$.
+Formally, we define a space of probabilistic types $\tilde{\mathcal{T}}$, where $\ptype \in \tilde{\mathcal{T}}$ has the form $\ptype=\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$.
+Figure~\ref{fig:ptypes} provides a calculus for probabilistic types over an example subset of basic types.
+This allows us to give a clear definition of the set of possible (\ie well-typed) equality rules.
+
+Every unique keyword $k \in \trainingSet$ has a probabilistic type, expressed $k:\ptype$, as opposed to the basic type notation $k::\tau$.
 The count for $(\tau_i,c_i) \in \ptype$ should be equal to the number of times a key in \trainingSet has a potential match to type $\tau_i$.
+The judgment {\scriptsize PTYPE} counts, over all files $C \in \trainingSet$, the times the value of a key matches a user defined set of acceptable values for each type $\tau_i \in \ptype$.
+We use the notation $\ptype[\tau_i=N]$ to create a probabilistic type with the count of $N$ for $\tau_i \in \ptype$.
 %We also denote the set of key-value pairs with $C$ and a keyword value pair that exists in some configuration file as $(k,v) \in C$.
 
-Fig.~\ref{fig:ptypes} provides a calculus for type judgments for deriving equality rules with probabilistic types.
-We use the notation $\ptype[\tau=N]$ to create a probabilistic type with the count of $N$ for $\tau$ in {\scriptsize PTYPE}.
-This rule simply counts the regex matches for each key value pair.
-In the {\scriptsize BOOL} judgment, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to the basic type $bool$ when the $\ptype$ satisfies the predicate $p_{bool}$, \ie\ the probabilistic type has enough evidence.
-The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
+In the {\scriptsize BOOL} judgment, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to the basic type $bool$ when the $\ptype$ satisfies the resolution predicate $p_{bool}$, \ie\ the probabilistic type has sufficient evidence.
+The definition of sufficient evidence must be empirically determined by the user depending on the quality of the training set.
 
@@
 
-In order to define predicates, we use the notation $|\tau_i\ptype|$ to select $c_i$ from a $\ptype \in \tilde{\mathcal{T}}$.
-As an example, we can set the predicate $p_{bool}(\ptype)= |bool\ptype| \geq 3 \land |int\ptype| \leq 1$,
-Then taking these type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
-The resultant probabilistic type \texttt{bar}$:[bool=3,int=1]$ is then resolved to \texttt{bar}$::bool$.
+In order to define resolution predicates, we use the notation $|\tau_i\ptype|$ to select $c_i$ from a $\ptype \in \tilde{\mathcal{T}}$.
+As an example, for the sample training set provided in Figure~\ref{fig:tset}, we might choose to set $p_{bool}(\ptype)= |bool\ptype| \geq 3 \land |int\ptype| \leq 1$ and $p_{int}(\ptype)= |int\ptype| \geq 3$.
+We then can run inference on that sample training set to derive a probabilistic type \texttt{bar}$:[bool=3,int=1]$.
+This is then resolved, as required in our earlier example, to \texttt{bar}$::bool$.
 
-A user may pick predicates for probabilistic type resolution that result in overlapping inference rules.
-For example, if a user picks $p_{int}(\ptype)= |int\ptype| \geq 1$, then {\scriptsize INT} overlaps with {\scriptsize BOOL}.
-To resolve the ambiguity in this case we must add a new rule {\scriptsize INTBOOL} that introduces a new type $intbool$.
-This type is only a place holder to be used in the additional subtyping relations $intbool <: int$ and $intbool <: bool$.
-These subtype relations allow the $intbool$ to take the place of either $int$ or $bool$ when determining if two keyswords may be compared in the {\scriptsize EQ\_RULE}.
+Note that a user may pick predicates for probabilistic type resolution that result in overlapping inference rules.
+For example, if a user instead picked $p_{int}(\ptype)= |int\ptype| \geq 1$, {\scriptsize INT} would overlap with {\scriptsize BOOL}.
+To resolve the ambiguity in this case, we must add a new rule {\scriptsize INTBOOL} that introduces a new, internal type $intbool$ to be created when both resolution predicates are true.
+The antecedent statement of {\scriptsize INT} must also be updated to $p_{int}(\ptype) \land \neg p_{bool}(\ptype)$, and likewise with {\scriptsize BOOL}.
+The $intbool$ type is only a placeholder to be used with the additional subtyping relations $intbool <: int$ and $intbool <: bool$
+These subtype relations allow the $intbool$ to take the place of either $int$ or $bool$ when determining if two keywords may be compared in the {\scriptsize EQ\_RULE}.
 

### 2017-01-25 CAV17/secs/intro.tex
cav17: intro

@@
 In this paper we propose
-a framework for automated verification of configuration files: we are analyzing 
-configuration files of interest and proactively reporting potential errors, without waiting for them to happen. We developed a tool, called \app, 
+a framework for automated verification of configuration files: 
+we derive specifications by learning ``raw'' configuration files 
+and proactively report potential errors in the configuration files
+of interest, without waiting for them to happen. 
+We developed a tool, called \app, 
 and evaluated it on 
@@
 the target systems and need to run these systems
-multiple times to understand where is the error---\ie,
+multiple times to understand where are the errors---\ie,
 they are still not on a level of
@@
 We believe there are two main obstacles 
-to why we cannot simply apply  the existing automatic 
-tools and techniques to verification of configuration files:
+to why we cannot simply apply the existing automatic program
+verification 
+techniques to verification of configuration files:
 1) the lack
@@
 
-To our knowledge, there have been several prior efforts that attempt to verify 
+To the best of our knowledge, there have been several prior efforts that attempt to verify 
 configuration files~\cite{santolucitoCAV, xu16early,

### 2017-01-25 CAV17/secs/learner.tex
autocommit

@@
 
-Support is the frequency that the that set of keywords in the proposed rule, $S \cup T$, have been seen in the configuration files $C$ in the training set \trainingSet.
+Support is the frequency that the set of keywords in the proposed rule, $S \cup T$, have been seen in the configuration files $C$ in the training set \trainingSet.
 %Notice support does not consider the predicate itself, only how many times the predicate had the chance to be evaluated.
-Confidence is the number of times the rule predicate has held true over the given keywords.
+Confidence is the percentage of times the rule predicate has held true over the given keywords.
 In the learning process, each class of rule is manually assigned a support and confidence threshold, $t_s$ and $t_c$ respectively, below which a rule will be rejected for lack of evidence.

### 2017-01-25 CAV17/secs/intro.tex

@@
 \item We propose the automated configuration verification
-framework, \app, that can learn specifications (rules) from a training set
+framework, \app, that can learn specifications from a training set
 of configuration files, and then use the specifications to verify 

### 2017-01-25 CAV17/secs/abs.tex
stuff

--- 2017-01-24 CAV17/secs/abs.tex
@@
 System failures resulting from configuration errors 
-are major reasons for compromised reliability of today's software
-systems. Although a lot of program verification techniques 
-have been proposed, verifying configuration files is still 
-an open problem,
+are one of the major reasons for compromised reliability of today's software
+systems. Although many techniques have been proposed for a 
+configuration error
+detection, these approaches mainly can be applied after an error has occurred. Verifying configuration files is, nevertheless, 
+a challenging problem,
 because 1) software configurations are typically written in
@@
 verification is challenging in practice.
-
 This paper presents \app, the first automatic verification framework for
 general software configurations.
-\app verifies a target configuration file $F$ through three steps.
+Our framework works as follows: in the pre-processing stage, we first automatically derive a specification.
+Once we have a specification, we check if a given configuration file adheres to that specification.
+The process of learning specification works through three steps.
 First, \app parses a training set of configuration 
-files (not necessarily correct) belonging to the same system as $F$,
-translating these files to a
+files (not necessarily all correct) into a
 well-structured and probabilistically-typed 
 intermediate representation.
-Second, \app derives configuration rules by learning
-these intermediate representations.
+Second, based on the association rule
+learning algorithm \app learns rules from 
+these intermediate representations. These rules are 
+establishing relationships between the keywords appearing in the files. 
 Finally, \app employs rule graph analysis to refine the 
-resulting rules, and uses the refined rules to verify $F$.
-
-\app is capable of detecting various configuration errors,
+resulting rules. \app is capable of detecting various configuration errors,
 including ordering errors, integer correlation errors, type errors,
 and missing entry errors. We evaluated \app by verifying 
-public configuration files on github, and detected the above 
-configuration errors in these widely-deployed files.
+public configuration files on Github, and we show that \app can 
+detect known configuration errors in these files.
 

### 2017-01-25 CAV17/secs/abs.tex
autocommit

@@
 
-System failures resulting from configuration errors 
-are one of the major reasons for compromised reliability of today's software
-systems. Although many techniques have been proposed for a 
-configuration error
-detection, these approaches mainly can be applied after an error has occurred. Verifying configuration files is, nevertheless, 
-a challenging problem,
-because 1) software configurations are typically written in
-poorly structured and untyped ``languages'', and 
-2) specifying rules for configuration 
-verification is challenging in practice.
-This paper presents \app, the first automatic verification framework for
-general software configurations.
+System failures resulting from configuration errors are one of the major reasons for compromised reliability of today's software systems. 
+Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred. 
+Verifying configuration files is, nevertheless, a challenging problem, because 
+  1) software configurations are typically written in poorly structured and untyped ``languages'', and 
+  2) specifying rules for configuration verification is challenging in practice.
+This paper presents \app, a verification framework for general software configurations.
 Our framework works as follows: in the pre-processing stage, we first automatically derive a specification.
@@
 The process of learning specification works through three steps.
-First, \app parses a training set of configuration 
-files (not necessarily all correct) into a
-well-structured and probabilistically-typed 
-intermediate representation.
-Second, based on the association rule
-learning algorithm \app learns rules from 
-these intermediate representations. These rules are 
-establishing relationships between the keywords appearing in the files. 
-Finally, \app employs rule graph analysis to refine the 
-resulting rules. \app is capable of detecting various configuration errors,
-including ordering errors, integer correlation errors, type errors,
-and missing entry errors. We evaluated \app by verifying 
-public configuration files on Github, and we show that \app can 
-detect known configuration errors in these files.
+First, \app parses a training set of configuration files (not necessarily all correct) into a well-structured and probabilistically-typed intermediate representation.
+Second, based on the association rule learning algorithm \app learns rules from these intermediate representations. 
+These rules establish relationships between the keywords appearing in the files. 
+Finally, \app employs rule graph analysis to refine the resulting rules. 
+\app is capable of detecting various configuration errors, including ordering errors, integer correlation errors, type errors, and missing entry errors. 
+We evaluated \app by verifying public configuration files on Github, and we show that \app can detect known configuration errors in these files.
 

### 2017-01-25 CAV17/secs/concl.tex
stuff

--- 2017-01-23 CAV17/secs/concl.tex
@@
 that allows automatic verification of configuration files.
-\app employs a translator to parse a training set
-of configuration files into an intermediate representation,
-and then uses a learner module to derive rules.
-\app finally uses post analysis module to refine these learned
-rules, enabling users to verify the configuration files of
-their interest.
-Our evaluation based on a real-world misconfiguration
-dataset~\cite{configdataset} shows that \app is able to
-correctly detect configuration errors
+The main problem for verification of configuration files is their lack
+of specification, so they are not a traditional target area
+for formal methods.
+Inspired by the association rule learning algorithm, \app learns 
+a set of rules which describe properties and relations between keywords appearing in configuration files. These rules corresponding to the specification.
+Our evaluation, based on a real-world  examples, shows that \app is able to
+correctly detect and report configuration errors
 including ordering, missing entry, integer correlation

### 2017-03-21 CAV17/secs/related.tex

@@
 
-\com{
-\para{Misconfiguration tolerance}
-There have been several efforts proposed to test whether systems are 
-tolerant to misconfigurations~\cite{xu13do}. 
-SPEX~\cite{xu13do}, for example, takes 
-a white-box testing approach to automatically
-extract configuration parameter constraints from source code and generates 
-misconfigurations to test whether systems can tolerate potential
-configuration errors.
-
-Making systems gracefully handle misconfigurations and eliminating
+\com{Making systems gracefully handle misconfigurations and eliminating
 configuration errors are two orthogonal directions.

### 2017-04-15 PLDI/secs/abs.tex
fix words

--- 2017-01-25 CAV17/secs/abs.tex
@@
-\begin{abstract}
-
-System failures resulting from configuration errors are one of the major reasons for compromised reliability of today's software systems. 
-Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred. 
-Verifying configuration files is, nevertheless, a challenging problem, because 
+System failures resulting from configuration errors are one of the major reasons for the compromised reliability of today's software systems. 
+Although many techniques have been proposed for configuration error detection, these approaches can generally only be applied after an error has occurred. 
+Proactively verifying configuration files is a challenging problem, because 
   1) software configurations are typically written in poorly structured and untyped ``languages'', and 
@@
 Once we have a specification, we check if a given configuration file adheres to that specification.
-The process of learning specification works through three steps.
+The process of learning a specification works through three steps.
 First, \app parses a training set of configuration files (not necessarily all correct) into a well-structured and probabilistically-typed intermediate representation.
-Second, based on the association rule learning algorithm \app learns rules from these intermediate representations. 
+Second, based on the association rule learning algorithm, \app learns rules from these intermediate representations. 
 These rules establish relationships between the keywords appearing in the files. 
@@
 We evaluated \app by verifying public configuration files on Github, and we show that \app can detect known configuration errors in these files.
-
-\end{abstract}

### 2017-04-15 PLDI/secs/arch.tex
fix words

--- 2017-01-25 CAV17/secs/arch.tex
@@
 The learner converts the intermediate representation from the translator to a set of rules.
-It employs variation on the {\em rule association 
+It employs variation on the {\em association rule 
 algorithm}~\cite{agrawal1993mining}, to generate this list of rules, which describe properties of a correct configuration file. 
@@
 
-\para{Post Analysis}
+\para{Rule Graph Analysis}
 Finally, the logically structured representation of learned rules allows for a further \textit{rule graph analysis}.
-We introduce the concept of a rule graph that can be built from the output of the modified association rule learning algorithm.
-We analyze the properties of this graph to construct an ordering of rules by their importance, 
+The purpose of this module is to refine the learned rules.
+To this end, we introduce the concept of a rule graph that can be built from the output of the modified association rule learning algorithm.
+We analyze the properties of this graph to construct a ranking of rules by their importance, 
   as well as to produce a measure of complexity for any configuration of the target system.

### 2017-04-15 PLDI/secs/intro.tex
fix words

--- 2017-01-25 CAV17/secs/intro.tex
@@
 
-\item We propose the first automatic configuration verification
+\item We propose a configuration verification
 framework, \app, that can learn a language model from a sample

### 2017-04-15 PLDI/secs/motiv.tex
fix words

--- 2017-01-25 CAV17/secs/motiv.tex
@@
   thread_concurrency            = 8
-
   key_buffer_size               = 4G
   max_heap_table_size           = 128M
-
   join_buffer_size              = 32M
@@
 FINE GRAINED ERROR: Expected 
-  "max_connections" * "sort_buffer_size" >= "key_buffer_size"
+  "max_connections" * "sort_buffer_size" > "key_buffer_size"
 \end{lstlisting}

### 2017-04-15 PLDI/secs/postanal.tex
fix words

--- 2017-01-25 CAV17/secs/postanal.tex
@@
 
-\section{rule graph Analysis}
+\section{Rule Graph Analysis}
 \label{sec-post}
@@
 parameters where rules learned are more likely to be governed by 
-tehchnical necessity, rather than industry convention. As such, errors
+technical necessity, rather than industry convention. As such, errors
 reported involving low-degree keywords are more likely to be errors

### 2017-04-15 PLDI/secs/related.tex
fix words

--- 2017-03-21 CAV17/secs/related.tex
@@
 failures occur, which leads to prolonged recovery time.
-
-\com{Making systems gracefully handle misconfigurations and eliminating
-configuration errors are two orthogonal directions.
-The former helps improve the robustness of systems and make 
-diagnosis easier. This is especially important for 
-software that will be widely distributed to end users.
-Our work belongs to the latter case, which is used to 
-prevent configuration errors before system outages.}

### 2017-04-15 PLDI/secs/trans.tex
fix words

--- 2017-01-25 CAV17/secs/trans.tex
@@
 In order to define resolution predicates, we use the notation $|\tau_i\ptype|$ to select $c_i$ from a $\ptype \in \tilde{\mathcal{T}}$.
-As an example, for the sample training set provided in Figure~\ref{fig:tset}, we might choose to set $p_{bool}(\ptype)= |bool\ptype| \geq 3 \land |int\ptype| \leq 1$ and $p_{int}(\ptype)= |int\ptype| \geq 3$.
+As an example, for the sample training set provided in Figure~\ref{fig:tset}, we might choose to set $p_{bool}(\ptype)= |bool_{\ptype}| \geq 3 \land |int_{\ptype}| \leq 1$ and $p_{int}(\ptype)= |int\ptype| \geq 3$.
 We then can run inference on that sample training set to derive a probabilistic type \texttt{bar}$:[bool=3,int=1]$.
@@
 For example, if a user instead picked $p_{int}(\ptype)= |int\ptype| \geq 1$, {\scriptsize INT} would overlap with {\scriptsize BOOL}.
+This means that types are not unique in this system, i.e. $k:\ptype \land k:\ptype' \centernot\implies \ptype = \ptype'$.
+
 To resolve the ambiguity in this case, we must add a new rule {\scriptsize INTBOOL} that introduces a new, internal type $intbool$ to be created when both resolution predicates are true.

### 2017-04-15 code2/src/Learners/Common.hs
fixzed result for table

@@ -61,7 +61,7 @@ units v = if
   | all C.isNumber (T.unpack $ T.init v) -> Just $ scale $ T.last v
   | otherwise -> Nothing
 scale c = if
-  | C.toUpper c == 'M' -> 1
+  | C.toUpper c == 'M' -> 1 
   | C.toUpper c == 'K' -> 1000
   | C.toUpper c == 'G' -> 1000000
   | otherwise -> 1 
@@ -96,10 +96,10 @@ sameConfigModule (ir1,ir2) = let
 
 
 --TYPES
-validAsString v = (((T.length $ T.takeWhile C.isAlpha v) > 1) || (T.length v>=3 && T.head v == '"' && T.last v == '"')) || mysqlvar v
+validAsString v = (((T.length $ T.takeWhile C.isAlpha v) > 1) || (T.length v>=2 && T.head v == '"' && T.last v == '"')) || mysqlvar v
 validAsPath v  = ((T.isInfixOf "/" v) || (T.isInfixOf "." v)) || mysqlvar v
-validAsBool v = (v == "") || mysqlvar v--flag keywords have no values 
-validAsInt v = ((all C.isNumber $T.unpack v) && (T.length v>0)) || mysqlvar v
+validAsBool v = (any (==v) ["","on","off","ON","OFF","0","1"]) || mysqlvar v--flag keywords have no values 
+validAsInt v = ((all C.isNumber $T.unpack $T.filter (/='.') v)&& (T.length v>0)) && (T.length v <=1+(T.length $ T.filter (/='.') v))|| mysqlvar v
 validAsSize v = ((or $ map (\x-> T.isSuffixOf x v) ["G","g","M","m","K","k"]) &&
                  (T.length $ T.takeWhile C.isNumber v) == (T.length v -1) ) || mysqlvar v
 --a var can have any type

### 2017-04-15 code2/src/Learners/FineGrained.hs

@@ -57,9 +57,9 @@ instance Learnable R.FineGrained Formula where
     xs = ["dir","socket","port"]
     tris = triples $ filter (\ir -> not $ any (\k -> T.isInfixOf k (keyword ir)) xs) rs
     -- TODO should use learning result from TypeErr module
-    rs' = filter (\(ir1,ir2,ir3)-> ((validAsSize $ value ir1) `B.xor` (validAsSize $ value ir2) && (validAsSize $ value ir3)) ||
+    wellTypedTris = filter (\(ir1,ir2,ir3)-> ((validAsSize $ value ir1) `B.xor` (validAsSize $ value ir2) && (validAsSize $ value ir3)) ||
                                     all (validAsInt.value) [ir1,ir2,ir3]) tris
-    eqs = map toFineGrained rs' --tris
+    eqs = map toFineGrained (if Settings.pROBTYPES then wellTypedTris else tris)
    in
     M.fromList $ eqs
 

### 2017-04-15 code2/src/Learners/IntRel.hs

@@ -57,7 +57,8 @@ instance Learnable R.IntRel Formula where
   toError ir fname ((IntRel k1 k2),rd) = Error{
      errLocs = map (\x->(fname, x)) [k1,k2]
     ,errIdent = INTREL
-    ,errMsg = "INTEGER RELATION ERROR: Expected "++(show k1)++(show rd)++(show k2)++" \n Found values: "++(show $ filter (\x->keyword x==k1 || keyword x==k2) ir)
+    ,errMsg = "INTEGER RELATION ERROR: Expected "++(show k1)++(show rd)++(show k2)++" \n Found values: "
+              ++(show $ map (\x-> (T.unpack$ keyword x)++"="++(T.unpack$ value x)) $ filter (\x->keyword x==k1 || keyword x==k2) ir)
     ,errSupport = gt rd + lt rd + eq rd
     }
 

### 2017-04-15 code2/src/Settings.hs

@@ -13,12 +13,13 @@ module Settings where
   pROBRULES = Prob
   data ModeSetting = NonProb | Prob | Test
 
+  sortingStyle  =  RuleGraphDegree
+  data SortStyles = Support | RuleGraphDegree deriving (Eq)
+
+  pROBTYPES = True
   --cutoffs (see https://en.wikipedia.org/wiki/Association_rule_learning#Useful_Concepts)
   -- an abusive of notation here, we use slightly different interprtation of the words - same idea in the end
   --TODO unify numerical comutations to be consistent with true interpretation of support and confidence
-
-  sortingStyle  =  RuleGraphDegree
-  data SortStyles = Support | RuleGraphDegree deriving (Eq)
 
   --TODO this should really be read from training set dir
   totalFiles = 971

### 2017-04-15 PLDI/secs/concl.tex
fix typos

--- 2017-01-25 CAV17/secs/concl.tex
@@
 correctly detect and report configuration errors
-including ordering, missing entry, integer correlation
+including ordering, missing entry, integer correlation,
 and type errors.

### 2017-04-15 PLDI/secs/eval.tex
fix words
fix typos

--- 2017-01-25 CAV17/secs/eval.tex
@@
 \app is written in Haskell and is available open source at \textit{url redacted for anonymity}.
-Thanks to the Haskell's powerful type system, the implementation can easily be extended with with new rule classes or applied to different configuration languages with minimal change to the rest of the code base.
+Thanks to the Haskell's powerful type system, the implementation can easily be extended with new rule classes or applied to different configuration languages with minimal change to the rest of the code base.
 A user only needs to provide the functions for the rule interface (a typeclass in Haskell) to 1) learn relations from a single file 2) merge two sets of rules and 3) check a file given some set of rules.
@@
 total of 973 files.
-In our evaluation we focus on MySQL for comparability of results, but \app can handle any configuration language (that can be parsed to the intermediate representation from Sec.~\ref{sec:trans}).
+In our evaluation, we focus on MySQL for comparability of results, but \app can handle any configuration language (that can be parsed to the intermediate representation from Sec.~\ref{sec:trans}).
 
-We report the number of rules learned from the training set and number of errors detected in the test set in Table~\ref{table:learning}.
+We report the number of rules learned from the training set and the number of errors detected in the test set in Table~\ref{table:learning}.
 One interesting note is that without probabilistic types we learned 327 fine grained rules and detected 1367 errors.
 By introducing probabilistic types, we remove 114 rules and 1023 false positives.
-We can be guaranteed these are all false positives since there cannot be a rule of type $size*size=size$ because of the semantic interpretation of the $size$ units.
+We are guaranteed these are all false positives since there cannot be a rule of type $size*size=size$ because of the semantic interpretation of the $size$ units.
 
@@
 
-Although we cannot identify false positives, we can identify true positives by examining online forums, like StackOverflow, for record that
-particular configuration settings have caused problems on real-world systems.
+Although we cannot identify false positives, we can identify true positives by examining online forums, like StackOverflow.
+On these forums we find reports that particular configuration settings have caused problems on real-world systems.
 Furthermore, any error for which we can find evidence online is likely to be more problematic than errors that do not have an online record, 
   using the reasoning that this error has caused enough problems for people to seek help online.
-In this case, we would like \app to can sort the errors by their importance or potential severity.
+In this case, we would like \app to sort the errors by their importance or potential severity.
 To achieve this sorting we use the rule graph analysis metric described in Sec.~\ref{sec:ruleorder}.
@@
 For this table, we picked the known true positive rules, listed in the Errors column, and pick configuration files in the test set that have these errors.
-We picked 3 files for each true positive by choosing the files the most total errors to most clearly observe the effects of our optimizations.
+We picked 3 files for each true positive by choosing the files with the highest number of total reported errors in order to clearly observe the effects of our optimizations.
+Although this gives a more clear picture of the effect of our optimizations, it results in a slightly inflated false positive rate.
+
 We test the following conditions; just rule graph analysis (RG) to sort the errors, just probabilistic types to filter the rules (PT), and both optimizations at the same time (RG $\land$ PT).
-For each entry we list X/Y, where X is the rank of the known true positive, and Y is the total number of errors found on that file.
+For each entry we list X/Y, where X is the rank of the known true positive, and Y is the total number of errors found in that file.
 

### 2017-04-15 PLDI/secs/motiv.tex
fix typos

@@
 %in the configuration file.
-We call these errors as {\em fine-grained integer correlations}. 
+We call these errors {\em fine-grained integer correlations}. 
 \app can also detect simpler integer correlation: one entry's
@@
 Many system availability problems are caused by 
-assigning incorrect type of values. Consider the following  misconfiguration
+assigning incorrect values of an incorrect type to a keyword. Consider the following  misconfiguration
 file from github~\cite{typeerror}:

### 2017-04-15 PLDI/secs/related.tex
fix typos

@@
 First, ConfigC requires the configuration files in the training set must 
-be correct, which is quite impractical, because it is very difficult to
+be correct, which is impractical because it is very difficult to
 determine a correct configuration set in reality.
-Second, ConfigC can only cover less types of misconfigurations than \app. 
+Second, ConfigC covers fewer types of misconfigurations than \app. 
 Finally, the training time of ConfigC is much longer than \app.

### 2017-04-15 PLDI/secs/concl.tex
fix typos

--- 2017-01-25 CAV17/secs/concl.tex
@@
 a set of rules which describe properties and relations between keywords appearing in configuration files. These rules corresponding to the specification.
-Our evaluation, based on a real-world  examples, shows that \app is able to
+Our evaluation, based on real-world examples, shows that \app is able to
 correctly detect and report configuration errors
-including ordering, missing entry, integer correlation
+including ordering, missing entry, integer correlation,
 and type errors.

### 2017-04-15 OOPSLA17/secs/arch.tex
rename fodler

--- 2017-04-15 PLDI/secs/arch.tex
@@
 The learner converts the intermediate representation from the translator to a set of rules.
-It employs variation on the {\em association rule 
+It employs a variation on the {\em association rule 
 algorithm}~\cite{agrawal1993mining}, to generate this list of rules, which describe properties of a correct configuration file. 
@@
 The learning algorithm uses various instances of a rule interface to learn different classes of rules, such as ordering or integer relations.
-These rules are then considered to be required for any configuration files to be correct, and can be used for verification.
+These rules are then considered necessary for any correct configuration files, and can be used for verification.
 
@@
 While the metrics in used in \app are effective, they are not intended to be exhaustive.
-The information contained in the structured representation of the learned rules, 
+The information contained in the structured representation of the learned rules
   is a unique benefit of the learning algorithm, that has potential to be leveraged in many new ways.

### 2017-04-15 OOPSLA17/secs/intro.tex
rename fodler

--- 2017-04-15 PLDI/secs/intro.tex
@@
 
-In this paper we propose
+In this paper, we propose
 a framework for automated verification of configuration files: 
@@
 
-To the best of our knowledge, there have been several prior efforts that attempt to verify 
+To the best of our knowledge, there have been several prior efforts that attempt to proactively verify 
 configuration files~\cite{santolucitoCAV, xu16early,
 zhang14encore, huang15confvalley}.
-However, state-of-the-art efforts either are impractical to be used
-in reality, or can only deal with simplistic configuration errors.
-In general, these efforts fall into two categories.\begin{itemize}
+However, state-of-the-art efforts have limitations that are impractical to meet in practice.
+In general, these efforts fall into two categories with respect to their limitations.\begin{itemize}
 \item On the one hand there are tools that can detect sophisticated 
@@
 
-Our learning algorithm surmounts all of difficulties present in 
+Our learning algorithm surmounts both of these shortcomings present in 
 existing tools.  \app implements a learning
@@
 in a small percentage of files. We first translate those file into an 
-intermediary typed language. With with every type we associate 
-a set of very general interfaces. An \app's user does not
-need to provide them, they are internally associated to the types. The 
+intermediary typed language. With with every type, we associate 
+a set of very general interfaces. The user does not
+need to provide them - they are internally associated with the types. The 
 learner then instantiates those interfaces with the keywords appearing in 
@@
 annotated with the probability of correctness.  
-To ensure the learned rules are good enough,
-\app employs a further analysis to refine the learned rules.
-In general, \app builds a graph modeling the learned rules,
-and then analyzes this graph to rank the importance
-and relevance of the learned rules.
+To ensure the learned rules are correct enough,
+\app employs a graph analysis to refine the set learned rules.
+\app analyzes the rule graph to rank the importance and relevance of the learned rules.
 

### 2017-04-15 OOPSLA17/secs/learner.tex
rename fodler

--- 2017-01-25 CAV17/secs/learner.tex
@@
 The two metrics, support and confidence, are used in association rule learning, as well as other rule based machine learning techniques~\cite{han2007frequent,langley1995applications}.
-We use slightly modified definitions of of these to handle arbitrary predicates as rules.
+We use slightly modified definitions of these, stated below, to handle arbitrary predicates as rules.
 During the learning process, each rule is assigned a support and confidence to measure the amount and quality of evidence for the rule.
@@
 The integer correlation rules also use probabilistic types to prune the search space.
-To avoid learning too many false positives, we restrict this rule to either $size*int=size$, $int*size=size$, or $int*int = int$.
+To avoid learning too many false positives, we restrict this rule to either $size*int=size$, or $int*int = int$.
 Without probabilistic typing, we would also learn, for example, $size*size=size$, which is an invalid interpretation.

### 2017-04-16 OOPSLA17/secs/eval.tex
more consistent and thourough defs

--- 2017-04-15 PLDI/secs/eval.tex
@@
 \section{Implementation and Evaluation}
+\label{sec:eval}
 
@@
 One interesting note is that without probabilistic types we learned 327 fine grained rules and detected 1367 errors.
-By introducing probabilistic types, we remove 114 rules and 1023 false positives.
-We are guaranteed these are all false positives since there cannot be a rule of type $size*size=size$ because of the semantic interpretation of the $size$ units.
+By introducing probabilistic types, we remove 114 incorrect rules and thereby remove 1023 false positives.
+We are guaranteed these are all false positives since there cannot be a correct rule of relating the types $size*size$ and $size$ because of the semantic interpretation of the $size$ units.
 

### 2017-04-16 OOPSLA17/secs/learner.tex
more consistent and thourough defs

@@
 
-To learn rules over sets of configuration files, we use a generalization of \textit{association rule learning}~\cite{agrawal1993mining}, a technique that can be summarized as inductive machine learning.
-Association rule learning is a technique to learn how frequently items of a set appear together.
-For example, by examining a list of food store receipts, we would learn that when a customer buys bread and peanut butter, the set of purchased items is also likely to include jelly.
-Since configuration files have complex relations, we extend these association relationships to generalized predicates.
+To learn rules over sets of configuration files, we use a generalization of \textit{association rule learning}~\cite{agrawal1993mining}, a technique very briefly summarized as inductive machine learning.
+Association rule learning is used to learn how frequently items of a set appear together.
+For example, by examining a list of food store receipts, we might learn that when a customer buys bread and peanut butter, the set of purchased items is also likely to include jelly.
+Since configuration files have multiple complex relations, we extend these association relationships to generalized predicates.
 
-A \textit{rule}, $r$, is then an implication relationship, $r = S \implies p(S,T)$, between two possibly empty sets of keywords $S,T \subset \keys$, which we call the source and target keyword sets.
+A \textit{rule}, $r$, takes the form of an implication relationship, $r = S \in \validSet \implies T \in \validSet \land p(S,T)$, between two possibly empty sets of keywords $S,T \subset \keys$ where \validSet is the set of all valid configuration files.
+In keeping with vocabulary from association rule learning, we refer to $S$ and $T$ as the source and target keyword sets respectively.
+A rule states that if the source set of keyword appears in a valid configuration file, the target set of keywords must be present and the given predicate must hold.
+For simplicity of notation, we treat the $S,T \in \validSet$ as implicit when writing a rule.
+
+Taking the food store example, our learned rule would be $\{bread, butter\} \implies assoc(\{bread,butter\},\{jelly\})$.
 The set $\keys$ is the set of unique keys from the training set (denoted \trainingSet) and the predicate $p$ is one of the classes of configuration errors.
-Implicitly we interpret a rule to mean that if the keywords $S\cup T$ appear in a configuration file, the predicate $p$ should hold.
 The task of the learning algorithm is to transform a training set to a set of rules, weighted with \textit{support} and \textit{confidence}.
@@
 In the learning process, each class of rule is manually assigned a support and confidence threshold, $t_s$ and $t_c$ respectively, below which a rule will be rejected for lack of evidence.
-The denote the set rules that are learned and included as part of the final specification are as follows:
+We denote the set rules that are learned and included as part of the final specification are as follows:
 
@@
 Each class of error forms a rule with a predicate $p$, and additional restrictions on the sets $S, T$.
-Ordering errors have $|S|, |T| = 1$ and use the predicate $order$ to mean the keyword $S$ must come before the keyword $T$ in any configuration file.
-Missing keyword entry errors also require $|S|, |T| = 1$ and use the predicate $missing$ to mean the keyword $S$ must appear in the same file as the keyword $T$ in any configuration file.
-The type rule is a set of rules over multiple predicates, which take the
-form $S \implies \textit{isType}\ast(S)$, where $|S|=1, |T|=0$ and $\ast$ matches all the basic types (string, int, etc).
+Ordering errors require $|S|, |T| = 1$ and use the predicate $order$ to mean the keyword $S$ must come before the keyword $T$ in any configuration file.
+For example, the ordering error given in Sec.~\ref{sec:motiv} is expressed:
+%
+\begin{equation*}
+\{\texttt{innodb\_data\_home\_dir}\} \in \validSet \implies ord(\{\texttt{innoddb\_data\_home\_dir}\},\{\texttt{innodb\_data\_file\_path}\})
+\end{equation*}
+%
+Missing keyword entry errors require $|S|, |T| = 1$ and use the predicate $missing$ to mean the keyword $T$ must appear in the same file as the keyword $S$ in any configuration file.
+The type rule is a set of rules over multiple predicates, where $|S|=1, |T|=0$.
+These type rules take the form $S \implies is\_(S)$ where $\_$ matches all the basic types (bool, int, size, etc).
 
@@
 The integer correlation rules also use probabilistic types to prune the search space.
-To avoid learning too many false positives, we restrict this rule to either $size*int=size$, or $int*int = int$.
-Without probabilistic typing, we would also learn, for example, $size*size=size$, which is an invalid interpretation.
-%TODO include exactly how many false positive we prune with types over our training set? Here or in eval?
+To avoid learning too many false positives, we restrict this rule to either $size*int=size$, or $int*int = int$, as shown in Fig.~\ref{fig:allrules}.
+Without probabilistic typing, we would also learn rules which do not have a invalid sematinc interpretation, for example a relation between three size keywords ($k1,k2,k3::size$) of the form $k1*k2>k3$.
+
+{
+\setlength{\abovecaptionskip}{-.05pt}
+\setlength{\belowcaptionskip}{-15pt}
+\begin{figure}
+\begin{mathpar}
+%\hspace{-1cm} %no idea why, but this is better than \centering here
+\inferrule* [Right=bool]
+{k1 :: bool}
+{isbool(k1) :: Rule}
+\and\quad
+\inferrule* [Right=int]
+{k1 :: int}
+{isint(k1) :: Rule}
+\and\\
+\inferrule* [Right=fine\_grain\_rule]
+{k1,k2,k3 :: int}
+{fine(k1,k2,k3) :: Rule}
+\and\quad
+\inferrule* [Right=fine\_grain\_rule]
+{k1,k3 :: size \\ k2 :: int}
+{fine(k1,k2,k3) :: Rule}
+\end{mathpar}
+\caption{An expanded set of typing judgements for valid rules}
+\label{fig:allrules}
+\end{figure}
+}
 
@@
 With the rules generated by the learner module, \app checks whether any entry in a target configuration file violates the learned rules and constraints.
-\app parses a verification target configuration file with the translator from Sec.~\ref{sec:trans}  to obtain a set of key-value pairs, $\mathcal{V}$, for that file.
-Then, the checker applies the learner from Eq.~\ref{eq:learn},
-$\textit{Learn}(\mathcal{V})$ to build the set of relations observed in the file, with the thresholds $t_s,t_c = 100\%$. 
+\app parses a single verification target configuration file with the translator from Sec.~\ref{sec:trans}  to obtain a set of key-value pairs, $\mathcal{C}$, for that file.
+Then, the checker applies the learner from Eq.~\ref{eq:learn} with $\textit{Learn}(\mathcal{C})$,
+  to build the set of relations observed in the file, with the thresholds $t_s,t_c = 100\%$. 
 The checker will then report the following set of errors:
@@
 \begin{align*}
-\textit{Errors}(\mathcal{V}) = \{ r\ |\ & S_r \cup T_r \in \mathcal{V} \ \land \\
+\textit{Errors}(\mathcal{C}) = \{ r\ |\ & S_r \cup T_r \in \mathcal{C} \ \land \\
                                & r \in \textit{Learn}(\trainingSet) \ \land \\
-                               & r \notin \textit{Learn}(\mathcal{V})
+                               & r \notin \textit{Learn}(\mathcal{C})
 \end{align*}

### 2017-04-16 OOPSLA17/secs/postanal.tex
rename fodler
more consistent and thourough defs

--- 2017-04-15 PLDI/secs/postanal.tex
@@
 described in Sec.~\ref{sec-learn}. Recall that a rule is 
-an implication relationship of the form $r = S \implies p(S,T)$.
+an implication relationship of the basic form $r = S \implies p(S,T)$.
 This data is necessary to perform the core verification task,
@@
 conditional random fields~\cite{raychev2015predicting}, these analyses require a deep knowledge of the applied techniques.
-In contrast the rule graph is a relatively simple, yet information rich, representation of the learned model.
+In contrast, the rule graph is a relatively simple, yet information rich, representation of the learned model.
 The following section provides a precise definition of the rule graph
@@
 
-The results from ranking errors in this way are presented later in
-the paper.
+The results from ranking errors in this way are presented in Sec.~\ref{sec:eval}.
 

### 2017-04-16 OOPSLA17/secs/related.tex
more consistent and thourough defs

--- 2017-04-15 PLDI/secs/related.tex
@@
 failures occur, which leads to prolonged recovery time.
+
+\para{Association Rule Learning}
+This approach is not only generalizes association rule learning, but also another popular learning strategy called \textit{sequential pattern mining}~\cite{seqMine}.
+Our ordering rules are similar to the rules learned in sequential pattern mining, although can restrict our ordering rules to |S|,|T|=1 since these are the most common misconfigurations we encounter in practice.
+While a major limitation to sequential pattern mining is the scalability of the problem, we escape this issue since configuration files tend to be no more than thousands of lines at a time.

### 2017-04-16 OOPSLA17/secs/trans.tex
more consistent and thourough defs

--- 2017-04-15 PLDI/secs/trans.tex
@@
 However the correct classification needed is a Boolean type.
-Let us assume that there is a critical rule we must learn that the Boolean keywords should have the same values, $eq(\texttt{foo},\texttt{bar})$.
+For illustrative purposes, let us assume that there is a critical rule we must learn where tow Boolean keywords should always have the same values, e.g. $eq(\texttt{foo},\texttt{bar})$.
 If we take {\tt bar}$::int$, we do not learn the above rule, nor do we learn this rule with {\tt bar}$::string$ - only with {\tt bar}$::bool$ is the rule is valid.
@@
 \begin{mathpar}
-\hspace{-1cm} %no idea why, but this is better than \centering here
+%\hspace{-1cm} %no idea why, but this is better than \centering here
 \inferrule* [Right=ptype]
-{c_{int} = |\{\forall C \in \trainingSet.\ \forall (k,v) \in C.\ v \in \mathbb{Z}\}| \\ c_{bool} = |\{\forall C \in \trainingSet.\ \forall (k,v) \in C.\ v \in \{0,1,ON,OFF\}\}| }
+{c_{int} = |\{\forall C \in \trainingSet.\ \forall (k,v) \in C.\ v \in \mathbb{Z}\}| \\\\ c_{bool} = |\{\forall C \in \trainingSet.\ \forall (k,v) \in C.\ v \in \{0,1,ON,OFF\}\}| }
 {k : \ptype[int = c_{int}, bool = c_{bool}]}
@@
 {k :: bool}
-\and
+\and\\
 \inferrule* [Right=eq\_rule]
@@
 {eq(k_1,k_2) :: Rule}
+\and
+\inferrule* [Right=order\_rule]
+{k1,k2 \in C \\ k1 \neq k2}
+{ord(k1,k2) :: Rule}
 \end{mathpar}
-\caption{Type judgments for a probabilistic type system with $\mathcal{T} = \{bool,int\}$ and an equality rule}
+\caption{Type judgments for a probabilistic type system with $\mathcal{T} = \{bool,int\}$ and an equality and ordering rule}
 \label{fig:ptypes}
@@
 
-To resolve the ambiguity in this case, we must add a new rule {\scriptsize INTBOOL} that introduces a new, internal type $intbool$ to be created when both resolution predicates are true.
-The antecedent statement of {\scriptsize INT} must also be updated to $p_{int}(\ptype) \land \neg p_{bool}(\ptype)$, and likewise with {\scriptsize BOOL}.
-The $intbool$ type is only a placeholder to be used with the additional subtyping relations $intbool <: int$ and $intbool <: bool$
-These subtype relations allow the $intbool$ to take the place of either $int$ or $bool$ when determining if two keywords may be compared in the {\scriptsize EQ\_RULE}.
-
-\begin{mathpar}
-\hspace{-0.8cm} %no idea why, but this is better than \centering here
-\inferrule* [Right=intbool]
-{k:\ptype \\ p_{bool}(\ptype) \\ p_{int}(\ptype)}
-{k :: intbool}
-\and
-\inferrule* [Right=order\_rule]
-{k1,k2 \in C \\ k1 \neq k2}
-{ord(k1,k2) :: Rule}
-\end{mathpar}
-
 In the case that there is not enough evidence to resolve a probabilistic type to a basic type, no type-dependent rules may be learned over that keyword.

### 2017-04-16 OOPSLA17/secs/learner.tex
fixed rule def to be entierly consistent (i hope)

@@
 
-A \textit{rule}, $r$, takes the form of an implication relationship, $r = S \in \validSet \implies T \in \validSet \land p(S,T)$, between two possibly empty sets of keywords $S,T \subset \keys$ where \validSet is the set of all valid configuration files.
-In keeping with vocabulary from association rule learning, we refer to $S$ and $T$ as the source and target keyword sets respectively.
-A rule states that if the source set of keyword appears in a valid configuration file, the target set of keywords must be present and the given predicate must hold.
-For simplicity of notation, we treat the $S,T \in \validSet$ as implicit when writing a rule.
+In traditional association rule learning, rules take the form of an implication:
+\begin{align*}
+r = \{S_0,...,S_{|S|}\} \in\ valid\ \implies \{T_0,...,T_{|T|}\} \in\ valid
+\end{align*}
+where $S$ and $T$ are source and target sets of words.
+This rule states that if the set of words $S$ appear in some $valid$ (i.e. non-rule breaking) file, the words $T$ must also appear in that file.
+We generalize this relation so that a rule, $r$, instead takes the following form:
+%
+\begin{align*}
+r = [S_0,...,S_{|S|}] \in \validSet \implies \validSet \vdash p([S_0,...,S_{|S|}],[T_0,...,T_{|T|}])
+\end{align*}
+%
+This rule relates the keywords $S_i,T_j \subseteq \keys$ for $0 \leq i \leq |S|, 0 \leq j \leq |T|$ with a predicate $p$.
+Whenever the set of keywords $S$ is present in some valid configuration file, \validSet, the predicate $p$ must hold over $S$ and $T$ given the context of \validSet.
+In keeping with vocabulary from association rule learning, we refer to $S_r$ and $T_r$ as the source and target keyword lists of rule $r$ respectively.
+A rule states that if the source list of keyword appears in a valid configuration file, the given predicate must hold between the source and target lists.
+For clarity in notation, we define all predicates to have arity 2 by separating the source and target keywords into lists of length $|S|$ and $|T|$ respectively,
+   but these can be equivalently thought of as predicates of arity $|S|+|T|$ as notated in Fig.~\ref{fig:ptypes}.
 
-Taking the food store example, our learned rule would be $\{bread, butter\} \implies assoc(\{bread,butter\},\{jelly\})$.
+Taking the food store example, our learned rule would be:
+\begin{align*}
+[bread, butter] \in\ valid \implies\ valid \vdash assoc([bread,butter],[jelly])
+\end{align*}
+%
+where the $assoc$ predicate denotes that the words must all appear in a file. 
+In this way, our formalism is more expressive than the classic association rule learning problem.
+
 The set $\keys$ is the set of unique keys from the training set (denoted \trainingSet) and the predicate $p$ is one of the classes of configuration errors.
@@
 \begin{equation*}
- \textit{confidence(r)} = \frac{|\{C \in \trainingSet \mid p_r(S_r,T_r) \subseteq C\}| } {support(r)*|\trainingSet|}
+ \textit{confidence(r)} = \frac{|\{C \in \trainingSet \mid C\ \vdash p_r(S_r,T_r) \}| } {support(r)*|\trainingSet|}
 \end{equation*}
@@
     & \textit{confidence(r)} > t_c\ \land \label{eq:learn}\\ 
-    & S,\ T \subset \keys\} \nonumber
+    & S,\ T \subseteq \keys\} \nonumber
 \end{align}
@@
 \subsection{Error Classes}
-Each class of error forms a rule with a predicate $p$, and additional restrictions on the sets $S, T$.
-Ordering errors require $|S|, |T| = 1$ and use the predicate $order$ to mean the keyword $S$ must come before the keyword $T$ in any configuration file.
+Each class of error forms a rule with a predicate $p$, and choices of $|S|$ and $|T|$, the sizes of the source and target keyword lists.
+Ordering errors require $|S|=1, |T|=1$ and use the predicate $order$ which means if both keywords $S_0,T_0$ appear in a file, $S_0$ must come before $T_0$.
 For example, the ordering error given in Sec.~\ref{sec:motiv} is expressed:
 %
-\begin{equation*}
-\{\texttt{innodb\_data\_home\_dir}\} \in \validSet \implies ord(\{\texttt{innoddb\_data\_home\_dir}\},\{\texttt{innodb\_data\_file\_path}\})
-\end{equation*}
+\begin{align*}
+[\texttt{innodb\_data\_home\_dir}&] \in \validSet \implies \\
+&\validSet \vdash order([\texttt{innoddb\_data\_home\_dir}],[\texttt{innodb\_data\_file\_path}])
+\end{align*}
 %
-Missing keyword entry errors require $|S|, |T| = 1$ and use the predicate $missing$ to mean the keyword $T$ must appear in the same file as the keyword $S$ in any configuration file.
-The type rule is a set of rules over multiple predicates, where $|S|=1, |T|=0$.
-These type rules take the form $S \implies is\_(S)$ where $\_$ matches all the basic types (bool, int, size, etc).
+Missing keyword entry errors require $|S|, |T| = 1$ and use the predicate $missing$ to mean the keyword $T_0$ must appear, in any location, in the same file as the keyword $S_0$ in any configuration file.
+The type rule is a set of rules over multiple predicates, where $|S|=1, |T|=1$.
+These type rules take the form $S_0 \in \validSet \implies \validSet \vdash is\_([S_0],[S_0])$ where $\_$ matches all the basic types (bool, int, size, etc), as shown in Fig.~\ref{fig:allrules}.
+In this case, the source and target are the same keyword, since a type constraint is only on a single keyword.
 
 \app also supports two types of integer correlation rules, coarse-grained and fine-grained.
-Both integer correlation rules are set of rules over the predicates $\{<,=,>\}$.
+Both integer correlation rules are set of rules over the set of predicates $compare=\{<,=,>\}$.
 Coarse grain rules require $|S|, |T| = 1$, and the predicates have the typical interpretation.
-Fine-grained rules use $|S|=2,|T|=1$, and interpret the predicates such that for $k_1,\ k_2 \in S,\ k1*k2$ must have the predicate relation to $T$.
+Fine-grained rules use $|S|=2,|T|=1$, and interpret the predicates such that for $k_1,\ k_2 \in S,\ k1*k2$ must have the predicate relation to $T_0$.
 The integer correlation rules also use probabilistic types to prune the search space.
 To avoid learning too many false positives, we restrict this rule to either $size*int=size$, or $int*int = int$, as shown in Fig.~\ref{fig:allrules}.
-Without probabilistic typing, we would also learn rules which do not have a invalid sematinc interpretation, for example a relation between three size keywords ($k1,k2,k3::size$) of the form $k1*k2>k3$.
+Without probabilistic typing, we would also learn rules which do not have a valid sematinc interpretation, for example a relation between three size keywords ($k1,k2,k3::size$) of the form $k1*k2>k3$.
 
@@
 \inferrule* [Right=bool]
-{k1 :: bool}
-{isbool(k1) :: Rule}
+{k_1 :: bool}
+{isbool([k_1],[k_1]) :: Rule}
 \and\quad
 \inferrule* [Right=int]
-{k1 :: int}
-{isint(k1) :: Rule}
+{k_{1} :: int}
+{isint([k_1],[k_1]) :: Rule}
 \and\\
-\inferrule* [Right=fine\_grain\_rule]
-{k1,k2,k3 :: int}
-{fine(k1,k2,k3) :: Rule}
+\inferrule* [Right=missing]
+{ }
+{missing([k_1],[k_2]) :: Rule}
 \and\quad
-\inferrule* [Right=fine\_grain\_rule]
-{k1,k3 :: size \\ k2 :: int}
-{fine(k1,k2,k3) :: Rule}
+\inferrule* [Right=coarse\_grain]
+{k_1, k_2 :: int}
+{compare([k_1],[k_2]) :: Rule}
+\and\\
+\inferrule* [Right=fine\_grain,before=\hspace{-1.3cm}]
+{k_1,k_2,k_3 :: int}
+{compare([k_1,k_2],[k_3]) :: Rule}
+\and\quad
+\inferrule* [Right=fine\_grain]
+{k_1,k_3 :: size \\ k_2 :: int}
+{compare([k_1,k_2],[k_3]) :: Rule}
 \end{mathpar}

### 2017-04-16 OOPSLA17/secs/related.tex
fixed rule def to be entierly consistent (i hope)

@@
 This approach is not only generalizes association rule learning, but also another popular learning strategy called \textit{sequential pattern mining}~\cite{seqMine}.
-Our ordering rules are similar to the rules learned in sequential pattern mining, although can restrict our ordering rules to |S|,|T|=1 since these are the most common misconfigurations we encounter in practice.
+Our ordering rules are similar to the rules learned in sequential pattern mining, although can restrict our ordering rules to $|S|,|T|=1$ since these are the most common misconfigurations we encounter in practice.
 While a major limitation to sequential pattern mining is the scalability of the problem, we escape this issue since configuration files tend to be no more than thousands of lines at a time.

### 2017-04-16 OOPSLA17/secs/table2.tex
fixed rule def to be entierly consistent (i hope)

--- 2017-01-25 CAV17/secs/table2.tex
@@
-\newcommand{\tablewidth}{5.9cm}
+\newcommand{\tablewidth}{6.5cm}
 \definecolor{Gray}{gray}{0.80}
@@
 \hline
-{\bf Errors} & {\bf URLs} & {\bf None} & {\bf RG} & {\bf PT} & {\bf RG$\land$ PA}\\ 
+{\bf Errors} & {\bf URLs} & {\bf None} & {\bf RG} & {\bf PT} & {\bf RG$\land$ PT}\\ 
 \hline
@@
 
-\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize TYPE ERROR: Expected an integer for “slow\_query\_log”}}
-& \cite{type1} & 32/34 & 1/34 & 5/7   & 1/7 \\ 
-& \cite{type2} & 9/20  & 2/20 & 10/11 & 2/11 \\  
-& \cite{type3} & 9/19  & 2/19 & 10/11 & 2/11 \\
+\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize TYPE ERROR: Expected bool for ``thread\_cache\_size''}}
+& \cite{type1} & 1/12  & 1/12 & 1/4   & 1/4 \\ 
+& \cite{type2} & 1/9  & 1/9 & 1/1 & 1/1 \\  
+& \cite{type3} & 1/8  & 1/8 & 1/3 & 1/3 \\
 \hline

### 2017-04-17 OOPSLA17/secs/eval.tex
add new eval from CAV feedback (rahul and arrons classification)

@@
 
+\subsection{False Positive Rate}
+
+Because \app detects complex and subtle misconfigurations that, for example, may cause performance degradation in a high traffic load, false positives are system and use-case dependent and therefore ill-defined.
+However, we report an estimation of the false positive rate for comparison to other tools.
+To estimate a false positive rate, we asked two industry experts, one from MongoDB and one from Microsoft, to independently classify all errors from Table~\ref{table-casestudy}.
+For each unique error reported in Table~\ref{table-casestudy} (a total of 70 unique errors), the expert was asked to classify the error as: definitely false positive, potential true positive, or definitely true positive.
+The MongoDB expert rated 13/70 errors as definitely false positives. 
+The Microsoft expert rated 8/70 errors as definitely false positives. 
+The similarity between experts is suggestive that these are approximately correct classifications.
+
+The resulting false positive rate is then estimated to be 11\%-18\%.
+This is in the range of existing work, for example in the EnCore tool, which had a false positive rate of 13\%,21\%,32\% for MySQL, Apache, and PHP respectively~\cite{encore}.
+We note again that as opposed to a tool like EnCore, which is used mainly to detect initialization errors, thanks to the complex relations that can be learned, \app also learns misconfigurations causing runtime performance degradation.
+This means \app generates a larger rule set, and false positives cannot be garunteed, i.e. there may be some environment conditions that will cause a ``false'' positive to become a true positive.
+
+In contrast, a true positive can be confirmed as such based on evidence of unwanted system behvaior.
+The errors listed in Table~\ref{table-casestudy} are confirmed true positives, evidenced by posts on help forums.
+\app detected and reports these errors in the 15 code repositories listed in the URL column of Table~\ref{table-casestudy}. 
+These are real-world configuration files that contain errors that may be unknown to the maintainers of the repositories.
+%The errors were not submitted as patches to the repository owners, since it is possible the owner of the repository has a user case for this configuration file that will not trigger the unwanted behavior.
+
+\subsection{Runtime Performance}
 We also evaluate the speed of \app.

### 2017-04-17 OOPSLA17/secs/eval.tex
finish related work paragraph for sequential pattern mining

@@
 We note again that as opposed to a tool like EnCore, which is used mainly to detect initialization errors, thanks to the complex relations that can be learned, \app also learns misconfigurations causing runtime performance degradation.
-This means \app generates a larger rule set, and false positives cannot be garunteed, i.e. there may be some environment conditions that will cause a ``false'' positive to become a true positive.
+This means \app generates a larger rule set, and false positives cannot be guaranteed, \ie there may be some environment conditions that will cause a ``false'' positive to become a true positive.
 
-In contrast, a true positive can be confirmed as such based on evidence of unwanted system behvaior.
+In contrast, a true positive can be confirmed as such based on evidence of unwanted system behavior.
 The errors listed in Table~\ref{table-casestudy} are confirmed true positives, evidenced by posts on help forums.

### 2017-04-17 OOPSLA17/secs/related.tex
finish related work paragraph for sequential pattern mining

--- 2017-04-15 PLDI/secs/related.tex
@@
 \para{Misconfiguration diagnosis}
-Many misconfiguration diagnosis approaches have been proposed%
-~\cite{attariyan10automating, attariyan12x-ray}.
+Misconfiguration diagnosis approaches have been proposed to address configuration problems post-mortem.
 For example, ConfAid~\cite{attariyan10automating} 
 and X-ray~\cite{attariyan12x-ray} use dynamic information
-flow tracking to find possible configuration errors that may result in
+flow tracking to find possible configuration errors that may have resulted in
 failures or performance problems. AutoBash~\cite{su07autobash} 
@@
 failures occur, which leads to prolonged recovery time.
+
+\para{Association Rule Learning}
+The approach we have presented not only generalizes association rule learning, but also another learning strategy called \textit{sequential pattern mining}~\cite{mabroukeh2010taxonomy}.
+Ordering rules are similar to the patterns learned in sequential pattern mining, although we restrict our ordering rules to $|S|,|T|=1$ since these are the most common misconfigurations we encounter in practice.
+While a major limitation to sequential pattern mining is the scalability of the problem~\cite{ayres2002sequential}, we escape this issue with $|S|,|T|=1$ and the fact that a single configuration file tends to be less a few thousand lines.
+There has been other work in these same classes of algorithms~\cite{han2007frequent,langley1995applications} for various applications and variations on the core problem.
+A future direction for this work is to integrate advances in these domains into the configuration file verification problem.

### 2017-04-17 OOPSLA17/secs/intro.tex
stuff

@@
 this was caused by a change to the site's configuration systems.
-In a recent software system failures study~\cite{yin11anempirical},
-researchers revealed that about 31\% of system failures were caused by 
+\ruzica{1) one more such example? we have enough space. 2) do something about citations (mas 2015) looks silly 3) there is no comparison, or even
+mentioning of the OSDI paper 2016, which is on configuration files and they got even the best paper award }
+In a software system failures study~\cite{yin11anempirical},
+it was shown that about 31\% of system failures were caused by 
 configuration errors, which is higher than the percentage of

### 2017-04-17 OOPSLA17/secs/related.tex
vericonf: related work for tianyin's PCheck

--- 2017-04-16 OOPSLA17/secs/related.tex
@@
 
+PCheck~\cite{xu16early} aims to add configuration checking code to
+the system source code by emulating potential commands and behaviors
+of the system. However, PCheck is limited to the reliability problems
+caused by misconfiguration parameters; on the contrary, 
+\app can cover general misconfiguration issues 
+including performance, security, availability and reliability.
+In addition, PCheck's emulation capability heavily depends on 
+system category and source code.
+For example, for some systems (\eg, ZooKeeper) whose behaviors are 
+hard to emulate, PCheck cannot automatically generate the corresponding
+checking code; on the contrary, \app does not rely on specific
+system behaviors or source code.
+
 \para{Misconfiguration diagnosis}

### 2017-04-17 OOPSLA17/secs/trans.tex

@@
 However the correct classification needed is a Boolean type.
-For illustrative purposes, let us assume that there is a critical rule we must learn where tow Boolean keywords should always have the same values, e.g. $eq(\texttt{foo},\texttt{bar})$.
+For illustrative purposes, let us assume that there is a critical rule we must learn where tow Boolean keywords should always have the same values, \eg $eq(\texttt{foo},\texttt{bar})$.
 If we take {\tt bar}$::int$, we do not learn the above rule, nor do we learn this rule with {\tt bar}$::string$ - only with {\tt bar}$::bool$ is the rule is valid.
@@
 \and\\
-\inferrule* [Right=eq\_rule]
+\inferrule* [Right=eq\_rule,before=\hspace{-1.5cm}]
 {k_1 :: \tau \\ k_2 :: \tau}
@@
 \and
-\inferrule* [Right=order\_rule]
+\inferrule* [Right=order\_rule,before=\hspace{-1cm}]
 {k1,k2 \in C \\ k1 \neq k2}
@@
 
-In order to define resolution predicates, we use the notation $|\tau_i\ptype|$ to select $c_i$ from a $\ptype \in \tilde{\mathcal{T}}$.
-As an example, for the sample training set provided in Figure~\ref{fig:tset}, we might choose to set $p_{bool}(\ptype)= |bool_{\ptype}| \geq 3 \land |int_{\ptype}| \leq 1$ and $p_{int}(\ptype)= |int\ptype| \geq 3$.
+In order to define resolution predicates, we use the notation $|\tau_{i\ptype}|$ to select $c_i$ from a $\ptype \in \tilde{\mathcal{T}}$.
+As an example, for the sample training set provided in Figure~\ref{fig:tset}, we might choose to set $p_{bool}(\ptype)= |bool_{\ptype}| \geq 3 \land |int_{\ptype}| \leq 1$ and $p_{int}(\ptype)= |int_{\ptype}| \geq 3$.
 We then can run inference on that sample training set to derive a probabilistic type \texttt{bar}$:[bool=3,int=1]$.
@@
 Note that a user may pick predicates for probabilistic type resolution that result in overlapping inference rules.
-For example, if a user instead picked $p_{int}(\ptype)= |int\ptype| \geq 1$, {\scriptsize INT} would overlap with {\scriptsize BOOL}.
-This means that types are not unique in this system, i.e. $k:\ptype \land k:\ptype' \centernot\implies \ptype = \ptype'$.
+For example, if a user instead picked $p_{int}(\ptype)= |int_{\ptype}| \geq 1$, this predicate would overlap with the $p_{bool}$ predicate.
+This means that basic types are not unique in this system, \ie $k::\tau \land k::\tau' \centernot\implies \tau = \tau'$.
 

### 2017-04-17 OOPSLA17/secs/related.tex
autocommit

--- 2017-04-17 OOPSLA17/secs/related.tex
@@
 
+PCheck~\cite{xu16early} aims to add configuration checking code to the system source code by emulating potential commands and behaviors of the system. 
+This emulation is a ``white-box'' approach and requires access to the system's source code.
+One drawback to this approach is that for some systems (\eg, ZooKeeper) whose behavior is 
+hard to emulate, PCheck cannot automatically generate the corresponding checking code.
+Due to the emulation based testing strategy, PCheck's scope is limited to reliability problems caused by misconfiguration parameters. 
+In contrast, \app is a ``black-box'' approach and only requires a training set of configuration files to learn rules.
+By using a rule learning strategy of examples, \app is able to detect general misconfiguration issues that are outside the scope of emulation testing (\eg memory or thread usage settings), including performance, security, availability and reliability.
+
 \para{Misconfiguration diagnosis}

### 2017-04-17 OOPSLA17/secs/eval.tex
half rewrite of intro

@@
 Since these settings depend on both the user preference and training set quality, we simply choose values for which \app reports reasonably sized output.
+This is a determined by the user by examining the rule set output over the training set.
+Following common practice from association rule learning, initial values for support are confidence are generally 10\% and 90\% respectively.
 
@@
 The resulting false positive rate is then estimated to be 11\%-18\%.
-This is in the range of existing work, for example in the EnCore tool, which had a false positive rate of 13\%,21\%,32\% for MySQL, Apache, and PHP respectively~\cite{encore}.
+This is within the range of the false positive rate in existing work.
+For example in the EnCore tool, which had a false positive rate of 13\%,21\%,32\% for MySQL, Apache, and PHP respectively~\cite{encore}.
 We note again that as opposed to a tool like EnCore, which is used mainly to detect initialization errors, thanks to the complex relations that can be learned, \app also learns misconfigurations causing runtime performance degradation.

### 2017-04-17 OOPSLA17/secs/intro.tex
half rewrite of intro

--- 2017-04-15 OOPSLA17/secs/intro.tex
@@
 one of the major causes of system failures, resulting in security vulnerabilities,
-application outages, and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}. Recently, there was a problem in accessing  
-Facebook and Instagram~\cite{mashableNews}, 
+application outages, and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}. 
+In one high profile case,  
+Facebook and Instagram became inaccessible~\cite{mashableNews}
 and a Facebook spokeswoman reported that 
 this was caused by a change to the site's configuration systems.
-In a recent software system failures study~\cite{yin11anempirical},
-researchers revealed that about 31\% of system failures were caused by 
-configuration errors, which is higher than the percentage of
-failures resulting from program bugs (20\%).
+In another case, a system configuration change caused an outage of AT\&T's 911 service for five hours.
+During this time, 12,600 unique callers were not able to reach the 911 emergency line~\cite{att-outage}.
+These critical system failures are not rare either -
+a software system failures study~\cite{yin11anempirical},
+reports that about 31\% of system failures were caused by 
+configuration errors.
+This is even higher than the percentage of failures resulting from program bugs (20\%).
 
-In this paper, we propose
-a framework for automated verification of configuration files: 
-we derive specifications by learning ``raw'' configuration files 
-and proactively report potential errors in the configuration files
-of interest, without waiting for them to happen. 
-We developed a tool, called \app, 
-and evaluated it on 
-almost a thousand configuration files from Github. The systems research community has recognized this as an important
-problem~\cite{xu16early}. While many efforts have been proposed to
+The systems research community has recognized this as an important
+problem~\cite{xu16early} and many efforts have been proposed to
 check, troubleshoot, and diagnose configuration 
 errors~\cite{attariyan10automating,
-su07autobash, whitaker04configuration},
-those tools heavily rely on analyzing the source code of 
-the target systems and need to run these systems
-multiple times to understand where are the errors---\ie,
-they are still not on a level of
+su07autobash, whitaker04configuration,xu2016early}.
+However, these tools rely on analyzing the source code of 
+the target systems or need to run the system
+multiple times to understand the source of the errors.
+The support for a static analysis style verification for configuration files
+is still not on a level of
 automated verification tools used for regular program 
 verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
-detect errors without executing the code.
+preemptively detect errors.
 
-We believe there are two main obstacles 
-to why we cannot simply apply the existing automatic program
-verification 
-techniques to verification of configuration files:
-1) the lack
-of a specification describing properties of configuration files;
-2) the structure of configuration files -- they
+In this paper, we propose a framework for automated verification of configuration files: 
+we derive specifications for a correct configuration file by processing a training set of configuration files 
+and proactively report potential errors in the configuration files of interest.
+In this framework, the example configurations from which we derive the specifications do not need to be labeled as correct or incorrect.
+
+There are two main obstacles to directly applying existing automatic program
+verification techniques to verification of configuration files:
+1) the lack of a specification describing properties of configuration files;
+2) the flat structure of configuration files -- they
 are mainly a sequence of entries assigning some value to system
@@
 The language in which configuration files are written does 
-not adhere to a specific grammar or syntax. In particular, the
-entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries, and there
-is no explicit structure policy for the entries.
+not always adhere to a specific grammar or syntax. In particular, the
+entries in configuration files are untyped. 
+Moreover, there are surprisingly few rules specifying constraints on entries, 
+and there is no explicit structure policy for the entries.
 
@@
 the same kind (such as MySQL or HTTPD configuration files).
-We see this learning process as 
-a way of deriving  a specification for configuration files. 
-It is hard to talk here about a complete specification, but it is still
-a set of formal rules describing the properties that configuration files need to satisfy.
+This learning process is a way to derive a specification for configuration files. 
+%It is hard to talk here about a complete specification, but it is still
+%a set of formal rules describing the properties that configuration files need to satisfy.
 
@@
 
-The errors found can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
+The errors \app detects may cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
 Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging 
@@
 
-To the best of our knowledge, there have been several prior efforts that attempt to proactively verify 
+\markk{xu16early should go here somehow}
+There have been several prior efforts that attempt to proactively verify 
 configuration files~\cite{santolucitoCAV, xu16early,
@@
 more complex configuration errors, such as ordering errors or 
-Nevertheless, these types of errors cannot be detected by above existing
-efforts.
+Nevertheless, these types of errors cannot be detected by above existing efforts.
 \end{itemize}
@@
 
-% Encore also used association rule learning, but did not describe why it is useful for verification in particular,
+% EnCore also used association rule learning, but did not describe why it is useful for verification in particular,
 %   or how it contrasts with other ML techniques that are less appropriate for verification (NN).
@@
 
-% The problem is intractable for off-the-shelf data mining solutions (see Encore).
-% In addition to the optimizations Encore used, we add new ones that make our tool even better.  
+% The problem is intractable for off-the-shelf data mining solutions (see EnCore).
+% In addition to the optimizations EnCore used, we add new ones that make our tool even better.  
 \item An open-source implementation, \app, of this approach, which uses various domain specific optimizations to make the solution efficient. 

### 2017-04-17 OOPSLA17/secs/related.tex
half rewrite of intro

@@
 Several machine learning-based misconfiguration detection efforts 
-also have been proposed~\cite{yuan11context, zhang14encore}.
-EnCore~\cite{zhang14encore} is one of representative work in this area.
-EnCore introduces a template-based
+also have been proposed~\cite{yuan11context, zhang14encore, xu16early}.
+EnCore~\cite{zhang14encore} introduces a template-based
 learning approach to improve the accuracy of their learning results.

### 2017-04-17 OOPSLA17/secs/trans.tex
half rewrite of intro

@@
 However the correct classification needed is a Boolean type.
-For illustrative purposes, let us assume that there is a critical rule we must learn where tow Boolean keywords should always have the same values, \eg $eq(\texttt{foo},\texttt{bar})$.
+For illustrative purposes, let us assume that there is a critical rule we must learn where tow Boolean keywords should always have the same values, \textit{e.g.} $eq(\texttt{foo},\texttt{bar})$.
 If we take {\tt bar}$::int$, we do not learn the above rule, nor do we learn this rule with {\tt bar}$::string$ - only with {\tt bar}$::bool$ is the rule is valid.
@@
 \and\\
-\inferrule* [Right=eq\_rule,before=\hspace{-1.5cm}]
+\inferrule* [Right=eq,before=\hspace{-1.5cm}]
 {k_1 :: \tau \\ k_2 :: \tau}
@@
 \and
-\inferrule* [Right=order\_rule,before=\hspace{-1cm}]
+\inferrule* [Right=order,before=\hspace{-1cm}]
 {k1,k2 \in C \\ k1 \neq k2}
@@
 For example, if a user instead picked $p_{int}(\ptype)= |int_{\ptype}| \geq 1$, this predicate would overlap with the $p_{bool}$ predicate.
-This means that basic types are not unique in this system, \ie $k::\tau \land k::\tau' \centernot\implies \tau = \tau'$.
+This means that basic types are not unique in this system:  $k::\tau \land k::\tau' \centernot\implies \tau = \tau'$.
 

### 2017-04-18 OOPSLA17/secs/intro.tex
proper outline
autocommit

@@
 
+%what is the problem
 Configuration errors (also known as misconfigurations) have become
@@
 During this time, 12,600 unique callers were not able to reach the 911 emergency line~\cite{att-outage}.
-These critical system failures are not rare either -
+These critical system failures are not rare -
 a software system failures study~\cite{yin11anempirical},
@@
 
+%what has been done
 The systems research community has recognized this as an important
-problem~\cite{xu16early} and many efforts have been proposed to
+problem and many efforts have been proposed to
 check, troubleshoot, and diagnose configuration 
 errors~\cite{attariyan10automating,
-su07autobash, whitaker04configuration,xu2016early}.
+su07autobash, whitaker04configuration,xu16early}.
 However, these tools rely on analyzing the source code of 
@@
 The support for a static analysis style verification for configuration files
-is still not on a level of
+is still not on the level of
 automated verification tools used for regular program 
@@
 
-In this paper, we propose a framework for automated verification of configuration files: 
-we derive specifications for a correct configuration file by processing a training set of configuration files 
-and proactively report potential errors in the configuration files of interest.
-In this framework, the example configurations from which we derive the specifications do not need to be labeled as correct or incorrect.
-
-There are two main obstacles to directly applying existing automatic program
-verification techniques to verification of configuration files:
-1) the lack of a specification describing properties of configuration files;
-2) the flat structure of configuration files -- they
-are mainly a sequence of entries assigning some value to system
-variables (called {\emph {keywords}}). 
-The language in which configuration files are written does 
-not always adhere to a specific grammar or syntax. In particular, the
-entries in configuration files are untyped. 
-Moreover, there are surprisingly few rules specifying constraints on entries, 
-and there is no explicit structure policy for the entries.
-
-\app overcomes the above obstacles by first automatically inferring a
-specification for configuration files. It is unrealistic to expect the 
-users to write an entire specification for configuration files on their own. 
-This process can easily lead to incomplete or even contradictory 
-specifications. Instead, we learn specification from 
-a large training set of 
-configuration files~\cite{configdataset}. The first step is to 
-translate this training set into a more structured typed representation.
-We then apply the learning process and we learn an abundant set of rules 
-specifying various properties that hold on the given training set. The rules, in general, 
-specify which properties keywords in configuration files need to satisfy.
-The learning process is language-agnostic and works for any kind 
-of configuration files,  but all of the files in the training set need to be of 
-the same kind (such as MySQL or HTTPD configuration files).
-This learning process is a way to derive a specification for configuration files. 
-%It is hard to talk here about a complete specification, but it is still
-%a set of formal rules describing the properties that configuration files need to satisfy.
-
-Having a specification, \app can then efficiently check 
-the correctness of the configuration files of interest and detect 
-potential errors. Errors are reported if the configuration file does not 
-adhere to the derived specification.
-
-The errors \app detects may cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
-Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging 
-techniques~\cite{Zeller:2005:WPF:1077048} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.
-
-\markk{xu16early should go here somehow}
+%why is that insufficent
+%\markk{xu16early should go here somehow}
 There have been several prior efforts that attempt to proactively verify 
@@
 However, state-of-the-art efforts have limitations that are impractical to meet in practice.
-In general, these efforts fall into two categories with respect to their limitations.\begin{itemize}
+In general, these efforts fall into two categories with respect to their limitations.
+\begin{itemize}
 \item On the one hand there are tools that can detect sophisticated 
@@
 and simple integer correlation errors), but cannot detect
-more complex configuration errors, such as ordering errors or 
-Nevertheless, these types of errors cannot be detected by above existing efforts.
+more complex configuration errors, such as ordering errors, fine-grain correlations, missing entry errors.
 \end{itemize}
 
+%what do we do
+In this paper, we propose a framework for automated verification of configuration files: 
+We derive specifications for a correct configuration file by processing a training set of configuration files that may contain some errors.
+The errors that we learn are detailed and complex enough proactively report a wide range of potential misconfigurations.
+In this framework, the example configurations from which we derive the specifications do not need to be labeled as correct or incorrect.
+
+% how did we do it
+There are two main obstacles to directly applying existing automatic program
+verification techniques to configuration files.
+First, a lack of specifications on the properties of configuration files makes the verification task poorly defined.
+There are surprisingly few rules specifying constraints on entries, even written in plain English.
+Since asking users to write an entire specification for configuration files is impractical and error-prone, we instead take a specification generation approach.
+Second, the flat structure of configuration files is only a sequence of entries assigning some value to system
+variables (called {\emph {keywords}}) and provides little structural information.
+In particular, the keywords in configuration files are often untyped, a useful property to leverage in program verification.
+
+In order to learn a specification from a large training set of configuration files,
+the first step is to 
+translate this training set into a more structured typed representation.
+We then apply the learning process and we learn an abundant set of rules 
+specifying various properties that hold on the given training set. The rules, in general, 
+specify which properties keywords in configuration files need to satisfy.
+The learning process is language-agnostic and works for any kind 
+of configuration files, though all of the files in the training set need to be of 
+the same language (such as MySQL or HTTPD configuration files).
+This learning process is a way to derive a specification for configuration files. 
+With the learned specification, \app can then efficiently check 
+the correctness of the configuration files of interest and detect 
+potential errors. Errors are reported if the configuration file does not 
+adhere to the derived specification.
+
+The errors \app detects may cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
+Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging 
+technique~\cite{Zeller:2005:WPF:1077048} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.
+
+%did what we did work?
 Our learning algorithm surmounts both of these shortcomings present in 
@@
 algorithm inspired by {\em association rule
-learning}~\cite{agrawal1993mining}. It analyzes a large training set of configuration files~\cite{configdataset}. Those are real-world reported misconfigurations. A file in the training set might 
-contain several different errors and these errors only appear 
-in a small percentage of files. We first translate those file into an 
-intermediary typed language. With with every type, we associate 
-a set of very general interfaces. The user does not
-need to provide them - they are internally associated with the types. The 
-learner then instantiates those interfaces with the keywords appearing in 
+learning}~\cite{agrawal1993mining}. It analyzes a large training set of configuration files~\cite{configdataset}. Those are real-world reported misconfigurations. 
+A file in the training set might contain several different errors and these errors only appear 
+in a small percentage of files. 
+We first translate those file into an intermediary typed language. 
+With with every type, we associate a set of very general interfaces. 
+The user does not need to provide them - they are internally associated with the types. 
+The learner then instantiates those interfaces with the keywords appearing in 
 the training set. However, since files might also contain errors we take 

### 2017-04-18 OOPSLA17/secs/intro.tex
stuff

@@
 application outages, and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}. 
-In one high profile case,  
-Facebook and Instagram became inaccessible~\cite{mashableNews}
+In a recent high visible case~\cite{mashableNews},  
+Facebook and Instagram became inaccessible
 and a Facebook spokeswoman reported that 
@@
 %what do we do
-In this paper, we propose a framework for automated verification of configuration files: 
-We derive specifications for a correct configuration file by processing a training set of configuration files that may contain some errors.
-The errors that we learn are detailed and complex enough proactively report a wide range of potential misconfigurations.
-In this framework, the example configurations from which we derive the specifications do not need to be labeled as correct or incorrect.
+In this paper, we propose a framework for automated verification of 
+configuration files, which mimics standard automated verification 
+techniques: for a given configuration file, we  checked if it 
+adheres to a specification, and if there are issues we report them to 
+the user.
 
@@
 
-In order to learn a specification from a large training set of configuration files,
+Our main task was to first derive a specification for configuration 
+files. We first process a \ruzica{mention the size, size does matter :)}training set of configuration files. Those files are benchmarks 
+available on-line~\ruzica{put a citation here}. They are mostly correct
+but they also may contain some errors.
+
+In order to learn a specification from this large set of configuration
+files,
 the first step is to 
-translate this training set into a more structured typed representation.
+translate the training set into a more structured typed representation.
 We then apply the learning process and we learn an abundant set of rules 
-specifying various properties that hold on the given training set. The rules, in general, 
+specifying various properties that hold on the given training set. 
+\ruzica{say here 2 sentences about the learning process }
+
+The rules, in general, 
 specify which properties keywords in configuration files need to satisfy.
@@
 the same language (such as MySQL or HTTPD configuration files).
+
 This learning process is a way to derive a specification for configuration files. 
@@
 adhere to the derived specification.
+
+The errors that we learn are detailed and complex enough proactively report a wide range of potential misconfigurations.
+In this framework, the example configurations from which we derive the specifications do not need to be labeled as correct or incorrect.
 

### 2017-04-18 OOPSLA17/secs/intro.tex
stuff

@@
 specify which properties keywords in configuration files need to satisfy.
+\ruzica{examples of properties}
+
 The learning process is language-agnostic and works for any kind 
@@
 
-This learning process is a way to derive a specification for configuration files. 
+This learning process is a way of deriving a specification for configuration files. 
 With the learned specification, \app can then efficiently check 
 the correctness of the configuration files of interest and detect 
-potential errors. Errors are reported if the configuration file does not 
-adhere to the derived specification.
+potential errors.
 
-The errors that we learn are detailed and complex enough proactively report a wide range of potential misconfigurations.
-In this framework, the example configurations from which we derive the specifications do not need to be labeled as correct or incorrect.
-
-The errors \app detects may cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
+The errors that \app detects may cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
 Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging 
@@
 %did what we did work?
+
+\ruzica{hmmm... this appears to be repeating - can you merge some of those stuff with stuff above}
+
 Our learning algorithm surmounts both of these shortcomings present in 
@@
 Furthermore, we find compelling evidence that out optimizations are 
-effective, for example using probabilistic types removes 1023 false 
+effective, for example using probabilistic types \ruzica{this is the first time you mention them, so i don't know what is that}
+
+removes 1023 false 
 positives errors reports to reduce the total error reports to 324.
 The rule graph analysis drastically improves the ranking of importance of 
-the error reports, which allows users to more quickly fix the most 
+the error reports, which allows users to more quickly correct the most 
 critical misconfigurations.

### 2017-04-18 OOPSLA17/secs/intro.tex
ruzica part 1

--- 2017-04-18 OOPSLA17/secs/intro.tex
@@
 Our main task was to first derive a specification for configuration 
-files. We first process a \ruzica{mention the size, size does matter :)}training set of configuration files. Those files are benchmarks 
-available on-line~\ruzica{put a citation here}. They are mostly correct
+files. We first process a training set of 256 industrial configuration files. This training set of files is
+available on-line~\cite{configdataset}. They are mostly correct
 but they also may contain some errors.
@@
 translate the training set into a more structured typed representation.
-We then apply the learning process and we learn an abundant set of rules 
+We then apply our learning process to learn an abundant set of rules 
 specifying various properties that hold on the given training set. 
-\ruzica{say here 2 sentences about the learning process }
+The learning process is a more expressive form of association rule learning~\cite{agrawal1993mining}, which is used to learn predicate relations between multiple keywords in a configuration file.
 

### 2017-04-18 OOPSLA17/secs/intro.tex
autocommit

@@
 The learning process is a more expressive form of association rule learning~\cite{agrawal1993mining}, which is used to learn predicate relations between multiple keywords in a configuration file.
-
-The rules, in general, 
-specify which properties keywords in configuration files need to satisfy.
-\ruzica{examples of properties}
+The rules, in general, specify which properties such as, one kewyord must appear before another, or the value of one keyword should always be greater than another.
 
@@
 algorithm inspired by {\em association rule
-learning}~\cite{agrawal1993mining}. It analyzes a large training set of configuration files~\cite{configdataset}. Those are real-world reported misconfigurations. 
-A file in the training set might contain several different errors and these errors only appear 
+learning}~\cite{agrawal1993mining} that analyzes a training set of partially correct files.
+A file in the training set might contain several different errors, but errors only appear 
 in a small percentage of files. 
 We first translate those file into an intermediary typed language.
-With with every type, we associate a set of very general interfaces. 
-The user does not need to provide them - they are internally associated with the types. 
-The learner then instantiates those interfaces with the keywords appearing in 
-the training set. However, since files might also contain errors we take 
+\app then learns rules based on the inferred types of the keywords from the training set.
+However, since the files might also contain errors we take 
 this into account when learning correct rules. All learned rules are 
@@
 Furthermore, we find compelling evidence that out optimizations are 
-effective, for example using probabilistic types \ruzica{this is the first time you mention them, so i don't know what is that}
-
-removes 1023 false 
+effective
+For example, we introduce a probabilistic type inference system that removes 1023 false 
 positives errors reports to reduce the total error reports to 324.

### 2017-04-18 OOPSLA17/secs/intro.tex
autocommit

@@
 specifying various properties that hold on the given training set. 
-The learning process is a more expressive form of association rule learning~\cite{agrawal1993mining}, which is used to learn predicate relations between multiple keywords in a configuration file.
-The rules, in general, specify which properties such as, one kewyord must appear before another, or the value of one keyword should always be greater than another.
-
+The learning process is a more expressive form of \textit{association rule learning}~\cite{agrawal1993mining}, which is used to learn predicate relations between multiple keywords in a configuration file.
+The rules, in general, specify which properties such as, one keyword must appear before another, or the value of one keyword should always be greater than another.
+This set of learned rules constitutes a specification for a correct configuration file,
+which are then used to efficiently check the correctness of a user's configuration files and detect 
+potential errors. 
 The learning process is language-agnostic and works for any kind 
@@
 
-This learning process is a way of deriving a specification for configuration files. 
-With the learned specification, \app can then efficiently check 
-the correctness of the configuration files of interest and detect 
-potential errors.
-
-The errors that \app detects may cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
-Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging 
-technique~\cite{Zeller:2005:WPF:1077048} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.
+Our implementation, \app, detects errors that may cause total system failures, but can also find more insidious errors, for example configurations that will slow down the system only when the server load increases beyond a certain threshold.
+Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging techniques~\cite{Zeller:2005:WPF:1077048} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.
 
@@
 
-\ruzica{hmmm... this appears to be repeating - can you merge some of those stuff with stuff above}
-
 Our learning algorithm surmounts both of these shortcomings present in 
 existing tools. \app implements a learning
-algorithm inspired by {\em association rule
-learning}~\cite{agrawal1993mining} that analyzes a training set of partially correct files.
+algorithm inspired by association rule
+learning~\cite{agrawal1993mining} that analyzes a training set of partially correct files.
 A file in the training set might contain several different errors, but errors only appear 

### 2017-04-18 OOPSLA17/secs/intro.tex
...

@@
 application outages, and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}. 
-In a recent high visible case~\cite{mashableNews},  
+In a recent highly visible case~\cite{mashableNews},  
 Facebook and Instagram became inaccessible
@@
 %what do we do
-In this paper, we propose a framework for automated verification of 
+In this paper, we propose a framework, \app, for automated verification of 
 configuration files, which mimics standard automated verification 
@@
 the user.
+Our framework surmounts both of the aforementioned shortcomings present in existing tools.
 
@@
 
-Our implementation, \app, detects errors that may cause total system failures, but can also find more insidious errors, for example configurations that will slow down the system only when the server load increases beyond a certain threshold.
+\app detects errors that may cause total system failures, but can also find more insidious errors, for example configurations that will slow down the system only when the server load increases beyond a certain threshold.
 Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging techniques~\cite{Zeller:2005:WPF:1077048} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.
@@
 
-Our learning algorithm surmounts both of these shortcomings present in 
-existing tools. \app implements a learning
-algorithm inspired by association rule
-learning~\cite{agrawal1993mining} that analyzes a training set of partially correct files.
+\app works by analyzing a training set of partially correct files.
 A file in the training set might contain several different errors, but errors only appear 
@@
 
-We have implemented a tool, \app, and evaluated it on almost 1000 real-
+We implemented \app in Haskell  and evaluated it on almost 1000 real-
 world configuration files from Github.

### 2017-05-05 ISSTA17/response.txt
expaneded version of FMCAD for ISSTA

We thank the reviewers for their time and positive feedback.

@reviewerA: "What are the core contributions to an ICFP audience?"

We agree with the reviewer that the translation from automata to FRP
is mainly a technical result. However, let us try to convince you that
this translation is just one of several crucial building blocks needed
for our major contribution: the first synthesis approach for
FRP. Specifically,

1. we introduce TSL, the first temporal logic for the specification of
   data transformations over time,

2. we formulate the technical constructions needed to translate TSL to
   LTL, and automata to FRP, and

3. we show that our approach works on examples that are significantly
   out of reach for existing reactive synthesis methods.

Overall, our paper establishes the first connection between the
research areas of FRP and reactive synthesis, and shows that this
connection provides significant value to both sides.

We also agree with the reviewer that, in synthesis, scalability is
always a serious concern. The translation of the automaton to an FRP
program is, however, very much not the bottleneck. The two aspects
that are critical to scalability are the following:

1. The synthesis of the automaton from the LTL formula. This is a
   double-exponentially hard problem, which, as we know from the
   reactive synthesis community, cannot be applied to arbitrarily
   large LTL formulas. We do not consider this as a serious issue for
   two reasons: a) there are effective methods developed in the
   reactive synthesis community which we leverage, such as bounded and
   symbolic synthesis techniques, and b) we are in much better shape
   than the reactive synthesis community, because we only synthesize
   the control structure (which tends to be reasonably small), while
   they also synthesize the data transformation (which tends to be
   arbitrarily large).

2. The under-approximation, which is necessary because the TSL
   synthesis problem is undecidable. We have not found this to be a
   problem in our experiments. If needed, the under-approximation can
   be improved manually.

@reviewerC: "Why should TSL be prefered over LTL?"

TSL is fundamentally more expressive than LTL. While LTL only allows
reasoning about Boolean data streams, TSL describes streams of
abstract data types. TSL is also a much more appropriate logic to
describe FRP programs, which typically handle complex data. The power
of TSL is also reflected in that its synthesis problem is in general
undecidable. We show that, by separating control and data, we can use
LTL synthesis algorithms to synthesize programs from TSL
specifications, which has proven effective on substantial FRP
programs.

@reviewerC: "I would have expected infinite state transition systems."

Yes and no. Our method separates control and data. While the control
part is (as usual) finite, the data part can be infinite. In that
sense, the reviewer is correct in observing that our reasoning is
finite by using uninterpreted functions, which provide a finite
abstraction.

@reviewerB:

We thank you for your encouraging words, and we like your suggestions
on how to restructure the paper to improve it further.

### 2017-05-05 ISSTA17/secs/abstract.tex
expaneded version of FMCAD for ISSTA

Configuration files provide users with the ability to quickly alter the behavior of their software system.
Ensuring that a configuration file does not induce errors in the software is a complex verification issue.
The types of errors can be easy to measure, such as an initialization failure of system boot, 
   or more insidious such as performance degrading over time under heavy network loads.
In order to warn a user of potential configuration errors ahead of time, we propose using version space learning specifications for configuration languages.
We frame an existing tool, ConfigC, in terms of version space learning.
We extend that algorithm to leverage the temporal structuring avaible in training sets scraped from versioning control systems.
We plan to evaluate our system on a case study using TravisCI configuration files collected from Github.

### 2017-05-05 ISSTA17/secs/completeConfigC.tex
expaneded version of FMCAD for ISSTA

--- 2016-11-10 Travis/secs/completeConfigC.tex
@@
-This algorithm is complete but unsound.
+ConfigC is complete but unsound.
 We first define the set of incorrect files based on ground truth $Inc_{gt}$, and the set of files which are predicted by the model to be incorrect, $Inc_{prd}$.
-To define $Inc_{gt}$, we will introduce the set of relations that are necessary and breaking based on ground truth, $Nec_{gt}$ and $Br_{gt}$ respectivly.
+To define $Inc_{gt}$, we will introduce the set of relations that are necessary and breaking based on ground truth, $Nec_{gt}$ and $Br_{gt}$ respectively.
 The definition of $Inc_{prd}$ follows from the description of the algorithm.
@@
 
-To show completness we show that the $Inc_{gt} \subseteq Inc_{prd}$.
-
-\begin{align*}
-Nec \subseteq Nec_{gt}
-%Nec \disjoint Br_{gt}
-%\forall C \in {Incorrect(C)}, C \in system(Inc,C)   Nec_{True}, r \in Nec_{Learned} - (Nec_{Learned} \contains Nec_{True})
-%\not \exists C \in SysInc(C), C \notin {Incorrect(C)} 
-%\Nec_{Learned} \contains Nec_{Observable}
-%\forall r \in Br, r \notin Incorrect(C) \implies \exists r \in Nec_{True}, r \notin M(C)
-%Incorrect(C) \implies \exists r \in Nec, r \notin M(C)
-\end{align*}
-
-%The algorithm is complete if, for any file which breaks a relation for which we have a template (a misconfiguration) and have seen an correct example, the system will mark that file as incorrect.
-%Since the model always maintins the strongest conditions for correctness for any file, the algorithm is clearly complete.
-%Completness cooresponds to no false negatives.
-%This algorithm is however unsound, some correct file may be marked as incorrect, a false postive.
-%We have a high false postive rate since the model is an overappoximation of the true model.
+Completeness follows from showing that $Inc_{gt} \subseteq Inc_{prd}$.
+The algorithm is complete if, for any file which breaks a relation for which we have a template (a misconfiguration) and have seen an correct example, the system will mark that file as incorrect.
+Since the model always maintains the strongest conditions for correctness for any file, the algorithm is clearly complete.
+Completeness corresponds to no false negatives.
+However, this algorithm is unsound, as some correct file may be marked as incorrect, i.e. ConfigC returns a false positive.
+We have a high false positive rate since the model is an over-approximation of the true model.

### 2017-05-05 ISSTA17/secs/intro.tex
expaneded version of FMCAD for ISSTA

--- 2016-09-05 Travis/secs/intro.tex
@@
 
+%what is the problem
+Configuration files provide easy access to the most critical parameters of software systems in order to quickly tune the behavior system.
+This expressive power in a single file creates a large surface for potential errors that can degrade performance or take down systems entirely.
+The verification task for configuration files cannot be addressed with traditional software analysis techniques.
+There are rarely formal specifications of a correct configuration, 
+  the source code of the underlying system may not be available, 
+  and the configuration may depend on the external environment such as the network or available hardware.
+To address this issue, we propose a method for automated configuration file verification using a data set of labeled examples of correct and incorrect configurations.
+
+%what approach do we take to the problem
+In previous work, we used version space learning for configuration file verification.
+We extend that work which only works on correct examples, to work on temporally structured correct and incorrect examples by building an SMT formula to find a classification model.
+As a demonstration of this algorithm, we plan to implement it to automatically verify TravisCI configurations.
+The algorithm will utilize Github histories to allow us to detect potential build errors without actually building, saving valuable programmer and server time.
+
+%why cant we use existing approach
+%legibility issue
 Machine learning has been used in various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
@@
 For example, in the case of error detection, the system should not only report which files have errors, but also locate the errors.
+This justification issue is also called \textit{legibility} of machine learning.
+
+%correctness issue
+Additionally, these probabilistic approaches to machine learning cannot be guaranteed to be complete, that is they will always find the error.
+We use version space learning to address the need for a formal completeness guarantee in an automated model generation for verification.
 Version space learning is a technique for logical constraint classification~\cite{mitchell82}.
@@
 
-%However, many popular machine learning algorithms, such as neural nets and n-gram models, produce probabilistic models of correctness.
-%While effective in practice, these approachs cannot be garunteed to be complete, that is they will always find the error.
-%We use version space learning to address the need for a formal completness garuntee in automated model generation for verification.
-
+%What have we already done (labeled correct)
 In our previous work~\cite{Santolucito2016} we built a prototype to verify configuration files from a set of correct examples.
 The tool, ConfigC, takes as a training set a set of correct configuration files and builds a set of rules describing a language model.
-This model is then used to check if a new configuration file adhears to those rules.
-If a file is incorrect, the tool identifies the location of error, and reports what is incorrect.
-For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so" before "extension recode.so"}.
-While this prototype's results are promising, the main weakness are that the learning can only use correct configuration files.
+This model is then used to check if a new configuration file adheres to those rules.
+If a file is incorrect, the tool identifies the location of error and reports what is incorrect.
+For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so"} before \texttt{"extension recode.so"}.
+While this prototype's results are promising, the main weakness is that the learning can only use correct configuration files.
 Additionally, there is a relatively high false positive rate (marking correct files as incorrect).
 
-In order to extend the prototype, in this paper we provide a new description of ConfigC in terms of version space learning.
+%What do we 'plan' to do to extend this (labeled correct and incorrect)
+In order to extend ConfigC, in this paper we provide a new description of ConfigC in terms of version space learning.
 This description will allow us to understand how the justifications are produced in ConfigC.
 We can then extend ConfigC with a new algorithm to decrease the false positive rate, while maintaining the ability to provide justification.
-%and show that the results are garunteed to be complete.
 
-%Although the results are complete, the approach used previously produces a high false positive rate.
 We propose an extension to ConfigC that allows it to handle both correct and incorrect files in the training set.
@@
 While the previous training set from ConfigC was a random sampling of configuration files, many other training sets have a structure based on version history.
-%The algorithm we propose takes advantage of this commonly availible, but underutilized structure of training sets for software analysis.
-%Because most code does not exist in isolation, but changes over time with development, any training set of code from a verison control system, like Github, has a rich temporal structure. 
-This structure is simply a partial order, and can be used by our proposed algorithm for more effective learning.
-%A learning algorithm that uses the temporal structure of code to create sound classification with a low false positive rate can be used in at least the above listed software analysis techniques.
+The algorithm we propose takes advantage of this commonly available, but underutilized structure of training sets for software analysis.
+Because most code does not exist in isolation, but changes over time with development, any training set of code from a version control system, like Github, has this rich temporal structure. 
+This structure is a partial order over time, and can be used by our proposed algorithm for more effective learning.
 
+%evaluation plans
 To test this approach in practice, we plan to implement our algorithm to check for TravisCI\footnote{\url{http://www.travis-ci.com}} configuration errors.
@@
 
-Our main contributions are then as follow:
+Our main contributions are as follow:
 
@@
 
-\item We give a description of our prototype tool, ConfigC, in the context of version space learning.
-\item We propose a new algorithm for ConfigC to handle both incorrect and correct training data, as well as internal structure of a training set.
+\item We give a description of our tool, ConfigC, in the context of version space learning.
+\item We propose a new algorithm to handle both incorrect and correct training data, as well as the internal structure of a training set.
 \item We propose a real-world application of this approach, and outline the steps needed for an implementation.

### 2017-05-05 ISSTA17/secs/related.tex
expaneded version of FMCAD for ISSTA

--- 2017-04-17 OOPSLA17/secs/related.tex
@@
 services for convenient network reasoning and management.
-Compared with the above efforts, \app mainly focuses on software systems, 
+Compared with the above efforts, our work focuses on software systems, 
 \eg, MySQL and Apache, and our main purpose is to automate configuration
@@
 to convenient configuration-file writing.
-The closest effort to \app is ConfigC~\cite{santolucitoCAV},
-which aims to learn configuration-checking rules from a given training
-set. Compared with \app, ConfigC has the following disadvantages.
-First, ConfigC requires the configuration files in the training set must 
-be correct, which is impractical because it is very difficult to
-determine a correct configuration set in reality.
-Second, ConfigC covers fewer types of misconfigurations than \app. 
-Finally, the training time of ConfigC is much longer than \app.
 
@@
 whether given configuration files meet administrators' specifications. 
-Different from \app, ConfValley does not
+As opposed to our work, ConfValley does not
 have inherent misconfiguration checking capability, since it only offers
@@
 manually write specifications, which is an error-prone
-process. On the contrary, \app does not need users to manually
+process. On the contrary, our work does not need users to manually
 write anything.
@@
 failures occur, which leads to prolonged recovery time.
-
-\para{Association Rule Learning}
-The approach we have presented not only generalizes association rule learning, but also another learning strategy called \textit{sequential pattern mining}~\cite{mabroukeh2010taxonomy}.
-Ordering rules are similar to the patterns learned in sequential pattern mining, although we restrict our ordering rules to $|S|,|T|=1$ since these are the most common misconfigurations we encounter in practice.
-While a major limitation to sequential pattern mining is the scalability of the problem~\cite{ayres2002sequential}, we escape this issue with $|S|,|T|=1$ and the fact that a single configuration file tends to be less a few thousand lines.
-There has been other work in these same classes of algorithms~\cite{han2007frequent,langley1995applications} for various applications and variations on the core problem.
-A future direction for this work is to integrate advances in these domains into the configuration file verification problem.

### 2017-05-05 ISSTA17/secs/temporal.tex
expaneded version of FMCAD for ISSTA

--- 2016-10-03 Travis/secs/temporal.tex
@@
 
-Since a TravisCI configuration file is dependent on the code it is trying to build, we must consider a more general sense of configuration file.
-We will call this a program summary $P_t$, which is a representation of the repository which contains the information relevant to the learning process.
+While in ConfigC, configuration files were labeled in isolation from their system by an expert, TravisCI configurations are automatically labeled with respect to their containing repository.
+Because the correctness of TravisCI configuration files is dependent on the code it builds, we must model more than just the configuration file, $C$. 
+We introduce a program summary $P_t$, which is a combination of $C$ as well as the information relevant to the learning process from the repository.
 The subscript on $P_t$ is a timestamp tag based on the ordered git commit history.
@@
 %IMPORTANT, but no space
-However, a git history is not a limited to a single linear timeline.
-Git features the ability to \textit{branch}, which allows to simultaneous commit chains.
+However, most versioning systems do not limit version history to a single linear timeline.
+For example, Git features the ability to \textit{branch}, which allows to simultaneous commit chains.
 To handle the start of a branch, add a superscript to indicate the branch, and restart the counter on a branch.
@@
 We then say that $P_{t'}^{y}$ has no successor commit $P_{t'+1}^{y}$.
-Note the ability to handle branching implies this method is suitable to any learning set which has a partial order.
+Note the ability to handle branching implies this method is suitable to any training set which has a partial order.
 
@@
 Note that this is an inclusive disjunction, since a erroring commit can break multiple things at once.
-Expressed formally, where $\setminus$ is the set difference, that is:
+When comparing multiple versions of configurations, it is important that we look at the difference between the models $M(P)$ and not just $P$.
+In the latter case, we would treat individual lines as error sources, when in fact we want to detect the relations between configuration settings.
+Expressed formally, where $\setminus$ is the set difference, we learn the following from a breaking commit:
 \begin{align}
@@
 
-We then can combine Eq \ref{eq:E}, \ref{eq:P}, and \ref{eq:PE} with conjunctions and ask a SMT solver for a model satifying the formula.
+We then can combine Eq \ref{eq:E}, \ref{eq:P}, and \ref{eq:PE} with conjunctions and ask a SMT solver for a model satisfying the formula.
 The resulting model will be the sets $Nec$, and $Br$, which can be used to check new configuration files.

### 2017-05-05 ISSTA17/secs/vspace_verify.tex
expaneded version of FMCAD for ISSTA

--- 2016-10-03 Travis/secs/vspace_verify.tex
@@
  \hline
- Template & Input  & Relation \\
+ Template & Arity & Relation \\
 \hline
- ordering & (Line,Line) & Before $\vert$ After $\vert$ None \\
+ ordering &            2 & Before $\vert$ After $\vert$ None \\
 \hline
- integer relation & (Line,Line)  & $< | == | >$  \\
+ coarse relation &     2  & $< | == | >$  \\
 \hline
- type & (Line,Line)  & String $\vert$ Int $\vert$ Filepath $\vert$ IP  \\
+ fine-grain relation & 3  & $< | == | >$  \\
 \hline
- missing entry & (Line,Line) & Required $\vert$ Not \\
+ type &                1  & String $\vert$ Int $\vert$ Boolean $\vert$ IP  \\
+\hline
+ missing entry &       2 & Required $\vert$ Not \\
 \hline
@@
 
-%When the system is run on a new file, one of the relations from the templates will not be satisfied.
-%To provide an error message, the system only needs to report which relation is not satisfied.
+When the system is run on a new file, one of the relations from the templates will not be satisfied.
+To provide an error message, the system only needs to report which relation is not satisfied.

### 2017-05-06 ISSTA17/secs/intro.tex
redoing intro a bit

@@
 %what is the problem
-Configuration files provide easy access to the most critical parameters of software systems in order to quickly tune the behavior system.
+Configuration files provide easy access to the most critical parameters of software systems in order to quickly tune the behavior of a system.
 This expressive power in a single file creates a large surface for potential errors that can degrade performance or take down systems entirely.
-The verification task for configuration files cannot be addressed with traditional software analysis techniques.
-There are rarely formal specifications of a correct configuration, 
+The verification task for configuration files cannot be addressed with traditional software analysis techniques because they take a less structured form than a program.
+As opposed to programs, configuration files rarely have formal specifications of a correctness, 
   the source code of the underlying system may not be available, 
   and the configuration may depend on the external environment such as the network or available hardware.
-To address this issue, we propose a method for automated configuration file verification using a data set of labeled examples of correct and incorrect configurations.
-
-%what approach do we take to the problem
-In previous work, we used version space learning for configuration file verification.
-We extend that work which only works on correct examples, to work on temporally structured correct and incorrect examples by building an SMT formula to find a classification model.
-As a demonstration of this algorithm, we plan to implement it to automatically verify TravisCI configurations.
-The algorithm will utilize Github histories to allow us to detect potential build errors without actually building, saving valuable programmer and server time.
-
-%why cant we use existing approach
-%legibility issue
-Machine learning has been used in various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
-However, many popular machine learning algorithms, such as neural nets and n-gram models, are not designed to provide simple justifications for their classification results.
-While effective in practice, the lack of justification for the results limits the applicability to software analysis, where justification is often critical.
-For example, in the case of error detection, the system should not only report which files have errors, but also locate the errors.
-This justification issue is also called \textit{legibility} of machine learning.
-
-%correctness issue
-Additionally, these probabilistic approaches to machine learning cannot be guaranteed to be complete, that is they will always find the error.
-We use version space learning to address the need for a formal completeness guarantee in an automated model generation for verification.
-Version space learning is a technique for logical constraint classification~\cite{mitchell82}.
-As a logical constraint system, version space learning can provide the justification that is difficult to obtain from other methods, but its main weakness is that it cannot handle noisy data.
+To overcome the unique challenges in this domain, we propose a method for automated configuration file verification using a data set of labeled examples of correct and incorrect configurations.
 
 %What have we already done (labeled correct)
-In our previous work~\cite{Santolucito2016} we built a prototype to verify configuration files from a set of correct examples.
-The tool, ConfigC, takes as a training set a set of correct configuration files and builds a set of rules describing a language model.
+In our previous work~\cite{Santolucito2016} we built the tool ConfigC to verify configuration files from a set of correct examples.
+ConfigC takes as a training set a set of correct configuration files and builds a set of rules describing a language model.
 This model is then used to check if a new configuration file adheres to those rules.
@@
 For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so"} before \texttt{"extension recode.so"}.
-While this prototype's results are promising, the main weakness is that the learning can only use correct configuration files.
+While ConfigC's results are promising, the main weakness is that the learning can only use correct configuration files.
 Additionally, there is a relatively high false positive rate (marking correct files as incorrect).
@@
 %What do we 'plan' to do to extend this (labeled correct and incorrect)
-In order to extend ConfigC, in this paper we provide a new description of ConfigC in terms of version space learning.
-This description will allow us to understand how the justifications are produced in ConfigC.
-We can then extend ConfigC with a new algorithm to decrease the false positive rate, while maintaining the ability to provide justification.
+Here we propose to extend that work, which only works on correct examples, to work on both correct and incorrect examples by building an SMT formula to find a classification model.
+By learning over both correct and incorrect examples, we expect that we will be able to decrease the high false positive rate observed in ConfigC.
+In order to extend ConfigC, we first provide a new description of ConfigC in terms of version space learning.
+This description allows us to understand how the error reports are are produced in ConfigC.
+Any extension to ConfigC must maintain the \textit{legibility} of learning - the tool must not only classify configuration files as correct or incorrect, but also identify the contributing factors (misconfigurations) to that classification.
 
-We propose an extension to ConfigC that allows it to handle both correct and incorrect files in the training set.
-Additionally, we extend ConfigC with the ability to use structure within the training set.
-While the previous training set from ConfigC was a random sampling of configuration files, many other training sets have a structure based on version history.
-The algorithm we propose takes advantage of this commonly available, but underutilized structure of training sets for software analysis.
+Additionally, our extension takes advantage of a commonly available, but underutilized structure of training sets for software analysis.
+While the previous training sets for ConfigC were an unsorted sampling of configuration files, typically we can obtain training sets that have a structure based on version history.
 Because most code does not exist in isolation, but changes over time with development, any training set of code from a version control system, like Github, has this rich temporal structure. 
 This structure is a partial order over time, and can be used by our proposed algorithm for more effective learning.
+
+%TODO NOW NEED TO CONNECT BACK TO legibility
+
+%legibility issue
+Machine learning has been used in various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
+However, many popular machine learning algorithms, such as neural nets and n-gram models, lack legibility and so are not able to provide simple justifications for their classification results.
+While these classification may be effective, the lack of justification for the results limits the applicability to software analysis, where justification is often critical.
+For example, in the case of error detection, the system should not only report which files have errors, but also locate the errors so a user may fix them.
+
+%correctness issue
+Additionally, these probabilistic approaches to machine learning cannot be guaranteed to be complete, that is they are not guaranteed to always find an error if one exists.
+We use version space learning to address the need for a formal completeness guarantee in an automated model generation for verification.
+Version space learning is a technique for logical constraint classification~\cite{mitchell82}.
+As a logical constraint system, version space learning not only provides justification of its classification results, but is has the foundation to build a completeness proof without the need for probabilistic thresholds.
+
+As a demonstration of this algorithm, we plan to implement it to automatically verify TravisCI configurations.
+The algorithm will utilize the temporal ordering on code in Github histories to allow us to detect potential build errors without actually building, saving valuable programmer and server time.
 

### 2017-05-06 ISSTA17/secs/intro.tex
submitted version

@@
 Here we propose to extend that work, which only works on correct examples, to work on both correct and incorrect examples by building an SMT formula to find a classification model.
-By learning over both correct and incorrect examples, we expect that we will be able to decrease the high false positive rate observed in ConfigC.
+By learning over both correct and incorrect examples, our hypothesis is that we will be able to decrease the high false positive rate observed in ConfigC, making the tool more useful to end users.
 In order to extend ConfigC, we first provide a new description of ConfigC in terms of version space learning.
@@
 Any extension to ConfigC must maintain the \textit{legibility} of learning - the tool must not only classify configuration files as correct or incorrect, but also identify the contributing factors (misconfigurations) to that classification.
+
+%legibility issue
+Legibility is a difficult property to achieve in machine learning and an active area of research~\cite{lei2016rationalizing}.
+Although machine learning has been used in various software analysis techniques, such as programming-by-example \cite{lau2000version} and invariant synthesis \cite{garg2014ice}, this requires careful selection of the algorithms.
+<any popular machine learning algorithms, such as neural nets and n-gram models, notoriously lack legibility and so are not well-suited to to provide simple justifications for their classification results.
+The lack of justification for the results limits the applicability to software analysis, where providing feedback to a user is critical.
+For example, in the case of error detection, the system should not only report which files have errors, but also locate the errors so a user may fix them.
+By using non-probabilistic version space learning, we expect to have a highly level of legibility in our learning results.
+
+%correctness issue
+Additionally, probabilistic approaches to machine learning cannot be guaranteed to be complete, that is they are not guaranteed to always find an error if one exists.
+We use version space learning to address the need for a formal completeness guarantee in an automated model generation for verification.
+Version space learning is a technique for logical constraint classification~\cite{mitchell82}.
+As a logical constraint system, version space learning not only provides justification of its classification results, but is has the foundation to build a completeness proof without the need for probabilistic thresholds.
 
@@
 
-%TODO NOW NEED TO CONNECT BACK TO legibility
-
-%legibility issue
-Machine learning has been used in various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
-However, many popular machine learning algorithms, such as neural nets and n-gram models, lack legibility and so are not able to provide simple justifications for their classification results.
-While these classification may be effective, the lack of justification for the results limits the applicability to software analysis, where justification is often critical.
-For example, in the case of error detection, the system should not only report which files have errors, but also locate the errors so a user may fix them.
-
-%correctness issue
-Additionally, these probabilistic approaches to machine learning cannot be guaranteed to be complete, that is they are not guaranteed to always find an error if one exists.
-We use version space learning to address the need for a formal completeness guarantee in an automated model generation for verification.
-Version space learning is a technique for logical constraint classification~\cite{mitchell82}.
-As a logical constraint system, version space learning not only provides justification of its classification results, but is has the foundation to build a completeness proof without the need for probabilistic thresholds.
-
-As a demonstration of this algorithm, we plan to implement it to automatically verify TravisCI configurations.
-The algorithm will utilize the temporal ordering on code in Github histories to allow us to detect potential build errors without actually building, saving valuable programmer and server time.
-
 %evaluation plans
@@
 This ensures the tool can always be automatically built correctly on a fresh machine.
+The algorithm will utilize the temporal ordering on code in Github histories to allow us to detect potential build errors without actually building, saving valuable programmer and server time.
 

### 2017-05-06 ISSTA17/secs/limits.tex
expaneded version of FMCAD for ISSTA
notes
submitted version

--- 2016-10-03 Travis/secs/limits.tex
@@
-\section{Limitations}
+\section{Properties of Temporal Learning}
 
-%\subsection{Unsatisfiability}
-Note we have made two assumptions in Eq.
-\ref{eq:E1}; first that the summary $P_t$ sufficently detailed, i.e.
+We have made two assumptions in Eq.
+\ref{eq:E1}; first that the summary $P_t$ sufficiently detailed, i.e.
 contains every piece of information that might lead to a build error, and second that the model $M(P_t)$ will learn all relations that might lead to a build error, i.e.
-has a templete for all types of errors.
+has a template for all types of errors.
 While these are the strong assumptions - our algorithm is able to detect cases where these assumptions are not met.
-If we cannot find a solution for Eq. \ref{eq:PE}, it means either $P_t$ or $M(P_t)$ has been underspecified.
+If we cannot find a solution for Eq. \ref{eq:PE}, it means either $P_t$ or $M(P_t)$ has been underspecified and is insufficiently detailed.
 It is then the user's responsibility to expand the definitions accordingly.
 
-\subsection{Trusted Base}
-In addition to the completeness of $P_t$ and $M(P_t)$, we must pick a trusted base.
+In addition to the sufficient detail of $P_t$ and $M(P_t)$, we must pick a trusted base.
 Since it is possible for TravisCI to have bugs, it is possible that between versions of TravisCI, two identical program summaries may have different build statuses.
@@
 $P_t = P_{t'} \implies S(P_t) = S(P_{t'})$.
+If we allow for noisy data, for example in the case that it is not possible to identify a trusted base, this predicate will no longer hold.
+This situation would require a noise tolerant version space learning~\cite{hong1997generalized}, though this may degrade the completeness guarantees.
+
+Picking the right assumptions upon which to build a completeness and soundness proof remain future work, either with a trusted base, or in the noisy context.
+Choosing the right assumption and building these proofs are a valuable direction, as it will allow us to identify which parts of the model and training set are most important to ensure coverage of the system.

### 2017-05-06 ISSTA17/secs/related.tex
notes
submitted version

@@
 
-Configuration verification has been considered a promising way  
+Static configuration verification has been proposed as an effective way  
 to tackle misconfiguration problems~\cite{xu15systems}.
@@
 
+%rewritten
 \para{Language-support misconfiguration checking}
-There have been several language-support efforts proposed for preventing
-configuration errors introduced by fundamental deficiencies in
-either untyped or low-level languages. For example, in the network
-configuration management area, administrators often
-produce configuration errors in their routing configuration files.
-PRESTO~\cite{enck07configuration} 
-automates the generation of device-native configurations
-with configlets in a template language. 
-Loo {\em et al.}~\cite{loo05declarative} adopt Datalog to reason about 
-routing protocols in a declarative fashion. 
-COOLAID~\cite{chen10declarative} constructs
-a language to describe domain knowledge about devices and
-services for convenient network reasoning and management.
-Compared with the above efforts, our work focuses on software systems, 
-\eg, MySQL and Apache, and our main purpose is to automate configuration
-verification rather than proposing new languages 
-to convenient configuration-file writing.
+One approach to statically checking configuration files is to avoid the difficult and unstructured nature of configuration files in the first place.
+To that end efforts have introduced special configuration languages that overcome the fundamental deficiencies in the existing untyped or low-level configuration languages. 
+For example, network administrators often produce configuration errors in their routing configuration files.
+PRESTO~\cite{enck07configuration} introduces configlets as a template language to automates the generation of device-native configurations.
+Other work uses Datalog to reason about routing protocols in a declarative fashion~\cite{loo05declarative}. 
+COOLAID~\cite{chen10declarative} is a domain specific language to describe knowledge about network devices and services.
+In contrast to this approach, our main purpose is to automate configuration verification of existing configuration languages, rather than proposing new, more powerful languages.
+This is largely motivated by the unwieldy amount of existing configuration files in industry production.
+%Furthermore, new systems are likely to continue to support the simple, unstructured style of existing configuration files beacuse the
 
-\para{Misconfiguration detection}
-Misconfiguration detection techniques aim at checking configuration
-efforts before system outages occur.
-Most existing detection approaches check 
-the configuration files against a set of predefined correctness 
-rules, named constraints, and then report errors if 
-the checked configuration files do not satisfy these rules.
-Huang {\em et al.}~\cite{huang15confvalley},
-for example, proposed a 
-language, ConfValley, to validate 
-whether given configuration files meet administrators' specifications. 
-As opposed to our work, ConfValley does not
-have inherent misconfiguration checking capability, since it only offers
-a language representation and requires administrators to
-manually write specifications, which is an error-prone
-process. On the contrary, our work does not need users to manually
-write anything.
+One approach to preemptive error detection is to use predefined constraints, or correctness rules, for checking.
+After encoding these constraints, it is straightforward to report errors if a target configuration file does not satisfy these rules.
+For example, ConfValley is specification language for administrators to provide constraints on their systems' configurations~\cite{huang15confvalley}. 
+This approach requires that administrators manually write specifications - an error-prone and difficult process. 
+In contrast, by using a learning approach, our work does not require users to manually write any specifications.
 
-Several machine learning-based misconfiguration detection efforts 
-also have been proposed~\cite{yuan11context, zhang14encore, xu16early}.
-EnCore~\cite{zhang14encore} introduces a template-based
-learning approach to improve the accuracy of their learning results.
-The learning process is guided by a set of predefined rule templates
-that enforce learning to focus on patterns of interest.
-In this way, EnCore filters out irrelevant information and reduces
-false positives; moreover, the templates are able to express
-system environment information that other machine learning
-techniques cannot handle.
-Compared with EnCore, \app has the following advantages.
-First, \app does not rely on any template. 
-Second, EnCore cannot detect missing entry errors, type errors,
-ordering errors and fine-grained integer correlation errors,
-but \app can detect all of them.
-Finally, \app is a very automatic system, but
-EnCore needs significant human interventions, \eg, system parameters
-and templates.
+\para{Learning}
+Using machine learning to tackle misconfiguration detection has also been explored~\cite{yuan11context, zhang14encore, xu16early}.
+As an example, EnCore~\cite{zhang14encore} uses a rule learning approach, augmented with user provided templates, to improve the accuracy of their learning results.
+The learning process is guided by a set of predefined rule templates that enforce learning to focus on patterns of interest and allow the problem to scale over larger training sets.
+EnCore uses the templates to filters out configuration entries that are unlikely to cause errors to reduce false positives.
+The templates are also used to directly encode system environment information that would not be contained in the training set for their machine learning.
+Compared with EnCore, our approach does not rely on templates - everything is automatically generated.
+Furthermore, none of the above approaches use the temporal ordering on the training set inside the learning process.
 
-PCheck~\cite{xu16early} aims to add configuration checking code to the system source code by emulating potential commands and behaviors of the system. 
-This emulation is a ``white-box'' approach and requires access to the system's source code.
-One drawback to this approach is that for some systems (\eg, ZooKeeper) whose behavior is 
-hard to emulate, PCheck cannot automatically generate the corresponding checking code.
+\para{White-box}
+In our approach we assume a ``black-box'' model where we cannot access the system source code.
+This is as opposed to a ``white-box'' model, where the source code is available and can leveraged in the configuration analysis.
+Although this is a strong assumption, PCheck~\cite{xu16early} explores misconfiguration detection by adding configuration checking code directly in the system source code.
+The system is then emulating with various potential configurations of the system.
+One drawback to this approach is that for some systems (\eg, ZooKeeper) whose behavior is hard to emulate, PCheck cannot automatically generate the corresponding checking code.
 Due to the emulation based testing strategy, PCheck's scope is limited to reliability problems caused by misconfiguration parameters. 
 In contrast, \app is a ``black-box'' approach and only requires a training set of configuration files to learn rules.
-By using a rule learning strategy of examples, \app is able to detect general misconfiguration issues that are outside the scope of emulation testing (\eg memory or thread usage settings), including performance, security, availability and reliability.
+By using the version space learning strategy of examples, we are also able to detect general misconfiguration issues that are outside the scope of emulation testing (\eg memory or thread usage settings), including performance, security, availability and reliability.
 
+\iffalse
+%TODO rewrite
 \para{Misconfiguration diagnosis}
@@
 failures occur, which leads to prolonged recovery time.
+\fi

### 2017-06-26 ISSTA17/secs/completeConfigC.tex
submitted version
camera ready - take 1

@@
-ConfigC is complete but unsound.
+\subsection{Completeness}
+
+We demonstrate that ConfigC is complete but unsound.
+That is, we will always detect a misconfiguration, but may also report correct files as misconfigurations.
 We first define the set of incorrect files based on ground truth $Inc_{gt}$, and the set of files which are predicted by the model to be incorrect, $Inc_{prd}$.
@@
 The definition of $Inc_{prd}$ follows from the description of the algorithm.
-
+%
 \begin{align}
@@
 Our definition of sound and complete are as follows:
-
+%
 \begin{align}
@@
 Completeness follows from showing that $Inc_{gt} \subseteq Inc_{prd}$.
-The algorithm is complete if, for any file which breaks a relation for which we have a template (a misconfiguration) and have seen an correct example, the system will mark that file as incorrect.
+The algorithm is complete if, for any file which breaks a relation for which we have a template (a misconfiguration) and have seen a correct example, the system will mark that file as incorrect.
 Since the model always maintains the strongest conditions for correctness for any file, the algorithm is clearly complete.

### 2017-06-26 ISSTA17/secs/intro.tex
camera ready - take 1

@@
 %What have we already done (labeled correct)
-In our previous work~\cite{Santolucito2016} we built the tool ConfigC to verify configuration files from a set of correct examples.
+In our previous work~\cite{Santolucito2016}, we built the tool ConfigC to verify configuration files from a set of correct examples.
 ConfigC takes as a training set a set of correct configuration files and builds a set of rules describing a language model.
@@
 If a file is incorrect, the tool identifies the location of error and reports what is incorrect.
-For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so"} before \texttt{"extension recode.so"}.
+For example, when analysing MySQL configurations, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so"} before \texttt{"extension recode.so"}.
 While ConfigC's results are promising, the main weakness is that the learning can only use correct configuration files.
@@
 By learning over both correct and incorrect examples, our hypothesis is that we will be able to decrease the high false positive rate observed in ConfigC, making the tool more useful to end users.
-In order to extend ConfigC, we first provide a new description of ConfigC in terms of version space learning.
-This description allows us to understand how the error reports are are produced in ConfigC.
+In order to extend ConfigC, we first provide a new description of ConfigC in terms of version space learning~\cite{mitchell82}.
+This description allows us to understand how the error reports are produced in ConfigC.
 Any extension to ConfigC must maintain the \textit{legibility} of learning - the tool must not only classify configuration files as correct or incorrect, but also identify the contributing factors (misconfigurations) to that classification.
@@
 Although machine learning has been used in various software analysis techniques, such as programming-by-example \cite{lau2000version} and invariant synthesis \cite{garg2014ice}, this requires careful selection of the algorithms.
-<any popular machine learning algorithms, such as neural nets and n-gram models, notoriously lack legibility and so are not well-suited to to provide simple justifications for their classification results.
+Many popular machine learning algorithms, such as neural nets and n-gram models, notoriously lack legibility and so are not well-suited to to provide simple justifications for their classification results.
 The lack of justification for the results limits the applicability to software analysis, where providing feedback to a user is critical.
@@
 We use version space learning to address the need for a formal completeness guarantee in an automated model generation for verification.
-Version space learning is a technique for logical constraint classification~\cite{mitchell82}.
+Version space learning is a technique for logical constraint classification.
 As a logical constraint system, version space learning not only provides justification of its classification results, but is has the foundation to build a completeness proof without the need for probabilistic thresholds.
@@
 A user adds a configuration file to the repository that enables TravisCI and specifies build conditions, such as which compiler to use, which dependencies are required, and a set of benchmarks to test.
-This ensures the tool can always be automatically built correctly on a fresh machine.
+This gives the developer confidence the code can always be automatically built correctly on a fresh machine.
 The algorithm will utilize the temporal ordering on code in Github histories to allow us to detect potential build errors without actually building, saving valuable programmer and server time.
@@
 If these malformed projects could be quickly statically checked on the client side, both TravisCI and its users could benefit.
+
+While ConfigC was applied to MySQL configurations, and we propose our next application as TravisCI, this approach can be used for any configuration language.
+TravisCI is just one example of an easily accessible set of labeled configuration files with a partial order.
 

### 2017-06-26 ISSTA17/secs/limits.tex
camera ready - take 1

@@
 has a template for all types of errors.
-While these are the strong assumptions - our algorithm is able to detect cases where these assumptions are not met.
-If we cannot find a solution for Eq. \ref{eq:PE}, it means either $P_t$ or $M(P_t)$ has been underspecified and is insufficiently detailed.
-It is then the user's responsibility to expand the definitions accordingly.
+While these are strong assumptions, our algorithm is able to detect cases where these conditions are not met.
+If we cannot find a solution for Eq. \ref{eq:PE}, it means either $P_t$ or $M(P_t)$ has been underspecified and is insufficiently detailed, and the definitions must be expanded accordingly.
 
 In addition to the sufficient detail of $P_t$ and $M(P_t)$, we must pick a trusted base.
-Since it is possible for TravisCI to have bugs, it is possible that between versions of TravisCI, two identical program summaries may have different build statuses.
+Since TravisCI may not always be backwards compatible, it is possible that between versions of TravisCI, two identical program summaries may have different build statuses.
 Since version space learning is (generally) intolerant of noise, we require that

### 2017-06-26 ISSTA17/secs/related.tex
camera ready - take 1

@@
 \section{Related Work}
-
-Static configuration verification has been proposed as an effective way  
-to tackle misconfiguration problems~\cite{xu15systems}.
-Nevertheless, a practical and automatic configuration
-verification approach still remains an open problem.
 
@@
 
-One approach to preemptive error detection is to use predefined constraints, or correctness rules, for checking.
-After encoding these constraints, it is straightforward to report errors if a target configuration file does not satisfy these rules.
-For example, ConfValley is specification language for administrators to provide constraints on their systems' configurations~\cite{huang15confvalley}. 
+Another language based approach is used by ConfValley, a specification language for administrators to provide constraints on their systems' configurations~\cite{huang15confvalley}. 
 This approach requires that administrators manually write specifications - an error-prone and difficult process. 
@@
 The system is then emulating with various potential configurations of the system.
-One drawback to this approach is that for some systems (\eg, ZooKeeper) whose behavior is hard to emulate, PCheck cannot automatically generate the corresponding checking code.
+One drawback to this approach is that for some systems (e.g. ZooKeeper) whose behavior is hard to emulate, PCheck cannot automatically generate the corresponding checking code.
 Due to the emulation based testing strategy, PCheck's scope is limited to reliability problems caused by misconfiguration parameters. 
-In contrast, \app is a ``black-box'' approach and only requires a training set of configuration files to learn rules.
-By using the version space learning strategy of examples, we are also able to detect general misconfiguration issues that are outside the scope of emulation testing (\eg memory or thread usage settings), including performance, security, availability and reliability.
+In contrast, our work is a ``black-box'' approach and only requires a training set of configuration files to learn rules.
+By using the version space learning strategy of examples, we are also able to detect general misconfiguration issues that are outside the scope of emulation testing (e.g.
+memory or thread usage settings), including performance, security, availability and reliability.
 
@@
 tracks causality and automatically fixes 
-misconfigurations. Unlike \app, most misconfiguration
+misconfigurations. Unlike our work, most misconfiguration
 diagnosis efforts aim at finding errors after system

### 2017-06-26 ISSTA17/secs/temporal.tex
camera ready - take 1

@@
 
-While in ConfigC, configuration files were labeled in isolation from their system by an expert, TravisCI configurations are automatically labeled with respect to their containing repository.
+While in ConfigC, configuration files were manually labeled in isolation from their system by an expert, TravisCI configurations are automatically labeled with respect to their containing repository.
 Because the correctness of TravisCI configuration files is dependent on the code it builds, we must model more than just the configuration file, $C$. 
@@
 The subscript on $P_t$ is a timestamp tag based on the ordered git commit history.
-In the case of TravisCI, this include the \verb|.travis.yml| file, as well as code features that may effect build status, such as programming language and a list of imported libraries.
-The summary must be \textit{sufficiently detailed}, that is it must contain every piece of information that might lead to a build error.
+In the case of TravisCI, this include the \verb|.travis.yml| file, as well as code features that may affect build status, such as programming language and a list of imported libraries.
+The summary must be \textit{sufficiently detailed}, that is, it must contain every piece of information that might lead to a build error.
 
@@
 However, most versioning systems do not limit version history to a single linear timeline.
-For example, Git features the ability to \textit{branch}, which allows to simultaneous commit chains.
-To handle the start of a branch, add a superscript to indicate the branch, and restart the counter on a branch.
+For example, Git features the ability to \textit{branch} and create temporally simultaneous commit chains.
+To handle the start of a branch, we add a superscript to indicate the branch ($x$ and $y$ here).
 To handle the merge of two branches $P_{t}^{x}$ and $P_{t'}^{y}$, step to $P_{t+1}^{x}$, where $x$ is the mainline branch.
@@
 
-In contrast with ConfigC, we now consider both incorrect and correct and so must introduce the \textit{general boundary}.
+In contrast with ConfigC, we now consider both incorrect and correct examples and so must introduce the \textit{general boundary}.
 The general boundary is the dual of the specific boundary, and is the most relaxed requirement for a positive classification.
@@
 
+In fact, to make full use of the partial order, we can generalize Eq \ref{eq:PE} to $P_{t,t+n}$.
+For example, the pattern $Pass_0,Err_1,Pass_2,Err_3$ yields a PE pattern on $P_{0,1}$, $P_{2,3}$, and $P_{0,3}$. 
+More complex chains could be built in the case of branching.
+
 We then can combine Eq \ref{eq:E}, \ref{eq:P}, and \ref{eq:PE} with conjunctions and ask a SMT solver for a model satisfying the formula.
@@
 Thanks to the practice of making incremental commits when using source control, these sets will be small and the SMT will be fairly cheap.
-In fact, the above implication generalizes to $P_{t,t+n}$, but for efficiency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is manageably small.
-The definition of small here remains to be experimentally determined.
+However, for efficiency we must choose a maximum $n$ such that $M(P_{t})\ \setminus M(P_{t+n})$ is manageably small.
+The definition of small and selection of maximum $n$ remains to be experimentally determined.

### 2017-06-26 ISSTA17/secs/vspace_verify.tex
submitted version
camera ready - take 1

@@
 As an example, ConfigC might derive the relation \texttt{extension mysql.so} comes before \texttt{extension recode.so} by using the ordering template.
-ConfigC features the following default templates.
-
-\begin{center}
-\begin{tabular} {|c |c |c |}
- \hline
- Template & Arity & Relation \\
-\hline
- ordering &            2 & Before $\vert$ After $\vert$ None \\
-\hline
- coarse relation &     2  & $< | == | >$  \\
-\hline
- fine-grain relation & 3  & $< | == | >$  \\
-\hline
- type &                1  & String $\vert$ Int $\vert$ Boolean $\vert$ IP  \\
-\hline
- missing entry &       2 & Required $\vert$ Not \\
-\hline
-\end{tabular}
-\end{center}
+ConfigC includes default templates for ordering, integer relations ($<,=,>$), type errors, and missing entries (two keywords must appear together irrespective of order).
 
@@
 To relax the model, two sets of relations from two files are merged into a single consistent set.
-\begin{lstlisting}
-n = {}
-for (c in files):
-  n1 = M(c)
-  n = merge(n, n1)
-\end{lstlisting}
+
+When the system is run on a new file, one of the relations from the templates will not be satisfied.
+To provide an error message, the system only needs to report which relation is not satisfied.
 
@@
 This is a problem when a user is then asked to manually review many files for errors, when the files are in fact correct.
-
-When the system is run on a new file, one of the relations from the templates will not be satisfied.
-To provide an error message, the system only needs to report which relation is not satisfied.
+However, the benefit to this approach is that, given the coverage of the training set, every misconfiguration will be detected.
